---
title: "Create df_prep and df_pairs"
format: html
---


```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)

```

> Sales are not winsorized

```{r warning = FALSE, message = FALSE}
#res_sales  <- readRDS("./data/processed/res_sales.rds") |> filter(sale_date > date("2010-01-01"))  

res_sales  <- readRDS("./data/processed/res_sales_buildings.rds") |> filter(sale_date > date("2010-01-01"))

pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

nicknames <- readxl::read_xlsx("../Merriman RA/ptax/Necessary_Files/muni_shortnames.xlsx")

pin_muni_key <- pin_muni_key |> left_join(nicknames)


```

```{r dropped_pins, message = FALSE}
# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N Lakeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000",     # another CoOp
               "21301140150000",  # vacant lot by the lake, 
               "21301140160000"   # vacant lot by the lake
               
)

res_sales <- res_sales |> 
  filter(pin %nin% drop_pins ) |>
  mutate(sale_price =  # price corrections randomly spotted 
         case_when(
           pin == "15154220240000" & sale_date == as_date("2006-11-01") ~ 180000,   # not 180 million
           pin == "08153010051151" ~ 81000, # not 81 million
         TRUE ~ sale_price)) |>
   # a couple outliers were in there
  filter( sale_price < 5000000)



repeat_sales <- res_sales |> 

  group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup() 



```

```{r warning = FALSE, message = FALSE}
puni_pins <- read_csv("data/processed/floodfactor_scores.csv")

pin_muni_key <- left_join(pin_muni_key, puni_pins)



```

```{r make-df_prep, message = FALSE}

# 1) Make sure sale_date is a Date (if not already)
df_prep <- repeat_sales %>%
  mutate(
    sale_year  = year(sale_date),
    eff_date = ymd(EFF_DATE),
    pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date, sale_year, sale_price, in_eff_sfha, in_prelim_sfha, 
         eff_date, pre_date, in_lomr, addedto_eff_sfha, removedfrom_eff_sfha,
         addedto_prelim_sfha, removedfrom_prelim_sfha, condo, class) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



df_prep <- left_join(df_prep, pin_muni_key)

df_prep <- df_prep |> 
  mutate(
    event = ifelse(sale_date <= as_date("2020-06-29"), "1. Pre", "2. Post"),
    high_ff_score = ifelse(env_flood_fs_factor > 4, TRUE, FALSE),
    new_info_released = as_date("2020-06-29")
  ) |>
  select(-c(agency_name, agency_num, short_name, shpfile_name) )

df_prep <- df_prep |> 
  group_by(pin) |>
  mutate(change_type = 
           case_when(
           sum(in_eff_sfha == "SFHA") == times_sold ~ "Always SFHA",
           sum(in_eff_sfha  == "SFHA") == 0 ~ "Never SFHA",
           T ~ "Changes SFHA"
    
  ),
  change_type = factor(change_type, levels = c("Never SFHA", "Always SFHA", "Changes SFHA"))
  ) |>
  ungroup()

```

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.

```{r}
df_prep |> filter(is.na(in_eff_sfha)) |> ## 22 missing indicators - Take care of 7/1/2023. Dropped in dropped_pins section.
  distinct(pin) |>
  arrange(pin)
# 21301140150000 is vacant lot right on the lake. Was coded as 241 in 2010 but is just a parking lot. will be filtered out. 
# 21301140160000 ditto. 



# muni_zip_lookup <- df_prep |> 
#   distinct(zip_code, clean_name, Triad, Township) |> 
#   filter(!is.na(clean_name) & !is.na(zip_code)& !is.na(Triad) & !is.na(Township))

missing_muniname <- df_prep |> 
  filter(is.na(clean_name)) |>
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 distinct(pin10, 
          nbhd_code, zip_code, 
         clean_name
          ) |>
  arrange(pin10)

muni_nbhd_lookup <- df_prep |> 
  distinct(nbhd_code, 
           zip_code,
           clean_name, Triad, Township) |> 
  filter(!is.na(clean_name) & !is.na(nbhd_code) & !is.na(zip_code) & !is.na(Triad) & !is.na(Township) ) 
  

df_prep <- df_prep |> 
  # WARNING: Uses first match. Some zipcodes and assessor neighborhoods 
  # are in multiple municipalities, triads, and townships which is IGNORED FOR NOW 
  left_join(muni_nbhd_lookup, by = c("zip_code", "nbhd_code"), multiple = "first") |>
    mutate(
      clean_name = ifelse(is.na(clean_name.x), clean_name.y, clean_name.x),
            Triad = ifelse(is.na(Triad.x), Triad.y, Triad.x),
            Township = ifelse(is.na(Township.x), Township.y, Township.x)


           ) |>
  select(-c(clean_name.x, clean_name.y, Triad.x, Triad.y, Township.x, Township.y))



missing_muniname2 <- df_prep |>   
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 filter(is.na(clean_name)) |> 
  distinct(pin10, zip_code, nbhd_code, clean_name)



missing_ff <- df_prep |> 
  filter(is.na(env_flood_fs_factor)) |>
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 distinct(pin10, 
         # pin, 
          nbhd_code, zip_code, clean_name
          ) |>
  arrange(pin10)

# missing_ff  # 4768 distinct pins, over 12K observations
# 2723 parcels missing flood factor scores

#write_csv(missing_ff, "data/processed/missing_floodfactor_scores.csv")
```


```{r}
manual_ff_scores <- readxl::read_xlsx("data/processed/pins_with_some_addresses_forgoogle.xlsx") |>
  mutate(pin = str_pad(pin, 14, "left", "0"), 
         pin10 = str_sub(pin,1,10)) |>
    select(pin10, flood_factor_score, clean_name)



df_prep <- df_prep  |>  
  mutate(pin10 = str_sub(pin, 1, 10)) |>
  left_join(manual_ff_scores, by= "pin10")

df_prep |> filter(is.na(env_flood_fs_factor)) |> count()
df_prep |> filter(is.na(clean_name.x)) |> count()

df_prep <- df_prep |> 
    mutate(flood_factor_score = ifelse(is.na(env_flood_fs_factor), flood_factor_score, env_flood_fs_factor),
           clean_name = ifelse(is.na(clean_name.x), clean_name.y, clean_name.x),
      high_ff_score = ifelse(env_flood_fs_factor > 4 | flood_factor_score > 4, TRUE, FALSE))

  
df_prep |> filter(is.na(flood_factor_score))
df_prep |> filter(is.na(clean_name)) |> count()


```

```{r make-df_pairs, message = FALSE}
# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),
  #  in_sfha_t1      = ifelse(is.na(in_sfha_t1), "Not SFHA", in_sfha_t1),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha,
  ) %>%

  ungroup() |> 
  mutate(new_info_released = as_date("2020-06-29")) |>
  # get rid of redundant variables that would be confusing
  select(-c(sale_price, sale_date, sale_year, in_eff_sfha)) 



df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)        
        # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")),  # between sales
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),    # between sales
        years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
        ann_d_log_price = d_log_price / years_btwn,

    
    # SFHA change as a factor variable
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
  ) |>
  
  # add additional location variables (Triad, township, municipality, etc)
  left_join(pin_muni_key)



df_pairs <- df_pairs |> 
  mutate(
    
    # relative time variables 
    t_months_eff = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
    
    t_years_eff = round(time_length(sale_date_t1 - eff_date, "years") ),    # first sale to FIRM upd ate, in years

    t_months_prelim = round(time_length(sale_date_t1 - pre_date, "months") ), # first sale to FIRM update, in months

    t_years_prelim = round(time_length(sale_date_t1 - pre_date, "years") ),    # first sale to FIRM update, in years

  )|>
  # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1))



df_pairs <- df_pairs |> 
  select(pin, 
         ann_d_log_price, d_log_price,
         sale_year_t1, sale_price_t1, in_sfha_t1, 
         sale_year_t2, sale_price_t2, in_sfha_t2, 
         years_btwn, change_type, everything()
  )

df_pairs <- df_pairs |> 
  mutate(change_type = factor(change_type, levels = c("Both Out of SFHA", "Both In SFHA", "Added", "Removed")))


df_pairs <- df_pairs |> 
  mutate(ff_factor = factor(env_flood_fs_factor))


```

There are `r n_distinct(df_pairs$pin)` pins remaining in `df_pairs`.

```{r}
## Create event indicators

## if the first sale was before the release and the next sale was after the release, then coded as TRUE, otherwise, FALSE
ff_pairs <- df_pairs |>  
  mutate(
    treated = ifelse(sale_date_t1 < as_date("2020-06-29") & sale_date_t2 >= as_date("2020-06-29"), TRUE, FALSE),
    high_ff_score = ifelse(env_flood_fs_factor > 4 | flood_factor_score > 4, TRUE, FALSE)
  )
```

```{r}
# saveRDS(df_pairs, file = "./data/processed/df_pairs.RDS")
# saveRDS(ff_pairs, file = "./data/processed/ff_pairs.RDS")
# saveRDS(df_prep, file = "./data/processed/df_prep.RDS")

saveRDS(ff_pairs, file = "./data/processed/ff_pairs_buildings.RDS")
saveRDS(df_prep, file = "./data/processed/df_prep_buildings.RDS")
saveRDS(df_pairs, file = "./data/processed/df_pairs_buildings.RDS")


```

> Note: ff_pairs is essentially the same as df_pairs but has the treated and high_ff_score variables added. 
