---
title: "Check Assumptions"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---


 


```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(cobalt)
library(did)

```


```{r}


pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

# df_pairs <- readRDS("./data/processed/df_pairs.RDS") |>
#   group_by(pin) |>
#   mutate(
#     years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
#      in_updated_firm = ifelse(pre_date > date("2008-01-01"), "Updated", "Not Updated"),
#     
#     treated_groups_eff = year(eff_date),
#     treated_groups_eff = ifelse(treated_groups_eff < 2010, NA, treated_groups_eff),
#     first_treat_year_prelim = year(pre_date),
#     first_treat_year_prelim = ifelse(first_treat_year_prelim < 2009, NA, first_treat_year_prelim),
#     
#     pin_num = as.numeric(pin),
#     treated = ifelse(sale_date_t1 < pre_date  & sale_date_t2 > pre_date & in_updated_firm == "Updated" & change_type %in% c("Added", "Removed"), "Treated", "Not Treated"),
#   ) 
# 


#parcels_w_buildings_sfha <- read_csv("./data/processed/sfha_indicator_buildings.csv")

df_prep <- read_rds("./data/processed/df_prep_buildings.RDS") # |>  # left_join(pin_muni_key) 


df_prep <- df_prep |>

  mutate(

    pin_num = as.numeric(pin),
    log_price = log(sale_price),
    placebo_event = ifelse(sale_year >2015, "2. Post", "1. Pre"),
    rel_year = sale_year - 2020) |>
  filter(!is.na(eff_date))

```

Condo rules: 

if the building touches the floodplain, the whole building has flood insurance

# Assumptions for Models

| Variable          | Description                                     |
| ----------------- | ----------------------------------------------- |
| `log_price`       |  log price  (your main DV)                      |
|`event` | Pre or Post data release | 
| `sale_year`       | Year of first sale                              |
| `change_type`     | SFHA transition category (e.g., Added, Removed) |
| `eff_date`        | Flood map effective date (treatment timing)     |
| `clean_name`      | Municipality                                    |
| `Triad`           | Subregional identifier (potential FE subgroup)  |



```{r}

table(df_prep$sale_year, df_prep$event, df_prep$in_eff_sfha)
```



```{r}
# summarize data
df_summary <- df_prep |> 
  group_by(sale_year, in_eff_sfha, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, event) |> 
  do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes")

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * event, data = df_summary)
summary(m)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:event2. Post = 0"))

```


```{r}
# summarize data
df_summary <- df_prep |> 
  filter(!is.na(high_ff_score)) |> 
  group_by(sale_year, in_eff_sfha, high_ff_score, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, event) |> 
  do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "high_ff_score", "event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~high_ff_score)

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = high_ff_score, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~in_eff_sfha)

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score* event, data = df_summary)
summary(m)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + high_ff_score + event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post=0",
                      "sale_year:high_ff_scoreTRUE:event2. Post = 0"

                      ))

```



## Placebo Test 1 


```{r}
library(dplyr)
library(ggplot2)
library(broom)

# summarize data
df_summary <- df_prep |> 
  group_by(sale_year, in_eff_sfha, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "placebo_event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2015) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("Placebo Test", subtitle = "By SFHA Status - Median Values with Slopes")

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)
summary(m)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0"))

```


```{r}
feols(log_price ~ in_eff_sfha*high_ff_score*placebo_event | pin + sale_year,
     # panel.id = "pin",
      vcov = "hetero", 
      data = df_prep) |> summary()
```



## Placebo Test 2 


```{r}
library(dplyr)
library(ggplot2)
library(broom)

# summarize data
df_summary <- df_prep |> 
  mutate(placebo_event = ifelse(sale_year > 2018, "2. Post", "1. Pre")) |>
  group_by(sale_year, in_eff_sfha, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "placebo_event"))

# plot
ggplot(df_summary |> filter(sale_year > 2012), 
       aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2018.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("Placebo Test", subtitle = "By SFHA Status - Median Values with Slopes")

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)
summary(m)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0"))

```

```{r}
# summarize data
df_summary <- df_prep |> 
    mutate(placebo_event = ifelse(sale_year > 2018, "2. Post", "1. Pre")) |>
  filter(!is.na(high_ff_score)) |> 
  group_by(sale_year, in_eff_sfha, high_ff_score, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, placebo_event) |> 
  do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "high_ff_score", "placebo_event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2018.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~high_ff_score)

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2018.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = high_ff_score, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~in_eff_sfha)

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score* placebo_event, data = df_summary)
summary(m)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + high_ff_score + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * placebo_event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:high_ff_scoreTRUE:placebo_event2. Post=0",
                      "sale_year:high_ff_scoreTRUE:placebo_event2. Post = 0"

                      ))

```



```{r}
feols(log_price ~ in_eff_sfha*high_ff_score*placebo_event | pin + sale_year,
     # panel.id = "pin",
      vcov = "hetero", 
      data = df_prep) |> summary()
```

## Regression based pre-trend test

```{r}

lm(log_price ~ in_eff_sfha, data = df_prep |> filter(sale_year < 2020)) |> summary()


lm(log_price ~ in_eff_sfha * factor(sale_year), data = df_prep |> filter(sale_year < 2020))

```

## Event Study style test

```{r}


df_prep <- df_prep |>
  mutate(rel_year = sale_year - 2020) 


df_prep <- df_prep |>
mutate(rel_year = factor(rel_year))

# summarize data
df_summary <- df_prep |> 
  group_by(rel_year, in_eff_sfha, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year * in_eff_sfha, data = df_summary)
summary(m)


est <- tidy(m, conf.int = TRUE)

# Keep only rel_year × in_eff_sfha terms
plot_data <- est |>
  filter(grepl("rel_year", term)) |>
  mutate(rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    sfha_group = case_when(
      grepl("in_eff_sfha", term) ~ "In SFHA",
      TRUE ~ "Not in SFHA"
    )
  )
ggplot(plot_data, aes(x = rel_num, y = estimate, color = sfha_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
  scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal()


```

```{r}
library(modelsummary)
m <- feols(log_price ~ i(rel_year, in_eff_sfha, ref = -1) | pin, data = df_prep)
summary(m)

```

```{r}
# summarize data
df_summary <- df_prep |> 
  group_by(rel_year, in_eff_sfha, high_ff_score, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year*in_eff_sfha*high_ff_score, data = df_summary)
summary(m)


est <- tidy(m, conf.int = TRUE)

plot_data <- est |>
    filter(grepl("rel_year", term) ) |>

  mutate(
    rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    treatment_group = case_when(
      grepl("high_ff_score", term) ~ "High FF Score",
      TRUE ~ "Low FF Score"
    ),
    sfha_group = case_when(
      grepl("in_eff_sfha", term) ~ "In SFHA",
      TRUE ~ "Not in SFHA"
    )
  )

ggplot(plot_data, aes(x = rel_num, y = estimate, color = treatment_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_vline(xintercept = 0) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~sfha_group)


ggplot(plot_data|> filter(rel_num > -6), aes(x = rel_num, y = estimate, color = sfha_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
    geom_vline(xintercept = 0) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~treatment_group)

```

