---
title: "Check Assumptions"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
---


 


```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(cobalt)
library(did)

```


```{r}

pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

df_prep <- read_rds("./data/processed/df_prep.RDS")  


df_prep <- df_prep |>
  filter(sale_year > 2011) |>

  mutate(
    pin_num = as.numeric(pin),
    log_price = log(sale_price),
    placebo_event = ifelse(sale_year >2015, "2. Post", "1. Pre"),
    # sale_year = ifelse(sale_date <= new_info_released & sale_year == 2020 & event == "1. Pre", 2019.5, 
    #                   ifelse(sale_date > new_info_released & sale_year == 2020 & event == "2. Post", 2020.5 , sale_year
    #                    )),
    sale_year_decimal = year(sale_date) + (quarter(sale_date) - 1) / 4,  # gives 2012.0, 2012.25, etc
    sale_label = paste0(year(sale_date), " Q", quarter(sale_date)),
    sale_quarter = quarter(sale_date),  # values 1–4

    rel_year = sale_year - 2020,
    rel_year_w_quarts = sale_year_decimal - 2020.5,
    rel_date = round(time_length(sale_date - new_info_released, unit = "year" ), digits = 1)
    )|>
  filter(!is.na(eff_date))

```

Condo rules: 

if the building touches the floodplain, the whole building has flood insurance

# Assumptions for Models

| Variable          | Description                                     |
| ----------------- | ----------------------------------------------- |
| `log_price`       |  log price  (your main DV)                      |
| `high_ff_score x event` |  Main treatment interaction     |
|`event` | Pre or Post data release. It is NOT the treatment. Just the additional extra value in homes after 2020 above and beyond the sale year fixed effects. | 
| `sale_year`       | Year of sale                    |
| `sale_quarter`       | Quarter of sale                       |
| `change_type`     | SFHA transition category (e.g., Added, Removed) |
| `eff_date`        | Flood map effective date (treatment timing)     |
| `clean_name`      | Municipality                                    |
| `Triad`           | Subregional identifier (potential FE subgroup)  |



```{r}
#| label: tbl-enteringsfha-peryear
#| tbl-cap: "Number of properties in an effective SFHA per year. Note that 2020 has sales considered Pre and Post Event due to the information becoming publicly available in June 2020."


table(df_prep$sale_year, df_prep$event, df_prep$in_eff_sfha)
```



```{r}
# summarize data
df_summary <- df_prep |>
  filter(!is.na(high_ff_score) & sale_year > 2012)  |>
  group_by(sale_year, high_ff_score, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# # fit slopes by group
# slopes <- df_summary |> 
#   group_by(high_ff_score, event) |> 
#   do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
#   filter(term == "sale_year") |> 
#   mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

slopes <- df_summary |>
  group_by(high_ff_score, event) |>
  group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>
  filter(term == "sale_year") |>
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))


# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(high_ff_score, event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("high_ff_score", "event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = high_ff_score, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By Flood Factor Risk - Median Values with Slopes")

```

The coefficient on sale_year is the baseline slope.

The sale_year:in_eff_sfha term tells you whether the slope differs between proprtis in an SFHA vs not within the SFHA (within the baseline event period).

The sale_year:event term tells you whether slopes differ pre vs post (within the baseline SFHA group).

The three-way sale_year:in_eff_sfha:event term tells you whether the slope difference across SFHA groups itself changes pre vs post.

```{r}
m <- lm(median_log_price ~ sale_year * high_ff_score * event, data = df_summary)
modelsummary::modelsummary(m, stars = TRUE)
```



If you only care about testing parallel slopes between groups, run an F-test with anova():

If p < 0.05, then at least one slope is statistically different.

If not significant, you can say slopes are statistically parallel.

Since sale_year is included in the anova() below, there will be slopes that are statistically significantly different.

```{r}
m1 <- lm(median_log_price ~ sale_year + high_ff_score + event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * high_ff_score * event, data = df_summary)

anova(m1, m2)
```

**Wald statistic with car::linearHypothesis() which gives you the Wald chi-square statistic, degrees of freedom, and p-value.**

This lets you calculate the linear model with interactions and then only pull and test specific slopes!

```{r preevent-tests, message = FALSE}
library(car)

# joint test of slope differences
car::linearHypothesis(m2, 
                      c(  
# pretrend for sale_year and high risk properties (even before they know their flood factor score):
                        "sale_year:high_ff_scoreTRUE = 0",
                        
                        "sale_year = 0"#,
                        #"sale_year:high_ff_scoreTRUE:event2. Post = 0"
                        ))
# 
# 
# # joint test of slope differences
# car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
#                       "sale_year:event2. Post = 0",
#                       "sale_year:in_eff_sfhaSFHA:event2. Post = 0"))

```




```{r}
#| label: fig-quarter3-only

# summarize data
df_summary <- df_prep |> 
  filter(!is.na(high_ff_score) & sale_quarter == 3& sale_year > 2012) |> 
  group_by(sale_year, in_eff_sfha, high_ff_score, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
# slopes <- df_summary |> 
#   group_by(in_eff_sfha, high_ff_score, event) |> 
#   do(tidy(lm(median_log_price ~ sale_year, data = .))) |> 
#   filter(term == "sale_year") |> 
#   mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

slopes <- df_summary |>
  group_by(high_ff_score, event, in_eff_sfha) |>
  group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>
  filter(term == "sale_year") |>
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "high_ff_score", "event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020,5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~high_ff_score)

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = event)) +
  geom_line() +
  geom_vline(xintercept=2020) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = high_ff_score, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By Flood Factor Risk & SFHA Status - Median Values with Slopes") +  facet_wrap(~in_eff_sfha)

```

```{r}

# 1. Summarize data by year, high_ff_score, event, and SFHA status
df_summary <- df_prep |>
    filter(!is.na(high_ff_score) #& sale_quarter == 3
           ) |> 

  filter(!is.na(high_ff_score) & sale_year > 2012) |>
  group_by(sale_year, high_ff_score, event, in_eff_sfha) |>
  summarize(
    median_log_price = median(log_price, na.rm = TRUE),
    .groups = "drop"
  )

# 2. Fit slopes by group and extract slope coefficients
slopes <- df_summary |>
  group_by(high_ff_score, event, in_eff_sfha) |>
  group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>
  filter(term == "sale_year") |>
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# 3. Determine label positions for each panel
label_positions <- df_summary |>
  group_by(high_ff_score, event, in_eff_sfha) |>
  summarize(
    x = max(sale_year),
    y = median(median_log_price),
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, 
                    by = c("high_ff_score", "event", "in_eff_sfha"))

# 4. Plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = event)) +
  geom_line() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 2020, linetype = "dashed") +
  geom_text(
    data = slopes,
    aes(x = x, y = y, label = slope_label, color = high_ff_score),
    hjust = 1,
    vjust = 2,
    show.legend = FALSE
  ) +
  facet_wrap(~in_eff_sfha) +
  ggtitle(#"Q3 Only!! 
          "By Flood Factor Risk & SFHA Status - Median Values with Slopes") +
  theme_minimal()

```

```{r preevent-test-withsfha, message = FALSE}

m <- lm(median_log_price ~ sale_year * high_ff_score *in_eff_sfha* event, data = df_summary)


# joint test of slope differences
car::linearHypothesis(m, 
                      c(  
# pretrend for sale_year and high risk properties (even before they know their flood factor score):
                        "sale_year:high_ff_scoreTRUE = 0",
                                    "sale_year:high_ff_scoreTRUE:in_eff_sfhaSFHA = 0",
            
                        "sale_year:in_eff_sfhaSFHA = 0"
                        ))

```

```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score* event, data = df_summary)
modelsummary::modelsummary(m, stars = TRUE)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + high_ff_score + event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * event, data = df_summary)

anova(m1, m2)
```



::: panel-tabset

## Placebo Test 1: 2017 Fake Event

Shifts the definition of the event year by -1 or -2.

If your slope test results completely change depending on the cutoff, that’s a red flag.

```{r}
# summarize data
df_summary <- df_prep |> 
  
  filter(sale_quarter == 3) |> 
  # for fake event in 2017 
  mutate(placebo_event = ifelse(sale_year > 2017, "2. Post", "1. Pre")) |>
  
  group_by(sale_year, in_eff_sfha, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>
  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "placebo_event"))

# plot
ggplot(df_summary |> filter(sale_year > 2012), 
       aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2017.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("Placebo Test: Q3 sales only", subtitle = "By SFHA Status - Median Values with Slopes")

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)
modelsummary::modelsummary(m, stars = TRUE)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

# joint test of slope differences
car::linearHypothesis(m2, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0"))

```

```{r}
# summarize data
df_summary <- df_prep |> 
  filter(sale_quarter == 3) |>
    mutate(placebo_event = ifelse(sale_year > 2017, "2. Post", "1. Pre")) |>
  filter(!is.na(high_ff_score)) |> 
  group_by(sale_year, in_eff_sfha, high_ff_score, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, placebo_event) |> 
group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, high_ff_score, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "high_ff_score", "placebo_event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2017.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("By SFHA Status - Median Values with Slopes") +
  facet_wrap(~high_ff_score)

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = high_ff_score, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2017.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = high_ff_score, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("!3 sales only by SFHA Status - Median Values with Slopes") +
  facet_wrap(~in_eff_sfha)

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score* placebo_event, data = df_summary)
modelsummary::modelsummary(m, stars = TRUE)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + high_ff_score + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * high_ff_score * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}

# joint test of slope differences
car::linearHypothesis(m2, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:high_ff_scoreTRUE:placebo_event2. Post=0",
                      "sale_year:high_ff_scoreTRUE:placebo_event2. Post = 0"

                      ))

```



```{r}
feols(log_price ~ in_eff_sfha*high_ff_score*placebo_event | pin + sale_year,
     # panel.id = "pin",
      vcov = "hetero", 
      data = df_prep) |> modelsummary::modelsummary()
```


## Placebo Test 2:2015

Pretend the event happened in an earlier year where nothing actually changed.

Re-run the regression with that placebo cutoff.

If you keep “finding” slope breaks at arbitrary years, your pre-trends aren’t actually parallel.

```{r}
# summarize data
df_summary <- df_prep |> 
  group_by(sale_year, in_eff_sfha, placebo_event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")

# fit slopes by group
slopes <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
group_modify(~ {
    model <- lm(median_log_price ~ sale_year, data = .x)
    broom::tidy(model)
  }) |>  filter(term == "sale_year") |> 
  mutate(slope_label = paste0("Slope = ", round(estimate, 3)))

# pick label positions (e.g., at the max year of each line)
label_positions <- df_summary |> 
  group_by(in_eff_sfha, placebo_event) |> 
  summarize(
    x = max(sale_year), 
    y = median(median_log_price), 
    .groups = "drop"
  )

slopes <- left_join(slopes, label_positions, by = c("in_eff_sfha", "placebo_event"))

# plot
ggplot(df_summary, aes(x = sale_year, y = median_log_price, 
                       color = in_eff_sfha, linetype = placebo_event)) +
  geom_line() +
  geom_vline(xintercept=2015.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(data = slopes, aes(x = x, y = y, label = slope_label, 
                               color = in_eff_sfha, linetype = NULL), 
           hjust = 1, vjust = 2, 
            show.legend = FALSE) +
  ggtitle("Placebo Test", subtitle = "By SFHA Status - Median Values with Slopes")

```
```{r}
m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)
modelsummary::modelsummary(m, stars = TRUE)
```

```{r}
m1 <- lm(median_log_price ~ sale_year + in_eff_sfha + placebo_event, data = df_summary)
m2 <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

anova(m1, m2)
```

```{r}
library(car)

m <- lm(median_log_price ~ sale_year * in_eff_sfha * placebo_event, data = df_summary)

# joint test of slope differences
car::linearHypothesis(m, c("sale_year:in_eff_sfhaSFHA = 0",
                      "sale_year:placebo_event2. Post = 0",
                      "sale_year:in_eff_sfhaSFHA:placebo_event2. Post = 0"))

```


```{r}
feols(log_price ~ in_eff_sfha*high_ff_score*placebo_event | pin + sale_year,
     # panel.id = "pin",
      vcov = "hetero", 
      data = df_prep) |> summary()
```

:::

## Event Study style test


If they bounce around zero without a clear trend, you’ve got support for parallel trends.

If they slope up/down before the event, that’s evidence of violation

::: panel-tabset

### Model results

```{r}
#| label: fig-riskgrouptrends
#| fig-cap: "There are obviously differing pre-event trends between properties that have low and high FF scores. Part of this MAY be because some properties are in high risk areas in designated FEMA flood zones."


df_prep <- df_prep |> 
  mutate(rel_year = sale_year_decimal - 2020.5)


df_prep <- df_prep |>
mutate(
  rel_year = factor(rel_year),
    rel_year = relevel(rel_year, ref = "-1")
       )

# summarize d ata
df_summary <- df_prep |> 
  group_by(rel_year, high_ff_score, event) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year * high_ff_score, data = df_summary)
summary(m)


est <- tidy(m, conf.int = TRUE)

# Keep only rel_year × in_eff_sfha terms
plot_data <- est |>
  filter(grepl("rel_year", term)) |>
  mutate(rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    risk_group = case_when(
      grepl("high_ff_score", term) ~ "High FF Score",
      TRUE ~ "Low FF Score"
    )
  )
ggplot(plot_data, aes(x = rel_num, y = estimate, color = risk_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = -.5) + 
  labs(x = "Years relative to event", y = "Effect on median log price") +
  scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal()


```



### Figures

```{r}
#| label: fig-sfhaandriskgrouptrends
#| fig-cap: "Trends for properties that had high flood factor score information in 2020 for properties in and outside of FEMA floodplaines."
#| 
# summarize data
df_summary <- df_prep |> 
  group_by(rel_year, in_eff_sfha, high_ff_score, Triad) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year*in_eff_sfha*high_ff_score + Triad, data = df_summary)

summary(m)


est <- tidy(m, conf.int = TRUE)

plot_data <- est |>
    filter(grepl("rel_year", term) ) |>

  mutate(
    rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    treatment_group = case_when(
      grepl("high_ff_score", term) ~ "High FF Score",
      TRUE ~ "Low FF Score"
    ),
    sfha_group = case_when(
      grepl("in_eff_sfha", term) ~ "In SFHA",
      TRUE ~ "Not in SFHA"
    )
  )

ggplot(plot_data, aes(x = rel_num, y = estimate, color = treatment_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
    geom_vline(xintercept = -.5) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~sfha_group)
```


```{r}
#| label: fig-relativeyeartrends-flipped
#| fig-cap: "Trends for properties that had high flood factor score information in 2020 for properties in and outside of FEMA floodplaines."
#| 
ggplot(plot_data|> filter(rel_num > -6), aes(x = rel_num, y = estimate, color = sfha_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
    geom_vline(xintercept = -.5) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~treatment_group)

```

## Pre-Event trends

In relative years

```{r}
feols(log_price ~ i(rel_year, ref = -1) * high_ff_score * in_eff_sfha | pin, df_prep) |> modelsummary::modelsummary()

```

# Change in Flood Factor Coding

```{r}
df_prep <- df_prep |>
  mutate(
high_ff_score = ifelse(high_ff_score == TRUE & event == "2. Post", "1", "0")
        )
```



Grouped by relative year and if they had a high flood factor score:

### Models 

```{r}
df_prep <- df_prep |>
  mutate(rel_year = sale_year_decimal - 2020.5)


df_prep <- df_prep |>
mutate(
  rel_year = factor(rel_year),
    rel_year = relevel(rel_year, ref = "-1")
       )

# summarize d ata
df_summary <- df_prep |> 
  group_by(rel_year, high_ff_score) |> 
  summarize(median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year * high_ff_score, data = df_summary)
modelsummary::modelsummary(m)
```

### Figures

```{r}
est <- tidy(m, conf.int = TRUE)

# Keep only rel_year × in_eff_sfha terms
plot_data <- est |>
  filter(grepl("rel_year", term)) |>
  mutate(rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    risk_group = case_when(
      grepl("high_ff_score", term) ~ "High FF Score",
      TRUE ~ "Low FF Score"
    )
  )
ggplot(plot_data, aes(x = rel_num, y = estimate, color = risk_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = -.5) + 
  labs(x = "Years relative to event", y = "Effect on median log price") +
  scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal()


```



### Both Variables


```{r}
#| label: fig-bothvariables
#| fig-cap: "If high_ff_score == 1 only after the information release, then coefficients look like this."
#| 
# summarize data
df_summary <- df_prep |> 
  mutate(rel_year = sale_year - 2020,
         rel_year  = factor(rel_year),
         rel_year = relevel(rel_year, ref = "-1")) |>
  
  group_by(rel_year, in_eff_sfha, high_ff_score) |> 
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
    median_log_price = median(log_price, na.rm = TRUE), .groups = "drop")


m <- lm(median_log_price ~ rel_year*in_eff_sfha*high_ff_score, data = df_summary)

summary(m)


est <- tidy(m, conf.int = TRUE)

plot_data <- est |>
    filter(grepl("rel_year", term) ) |>

  mutate(
    rel_num = as.integer(sub(".*rel_year(-?\\d+).*", "\\1", term)),
    treatment_group = case_when(
      grepl("high_ff_score", term) ~ "High FF Score",
      TRUE ~ "Low FF Score"
    ),
    sfha_group = case_when(
      grepl("in_eff_sfha", term) ~ "In SFHA",
      TRUE ~ "Not in SFHA"
    )
  )

ggplot(plot_data, aes(x = rel_num, y = estimate, color = treatment_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
    geom_vline(xintercept = -.5) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~sfha_group)



ggplot(plot_data |> filter(rel_num > -6), aes(x = rel_num, y = estimate, color = sfha_group)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
    geom_vline(xintercept = -.5) +

  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Years relative to event", 
       y = "Effect on median log price") +
 # scale_x_continuous(limits = c(-10, 5), breaks = c(-9, -5, 0, 4)) + 
  theme_minimal() + facet_wrap(~treatment_group)

```

# Recommended Specification

## Fixed Effects model

If high ff_score only exists after 2020. 

```{r}
feols(log_price ~ high_ff_score  * in_eff_sfha | pin + sale_year + sale_quarter, df_prep) |> 
  modelsummary::modelsummary(stars = TRUE)

```

## DiD estimates

```{r}
feols(log_price ~ i(rel_year, ref = -1) * high_ff_score * in_eff_sfha | pin + sale_quarter, df_prep) |> 
  modelsummary::modelsummary(stars = TRUE)


```

