---
title: "Check Assumptions"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---


 


```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(cobalt)
library(did)

```


```{r}


pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

df_pairs <- readRDS("./data/processed/df_pairs.RDS") |>
  group_by(pin) |>
  mutate(
    years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
     in_updated_firm = ifelse(pre_date > date("2008-01-01"), "Updated", "Not Updated"),
    
    treated_groups_eff = year(eff_date),
    treated_groups_eff = ifelse(treated_groups_eff < 2010, NA, treated_groups_eff),
    first_treat_year_prelim = year(pre_date),
    first_treat_year_prelim = ifelse(first_treat_year_prelim < 2009, NA, first_treat_year_prelim),
    
    pin_num = as.numeric(pin),
    treated = ifelse(sale_date_t1 < pre_date  & sale_date_t2 > pre_date & in_updated_firm == "Updated" & change_type %in% c("Added", "Removed"), "Treated", "Not Treated"),
  ) 



# df_pairs |>
#   select(-c(short_name, agency_number, agency_name, stayed_sfha, neither_sfha, shpfile_name, added_between, removed_between)) |>
#   write_csv("./data/processed/df_pairs.csv")



parcels_w_buildings_sfha <- read_csv("./data/processed/buildings_distinct_in_sfha.csv")

df_prep <- read_csv("./data/processed/df_prep.csv") |>  
    left_join(pin_muni_key) 


df_prep <- df_prep |>

  mutate(
       years_btwn = round(time_length(sale_date - pre_date, "years")),
    years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
    
    # if sale is in a FIRM that had a preliminary FIRM released after 2008
    in_updated_firm = ifelse(pre_date > date("2008-01-01"), "Updated", "Not Updated"),
    
    # using preliminary date for anticipation
    treated_groups_eff = year(eff_date),
    treated_groups_eff = ifelse(treated_groups_eff < 2010, 0, treated_groups_eff),
    first_treat_year_prelim = year(pre_date),
    first_treat_year_prelim = ifelse(first_treat_year_prelim < 2009, NA, first_treat_year_prelim),
    pin_num = as.numeric(pin),
    log_price = log(sale_price),
    treated = ifelse(sale_date > pre_date & in_updated_firm == "Updated" & in_prelim_sfha == "SFHA", "Treated", "Not Treated"),
    ) |>
  filter(!is.na(eff_date))

```

Condo rules: 

if the building touches the floodplain, the whole building has flood insurance

# Assumptions for Models

| Variable          | Description                                     |
| ----------------- | ----------------------------------------------- |
| `ann_d_log_price` | Annualized log price change (your main DV)      |
| `d_log_price`     | Raw log price change                            |
| `sale_year_t1`    | Year of first sale                              |
| `sale_year_t2`    | Year of second sale                             |
| `years_btwn`      | Years between sales                             |
| `change_type`     | SFHA transition category (e.g., Added, Removed) |
| `eff_date`        | Flood map effective date (treatment timing)     |
| `clean_name`      | Municipality                                    |
| `Triad`           | Subregional identifier (potential FE subgroup)  |

Step 1. Treatment Cohorts

- Based on when FIRMs were updated (eff_date or pre_date)  
- use earlier format of data before it is in repeat sales format. 

```{r}

table(df_prep$sale_year, df_prep$in_updated_firm)
table(df_prep$sale_year, df_prep$in_updated_firm, df_prep$in_eff_sfha)
table(df_prep$sale_year, df_prep$in_updated_firm, df_prep$treated)
```

Step 2. Create Relative Time and Filter Control Units

- Time relative to the treatment: sale_date_tX and sale_year_tX

```{r}
control_pool <- df_prep |> 
  mutate(relative_time_pre = difftime(sale_date, pre_date, "months"),
        relative_time_eff = difftime(sale_date, eff_date, "months"),

  ) |>
  filter(sale_date < pre_date | is.na(first_treat_year_prelim))



sfha_sales <- df_prep |> 
  mutate(pin10 = str_sub(pin, 1, 10)) |> 
  filter(pin10 %in% parcels_w_buildings_sfha$pin10)


```


```{r}
df_prep |> 
  group_by(sale_year, first_treat_year_prelim, in_updated_firm, in_prelim_sfha,) |> 
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = in_updated_firm, lty = in_prelim_sfha)) + 
  facet_wrap(~first_treat_year_prelim) +
  ggtitle(label = "Preliminary FIRM Releases - Median Values")

df_prep |> 
  group_by(sale_year, treated_groups_eff, in_updated_firm, in_eff_sfha,) |> 
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = in_updated_firm, lty = in_eff_sfha)) + 
  facet_wrap(~treated_groups_eff) +
    ggtitle(label = "Effective FIRM Dates - Median Values")


df_prep |> 
  group_by(sale_year, first_treat_year_prelim, in_updated_firm, in_prelim_sfha,) |> 
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = avg_log_price, 
                color = in_updated_firm, lty = in_prelim_sfha)) + 
  facet_wrap(~first_treat_year_prelim) +
  ggtitle(label = "Preliminary FIRM Releases - Average Values")

df_prep |> 
  group_by(sale_year, treated_groups_eff, in_updated_firm, in_eff_sfha,) |> 
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = avg_log_price, 
                color = in_updated_firm, lty = in_eff_sfha)) + 
  facet_wrap(~treated_groups_eff) +
    ggtitle(label = "Effective FIRM Dates - Average Values")

```

```{r}

df_prep |> 
  group_by(sale_year, treated, agency_name)  |>
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = agency_name)) + 
  facet_wrap(~treated) +
  theme(legend.position = "none") +
    ggtitle(label = "Treatment based on preliminary FIRMs - Median Values")


```



```{r}
df_prep |> 
  group_by(sale_year, treated_groups_eff, agency_name)  |>
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = agency_name)) + 
  facet_wrap(~treated_groups_eff) +
  theme(legend.position = "none") +
    ggtitle(label = "Effective FIRM Dates - Median Values")

df_prep |> group_by(sale_year, first_treat_year_prelim, agency_name)  |>
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = agency_name)) + 
  facet_wrap(~first_treat_year_prelim) +
  theme(legend.position = "none") +
    ggtitle(label = "Preliminary FIRM Released - Median Values")

```



```{r}
df_prep |> group_by(sale_year, treated_groups_eff, agency_name, eff_date)  |>
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = agency_name)) + 
  facet_wrap(~eff_date) +
  theme(legend.position = "none") +
    ggtitle(label = "Effective FIRM Dates - Median Values")

df_prep |> group_by(sale_year, first_treat_year_prelim, agency_name, eff_date)  |>
  summarize(avg_log_price = mean(log_price, na.rm=TRUE),
            median_log_price = median(log_price, na.rm=TRUE)) |>
  ggplot() +
  geom_line(aes(x=sale_year, y = median_log_price, 
                color = agency_name)) + 
  facet_wrap(~eff_date) +
  theme(legend.position = "none") +
    ggtitle(label = "Preliminary FIRM Released - Median Values")

```

### Using df_pairs and repeat sales data structure

```{r}
# Means by treatment group
df_pairs |>
  group_by(treated, change_type) |> 
  summarise(mean_log_price_t1 = mean(log(sale_price_t1), na.rm=TRUE),
            median_log_price_t2 = median(log(sale_price_t1), na.rm=TRUE),
            count = n())

# Density plot
ggplot(df_pairs, aes(x = log(sale_price_t1), fill = change_type)) +
  geom_density(alpha = 0.4)
```

```{r}
# propensity scores
df_pairs$treated01 = ifelse(df_pairs$treated == "Treated", 1, 0)
glm(treated01 ~ log(sale_price_t1) + in_lomr, family = binomial(), data = df_pairs) |> summary()

```

Step 2.5

- Account for holding period and market-wide trends in price changes  
 
- 

```{r}
# Account for holding period and market-wide trends in price changes


# Add fixed effects or interactions to control for these influences
model_adjusted <- feols(d_log_price ~ months_btwn*factor(sale_year_t2) +
                          change_type | pin, 
                        data  = df_pairs)

summary(model_adjusted)
```


```{r}
## temporarily keeping ONLY observations that sell before and after treatment

updated_pool <- df_pairs |>
  filter(in_updated_firm == "Updated")



```

## Group-Time ATT with Staggered Design

**These take around an hour each to run so they are set to eval=FALSE**

```{r}
#| eval: false

table(df_pairs$first_treat_year)

att_gt_out <- att_gt(yname = "sale_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     panel = FALSE,
                     gname = "first_treat_year_prelim",
                     xformla = ~ in_eff_sfha*updated_firm,
                     data = df_prep)

att_gt_out
summary(att_gt_out)
```


```{r}
#| eval: false


df_pairs <- df_pairs |> 
  mutate(first_treat_year = ifelse(treated == "Treated", year(pre_date), 0))

table(df_pairs$first_treat_year)
  
  
att_gt_2 <- att_gt(yname = "d_log_price",
                     tname = "sale_year_t2",
                     idname = "pin_num",
                     panel = FALSE,
                     gname = "first_treat_year",  
                     data = df_pairs)

summary(att_gt_2)
```

Step 4. Visualize Event Study

```{r}
#| eval: false

library(ggdid)
ggdid(att_gt_out)
ggdid(att_gt_2)

```

Step 5. Interpret Pre-Treatment Periods

Review the event study plot:
- Are the estimates for periods prior to treatment flat and centered around zero?
- Are the confidence intervals wide or tight?
- Do any of the pre-treatment estimates appear significantly different from zero?
Why: Significant pre-trends violate the key identifying assumption of DiD  

# Centered around FIRM update

## Effective Dates

```{r}
# Assume your data is named df_pairs
df_pairs <- df_pairs |>
  mutate(
    eff_year = year(eff_date),
    rel_year = sale_year_t2 - as.numeric(eff_year),
   # change_group = if_else(is.na(change_type), "Unknown", change_type)
  )

# Filter to pre-treatment observations only
df_pre <- df_pairs |> filter(rel_year < 0)

# Aggregate to calculate mean annualized log price change
plot_data <- df_pre |>
  group_by(rel_year, change_type) |>
  summarise(mean_ann_dlogprice = mean(ann_d_log_price, na.rm = TRUE), .groups = "drop")

# Plot
ggplot(plot_data, aes(x = rel_year, y = mean_ann_dlogprice, color = change_type)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray") +
  labs(
    title = "Pre-Treatment Trends by SFHA Change Type",
    x = "Years Before FIRM Update",
    y = "Mean Annualized Log Price Change",
    color = "SFHA Change Type"
  ) +
  theme_minimal()

```



```{r}

# Filter to pre-treatment observations only
df_post <- df_pairs |> filter(rel_year >= 0)

# Aggregate to calculate mean annualized log price change
plot_data <- df_post |>
  group_by(rel_year, change_type) |>
  summarise(mean_ann_dlogprice = mean(ann_d_log_price, na.rm = TRUE), .groups = "drop")

# Plot
ggplot(plot_data, aes(x = rel_year, y = mean_ann_dlogprice, color = change_type)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray") +
  labs(
    title = "Post-Treatment Trends by SFHA Change Type",
    x = "Years After FIRM Update",
    y = "Mean Log Price of 2nd Sale",
    color = "SFHA Change Type"
  ) +
  theme_minimal()

```



# Using actual years on x axis


```{r}
df_pairs |> 
 # filter(sale_date_t1 < eff_date) |>
    filter(sale_date_t1 < eff_date & sale_year_t2 > 2010 & sale_year_t1 > 2010) |>

  group_by(change_type, sale_year_t1) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type")


df_pairs |> 
  filter(sale_date_t1 < eff_date & sale_year_t2 > 2010 & sale_year_t1 > 2010) |>
  group_by(change_type, sale_year_t2) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type")
```


```{r}
df_pre <- df_pairs |> filter(sale_date_t2 < eff_date)

df_pairs |> filter(sale_date_t2 > eff_date) |>
  group_by(change_type, sale_year_t2) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type")

df_pairs |> filter(sale_date_t2 > eff_date & sale_date_t1 < eff_date) |>
  group_by(change_type, sale_year_t2) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type")

eff_dates <- df_pairs |> distinct(eff_date)
prelim_dates <- df_pairs |> distinct(pre_date)

df_pairs |> filter(sale_date_t2 > eff_date & sale_date_t1 < eff_date) |>
  group_by(change_type, sale_year_t1) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = sale_year_t1, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type") +
  geom_vline(data = eff_dates, aes(xintercept = year(eff_date) ) )
```


```{r}
df_pairs |> filter(sale_date_t2 > pre_date & sale_date_t1 < pre_date) |>
  group_by(change_type, sale_year_t1) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
    ggplot(aes(x = sale_year_t1, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type, grouped by Sale1") +
  geom_vline(data = prelim_dates, aes(xintercept = year(pre_date) ) ) 

df_pairs |> filter(sale_date_t2 > pre_date & sale_date_t1 < pre_date) |>
  group_by(change_type, sale_year_t2) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = sale_year_t2, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type, grouped by Sale2") +
  geom_vline(data = prelim_dates, aes(xintercept = year(pre_date) ) ) 

```


## Effective Dates!

```{r}
df_pairs |>   
  filter(sale_year_t2 > 2010 & sale_year_t1 > 2010) |>

  filter(t1_years < 0 ) |>
  group_by(change_type, t1_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
    filter(sale_year_t2 > 2010 & sale_year_t1 > 2010) |>

#  filter(t1_years > 0 ) |>
  group_by(change_type, t1_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
      filter(sale_year_t2 > 2010 & sale_year_t1 > 2010) |>

  filter(t2_years > 0 ) |>
  group_by(change_type, t2_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t2_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Post-Treatment Trends by SFHA Change Type, grouped by Years after treatment sale") 
```

### Preliminary Dates!

```{r}
df_pairs |> 
  filter(t1_years_prelim < 0 ) |>
  group_by(change_type, t1_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
  group_by(change_type, t1_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
  filter(t2_years_prelim > 0 ) |>
  group_by(change_type, t2_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t2_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Post-Treatment Trends by SFHA Change Type, grouped by Years after treatment sale") 
```

```{r}

bal.tab(change_type ~ sale_price_t1 + years_btwn + Triad,
        data = df_pairs,
        estimand = "ATT")
```



## Regression based pre-trend test

```{r}

lm(ann_d_log_price ~ change_type, data = df_pairs |> filter(t1_years_prelim < 0)) |> summary()


lm(ann_d_log_price ~ change_type * factor(sale_year_t2), data = df_pairs |> filter(sale_date_t1 < eff_date))


lm(ann_d_log_price ~ change_type * factor(t1_years_prelim), data = df_pairs |> filter(t1_years_prelim < 0)) |> summary()
```

