---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---


```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(cobalt)

```


```{r}

df_pairs <- readRDS("./data/processed/df_pairs.RDS")

# df_pairs |>
#   select(-c(short_name, agency_number, agency_name, stayed_sfha, neither_sfha, shpfile_name, added_between, removed_between)) |>
#   write_csv("./data/processed/df_pairs.csv")

```

## Assumptions for Models

| Variable          | Description                                     |
| ----------------- | ----------------------------------------------- |
| `ann_d_log_price` | Annualized log price change (your main DV)      |
| `d_log_price`     | Raw log price change                            |
| `sale_year_t1`    | Year of first sale                              |
| `sale_year_t2`    | Year of second sale                             |
| `years_btwn`      | Years between sales                             |
| `change_type`     | SFHA transition category (e.g., Added, Removed) |
| `eff_date`        | Flood map effective date (treatment timing)     |
| `clean_name`      | Municipality                                    |
| `Triad`           | Subregional identifier (potential FE subgroup)  |


```{r}
#| eval: false
## temporarily keeping ONLY observations that sell before and after treatment

df_pairs_treated <- df_pairs |> filter(sale_date_t1 <= eff_date & sale_date_t2 > eff_date)

df_pairs <- df_pairs_treated
```


```{r}

df_pairs |> filter(sale_date_t1 < eff_date) |>
  group_by(change_type, sale_year_t1) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type")

df_pre <- df_pairs |> filter(sale_date_t2 < eff_date)

df_pairs |> filter(sale_date_t2 > eff_date) |>
  group_by(change_type, sale_year_t2) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type")

df_pairs |> filter(sale_date_t2 > eff_date & sale_date_t1 < eff_date) |>
  group_by(change_type, sale_year_t2) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type")

eff_dates <- df_pairs |> distinct(eff_date)
prelim_dates <- df_pairs |> distinct(pre_date)

df_pairs |> filter(sale_date_t2 > eff_date & sale_date_t1 < eff_date) |>
  group_by(change_type, sale_year_t1) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = sale_year_t1, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type") +
  geom_vline(data = eff_dates, aes(xintercept = year(eff_date) ) ) 

df_pairs |> filter(sale_date_t2 > pre_date & sale_date_t1 < pre_date) |>
  group_by(change_type, sale_year_t1) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
    ggplot(aes(x = sale_year_t1, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type, grouped by Sale1") +
  geom_vline(data = prelim_dates, aes(xintercept = year(pre_date) ) ) 

df_pairs |> filter(sale_date_t2 > pre_date & sale_date_t1 < pre_date) |>
  group_by(change_type, sale_year_t2) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = sale_year_t2, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre and Post-Treatment Trends by SFHA Change Type, grouped by Sale2") +
  geom_vline(data = prelim_dates, aes(xintercept = year(pre_date) ) ) 

```


### Effective Dates!

```{r}
df_pairs |> 
  filter(t1_years < 0 ) |>
  group_by(change_type, t1_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
#  filter(t1_years > 0 ) |>
  group_by(change_type, t1_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
  filter(t2_years > 0 ) |>
  group_by(change_type, t2_years) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t2_years, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Post-Treatment Trends by SFHA Change Type, grouped by Years after treatment sale") 
```

### Preliminary Dates!

```{r}
df_pairs |> 
  filter(t1_years_prelim < 0 ) |>
  group_by(change_type, t1_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
  group_by(change_type, t1_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t1_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Pre-Treatment Trends by SFHA Change Type, grouped by Years before treatment") 

df_pairs |> 
  filter(t2_years_prelim > 0 ) |>
  group_by(change_type, t2_years_prelim) |>
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |>
  ggplot(aes(x = t2_years_prelim, y = mean_growth, color = change_type)) +
  geom_line() +
  geom_point() +
  labs(title = "Post-Treatment Trends by SFHA Change Type, grouped by Years after treatment sale") 
```

```{r}

bal.tab(change_type ~ sale_price_t1 + years_btwn + Triad,
        data = df_pairs,
        estimand = "ATT")
```

## Centered around FIRM update

```{r}
# Assume your data is named df_pairs
df_pairs <- df_pairs |>
  mutate(
    sale_year_t2 = year(ymd(sale_date_t2)),
    eff_year = year(ymd(eff_date)),
    rel_year = sale_year_t2 - eff_year,
    change_group = if_else(is.na(change_type), "Unknown", change_type)
  )

# Filter to pre-treatment observations only
df_pre <- df_pairs |> filter(rel_year < 0)

# Aggregate to calculate mean annualized log price change
plot_data <- df_pre |>
  group_by(rel_year, change_group) |>
  summarise(mean_ann_dlogprice = mean(ann_d_log_price, na.rm = TRUE), .groups = "drop")

# Plot
ggplot(plot_data, aes(x = rel_year, y = mean_ann_dlogprice, color = change_group)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray") +
  labs(
    title = "Pre-Treatment Trends by SFHA Change Type",
    x = "Years Before FIRM Update",
    y = "Mean Annualized Log Price Change",
    color = "SFHA Change Type"
  ) +
  theme_minimal()

```

```{r}
# Assume your data is named df_pairs
df_pairs2 <- df_pairs |>
  mutate(
    #sale_year_t2 = year(ymd(sale_date_t2)),
   # eff_year = year(ymd(eff_date)),
    rel_date = sale_date_t1 - eff_date,
    rel_year = sale_year_t1 - year(eff_date),
    change_group = if_else(is.na(change_type), "Unknown", change_type)
  )

# Filter to pre-treatment observations only
df_pre <- df_pairs2 |> filter(rel_year <=  0)

# Aggregate to calculate mean annualized log price change
plot_data <- df_pre |>
  group_by(rel_year, change_group) |>
  summarise(mean_ann_dlogprice = mean(ann_d_log_price, na.rm = TRUE), .groups = "drop")

# Plot
ggplot(plot_data, aes(x = rel_year, y = mean_ann_dlogprice, color = change_group)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray") +
  labs(
    title = "Pre-Treatment Trends by SFHA Change Type",
    x = "Years Before FIRM Update",
    y = "Mean Log Price of First Sale",
    color = "SFHA Change Type"
  ) +
  theme_minimal()

```


```{r}
# Assume your data is named df_pairs
df_pairs2 <- df_pairs |>
  mutate(
    #sale_year_t2 = year(ymd(sale_date_t2)),
   # eff_year = year(ymd(eff_date)),
    rel_date = sale_date_t2 - eff_date,
    rel_year = sale_year_t2 - year(eff_date),
    change_group = if_else(is.na(change_type), "Unknown", change_type)
  )

# Filter to pre-treatment observations only
df_post <- df_pairs2 |> filter(rel_year >= 0)

# Aggregate to calculate mean annualized log price change
plot_data <- df_post |>
  group_by(rel_year, change_group) |>
  summarise(mean_ann_dlogprice = mean(ann_d_log_price, na.rm = TRUE), .groups = "drop")

# Plot
ggplot(plot_data, aes(x = rel_year, y = mean_ann_dlogprice, color = change_group)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray") +
  labs(
    title = "Post-Treatment Trends by SFHA Change Type",
    x = "Years After FIRM Update",
    y = "Mean Log Price of 2nd Sale",
    color = "SFHA Change Type"
  ) +
  theme_minimal()

```

## Geography Trends

```{r}
lm(log(sale_price_t1) ~ change_type * factor(sale_year_t2), data = df_pairs |> filter(sale_date_t1 < eff_date))

```


## Regression based pre-trend test

```{r}
lm(log(sale_price_t1) ~ change_type * factor(sale_year_t2), data = df_pairs |> filter(sale_date_t1 < eff_date))

```

