---
title: "Appendix - Nearby Property Controls"
format: 
  html:
    df-print: kable
    code-fold: true
    tbl-cap-location: margin
   # error: true
    toc: true
    warning: false
    message: false
---

```{r setup}
library(tidyverse)
library(fixest)
library(did)  
library(etwfe)
library(tidyverse)

library(modelsummary)
library(gt)

options(scipen = 999)
```


# Nearby control properties only

```{r}
# way too big of buffer zone
#close_comps <- readxl::read_xlsx("data/processed/parcelswithin600mof2026SFHA_ExportTable_TableToExcel.xlsx")

#300 meter buffer
close_comps <- readxl::read_xlsx("data/processed/bldgswithin300mof_SFHA_arcgis.xlsx")
lake100ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within100ft_ExportTable_TableToExcel.xlsx")
lake500ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within500ft_ExportTable_TableToExcel.xlsx")


# already has eff_sfha_category in it
data_path <- "outputs/q2_marginaleffects/bldg_sfha_q2_dissertation_prepped.RDS"
df <- readRDS(data_path)


df <- df |>
  mutate(coastal_100 = pin10 %in% lake100ft$PIN10,
         coastal_500 = pin10 %in% lake500ft$PIN10,
         nearby_300 = pin10 %in% close_comps$PIN10)

df_nocoast <- df |> filter(coastal_500==FALSE)
```


```{r}
nearby_props_model_pre_add <- feols(
  log_price ~ addedto_prelim_sfha | pin + sale_year ,
  cluster = ~ pin10,
  data = (df |> filter(nearby_300 == 
                         TRUE))
)

nearby_props_model_pre_remove <- feols(
  log_price ~ removedfrom_prelim_sfha  | pin + sale_year ,
  cluster = ~ pin10,
  data = (df |> filter(nearby_300 == 
                         TRUE))
)

nearby_props_model_eff_add <- feols(
  log_price ~ addedto_eff_sfha | pin + sale_year ,
  cluster = ~ pin10,
  data = (df |> filter(nearby_300 == 
                         TRUE))
)

nearby_props_model_eff_remove <- feols(
  log_price ~ removedfrom_eff_sfha| pin + sale_year ,
  cluster = ~ pin10,
  data = (df |> filter(nearby_300 == 
                         TRUE))
)
modelsummary(list(
  nearby_props_model_pre_add, nearby_props_model_pre_remove, nearby_props_model_eff_add, nearby_props_model_eff_remove), output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
            # coef_map = coef_map2_short,
             title = "Main spec: log(price) ~ HighFF x Event × SFHA + Triad + FE") |>
  tab_source_note(md("FE: pin, sale_year. SE clustered at 10-digit parcel level."))
```

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## PIN + Year Fixed Effects by FIRM Date

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha*factor(pre_date)  | pin + sale_year,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha*factor(pre_date)  | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha*factor(pre_date) | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha*factor(eff_date) | pin + sale_year,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha*factor(eff_date)  | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha*factor(eff_date)  | pin + sale_year,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha*factor(eff_date)  | pin + sale_year,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


## Year^Muni Fixed Effects

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## Year^Muni Fixed Effects within 300 Meters of SFHA

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## Year^FIRM_PAN Fixed Effects

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^FIRM_PAN,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^FIRM_PAN,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^FIRM_PAN,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## Year^Township Fixed Effects within 300 meters of treated properties

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


## Year^Township Fixed Effects all Cook County

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df )
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 ))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df)
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df)
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df )
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


# Exclude Coastal Properties 

## Only include properties within 300 meters of SFHA

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df_nocoast |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df_nocoast |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~pin10,
        data = (df_nocoast |> filter(nearby_300 == 
                         TRUE))
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 & nearby_300 == TRUE))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df_nocoast |> filter(nearby_300 == TRUE))
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000& nearby_300 == TRUE))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## Year^Muni Fixed Effects

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df_nocoast )
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 ))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df_nocoast)
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df_nocoast)
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 ))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df_nocoast )
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_nocoast |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```




# Spatial Spillover Concerns

Could exclude untreated properties within the 300 m buffer around SFHA areas or I could exclude properties that were in the 1 in 500 SFHA zone but not the SFHA zone since that is essentially a bufferzone in itself. 


```{r}
# way too big of buffer zone
#close_comps <- readxl::read_xlsx("data/processed/parcelswithin600mof2026SFHA_ExportTable_TableToExcel.xlsx")

#300 meter buffer
close_comps <- readxl::read_xlsx("data/processed/bldgswithin300mof_SFHA_arcgis.xlsx")

# already has eff_sfha_category in it
data_path <- "outputs/q2_marginaleffects/bldg_sfha_q2_dissertation_prepped.RDS"
df <- readRDS(data_path)


#excludes untreated properties within 300 meters of treated properties. 
df_spill <- df |>
  mutate(nearby_300 = pin10 %in% close_comps$PIN10) |>
  filter(nearby_300 == FALSE | 
           (ever_added_prelim == TRUE | ever_removed_prelim == TRUE | 
              ever_added_eff == TRUE | ever_removed_eff)
  )

nearby_props_model_pre_add <- feols(
  log_price ~ addedto_prelim_sfha | pin + sale_year ,
  cluster = ~ pin10,
  data = df_spill
)

nearby_props_model_pre_remove <- feols(
  log_price ~ removedfrom_prelim_sfha  | pin + sale_year ,
  cluster = ~ pin10,
  data = df_spill
)

nearby_props_model_eff_add <- feols(
  log_price ~ addedto_eff_sfha | pin + sale_year ,
  cluster = ~ pin10,
  data = df_spill
)

nearby_props_model_eff_remove <- feols(
  log_price ~ removedfrom_eff_sfha| pin + sale_year ,
  cluster = ~ pin10,
  data = df_spill
)
modelsummary(list(
  nearby_props_model_pre_add, nearby_props_model_pre_remove, nearby_props_model_eff_add, nearby_props_model_eff_remove), output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
            # coef_map = coef_map2_short,
             title = "Excludes non-treated properties within 300 meters of treated areas. Main spec: log(price) ~ HighFF x Event × SFHA + Triad + FE") |>
  tab_source_note(md("FE: pin, sale_year. SE clustered at 10-digit parcel level."))
```

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = df_spill
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data =(df_spill)
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000))
)
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = (df_spill)
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data =(df_spill )
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

## Year^Muni Fixed Effects

or year-township fixed effects of year-municipality became colinear with treated variable. 

```{r}

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df_spill )
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000 ))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data =(df_spill )
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year^Township,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}

eff_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~pin10,
        data = (df_spill )
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000 ))),

  "II" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data =(df_spill )
    ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year^clean_name,
    cluster = ~ pin10,
        data = (df_spill |> filter(change_type != "Never SFHA" & treat_year_add_eff == 10000))

  )
)

all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


