---
title: "Cook County Flood Damage"
format: html
editor: visual
---

## Illinois Flood Insurance Claims

```{r warning=FALSE, message=FALSE}
library(tidyverse)


ilclaims <- read_csv("inputs/data/nfipclaims_CookCounty2.csv") %>%   
  mutate(amountPaidOnBuildingClaim = as.numeric(amountPaidOnBuildingClaim),
        amountPaidOnContentsClaim = as.numeric(amountPaidOnContentsClaim),
       amountPaidOnIncreasedCostOfComplianceClaim = as.numeric(amountPaidOnIncreasedCostOfComplianceClaim),
       totalclaims = amountPaidOnBuildingClaim + amountPaidOnContentsClaim + amountPaidOnIncreasedCostOfComplianceClaim)

#table(ilclaims$yearOfLoss)
```

```{r}
ilclaims %>%  
  group_by(yearOfLoss) %>% 
  summarize(claims = n()) %>%
  ggplot() + 
  geom_col(aes(x=yearOfLoss, y = claims))+
  theme_classic() +
  scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024) )+
  labs(y = "Number of Claims", x = element_blank())


ilclaims %>% 
  group_by(yearOfLoss) %>% 
  summarize(claims = sum(amountPaidOnBuildingClaim + amountPaidOnContentsClaim + amountPaidOnIncreasedCostOfComplianceClaim, na.rm=TRUE)) %>%
  ggplot() + 
  theme_classic() +
  geom_col(aes(x=yearOfLoss, y = claims)) +
  scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024))+
  scale_y_continuous(labels = scales::dollar)+
  labs(y = "Claims Paid ($)", x = element_blank()) 

```

```{r}
table(ilclaims$ratedFloodZone)
table(ilclaims$crsClassificationCode)

# table(ilclaims$nfipCommunityName)  # dont trust! use manually cleaned excel file for names!!

table(ilclaims$floodZoneCurrent)


table(ilclaims$disasterAssistanceCoverageRequired)

table(ilclaims$stateOwnedIndicator)


```

# Insurance Policies
```{r}


ilpolicies <- read_csv("inputs/data/nfippolicies_CookCounty_all.csv", na="NULL") |>
#ilpolicies <- read_csv("inputs/nfippolicies_IL.csv") |>
  mutate(
 #   start_year = as_date(policyEffectiveDate),
#  end_year = as_date(policyTerminationDate),
    start_year = str_sub(policyEffectiveDate, 1, 4),
    end_year = str_sub(policyTerminationDate, 1, 4),
         )
```

```{r}
ilpolicies %>%  
  group_by(start_year) %>% 
  summarize(policies = n()) %>%
  ggplot() + 
  geom_col(aes(x=start_year, y = policies))+
  theme_classic() +
  #scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024) )+
  labs(y = "Number of Policies", x = element_blank())
```


Indicates if the policy is required by the mortgage lender. 
Yes is indicated with either a 'true' or '1'. No is indicated with either a 'false' or '0'	



```{r}
ilpolicies %>%  
  group_by(start_year, nfipCommunityName, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) 
```

Code indicating the use and occupancy type of the insured structure. Note, 2-digit codes are for Risk Rating 2.0 policies. 1 = Single family residence; 2 = 2 to 4 Unit residential building; 3 = Residential building with more than 4 units; 4 = Non-residential building; 6 = Non-Residential Business; 

11 = Single-family residential building with the exception of a mobile home or a single residential unit within a multi unit building;   
12 = A residential non-condo building with 2, 3, or 4 units seeking insurance on all units;  
13 = A residential non-condo building with 5 or more units seeking insurance on all units;   
14 = Residential mobile/manufactured home;    
15 = Residential condo association seeking coverage on a building with one or more units;   
16 = Single residential unit within a multi-unit building;   
17 = Non-residential mobile/manufactured home;   
18 = A non-residential building;    
19 = A non-residential unit within a multi-unit building;

```{r}

ilpolicies %>%  
  filter(start_year == 2013) |>
  group_by(nfipCommunityName, occupancyType) %>% 
  summarize(policies = n())


ilpolicies %>%  
  filter(start_year == 2025) |>
  group_by(nfipCommunityName, occupancyType) %>% 
  summarize(policies = n())



ilpolicies %>%  
  filter(start_year == 2024 | start_year == 2013) |>
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())

ilpolicies %>%  
  filter(start_year == 2024) |>
  group_by(nfipCommunityName, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())


ilpolicies %>%  
  filter(start_year == 2024) |>
  group_by(nfipCommunityName, occupancyType, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())
```

```{r}

ilpolicies %>%  
  group_by(start_year) %>% 
  summarize(policies = n()) |>
  ggplot(aes(x=start_year, y = policies)) +
  theme_classic() +
  geom_col() +
  labs(title = "Flood Insurance Policies, Cook County IL",
       y = "# Policies", x = element_blank())



ilpolicies %>%  
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) |>
    pivot_wider(names_from = mandatoryPurchaseFlag, values_from = policies)
  



ilpolicies %>%  
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) |>
  ggplot() +
  geom_line(aes(x=start_year, y = policies, group = mandatoryPurchaseFlag, color = mandatoryPurchaseFlag))



ilpolicies %>%
  mutate(purchase_year = str_sub(propertyPurchaseDate, 1,4)) |>
  group_by(purchase_year ) %>% 
  summarize(distinct_props = n_distinct(propertyPurchaseDate),
            policy_cost = sum(policyCost))

```


## Sources

FEMA's Open FEMA datasets.

National Weather Service Chicago, IL, 2023. "The July 2 and September 17, 2023, Flash Flood Events in the Chicago Metro Area." [Website](https://www.weather.gov/media/lot/events/2023/07_02/2023_07_02_and_2023_09_17_Chicago_FlashFloods.pdf)
