---
title: "Cook County Flood Insurance Policies and Insurance Claims"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    tbl-cap-location: top
    fig-cap-location: top
---

## Illinois Flood Insurance Claims

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(sf)


ilclaims <- read_csv("inputs/data/nfipclaims_CookCounty2.csv") %>%   
  mutate(amountPaidOnBuildingClaim = as.numeric(amountPaidOnBuildingClaim),
        amountPaidOnContentsClaim = as.numeric(amountPaidOnContentsClaim),
       amountPaidOnIncreasedCostOfComplianceClaim = as.numeric(amountPaidOnIncreasedCostOfComplianceClaim),
       totalclaims = amountPaidOnBuildingClaim + amountPaidOnContentsClaim + amountPaidOnIncreasedCostOfComplianceClaim)

#table(ilclaims$yearOfLoss)
county_rivers <- read_sf("inputs/Mapping_Firms/17031C_20240319/S_WTR_LN.shp")


```

```{r}
ilclaims %>%  
  group_by(yearOfLoss) %>% 
  summarize(claims = n()) %>%
  ggplot() + 
  geom_col(aes(x=yearOfLoss, y = claims))+
  theme_classic() +
  scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024) )+
  labs(y = "Number of Claims", x = element_blank())


ilclaims %>% 
  group_by(yearOfLoss) %>% 
  summarize(claims = sum(amountPaidOnBuildingClaim + amountPaidOnContentsClaim + amountPaidOnIncreasedCostOfComplianceClaim, na.rm=TRUE)) %>%
  ggplot() + 
  theme_classic() +
  geom_col(aes(x=yearOfLoss, y = claims)) +
  scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024))+
  scale_y_continuous(labels = scales::dollar)+
  labs(y = "Claims Paid ($)", x = element_blank()) 

```

```{r}
table(ilclaims$ratedFloodZone)
table(ilclaims$crsClassificationCode)

# table(ilclaims$nfipCommunityName)  # dont trust! use manually cleaned excel file for names!!

table(ilclaims$floodZoneCurrent)


table(ilclaims$disasterAssistanceCoverageRequired)

table(ilclaims$stateOwnedIndicator)


```

## Claims per Area

```{r}
tract_claims <- ilclaims |> 
  filter(yearOfLoss >= 2023 ) |>
  group_by(censusTract) |>
  summarize(n=n(),
            totalclaims = round(sum(totalclaims)))
tract_claims

tracts <- read_sf("inputs/shapefiles_cook/CookTracts.shp") |> mutate(tract = paste0("17031", TRACTCE))

tract_claims <- tract_claims %>%
  mutate(censusTract = as.character(censusTract))|>
  full_join(tracts, by = c("censusTract" = "tract") )

tract_map <- ggplot() +
  geom_sf(data = tract_claims, aes(geometry = geometry, fill = n),color = "black") +
  labs(title = "2023 and 2024: Flood Insurance Policy Claims",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "navy", low = "black",
  na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
    name = "Count",
  )  
tract_map
#table(county_rivers$SHOWN_INDX)
#table(county_rivers$SHOWN_FIRM)


  
# all rivers
#tract_map + geom_sf(data = county_rivers, aes(geometry = geometry), color = "blue", lwd = .5, alpha = .5) 
  

tract_claims %>%
  ggplot(aes(fill = totalclaims)) +
  geom_sf(aes(geometry = geometry), color = "black") +
  labs(title = "2023 and 2024: Flood Insurance Policy Claims",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "navy", low = "black",
  na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
  labels = scales::dollar,
    name = "$",
  )
```

```{r}
zip_claims <- ilclaims |> 
  filter(yearOfLoss >= 2023 ) |>
  group_by(reportedZipCode) |>
  summarize(n=n(),
            totalclaims = round(sum(totalclaims, na.rm = T)))
zip_claims


zipcodes <- read_sf("inputs/shapefiles_cook/CookZipcodes.shp")

zip_claims <- zip_claims %>%
  mutate(reportedZipCode = as.character(reportedZipCode))|>
  full_join(zipcodes, by = c("reportedZipCode" = "ZCTA5CE20") )

ggplot() +
  geom_sf(data = zip_claims, 
          aes(fill = n, geometry = geometry), 
          color = "black") +
  labs(title = "2023 and 2024: Flood Insurance Policy Claims",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "navy", low = "black",
    na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
    name = "Count",
  ) + 
  geom_sf(data = county_rivers, aes(geometry = geometry), color = "blue", lwd = .5, alpha = .5) 


ggplot() +
  geom_sf(data = zip_claims, 
          aes(geometry = geometry, fill = totalclaims), color = "black") +
  labs(title = "2023 and 2024: Flood Insurance Policy Claims",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "navy", low = "black",
  na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
  labels = scales::dollar,
    name = "$",
  ) + 
  geom_sf(data = county_rivers, aes(geometry = geometry), color = "blue", lwd = .5, alpha = .5) 
```

# Insurance Policies

```{r}


ilpolicies <- read_csv("inputs/data/nfippolicies_CookCounty_all.csv", na="NULL") |>
#ilpolicies <- read_csv("inputs/nfippolicies_IL.csv") |>
  mutate(
 #   start_year = as_date(policyEffectiveDate),
#  end_year = as_date(policyTerminationDate),
    start_year = str_sub(policyEffectiveDate, 1, 4),
    end_year = str_sub(policyTerminationDate, 1, 4),
         )
```

```{r}
ilpolicies %>%  
  group_by(start_year) %>% 
  summarize(policies = n()) %>%
  ggplot() + 
  geom_col(aes(x=start_year, y = policies))+
  theme_classic() +
  #scale_x_continuous(breaks = c(1980, 1990, 2000, 2010, 2020, 2024) )+
  labs(y = "Number of Policies", x = element_blank())
```

Indicates if the policy is required by the mortgage lender. Yes is indicated with either a 'true' or '1'. No is indicated with either a 'false' or '0'

```{r}
ilpolicies %>%  
  group_by(start_year, nfipCommunityName, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) 
```

Code indicating the use and occupancy type of the insured structure. Note, 2-digit codes are for Risk Rating 2.0 policies. 1 = Single family residence; 2 = 2 to 4 Unit residential building; 3 = Residential building with more than 4 units; 4 = Non-residential building; 6 = Non-Residential Business;

11 = Single-family residential building with the exception of a mobile home or a single residential unit within a multi unit building;\
12 = A residential non-condo building with 2, 3, or 4 units seeking insurance on all units;\
13 = A residential non-condo building with 5 or more units seeking insurance on all units;\
14 = Residential mobile/manufactured home;\
15 = Residential condo association seeking coverage on a building with one or more units;\
16 = Single residential unit within a multi-unit building;\
17 = Non-residential mobile/manufactured home;\
18 = A non-residential building;\
19 = A non-residential unit within a multi-unit building;

```{r}

ilpolicies %>%  
  filter(start_year == 2013) |>
  group_by(nfipCommunityName, occupancyType) %>% 
  summarize(policies = n())


ilpolicies %>%  
  filter(start_year == 2025) |>
  group_by(nfipCommunityName, occupancyType) %>% 
  summarize(policies = n())



ilpolicies %>%  
  filter(start_year == 2024 | start_year == 2013) |>
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())

ilpolicies %>%  
  filter(start_year == 2024) |>
  group_by(nfipCommunityName, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())


ilpolicies %>%  
  filter(start_year == 2024) |>
  group_by(nfipCommunityName, occupancyType, mandatoryPurchaseFlag) %>% 
  summarize(policies = n())
```

```{r}

ilpolicies %>%  
  group_by(start_year) %>% 
  summarize(policies = n()) |>
  ggplot(aes(x=start_year, y = policies)) +
  theme_classic() +
  geom_col() +
  labs(title = "Flood Insurance Policies, Cook County IL",
       y = "# Policies", x = element_blank())



ilpolicies %>%  
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) |>
    pivot_wider(names_from = mandatoryPurchaseFlag, values_from = policies)
  



ilpolicies %>%  
  group_by(start_year, mandatoryPurchaseFlag) %>% 
  summarize(policies = n()) |>
  ggplot() +
  geom_line(aes(x=start_year, y = policies, group = mandatoryPurchaseFlag, color = mandatoryPurchaseFlag))



ilpolicies %>%
  mutate(purchase_year = str_sub(propertyPurchaseDate, 1,4)) |>
  group_by(purchase_year ) %>% 
  summarize(distinct_props = n_distinct(propertyPurchaseDate),
            policy_cost = sum(policyCost))

```

## Census Block summaries


```{r}
block_totals <- ilpolicies |> 
  filter(start_year <= 2024 ) |>
  group_by(start_year, reportedZipCode, censusBlockGroupFips) |>
  summarize(n=n(),
            totalContentsInsuranceCoverage = sum(totalContentsInsuranceCoverage),
            totalInsurancePremiumOfThePolicy = sum(totalInsurancePremiumOfThePolicy),
            totalBuildingInsuranceCoverage = sum(totalBuildingInsuranceCoverage)
            ) |>
  arrange(desc(start_year))
block_totals

```


```{r}
#| eval: false
#blocks <- read_sf("inputs/cb_2023_17_bg_500k/cb_2023_17_bg_500k.shp") |> filter(COUNTYFP == "031")
block <- read_sf("inputs/shapefiles_cook/CookBlock.shp") |> mutate(block = paste0("17031", BLOCKCE20))

block_totals %>%
  filter(start_year == 2024) %>%
  mutate(censusBlockGroupFips = as.character(censusBlockGroupFips))|>
  full_join(block, by = c("censusBlockGroupFips" = "block") ) %>%    
  ggplot(aes(fill = n)) +
  geom_sf(aes(geometry = geometry), color = "black") +
  labs(title = "2024: Flood Insurance Policy Counts",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "darkblue", low = "black",
  na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
    name = "Count",
  )
```


## Census Tract summaries

```{r}
tract_totals <- ilpolicies |> 
  filter(start_year <= 2024 ) |>
  group_by(start_year, censusTract) |>
  summarize(n=n(),
            totalContentsInsuranceCoverage = sum(totalContentsInsuranceCoverage),
            totalInsurancePremiumOfThePolicy = sum(totalInsurancePremiumOfThePolicy),
            totalBuildingInsuranceCoverage = sum(totalBuildingInsuranceCoverage)
            ) |>
  arrange(desc(start_year))
tract_totals

#tracts <- read_sf("inputs/cb_2023_17_tract_500k/cb_2023_17_tract_500k.shp") |> filter(COUNTYFP == "031")

tracts <- read_sf("inputs/shapefiles_cook/CookTracts.shp") |> mutate(tract = paste0("17031", TRACTCE))

tract_totals %>%
  filter(start_year == 2024) %>%
  mutate(censusTract = as.character(censusTract))|>
  full_join(tracts, by = c("censusTract" = "tract") ) %>%    
  ggplot(aes(fill = n)) +
  geom_sf(aes(geometry = geometry), color = "black") +
  labs(title = "2024: Flood Insurance Policy Counts",
  caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "darkblue", low = "black",
  na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
    name = "Count",
  )
```

```{r}
muni_totals <- ilpolicies |> 
  filter(start_year <= 2024 ) |>
  group_by(start_year, nfipCommunityName, #reportedZipCode, censusBlockGroupFips
                       ) |>
  summarize(n=n(),
            totalContentsInsuranceCoverage = sum(totalContentsInsuranceCoverage),
            totalInsurancePremiumOfThePolicy = sum(totalInsurancePremiumOfThePolicy),
            totalBuildingInsuranceCoverage = sum(totalBuildingInsuranceCoverage)
            )
muni_totals
```

## Zipcodes

```{r}
zips <- ilpolicies |> 
  filter(start_year <= 2024) |>
  group_by(start_year, reportedZipCode) |>
  summarize(
    n=n(),
    totalContentsInsuranceCoverage = sum(totalContentsInsuranceCoverage),
    totalInsurancePremiumOfThePolicy = sum(totalInsurancePremiumOfThePolicy),
    totalBuildingInsuranceCoverage = sum(totalBuildingInsuranceCoverage)
  ) |>
  mutate(across(where(is.numeric), round, digits =0))


zipcodes <- read_sf("inputs/shapefiles_cook/CookZipcodes.shp")

zips <- zips |> 
  mutate(reportedZipCode = as.character(reportedZipCode))|>
  full_join(zipcodes, by = c("reportedZipCode" = "ZCTA5CE20")) 

ggplot() +
  geom_sf(data = (zips |> filter(start_year == 2024)), 
          aes(geometry = geometry, fill = n), 
          color = "black") +
    labs(title = "2024 FEMA Flood Insurance Policies", caption = "") +
    theme_void() +
    theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
    scale_fill_steps2(
      
      na.value = "white",
      nice.breaks = FALSE,
      show.limits=TRUE,
      name = "Count",
    ) +
    geom_sf(data = county_rivers, aes(geometry = geometry), color = "blue", lwd = .5, alpha = .5) 
  

ggplot() +
  geom_sf(data = (zips |> filter(start_year == 2023)), 
                  aes(geometry = geometry, fill = n), 
                  color = "black") +
  labs(title = "2023 FEMA Flood Insurance Policies", caption = "") +
  theme_void() +
  theme(axis.ticks = element_blank(), axis.text = element_blank())+# +#+
  scale_fill_steps2(
    high = "brown", low = "black",
    na.value = "white",
    nice.breaks = FALSE,
    show.limits=TRUE,
    name = "Count",
  ) +
  geom_sf(data = county_rivers, aes(geometry = geometry), color = "blue", lwd = .5, alpha = .5) 
```



## Sources

FEMA's Open FEMA datasets.

National Weather Service Chicago, IL, 2023. "The July 2 and September 17, 2023, Flash Flood Events in the Chicago Metro Area." [Website](https://www.weather.gov/media/lot/events/2023/07_02/2023_07_02_and_2023_09_17_Chicago_FlashFloods.pdf)
