---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
---

# Data Prep

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

```{r setup, warning=FALSE, message=FALSE}
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
```

# Old SFHA PINs as of 2018 NFHL

Downloaded archieved replication materials from Miyuki et al. and took the Illinois Flood Hazard Layer as it was in 2018. Clipped all Parcels that intersected with the SFHAs and made a list of pins. 

```{r warning = FALSE}
# 
sfha_pins2018 <-readxl::read_xlsx("inputs/data/Parcels_SFHA_2018NFHL.xlsx")

string_sfha_pins2018 <- sfha_pins2018 |> 
  select(PIN14) |> 
  pull()
```

# FEMA Effective Floodzones as of 2024

```{r warning = FALSE}
 
sfha_pins2024 <-readxl::read_xlsx("inputs/data/parcels_inSFHA_2024NFHL.xlsx") 

string_sfha_pins2024 <- sfha_pins2024 |> 
  select(PIN14) |> 
  pull()

```

```{r}
sfha_pins2024 |> filter(!PIN14 %in% string_sfha_pins2018)

sfha_pins2018 |> filter(!PIN14 %in% string_sfha_pins2024)

```

```{r}
res_sales |> 
  filter(pin %in% string_sfha_pins2018) |> 
  group_by(pin) |>
  summarize(n=n()) |>
  filter(n > 1)
```

```{r}
res_sales |> 
  filter(pin %in% string_sfha_pins2024) |> 
  group_by(pin) |>
  summarize(n=n()) |>
  filter(n > 1)
```

# FEMA Preliminary Floodzones - For NW Cook County Update

Used preliminary SFHA boundaries for North West areas of Cook County Used parcel boundaries and flood plain in arcgis pro to clip parcels that were changed.

```{r}
prelim_SFHA <- readxl::read_xlsx("inputs/data/Parcels_in_PrelimFIRMSFHA_NWCook.xlsx")

prelim_SFHA %>% filter(!PIN14 %in% string_sfha_pins2018)

prelim_SFHA %>% filter(!PIN14 %in% string_sfha_pins2024)

```


# Sales Data

1,762,627 sales for all property classes (1,869,796 after new download in January)

1,070,348 sales for Class 2 Residential properties (1,655,745 after new download and identifying any pin that was residential at any point in time and including it)



```{r, warning=FALSE, message=FALSE}
#sales <- read_csv("./inputs/Assessor_Parcel_Sales_20240911.csv")
sales <- read_csv("./inputs/Assessor_Parcel_Sales_20250105.csv") %>% 
  filter(year > 2005) %>%
  mutate(date = lubridate::mdy(sale_date))


sales |> 
  mutate(class = as.numeric(class),
         res_c2 = ifelse(class >= 200 & class <= 299, 1, 0)) |> 
  group_by(pin) |>
  mutate(
    res_c2 = ifelse(sum(res_c2) > 1, TRUE, FALSE),
    sold_once = ifelse(n() == 1, TRUE, FALSE),
    sold_multi = ifelse(n() > 1, TRUE, FALSE),
    
    sold_pre2014 = ifelse(year <= 2013, TRUE, FALSE),
    sold_post2013 = ifelse(year > 2013, TRUE, FALSE),
    
    sold_pre2024 = ifelse(year <= 2023, TRUE, FALSE),
    sold_post2023 = ifelse(year > 2023, TRUE, FALSE),
) |> 
    ungroup() |> 
    group_by(res_c2, sold_once, sold_multi) |> 
    summarize(n=n())


res_sales <- sales |> 
  mutate(class = as.numeric(class),
         res_c2 = ifelse(class >= 200 & class <= 299, TRUE, FALSE),
) |> 
  group_by(pin) |>
  filter(sum(res_c2==TRUE) >= 1) |>
  mutate(
    times_sold = n(),

    sold_once = ifelse(times_sold == 1, TRUE, FALSE),
    sold_multi = ifelse(times_sold > 1 , TRUE, FALSE),
    ) |> 
  ungroup() |>
  mutate(
    sold_pre2014 = ifelse(year <= 2013, TRUE, FALSE),
    sold_post2013 = ifelse(year > 2013, TRUE, FALSE),
    
    sold_btwn_20132023 = ifelse(year > 2013 & year < 2024, TRUE, FALSE),
    
    sold_pre2024 = ifelse(year <= 2023, TRUE, FALSE),
    sold_post2023 = ifelse(year > 2023, TRUE, FALSE),
    ) |> 
  ungroup()


res_sales <- res_sales |> 
  mutate(insfha_2018 = ifelse(pin %in% string_sfha_pins2018, 1, 0),
         insfha_2024 = ifelse(pin %in% string_sfha_pins2024, 1, 0),
         inprelimsfha = ifelse(pin %in% prelim_SFHA$PIN14, 1, 0))

res_sales <- res_sales |> 
  mutate(change_sfha = insfha_2024 - insfha_2018)
```


```{r}
#| tbl-cap: "6,594 distinct pins have been in an SFHA and sold"

res_sales |> 
  filter(sold_multi == TRUE & 
           (pin %in% string_sfha_pins2018 | 
              pin %in% string_sfha_pins2024) ) |> distinct(pin)
```


```{r}
#| tbl-cap: "465  distinct pins have either been added to or removed from an SFHA and sold multiple times."

res_sales |> 
  filter(sold_multi == TRUE & change_sfha !=0 ) |> 
  distinct(pin)
```


```{r, warning=FALSE, message=FALSE}
table(res_sales$insfha_2018)
table(res_sales$insfha_2024)
table(res_sales$change_sfha)
```


```{r, warning=FALSE, message=FALSE}
res_sales |> 
  group_by(sold_multi) |> 
    summarize(n=n(),
              distinct_pins = n_distinct(pin))

res_sales |> 
  group_by(times_sold) |> 
    summarize(distinct_pins = n_distinct(pin))

res_sales |>
  group_by(sold_pre2014, sold_btwn_20132023, sold_post2023) |> 
  summarize(n = n(), n_distinct = n_distinct(pin))

res_sales |>
  filter(times_sold < 10 & sale_price > 5000) |>
  group_by(sold_multi, 
         #  sold_pre2014, sold_btwn_20132023, sold_post2023, 
           insfha_2024, insfha_2018) |> 
  summarize(n = n(), n_distinct = n_distinct(pin))
```






```{r, warning=FALSE, message=FALSE}
ccao_loa <- read_csv("./inputs/ccao_loa.csv") %>%
  mutate(loa = ifelse(loa == 0, NA, loa))
 # mutate(class_code = as.character(class_code))


# All PINs that are located in land blocks that have at least 1 SFHA pin
landblock_pins <- read_csv("outputs/pins_in_Blocks_2006_2023_20241126.csv") |> 
  # landblock_pins <- read_csv("./inputs/flood_pins_ptax.csv") %>%

  left_join(ccao_loa, by = c("year","class" = "class_code")) %>%
  mutate(class = as.character(class),
         class_1dig = str_sub(class, 1, 1)) %>%
   mutate(fmv_mailed = av_mailed/loa,
          fmv_board = av_board/loa,
          fmv_clerk = av_clerk/loa
         ) |>
  mutate(across(fmv_mailed:fmv_clerk, round, digits = 0))


nbh_pins <- read_csv("outputs/nbh_pins_parceluniversepull2022.csv")




sfha_pins <- landblock_pins %>% 
  filter(SFHA == 1) %>%
  select(pin) |> 
  distinct() |> 
  pull()

fsf_5plus <- nbh_pins %>% 
  filter(env_flood_fs_factor >= 5) %>%
  select(pin) |>
  distinct() |> 
  pull()

fsf_4plus <- nbh_pins %>% 
  filter(env_flood_fs_factor >= 4) %>%
  select(pin) |>
  distinct() |> 
  pull()


```




**Note that `sfha_pins` are PINs that have the SFHA indicator == 1 and `fsf_5plus` are PINs that have a flood factor rating of 5 or higher**  

```{r}
#| label: sold-properties-infloodzones

res_sales <- res_sales |>
  mutate(in_sfha = ifelse(pin %in% sfha_pins, 1, 0), # according to CCAO dataset, not FEMA shapefiles
         in_ffs_4plus = ifelse(pin %in% fsf_4plus, 1, 0),
         in_ffs_5plus = ifelse(pin %in% fsf_5plus, 1, 0),
         # group1 = ifelse(sold_pre2014 == T & sold_btwn_20132023 == T & sold_post2023 == T, 1, 0),
         # group2 = ifelse(sold_pre2014 == F & sold_btwn_20132023 == T & sold_post2023 == T, 1, 0),
         # group3 = ifelse(sold_pre2014 == T & sold_btwn_20132023 == T & sold_post2023 == T, 1, 0),
         # group4 = ifelse(sold_pre2014 == T & sold_btwn_20132023 == T & sold_post2023 == T, 1, 0),
         
  )

pin_groups <- res_sales |>
  mutate(risk_change = case_when(
    insfha_2018 != insfha_2024  ~ "Changes SFHA - Recent",
    insfha_2018 == 1 & insfha_2024 == 1 ~ "Always in SFHA",
    insfha_2018 == 0 & insfha_2024 == 0 ~ "Never in SFHA",
    T ~ "Check me") )|>
  filter(sale_price > 5000) |>
  group_by(pin, risk_change) |> 
  mutate(n = n(),
         ) |>
  filter(n() < 10) |>
  summarize(times_sold = ifelse(n() > 1, "Multi", "Once"),
           # years_sold = as.character(list(unique(year))),
            sold_post2023 = ifelse(any(year > 2022), 1, 0)            
            ) |>
  mutate(
      risk_type = case_when(
     #   pin %in% sfha_pins ~ "In SFHA",     ## Too vague!
        pin %in% sfha_pins & !pin %in% fsf_5plus ~ "In SFHA Only",
        pin %in% fsf_5plus & pin %in% sfha_pins ~ "SFHA & FSF Score 5+",
        pin %in% fsf_5plus & !pin %in% sfha_pins ~"FSF Score 5+ Only",
        T ~ "Low Risk"
      )  #,
    #  flooded = case_when(
    # ...   ~ "Reported Damage",
    # ...   ~ "Did not report Damage",
    # ...   ~ "Flooded Pre-Sale",
    # ...   ~ "Flooded Post-Sale"
    #  )
    
  )
  
table(pin_groups$risk_type, pin_groups$times_sold, pin_groups$sold_post2023)
table(pin_groups$risk_type, pin_groups$times_sold, pin_groups$risk_change)

```

```{r}
pin_groups |>
  group_by(times_sold, risk_type, risk_change
         #  sold_pre2014, sold_btwn_20132023, sold_post2023, 
          # insfha_2024, insfha_2018
           ) |> 
  summarize(n = n(), n_distinct = n_distinct(pin))
```


```{r}
#| label: tbl-SFHAparcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels in SFHAs that have been sold."

sfhasales <-  res_sales %>%
  filter(pin %in% sfha_pins) %>%
  left_join(landblock_pins, by = c("year", "pin")) %>%
  mutate(parcel = str_sub(pin, 1, 10))

sfhasales %>% 
  group_by(parcel, year, sale_document_num) %>%
  summarize(pincount = n(),
            sale_price = first(sale_price),
            sale_price_sum = sum(sale_price)) %>% 
  arrange(desc(pincount))

sfhasales %>% 
  filter(sale_price >5000) |>
  group_by(parcel, year, sale_document_num) %>%
  summarize(pincount = n(),
            sale_price = first(sale_price),
            sale_price_sum = sum(sale_price)) %>% 
  arrange(desc(parcel))

duplicates <- sfhasales |> janitor::get_dupes(pin, parcel, year, sale_price)

sfhasales |> 
  filter(sale_price > 5000) |>
  group_by(pin, parcel, year, sale_price) |> 
  distinct(pin,year,sale_price, .keep_all = TRUE)
```


```{r}
#| label: tbl-SFHAparcels-soldtimes
#| tbl-cap-location: margin
#| tbl-cap: "SFHA PIN Sales: Number of times sold and count of years properties were sold in"

sfhasales %>% 
  filter(sale_price>5000) |>
  group_by(pin) %>% 
  summarize(timessold=n(),
            distinct_years = n_distinct(year),
            max_price= max(sale_price),
            min_price = min(sale_price),
            class = max(class_1dig)) %>% 
  filter(timessold>1) %>% 
  arrange(desc(timessold))
```


```{r}
#| label: tbl-salesover5K
#| tbl-cap-location: margin
#| tbl-cap: "Sales of SFHA PINs over $5000 for properties in SFHA FEMA Zones. N = 18,157"

sfhasales %>% 
  filter(!is.na(sale_price) & sale_price > 5000) %>% 
  arrange(desc(num_parcels_sale), sale_document_num, pin )
```

```{r}
#| label: fig-pinsales-andAV
#| fig-cap: "PIN Sale Price and Assessed Values over time."
#| layout-ncol: 3


sfhasales %>% 
  filter(pin == "09163040191019") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "05201210150000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "09281140060000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)


```

```{r}
#| label: tbl-floodfactor-parcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels with Flood Factor Risk Rating >= 5  that have been sold. 206,304 PINs have sales prices above $5K and flood factor ratings."

floodsales <- sales %>% 
  filter(pin %in% sfha_pins) %>%
  left_join(landblock_pins, by = c("year", "pin", "class"))



#floodsales %>% filter(!is.na(sale_price))
floodsales %>% filter(#!is.na(sale_price) & 
                        sale_price > 5000)
# 206,304 sales for pins in flood factor high risk areas of 5 or higher
```



### SFHA PINs

#### 2018 SHFA PINs

```{r}
sales |> 
  filter(pin %in% sfhapins2018) |>
  distinct(pin)

sales |> 
  filter(sale_price> 5000) |>
  filter(pin %in% sfhapins2018) |>
  group_by(pin) |> 
  summarize(timessold=n()) |> arrange(desc(timessold))
```


#### 2022? or more recent SFHA Pins

```{r}
#| label: fig-saleprices-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average Sale Prices per year by Major Property Class.** Some years have very few sales and can be skewed by whatever property happens to be sold that year."
#| warning: false
#| message: false

sfhasales %>% 
  group_by(year, major_class) %>%
  summarize(sale_price = mean(sale_price, na.rm=TRUE)) %>%
  ggplot() +
  geom_line(aes(x=year, y = sale_price)) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg Sale Price for Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free"             )
```


```{r}
#| label: tbl-SFHAsales-byclass
#| tbl-cap: "Number of SFHA sales per year by major class."

sfhasales %>% 
  group_by(year, major_class) %>%
  summarize(NumberSold=n()) %>%
  pivot_wider(names_from = major_class, values_from = NumberSold)
```

```{r}
#| label: fig-AV-bymajorclass-SOLD
#| fig-cap-location: margin
#| fig-cap: "**Average Assessed Value per year by Major Property Class for properties within FEMA SFHAs THAT WERE SOLD!** Some major classes have very few properties located in SFHAs so sudden changes in AV for one or two properties can skew the graphs very easily."
#| warning: false
#| message: false

sfhasales %>% 
  filter(!major_class %in% c("EX", "E", "R", "RR", "4"))%>%
  group_by(year, major_class) %>%
  summarize(av_mailed = mean(av_mailed, na.rm=TRUE),
            av_board = mean(av_board, na.rm=TRUE),
            av_clerk = mean(av_clerk, na.rm=TRUE)) %>%
  ggplot() +
      geom_line(aes(x=year, y = av_clerk)) + 
    geom_point(aes(x=year, y = av_clerk)) + 
# 
#   geom_line(aes(x=year, y = av_mailed
#                 ), linetype = 2 ) + 
#     geom_line(aes(x=year, y = av_board
#                   ) ) + 
#     geom_point(aes(x=year, y = av_board
#                    )) + 
#     geom_line(aes(x=year, y = av_mailed
#                 ), linetype = 2 ) + 
  theme_classic() + 
  
  scale_y_continuous(name = "Avg Assessed Value for Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free"
             )
```

```{r}
#| label: fig-FMV-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV per year by Major Property Class for properties within FEMA SFHAs.** Some major classes have very few properties located in SFHAs so sudden changes in AV for one or two properties can skew the graphs very easily. Roughly accounts for change in assessment ratio that occured during 2010ish. Only did rough estimate for classes 2 & 5."
#| warning: false
#| message: false
#| 
landblock_pins %>% 
  filter(pin %in% sfha_pins & class_1dig %in% c(2, 5)) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=TRUE)) %>%
  ggplot() +
      geom_line(aes(x=year, y = fmv_clerk)) + 
    geom_point(aes(x=year, y = fmv_clerk)) + 

  # geom_line(aes(x=year, y = fmv_mailed), linetype = 2 ) + 
  #   geom_line(aes(x=year, y = fmv_board) ) + 
  #   geom_point(aes(x=year, y = fmv_board)) + 
  #   geom_line(aes(x=year, y = fmv_mailed), linetype = 2 ) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```

```{r}
landblock_pins %>% 
  mutate(sfha_flag = as.factor(ifelse(pin %in% sfha_pins, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class, sfha_flag) %>%
  summarize( pincount = n()) %>% 
  pivot_wider(values_from = pincount, names_from = c("major_class", "sfha_flag"))
```

```{r}
#| label: fig-FMV-bymajorclass-comparison
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV per year by Major Property Class for properties:  FEMA SFHA Properties vs non-SFHA Properties.** Compares all PINs located within a block of land (first 7 digits of PIN). Includes land blocks that have at least one PIN in an SFHA. Assumption is that PINs in close proximity are aware of nearby properties flooding."
#| warning: false
#| message: false
#| 
landblock_pins %>% 
  mutate(sfha_flag = as.factor(ifelse(pin %in% sfha_pins, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class, sfha_flag) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=TRUE),

            pincount = n()) %>%
  filter(major_class!= 0) %>%
  ggplot() +
    geom_line(aes(x=year, y = fmv_clerk, color = sfha_flag)) + 
    geom_point(aes(x=year, y = fmv_clerk, color = sfha_flag)) + 

 # geom_line(aes(x=year, y = fmv_mailed, color = sfha_flag)) + 
  #  geom_line(aes(x=year, y = fmv_board, color = sfha_flag), linetype = 2 ) + 
  #  geom_point(aes(x=year, y = fmv_board, color = sfha_flag)) + 
   # geom_line(aes(x=year, y = fmv_mailed, color = sfha_flag), linetype = sfha_flag ) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```


### Flood Factor PINs and AV

```{r}
#| label: fig-FMV-bymajorclass-floodfactorcomparison
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV by Major Property Class & Flood Factor Risk: For Properties with a rating of 5 or higher designating them as high risk** Roughly accounts for change in assessment ratio that occured during 2010ish. Only did rough estimate for classes 2 & 5."
#| warning: false
#| message: false

landblock_pins %>% 
  mutate(ff_flag = as.factor(ifelse(pin %in% fsf_5plus, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class, ff_flag) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=T),
            pincount = n()) %>%
  filter(#pincount > 60 & 
           major_class != 0) %>%
  ggplot() + 
      geom_line(aes(x=year, y = fmv_clerk, color = ff_flag)) + 
    geom_point(aes(x=year, y = fmv_clerk, color = ff_flag)) + 

  # geom_line(aes(x=year, y = fmv_mailed, color = ff_flag)) + 
  #   geom_line(aes(x=year, y = fmv_board, color = ff_flag), linetype = 2 ) + 
  #   geom_point(aes(x=year, y = fmv_board, color = ff_flag)) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```

```{r}
#| label: fig-AV-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average Assessed Value per year by Major Property Class for properties within FEMA SFHAs.** Some major classes have very few properties located in SFHAs so sudden changes in AV for one or two properties can skew the graphs very easily."
#| warning: false
#| message: false
#| 
landblock_pins %>% 
  filter(pin %in% sfha_pins) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(av_mailed = mean(av_mailed, na.rm=TRUE),
            av_board = mean(av_board, na.rm=TRUE)) %>%
  ggplot() +
  geom_line(aes(x=year, y = av_mailed), linetype = 2 ) + 
    geom_line(aes(x=year, y = av_board) ) + 
    geom_point(aes(x=year, y = av_board)) + 
    geom_line(aes(x=year, y = av_mailed), linetype = 2 ) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg Assessed Value for Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006,  2015,  2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```

### FMV and Sales

```{r}
#| label: fig-FMV-andsales
#| fig-cap-location: margin
#| fig-cap: "**Fair Market Value and Sales Price"
#| warning: false
#| message: false

landblock_pins %>% 
  left_join(sales %>% filter(sale_price > 5000) %>% select(-class), by = c("year", "pin")) %>%
  mutate(ff_flag = as.factor(ifelse(pin %in% fsf_5plus, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=T),
            sales = mean(sale_price, na.rm=T),
            pincount = n()) %>%
  filter(major_class != 0) %>%
  ggplot() + 
    geom_line(aes(x=year, y = fmv_clerk)) + 
    geom_point(aes(x=year, y = fmv_clerk)) + 
    geom_line(aes(x=year, y = sales, color="red")) + 
    geom_point(aes(x=year, y = sales, color="red")) +
  # geom_line(aes(x=year, y = fmv_mailed, color = ff_flag)) + 
  #   geom_line(aes(x=year, y = fmv_board, color = ff_flag), linetype = 2 ) + 
  #   geom_point(aes(x=year, y = fmv_board, color = ff_flag)) + 
  theme_classic() + 
  scale_y_continuous(name = "Dollars", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```


# Lived Experience PINs

## Flood Event 2023 - Disaster Declarations / Lived Experience

Cicero and Berwyn had lots of damage during DR 4728. Cicero had 25,836 housing units in 2020 and over 6000 of them applied and were granted IHP funds. 


Dolton and Calumet City were damaged during DR 4749.

```{r}
ptax245 <- readxl::read_xlsx("inputs/PTAX-245_data.xlsx")

ptax245 <- ptax245 %>% 
  mutate(
    pin = str_remove_all(pin, "-"),
    keypin = as.character(KeyPIN)) %>%
  mutate(keypin_concat = as.character(keypin),
         keypin_concat = str_remove_all(keypin_concat, "-"),
         keypin_concat = str_pad(keypin_concat, 14, "left", pad = "0"),
         major_class = str_sub(Class, 1, 1),
         parcel = str_sub(pin, 1, 10),
         block = str_sub(pin, 1, 7),
         year = 2023,
         appealed = 1 ) %>%
  select(pin, keypin_concat, parcel, block, Class, major_class, everything()) %>% 
  distinct() %>% 
  arrange(pin)
ptax_pins <- ptax245 |> select(pin) |> pull()

res_sales <- res_sales |> mutate(flood2023 = ifelse(pin %in% ptax245, 1, 0))

```

245 PINs in Cicero and 45 PINs in Berwyn appealed their property tax (plus 2 in Oak Park, 2 in River Forest, and 1 in Riverside).

```{r}

res_sales %>% filter(pin %in% ptax245)

```


90,000 Post Disaster Individual Assistance Grants between the two disasters in 2023. 
Only a few million in NFIP claims were paid out from these flood events but over $300 million in IHP fund were distributed. 

- Part of this is because the areas hit hardest (Cicero and Berwyn have no SFHAs and no properties are required to have flood insurance. In general, not many properties in SFHAs in Cook County, especially where these flood events occurred. Makes it unlikely that residents have flood insurance and they can't file flood insurance claims if they don't have flood insurance. )

Cook County also had disaster declarations in 1993, 1996, 1997, 2007, 2009, 2010, 2013, and 2023X2.

