---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    tbl-cap-location: top
    fig-cap-location: top
---

# Data Prep

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

Parcel shapefile used in ArcGIS Pro is downloaded from CCAO's Archived 2022 parcel dataset [here.](https://datacatalog.cookcountyil.gov/Property-Taxation/ccgisdata-Parcel-2021/77tz-riq7/about_data)

```{r setup, warning=FALSE, message=FALSE}
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)

sales <- read_csv("./inputs/Assessor_Parcel_Sales_20250105.csv") %>% 
  filter(year > 2005) %>%
  mutate(date = lubridate::mdy(sale_date))


```

# FEMA FIRM Shapefiles
## FEMA Effective Floodzones from 2018 NFHL

Downloaded archieved replication materials from Miyuki et al. and took the Illinois Flood Hazard Layer as it was in 2018. Clipped all Parcels that intersected with the SFHAs and made a list of pins. 

```{r warning = FALSE}
# 
sfha_pins2018 <-readxl::read_xlsx("inputs/data/Parcels_SFHA_2018NFHL.xlsx") |>
  select(PIN14, township = PINA, AssessorBLDGclass, `Parcel Type`, MUNICIPALITY, UPPER_ELEV, LOWER_ELEV, everything())

string_sfha_pins2018 <- sfha_pins2018 |> 
  select(PIN14) |> 
  pull()
```

## FEMA Effective Floodzones as of 2024

```{r warning = FALSE}
#| layout-ncol: 2
#| tbl-cap: "SFHA Comparison. Data from FEMA FIRMs downloaded in 2018 and in 2024."
#| tbl-subcap: 
#|  - "PINs that were in SFHAs in 2024 but not in 2018."
#|  - "PINs that were in SFHAs in 2018 but not in 2024."
 
sfha_pins2024 <- readxl::read_xlsx("inputs/data/parcels_inSFHA_2024NFHL.xlsx") |>
  select(PIN14, township = PINA, AssessorBLDGclass, `Parcel Type`, MUNICIPALITY, UPPER_ELEV, LOWER_ELEV, everything())

string_sfha_pins2024 <- sfha_pins2024 |> 
  select(PIN14) |> 
  pull()

sfha_pins2024 |> filter(!PIN14 %in% string_sfha_pins2018)

sfha_pins2018 |> filter(!PIN14 %in% string_sfha_pins2024)

```


```{r, warning=FALSE, message=FALSE}
ccao_loa <- read_csv("./inputs/ccao_loa.csv") %>%
  mutate(loa = ifelse(loa == 0, NA, loa))
 # mutate(class_code = as.character(class_code))


# All PINs that are located in land blocks that have at least 1 SFHA pin
landblock_pins <- read_csv("outputs/pins_in_Blocks_2006_2023_20241126.csv") |> 
  # landblock_pins <- read_csv("./inputs/flood_pins_ptax.csv") %>%

  left_join(ccao_loa, by = c("year","class" = "class_code")) %>%
  mutate(class = as.character(class),
         class_1dig = str_sub(class, 1, 1)) %>%
   mutate(fmv_mailed = av_mailed/loa,
          fmv_board = av_board/loa,
          fmv_clerk = av_clerk/loa
         ) |>
  mutate(across(fmv_mailed:fmv_clerk, round, digits = 0))


nbh_pins <- read_csv("outputs/nbh_pins_parceluniversepull2022.csv")




sfha_pins <- landblock_pins %>% 
  filter(SFHA == 1) %>%
  select(pin) |> 
  distinct() |> 
  pull()

fsf_5plus <- nbh_pins %>% 
  filter(env_flood_fs_factor >= 5) %>%
  select(pin) |>
  distinct() |> 
  pull()

fsf_4plus <- nbh_pins %>% 
  filter(env_flood_fs_factor >= 4) %>%
  select(pin) |>
  distinct() |> 
  pull()


```


```{r}
#| layout-ncol: 2
#| tbl-cap: "Number of sales (all property classes) for properties that were in an SFHA at some point."
#| tbl-subcap:  
#| - "Number of Sales for PINs in SFHA in 2018."
#| - "Number of Sales for PINs in SFHA in 2024."
 

sales |> 
  filter(pin %in% string_sfha_pins2018) |> 
  group_by(pin) |>
  summarize(n=n()) |>
  filter(n > 1)

sales |> 
  filter(pin %in% string_sfha_pins2024) |> 
  group_by(pin) |>
  summarize(n=n()) |>
  filter(n > 1)
```

## FEMA Preliminary Floodzones - For NW Cook County Update

Used preliminary SFHA boundaries for North West areas of Cook County Used parcel boundaries and flood plain in arcgis pro to clip parcels that were changed.

```{r}
#| layout-ncol: 2
#| tbl-cap: "PINs in the preliminary SFHA released in NW Cook County that are not peviously in SFHAs."
#| tbl-subcap:
#| - "Preliminary PINs not in 2018 SFHA"
#| - "Preliminary PINs not in 2024 SFHA"



prelim_SFHA <- readxl::read_xlsx("inputs/data/Parcels_in_PrelimFIRMSFHA_NWCook.xlsx") |>
  select(PIN14, township = PINA, AssessorBLDGclass, `Parcel Type`, MUNICIPALITY, UPPER_ELEV, LOWER_ELEV, everything())

prelim_SFHA %>% filter(!PIN14 %in% string_sfha_pins2018)

prelim_SFHA %>% filter(!PIN14 %in% string_sfha_pins2024)

```


# Sales Data

1,762,627 sales for all property classes (1,869,796 after new download in January)

1,070,348 sales for Class 2 Residential properties (1,655,745 after new download and identifying any pin that was residential at any point in time and including it)

# Frequency of Sales

```{r}

sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(pin %in% sfha_pins, "In FP", "Outside FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Sales") |>
  mutate(
    Year = as.character(year),
    TotalSales = `In FP` + `Outside FP`,
    `FP Share (%)` = `In FP` / TotalSales,
   `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)) |>
  select(-c(TotalSales, year)) |> 
  mutate(Year = as.character(Year), .before = `In FP`) |> 
  select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |>
  flextable::flextable()

```

```{r}
sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(pin %in% sfha_pins, "In FP", "Outside FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
   Ratio =  scales::percent(Ratio, accuracy = 0.01),
   Year = as.character(year)) |> 
  select(Year, Sales, `In FP`, `Outside FP`, Ratio) |>
  flextable::flextable()
```


# Timing of Sales around variables of interest

```{r, warning=FALSE, message=FALSE}

res_sales <- sales |> 
  mutate(class = as.numeric(class),
         res_c2 = ifelse(class >= 200 & class <= 299, TRUE, FALSE),
) |> 
  group_by(pin) |>
  filter(sum(res_c2==TRUE) >= 1) |>
  mutate(
    times_sold = n(),

    sold_once = ifelse(times_sold == 1, TRUE, FALSE),
    sold_multi = ifelse(times_sold > 1 , TRUE, FALSE),
    ) |> 
  ungroup() |>
  mutate(
    sold_pre2014 = ifelse(year <= 2013, TRUE, FALSE),
    sold_post2013 = ifelse(year > 2013, TRUE, FALSE),
    
    sold_btwn_20132023 = ifelse(year > 2013 & year < 2024, TRUE, FALSE),
    
    sold_pre2024 = ifelse(year <= 2023, TRUE, FALSE),
    sold_post2023 = ifelse(year > 2023, TRUE, FALSE),
    ) |> 
  ungroup()


res_sales <- res_sales |> 
  mutate(insfha_2018 = ifelse(pin %in% string_sfha_pins2018, 1, 0),
         insfha_2024 = ifelse(pin %in% string_sfha_pins2024, 1, 0),
         inprelimsfha = ifelse(pin %in% prelim_SFHA$PIN14, 1, 0))

res_sales <- res_sales |> 
  mutate(change_sfha = insfha_2024 - insfha_2018)

res_sales
```


```{r}
#| tbl-cap: "Residential PINs with multiple sales"
#| tbl-subcap:
#| - "6,594 distinct residential pins have been in an SFHA and sold multiple times"
#| - "465  distinct pins have either been added to or removed from an SFHA and sold multiple times."

res_sales |> 
  filter(sold_multi == TRUE & 
           (pin %in% string_sfha_pins2018 | 
              pin %in% string_sfha_pins2024) ) |> 
  distinct(pin)


res_sales |> 
  filter(sold_multi == TRUE & change_sfha !=0 ) |> 
  distinct(pin)
```


```{r, warning=FALSE, message=FALSE}
table(res_sales$insfha_2018)
table(res_sales$insfha_2024)
table(res_sales$change_sfha)
```


```{r, warning=FALSE, message=FALSE}
res_sales |> 
  group_by(sold_multi) |> 
    summarize(n=n(),
              distinct_pins = n_distinct(pin))

res_sales |> 
  group_by(times_sold) |> 
    summarize(distinct_pins = n_distinct(pin))

res_sales |>
  group_by(sold_pre2014, sold_btwn_20132023, sold_post2023) |> 
  summarize(n = n(), n_distinct = n_distinct(pin))

res_sales |>
  filter(times_sold < 10 & sale_price > 5000) |>
  group_by(sold_multi, 
         #  sold_pre2014, sold_btwn_20132023, sold_post2023, 
           insfha_2024, insfha_2018) |> 
  summarize(n_sales = n(), n_distinct_PIN = n_distinct(pin))
```










**Note that `sfha_pins` are PINs that have the SFHA indicator == 1 according to CCAO data and `fsf_5plus` are PINs that have a flood factor rating of 5 or higher**  

```{r}
#| label: sold-properties-infloodzones
#| layout-ncol: 2

res_sales <- res_sales |>
  mutate(ccao_sfha = ifelse(pin %in% sfha_pins, 1, 0), # according to CCAO dataset, not FEMA shapefiles
         in_ffs_4plus = ifelse(pin %in% fsf_4plus, 1, 0),
         in_ffs_5plus = ifelse(pin %in% fsf_5plus, 1, 0)
  )

pin_groups <- res_sales |>
  mutate(risk_change = case_when(
    ccao_sfha == 1 & insfha_2024 == 0 ~ "Removed from SFHA",
    insfha_2018 != insfha_2024 ~ "Changes SFHA - since 2018",
    insfha_2018 == 1 & insfha_2024 == 1 & ccao_sfha == 1 ~ "Always in SFHA",
    insfha_2018 == 0 & insfha_2024 == 0 ~ "Never in SFHA",
    (insfha_2018 == 1 | insfha_2024 == 1) & ccao_sfha == 0 ~ "LOMAs?",
    T ~ "Check me") )|>
  filter(sale_price > 5000) |>
  group_by(pin) |> 
  mutate(n = n(),
         ) |>
  filter(n() < 10) |>
  summarize(times_sold = ifelse(n() > 1, "Multi", "Once"),
           # years_sold = as.character(list(unique(year))),
            sold_post2023 = ifelse(any(year > 2022), 1, 0),  
           risk_change = first(risk_change),
           ccao_sfha = first(ccao_sfha),
           insfha_2018 = first(insfha_2018),
           insfha_2024 = first(insfha_2024),
           min_price = min(sale_price),
           max_price = max(sale_price)
            ) |>
  mutate(
    loma_difs = case_when(
      ccao_sfha == 1 & insfha_2018 == 1 ~ "In SFHA",
      ccao_sfha == 0 & (insfha_2018 ==1 | insfha_2024==1) ~ "Probably LOMAs",
      ccao_sfha == 0 & insfha_2018 == 0 ~ "Not SFHA",
      T ~ "Check Me"
    ) ,
      risk_type = case_when(
        loma_difs == "Probably LOMAs" ~ "Probably LOMAs",
        pin %in% sfha_pins & !pin %in% fsf_5plus ~ "In CCAO SFHA Only",
        pin %in% fsf_5plus & pin %in% sfha_pins ~ "SFHA & FSF Score 5+",
        pin %in% fsf_5plus & !pin %in% sfha_pins ~"FSF Score 5+ Only",
        T ~ "Low Risk"
      )  #,
    #  flooded = case_when(
    # ...   ~ "Reported Damage",
    # ...   ~ "Did not report Damage",
    # ...   ~ "Flooded Pre-Sale",
    # ...   ~ "Flooded Post-Sale"
    #  )
    
  )
  
table(pin_groups$risk_type, pin_groups$times_sold)
table(pin_groups$risk_type,  pin_groups$risk_change, pin_groups$times_sold)

```

```{r}
pin_groups |>
  group_by(times_sold, risk_type, risk_change,
         #  sold_pre2014, sold_btwn_20132023, 
        # sold_post2023, 
          # insfha_2024, insfha_2018
           ) |> 
  summarize(
            n_pins = n_distinct(pin))

pin_groups |>
  group_by(times_sold, risk_type,        
           # sold_post2023, 
           ) |> 
  summarize(
            n_pins = n_distinct(pin))
```

### Research Question 1 

```{r}
tbl_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Removed from SFHA") |>

  #filter(risk_change == "Removed from SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2020 & min(year) < 2019, "SFHA Change btwn sales", "SFHA not btwn sales"))|>
  group_by(year, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
tbl_R1

tbl_R1 |> ggplot(aes(x=year, y=n, color = sold_post2021)) + geom_line()

tbl_R1 |> ggplot(aes(x=year, y=median_price, color = sold_post2021)) + geom_line()


res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Removed from SFHA" | risk_change == "Always in SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "SFHA Change btwn sales", "SFHA Change not btwn sales"))|>
  group_by(year, sold_post2021, risk_change ) |> 
  summarize( n = n_distinct(pin), median_price = median(sale_price)) |>
  ggplot()+
  geom_line(aes(x=year, y = median_price/1000000, group = risk_change, color = risk_change)) + 
  geom_text(aes(x = 2016, y = 0.2, label = c(sum(n))) )+
  facet_wrap(~sold_post2021)

control_tbl2_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Always in SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "Sold b4&after 2021", "Not sold b4&after 2021"))|>
  group_by(sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price))

control_tbl2_R1


control_tbl_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "Sold b4&after 2021", "Not sold b4&after 2021"))|>
  group_by(sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price))

control_tbl_R1


```

### Research Question 2

```{r}
tbl_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "FSF Score 5+ Only" | risk_type == "SFHA & FSF Score 5+" | risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 

tbl_R2

control_tbl_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "In CCAO SFHA Only") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
control_tbl_R2


control_tbl2_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
control_tbl2_R2
```

### Research Question 3

> Need indicator for if property flooded. Which I do not cleanly have.

```{r}
#| label: tbl-SFHAparcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels in SFHAs that have been sold."

sfhasales <-  res_sales %>%
  filter(ccao_sfha == 1) %>%
  left_join(landblock_pins, by = c("year", "pin")) %>%
  mutate(parcel = str_sub(pin, 1, 10))

sfhasales %>% 
  filter(sale_price >5000) |>
  group_by(parcel, year, sale_document_num) %>%
  summarize(pincount = n(),
            sale_price = first(sale_price),
            sale_price_sum = sum(sale_price)) %>% 
  arrange(desc(parcel))

duplicates <- sfhasales |> janitor::get_dupes(pin, parcel, year, sale_price)
duplicates

sfhasales |> 
  filter(sale_price > 5000) |>
  group_by(pin, parcel, year, sale_price) |> 
  distinct(pin,year,sale_price, .keep_all = TRUE)
```


```{r}
#| label: tbl-SFHAparcels-soldtimes
#| tbl-cap-location: margin
#| tbl-cap: "Multisales SFHA PIN Sales: Number of times sold and count of years properties were sold in. Filtered for pins that were sold more than once."

sfhasales %>% 
  filter(sale_price>5000) |>
  group_by(pin) %>% 
  summarize(timessold=n(),
            distinct_years = n_distinct(year),
            max_price= max(sale_price),
            min_price = min(sale_price),
            class = max(class_1dig)) %>% 
  filter(timessold>1) %>% 
  arrange(desc(timessold))
```


```{r}
#| label: tbl-salesover5K
#| tbl-cap-location: margin
#| tbl-cap: "Sales of SFHA PINs over $5000 for properties in SFHA FEMA Zones. N = 18,157"

sfhasales %>% 
  filter(!is.na(sale_price) & sale_price > 5000) %>% 
  arrange(desc(num_parcels_sale), sale_document_num, pin )
```

```{r}
#| label: fig-pinsales-andAV
#| fig-cap: "PIN Sale Price and Assessed Values over time."
#| fig-subcap: 
#| - pin == 09163040191019
#| - pin == 05201210150000
#| - pin == 05201210150000
#| layout-ncol: 3


sfhasales %>% 
  filter(pin == "09163040191019") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "05201210150000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "09281140060000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)


```

```{r}
#| label: tbl-floodfactor-parcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels with Flood Factor Risk Rating >= 5  that have been sold. 206,304 PINs have sales prices above $5K and flood factor ratings."

floodsales <- sales %>% 
  filter(pin %in% sfha_pins) %>%
  left_join(landblock_pins, by = c("year", "pin", "class"))



#floodsales %>% filter(!is.na(sale_price))
floodsales %>% filter(#!is.na(sale_price) & 
                        sale_price > 5000)
# 206,304 sales for pins in flood factor high risk areas of 5 or higher
```



# SFHA PINs

There were `{r} sales |> filter(sale_price> 5000) |> filter(pin %in% string_sfha_pins2018) |> n_distinct()` sale observations for the properties that were in the SFHA (FEMA 100-year floodzone) according to the 2018 NFHL. 


## Average Sales Prices

Uses the CCAO indicator for if it was in a floodplain. 

```{r}
#| label: fig-saleprices-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average Sale Prices per year by Major Property Class.** Some years have very few sales and can be skewed by whatever property happens to be sold that year."
#| warning: false
#| message: false

sfhasales %>% 
  group_by(year, major_class) %>%
  summarize(sale_price = mean(sale_price, na.rm=TRUE)) %>%
  ggplot() +
  geom_line(aes(x=year, y = sale_price)) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg Sale Price for Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2024), name = ""  ) + 
  facet_wrap(~major_class, scales = "free"             )
```

```{r}
#| label: fig-saleprices-bySFHAtype
#| fig-cap-location: margin
#| fig-cap: "**Average Sale Prices per year by Major Property Class.**"
#| warning: false
#| message: false

avg_sales_peryear = res_sales %>% 
  mutate(ccao_sfha =as.character(ccao_sfha)) |>
  group_by(year, ccao_sfha) %>%
  summarize(sale_count = n()) |>
  ungroup()|> 
  group_by(ccao_sfha) |>
  summarize(average_salecount = mean(sale_count))


res_sales %>% 
  mutate(ccao_sfha = as.factor(ccao_sfha)) |>
  group_by(year, ccao_sfha) %>%
  summarize(sale_price = mean(sale_price, na.rm=TRUE)) %>%
  ggplot() +
  geom_line(aes(x=year, y = sale_price, color = ccao_sfha)) + 
  theme_classic() + 
  labs(title = "Avg Sale Price for Class 2 Properties") +
  scale_y_continuous(name = "$", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2020, 2024), name = ""  )
```

 On average, there are around `{r} round(avg_sales_peryear$average_salecount[[1]])` sales for properties outside of an SFHA and around `{r} round(avg_sales_peryear$average_salecount[[2]])`
 
```{r}
#| label: tbl-SFHAsales-byclass
#| tbl-cap: "Number of SFHA sales per year by major class."

sfhasales %>% 
  group_by(year, major_class) %>%
  summarize(NumberSold=n()) %>%
  pivot_wider(names_from = major_class, values_from = NumberSold)
```


```{r}
#| label: fig-FMV-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV per year by Major Property Class for properties in FEMA SFHAs.** The dashed line is the mailed AV and solid line is final AV"
#| warning: false
#| message: false
#| 
landblock_pins %>% 
  filter(pin %in% sfha_pins & class_1dig %in% c(2, 5)) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=TRUE)) %>%
  ggplot() +
      geom_line(aes(x=year, y = fmv_clerk)) + 
    geom_point(aes(x=year, y = fmv_clerk)) + 

    geom_line(aes(x=year, y = fmv_mailed), linetype = 2 ) +
   # geom_line(aes(x=year, y = fmv_board) ) +
   # geom_point(aes(x=year, y = fmv_board)) +
    geom_point(aes(x=year, y = fmv_mailed)) +
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2024), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```


```{r}
#| label: fig-FMV-bymajorclass-comparison
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV per year by Major Property Class for properties:  FEMA SFHA Properties vs non-SFHA Properties.** Compares all PINs located within a block of land (first 7 digits of PIN). Includes land blocks that have at least one PIN in an SFHA. Assumption is that PINs in close proximity are aware of nearby properties flooding. Uses all PINs located in the same land block if the land block contains at least one property in a floodplain."
#| warning: false
#| message: false

landblock_pins %>% 
  mutate(sfha_flag = as.factor(ifelse(pin %in% sfha_pins, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class, sfha_flag) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=TRUE),

            pincount = n()) %>%
  filter(major_class!= 0) %>%
  ggplot() +
    geom_line(aes(x=year, y = fmv_clerk, color = sfha_flag)) + 
    geom_point(aes(x=year, y = fmv_clerk, color = sfha_flag)) + 

 # geom_line(aes(x=year, y = fmv_mailed, color = sfha_flag)) + 
  #  geom_line(aes(x=year, y = fmv_board, color = sfha_flag), linetype = 2 ) + 
  #  geom_point(aes(x=year, y = fmv_board, color = sfha_flag)) + 
   # geom_line(aes(x=year, y = fmv_mailed, color = sfha_flag), linetype = sfha_flag ) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2024), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```

## FMV and Sales

```{r}
#| label: fig-FMV-andsales
#| fig-cap-location: margin
#| fig-cap: "**Fair Market Value and Sales Price. Red dots are for average Sale Price. Note that some property types do not have many sales (e.g. major class 3, 4, 7, 9. Pretty much anything except major class 2)"
#| warning: false
#| message: false

landblock_pins %>% 
  left_join(sales %>% filter(sale_price > 5000) %>% select(-class), by = c("year", "pin")) %>%
  mutate(ff_flag = as.factor(ifelse(pin %in% fsf_5plus, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=T),
            sales = mean(sale_price, na.rm=T),
            pincount = n()) %>%
  filter(major_class != 0) %>%
  ggplot() + 
    geom_line(aes(x=year, y = fmv_clerk)) + 
    geom_point(aes(x=year, y = fmv_clerk)) + 
    geom_line(aes(x=year, y = sales, color="red")) + 
    geom_point(aes(x=year, y = sales, color="red")) +
  # geom_line(aes(x=year, y = fmv_mailed, color = ff_flag)) + 
  #   geom_line(aes(x=year, y = fmv_board, color = ff_flag), linetype = 2 ) + 
  #   geom_point(aes(x=year, y = fmv_board, color = ff_flag)) + 
  theme_classic() + 
  scale_y_continuous(name = "Dollars", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2024), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```



# Assessed Value

## Flood Factor Score 5+ PINs and Assessed Value

```{r}
#| label: fig-FMV-bymajorclass-floodfactorcomparison
#| fig-cap-location: margin
#| fig-cap: "**Average  FMV by Major Property Class & Flood Factor Risk: For Properties with a rating of 5 or higher designating them as high risk**"
#| warning: false
#| message: false

landblock_pins %>% 
  mutate(ff_flag = as.factor(ifelse(pin %in% fsf_5plus, 1, 0))) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class, ff_flag) %>%
  summarize(fmv_mailed = mean(fmv_mailed, na.rm=TRUE),
            fmv_board = mean(fmv_board, na.rm=TRUE),
            fmv_clerk = mean(fmv_clerk, na.rm=T),
            pincount = n()) %>%
  filter(#pincount > 60 & 
           major_class != 0) %>%
  ggplot() + 
      geom_line(aes(x=year, y = fmv_clerk, color = ff_flag)) + 
    geom_point(aes(x=year, y = fmv_clerk, color = ff_flag)) + 

  # geom_line(aes(x=year, y = fmv_mailed, color = ff_flag)) + 
  #   geom_line(aes(x=year, y = fmv_board, color = ff_flag), linetype = 2 ) + 
  #   geom_point(aes(x=year, y = fmv_board, color = ff_flag)) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg FMV by Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006, 2015, 2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```

```{r}
#| label: fig-AV-bymajorclass
#| fig-cap-location: margin
#| fig-cap: "**Average Assessed Value per year by Major Property Class for properties within FEMA SFHAs.** Some major classes have very few properties located in SFHAs so sudden changes in AV for one or two properties can skew the graphs very easily."
#| warning: false
#| message: false
#| 
landblock_pins %>% 
  filter(pin %in% sfha_pins) %>%
  mutate(major_class = str_sub(class, 1,1)) %>%
  group_by(year, major_class) %>%
  summarize(av_mailed = mean(av_mailed, na.rm=TRUE),
            av_board = mean(av_board, na.rm=TRUE)) %>%
  ggplot() +
  geom_line(aes(x=year, y = av_mailed), linetype = 2 ) + 
    geom_line(aes(x=year, y = av_board) ) + 
    geom_point(aes(x=year, y = av_board)) + 
    geom_line(aes(x=year, y = av_mailed), linetype = 2 ) + 
  theme_classic() + 
  scale_y_continuous(name = "Avg Assessed Value for Major Class", labels = scales::dollar ) +
  scale_x_continuous(breaks = c(2006,  2015,  2023), name = ""  ) + 
  facet_wrap(~major_class, scales = "free" )
```


# Lived Experience PINs

## Flood Event 2023 - Disaster Declarations / Lived Experience

Cicero and Berwyn had lots of damage during DR 4728. Cicero had 25,836 housing units in 2020 and over 6000 of them applied and were granted IHP funds. 


Dolton and Calumet City were damaged during DR 4749.

```{r}
ptax245 <- readxl::read_xlsx("inputs/PTAX-245_data.xlsx")

ptax245 <- ptax245 %>% 
  mutate(
    pin = str_remove_all(pin, "-"),
    keypin = as.character(KeyPIN)) %>%
  mutate(keypin_concat = as.character(keypin),
         keypin_concat = str_remove_all(keypin_concat, "-"),
         keypin_concat = str_pad(keypin_concat, 14, "left", pad = "0"),
         major_class = str_sub(Class, 1, 1),
         parcel = str_sub(pin, 1, 10),
         block = str_sub(pin, 1, 7),
         year = 2023,
         appealed = 1 ) %>%
  select(pin, keypin_concat, parcel, block, Class, major_class, everything()) %>% 
  distinct() %>% 
  arrange(pin)
ptax_pins <- ptax245 |> select(pin) |> pull()

res_sales <- res_sales |> mutate(flood2023 = ifelse(pin %in% ptax245, 1, 0))

```

245 PINs in Cicero and 45 PINs in Berwyn appealed their property tax (plus 2 in Oak Park, 2 in River Forest, and 1 in Riverside).

```{r}

res_sales %>% filter(pin %in% ptax245)

```


90,000 Post Disaster Individual Assistance Grants between the two disasters in 2023. 
Only a few million in NFIP claims were paid out from these flood events but over $300 million in IHP fund were distributed. 

- Part of this is because the areas hit hardest (Cicero and Berwyn have no SFHAs and no properties are required to have flood insurance. In general, not many properties in SFHAs in Cook County, especially where these flood events occurred. Makes it unlikely that residents have flood insurance and they can't file flood insurance claims if they don't have flood insurance. )

Cook County also had disaster declarations in 1993, 1996, 1997, 2007, 2009, 2010, 2013, and 2023X2.

