---
title: "Cook County - Parcel Mapping"
format: html
---

## Mapping Parcels

Example Link: [<https://ccao-data.github.io/ptaxsim/articles/mapping.html>]

At the 10 digit pin number, there are 23,332 pins.

-   Last 4 digits of the 14 digit pin are for indicating the unit number within a building. Single family homes with only one tax payer end with 0000; condos with more than one unit end with additional identifiers. The 10-digit pin corresponds to a geographic location of the building.

Pin geometries for pins with flood zone SFHA status.

> make smaller maps. Either by Triad or township or something else smaller than Cook County.

```{r}
#install.packages("prettymapr")
library(prettymapr)

flood_pin10s <- flood_pins_ptax %>% 
  mutate(pin10 = str_sub(pin, 1, 10)) %>%
  select(pin10) %>% distinct(pin10)

flood_pin10s <- as.character(flood_pin10s$pin10)

flood_pins_geo <- lookup_pin10_geometry(year = 2021, 
                                        pin10 = flood_pin10s) %>%
  st_as_sf(wkt = "geometry", crs = 4326)

flood_pins_geo <- flood_pins_ptax %>% 
  filter(year == 2021) %>%
  right_join(flood_pins_geo, by = c("parcel_num" = "pin10"))

table(flood_pins_geo$major_class)

twnshp_codes$township_code <- as.character(twnshp_codes$township_code)

flood_pins_geo <- flood_pins_geo %>% 
  left_join(twnshp_codes, by =c("township_name" = "township_name"))

table(flood_pins_geo$township_name)
table(flood_pins_geo$triad_code)

table(flood_pins_geo$township)



# add border for cook County
cook_border <- read_sf("https://gis.cookcountyil.gov/traditional/rest/services/plss/MapServer/1/query?outFields=*&where=1%3D1&f=geojson")
```

```{r eval = FALSE, include = FALSE}
flood_pins_map_all <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo,
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
 geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom"
  )

flood_pins_map_all
```

```{r eval=FALSE, code.fold=TRUE}
top5 <- c("05")
flood_pins_map_north <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo %>% filter(township %in% top5),
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
#  geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom"
  ) + facet_wrap(~township, # scales = "free",
                # nrow = 5,
                 shrink = FALSE)

flood_pins_map_north
```

#### New Trier

```{r eval=FALSE, code.fold = TRUE}


flood_pins_geo %>% # filter(year == 2021) %>%
  filter(township == 23) %>% 
  group_by(major_class_fct) %>%
  summarize(pins_per_year = n(),
            av = sum(av_mailed)) %>%
  mutate(av_per_pin = av/pins_per_year) %>%  ggplot() +
  geom_line(aes(x=year, y=av_per_pin, color = major_class_fct))


grouped_bills %>% filter(township == 10) %>% 
  group_by(year, major_class_fct) %>%
  summarize(pins_per_year = n(),
            av = sum(av),
            eav = sum(eav),
            eav_per_pin = eav/pins_per_year,
            av_per_pin = av/pins_per_year) %>%  ggplot() +
  geom_line(aes(x=year, y=av_per_pin, color = major_class_fct)) +
  geom_vline(aes(xintercept= (2009))) +
  geom_vline(aes(xintercept= (2012))) +
  geom_vline(aes(xintercept= (2015))) +
    geom_vline(aes(xintercept= (2018)))

  
```

New Trier had corrected bills mailed out in 2019 when the assessor began using floodplain data. New Trier is township #23 in Cook County township codes. New Trier is in the North Triad, up by Glencoe.

> Pull first round assessments and then corrected assessments!

```{r NewTrier, eval=FALSE}
townships <- c("08")

grouped_bills %>% 
  filter(township %in% c("23")) %>% 
  group_by(year, major_class_fct) %>%
  summarize(pins_per_year = n(),
            av = sum(av),
            eav = sum(eav),
            eav_per_pin = eav/pins_per_year,
            av_per_pin = av/pins_per_year) %>%  ggplot() +
  geom_line(aes(x=year, y=av_per_pin, color = major_class_fct)) +
  geom_vline(aes(xintercept= (2019))) +
  labs(title = "New Trier assessments",
       subtitle = "New information in 2019")

flood_pins_map_north <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo %>% filter(township %in% townships),
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
 # geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom" 
  ) + labs(title = "New Trier Parcels in SFHA")

flood_pins_map_north
```

```{r eval=FALSE}
townships <- c("28", "29")


flood_pins_map_south <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo %>% filter(township %in% townships),
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
 # geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom"
  )
  

flood_pins_map_south

grouped_bills %>% filter(township %in% c("28", "29")) %>% 
  group_by(year, major_class_fct) %>%
  summarize(pins_per_year = n(),
            av = sum(av),
            eav = sum(eav),
            eav_per_pin = eav/pins_per_year,
            av_per_pin = av/pins_per_year) %>%  ggplot() +
  geom_line(aes(x=year, y=av_per_pin, color = major_class_fct)) +
  geom_vline(aes(xintercept= (2010))) +
  geom_vline(aes(xintercept= (2013))) +
  geom_vline(aes(xintercept= (2016))) +
    geom_vline(aes(xintercept= (2019)))

```

```{r Cicero, eval=FALSE}
townships <- c("15")


flood_pins_map_south <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo %>% filter(township %in% townships),
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
 # geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom"
  )
  

flood_pins_map_south

grouped_bills %>% filter(township %in% c("15")) %>% 
  group_by(year, major_class_fct) %>%
  summarize(pins_per_year = n(),
            av = sum(av),
            eav = sum(eav),
            eav_per_pin = eav/pins_per_year,
            av_per_pin = av/pins_per_year) %>%  ggplot() +
  geom_line(aes(x=year, y=av_per_pin, color = major_class_fct)) +
  geom_vline(aes(xintercept= (2010))) +
  geom_vline(aes(xintercept= (2013))) +
  geom_vline(aes(xintercept= (2016))) +
    geom_vline(aes(xintercept= (2019)))
```

```{r eval=FALSE}
flood_pins_map_chi <- ggplot() +
  annotation_map_tile(type = "cartolight", zoomin = -1) +
  geom_sf(
    data = flood_pins_geo,
    aes(fill = major_class_fct),
    alpha = 0.5,
    linewidth = 0.1
  ) +
  geom_sf(data = cook_border, fill = "transparent", linewidth = 1) +
  annotation_scale(location = "br") +
  scale_fill_manual(
    name = "",
    values = c(
      "0 & 1 - Vacant and Exempt" = "#984ea3",
      "2 - Residential" = "#e41a1c",
      "3 & 5 - Commercial" = "#377eb8",
      "6, 7, 8 - Incentive" = "#4daf4a"
    )
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme_void() +
  theme(
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 10),
    legend.key.size = unit(18, "points"),
    legend.position = "bottom"
  )

```

