---
title: "Make Panel Data"
format: 
  html:
    toc: true
---

> The single_fam csv is the "easy" PINs -- properties that were always residential and existed all years. 

It was created in `create_panel_data.qmd`. 

[X] TO DO: Change pre_date of 9999-09-08 to beginning of study period


- Start with all PINs that were ever residential for at least 1 year
  - `data/raw/residential_pins_ever.csv` from `pull_distinct_res_PINs.R`
  - made from PTAXSIM database (from CCAO) 
  - has Assessed Values (Initial, Board of Review, Clerk/Final)
  - has PIN class
  
- FIRM Update Dates
  - [X] Join FIRM data to parcels      
    - `parcels_wFIRMS.csv` from `pull_parcel_sfs.R`. Uses XY coordinates for parcel centroids from ptaxsim.db and intersects with 2024 FIRM polygons.
    - CSV version of 2024 FIRMs in `S_FIRM_PAN.csv`
  - [ ] **Need to manually add preliminary dates**  -- Partially done  
  - [ ] Create variable for each pin-year: 
    - [ ] if year < pre_date, then preliminary update == 0
    - [ ] if year >= pre_date, then preliminary update == 1
  - [ ] do same for effective date (when financial implications become active for mortgage holders)  


- [ ] Left join flood factor score by PIN. It does not change with time.
  - Flood Factor Score from Assessor's parcel universe API
    - csv: `floodfactor_scores.csv`

- [ ] Sale Date and Sale Price   
  - Join by PIN and year
  - csv: `./data/raw/Assessor_Parcel_Sales_20250105.csv`




```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)

```

> Coding note: sale_price is winsorized by grouping the year & major class (technically the 1st digit of the class code). Check that this is how you want it to be winsorized. 

> Drop those variables earlier! before even making the singlefamily_assessed_values file!

```{r}
pins <- read_csv("./data/processed/singlefamily_assessed_values.csv") |> 
  select(-c(`building type`:landuse_change, improvement_ind))
```


ff_score = 1-10, from parcel universe (CCAO obtained in 2019)

> when grouping by pin, if there were duplicates in the data before comparing years in the dataset to the timespan, it would not be an accurate count of years.


```{r}
table(pins$class[pins$year==2023])

```


## Add in SFHA and LOMR indicators


sfha_ind made from these files

- lomrs <- read_csv("./data/processed/LOMR_pins_2024.csv")  

- sfha_2018 <- read_csv("./data/processed/parcels_sfha_2018.csv")  

- sfha_2024 <- read_csv("./data/processed/parcels_sfha_2024.csv")  

- buyouts <- read_csv("./data/processed/BuyoutPoints_Statewide.xlsx")  


```{r}

sfha_ind <- read_csv("./data/processed/sfha_indicator_pins.csv")
sfha_ind <- sfha_ind |> select(pin, sfha2018:lomr2024)

pins <- pins |> full_join(sfha_ind, by ="pin")
```


```{r}
table(pins$class[pins$year==2023])
```







```{r}
pins <- pins |>
  mutate(class = as.character(class),
         lomr2024 = as.character(lomr2024),
         sfha2024 = as.character(sfha2024)) 

firms <- read_csv("./data/processed/parcels_wFIRMS.csv")

lomrs <- read_csv("./data/processed/lomr_pins_2024.csv") |>
  rename(lomr_eff = EFF_DAT,
         lomr_dfirm_id = DFIRM_ID) |>
  mutate(lomr_eff = as_date(lomr_eff))

pins <- pins |> 
  mutate(pin10 = str_sub(pin, 1, 10) ) |>
  left_join(firms, by = "pin10")

```


```{r}
pins <- pins |>
  mutate(
    prelim_date = ifelse(PRE_DATE == "9999-09-09" | is.na(PRE_DATE), "2005-01-01", PRE_DATE),
    
    ccao_sfha = ifelse(sfha2024 == 1 & year >= 2021, "SFHA", "Not SFHA"),
    ccao_sfha = ifelse(is.na(ccao_sfha), "Not SFHA", ccao_sfha),
    
    # the flood zones that existed in the 2018 state NFHL were last updated in 2008. sfha2018 is the default SFHA status for the observations, then lomrs and future updates will be incorporated
    in_eff_sfha = ifelse(sfha2018 == 1, "In SFHA", "Not in SFHA"),
    
    in_eff_sfha = ifelse(sfha2024 == 1 & year >= year(EFF_DATE), "In SFHA", 
                         ifelse(year >= year(EFF_DATE) & sfha2024 == 0, "Not in SFHA", in_eff_sfha)),
    
    in_eff_sfha = ifelse((sfha2018 == 0 & sfha2024 == 0 ) | (is.na(sfha2018) & is.na(sfha2024)) , "Not in SFHA", in_eff_sfha))

table(pins$year, pins$in_eff_sfha)


pins <- pins |>
  left_join(lomrs, by = c("pin")) |>
  mutate(
    in_lomr = ifelse(year >= year(lomr_eff) & !is.na(LOMR_ID), "In LOMR", "Not in LOMR") ,
    in_prelim_sfha = ifelse(year >= as_date(prelim_date), "1", "0"),
      ) |>
  mutate(in_eff_sfha = ifelse(in_eff_sfha == 1 & in_lomr == 1, in_eff_sfha == 0, in_eff_sfha))

rm(lomrs)
rm(firms)

table(pins$year, pins$in_eff_sfha)

table(pins$year, pins$in_lomr)
```


```{r}
table(pins$year, pins$ccao_sfha)

```

> Being in an effective SFHA shouldn't be super significant because it wasn't used by the assessor until 2021 or 2020 or something around that time. It should be a better predictor for the sales data. 


> probably should add triad to model to deal with reassessment cycles or shift it to that the reassessment cycles line up? 


```{r}
naive_ols <- lm(av_clerk ~ ccao_sfha,
                data = pins |> filter(year==2023))

naive_ols
```

```{r}
naive_ols <- lm(av_clerk ~ class + lomr2024 + sfha2024,
                data = pins |> filter(year==2023))

naive_ols
```

```{r}
naive_ols <- lm(av_clerk ~ lomr2024 + sfha2024,
                data = pins |> filter(year==2023))

naive_ols
```


```{r}
naive_ols <- lm(av_clerk ~ lomr2024 + sfha2024,
                data = pins |> filter(year==2019))

naive_ols
```

# Fixed Effects

```{r}
library(fixest)
paper_models <- list(

    "I" = 
    
    feols(av_clerk ~ in_eff_sfha
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = pins)
    
    )
paper_models
```


```{r}
paper_models <- list(

    "I" = 
    
    feols(av_clerk ~ in_eff_sfha + in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = pins)
    
    )
paper_models
```

```{r}
paper_models <- list(

    "I" = 
    
    feols(av_clerk ~ class + ccao_sfha
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = pins)
    
    )
paper_models
```


```{r}
paper_models <- list(

    "I" = 
    
    feols(av_clerk ~ class + ccao_sfha + in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = pins)
    
    )
paper_models
```
