---
title: "Make Panel Data"
format: 
  html:
    toc: true
---

> The single_fam csv is the "easy" PINs -- properties that were always residential and existed all years. 

It was created in `create_panel_data.qmd`. 

[ ] TO DO: Change pre_date of 9999-09-08 to beginning of study period


- Start with all PINs that were ever residential for at least 1 year
  - `data/raw/residential_pins_ever.csv` from `pull_distinct_res_PINs.R`
  - made from PTAXSIM database (from CCAO) 
  - has Assessed Values (Initial, Board of Review, Clerk/Final)
  - has PIN class
  
- FIRM Update Dates
  - [X] Join FIRM data to parcels      
    - `parcels_wFIRMS.csv` from `pull_parcel_sfs.R`. Uses XY coordinates for parcel centroids from ptaxsim.db and intersects with 2024 FIRM polygons.
    - CSV version of 2024 FIRMs in `S_FIRM_PAN.csv`
  - [ ] **Need to manually add preliminary dates**  -- Partially done  
  - [ ] Create variable for each pin-year: 
    - [ ] if year < pre_date, then preliminary update == 0
    - [ ] if year >= pre_date, then preliminary update == 1
  - [ ] do same for effective date (when financial implications become active for mortgage holders)  


- [ ] Left join flood factor score by PIN. It does not change with time.
  - Flood Factor Score from Assessor's parcel universe API
    - csv: `floodfactor_scores.csv`

- [ ] Sale Date and Sale Price   
  - Join by PIN and year
  - csv: `./data/raw/Assessor_Parcel_Sales_20250105.csv`




```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)

```

> Coding note: sale_price is winsorized by grouping the year & major class (technically the 1st digit of the class code). Check that this is how you want it to be winsorized. 

```{r}
pins <- read_csv("./data/processed/singlefamily_assessed_values.csv") |> 
  select(-c(`building type`:landuse_change))


```


ff_score = 1-10, from parcel universe (CCAO obtained in 2019)

> when grouping by pin, if there were duplicates in the data before comparing years in the dataset to the timespan, it would not be an accurate count of years.


```{r}
table(pins$class[pins$year==2023])

```


## Add in SFHA and LOMR indicators


sfha_ind made from these files

- lomrs <- read_csv("./data/processed/LOMR_pins_2024.csv")  

- sfha_2018 <- read_csv("./data/processed/parcels_sfha_2018.csv")  

- sfha_2024 <- read_csv("./data/processed/parcels_sfha_2024.csv")  

- buyouts <- read_csv("./data/processed/BuyoutPoints_Statewide.xlsx")  


```{r}

sfha_ind <- read_csv("./data/processed/sfha_indicator_pins.csv")
sfha_ind <- sfha_ind |> select(pin, sfha2018:lomr2024)

pins <- pins |> full_join(sfha_ind, by ="pin")
```


```{r}
table(pins$class[pins$year==2023])
```


```{r}
table(pins$lomr2024[pins$year==2023])
table(pins$lomr2018[pins$year==2023])
```

```{r}
table(pins$sfha2018[pins$year==2023])
table(pins$sfha2024[pins$year==2023])

```


- improvement_ind is all 0's -- drop it?

```{r}
# all 0's, drop variable?
table(pins$improvement_ind[pins$year==2023])

table(pins$prelimsfha[pins$year==2023])

```


```{r}
pins <- pins |>
  mutate(class = as.character(class),
         lomr2024 = as.character(lomr2024),
         sfha2024 = as.character(sfha2024))

naive_ols <- lm(av_clerk ~ class,
                data = pins |> filter(year==2023))

naive_ols
```

```{r}
naive_ols <- lm(av_clerk ~ class + lomr2024 + sfha2024,
                data = pins |> filter(year==2023))

naive_ols
```

```{r}
naive_ols <- lm(av_clerk ~ lomr2024 + sfha2024,
                data = pins |> filter(year==2023))

naive_ols

naive_ols <- lm(av_clerk ~ lomr2024 + sfha2024,
                data = pins |> filter(year==2019))

naive_ols
```

```{r eval=FALSE}
library(fixest)

models <- list(
  "Project-Year FE" = feols(fmv_growth_2011_w ~  land_use2*incent_prop2 | actual_keypin + year, panel.id = c("actual_keypin", "year"),                                      vcov = "newey_west",

                            data = proj_panel),
  
  "Project, Year & Muni FE" = feols(fmv_growth_2011_w ~ land_use2*incent_prop2  | actual_keypin + clean_name + year, 
                                    vcov = "newey_west",
                                          panel.id = c("actual_keypin", "year"), data = proj_panel)
)


modelsummary::modelsummary(model = models, output = "flextable",
                           stars = TRUE,
                           gof_omit = "AIC|BIC")
```

