---
title: "Q2 Figures and Tables"
subtitle: "Impact of visible flood factor scores on sale price"
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 3
execute:
  echo: false
  warning: false
  message: false
  error: true
---

```{r setup}
library(tidyverse)
library(modelsummary)
library(gt)
library(DT)
library(fixest)
library(did)  

options(scipen = 999)

out_dir <- "outputs/q2_marginaleffects"
table_dir <- file.path(out_dir, "tables")
me_dir <- file.path(out_dir, "marginaleffects")
etwfe_dir <- file.path(out_dir, "etwfe")
diagnostics_dir <- file.path(out_dir, "diagnostics")

# good way to make sure files exist  before running but also kind of unnecessary 
# required_files <- c(
#   file.path(out_dir, "bldg_sfha_q2_dissertation_prepped.rds"),
#   file.path(out_dir, "basic_twfe_effective_table.rds"),
#   file.path(out_dir, "basic_twfe_prelim_table.rds"),
#   file.path(out_dir, "basic_twfe_highff_prelim_table.rds"),
#   file.path(etwfe_dir, "etwfe_base_table.rds"),
#   file.path(etwfe_dir, "etwfe_triad_table.rds"),
#   file.path(out_dir, "q2_main_table.rds"),
#   file.path(out_dir, "highff_post_table.rds"),
#   file.path(me_dir, "q2_main_marginaleffects_list.rds"),
#   file.path(out_dir, "robust_prelim_high_ff_table.rds"),
#   file.path(out_dir, "robust_prelim_highff_post_table.rds")
# )
# 
# missing_files <- required_files[!file.exists(required_files)]
# 
# if (length(missing_files) > 0) {
#   stop(
#     "These saved outputs are missing. Run source('scripts/q2_dissertation_run_all.R') from the project root first:\n",
#     paste(missing_files, collapse = "\n")
#   )
# }

# ========================================================
# LOAD DATA SUMMARIES / MODEL TABLES
# ========================================================

bldg_sfha <- readRDS(
  file.path(out_dir, "bldg_sfha_q2_dissertation_prepped.rds")
)

groups_prelim_long <- readRDS(
  file.path(out_dir, "groups_prelim_long.rds")
)

basic_twfe_effective_table <- readRDS(
  file.path(out_dir, "basic_twfe_effective_table.rds")
)

basic_twfe_prelim_table <- readRDS(
  file.path(out_dir, "basic_twfe_prelim_table.rds")
)

basic_twfe_highff_prelim_table <- readRDS(
  file.path(out_dir, "basic_twfe_highff_prelim_table.rds")
)

etwfe_base_table <- readRDS(
  file.path(etwfe_dir, "etwfe_base_table.rds")
)

etwfe_triad_table <- readRDS(
  file.path(etwfe_dir, "etwfe_triad_table.rds")
)

q2_main_table <- readRDS(
  file.path(out_dir, "q2_main_table.rds")
)

highff_post_table <- readRDS(
  file.path(out_dir, "highff_post_table.rds")
)

robust_prelim_high_ff_table <- readRDS(
  file.path(out_dir, "robust_prelim_high_ff_table.rds")
)

robust_prelim_highff_post_table <- readRDS(
  file.path(out_dir, "robust_prelim_highff_post_table.rds")
)

# ========================================================
# LOAD MARGINAL EFFECTS OUTPUTS
# ========================================================

main_me <- readRDS(
  file.path(me_dir, "q2_main_marginaleffects_list.rds")
)
me_way_event_sequential_simp <- main_me$me_way_event_sequential_simp
me_way_event_ff_sfha <- main_me$me_way_event_ff_sfha
me_way_event_sequential <- main_me$me_way_event_sequential
me_event_by_high_ff <- main_me$me_event_by_high_ff
me_change_type_sequential <- main_me$me_change_type_sequential
me_event_by_change_type <- main_me$me_event_by_change_type
me_never_sfha_event <- main_me$me_never_sfha_event
me_never_prelim_event_by_triad <- main_me$me_never_prelim_event_by_triad
me_all_effective_grid <- main_me$me_all_effective_grid
me_high_ff_post_by_change_type <- main_me$me_high_ff_post_by_change_type
me_highff_post_by_change_type <- main_me$me_highff_post_by_change_type
hyp_highff_post_by_change_type <- main_me$hyp_highff_post_by_change_type
me_highff_post_triad_by_change_type <- main_me$me_highff_post_triad_by_change_type
hyp_highff_post_triad_by_change_type <- main_me$hyp_highff_post_triad_by_change_type
me_highff_post_partial_by_change_type <- main_me$me_highff_post_partial_by_change_type
me_highff_post_grid_by_change_type_triad <- main_me$me_highff_post_grid_by_change_type_triad

# ========================================================
# LOAD DIAGNOSTICS
# ========================================================

read_diag <- function(file_stem) {
  path <- file.path(diagnostics_dir, paste0(file_stem, ".rds"))
  if (file.exists(path)) readRDS(path) else tibble()
}

dropped_terms_basic_twfe_effective <- read_diag("dropped_terms_basic_twfe_effective")
dropped_terms_basic_twfe_prelim <- read_diag("dropped_terms_basic_twfe_prelim")
dropped_terms_basic_twfe_highff_prelim <- read_diag("dropped_terms_basic_twfe_highff_prelim")
dropped_terms_q2_main <- read_diag("dropped_terms_q2_main")
dropped_terms_highff_post <- read_diag("dropped_terms_highff_post")
dropped_terms_robust_prelim_high_ff <- read_diag("dropped_terms_robust_prelim_high_ff")
dropped_terms_robust_prelim_highff_post <- read_diag("dropped_terms_robust_prelim_highff_post")

fmt_me <- function(x) {
  x |>
    as.data.frame() |>
    select(any_of(c(
      "term", "contrast", "change_type", "change_type_prelim", "Triad",
      "high_ff_score", "highff_post", "event", "estimate", "std.error",
      "conf.low", "conf.high", "p.value"
    ))) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |>
    modelsummary::datasummary_df(output = "gt")
}
```


# Combined Indicator & Preliminary SFHA Status

::: {.panel-tabset}

## Naive/Combinded Indicator Model

```{r basic-highff-prelim}
basic_twfe_highff_prelim_table
```

## HighFF Post Model Table

```{r highff-post-table}
highff_post_table
```


## HighFF Post by Change Type

```
me_highff_post_by_change_type <- avg_comparisons(
  highff_post_models[["Change Type × HighFF Post"]],
  variables = "highff_post",
  by = "change_type"
)
```

```{r highff-post-by-change-type}
fmt_me(me_highff_post_by_change_type)
```

## Hypothesis Test: HighFF Post by Change Type

```
hyp_highff_post_by_change_type <- avg_comparisons(
  highff_post_models[["Change Type × HighFF Post"]],
  variables = "highff_post",
  by = "change_type",
  hypothesis = "b1=b2"
)
```

```{r hyp-highff-post-by-change-type}
fmt_me(hyp_highff_post_by_change_type)
```

## HighFF Post × Triad by Change Type

```
me_highff_post_triad_by_change_type <- avg_comparisons(
  highff_post_models[["Change Type × HighFF Post × Triad"]],
  variables = "highff_post",
  by = "change_type"
)
```

```{r highff-post-triad-by-change-type}
fmt_me(me_highff_post_triad_by_change_type)
```

## Hypothesis Test: HighFF Post × Triad by Change Type

```
hyp_highff_post_triad_by_change_type <- avg_comparisons(
  highff_post_models[["Change Type × HighFF Post × Triad"]],
  variables = "highff_post",
  by = "change_type",
  hypothesis = "b1=b2"
)
```


```{r hyp-highff-post-triad-by-change-type}
fmt_me(hyp_highff_post_triad_by_change_type)
```

## Partially Interacted HighFF Post Model

```
me_highff_post_partial_by_change_type <- avg_comparisons(
  highff_post_models[["Partially interacted"]],
  variables = "highff_post",
  by = "change_type"
)
```

```{r highff-post-partial-by-change-type}
fmt_me(me_highff_post_partial_by_change_type)
```

## HighFF Post Grid by Change Type and Triad

```
me_highff_post_grid_by_change_type_triad <- comparisons(
  highff_post_models[["Change Type × HighFF Post × Triad"]],
  variables = "highff_post",
  newdata = datagrid(
    change_type = c("Never SFHA", "Always SFHA", "Changes SFHA"),
    Triad = c("South", "North", "City")
  ),
  vcov = ~pin10
)
```

```{r highff-post-grid-change-type-triad}
fmt_me(me_highff_post_grid_by_change_type_triad)
```

:::


# Separated Timing and Underlying Risk: Base Models

This file now loads saved model objects, tables, and marginal effects from scripts rather than estimating the models while rendering the Quarto document. The heavy computations are created by the scripts in the `scripts/` folder and saved under `outputs/q2_marginaleffects/`.

`event == TRUE` for all sales that occurred after First Street released its flood risk data. `high_ff_score == TRUE` for properties with a Flood Factor score of 5 or higher.


::: {.panel-tabset}

## Using Effective Map Status

```{r basic-effective}
basic_twfe_effective_table
```

## Using Preliminary Map Status

```{r basic-prelim}
basic_twfe_prelim_table
```

:::

# Appendic C and model behind marginal effects below

```{r q2-main-table}
q2_main_table
```

# Main Marginal Effects

::: {.panel-tabset}

## Overall Post-Release Effect from Fully Interacted Model

Not what I want.

```
me_way_event_sequential <- avg_comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = list(event = c(FALSE, TRUE))
)  # 0.0403
```

```{r}
fmt_me(me_way_event_sequential)
```

## Post-Release Effect by High Flood Factor Status

What I want.

```
me_event_by_high_ff <- avg_comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = "event",
  by = "high_ff_score"
)
```

```{r}
fmt_me(me_event_by_high_ff)
```


## Change Type: Sequential Comparisons

```{r me-change-type-sequential}
fmt_me(me_change_type_sequential)
```

## Simple Post-Release Effect

```
me_way_event_sequential_simp <- avg_comparisons(
  q2_main_models[["Post × HighFF"]],
  variables = list(event = c(FALSE, TRUE))
) # 0.0431
```

```{r me-way-event-sequential-simp}
fmt_me(me_way_event_sequential_simp)
```

## By FF & SFHA

```
me_way_event_ff_sfha <- avg_comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = "event",
  by = c("change_type", "high_ff_score")
)
```

```{r me-way-event-ff-sfha}
fmt_me(me_way_event_ff_sfha)
```

```{r}
wald(
  me_way_event_ff_sfha,
  keep = "high_ff_scoreTRUE:eventTRUE:change_type.*:Triad"
)
```

## Post Release by Effective SFHA Change Type


These outputs estimate whether the estimated effect of high Flood Factor exposure differs across FEMA SFHA status categories.

```
me_event_by_change_type <- avg_comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = list(event = c(FALSE, TRUE)),
  by = "change_type"
)
```

```{r me-event-by-change-type}
fmt_me(me_event_by_change_type)
```

## Never SFHA: Post-Release Effect

This is the targeted contrast from the effective-map model for properties categorized as `Never SFHA`, allowing high and low Flood Factor properties to be represented in the comparison.

```
me_never_sfha_event <- avg_comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = "event",
  newdata = datagrid(
    change_type = "Never SFHA",
    high_ff_score = c(TRUE, FALSE)
  ),
  by = NULL
)
```

```{r me-never-sfha-event}
fmt_me(me_never_sfha_event)
```

## Never Preliminary SFHA: Post-Release Effect by Triad

```{r me-never-prelim-event-by-triad}
fmt_me(me_never_prelim_event_by_triad)



```

## All Effective Map Status Options

```
me_all_effective_grid <- comparisons(
  q2_main_models[["Post × HighFF × SFHA"]],
  newdata = datagrid(
    event = unique,
    high_ff_score = unique,
    change_type = unique
  )
)
```

```{r me-all-effective-grid}
fmt_me(me_all_effective_grid) 
```

```{r}
me_all_effective_grid  |>
    as.data.frame() |>
    select(any_of(c(
      "term", "contrast", "change_type", "change_type_prelim", "Triad",
      "high_ff_score", "highff_post", "event", "estimate", "std.error",
      "conf.low", "conf.high", "p.value"
    ))) |>
 filter( change_type != "Changes SFHA") |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |> DT::datatable()

me_all_effective_grid  |>
    as.data.frame() |>
   filter(term == "event" & change_type != "Changes SFHA") |>

    select(any_of(c(
      "term", "contrast", "change_type", "change_type_prelim", "Triad",
      "high_ff_score", "highff_post", "event", "estimate", "std.error",
      "conf.low", "conf.high", "p.value"
    ))) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |> DT::datatable()
```

## High Flood Factor Effects by SFHA Change Type and Triad

```
me_high_ff_post_by_change_type <- comparisons(
  q2_main_models[["Post × HighFF × Triad × SFHA"]],
  variables = "event",
  newdata = datagrid(
    high_ff_score = TRUE,
    change_type = c("Never SFHA", "Always SFHA", "Changes SFHA"),
    Triad = c("South", "North", "City")
  ),
  vcov = ~pin10
)
```

```{r me-high-ff-change-type-triad}
fmt_me(me_high_ff_post_by_change_type)
```

:::



# Q2 Robustness Checks

## Calculated with ETWFE Package

These models use the `etwfe` package. The saved outputs below are produced by `scripts/q2_dissertation_02_etwfe_models.R`.

::: {.panel-tabset}

### Base Model

This version does not include SFHA status or Triad in the equation.

```{r etwfe-base}
etwfe_base_table
```

### Regional Heterogeneity

```{r etwfe-triad}
etwfe_triad_table
```

:::


## Models using Preliminary FIRMs

These models are pretty crappy and not used in the dissertation document, but they do make me feel better about the models using effective FIRM status for the dissertation. (Having no results is a good thing when there shouldn't be results, yay.)

::: {.panel-tabset}

### Preliminary SFHA × High FF × Post by Triad

```{r robust-prelim-high-ff}
robust_prelim_high_ff_table
```

### Preliminary SFHA × HighFF Post by Triad

```{r robust-prelim-highff-post}
robust_prelim_highff_post_table
```

:::

# Diagnostics and Data Checks

::: {.panel-tabset}

## Analysis Data

```{r data-summary}
tibble(
  observations = nrow(bldg_sfha),
  parcels = n_distinct(bldg_sfha$pin),
  pin10s = n_distinct(bldg_sfha$pin10),
  min_sale_year = min(bldg_sfha$sale_year, na.rm = TRUE),
  max_sale_year = max(bldg_sfha$sale_year, na.rm = TRUE),
  post_release_sales = sum(bldg_sfha$event, na.rm = TRUE),
  high_ff_sales = sum(bldg_sfha$high_ff_score, na.rm = TRUE)
) |>
  modelsummary::datasummary_df(output = "gt")
```

## Preliminary Control Groups

```{r prelim-control-groups}
groups_prelim_long |>
  count(group, name = "observations") |>
  arrange(group) |>
  modelsummary::datasummary_df(output = "gt")
```

## Effective Control Groups

```{r eff-control-groups}

groups_eff_long <- readRDS(
  file.path(out_dir, "groups_eff_long.rds")
)

groups_eff_long |>
  count(group, name = "observations") |>
  arrange(group) |>
  modelsummary::datasummary_df(output = "gt")
```

:::


# Diagnostics: Dropped Terms

These tables show terms removed from the presentation tables because their standard errors were missing or larger than the threshold used in the scripts. In this fixed-effects setup, these terms are usually either not identified within PIN over time or are extremely sparse combinations.

::: {.panel-tabset}

## Basic TWFE: Effective

```{r diag-basic-effective}
fmt_me(dropped_terms_basic_twfe_effective)
```

## Basic TWFE: Preliminary

```{r diag-basic-prelim}
fmt_me(dropped_terms_basic_twfe_prelim)
```

## Basic TWFE: HighFF + Preliminary

```{r diag-basic-highff-prelim}
fmt_me(dropped_terms_basic_twfe_highff_prelim)
```

## Q2 Main Models

```{r diag-q2-main}
fmt_me(dropped_terms_q2_main)
```

## HighFF Post Models

```{r diag-highff-post}
fmt_me(dropped_terms_highff_post)
```

## Robustness: Preliminary + High FF

```{r diag-robust-high-ff}
fmt_me(dropped_terms_robust_prelim_high_ff)
```

## Robustness: Preliminary + HighFF Post

```{r diag-robust-highff-post}
fmt_me(dropped_terms_robust_prelim_highff_post)
```

:::



## Ordinal & Continuous FF Risk Variable

> See `q2_FF_variable_checks.qmd`

# Appendix B

## Figures 13-14 in Q2_assumption_graphs.qmd

## Figures 17-19, 22 in Q2 assumption graphs.qmd


## Table 18: Q2 PreTrend Slope Test



```{r}
# Option A: Linear pre-trend slope test (restrict to Pre)
df = bldg_sfha

pre <- df |> mutate(new_info_released = 2017) |>
  filter(sale_year < 2020)

# Compare slopes over time by SFHA, by High FF, and by their interaction
m_sfha   <- feols(log_price ~ sale_year * in_eff_sfha, data = pre, cluster = ~pin10)
m_highff <- feols(log_price ~ sale_year * high_ff_score, data = pre, cluster = ~pin10)

# technically high_ff_Score is not known yet, but it could could convey true risk and if properties that were high risk were already on a different trend than less risky properties.
m_both   <- feols(log_price ~ sale_year * in_eff_sfha * high_ff_score, data = pre, cluster = ~pin10)

modelsummary(
  list("SFHA × time" = m_sfha, "HighFF × time" = m_highff, "SFHA×HighFF × time" = m_both),
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests"
) |>
  tab_options(data_row.padding = px(2)) |>
  tab_source_note(md("We want NOT statistically significant interaction slope terms for variables interacted with sale_year."))
```

**Has TWFE:**

```{r}
# Optbldg_sfha# Option B: Linear pre-trend slope test (restrict to Pre)
pre <- df |> filter(sale_date < new_info_released)
pre <- pre |> mutate(prelim_sfha_category =  relevel(factor(prelim_sfha_category), ref = "Never SFHA"))

# Compare slopes over time by SFHA, by High FF, and by their interaction
m_sfha   <- feols(log_price ~ sale_year * prelim_sfha_category | pin + sale_year, data = pre, cluster = ~pin10)
m_highff <- feols(log_price ~ sale_year * high_ff_score| pin + sale_year, data = pre, cluster = ~pin10)

# technically high_ff_Score is not known yet, but it could could convey true risk and if properties that were high risk were already on a different trend than less risky properties.
m_both   <- feols(log_price ~ sale_year * prelim_sfha_category * high_ff_score | pin + sale_year, data = pre, cluster = ~pin10)

modelsummary(
  list("SFHA × time" = m_sfha, "HighFF × time" = m_highff, "SFHA×HighFF × time" = m_both),
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests"
) |>
  tab_options(data_row.padding = px(2))|>
  tab_source_note(md("We want NOT statistically significant interaction slope terms for variables interacted with sale_year."))
```


### Models (by Triad)

```{r}
pre <- df |> 
  filter(sale_date < new_info_released, !is.na(Triad)) |> 
  mutate(prelim_sfha_category =  relevel(factor(prelim_sfha_category), ref = "Never SFHA"))

triads <- unique(pre$Triad)

mods <- purrr::map(triads, function(tr){
  d <- dplyr::filter(pre, Triad == tr)
  feols(log_price ~ sale_year * prelim_sfha_category * high_ff_score, data = d, cluster = ~pin10)
}) |> rlang::set_names(triads)

modelsummary(
  mods,
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests by Triad"
)
```

**Does not have TWFE:**
```{r}
pre <- df |> dplyr::filter(sale_date < new_info_released, !is.na(Triad))  |> mutate(prelim_sfha_category =  relevel( as.factor(prelim_sfha_category), ref = "Never SFHA"))

triads <- unique(pre$Triad)

mods <- feols(log_price ~ sale_year * prelim_sfha_category * high_ff_score * Triad, data = pre, cluster = ~pin10)

modelsummary(
  mods,
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests by Triad"
)
```

## Table 21: Q2 placebo test


```{r}
placebo_cut <- 2017
pre_placebo <- df |> filter(sale_year <= 2019) |> 
  mutate(event_pb = if_else(sale_year > placebo_cut, "PostPB", "PrePB") |> factor(c("PrePB","PostPB")))

models = list(
    placebo_simple <- feols(log_price ~ high_ff_score * event_pb | pin + sale_year + qtr,
             cluster = ~pin10, data = pre_placebo),
  
  placebo <- feols(log_price ~ high_ff_score * change_type * event_pb | pin + sale_year + qtr,
             cluster = ~pin10, data = pre_placebo),
    actual_simple <- feols(log_price ~ high_ff_score * event | pin + sale_year + qtr,
             cluster = ~pin10, data = bldg_sfha),

  actual <- feols(log_price ~ high_ff_score * change_type * event | pin + sale_year + qtr,
             cluster = ~pin10, data = bldg_sfha)
)

modelsummary(models, output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             title = "Placebo test (cut at 2017)")

```



