---
title: "Q2 Marginal Effects"
format: html
---



```{r setup}
library(tidyverse)
library(fixest)
library(did)  
library(etwfe)
library(tidyverse)
library(modelsummary)
library(gt)
library(marginaleffects)

options(scipen = 999)

# bldg_sfha <- readRDS("data/processed/variants/df_prep__bldg_sfha.RDS")
# 
# parcels <- readRDS("data/processed/variants/df_prep__parcel_sfha.RDS")
# 
# bldg_1in500 <- readRDS("data/processed/variants/df_prep__bldg_1in500.RDS")

source("R/helper_pins_to_drop.R")
```


```{r}

lake100ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within100ft_ExportTable_TableToExcel.xlsx")
lake500ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within500ft_ExportTable_TableToExcel.xlsx")

bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS")

bldg_sfha <- bldg_sfha |> filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014)
             )

make_control_groups <- function(df, 
                                ever_added,
                                ever_removed,
                    pre_eff_change_type, 
                    type = c("pre", "eff")
                                ){
  
  # Treated Group A: Added to Risk Zone
  group_T_A <- df |>
    filter( {{ever_added}} == TRUE )
  
  # Treated Group B: Removed from Risk Zone
  group_T_B <- df |> 
      filter( {{ever_removed}}  == TRUE)

  # Control Group A:  Never in SFHA, FIRM panels never updated
    
   if(type == "pre"){
   group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
             pre_date_chr %in% c("2005-01-01")
         )
  }else if(type == "eff"){  # for effective maps
  group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
         eff_date_chr %in% c("2008-08-19") 
         ) 
  }  

    # Control Group B: Never in SFHA, FIRM Panels are updated
    group_C_B  <- df |> 
      filter( 
        {{pre_eff_change_type}} == "Never SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
         )

    # Control Group C: Always in SFHA, FIRM Panels are not updated 
    if(type == "pre"){
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &             
          pre_date_chr %in% c("2005-01-01")
      )}
    else if(type == "eff") {  # this probably is tainted by prelim map cohort in 2021 though....
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") )
      )
    
    group_C_C_alt <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") | 
            pre_date_chr %in% c("2005-01-01")
          )
      )
    }
    
    # Always in SFHA but FIRM panels have been recently updated
   
    if(type == "eff") {
      group_C_D <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10"))
         )
      
       group_C_D_alt <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
             )
         )
    } else if (type == "pre") {
      group_C_D <- df |> 
         filter(
        {{pre_eff_change_type}} == "Always SFHA" &
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
    }
      list(
    group_T_A = group_T_A,
    group_T_B = group_T_B,
    group_C_A = group_C_A,
    group_C_B = group_C_B,
    group_C_C = group_C_C,
    group_C_D = group_C_D

  )

}

groups <- make_control_groups(df = bldg_sfha, 
                    ever_added = ever_added_prelim, 
                    ever_removed = ever_removed_prelim, 
                    pre_eff_change_type = change_type_prelim, 
                    type = "pre")

groups_long <- imap_dfr(groups, ~ {
  .x |>
    mutate(group = .y)
})
```


```{r}

bldg_sfha <- bldg_sfha |> mutate(event = sale_date> new_info_released)

bldg_sfha <- bldg_sfha |> mutate(highff_post = high_ff_score == TRUE &  sale_date > new_info_released )

bldg_sfha <- bldg_sfha |> 
  group_by(pin) |>
  mutate(pin_num = as.numeric(pin),
    # ff_group = ifelse(high_ff_score==TRUE & sale_date > new_info_released, as.character(min(sale_year[sale_date > new_info_released])), "0")) |>
      ff_group = ifelse(high_ff_score==TRUE & sale_date > new_info_released, "2020", "0")) |>

  ungroup()


```


# Basic TWFE models


```{r}
models <- list(
  "County" = feols(log_price ~ prelim_sfha_category * high_ff_score * event | pin + sale_year, data= bldg_sfha, cluster = ~ pin10),
  
  "Triad Interactions" = feols(log_price ~ prelim_sfha_category * high_ff_score * event *Triad | pin + sale_year, data= bldg_sfha, cluster = ~ pin10)

)
modelsummary(models, stars = TRUE)
```

# ETWFE comparisons


```{r}

mod_etwfe <- etwfe(
  fml  = log(sale_price) ~ 1, 
  data = bldg_sfha, 
  ivar   = pin_num, 
  tvar = sale_year,
  tref = "2019",
  gref = "0",
  gvar = ff_group, 
  vcov = ~pin10
)

emfx(mod_etwfe)

```

```{r}
mod_etwfe2 <- etwfe(
  fml  = log(sale_price) ~ 1, 
  data = bldg_sfha, 
  ivar = pin, 
  tvar = sale_year,
  tref = "2019",
  gref = "0",
  gvar = ff_group, 
  vcov = ~pin10,
  xvar = Triad)

emfx(mod_etwfe2)
emfx(mod_etwfe2, type = "group")


```


# Marginal Effects


```{r}
models <- list(
  "County" = feols(log_price ~ highff_post * prelim_sfha_category  | pin + sale_year, data= bldg_sfha, cluster = ~ pin10),
  
  "Triad Interactions" = feols(log_price ~ highff_post * prelim_sfha_category * Triad | pin + sale_year, data= bldg_sfha, cluster = ~ pin10)

)
modelsummary(models, stars = TRUE)
```

# Question 2

## Table 15: Question 2 Main Model

```{r}

## change type is for effective maps
triad_mod_notriads = feols(log(sale_price) ~ change_type * high_ff_score * event  | pin + sale_year, vcov = ~pin10, data= bldg_sfha)

## change type is for effective maps
triad_mod = feols(log(sale_price) ~ change_type * high_ff_score * event * Triad | pin + sale_year, vcov = ~pin10, data= bldg_sfha)

triad_mod_pre <- feols(log_price ~ prelim_sfha_category * high_ff_score * event * Triad | pin + sale_year, data = bldg_sfha, cluster = ~ pin10)


etable(triad_mod)


# a specific scenario I'm curious about
example_grid = data.frame(event = TRUE, change_type = "Never SFHA", high_ff_score = TRUE, Triad = "City")


```


```{r}
avg_results <- avg_comparisons(
  triad_mod,
  variables = list(change_type ="sequential")
  )
avg_results
```

```{r}
# avg_results_pre <- avg_comparisons(
#   triad_mod_pre,
#   variables = list(change_type ="sequential")
#   )
# avg_results_pre
```

```{r}
avg_results <- avg_comparisons(
  triad_mod,
  variables = list("event" = c(FALSE, TRUE)),
  by = "change_type")

avg_results
```




```{r}
### this one works great!
never_sfha_effect <- avg_comparisons(
  triad_mod,
  variables = "event",
  newdata = datagrid(
    change_type = "Never SFHA",
    "high_ff_score"   = c(TRUE,FALSE)
  ),
   by = NULL)

never_sfha_effect
```


```{r}

## only shows coefficient for City
never_sfha_effect_byTriad <- avg_comparisons(
  triad_mod_pre,
  variables = "event",
  newdata = datagrid(
    prelim_sfha_category = "Never SFHA",
    high_ff_score   = c(TRUE,FALSE)
  ),
  by = "Triad")

never_sfha_effect_byTriad
```

```{r}
# always_sfha_effect <- avg_comparisons(
#   triad_mod_pre,
#   variables = "event",
#   newdata = datagrid(
#     prelim_sfha_category = "Always SFHA",
#         high_ff_score   = c(FALSE,TRUE)
# ),
#    by = NULL
# )
# 
# always_sfha_effect
```

```{r}
# always_sfha_effect_byTriad <- avg_comparisons(
#   triad_mod_pre,
#   variables = "event",
#   newdata = datagrid(
#     prelim_sfha_category = "Always SFHA",
#         "high_ff_score"   = c(TRUE,FALSE)
# ),
#    by = "Triad"
# )
# 
# always_sfha_effect_byTriad
```

```{r}
all_opts <- comparisons(triad_mod_notriads, newdata = datagrid(event = unique, high_ff_score = unique, change_type = unique))

```

**Is the effect of having a high flood score moderated by SFHA status?**

`all_opts <- avg_comparisons(triad_mod, variables = "highff_post", by = "change_type")`

The expected change in Y (logged sale price) assoiated with a change in X (one SFHA status to another) differs based on the value of `change_type`

Never SFHA(-0.574) vs (-0.0450)

Are these statistically significantly different from each other?

```{r}
triad_mod <- feols(log_price ~ change_type * highff_post | pin + sale_year, data = bldg_sfha, cluster = ~ pin10)

all_opts <- avg_comparisons(triad_mod, variables = "highff_post", by = "change_type")
all_opts

avg_comparisons(triad_mod, variables = "highff_post", by = "change_type", hypothesis = "b1=b2")
```
Always SFHA not statistically significant from Never SFHA

```{r}
triad_mod <- feols(log_price ~ change_type * highff_post * Triad | pin + sale_year, data = bldg_sfha, cluster = ~ pin10)

all_opts <- avg_comparisons(triad_mod, variables = "highff_post", by = "change_type")
all_opts

avg_comparisons(triad_mod, variables = "highff_post", by = "change_type", hypothesis = "b1=b2")
```


```{r}
triad_mod2 <- feols(log_price ~ change_type:highff_post + highff_post:Triad | pin + sale_year, data = bldg_sfha, cluster  = ~ pin10)

all_opts <- avg_comparisons(triad_mod2, variables = "highff_post", by = "change_type")
all_opts
```
```{r}
ff_effects_filtered <- comparisons(
  triad_mod,
  variables = "highff_post",
  newdata = datagrid(
    change_type = c("Never SFHA", "Always SFHA", "Changes SFHA"),
    Triad = c("South", "North", "City")
  ),
  vcov = ~pin10
)
ff_effects_filtered
```
```{r}
triad_mod <- feols(log_price ~ event* change_type * high_ff_score * Triad | pin + sale_year, data = bldg_sfha, cluster = ~ pin10)

ff_effects_filtered <- comparisons(
  triad_mod,
  variables = "high_ff_score",
  newdata = datagrid(
    event = TRUE,
    change_type = c("Never SFHA", "Always SFHA", "Changes SFHA"),
    Triad = c("South", "North", "City")
  ),
  vcov = ~pin10
)
ff_effects_filtered
```

## Q2 Robustness Checks

```{r}
models <- list(
  "South" = feols(log_price ~ prelim_sfha_category * high_ff_score * event | pin + sale_year, data = bldg_sfha |> filter(Triad == "South"), cluster = ~pin10),
  "North" = feols(log_price ~ prelim_sfha_category * high_ff_score* event | pin + sale_year, data = bldg_sfha |> filter(Triad == "North"), cluster = ~pin10),
    "City" = feols(log_price ~ prelim_sfha_category * high_ff_score * event | pin + sale_year, data = bldg_sfha |> filter(Triad == "City"), cluster = ~pin10)
)

modelsummary(
  models,
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests by Triad"
)
```


```{r}
models <- list(
  "South" = feols(log_price ~ prelim_sfha_category * highff_post | pin + sale_year, data = bldg_sfha |> filter(Triad == "South"), cluster = ~pin10),
  "North" = feols(log_price ~ prelim_sfha_category * highff_post | pin + sale_year, data = bldg_sfha |> filter(Triad == "North"), cluster = ~pin10),
    "City" = feols(log_price ~ prelim_sfha_category * highff_post | pin + sale_year, data = bldg_sfha |> filter(Triad == "City"), cluster = ~pin10)
)

modelsummary(
  models,
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests by Triad"
)
```


## Ordinal Risk Variable

```{r}
feols(log(sale_price) ~  factor(env_flood_fs_factor) * change_type * highff_post | pin + sale_year, data = bldg_sfha) |> modelsummary(stars=TRUE)

```

