---
title: "Q1 Figures and Tables"
subtitle: "Impact of FEMA designated risk zones on sale price"
format: 
  html:
    df-print: kable
    code-fold: true
    tbl-cap-location: margin
    error: true
    toc: true
    warning: false
    message: false
---

# Setup stuff 

```{r setup}
library(tidyverse)
library(fixest)
library(did)  
library(etwfe)
library(tidyverse)

library(modelsummary)
library(gt)

options(scipen = 999)

# bldg_sfha <- readRDS("data/processed/variants/df_prep__bldg_sfha.RDS")
# 
# parcels <- readRDS("data/processed/variants/df_prep__parcel_sfha.RDS")
# 
# bldg_1in500 <- readRDS("data/processed/variants/df_prep__bldg_1in500.RDS")

source("R/helper_pins_to_drop.R")
```


```{r}

lake100ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within100ft_ExportTable_TableToExcel.xlsx")
lake500ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within500ft_ExportTable_TableToExcel.xlsx")

bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS")

parcels <- readRDS("data/processed/targets/sales/df_prep_land_v2026_03.RDS")

bldg_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_v2026_03.RDS")  |>
  filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014))

# bldg_sfha <- readRDS("data/processed/variants/df_prep__bldg_sfhaarcgis_redo_2026sales.RDS")
# 
# parcels <- readRDS("data/processed/variants/df_prep__parcel_sfhaarcgis_redo_2026sales.RDS")
# 
# bldg_1in500 <- readRDS("data/processed/variants/df_prep__bldg_1in500arcgis_redo_2026sales.RDS") |> 
#   filter(!pin10 %in% drop_parcels  |          
#            (pin10 == "0113301013" & sale_year > 2014))


bldg_sfha <- bldg_sfha |> filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014)
             )

parcels <- parcels |> filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014)
             )

make_control_groups <- function(df, 
                                ever_added,
                                ever_removed,
                    pre_eff_change_type, 
                    type = c("pre", "eff")
                                ){
  
  # Treated Group A: Added to Risk Zone
  group_T_A <- df |>
    filter( {{ever_added}} == TRUE )
  
  # Treated Group B: Removed from Risk Zone
  group_T_B <- df |> 
      filter( {{ever_removed}}  == TRUE)

  # Control Group A:  Never in SFHA, FIRM panels never updated
    
   if(type == "pre"){
   group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
             pre_date_chr %in% c("2005-01-01")
         )
  }else if(type == "eff"){  # for effective maps
  group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
         eff_date_chr %in% c("2008-08-19") 
         ) 
  }  

    # Control Group B: Never in SFHA, FIRM Panels are updated
    group_C_B  <- df |> 
      filter( 
        {{pre_eff_change_type}} == "Never SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
         )

    # Control Group C: Always in SFHA, FIRM Panels are not updated 
    if(type == "pre"){
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &             
          pre_date_chr %in% c("2005-01-01")
      )}
    else if(type == "eff") {  # this probably is tainted by prelim map cohort in 2021 though....
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") )
      )
    
    group_C_C_alt <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") | 
            pre_date_chr %in% c("2005-01-01")
          )
      )
    }
    
    # Always in SFHA but FIRM panels have been recently updated
   
    if(type == "eff") {
      group_C_D <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10"))
         )
      
       group_C_D_alt <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
             )
         )
    } else if (type == "pre") {
      group_C_D <- df |> 
         filter(
        {{pre_eff_change_type}} == "Always SFHA" &
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
    }
      list(
    group_T_A = group_T_A,
    group_T_B = group_T_B,
    group_C_A = group_C_A,
    group_C_B = group_C_B,
    group_C_C = group_C_C,
    group_C_D = group_C_D

  )

}

groups <- make_control_groups(df = bldg_sfha, 
                    ever_added = ever_added_prelim, 
                    ever_removed = ever_removed_prelim, 
                    pre_eff_change_type = change_type_prelim, 
                    type = "pre")

groups_long <- imap_dfr(groups, ~ {
  .x |>
    mutate(group = .y)
})
```



```{r}
groups_long |>
  group_by(group) |>
  summarise(
    n = n(),
    n_properties = n_distinct(pin),
    mean_price = mean(sale_price, na.rm = TRUE),
    mean_log_price = mean(log_price, na.rm = TRUE)
  )
```

## Line Graphs

```{r }
group_trends <- groups_long |>
  group_by(group, sale_year) |>
  summarise(
    mean_log_price = mean(log_price, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

ggplot(group_trends, aes(x = sale_year, y = mean_log_price, color = group)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  labs(
    x = "Year",
    y = "Mean Log Price",
    color = "Group"
  ) +
  theme_minimal()
```

```{r}
#| layout-ncol: 2


groups_long <- groups_long |>
  mutate(group_type = case_when(
    group %in% c("group_T_A", "group_T_B") ~ "Treated",
    TRUE ~ "Control"
  ))

group_trends2 <- groups_long |>
  group_by(group_type, sale_year) |>
  summarise(
    mean_log_price = mean(log_price, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(group_trends2, aes(x = sale_year, y = mean_log_price, color = group_type)) +
  geom_line(linewidth = 1.2)

ggplot(group_trends, aes(x = sale_year, y = mean_log_price)) +
  geom_line() +
  facet_wrap(~ group)
```
# Question 1

## Table 2: Sample Counts

```{r}
table(bldg_sfha$prelim_sfha_category)
table(bldg_sfha$change_type_prelim)
```


```{r}
df_es_added <- bldg_sfha |>
  filter(pin10 %in% groups$group_T_A$pin10 | pin10 %in% groups$group_C_B$pin10 )|>
 # filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(pin_num = as.numeric(pin)) |>
  dplyr::arrange(pin_num, sale_year, sale_date) |>
  dplyr::group_by(pin_num, sale_year, pre_date_chr) |>
  dplyr::slice_tail(n = 1) |>
  dplyr::ungroup() |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA") |> 
  
   group_by(pin_num) |>
  mutate(
    g_add = if (any(addedto_prelim_sfha == 1, na.rm = TRUE)) {
      min(sale_year[addedto_prelim_sfha == 1], na.rm = TRUE)
    } else {
      0L
    }
  ) |>
  ungroup()


added_counts <- table(df_es_added$g_add, df_es_added$pre_date)



df_es_removed <- bldg_sfha |>
    filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 )|>

  #filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(pin_num = as.numeric(pin)) |>
  dplyr::arrange(pin_num, sale_year, sale_date) |>
  dplyr::group_by(pin_num, sale_year, pre_date_chr) |>
  dplyr::slice_tail(n = 1) |>
  dplyr::ungroup() |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA") |> 
  
   group_by(pin_num) |>
  mutate(
    g_remove = if (any(removedfrom_prelim_sfha == TRUE, na.rm = TRUE)) {
      min(sale_year[removedfrom_prelim_sfha == TRUE], na.rm = TRUE)
    } else {
      0L
    }
  ) |>
  ungroup()


removed_counts <- table(df_es_removed$g_remove, df_es_removed$pre_date)
```

```{r}
#| label: tbl-table1-treatedsalesbycohort
#| tbl-cap: "Table 1: Treated Sales by Cohort and Treatment Direction"
#| layout-ncol: 2

added_counts 
removed_counts 
```

## Table 3

```{r}
#| label: tbl-table3-descriptivestatsforQ1
#| tbl-cap: "Table3: Descriptive Statistics for Sample"

sfha_category_stats <- bldg_sfha |>
  group_by(pin) |> mutate(n_sales = n()) |> ungroup() |>
  group_by(change_type_prelim) |>
 summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- bldg_sfha |>
    mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(change_type_prelim) |>
  filter(ever_firm_update==TRUE) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- bldg_sfha |>
  group_by(prelim_sfha_category) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- bldg_sfha |>
    mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(prelim_sfha_category) |>
  filter(ever_firm_update==TRUE) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats
```

```{r}
#| label: fig-figure5
#| layout-ncol: 2


allsales_bldg_sfha <- readRDS("data/processed/targets/sales/allsales_bldg_v2026_03.RDS")


allsales_bldg_sfha <- allsales_bldg_sfha |> 
  filter(!pin10 %in% c("0122400028", "0516106013"))|> 
  filter(!(Triad != "City" & log_price > 13.5))
```


```{r}
#| label: fig-figure5-cohorttrends
#| fig-cap: 
#|   - "Includes Chicago"
#|   - "Excludes Chicago"

allsales_bldg_sfha |>
  filter(!pin10 %in% c("0122400028", "0516106013")) |> #filter(log_price > 13.5)|>
  filter(prelim_sfha_category %in% c("Always SFHA", "Never SFHA")) |> 
    group_by(sale_year, prelim_sfha_category, pre_date_chr) |> 
  summarise(avg_logprice = mean(log_price, na.rm = TRUE) )|> 

  ggplot(aes(x = sale_year , y = avg_logprice, shape = prelim_sfha_category)) +
  theme_classic() + 
  theme(legend.position = "bottom")+
  geom_smooth(aes(lty = prelim_sfha_category), method = "lm", se = FALSE, color = "darkgray", alpha= 0.5, lwd = 1) + 
  geom_line(aes(lty = prelim_sfha_category)) +
  geom_point(size = 2) + 
  
  scale_x_continuous(breaks = c(2010, 2015, 2020, 2026)) +
  labs(#title = "Cohort Trends by SFHA Group: Always In vs. Always Out",
       #subtitle = "Includes Chicago",
       y = "Avg. Logged Sale Price",
       x = NULL,
              shape = "SFHA Group",
       lty = "SFHA Group",
              caption = "Graphed with all sales, not just repeat sales. Includes Chicago") +
  facet_wrap(~pre_date_chr)

# EXCLUDE CHCICGO
allsales_bldg_sfha |>   
  filter(!pin10 %in% c("0122400028", "0516106013")) |> filter(Triad != "City")|>
  filter(prelim_sfha_category %in% c("Always SFHA", "Never SFHA")) |> 
    group_by(sale_year, prelim_sfha_category, pre_date_chr) |> 
  summarise(avg_logprice = mean(log_price, na.rm = TRUE) )|> 

  ggplot(aes(x = sale_year , y = avg_logprice, shape = prelim_sfha_category)) +
  theme_classic() + 
  theme(legend.position = "bottom")+
  geom_smooth(aes(lty = prelim_sfha_category), method = "lm", se = FALSE, color = "darkgray", alpha= 0.5, lwd = 1) + 
  geom_line(aes(lty = prelim_sfha_category)) +
  geom_point(size = 2) + 
  
  scale_x_continuous(breaks = c(2010, 2015, 2020, 2026)) + 
  labs(#title = "Cohort Trends by SFHA Group: Always In vs. Always Out",
       #subtitle = "Excludes Chicago",
       y = "Avg. Logged Sale Price",
       x = NULL,
              shape = "SFHA Group",
       lty = "SFHA Group",
       caption = "Graphed with all sales, not just repeat sales. Excludes Chicago") +
  facet_wrap(~pre_date_chr)
```

```{r}
#| label: fig-figure6
#| fig-label: "Figure 6"


allsales_bldg_sfha |>   
   filter(!pin10 %in% c("0122400028", "0516106013")) |> 
  #filter(!(Triad != "City" & log_price > 13.5))|>
  filter(prelim_sfha_category %in% c("Always SFHA", "Never SFHA")) |> 
    group_by(sale_year, prelim_sfha_category) |> 
  summarise(avg_logprice = mean(log_price, na.rm = TRUE) )|> 

  ggplot(aes(x = sale_year , y = avg_logprice, shape = prelim_sfha_category)) +
  theme_classic() + 
  theme(legend.position = "bottom")+
  geom_smooth(aes(lty = prelim_sfha_category), method = "lm", se = FALSE, color = "darkgray", alpha= 0.5, lwd = 1) + 
  geom_line(aes(lty = prelim_sfha_category)) +
  geom_point(size = 2.5) + 
  
  scale_x_continuous(breaks = c(2010, 2015, 2020, 2026)) + 
  labs(title = "County Trends by SFHA Group: Always In vs. Always Out",
       y = "Avg. Logged Sale Price",
       x = NULL,
       caption= "Uses All Sales",
              shape = "SFHA Group",
       lty = "SFHA Group")
```


## Table 4: County Wide Effect

```{r }
#| label: tbl-table4-prelim-countywide 
#| tbl-cap: "Table 4"

bldg_sfha <- bldg_sfha |>
  mutate(nbhd_code = if_else(
    is.na(nbhd_code),
    "Missing",
    as.character(nbhd_code)
  ))

mods <- list (
 no_fe <- feols(
    log_price ~ in_prelim_sfha,
    vcov = ~pin10,
    data = bldg_sfha
  ),
  
 one_fe <- feols(
    log_price ~ in_prelim_sfha | sale_year,
    data = bldg_sfha,
     vcov = ~pin10
  ),
   pin_fe <- feols(
    log_price ~ in_prelim_sfha | pin ,
    data = bldg_sfha,
        vcov = ~pin10,

  ),
  
  two_fe <- feols(
    log_price ~ in_prelim_sfha | pin + sale_year,
    data = bldg_sfha,
     vcov = ~pin10
  ),
  
  three_fe <- feols(
    log_price ~ in_prelim_sfha | pin + sale_year + qtr,
    data = bldg_sfha,
     vcov = ~pin10
)
)
# mod_prelim_3fe <- feols(
#   log_price ~ in_prelim_sfha | pin + sale_year + qtr,
#   data = bldg_sfha
# )
# 
# mod_eff_3fe <- feols(
#   log_price ~ in_eff_sfha | pin + sale_year + qtr,
#   data = bldg_sfha
# )
# 
# mods_names <- list(
#   "Preliminary"      = mod_prelim,
#   "Effective"        = mod_eff
#   # , "Prelim w/ Qtr FE" = mod_prelim_3fe,
#   #"Eff w/ Qtr FE"    = mod_eff_3fe
# )
# 
# vcovs <- list(
#   "Parcel" = ~pin10,
#   "Municipality" = ~clean_name
#   # , "Neighborhood" = ~nbhd_code
# )
# 
# gof_labels <- c(
#   "nobs"      = "Observations",
#   "r.squared" = "R-squared"
# )

coef_labels = c(
  "in_prelim_sfhaTRUE" = "In SFHA (Preliminary Map)",
  "in_eff_sfhaTRUE"    = "In SFHA (Effective Map)"
)

# ms_models <- list()
# ms_vcov   <- list()
# 
# for (m in names(mods)) {
#   for (v in names(vcovs)) {
#     ms_models[[paste(m, v, sep = "\n")]] <- mods[[m]]
#     ms_vcov[[length(ms_vcov) + 1]] <- vcovs[[v]]
#   }
# }
# 
# modelsummary::modelsummary(
#   ms_models,
#   vcov = ms_vcov,
#   stars = TRUE,
# 
# )

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within"
#  ,
 # estimate = "{estimate}{stars}",
#  statistic = "\n({std.error})"#,
,  coef_map = coef_labels
)
```


```{r }
#| label: table4-prelim-countywide-robustnesschecks 
#| tbl-cap: "Table 4 robustness check"

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within",
vcov = ~clean_name
,  coef_map = coef_labels
)

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within",
vcov = ~nbhd_code
,  coef_map = coef_labels
)
```

##  Table 5: Simple Directional Effects - Standard TWFE

```{r}
#| label: tbl-table5-simple-effectofremapping
#| tbl-cap: "Table 5: Effect of Being Mapped Into or Out of a FEMA Flood Plain"

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = bldg_sfha
  ),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,

  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,
  ))
 


all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```



## Table 5 & 6: Directional Effects & Control Group Subsamples


```{r}
#| label: tbl-effectofremapping
#| tbl-cap: "**Table 5 & 6** Effect of Being Mapped Into or Out of a FEMA Flood Plain. A lot of models all by each other."
#| error: true
##| eval: false

prelim_twfe <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~pin10,
        data = bldg_sfha
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (bldg_sfha |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000)),

  ),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,

  ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = (bldg_sfha |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000)),

  ),
 
  # Symmetric effect of location in risk zone
    "Symmetric" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,
  ),
 
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


## Table 7: Restrict Samples - Updated FIRM Panels only

```{r}
#| label: tbl-table-7-subset-removedfrom
#| tbl-cap: "**Table 7:** Mapped out of Preliminary SFHA - Restricted Samples"
#| 

# function with default options:
fn_valid_cohorts <- function(df){
  
  df |> 
    mutate(pre_date_chr = as.character(pre_date_chr)) |>
    group_by(pre_date_chr) |>
    summarise(
      n = n(),
      n_treated = sum(removedfrom_prelim_sfha == TRUE, na.rm = TRUE),
      n_untreated = sum(removedfrom_prelim_sfha == FALSE, na.rm = TRUE),
          .groups = "drop"

      ) |>
    filter(n_treated > 0,  n_untreated > 0) |>
    pull(pre_date_chr)
}



#table(bldg_sfha$Triad, bldg_sfha$prelim_sfha_category)

df_sub <- bldg_sfha |> 
      filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 )
  # filter(change_type_prelim != "Never SFHA" & 
  #          # and properties that are never treated for being added to the SFHA
  #          treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)

valid_cohorts_bldg <- fn_valid_cohorts(df_sub)
bldgs_fsplit <- df_sub |> filter(pre_date_chr %in% valid_cohorts_bldg)


#table(parcels$Triad, parcels$prelim_sfha_category)
#table(parcels$removed_pre_thisyear, parcels$year)

# df_sub_parcels <- parcels |> 
#       filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 )
#   # filter(change_type_prelim != "Never SFHA" & 
#   #          # and properties that are never treated for being added to the SFHA
#   #          treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)
# 
# valid_cohorts_parcels <- fn_valid_cohorts(df = df_sub_parcels)
# parcels_fsplit <- df_sub_parcels |> filter(pre_date_chr %in% valid_cohorts_parcels)
# 
# table(bldg_1in500$removed_pre_thisyear, bldg_1in500$year)
# table(bldg_1in500$removedfrom_prelim_sfha, bldg_1in500$year)
# table(bldg_1in500$Triad, bldg_1in500$prelim_sfha_category)
# df_sub_1in500 <- bldg_1in500 |> 
#   filter(change_type_prelim != "Never SFHA" & 
#            # and properties that are never treated for being added to the SFHA
#            treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)
# valid_cohorts_1in500 <- fn_valid_cohorts(df = df_sub_1in500)
# bldg_1in500_fsplit <- df_sub_1in500 |> filter(pre_date_chr %in% valid_cohorts_1in500)
# 
# 




models <- list(
 "Bldg SFHA" = feols(
       log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,

   # log(sale_price) ~ event_remapped*ever_removed_prelim | pin + sale_year,
    data = bldgs_fsplit,
  fsplit = ~pre_date_chr,
    cluster = ~pin10
  )
  # 
  # "Bldg 1in500" = feols(
  #          log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
  # 
  # #  log(sale_price) ~ event_remapped*ever_removed_prelim | pin + sale_year,
  #   data = bldg_1in500_fsplit,
  # fsplit = ~pre_date_chr,
  #   cluster = ~pin10
  # 
  # ),
  # 
  # "Parcels" = feols(
  #          log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
  # 
  # #  log(sale_price) ~ event_remapped*ever_removed_prelim | pin + sale_year,
  #   data = parcels_fsplit,
  # fsplit = ~pre_date_chr,
  #   cluster = ~pin10
  # 
  # )
)

all_models_formatted <- modelsummary::modelsummary(models,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted

```


## Table 8
```{r}
#| label: tbl-table8-subset-prelim_addedto
#| tbl-cap: "Table 8: Mapped into Preliminary SFHA - Restricted Sample"
#| 

#table(bldg_sfha$added_pre_thisyear, bldg_sfha$year)

# function with default options:
fn_valid_cohorts <- function(df){
  
  df |>  
    mutate(pre_date_chr = as.character(pre_date_chr)) |>
    group_by(pre_date_chr) |>
    summarise(
      n = n(),
      n_treated = sum(addedto_prelim_sfha == TRUE, na.rm = TRUE),
      n_untreated = sum(addedto_prelim_sfha == FALSE, na.rm = TRUE),
          .groups = "drop"

      ) |>
    filter(n_treated > 0,  n_untreated > 0) |>
    pull(pre_date_chr)
}




table(bldg_sfha$Triad, bldg_sfha$prelim_sfha_category)

df_sub <- bldg_sfha |> 
    filter(pin10 %in% groups$group_T_A$pin10 | pin10 %in% groups$group_C_B$pin10 )
  # filter(change_type_prelim != "Always SFHA" & 
  #          # and properties that are never treated for being removed from the SFHA
  #          treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)

valid_cohorts_bldg <- fn_valid_cohorts(df_sub)
bldgs_fsplit <- df_sub |> filter(pre_date_chr %in% valid_cohorts_bldg)


# table(parcels$Triad, parcels$prelim_sfha_category)
# table(parcels$removed_pre_thisyear, parcels$year)

df_sub_parcels <- parcels |> 
    filter(pin10 %in% groups$group_T_A$pin10 | pin10 %in% groups$group_C_B$pin10 )
  # filter(change_type_prelim != "Always SFHA" & 
  #          # and properties that are never treated for being removed from the SFHA
  #          treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)
valid_cohorts_parcels <- fn_valid_cohorts(df = df_sub_parcels)
parcels_fsplit <- df_sub_parcels |> filter(pre_date_chr %in% valid_cohorts_parcels)


# 
# table(bldg_1in500$removed_pre_thisyear, bldg_1in500$year)
# table(bldg_1in500$removedfrom_prelim_sfha, bldg_1in500$year)
# table(bldg_1in500$Triad, bldg_1in500$prelim_sfha_category)

# df_sub_1in500 <- bldg_1in500 |> 
#     filter(pin10 %in% groups$group_T_A$pin10 | pin10 %in% groups$group_C_B$pin10 )
  # filter(change_type_prelim != "Always SFHA" & 
  #          # and properties that are never treated for being removed from the SFHA
  #          treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)
#valid_cohorts_1in500 <- fn_valid_cohorts(df = df_sub_1in500)
#bldg_1in500_fsplit <- df_sub_1in500 |> filter(pre_date_chr %in% valid_cohorts_1in500)




models_pre_add <- list(
  # Heterogeneity by Triad: added/removed interacted with Triad
  # 
  # # Heterogeneity by Triad: added/removed interacted with Triad
  "Buildings in SFHA" =  feols(
    log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
    fsplit = ~pre_date_chr,
    cluster = ~pin10,
    data = bldgs_fsplit
  ),
    "Buildings in SFHA" =  feols(
    log(sale_price) ~ addedto_prelim_sfha*condo | pin + sale_year,
    fsplit = ~pre_date_chr,
    cluster = ~pin10,
    data = bldgs_fsplit
  ),

  "Buildings in SFHA" =  feols(
    log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
    cluster = ~pin10,
    data = bldg_sfha
  )
  # 
  # "Buildings - 1-in-500" =  feols(
  #   log(sale_price) ~ addedto_prelim_sfha | pin + year,
  #   fsplit = ~pre_date_chr,
  #   cluster = ~pin10,
  #   data = bldg_1in500_fsplit
  # ),
  # 
  # "Buildings - 1-in-500" =  feols(
  #   log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
  #   cluster = ~pin10,
  #   data = bldg_1in500
  # )
)

all_models_formatted <- modelsummary::modelsummary(models_pre_add,
                                                   output = "flextable",
                                                   fmt = function(x) round(x, 2),
                                                   
                                                   stars = TRUE)

all_models_formatted

```


## Table 9: County-wide and Cohort Directional Models using Extended TWFE

### Added To Risk Zone

```{r}
#| label: tbl-table9-column1-extwfe-with-groups-withchicago
#| tbl-cap: "Control Groups A, B, C, & D (so all PINs that never changed SFHA status; both always in, and always out)"


mod1c = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (bldg_sfha |>
            filter(
             (pin %in% groups$group_T_A$pin |
              pin %in% groups$group_C_A$pin |
              pin %in% groups$group_C_B$pin | 
              pin %in% groups$group_C_C$pin |
              pin %in% groups$group_C_D$pin )
                     )
          )
  )
# mod1c
emfx(mod1c)

emfx(mod1c, type = "group")

```

```{r}
#| label: test-table-with-groups-withchicago
#| tbl: "Includes Chicago Observations. Control Groups A & B"
#| eval: false
#| include: false


mod1c = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (bldg_sfha |>
            filter(
             (pin %in% groups$group_T_A$pin |
              pin %in% groups$group_C_A$pin |
              pin %in% groups$group_C_B$pin )
                     )
          )
  )
mod1c
emfx(mod1c)

emfx(mod1c, type = "group")

```
### Mapped Out of SFHA, Column 3

```{r table9-column3}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_B$pin10 | 
                         pin10 %in% groups$group_C_D$pin10 | 
                         pin10 %in% groups$group_C_C$pin10 |
                         pin10 %in% groups$group_C_A$pin10 | 
                         pin10 %in% groups$group_C_B$pin10 )

          )
  )
# mod2
emfx(mod2)
emfx(mod2, type = "group")
plot(emfx(mod2, type = "group"))

```


### Removed - Subset (Column 4)

```{r}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_B$pin10 | 
                         pin10 %in% groups$group_C_D$pin10 | 
                         pin10 %in% groups$group_C_C$pin10 )

          )
  )
# mod2
emfx(mod2)
emfx(mod2, type = "group")
#plot(emfx(mod2, type = "group"))


```


## Table 10: Regional Slopes

### Mapped into SFHA

```{r table10-column1-regional-slopes}

library(etwfe)

mod1 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = Triad, 
  cgroup = "never",
  gvar = treat_year_add_prelim,
  vcov = ~pin10, 
  data = (bldg_sfha |> 
            filter(treat_year_remove_prelim==10000
                   
                   & change_type_prelim != "Always SFHA")
          )
  
  )
#mod1
emfx(mod1)

emfx(mod1, type = "group")
plot(emfx(mod1))

```


### Added with regional slopes

```{r table10-column1}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
    xvar = Triad, 

  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_A$pin10 | 
                         pin10 %in% groups$group_C_A$pin10 |
                         pin10 %in% groups$group_C_B$pin10)
          )
  )
# mod2
emfx(mod2)
emfx(mod2, type = "group")

```

```{r table10-column2}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  xvar = group_name_prelim, 
  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_A$pin10 | 
                         pin10 %in% groups$group_C_A$pin10 |
                         pin10 %in% groups$group_C_B$pin10 
                         )
          )
  )
# mod2
emfx(mod2)
emfx(mod2, type = "group")

```



```{r table10-column3}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_remove_prelim, 
    xvar = Triad, 

  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_B$pin10 | 
                         pin10 %in% groups$group_C_D$pin10 |
                         pin10 %in% groups$group_C_C$pin10 
                         )
          )
  )
# mod2
#emfx(mod2)
emfx(mod2, type = "group")

```

```{r table10-column4}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  gvar = treat_year_remove_prelim, 
  xvar = group_name_prelim, 

  vcov = ~pin10, 
  data = (bldg_sfha|> 
                filter(pin10 %in% groups$group_T_B$pin10 | 
                         pin10 %in% groups$group_C_D$pin10 |
                         pin10 %in% groups$group_C_C$pin10 
                         )
          )
  )
# mod2
emfx(mod2)
emfx(mod2, type = "group")

```




```{r}
#| label: tbl-table11-effectiveSFHA-subset-removed
#| tbl-cap: "Table 11: Mapped out of EFFECTIVE SFHA - Restricted Sample"
#| 

#table(bldg_sfha$added_pre_thisyear, bldg_sfha$year)

# function with default options:
fn_valid_cohorts <- function(df){
  
  df |> 
    mutate(eff_date_chr = as.character(eff_date_chr)) |>
    group_by(eff_date_chr) |>
    summarise(
      n = n(),
      n_treated = sum(removedfrom_eff_sfha == TRUE, na.rm = TRUE),
      n_untreated = sum(removedfrom_eff_sfha == FALSE, na.rm = TRUE),
          .groups = "drop"

      ) |>
    filter(n_treated > 0,  n_untreated > 0) |>
    pull(eff_date_chr)
}





df_sub <- bldg_sfha |> 
      filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 )
  # filter(change_type_prelim != "Never SFHA" & 
  #          # and properties that are never treated for being addedto from the SFHA
  #          treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)

valid_cohorts_bldg <- fn_valid_cohorts(df_sub)
bldgs_fsplit <- df_sub |> filter(eff_date_chr %in% valid_cohorts_bldg)


# table(parcels$Triad, parcels$prelim_sfha_category)
# table(parcels$removed_pre_thisyear, parcels$year)

df_sub_parcels <- parcels |> 
      filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 )
  # filter(change_type_prelim != "Never SFHA" & 
  #          # and properties that are never treated for being added to the SFHA
  #          treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)
valid_cohorts_parcels <- fn_valid_cohorts(df = df_sub_parcels)
parcels_fsplit <- df_sub_parcels |> filter(eff_date_chr %in% valid_cohorts_parcels)


# 
# table(bldg_1in500$removed_pre_thisyear, bldg_1in500$year)
# table(bldg_1in500$removedfrom_prelim_sfha, bldg_1in500$year)
# table(bldg_1in500$Triad, bldg_1in500$prelim_sfha_category)

df_sub_1in500 <- bldg_1in500 |> 
      filter(pin10 %in% groups$group_T_B$pin10 | pin10 %in% groups$group_C_D$pin10 ) 
  # filter(change_type_prelim != "Never SFHA" & 
  #          # and properties that are never treated for being addedto the SFHA
  #          treat_year_add_prelim == 10000 & treat_year_add_eff == 10000)
valid_cohorts_1in500 <- fn_valid_cohorts(df = df_sub_1in500)
bldg_1in500_fsplit <- df_sub_1in500 |> filter(eff_date_chr %in% valid_cohorts_1in500)




models <- list(
  
  # "Buildings in SFHA" =  feols(
  #   log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
  #   fsplit = ~eff_date_chr,
  #   cluster = ~pin10,
  #   data = bldgs_fsplit
  # ),

  "Buildings in SFHA" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    fsplit = ~eff_date_chr,

    cluster = ~pin10,
    data = parcels_fsplit
  ),

  "Buildings - 1-in-500" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + year,
    fsplit = ~eff_date_chr,
    cluster = ~pin10,
    data = bldg_1in500_fsplit
  )
)

all_models_formatted <- modelsummary::modelsummary(models,
                                                   output = "flextable",
                                                   fmt = function(x) round(x, 2),
                                                   
                                                   stars = TRUE)

all_models_formatted

```




```{r}
#| label: table11-effectiveSFHA-subset-addedto
#| tbl-cap: "Table 11: Mapped into EFFECTIVE SFHA - Restricted Sample"
#| 

#table(bldg_sfha$added_pre_thisyear, bldg_sfha$year)

# function with default options:
fn_valid_cohorts <- function(df){
  
  df |> 
    mutate(eff_date_chr = as.character(eff_date_chr)) |>
    group_by(eff_date_chr) |>
    summarise(
      n = n(),
      n_treated = sum(addedto_eff_sfha == TRUE, na.rm = TRUE),
      n_untreated = sum(addedto_eff_sfha == FALSE, na.rm = TRUE),
          .groups = "drop"

      ) |>
    filter(n_treated > 0,  n_untreated > 0) |>
    pull(eff_date_chr)
}




table(bldg_sfha$Triad, bldg_sfha$prelim_sfha_category)

df_sub <- bldg_sfha |> 
  filter(change_type_prelim != "Always SFHA" & 
           # and properties that are never treated for being removed from the SFHA
           treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)

valid_cohorts_bldg <- fn_valid_cohorts(df_sub)
bldgs_fsplit <- df_sub |> filter(eff_date_chr %in% valid_cohorts_bldg)


# table(parcels$Triad, parcels$prelim_sfha_category)
# table(parcels$removed_pre_thisyear, parcels$year)

df_sub_parcels <- parcels |> 
  filter(change_type_prelim != "Always SFHA" & 
           # and properties that are never treated for being removed from the SFHA
           treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)
valid_cohorts_parcels <- fn_valid_cohorts(df = df_sub_parcels)
parcels_fsplit <- df_sub_parcels |> filter(eff_date_chr %in% valid_cohorts_parcels)


# 
# table(bldg_1in500$removed_pre_thisyear, bldg_1in500$year)
# table(bldg_1in500$removedfrom_prelim_sfha, bldg_1in500$year)
# table(bldg_1in500$Triad, bldg_1in500$prelim_sfha_category)

df_sub_1in500 <- bldg_1in500 |> 
  filter(change_type != "Always SFHA" & 
           # and properties that are never treated for being removed from the SFHA
           treat_year_remove_prelim == 10000 & treat_year_remove_eff == 10000)
valid_cohorts_1in500 <- fn_valid_cohorts(df = df_sub_1in500)
bldg_1in500_fsplit <- df_sub_1in500 |> filter(eff_date_chr %in% valid_cohorts_1in500)




models <- list(

  # "Buildings in SFHA" =  feols(
  #   log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
  #   fsplit = ~eff_date_chr,
  #   cluster = ~pin10,
  #   data = bldgs_fsplit
  # ),

  "Buildings in SFHA" =  feols(
    log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
    cluster = ~pin10,
    data = bldg_sfha
  ),

  "Buildings - 1-in-500" =  feols(
    log(sale_price) ~ addedto_eff_sfha | pin + year,
    fsplit = ~eff_date_chr,
    cluster = ~pin10,
    data = bldg_1in500_fsplit
  ),

  "Buildings - 1-in-500" =  feols(
    log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
    cluster = ~pin10,
    data = bldg_1in500
  )
)

all_models_formatted <- modelsummary::modelsummary(models,
                                                   output = "flextable",
                                                   fmt = function(x) round(x, 2),
                                                   
                                                   stars = TRUE)

all_models_formatted

```

## Table 11: Countywide Effective Map Dates

```{r}
eff_twfe = list(
 "I-Eff" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha
  ),

    "I-Eff Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = (bldg_sfha |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000)),

  ),

  "II-Eff" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,

  ),


  "II-Eff Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha |> filter(change_type != "Never SFHA" & treat_year_add_prelim == 10000),

  ),
 
  # Symmetric effect of location in risk zone
    "III-Eff" = feols(
    log(sale_price) ~ in_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,

  ),
  # Asymmetric: added vs removed in one equation
  "0-Eff" = feols(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_sfha,

  )
 )
all_models_formatted <- modelsummary::modelsummary(eff_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}
#| label: tbl-table11-effective-countywide
#| tbl-cap: "Table 11"




mods <- list (
 no_fe <- feols(
    log_price ~ in_eff_sfha,
    vcov = ~pin10,
    data = bldg_sfha
  ),
  
 one_fe <- feols(
    log_price ~ in_eff_sfha | sale_year,
    data = bldg_sfha,
     vcov = ~pin10
  ),
pin_fe <- feols(
    log_price ~ in_eff_sfha | pin ,
    data = bldg_sfha,
        vcov = ~pin10,
  ),
  
  two_fe <- feols(
    log_price ~ in_eff_sfha | pin + sale_year,
    data = bldg_sfha,
     vcov = ~pin10
  ),
  
  three_fe <- feols(
    log_price ~ in_eff_sfha | pin + sale_year + qtr,
    data = bldg_sfha,
     vcov = ~pin10
)
)


coef_labels = c(
  "in_prelim_sfhaTRUE" = "In SFHA (Preliminary Map)",
  "in_eff_sfhaTRUE"    = "In SFHA (Effective Map)"
)

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within"
,  coef_map = coef_labels
)
```


```{r}
#| label: table-11-effective-countywide-robustnesschecks
#| tbl-cap: "Table 11 robustness checks"
#| layout-ncol: 2
#| eval: false
#| include: false

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within",
vcov = ~clean_name
,  coef_map = coef_labels
)

modelsummary::modelsummary(
  mods,
  stars = TRUE,
 gof_omit = "IC|Log|Adj|Within",
vcov = ~nbhd_code
,  coef_map = coef_labels
)
```


## Table 12 & 13


```{r}
tbl <- readRDS("outputs/tables/grid_tbl_twfe.rds")
tbl
```


## Table 14

```{r}
tbl <- readRDS("outputs/tables/grid_tbl_etwfe.rds")
tbl
```



# Appendix A

## Table 16 & 17, and Figure 11

```{r}

out_dir <- "outputs/q2_marginaleffects"
prep_path <- file.path(out_dir, "bldg_sfha_q2_dissertation_prepped.rds")
if (!file.exists(prep_path)) {
  source("scripts/q2_dissertation_00_prep_data.R")
}

bldg_sfha <- readRDS(prep_path)

df_prep <- bldg_sfha |>
  mutate(
    pre_year = if ("pre_year" %in% names(df)) pre_year else as.integer(format(pre_date, "%Y")),
    eff_year = if ("eff_year" %in% names(df)) eff_year else as.integer(format(eff_date, "%Y")),
    event_time = sale_year - pre_year,
    event_time = ifelse(event_time == 0 & sale_date < pre_date, -1, event_time)
  )

# ----  bin leads/lags ----
df_prep <- df_prep |>
  mutate(
    event_time_binned = case_when(
      event_time <= -5 ~ -5L,
      event_time >=  5 ~  5L,
      TRUE ~ as.integer(event_time)
    )
  )

# ---- define sample + treatment (Added vs Never) ----
# Added to SFHA comparison!
df_es_add <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA")

# ---- (A) event-study regression ----
# base model, no flexible fixed effects
mod_es_add_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_add
)


# ----  plot ----
iplot(mod_es_add_none, xlab = "Years relative to map year", main = "Event Study: Added")
```


```{r}
# ---- pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_add_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ----  joint test of pre-trends ----
wald(mod_es_add_none, keep = "event_time_binned::-(5|4|3|2)")
```

## Removed from SFHA - Event Study

```{r}
# --- define sample + treatment (Removed vs Always) ----
df_es_removed <- df_prep |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA")

range(df_es_removed$sale_year, na.rm = TRUE)

# ---- event-study regression ----
mod_es_removed_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_removed
)

# ----  plot ----
iplot(mod_es_removed_none, xlab = "Years relative to map year", main = "Event Study: Removed")
```



This spec is implicitly assuming North Cook, South Cook, and Chicago share a single price trend. That assumption is false. Regional growth differences get misattributed to the flood-risk information shock.

```{r}
# ---- pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_removed_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ----  joint test of pre-trends ----
wald(mod_es_removed_none, keep = "event_time_binned::-(5|4|3|2)")

```

> Passed pre-trend test: Coefficients were not statistically significant from each other. 


## Figure 12: Local Average Treatment Effect

```{r}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = group_name_prelim, 
    cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000 &
                     # and only want to compare to properties that were Always in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Never SFHA") 
          )
  )
#mod2
emfx(mod2, type = "group")
plot(emfx(mod2), pch = c(16, 15, 18, 19))
plot(emfx(mod2, type = "event"), pch = c(16, 15, 18, 19)) 

```

```{r}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = group_name_prelim, 
    cgroup = "never",

  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_remove_prelim==10000 &
                     # and only want to compare to properties that were Never in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Always SFHA") 
          )
  )
#mod2
emfx(mod2, type = "group")
plot(emfx(mod2), pch = c(16, 15, 18, 19))
plot(emfx(mod2, type = "event"), pch = c(16, 15, 18, 19)) 


# mod2 = etwfe(
#   fml = log_price ~ 1, 
#   tvar = sale_year, 
#   ivar = pin, 
#   xvar = group_name_prelim, 
#     cgroup = "notyet",
# 
#   gvar = treat_year_add_prelim, 
#   vcov = ~pin10, 
#   data = (df_prep|> 
#             # do not want treated properties that move in opposite direction. 
#             filter(treat_year_remove_prelim==10000 &
#                      # and only want to compare to properties that were Never in the SFHA (also keeps properties that changed SFHA status), 
#                      change_type_prelim != "Always SFHA") 
#           )
#   )
# #mod2
# emfx(mod2, type = "group")
# plot(emfx(mod2), pch = c(16, 15, 18, 19))
# plot(emfx(mod2, type = "event"), pch = c(16, 15, 18, 19))
```


## Table 17: Q1 Placebo Test

**Purpose**: Estimate treatment effects in periods before any treatment occurs.

**Why**: If “effects” show up before treatment, you’ve got either model misspecification or anticipation dynamics. Either way, your core assumptions are shaky.


```{r}
#| label: tbl-appendixA-placebotest
#| 

# df_prep must have: pin, pin10, sale_date, sale_year, pre_date, prelim_sfha_category, log_price

run_placebo_did <- function(df,
                            fake_shift_years = 2,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }
  df_placebo <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label,
      placebo_date = pre_date %m-% years(fake_shift_years),
      placebo_post = sale_date >= placebo_date
    ) |>
    # keep only observations strictly before the *real* event (so placebo is truly placebo)
    filter(sale_date < pre_date) |>
    # optional: keep only observations with a defined placebo_date
    filter(!is.na(placebo_date))

  fml <- as.formula(paste0(
    "log_price ~ treated * placebo_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_placebo
  )
}


m_placebo <- run_placebo_did(bldg_sfha, treated_label = "Removed from prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)

m_placebo <- run_placebo_did(bldg_sfha, treated_label = "Added to prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)
```

```{r}
#| label: tbl-did_test_normal
#| tbl-cap: "Same set up as placebo test, but without the placebo. Includes all years of data."


run_normal_did <- function(df,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }

  df_did <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label, #== treated_label,
      treated_date = pre_date,
      event_post = (sale_date >= treated_date  & pre_date_chr != "2005-01-01")
    ) 

  fml <- as.formula(paste0(
    "log_price ~ treated * event_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_did
  )
}


normal_did_add <- run_normal_did(bldg_sfha, treated_label = "Added to prelim SFHA")
etable(normal_did_add)

normal_did_remove <- run_normal_did(bldg_sfha, treated_label = "Removed from prelim SFHA")
etable(normal_did_remove)
```


