---
title: "ETWFE Summary Tables"
format:
  html:
    code-fold: true
    toc: true
    toc-location: left
execute:
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(etwfe)
library(gt)
library(DT)
options(scipen = 999)
```

## Purpose

This file runs a common set of ETWFE models across multiple datasets and produces three summary tables:

1. Overall ATT-style summaries by dataset
2. Heterogeneity by Triad
3. Heterogeneity by cohort

This version uses `group_name_prelim` and `group_name_eff` instead of raw date variables.

## Read data

```{r read-data}
source("R/helper_pins_to_drop.R")

bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014)) |> 
   select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr, addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code, zip_code, event, change_type, change_type_prelim, Triad, clean_name, pin10, log_price, eff_date_chr, pre_date_chr,treat_year_add_eff, treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff, qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim, treated_group_eff:prelim_sfha_category)

parcel_sfha <- readRDS("data/processed/targets/sales/df_prep_land_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014)) |> 
   select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr, addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code, zip_code, event, change_type, change_type_prelim, Triad, clean_name, pin10, log_price, eff_date_chr, pre_date_chr,treat_year_add_eff, treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff, qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim, treated_group_eff:prelim_sfha_category)

bldg_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014)) |> 
   select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr, addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code, zip_code, event, change_type, change_type_prelim, Triad, clean_name, pin10, log_price, eff_date_chr, pre_date_chr,treat_year_add_eff, treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff, qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim, treated_group_eff:prelim_sfha_category)

parcel_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_land_v2026_03.RDS") |>
   filter(!pin10 %in% drop_parcels |
            (pin10 == "0113301013" & sale_year > 2014)) |> 
   select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr, addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code, zip_code, event, change_type, change_type_prelim, Triad, clean_name, pin10, log_price, eff_date_chr, pre_date_chr,treat_year_add_eff, treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff, qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim, treated_group_eff:prelim_sfha_category)

# Put whichever datasets you want into this list.
datasets <- list(
  bldg_sfha = bldg_sfha
   , parcel_sfha   = parcel_sfha
   , bldg_1in500   = bldg_1in500
   , parcel_1in500 = parcel_1in500
)

dataset_labels <- c(
  bldg_sfha     = "Buildings - SFHA",
  parcel_sfha   = "Parcels - SFHA",
  bldg_1in500   = "Buildings - 1 in 500"
  , parcel_1in500 = "Parcels - 1 in 500"
)
```


## Sample filters

```{r sample-filters}
prep_added_sample_prelim <- function(df) {
  df |>
      mutate(group_name_eff = factor(group_name_eff, levels = c("0", "2019", "2021"))) |>

    filter(
      Triad != "City" &
      treat_year_remove_prelim == 10000 &
      change_type_prelim != "Always SFHA"
    )
}

prep_removed_sample_prelim <- function(df) {
  df |>
      mutate(group_name_eff = factor(group_name_eff, levels = c("0", "2019", "2021")))|>
    filter(
            Triad != "City" &

      treat_year_add_prelim == 10000 &
        change_type_prelim != "Never SFHA"
    )
}


prep_added_sample_eff <- function(df) {
  df |>
          mutate(group_name_eff = factor(group_name_eff, levels = c("0", "2019", "2021")))|>

    filter(
            Triad != "City" &

      treat_year_remove_eff == 10000 &
      change_type != "Always SFHA"
    )
}

prep_removed_sample_eff <- function(df) {
  df |>
          mutate(group_name_eff = factor(group_name_eff, levels = c("0", "2019", "2021")))|>

    filter(
            Triad != "City" &

      treat_year_add_eff == 10000 &
        change_type != "Never SFHA"
    )
}
```

## ETWFE helpers

```{r helpers}
add_stars <- function(p) {
  case_when(
    is.na(p)      ~ "",
    p < 0.01      ~ "***",
    p < 0.05      ~ "**",
    p < 0.1       ~ "*",
    TRUE          ~ ""
  )
}


get_xvar <- function(heterogeneity, map_version) {
  case_when(
    heterogeneity == "overall" ~ NA_character_,
    heterogeneity == "triad" ~ "Triad",
    heterogeneity == "cohort" & map_version == "prelim" ~ "group_name_prelim",
    heterogeneity == "cohort" & map_version == "eff" ~ "group_name_eff",
    TRUE ~ NA_character_
  )
}

run_etwfe_model <- function(df,
                            direction = c("added", "removed"),
                            heterogeneity = c("overall", "triad", "cohort"),
                            map_version = c("prelim", "eff")) {
  direction <- match.arg(direction)
  heterogeneity <- match.arg(heterogeneity)
  map_version <- match.arg(map_version)

  df_use <- case_when(
    direction == "added" & map_version == "prelim" ~ list(prep_added_sample_prelim(df)),
    direction == "removed" & map_version == "prelim" ~ list(prep_removed_sample_prelim(df)),
    direction == "added" & map_version == "eff" ~ list(prep_added_sample_eff(df)),
    direction == "removed" & map_version == "eff" ~ list(prep_removed_sample_eff(df))
  ) |>
    purrr::pluck(1)

  gvar <- case_when(
    direction == "added" & map_version == "prelim" ~ "treat_year_add_prelim",
    direction == "removed" & map_version == "prelim" ~ "treat_year_remove_prelim",
    direction == "added" & map_version == "eff" ~ "treat_year_add_eff",
    direction == "removed" & map_version == "eff" ~ "treat_year_remove_eff"
  )

  xvar <- get_xvar(heterogeneity = heterogeneity, map_version = map_version)

  if (is.na(xvar)) {
    etwfe(
      fml = log_price ~ 1,
      tvar = sale_year,
      ivar = pin,
      cgroup = "never",
      gvar = gvar,
      vcov = ~ pin10,
      data = df_use
    )
  } else {
    etwfe(
      fml = log_price ~ 1,
      tvar = sale_year,
      ivar = pin,
      xvar = xvar,
      cgroup = "never",
      gvar = gvar,
      vcov = ~ pin10,
      data = df_use
    )
  }
}


extract_emfx <- function(model, heterogeneity) {
  out <- if (heterogeneity == "overall") {
    emfx(model)
  } else {
    emfx(model, type = "group")
  }

  out <- tibble::as_tibble(out)

  if (heterogeneity == "overall") {
    out$group_value <- "Overall"
  }

  out
}


normalize_emfx_cols <- function(df) {
  nm <- names(df)

  if (!"estimate" %in% nm) {
    est_match <- nm[stringr::str_detect(nm, stringr::regex("estimate", ignore_case = TRUE))]
    if (length(est_match) > 0) {
      df <- dplyr::rename(df, estimate = dplyr::all_of(est_match[1]))
    }
  }

  if (!"std.error" %in% names(df)) {
    se_match <- nm[stringr::str_detect(
      nm,
      stringr::regex("std\\.?error|std_error|se$", ignore_case = TRUE)
    )]
    if (length(se_match) > 0) {
      df <- dplyr::rename(df, std.error = dplyr::all_of(se_match[1]))
    }
  }

  if (!"p.value" %in% names(df)) {
    p_match <- intersect(c("p.value", "p_value", "Pr(>|t|)"), names(df))
    if (length(p_match) > 0) {
      df <- dplyr::rename(df, p.value = dplyr::all_of(p_match[1]))
    }
  }

  if (!"group_value" %in% names(df)) {
    grp_match <- intersect(c("group_value", "group", "Triad", "group_name_prelim", "group_name_eff", "xvar", "by"), names(df))
    if (length(grp_match) > 0) {
      df <- dplyr::rename(df, group_value = dplyr::all_of(grp_match[1]))
    } else {
      df <- dplyr::mutate(df, group_value = NA_character_)
    }
  }

  df |>
    dplyr::mutate(group_value = as.character(group_value))
}



fmt_est_se <- function(est, se, p, digits = 3) {
  paste0(
formatC(est, digits = 3, format = "f", flag = "0"),
    add_stars(p),
    "\n(",
formatC(se, digits = 3, format = "f", flag = "0"),
    ")"
  )
}

```

## Preliminary Model grid

```{r model-grid}
# Set map_version = "prelim" if you want the preliminary-map treatment timing.
# Switch to "eff" if you want the effective-map version instead.
map_version_to_run <- "prelim"

model_grid <- tribble(
  ~direction, ~heterogeneity,
  "added",   "overall",
  "removed", "overall",
  "added",   "triad",
  "removed", "triad",
  "added",   "cohort",
  "removed", "cohort"
)
```

## Run all models

```{r run-models}
#| eval: false

all_models <- tidyr::crossing(
  dataset_name = names(datasets),
  model_id = seq_len(nrow(model_grid))
) |>
  mutate(
    direction = model_grid$direction[model_id],
    heterogeneity = model_grid$heterogeneity[model_id],
     n_obs_raw = purrr::map_int(dataset_name, ~nrow(datasets[[.x]])),
    n_pin_raw = purrr::map_int(dataset_name, ~dplyr::n_distinct(datasets[[.x]]$pin)),
  
    model = purrr::pmap(
      list(dataset_name, direction, heterogeneity),
      function(dataset_name, direction, heterogeneity) {
        run_etwfe_model(
          df = datasets[[dataset_name]],
          direction = direction,
          heterogeneity = heterogeneity,
          map_version = map_version_to_run
        )
      }
    ),
    results = purrr::map2(model, heterogeneity, extract_emfx),
    results = purrr::map(results, normalize_emfx_cols)
    )

saveRDS(all_models, "outputs/q1_all_models_prelim_etwfe_noChicago.RDS", compress = FALSE)
```


```{r readin-models}
all_models <- readRDS("outputs/q1_all_models_prelim_etwfe_noChicago.RDS")


#all_models <- readRDS("outputs/q1_all_models_prelim_etwfe.RDS")

```

## Build one long results object

```{r tidy-results}
all_results <- all_models |>
  select(dataset_name, direction, heterogeneity, results) |>
  unnest(results) |>
  mutate(
    dataset_label = recode(dataset_name, !!!dataset_labels),
    direction_label = recode(
      direction,
      added = "Added",
      removed = "Removed"
    ),
cell = fmt_est_se(estimate, std.error, p.value)  )

num_cols <- all_results |>
  select(where(is.numeric)) |>
  names()

all_results |> select(-c(term)) |> 
  mutate(p.value = round(p.value, digits = 3)) |>
  DT::datatable(rownames = FALSE) |>
  DT::formatRound(columns = num_cols, digits = 3)

```

## Table 1: overall ATT-style summaries

```{r tbl-overall}
table1_df <- all_results |>
  filter(heterogeneity == "overall") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - County",
      removed = "Removed - County"
    )
  ) |>
  select(dataset_label, direction_label, cell) |>
#  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(factor(dataset_label, levels = unname(dataset_labels)))

table1_df |>
  gt() |>
  tab_header(
    title = md("**Table 1. Overall ATT-style summaries**")
  )
```

## Table 2: heterogeneity by Triad

```{r tbl-triad}
table2_df <- all_results |>
  filter(heterogeneity == "triad") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Triad",
      removed = "Removed - Triad"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table2_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Triad") |>
  tab_header(
    title = md("**Table 2. Heterogeneity by Triad**")
  )


table2_df <- all_results |>
  filter(heterogeneity == "triad") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Triad",
      removed = "Removed - Triad"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  # distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table2_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Triad") |>
  tab_header(
    title = md("**Table 2. Heterogeneity by Triad**")
  )
```

## Table 3: heterogeneity by cohort

```{r tbl-cohort}
table3_df <- all_results |>
  filter(heterogeneity == "cohort") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Cohort",
      removed = "Removed - Cohort"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table3_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Cohort") |>
  tab_header(
    title = md("**Table 3. Heterogeneity by cohort**")
  )
```


# Effective Models

## Effective Model grid

```{r model-grid-eff}
# Set map_version = "prelim" if you want the preliminary-map treatment timing.
# Switch to "eff" if you want the effective-map version instead.
map_version_to_run <- "eff"

model_grid <- tribble(
  ~direction, ~heterogeneity,
  "added",   "overall",
  "removed", "overall",
  "added",   "triad",
  "removed", "triad",
  "added",   "cohort",
  "removed", "cohort"
)
```

## Run all models

```{r run-models-eff}
#| eval: false


all_models_eff <- tidyr::crossing( 
  dataset_name = names(datasets),
  model_id = seq_len(nrow(model_grid))
) |>
  mutate(
    direction = model_grid$direction[model_id],
    heterogeneity = model_grid$heterogeneity[model_id],
     n_obs_raw = purrr::map_int(dataset_name, ~nrow(datasets[[.x]])),
    n_pin_raw = purrr::map_int(dataset_name, ~dplyr::n_distinct(datasets[[.x]]$pin)),
  
    model = purrr::pmap(
      list(dataset_name, direction, heterogeneity),
      function(dataset_name, direction, heterogeneity) {
        run_etwfe_model(
          df = datasets[[dataset_name]],
          direction = direction,
          heterogeneity = heterogeneity,
          map_version = map_version_to_run
        )
      }
    ),
    results = purrr::map2(model, heterogeneity, extract_emfx),
    results = purrr::map(results, normalize_emfx_cols)
    )

saveRDS(all_models_eff, "outputs/q1_all_models_eff_etwfe_noChicago.RDS", compress = FALSE)

```

## Build one long results object


```{r tidy-results-eff}
all_models_eff <- readRDS("outputs/q1_all_models_eff_etwfe.RDS")

all_models_eff <- readRDS("outputs/q1_all_models_eff_etwfe_noChicago.RDS")

all_results <- all_models_eff |>
  select(dataset_name, direction, heterogeneity, results) |>
  unnest(results) |>
 
  mutate(
    dataset_label = recode(dataset_name, !!!dataset_labels),
    direction_label = recode(
      direction,
      added = "Added",
      removed = "Removed"
    ),
cell = fmt_est_se(estimate, std.error, p.value)  )

num_cols <- all_results |>
  select(where(is.numeric)) |>
  names()

all_results|>  
  mutate(p.value = round(p.value, digits = 3)) |>
  DT::datatable(rownames = FALSE) |>
  DT::formatRound(columns = num_cols, digits = 3)

```


## Table 4: Effective overall ATT-style summaries

```{r tbl-overall-eff}
table1_df <- all_results |>
  filter(heterogeneity == "overall") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - County",
      removed = "Removed - County"
    )
  ) |>
  select(dataset_label, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(factor(dataset_label, levels = unname(dataset_labels)))

table1_df |>
  gt() |>
  tab_header(
    title = md("**Table 4. Overall ATT-style summaries**")
  )  |>
  tab_options(
    data_row.padding = px(8),
    column_labels.padding = px(10)
  ) |>
  tab_source_note(
    source_note = md("*p* < 0.1, **p** < 0.05, ***p*** < 0.01")
  )
```

## Table 5: Effective heterogeneity by Triad

```{r tbl-triad-eff}
table2_df <- all_results|>
  filter(heterogeneity == "triad") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Triad",
      removed = "Removed - Triad"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table2_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Triad") |>
  tab_header(
    title = md("**Table 5. Heterogeneity by Triad**")
  )  |>
  tab_options(
    data_row.padding = px(8),
    column_labels.padding = px(10)
  )|>
  tab_source_note(
    source_note = md("*p* < 0.1, **p** < 0.05, ***p*** < 0.01")
  )
```

## Table 6: heterogeneity by cohort

```{r tbl-cohort-eff}
table3_df <- all_results |>
  filter(heterogeneity == "cohort") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Cohort",
      removed = "Removed - Cohort"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table3_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Cohort") |>
  tab_header(
    title = md("**Table 6. Heterogeneity by cohort**")
  )|>
  tab_source_note(
    source_note = md("*p* < 0.1, **p** < 0.05, ***p*** < 0.01")
  )
```



## Optional diagnostics


## Notes

- Right now the removed-sample logic uses the more restrictive comparison group:
  - for preliminary maps: `treat_year_add_prelim == 10000 & change_type_prelim != "Never SFHA"`
  - for effective maps: `treat_year_add_eff == 10000 & change_type != "Never SFHA"`
- If you want the larger removed-sample comparison group instead, change `prep_removed_sample_prelim_nofilt()` and `prep_removed_sample_eff_nofilt()`.  
- inspect `all_results` once after the first run to check column names
