---
title: "ETWFE Summary Tables"
format:
  html:
    code-fold: true
    toc: true
    toc-location: left
execute:
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(etwfe)
library(gt)
options(scipen = 999)
```

## Purpose

This file runs a common set of ETWFE models across multiple datasets and produces three summary tables:

1. Overall ATT-style summaries by dataset
2. Heterogeneity by Triad
3. Heterogeneity by cohort

This version uses `group_name_prelim` and `group_name_eff` instead of raw date variables.

## Read data

```{r read-data}
source("R/helper_pins_to_drop.R")

bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014))

# Uncomment and edit these as needed.
parcel_sfha <- readRDS("data/processed/targets/sales/df_prep_land_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014))

bldg_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014))

 parcel_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_land_v2026_03.RDS") |>
   filter(!pin10 %in% drop_parcels |
            (pin10 == "0113301013" & sale_year > 2014))

# Put whichever datasets you want into this list.
datasets <- list(
  bldg_sfha = bldg_sfha
   , parcel_sfha   = parcel_sfha
   , bldg_1in500   = bldg_1in500
   , parcel_1in500 = parcel_1in500
)

dataset_labels <- c(
  bldg_sfha     = "Buildings - SFHA",
  parcel_sfha   = "Parcels - SFHA",
  bldg_1in500   = "Buildings - 1 in 500",
  parcel_1in500 = "Parcels - 1 in 500"
)
```


## Sample filters

```{r sample-filters}
prep_added_sample_prelim <- function(df) {
  df |>
    filter(
      treat_year_remove_prelim == 10000 &
      change_type_prelim != "Always SFHA"
    )
}

prep_removed_sample_prelim <- function(df) {
  df |>
    filter(
      treat_year_add_prelim == 10000 &
        change_type_prelim != "Never SFHA"
    )
}

prep_removed_sample_prelim_nofilt <- function(df) {
  df |>
    filter(
      treat_year_add_prelim == 10000 
    )
}

prep_added_sample_eff <- function(df) {
  df |>
    filter(
      treat_year_remove_eff == 10000 &
      change_type != "Always SFHA"
    )
}

prep_added_sample_eff_nofilt <- function(df) {
  df |>
    filter(
      treat_year_remove_eff == 10000)
}

prep_removed_sample_eff <- function(df) {
  df |>
    filter(
      treat_year_add_eff == 10000 &
        change_type != "Never SFHA"
    )
}
```

## ETWFE helpers

```{r helpers}
get_xvar <- function(heterogeneity, map_version) {
  case_when(
    heterogeneity == "overall" ~ NA_character_,
    heterogeneity == "triad" ~ "Triad",
    heterogeneity == "cohort" & map_version == "prelim" ~ "group_name_prelim",
    heterogeneity == "cohort" & map_version == "eff" ~ "group_name_eff",
    TRUE ~ NA_character_
  )
}

run_etwfe_model <- function(df,
                            direction = c("added", "removed"),
                            heterogeneity = c("overall", "triad", "cohort"),
                            map_version = c("prelim", "eff")) {
  direction <- match.arg(direction)
  heterogeneity <- match.arg(heterogeneity)
  map_version <- match.arg(map_version)

  df_use <- case_when(
    direction == "added" & map_version == "prelim" ~ list(prep_added_sample_prelim(df)),
    direction == "removed" & map_version == "prelim" ~ list(prep_removed_sample_prelim(df)),
    direction == "added" & map_version == "eff" ~ list(prep_added_sample_eff(df)),
    direction == "removed" & map_version == "eff" ~ list(prep_removed_sample_eff(df))
  ) |>
    purrr::pluck(1)

  gvar <- case_when(
    direction == "added" & map_version == "prelim" ~ "treat_year_add_prelim",
    direction == "removed" & map_version == "prelim" ~ "treat_year_remove_prelim",
    direction == "added" & map_version == "eff" ~ "treat_year_add_eff",
    direction == "removed" & map_version == "eff" ~ "treat_year_remove_eff"
  )

  xvar <- get_xvar(heterogeneity = heterogeneity, map_version = map_version)

  if (is.na(xvar)) {
    etwfe(
      fml = log_price ~ 1,
      tvar = sale_year,
      ivar = pin,
      cgroup = "never",
      gvar = gvar,
      vcov = ~ pin10,
      data = df_use
    )
  } else {
    etwfe(
      fml = log_price ~ 1,
      tvar = sale_year,
      ivar = pin,
      xvar = xvar,
      cgroup = "never",
      gvar = gvar,
      vcov = ~ pin10,
      data = df_use
    )
  }
}

extract_emfx <- function(model, heterogeneity) {
  if (heterogeneity == "overall") {
    out <- emfx(model)
  } else {
    out <- emfx(model, type = "group")
  }

  out |>
    as_tibble()
}

normalize_emfx_cols <- function(df) {
  nm <- names(df)

  if (!"estimate" %in% nm) {
    est_match <- nm[str_detect(nm, regex("estimate", ignore_case = TRUE))]
    if (length(est_match) > 0) df <- df |> rename(estimate = all_of(est_match[1]))
  }

  if (!"std.error" %in% nm) {
    se_match <- nm[str_detect(nm, regex("std\\.?error|std_error|se$", ignore_case = TRUE))]
    if (length(se_match) > 0) df <- df |> rename(std.error = all_of(se_match[1]))
  }

  if (!"group_value" %in% names(df)) {
    grp_candidates <- c("group", "Triad", "group_name_prelim", "group_name_eff", "xvar")
    grp_match <- grp_candidates[grp_candidates %in% names(df)]
    if (length(grp_match) > 0) {
      df <- df |> rename(group_value = all_of(grp_match[1]))
    }
  }

  df
}

fmt_est_se <- function(est, se, digits = 3) {
  ifelse(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = digits, format = "f"),
      "\n(",
      formatC(se, digits = digits, format = "f"),
      ")"
    )
  )
}
```

## Model grid

```{r model-grid}
# Set map_version = "prelim" if you want the preliminary-map treatment timing.
# Switch to "eff" if you want the effective-map version instead.
map_version_to_run <- "prelim"

model_grid <- tribble(
  ~direction, ~heterogeneity,
  "added",   "overall",
  "removed", "overall",
  "added",   "triad",
  "removed", "triad",
  "added",   "cohort",
  "removed", "cohort"
)
```

## Run all models

```{r run-models}
all_models <- tidyr::crossing(
  dataset_name = names(datasets),
  model_id = seq_len(nrow(model_grid))
) |>
  mutate(
    dataset = datasets[dataset_name],
    direction = model_grid$direction[model_id],
    heterogeneity = model_grid$heterogeneity[model_id],
    model = purrr::pmap(
      list(dataset, direction, heterogeneity),
      function(dataset, direction, heterogeneity) {
        run_etwfe_model(
          df = dataset,
          direction = direction,
          heterogeneity = heterogeneity,
          map_version = map_version_to_run
        )
      }
    ),
    results = purrr::map2(model, heterogeneity, extract_emfx),
    results = purrr::map(results, normalize_emfx_cols)
  )
```

## Build one long results object

```{r tidy-results}
all_results <- all_models |>
  select(dataset_name, direction, heterogeneity, results) |>
  unnest(results) |>
  mutate(
    dataset_label = recode(dataset_name, !!!dataset_labels),
    direction_label = recode(
      direction,
      added = "Added",
      removed = "Removed"
    ),
    cell = fmt_est_se(estimate, std.error)
  )

all_results |> DT::datatable(rownames = FALSE)
```

## Table 1: overall ATT-style summaries

```{r tbl-overall}
table1_df <- all_results |>
  filter(heterogeneity == "overall") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - County",
      removed = "Removed - County"
    )
  ) |>
  select(dataset_label, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(factor(dataset_label, levels = unname(dataset_labels)))

table1_df |>
  gt() |>
  tab_header(
    title = md("**Table 1. Overall ATT-style summaries**")
  )
```

## Table 2: heterogeneity by Triad

```{r tbl-triad}
table2_df <- all_results |>
  filter(heterogeneity == "triad") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Triad",
      removed = "Removed - Triad"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table2_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Triad") |>
  tab_header(
    title = md("**Table 2. Heterogeneity by Triad**")
  )
```

## Table 3: heterogeneity by cohort

```{r tbl-cohort}
table3_df <- all_results |>
  filter(heterogeneity == "cohort") |>
  mutate(
    direction_label = recode(
      direction,
      added = "Added - Cohort",
      removed = "Removed - Cohort"
    )
  ) |>
  select(dataset_label, group_value, direction_label, cell) |>
  distinct() |>
  pivot_wider(
    names_from = direction_label,
    values_from = cell
  ) |>
  arrange(
    factor(dataset_label, levels = unname(dataset_labels)),
    group_value
  )

table3_df |>
  gt(groupname_col = "dataset_label") |>
  cols_label(group_value = "Cohort") |>
  tab_header(
    title = md("**Table 3. Heterogeneity by cohort**")
  )
```

## Optional diagnostics


## Notes

- Right now the removed-sample logic uses the more restrictive comparison group:
  - for preliminary maps: `treat_year_add_prelim == 10000 & change_type_prelim != "Never SFHA"`
  - for effective maps: `treat_year_add_eff == 10000 & change_type != "Never SFHA"`
- If you want the larger removed-sample comparison group instead, change `prep_removed_sample_prelim_nofilt()` and `prep_removed_sample_eff_nofilt()`.  
- inspect `all_results` once after the first run to check column names
