---
title: "Extended TWFE Models"
format: 
  html: 
    code-fold: true
    toc: true
    toc-location: left
---

# Setup

```{r setup}
library(tidyverse)
library(fixest)

library(didFF)   # for testing if functional form matters for the analysis. Tests if parallel trends assumption is sensitive to functional form (i.e. logged variable vs unlogged variable)
library(did)  # for step 3 and 4
library(etwfe)
options(scipen = 999)
```





```{r}
bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS")

#parcels <- readRDS("data/processed/targets/sales/df_prep_land_v2026_03.RDS")

# bldg_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_v2026_03.RDS") # |>
#   filter(!pin10 %in% drop_parcels  |
#                (pin10 == "0113301013" & sale_year > 2014))

# bldg_sfha <- readRDS("data/processed/targets/sales/allsales_bldg_v2026_03.RDS")

df_prep <- bldg_sfha
#df_prep <- bldg_1in500


source("R/helper_pins_to_drop.R")

df_prep <- df_prep |> filter(!pin10 %in% drop_parcels  |          
               (pin10 == "0113301013" & sale_year > 2014)
             ) |>
  mutate(group_name_eff = factor(group_name_eff, levels = c("0", "2019", "2021")))


table(df_prep$change_type)
table(df_prep$change_type_prelim)

table(df_prep$pre_date)
table(df_prep$prelim_sfha_category)
table(df_prep$group_name_prelim)

table(df_prep$group_name_eff)
class(df_prep$group_name_eff)
```



Optional interacted categorical covariate for estimating heterogeneous treatment effects. Enables recovery of the marginal treatment effect for distinct levels of xvar, e.g. "child", "teenager", or "adult". Note that the "x" prefix in "xvar" represents a covariate that is interacted with treatment, as opposed to a regular control variable.


```{r}

make_control_groups <- function(df, 
                                ever_added,
                                ever_removed,
                    pre_eff_change_type, 
                    type = c("pre", "eff")
                                ){
  
  # Treated Group A: Added to Risk Zone
  group_T_A <- df |>
    filter( {{ever_added}} == TRUE )
  
  # Treated Group B: Removed from Risk Zone
  group_T_B <- df |> 
      filter( {{ever_removed}}  == TRUE)

  # Control Group A:  Never in SFHA, FIRM panels never updated
    
   if(type == "pre"){
   group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
             pre_date_chr %in% c("2005-01-01")
         )
  }else if(type == "eff"){  # for effective maps
  group_C_A <- df |> 
      filter(
        {{pre_eff_change_type}} == "Never SFHA" &
         eff_date_chr %in% c("2008-08-19") 
         ) 
  }  

    # Control Group B: Never in SFHA, FIRM Panels are updated
    group_C_B  <- df |> 
      filter( 
        {{pre_eff_change_type}} == "Never SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
         )

    # Control Group C: Always in SFHA, FIRM Panels are not updated 
    if(type == "pre"){
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &             
          pre_date_chr %in% c("2005-01-01")
      )}
    else if(type == "eff") {  # this probably is tainted by prelim map cohort in 2021 though....
    group_C_C <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") )
      )
    
    group_C_C_alt <- df |> 
      filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2008-08-19") | 
            pre_date_chr %in% c("2005-01-01")
          )
      )
    }
    
    # Always in SFHA but FIRM panels have been recently updated
   
    if(type == "eff") {
      group_C_D <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10"))
         )
      
       group_C_D_alt <- df |> 
        filter(
        {{pre_eff_change_type}} == "Always SFHA" &
         (eff_date_chr %in% c("2019-11-01", "2021-09-10") | 
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
             )
         )
    } else if (type == "pre") {
      group_C_D <- df |> 
         filter(
        {{pre_eff_change_type}} == "Always SFHA" &
             pre_date_chr %in% c("2015-02-12", "2019-07-01", "2021-09-22")
         )
    }
      list(
    group_T_A = group_T_A,
    group_T_B = group_T_B,
    group_C_A = group_C_A,
    group_C_B = group_C_B,
    group_C_C = group_C_C,
    group_C_D = group_C_D

  )

}

groups <- make_control_groups(df = bldg_sfha, 
                    ever_added = ever_added_prelim, 
                    ever_removed = ever_removed_prelim, 
                    pre_eff_change_type = change_type_prelim, 
                    type = "pre")

groups_long <- imap_dfr(groups, ~ {
  .x |>
    mutate(group = .y)
})

groups_long |>
  group_by(group) |>
  summarise(
    n = n(),
    n_properties = n_distinct(pin),
    mean_price = mean(sale_price, na.rm = TRUE),
    mean_log_price = mean(log_price, na.rm = TRUE)
  )
```

# Added to Risk Zone

```{r}
#| label: tbl-etwfe-addedtozone-county

mod1b = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
 # xvar = group_name_prelim,
  gvar = treat_year_add_prelim, 
 gref = 10000,
 window = 5,
  vcov = ~pin10, 
  data = (df_prep|> 
            filter(treat_year_remove_prelim==10000
                   & change_type_prelim != "Always SFHA"
                 )
          )
  )

# mod1b


emfx(mod1b)


emfx(mod1b, type = "group")
plot(emfx(mod1b))
plot(emfx(mod1b, type = "event"))

```



```{r}
#| label: tbl-etwfe-addedtozone-filtered
#| tbl-cap: "**Added to Risk Zone** Excludes Properties that were Always in the SFHA or were removed from the SFHA from the comparison group."

mod1c = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = Triad, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            filter(treat_year_remove_prelim==10000
                   & change_type_prelim != "Always SFHA"
                 )
          )
  )

mod1c


emfx(mod1c)


emfx(mod1c, type = "group")
plot(emfx(mod1c))
plot(emfx(mod1c, type = "event"))

```


```{r}
#| label: tbl-etwfe-addedtozone-bycohort-filtered
#| tbl-cap: "**Added to Risk Zone** Excludes Properties that were Always in the SFHA or were removed from the SFHA from the comparison group."

mod1d = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = group_name_prelim, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            filter(treat_year_remove_prelim==10000
                   & change_type_prelim != "Always SFHA"
                 )
          )
  )

mod1d


emfx(mod1d)


emfx(mod1d, type = "group")
plot(emfx(mod1d))
plot(emfx(mod1d, type = "event"))

```

if not treated, then treat_year_remove_prelim == 0


# Removed from Risk Zone 

```{r}
#| label: tbl-etwfe-countywide-removedfromzone-filtered
#| tbl-cap: "**County-wide: Removed from Risk Zone** Excludes properties that were added to the SFHA or were never in the SFHA from the comparison group. By Triad."

mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000 &
                     # and only want to compare to properties that were Always in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Never SFHA"
                  ) 
          )
  )
mod2
emfx(mod2)
emfx(mod2, type = "group")
plot(emfx(mod2))
plot(emfx(mod2, type = "event"))


```

```{r}
#| tbl-cap: "**County-wide by muni: Removed from Risk Zone** Excludes properties that were added to the SFHA or were never in the SFHA from the comparison group. By Triad."

mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  cgroup = "never",
  xvar = FIRM_PAN,
  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep)
  )

mod2
emfx(mod2)
emfx(mod2, type = "group")
plot(emfx(mod2))
plot(emfx(mod2, type = "event"))


```

```{r}
#| label: tbl-etwfe-removedfromzone-filtered
#| tbl-cap: "**Removed from Risk Zone** Excludes properties that were added to the SFHA or were never in the SFHA from the comparison group. By Triad."

mod2b = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = Triad, 
  cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000 &
                     # and only want to compare to properties that were Always in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Never SFHA"
                  ) 
          )
  )
mod2b
emfx(mod2b)
emfx(mod2b, type = "group")
plot(emfx(mod2b))
plot(emfx(mod2b, type = "event"))


```

```{r}
#| label: tbl-etwfe-removedfromzone-bycohort-filtered
#| tbl-cap: "**Removed from Risk Zone** Excludes properties that were added to the SFHA or were never in the SFHA from the comparison group. By cohort."

mod3_data <- (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000 &
                     # and only want to compare to properties that were Always in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Never SFHA"
                  ) 
          )

mod2c = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = group_name_prelim, 
  cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = mod3_data
  )
mod2c
emfx(mod2c)
emfx(mod2c, type = "group")
plot(emfx(mod2c))
plot(emfx(mod2c, type = "event"))


```

### Not filtered: Includes properties Never in SFHA in control group

```{r}
#| label: tbl-etwfe-removedfromzone-bycohort
#| tbl-cap: "**Removed from Risk Zone** Excludes Properties that were added to the SFHA from the comparison group. By Cohort. Still includes properties that were never in the SFHA to increase comparison group sample size. (Pretty sure never treated properties, aka both never in sfha and always in sfha, had parallel trends overall so you can combine them as a comparison group. I just didn't want to.)"


mod2d = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = group_name_prelim, 
  cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000
                  ) 
          )
  )
mod2d
#emfx(mod2d)
emfx(mod2d, type = "group")
plot(emfx(mod2d))
plot(emfx(mod2d, type = "event"))


```


