---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    tbl-cap-location: top
    fig-cap-location: top
---


# Data Prep

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

Parcel shapefile used in ArcGIS Pro is downloaded from CCAO's Archived 2022 parcel dataset [here.](https://datacatalog.cookcountyil.gov/Property-Taxation/ccgisdata-Parcel-2021/77tz-riq7/about_data)

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
```


```{r codein-data_prep-rscript}
# sales <- read_csv("./data/raw/Assessor_Parcel_Sales_20250105.csv") %>% 
#   filter(year > 2005) %>%
#   
#   mutate(class_1dig = str_sub(class, 1, 1),
#          class = as.numeric(class)) |>
#   # filter(class > 199 & class < 1000) |>
#   mutate(date = lubridate::mdy(sale_date)) # |>
#   #group_by(year, class_1dig)|>
#   #mutate(sale_price = Winsorize(sale_price, quantile(sale_price, probs = c(0.03, 0.97), na.rm=FALSE) )) |>
#  # ungroup() 
# 
# firms <- read_csv("./data/processed/parcels_wFIRMS.csv")
# 
# # add flood variables to sales data
# sales <- sales |> 
#     mutate(pin10 = str_sub(pin, 1, 10)) |>
#   left_join(firms, by = "pin10")
# 
# sales <- sales |>   
#   mutate(Location = ifelse(pin10 %in% firms$pin10, "In FP", "Outside FP" )) 
# 
# sfha_ind <- read_csv("./data/processed/sfha_indicator_pins.csv")
# sfha_ind <- sfha_ind |> select(pin, sfha2018:lomr2024)
# 
# sales <- sales |> left_join(sfha_ind, by ="pin")
# 
# sales <- sales |>
#   mutate(class = as.character(class),
#          lomr2024 = as.character(lomr2024),
#          sfha2024 = as.character(sfha2024)) 
# 
# 
# lomrs <- read_csv("./data/processed/lomr_pins_2024.csv") |>
#   rename(lomr_eff = EFF_DAT,
#          lomr_dfirm_id = DFIRM_I) |>
#   mutate(lomr_eff = as_date(lomr_eff))
# 
# sales <- sales |>
#   mutate(
#     prelim_date = ifelse(PRE_DATE == "9999-09-09" | is.na(PRE_DATE), "2005-01-01", PRE_DATE),
#     
#     ccao_sfha = ifelse(sfha2024 == 1 & year >= 2021, "SFHA", "Not SFHA"),
#     ccao_sfha = ifelse(is.na(ccao_sfha), "Not SFHA", ccao_sfha),
#     
#     # the flood zones that existed in the 2018 state NFHL were last updated in 2008. sfha2018 is the default SFHA status for the observations, then lomrs and future updates will be incorporated
#     in_eff_sfha = ifelse(sfha2018 == 1, "In SFHA", "Not in SFHA"),
#     
#     in_eff_sfha = ifelse(sfha2024 == 1 & year >= year(EFF_DATE), "In SFHA", 
#                          ifelse(year >= year(EFF_DATE) & sfha2024 == 0, "Not in SFHA", in_eff_sfha)),
#     
#     in_eff_sfha = ifelse((sfha2018 == 0 & sfha2024 == 0 ) | (is.na(sfha2018) & is.na(sfha2024)) , "Not in SFHA", in_eff_sfha))
# 
# table(sales$year, sales$in_eff_sfha)
# 
# 
# sales <- sales |>
#   left_join(lomrs, by = c("pin")) |>
#   mutate(
#     in_lomr = ifelse(year >= year(lomr_eff) & !is.na(LOMR_ID), "In LOMR", "Not in LOMR") ,
#     in_prelim_sfha = ifelse(year >= as_date(prelim_date), "1", "0"),
#       ) |>
#   
#   # do I want this line of code? LOMRs don't remove you from the "risky" area, but they do indicate that property was either mitigated or on higher ground and results in removal of flood insurance requirement
#   # if in SFHA and in a LOMR, keep both variables as 1 instead of recoding in_eff_sfha to 0?
#   mutate(in_eff_sfha = ifelse(in_eff_sfha == 1 & in_lomr == 1, in_eff_sfha == 0, in_eff_sfha))
```

> Coding note: sale_price can be winsorized by grouping the year & major class (technically the 1st digit of the class code). Check that this is how you want it to be winsorized. It is currenty commented out and NOT WINSORIZED.

> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. 


# Sales Data

1,762,627 sales for all property classes (1,869,796 after new download in January)

1,070,348 sales for Class 2 Residential properties (1,655,745 after new download and identifying any pin that was residential at any point in time and including it)


> TO DO: Use grepl() to identify properties bought by municipalities? list of Muni names and if they are similar to the buyer name? Useful for flagging buyouts?


# Frequency of Sales

`res_sales` includes any pin that was residential at some point in time. 

 
```{r}
#sales      <- readRDS("./data/processed/sales_prepped.rds")
res_sales  <- readRDS("./data/processed/res_sales.rds") 


# sampled_data <- res_sales |> 
#   sample_frac(0.05)
# write_csv(sampled_data, 
#           "data_sample.csv")

```


**Are there condos in floodplains?** -- Yes. and "297s are special residential improvements" 

```{r}
res_sales |> 
  filter(in_eff_sfha == "SFHA") |>
  filter(class %in% c(297, 298, 299))
```

**Are there CoOps and other weird properties in floodplains?** -- NO, filter these property classes out and don't worry about them.

```{r}
table(res_sales$in_eff_sfha)

```


```{r}

repeat_sales <- res_sales |> group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup()
  
table(repeat_sales$times_sold)

table(res_sales$PRE_DATE)

table(res_sales$year, res_sales$in_eff_sfha)
table(res_sales$year, res_sales$in_lomr)

#res_sales |> group_by(pin, sale_date) |> n_distinct()
```

```{r inspect-highmultisales, include=FALSE}

# price corrections randomly spotted
res_sales <- res_sales |> 
  mutate(sale_price = 
         case_when(
           pin == "15154220240000" ~ 180000,   # not 180 million
         TRUE ~ sale_price
         ))


# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N LAkeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000"     # another CoOp
               
)

res_sales |> filter(times_sold > 5) |> arrange(desc(sale_price))

res_sales |> filter(times_sold > 5) |>  filter(pin %nin% drop_pins) |> arrange(desc(sale_price))

res_sales |> filter(num_parcels_sale > 10) |> arrange(pin, desc(num_parcels_sale)) |>
  select(pin, year, num_parcels_sale, sale_price, in_eff_sfha, class, everything())

res_sales |> filter(times_sold > 5) |> 
  ggplot() + 
  geom_line(aes(x=sale_date, y = sale_price, group = pin))
```


```{r}
#| label: fig-pinsales
#| fig-cap: "PIN Sale Price Over time."
#| fig-subcap: 
#| - pin == 09163040191019. Flood Factor 6/10 & in SFHA. 1675 E Mills St. Des Plaines IL. Condo building.
#| - pin == 05201210150000. Flood Factor 6/10 & in SFHA. 1103 Willow Rd Winnetka. (Side note, this is in New Trier Township, if worried about Assessor's timing of using the flood zone variables in assessment models). Class 207 for first sale and then class 205 for later sales.
#| - pin == 09281140060000. Flood Factor 5/10 and in SFHA.  1918 Kennicott Ct Des Plaines. Class 205.
#| layout-ncol: 3
#| include: false


res_sales %>% 
  filter(pin == "09163040191019") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price))



res_sales %>% 
  filter(pin == "05201210150000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price))



res_sales %>% 
  filter(pin == "09281140060000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) 


```


## Sales in and Out of FEMA SFHAs

```{r}

res_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Sales") |>
  mutate(
    Year = as.character(year),
    TotalSales = `In FP` + `Outside FP`,
    `FP Share (%)` = `In FP` / TotalSales,
   `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)) |>
  select(-c(TotalSales, year)) |> 
  mutate(Year = as.character(Year), .before = `In FP`) |> 
  select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |>
  flextable::flextable()


res_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  # ungroup() |>
   pivot_wider(names_from = "Location", values_from = "Sales") |>
   mutate(
     TotalSales = `In FP` + `Outside FP`,
     `FP Share (%)` = `In FP` / TotalSales,
     # `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)
   ) |>
  # select(-c(TotalSales, year)) |> 
  # mutate(Year = as.character(Year), .before = `In FP`) |> 
  # select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |> 
  ggplot() +
  geom_line(aes(x=year, y= `FP Share (%)`)) + 
  scale_y_continuous(limits = c(0, 0.06), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Flood Plain Properties make up less than 1.5% of Sales",
       x = element_blank(),
       y = "Share of Sales")
```

```{r}
res_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
   Ratio =  scales::percent(Ratio, accuracy = 0.01),
   Year = as.character(year)) |> 
  select(Year, Sales, `In FP`, `Outside FP`, Ratio) |>
  flextable::flextable()

res_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
  # Ratio =  scales::percent(Ratio, accuracy = 0.01)
   ) |>
  ggplot() +
  geom_line(aes(x=year, y = Ratio)) +
  scale_y_continuous(limits = c(0, 1), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Ratio of Median Value for Properties In and Out of Floodplain",
       x = element_blank(),
       y = "Ratio",
       caption = "Ratio = Median Sale Price in FP / Median Price outside FP") 
```



# Research Question 1 

**Does the value of real estate parcels increase when they are removed from an SFHA?** 

H1: A property removed from a SFHA will increase in value, compared to properties with otherwise shared characteristics.

## Repeat Sales

To investigate whether the value of real estate parcels increases when they are removed from a Special Flood Hazard Area (SFHA), I used a repeat-sales analysis. This approach compares the change in sales price of the same property over time, allowing me to control for fixed, unobservable characteristics of each parcel.

The dataset was first prepared by filtering out irrelevant parcels and ensuring that each property had at least two recorded sales. For each parcel, I paired consecutive sales and calculated the log change in price between sales (i.e., d_log_price), which serves as the dependent variable in the regression models. I also recorded whether the parcel was in or out of an SFHA at each sale, identifying cases where the floodplain status changed.

Additional variables were constructed to measure the timing of sales relative to the date a new Flood Insurance Rate Map (FIRM) took effect, allowing me to distinguish between sales occurring before and after floodplain reclassification. The time between sales was measured in both months and years.

Several regression models were estimated using the feols() function from the fixest package. 

These models tested whether being removed from the SFHA is associated with a statistically significant increase in log sale price, controlling for time between sales. I also explored interaction terms with LOMR status (since people can appeal their flood zone designation and have the map altered. This results in them no longer having mandatory flood insurance if their appeal is accepted) and included alternative specifications, such as directly including binary indicators for whether a parcel was added or removed from an SFHA. All models clustered standard errors at the parcel (PIN) level to account for repeated observations of the same property.

This repeat-sales framework is well-suited to estimating the capitalization effect of flood risk removal, since it isolates within-parcel price changes and reduces bias from time-invariant confounding factors.


Notes:

1. Removal from the SFHA is due to the FEMA flood insurance rate maps being updated. Properties are either in or out of the "1-in-100" year flood plain. They can be located in the SFHA and also have a LOMR that "removes" them from the floodplain. This information is represented in multiple variables (`in_eff_sfha` and `in_lomr`). If an observation is coded as `Removed` from an SFHA, it indicates that the floodplain shapefile itself changed that was created by FEMA. If a FIRM is updated and the property previously had a LOMR and FEMA finds that the LOMR still is good. 

- If a property was in an SFHA in a FIRM and had an approved LOMR and then the FIRM is updated years later and the LOMR was still viewed as accurate and valid, then the PIN will appear as "removed from the SFHA" becauese the updated FIRM will incorporate the old LOMR into the updated floodplain.   

2. Treatment window timing: In theory, EFF_DATE would be associated with a change in price due to the capitalization of mandatory flood insurance requirement for homes that have mortgages in floodplains. The knowledge of the risk and the potential loss due to future floods may decrease the amount that buyers are willing to pay for a property that they know see as more risky even if the financial ties to required flood insurance are not effective yet. PRE_DATE is used due to a buyers anticipation of a policy's impact. 

Concerns: 

- Who's included or excluded? Are the properties that are in floodplains different in ways that impact the sales? Are people less willing to buy risky properties in general, resulting in fewer sales? 

 - Inflation? Market trends? Year or regional fixed effects?   
 
 - If parcels were removed from the FEMA flood zone but still at risk, does that say more about information asymmetry or regulatory trust than flood safety?
 
 
 - Areas that have received new flood maps are mostly wealthier parts of Cook County. The 800+ pins added to flood plains in the preliminary FIRM are all in Northern Cook County. The FIRMs updated in 2018 and 2021 are along the lake front and include Glencoe/Wilmette areas. Could really influence price trends.

```{r}

# 1) Make sure sale_date is a Date (if not already)
df_prep <- res_sales %>%
  filter(pin %nin% drop_pins) |> 
  
  mutate(
  #  sale_date2 = mdy(sale_date),         # parse "September 01 2018" → Date
    sale_year  = year(sale_date),       # or just use your existing `year` column
  eff_date = ymd(EFF_DATE),
  pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date, sale_year, sale_price, in_eff_sfha, eff_date, pre_date, in_lomr) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha
  ) %>%

  ungroup()
```


```{r }
df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)

    removed_between = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA"),
    added_between = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA"),
    stayed_sfha = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA"),
    neither_sfha = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA"),
    
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
    )
```

```{r code-for-preliminaryFIRMdate}
df_pairs <- df_pairs |> 
  mutate(t1_months = round(time_length(pre_date - sale_date_t1, "months") ), # first sale to FIRM update, in months
         t2_months = round(time_length(sale_date_t2 - pre_date, "months")),
         
         t1_years = round(time_length(pre_date - sale_date_t1, "years") ),    # first sale to FIRM update, in years
         t2_years = round(time_length(sale_date_t2 - pre_date, "years")),     # time since FIRM update, in years

         # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")), 
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),


  )|>
      # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1))

df_pairs <- df_pairs |> filter(change_type != "OTHER")
table(df_pairs$years_btwn, df_pairs$change_type)
```


```{r code-for-effectiveFIRM, eval=FALSE, include=FALSE}
df_pairs <- df_pairs |> 
  mutate(t1_months = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
         t2_months = round(time_length(sale_date_t2 - eff_date, "months")),
         
         t1_years = round(time_length(sale_date_t2 - eff_date, "years") ),    # first sale to FIRM update, in years
         t2_years = round(time_length(sale_date_t2 - eff_date, "years")),     # time since FIRM update, in years

         # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")), 
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),


  )|>
      # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1)) #%>%
  
  # keep obs where sales happened around FIRM effective date
 # filter(sale_date_t1 < eff_date & sale_date_t2 > eff_date)
```



```{r eval=FALSE, include = FALSE}
df_pin_summary <- df_pairs %>%
  group_by(pin) %>%
  summarize(
    n_pairs    = n(),
    avg_dlog   = mean(d_log_price),
    ever_removed = as.integer(any(removed_between == 1))
  )
```


```{r}
df_pairs <- df_pairs %>%
  mutate(years_btw_sales = sale_year_t2 - sale_year_t1,
         time_btw_sales = lubridate::as.difftime(sale_date_t2 - sale_date_t1)
  )

df_pairs <- df_pairs |> 
  select(pin, d_log_price,
         sale_year_t1, sale_price_t1, in_sfha_t1, t1_months, t1_years,
         sale_year_t2, sale_price_t2, in_sfha_t2, t1_months, t1_years,
         years_btw_sales, removed_between, added_between, change_type, everything()
  )

df_pairs <- df_pairs |> 
  mutate(change_type = factor(change_type, levels = c("Both Out of SFHA", "Both In SFHA", "Added", "Removed")))
df_pairs


```


```{r}
# 2) Run the repeat‐sales regression
rs_model <- feols(
  d_log_price ~ log(years_btw_sales) + change_type,
  #  d_log_price ~ years_btw_sales + removed_between,

  data = df_pairs,
    cluster = ~pin

)

summary(rs_model)
```



```{r}
rs_model <- feols(
  d_log_price ~ change_type
  | 0,       
  data = df_pairs,
  cluster = ~pin

)
summary(rs_model)
```

```{r}
rs_model <- feols(
  d_log_price ~ change_type*in_lomr
  | 0,       
  data = df_pairs,
  cluster = ~pin

)
summary(rs_model)
```


```{r}
rs_model <- feols(
  d_log_price ~ added_between + removed_between + years_btw_sales
  | 0,
  data = df_pairs,
   cluster = ~pin

)
summary(rs_model)
```


```{r}
df_pairs <- df_pairs %>%
  mutate(
    log_years_btw = log(years_btw_sales)  # where year_t2_t1_diff = sale_year_t2 - sale_year_t1
  )

rs_model2 <- feols(
  d_log_price ~ removed_between 
             + log_years_btw
  | 0,
  data = df_pairs,
  cluster = ~pin
)
summary(rs_model2)

```



## Event Study Sales Pairs

```{r}
df_event_pairs <- df_prep %>%
  group_by(pin) %>%
  # Identify the sale dates when the parcel transitions out of SFHA
  mutate(
    ever_removed = any(in_eff_sfha == "SFHA" & lead(in_eff_sfha) == "Not SFHA", na.rm = TRUE)
  ) %>%
  filter(ever_removed) %>%             # keep only pins that *ever* transition out
  # Now each PIN that ever_removed == TRUE needs exactly one pair.
  do({
    pin_data <- .
    # 1a) find the row‐number of the *last* sale where in_eff_sfha == TRUE
    idx_pre  <- which(pin_data$in_eff_sfha == "SFHA") |> max()

    # 1b) find the row‐number of the next sale after idx_pre
    idx_post <- idx_pre + 1

    # 2) slice out just those two rows:
    pin_data[c(idx_pre, idx_post), ]
  }) %>%
  ungroup()


df_before_after <- df_event_pairs %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  slice(1:2) %>%   # 1st row is “pre” (t1), 2nd is “post” (t2)
  summarise(
    # Grab everything from row 1 as “_t1”:
    sale_price_t1      = sale_price[1],
    sale_date_t1       = sale_date[1],
    year_t1            = year(sale_date[1]),
    in_sfha_t1         = in_eff_sfha[1],

    # Grab everything from row 2 as “_t2”:
    sale_price_t2      = sale_price[2],
    sale_date_t2       = sale_date[2],
    year_t2            = year(sale_date[2]),
    in_sfha_t2         = in_eff_sfha[2]
  ) %>%
  ungroup()

```

```{r}
res_sales <- res_sales |>
  mutate(time_to_update = year - year(EFF_DATE),
         post_update = ifelse(year > year(EFF_DATE),"Post", "Before"))

fixest::feols(
  log(sale_price) ~ i(time_to_update, in_eff_sfha, ref = -1) | pin + year,
  data = res_sales |> filter(time_to_update >-10 & time_to_update < 10)
) |> etable()

fixest::feols(
  log(sale_price) ~ time_to_update * post_update | pin,
  data = res_sales |> filter(time_to_update >-10 & time_to_update < 10)
    ) |> etable()
```

### Coding the Counterfactual 

```{r}
# 1b) For each PIN, find the "last sale before firm_date"
df_before <- df_prep %>%
  filter(sale_date < eff_date) %>%
  group_by(pin) %>%
  slice_max(sale_date, with_ties = FALSE) %>%  # keep exactly 1 row per pin
  ungroup() |>
    rename(
    sale_date_t1    = sale_date,
    sale_price_t1 = sale_price,
    in_sfha_t1    = in_eff_sfha
  )

# 1c) For each PIN, find the "first sale after or on firm_date"
df_after <- df_prep %>%
  filter(sale_date >= eff_date) %>%
  group_by(pin) %>%
  slice_min(sale_date, with_ties = FALSE) %>%  # keep exactly 1 row per pin
  ungroup() %>%
  rename(
    sale_date_t2    = sale_date,
    sale_price_t2 = sale_price,
    in_sfha_t2    = in_eff_sfha
  )


df_pairs_joined <- df_before %>%
  inner_join(df_after, by = "pin") %>%
  # compute some auxiliaries
  mutate(
    year_t1    = year(sale_date_t1),
    year_t2    = year(sale_date_t2),

    # change in log price (the repeat‐sales DV)
    d_log_price = log(sale_price_t2) - log(sale_price_t1),

    # how many days/months between the sale before and the sale after?
    days_between = as.integer(sale_date_t2 - sale_date_t1),
    months_between = interval(sale_date_t1, sale_date_t2) %/% months(1)
  )


df_pairs_joined <- df_pairs_joined %>%
  mutate(
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "AlwaysIn",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "AlwaysOut",
      TRUE ~ "OTHER"),
    
    # turn it into a factor with a clear baseline
    change_type_f = factor(
      change_type,
      levels = c("AlwaysOut", "AlwaysIn", "Added", "Removed")
    ),
    
    removed_between = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA"),
    added_between = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA"),
    stayed_sfha = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA"),
    neither_sfha = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA"),
  
  )


# 1) Turn year_t2 into a factor (if not already)
df_pairs_joined <- df_pairs_joined %>%
  mutate(year2_f = factor(year_t2))

# 2) Run the regression
mod <- feols(
  d_log_price ~ change_type_f  + months_between
             + i(year2_f, ref = "2024") 
  | 0,
  data    = df_pairs_joined,
  cluster = ~pin       # one row per pin, but safe to cluster anyway
)

summary(mod)

```


firm update = year 0


```{r}
library(fixest)


paper_models <- list(

    "I" = 
    
    feols(sale_price ~ in_eff_sfha + in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = res_sales))
    
    
paper_models |> etable()

paper_models <- list(

    "I" = 
    
    feols(sale_price ~ in_eff_sfha*in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = res_sales )
    
    )
paper_models |> etable()

```


# Research Question 2

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.



# Research Question 3

**Is lived experience capitalized into sales prices? is this effect (if any) moderated by other existing sources of increased flood risk?**

H4: Experiencing a flood event conveys new risk information. Properties damaged by a flood event that were not in an SFHA expereince a decrease in value larger than damaged properties taht were in an SFHA. 

> Need indicator for if property flooded. Which I do not cleanly have.

> treated zipcodes file! or treated census blocks? from Individual Assistance version updated by FEMA.





# Lived Experience PINs

## Flood Event 2023 - Disaster Declarations / Lived Experience

Cicero and Berwyn had lots of damage during DR 4728. Cicero had 25,836 housing units in 2020 and over 6000 of them applied and were granted IHP funds. 


Dolton and Calumet City were damaged during DR 4749.

```{r}
#| include: false
#| 
ptax245 <- readxl::read_xlsx("inputs/PTAX-245_data.xlsx")
tr_zips <- read_csv("./data/processed/treated_zipcodes.csv")

ptax245 <- ptax245 %>% 
  mutate(
    pin = str_remove_all(pin, "-"),
    keypin = as.character(KeyPIN)) %>%
  mutate(keypin_concat = as.character(keypin),
         keypin_concat = str_remove_all(keypin_concat, "-"),
         keypin_concat = str_pad(keypin_concat, 14, "left", pad = "0"),
         major_class = str_sub(Class, 1, 1),
         parcel = str_sub(pin, 1, 10),
         block = str_sub(pin, 1, 7),
         year = 2023,
         appealed = 1 ) %>%
  select(pin, keypin_concat, parcel, block, Class, major_class, everything()) %>% 
  distinct() %>% 
  arrange(pin)
ptax_pins <- ptax245 |> select(pin) |> pull()

res_sales <- res_sales |> mutate(flood2023 = ifelse(pin %in% ptax245, 1, 0))

```

245 PINs in Cicero and 45 PINs in Berwyn appealed their property tax (plus 2 in Oak Park, 2 in River Forest, and 1 in Riverside).

```{r}
#| include: false

res_sales %>% filter(pin %in% ptax245)

```


90,000 Post Disaster Individual Assistance Grants between the two disasters in 2023. 
Only a few million in NFIP claims were paid out from these flood events but over $300 million in IHP fund were distributed. 

- Part of this is because the areas hit hardest (Cicero and Berwyn have no SFHAs and no properties are required to have flood insurance. In general, not many properties in SFHAs in Cook County, especially where these flood events occurred. Makes it unlikely that residents have flood insurance and they can't file flood insurance claims if they don't have flood insurance. )

Cook County also had disaster declarations in 1993, 1996, 1997, 2007, 2009, 2010, 2013, and 2023X2.

