---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    tbl-cap-location: top
    fig-cap-location: top
---


# Data Prep

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

Parcel shapefile used in ArcGIS Pro is downloaded from CCAO's Archived 2022 parcel dataset [here.](https://datacatalog.cookcountyil.gov/Property-Taxation/ccgisdata-Parcel-2021/77tz-riq7/about_data)

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
```


```{r codein-data_prep-rscript}
# sales <- read_csv("./data/raw/Assessor_Parcel_Sales_20250105.csv") %>% 
#   filter(year > 2005) %>%
#   
#   mutate(class_1dig = str_sub(class, 1, 1),
#          class = as.numeric(class)) |>
#   # filter(class > 199 & class < 1000) |>
#   mutate(date = lubridate::mdy(sale_date)) # |>
#   #group_by(year, class_1dig)|>
#   #mutate(sale_price = Winsorize(sale_price, quantile(sale_price, probs = c(0.03, 0.97), na.rm=FALSE) )) |>
#  # ungroup() 
# 
# firms <- read_csv("./data/processed/parcels_wFIRMS.csv")
# 
# # add flood variables to sales data
# sales <- sales |> 
#     mutate(pin10 = str_sub(pin, 1, 10)) |>
#   left_join(firms, by = "pin10")
# 
# sales <- sales |>   
#   mutate(Location = ifelse(pin10 %in% firms$pin10, "In FP", "Outside FP" )) 
# 
# sfha_ind <- read_csv("./data/processed/sfha_indicator_pins.csv")
# sfha_ind <- sfha_ind |> select(pin, sfha2018:lomr2024)
# 
# sales <- sales |> left_join(sfha_ind, by ="pin")
# 
# sales <- sales |>
#   mutate(class = as.character(class),
#          lomr2024 = as.character(lomr2024),
#          sfha2024 = as.character(sfha2024)) 
# 
# 
# lomrs <- read_csv("./data/processed/lomr_pins_2024.csv") |>
#   rename(lomr_eff = EFF_DAT,
#          lomr_dfirm_id = DFIRM_I) |>
#   mutate(lomr_eff = as_date(lomr_eff))
# 
# sales <- sales |>
#   mutate(
#     prelim_date = ifelse(PRE_DATE == "9999-09-09" | is.na(PRE_DATE), "2005-01-01", PRE_DATE),
#     
#     ccao_sfha = ifelse(sfha2024 == 1 & year >= 2021, "SFHA", "Not SFHA"),
#     ccao_sfha = ifelse(is.na(ccao_sfha), "Not SFHA", ccao_sfha),
#     
#     # the flood zones that existed in the 2018 state NFHL were last updated in 2008. sfha2018 is the default SFHA status for the observations, then lomrs and future updates will be incorporated
#     in_eff_sfha = ifelse(sfha2018 == 1, "In SFHA", "Not in SFHA"),
#     
#     in_eff_sfha = ifelse(sfha2024 == 1 & year >= year(EFF_DATE), "In SFHA", 
#                          ifelse(year >= year(EFF_DATE) & sfha2024 == 0, "Not in SFHA", in_eff_sfha)),
#     
#     in_eff_sfha = ifelse((sfha2018 == 0 & sfha2024 == 0 ) | (is.na(sfha2018) & is.na(sfha2024)) , "Not in SFHA", in_eff_sfha))
# 
# table(sales$year, sales$in_eff_sfha)
# 
# 
# sales <- sales |>
#   left_join(lomrs, by = c("pin")) |>
#   mutate(
#     in_lomr = ifelse(year >= year(lomr_eff) & !is.na(LOMR_ID), "In LOMR", "Not in LOMR") ,
#     in_prelim_sfha = ifelse(year >= as_date(prelim_date), "1", "0"),
#       ) |>
#   
#   # do I want this line of code? LOMRs don't remove you from the "risky" area, but they do indicate that property was either mitigated or on higher ground and results in removal of flood insurance requirement
#   # if in SFHA and in a LOMR, keep both variables as 1 instead of recoding in_eff_sfha to 0?
#   mutate(in_eff_sfha = ifelse(in_eff_sfha == 1 & in_lomr == 1, in_eff_sfha == 0, in_eff_sfha))
```

> Coding note: sale_price can be winsorized by grouping the year & major class (technically the 1st digit of the class code). Check that this is how you want it to be winsorized. It is currenty commented out and NOT WINSORIZED.

> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. 


# Sales Data

1,762,627 sales for all property classes (1,869,796 after new download in January)

1,070,348 sales for Class 2 Residential properties (1,655,745 after new download and identifying any pin that was residential at any point in time and including it)


> TO DO: Use grepl() to identify properties bought by municipalities? list of Muni names and if they are similar to the buyer name? Useful for flagging buyouts?


# Frequency of Sales

`res_sales` includes any pin that was residential at some point in time. 

 
```{r}
#sales      <- readRDS("./data/processed/sales_prepped.rds")
res_sales  <- readRDS("./data/processed/res_sales.rds") 


# sampled_data <- res_sales |> 
#   sample_frac(0.05)
# write_csv(sampled_data, 
#           "data_sample.csv")

firms <- readxl::read_xlsx("./data/raw/S_FIRM_PAN.xlsx")
```

# Random questions to check

**Are there condos in floodplains?** -- Condos were filtered out at an earlier step (298 and 299).

"297s are special residential improvements"

```{r}
res_sales |> 
  filter(in_eff_sfha == "SFHA") |>
  filter(class %in% c(297, 298, 299))
```

**Are there CoOps and other weird properties in floodplains?** -- NO, filter these property classes out and dont worry about them.

```{r}
table(res_sales$in_eff_sfha)

```


```{r}
res_sales <- left_join(res_sales, firms, by = c("FIRM_PAN"))


repeat_sales <- res_sales |> group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup()
  
table(repeat_sales$times_sold)

table(res_sales$PRE_DATE)

table(res_sales$year, res_sales$in_eff_sfha)
table(res_sales$year, res_sales$in_lomr)

```

```{r inspect-highmultisales}

# price corrections randomly spotted
res_sales <- res_sales |> 
  mutate(sale_price = 
         case_when(
           pin == "15154220240000" ~ 180000,   # not 180 million
         TRUE ~ sale_price
         ))


# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N LAkeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000"     # another CoOp
               
)

res_sales |> filter(times_sold > 5) |> arrange(desc(sale_price))
res_sales |> filter(times_sold > 5) |>  filter(pin %nin% drop_pins) |> arrange(desc(sale_price))



res_sales |> filter(times_sold >15) |> 
  ggplot() + 
  geom_line(aes(x=sale_date, y = sale_price, group = pin))
```

```{r}

# 1) Make sure sale_date is a Date (if not already)
df_prep <- res_sales %>%
  filter(times_sold < 15) |>
  filter(pin %nin% drop_pin) |> 
  
  mutate(
    sale_date2 = mdy(sale_date),         # parse "September 01 2018" → Date
    sale_year  = year(sale_date2),       # or just use your existing `year` column
  eff_date = ymd(eff_date),
  pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date2, sale_year, sale_price, in_eff_sfha, eff_date, pre_date) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date2) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date2) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date2),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date2,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha
  ) %>%

  ungroup()
```


```{r }
df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)

    removed_between = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA"),
    added_between = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA"),
    stayed_sfha = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA"),
    neither_sfha = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA"),
    
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
    )
```

```{r code-for-preliminaryFIRMdate}
df_pairs <- df_pairs |> 
  mutate(t1_months = round(time_length(sale_date_t1 - pre_date, "months") ), # first sale to FIRM update, in months
         t2_months = round(time_length(sale_date_t2 - pre_date, "months")),
         
         t1_years = round(time_length(sale_date_t2 - pre_date, "years") ),    # first sale to FIRM update, in years
         t2_years = round(time_length(sale_date_t2 - pre_date, "years")),     # time since FIRM update, in years

         # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")), 
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),


  )|>
      # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1))
```


```{r code-for-effectiveFIRM, eval=FALSE, include=FALSE}
df_pairs <- df_pairs |> 
  mutate(t1_months = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
         t2_months = round(time_length(sale_date_t2 - eff_date, "months")),
         
         t1_years = round(time_length(sale_date_t2 - eff_date, "years") ),    # first sale to FIRM update, in years
         t2_years = round(time_length(sale_date_t2 - eff_date, "years")),     # time since FIRM update, in years

         # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")), 
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),


  )|>
      # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1)) #%>%
  
  # keep obs where sales happened around FIRM effective date
 # filter(sale_date_t1 < eff_date & sale_date_t2 > eff_date)
```


```{r}
table(df_pairs$t2_years, df_pairs$change_type)
table(df_pairs$t1_years, df_pairs$removed_between)
table(df_pairs$t1_years, df_pairs$added_between)

table(df_pairs$years_btwn, df_pairs$change_type)


```


```{r}
df_pairs <- df_pairs %>%
  mutate(years_btw_sales = sale_year_t2 - sale_year_t1,
         time_btw_sales = lubridate::as.difftime(sale_date_t2 - sale_date_t1)
  )

df_pairs <- df_pairs |> 
  select(pin, 
         sale_year_t1, sale_price_t1, in_sfha_t1, t1_months, t1_years,
         sale_year_t2, sale_price_t2, in_sfha_t2, t1_months, t1_years,
         years_btw_sales, removed_between, added_between, change_type
  )
```


```{r}



# 2) Run the repeat‐sales regression
rs_model <- feols(
  d_log_price ~ removed_between + years_btw_sales,
  # no extra fixed‐effects needed (year dummies are explicit)
  data = df_pairs#|>filter(!is.na(EFF_DATE))
)
summary(rs_model)


rs_model <- feols(
  d_log_price ~ removed_between
  + i(year_t2_f, ref = "0")     # “ref” is any omitted baseline year; pick one that makes sense
  | 0,                             # no extra fixed‐effects needed (year dummies are explicit)
  data = df_pairs
)
summary(rs_model)


rs_model <- feols(
  d_log_price ~ added_between + removed_between
#  + i(year_t2_f, ref = "2018")     # “ref” is any omitted baseline year; pick one that makes sense
  | 0,                             # no extra fixed‐effects needed (year dummies are explicit)
  data = df_pairs
)
summary(rs_model)

rs_model <- feols(
  d_log_price ~ added_between + removed_between
 # + i(year_t2_f, ref = "2018")     # “ref” is any omitted baseline year; pick one that makes sense
  
  + years_btw_sales
  | 0,                             # no extra fixed‐effects needed (year dummies are explicit)
  data = df_pairs
)
summary(rs_model)
```


```{r}
df_pairs <- df_pairs %>%
  mutate(
    log_years_btw = log(year_t2_t1_diff)  # where year_t2_t1_diff = sale_year_t2 - sale_year_t1
  )

rs_model2 <- feols(
  d_log_price ~ removed_between 
             + i(year_t2_f, ref = "2018")
             + log_years_btw
  | 0,
  data = df_pairs,
  cluster = ~pin
)
summary(rs_model2)

```

```{r}
res_sales <- res_sales |>
  mutate(time_to_update = year - year(eff_date),
         post = ifelse(year > year(EFF_DATE),"1", "0"))

fixest::feols(
  log(sale_price) ~ i(time_to_update, in_eff_sfha, ref = -1) | pin + year,
  data = res_sales
) |> etable()

fixest::feols(
  log(sale_price) ~ in_eff_sfha * post | pin + year,
  data = res_sales
    ) |> etable()
```


## Sales in and Out of FEMA SFHAs

```{r}

res_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Sales") |>
  mutate(
    Year = as.character(year),
    TotalSales = `In FP` + `Outside FP`,
    `FP Share (%)` = `In FP` / TotalSales,
   `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)) |>
  select(-c(TotalSales, year)) |> 
  mutate(Year = as.character(Year), .before = `In FP`) |> 
  select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |>
  flextable::flextable()


sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  # ungroup() |>
   pivot_wider(names_from = "Location", values_from = "Sales") |>
   mutate(
     TotalSales = `In FP` + `Outside FP`,
     `FP Share (%)` = `In FP` / TotalSales,
     # `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)
   ) |>
  # select(-c(TotalSales, year)) |> 
  # mutate(Year = as.character(Year), .before = `In FP`) |> 
  # select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |> 
  ggplot() +
  geom_line(aes(x=year, y= `FP Share (%)`)) + 
  scale_y_continuous(limits = c(0, 0.02), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Flood Plain Properties make up less than 1.5% of Sales",
       x = element_blank(),
       y = "Share of Sales")
```

```{r}
sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
   Ratio =  scales::percent(Ratio, accuracy = 0.01),
   Year = as.character(year)) |> 
  select(Year, Sales, `In FP`, `Outside FP`, Ratio) |>
  flextable::flextable()

sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
  # Ratio =  scales::percent(Ratio, accuracy = 0.01)
   ) |>
  ggplot() +
  geom_line(aes(x=year, y = Ratio)) +
  scale_y_continuous(limits = c(0, 1), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Ratio of Median Value for Properties In and Out of Floodplain",
       x = element_blank(),
       y = "Ratio",
       caption = "Ratio = Median Sale Price in FP / Median Price outside FP") 
```


# Timing of Sales around variables of interest

```{r, warning=FALSE, message=FALSE}
# 
# res_sales <- sales |> 
#     filter(sale_price > 200) |>
# 
#   mutate(class = as.numeric(class),
#          res_c2 = as.factor(ifelse(class >= 200 & class <= 297, TRUE, FALSE)),
# ) |> 
#   group_by(pin) |>
#   arrange(year) |>
#   filter(sum(res_c2==TRUE) >= 1) |>
#   mutate(
#     times_sold = n(),
#     years_btw_sales = year - lag(year),
# 
#     sold_once = ifelse(times_sold == 1, TRUE, FALSE),
#     sold_multi = ifelse(times_sold > 1 , TRUE, FALSE),
#     ) |> 
#   ungroup() |>
#   mutate(
#     sold_pre2014 = ifelse(year <= 2013, TRUE, FALSE),
#     sold_post2013 = ifelse(year > 2013, TRUE, FALSE),
#     
#     sold_btwn_20132023 = ifelse(year > 2013 & year < 2024, TRUE, FALSE),
#     
#     sold_pre2024 = ifelse(year <= 2023, TRUE, FALSE),
#     sold_post2023 = ifelse(year > 2023, TRUE, FALSE),
#     )
```


```{r, warning=FALSE, message=FALSE}
res_sales |> group_by(pin) |> arrange(pin) |> filter(any(years_btw_sales > 0))
```


```{r, warning=FALSE, message=FALSE}
res_sales |> 
  group_by(sold_multi) |> 
    summarize(n=n(),
              distinct_pins = n_distinct(pin))

res_sales |> 
  group_by(times_sold) |> 
    summarize(distinct_pins = n_distinct(pin))

res_sales |>
  group_by(sold_pre2014, sold_btwn_20132023, sold_post2023) |> 
  summarize(n = n(), n_distinct = n_distinct(pin))
```


```{r}

pin_groups |>
  group_by(times_sold, sold_post2023, 
           ) |> 
  summarize(
            n_pins = n_distinct(pin))
```

# Missing Value Check

```{r}
```


# Research Questions


### Research Question 1 


**Does the value of real estate parcels increase when they are removed from an SFHA?** 

H1: A property removed from a SFHA will increase in value, compared to properties with otherwise shared characteristics.

firm update = year 0


```{r}
library(fixest)


paper_models <- list(

    "I" = 
    
    feols(sale_price ~ in_eff_sfha + in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = res_sales |> filter(class_1dig == 2 & class %nin% c( 218, 219, 298, 299)))
    
    )
paper_models |> etable()

paper_models <- list(

    "I" = 
    
    feols(sale_price ~ in_eff_sfha*in_lomr
                           | pin + year,
                           panel.id = c("pin", "year"),
                           data = res_sales |> filter(class_1dig == 2 & class %nin% c( 218, 219, 298, 299)))
    
    )
paper_models |> etable()

```

```{r}
tbl_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Removed from SFHA") |>

  #filter(risk_change == "Removed from SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2020 & min(year) < 2019, "SFHA Change btwn sales", "SFHA not btwn sales"))|>
  group_by(year, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
tbl_R1

tbl_R1 |> ggplot(aes(x=year, y=n, color = sold_post2021)) + geom_line()

tbl_R1 |> ggplot(aes(x=year, y=median_price, color = sold_post2021)) + geom_line()


res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Removed from SFHA" | risk_change == "Always in SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "SFHA Change btwn sales", "SFHA Change not btwn sales"))|>
  group_by(year, sold_post2021, risk_change ) |> 
  summarize( n = n_distinct(pin), median_price = median(sale_price)) |>
  ggplot()+
  geom_line(aes(x=year, y = median_price/1000000, group = risk_change, color = risk_change)) + 
  geom_text(aes(x = 2016, y = 0.2, label = c(sum(n))) )+
  facet_wrap(~sold_post2021)

control_tbl2_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_change == "Always in SFHA") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "Sold b4&after 2021", "Not sold b4&after 2021"))|>
  group_by(sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price))

control_tbl2_R1


control_tbl_R1 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "Sold b4&after 2021", "Not sold b4&after 2021"))|>
  group_by(sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price))

control_tbl_R1


```

### Research Question 2

```{r}
tbl_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "FSF Score 5+ Only" | risk_type == "SFHA & FSF Score 5+" | risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 

tbl_R2

control_tbl_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "In CCAO SFHA Only") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
control_tbl_R2


control_tbl2_R2 <- res_sales |>
  left_join(pin_groups, by = "pin") |>  
  filter(risk_type == "Low Risk") |>
  group_by(pin) |>
  mutate(sold_post2021 = ifelse(max(year) >= 2021 & min(year) < 2021, "FSF Change btwn sales", "FSF not btwn sales"))|>
  group_by(risk_type, sold_post2021) |> 
  summarize( n = n_distinct(pin),
             median_price = median(sale_price)) 
control_tbl2_R2
```

### Research Question 3

> Need indicator for if property flooded. Which I do not cleanly have.

```{r}
#| label: tbl-SFHAparcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels in SFHAs that have been sold."

sfhasales <-  res_sales %>%
  filter(ccao_sfha == 1) %>%
  left_join(landblock_pins, by = c("year", "pin")) %>%
  mutate(parcel = str_sub(pin, 1, 10))

sfhasales %>% 
  filter(sale_price >5000) |>
  group_by(parcel, year, sale_document_num) %>%
  summarize(pincount = n(),
            sale_price = first(sale_price),
            sale_price_sum = sum(sale_price)) %>% 
  arrange(desc(parcel))

duplicates <- sfhasales |> janitor::get_dupes(pin, parcel, year, sale_price)
duplicates

sfhasales |> 
  filter(sale_price > 5000) |>
  group_by(pin, parcel, year, sale_price) |> 
  distinct(pin,year,sale_price, .keep_all = TRUE)
```


```{r}
#| label: tbl-SFHAparcels-soldtimes
#| tbl-cap-location: margin
#| tbl-cap: "Multisales SFHA PIN Sales: Number of times sold and count of years properties were sold in. Filtered for pins that were sold more than once."

sfhasales %>% 
  filter(sale_price>5000) |>
  group_by(pin) %>% 
  summarize(timessold=n(),
            distinct_years = n_distinct(year),
            max_price= max(sale_price),
            min_price = min(sale_price),
            class = max(class_1dig)) %>% 
  filter(timessold>1) %>% 
  arrange(desc(timessold))
```


```{r}
#| label: tbl-salesover5K
#| tbl-cap-location: margin
#| tbl-cap: "Sales of SFHA PINs over $5000 for properties in SFHA FEMA Zones. N = 18,157"

sfhasales %>% 
  filter(!is.na(sale_price) & sale_price > 5000) %>% 
  arrange(desc(num_parcels_sale), sale_document_num, pin )
```

```{r}
#| label: fig-pinsales-andAV
#| fig-cap: "PIN Sale Price and Assessed Values over time."
#| fig-subcap: 
#| - pin == 09163040191019
#| - pin == 05201210150000
#| - pin == 05201210150000
#| layout-ncol: 3


sfhasales %>% 
  filter(pin == "09163040191019") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "05201210150000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)



sfhasales %>% 
  filter(pin == "09281140060000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) +
  geom_line(aes(x=year, y = av_clerk), lty = 3)+
  geom_line(aes(x=year, y = fmv_clerk), lty=2)


```

```{r}
#| label: tbl-floodfactor-parcels
#| tbl-cap-location: margin
#| tbl-cap: "Parcels with Flood Factor Risk Rating >= 5  that have been sold. 206,304 PINs have sales prices above $5K and flood factor ratings."

floodsales <- sales %>% 
  filter(pin %in% sfha_pins) %>%
  left_join(landblock_pins, by = c("year", "pin", "class"))



#floodsales %>% filter(!is.na(sale_price))
floodsales %>% filter(#!is.na(sale_price) & 
                        sale_price > 5000)
# 206,304 sales for pins in flood factor high risk areas of 5 or higher
```


# Lived Experience PINs

## Flood Event 2023 - Disaster Declarations / Lived Experience

Cicero and Berwyn had lots of damage during DR 4728. Cicero had 25,836 housing units in 2020 and over 6000 of them applied and were granted IHP funds. 


Dolton and Calumet City were damaged during DR 4749.

```{r}
ptax245 <- readxl::read_xlsx("inputs/PTAX-245_data.xlsx")
tr_zips <- read_csv("./data/processed/treated_zipcodes.csv")

ptax245 <- ptax245 %>% 
  mutate(
    pin = str_remove_all(pin, "-"),
    keypin = as.character(KeyPIN)) %>%
  mutate(keypin_concat = as.character(keypin),
         keypin_concat = str_remove_all(keypin_concat, "-"),
         keypin_concat = str_pad(keypin_concat, 14, "left", pad = "0"),
         major_class = str_sub(Class, 1, 1),
         parcel = str_sub(pin, 1, 10),
         block = str_sub(pin, 1, 7),
         year = 2023,
         appealed = 1 ) %>%
  select(pin, keypin_concat, parcel, block, Class, major_class, everything()) %>% 
  distinct() %>% 
  arrange(pin)
ptax_pins <- ptax245 |> select(pin) |> pull()

res_sales <- res_sales |> mutate(flood2023 = ifelse(pin %in% ptax245, 1, 0))

```

245 PINs in Cicero and 45 PINs in Berwyn appealed their property tax (plus 2 in Oak Park, 2 in River Forest, and 1 in Riverside).

```{r}

res_sales %>% filter(pin %in% ptax245)

```


90,000 Post Disaster Individual Assistance Grants between the two disasters in 2023. 
Only a few million in NFIP claims were paid out from these flood events but over $300 million in IHP fund were distributed. 

- Part of this is because the areas hit hardest (Cicero and Berwyn have no SFHAs and no properties are required to have flood insurance. In general, not many properties in SFHAs in Cook County, especially where these flood events occurred. Makes it unlikely that residents have flood insurance and they can't file flood insurance claims if they don't have flood insurance. )

Cook County also had disaster declarations in 1993, 1996, 1997, 2007, 2009, 2010, 2013, and 2023X2.

