---
title: "example graph"
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 3
---

PIN fixed effects remove time-invariant differences across properties, such as location, structure type, and baseline price level. Year fixed effects remove market-wide shocks common to all properties in a given year. The remaining comparison asks whether properties with high Flood Factor scores followed different post-release price trajectories than otherwise similar repeated-sale properties after accounting for those fixed property differences and common year effects.

```{r}
library(tidyverse)

toy_fe <- tibble::tribble(
  ~pin, ~sale_year, ~high_ff_score, ~event, ~sale_price,
  "A", 2018, FALSE, FALSE, 200000,
  "A", 2022, FALSE, TRUE, 230000,
  "B", 2018, TRUE,  FALSE, 200000,
  "B", 2022, TRUE,  TRUE, 185000,
  "C", 2018, FALSE, FALSE, 500000,
  "C", 2022, FALSE, TRUE, 575000,
  "D", 2018, TRUE,  FALSE, 500000,
  "D", 2022, TRUE,  TRUE, 460000
) |>
  mutate(
    log_price = log(sale_price),
    group = if_else(high_ff_score, "High Flood Factor", "Low Flood Factor")
  )
```

```{r}
toy_fe |>
  ggplot(aes(
    x = sale_year,
    y = sale_price,
    group = pin,
    linetype = group
  )) +
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  labs(
    x = "Sale year",
    y = "Sale price",
    linetype = "Flood Factor group",
    title = "Raw within-property price trajectories",
    subtitle = "PIN fixed effects compare each property to itself over time"
  )

```

```{r}
toy_changes <- toy_fe |>
  arrange(pin, sale_year) |>
  group_by(pin) |>
  mutate(
    first_log_price = first(log_price),
    log_price_change = log_price - first_log_price,
    pct_change_from_first_sale = 100 * (exp(log_price_change) - 1)
  ) |>
  ungroup()
```

```{r}
toy_changes |>
  ggplot(aes(
    x = sale_year,
    y = pct_change_from_first_sale,
    group = pin,
    linetype = group
  )) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  labs(
    x = "Sale year",
    y = "Change from property’s first sale (%)",
    linetype = "Flood Factor group",
    title = "After removing property-specific price levels",
    subtitle = "The comparison is about different post-release trajectories, not raw price levels"
  )
```



```{r}
# toy_fe <- tibble::tribble(
#   ~pin, ~sale_year, ~high_ff_score, ~sale_price,
#   "A", 2018, FALSE, 200000,
#   "A", 2022, FALSE, 240000,  # +20%
#   "B", 2018, TRUE,  200000,
#   "B", 2022, TRUE,  210000,  # +5%
#   "C", 2018, FALSE, 500000,
#   "C", 2022, FALSE, 600000,  # +20%
#   "D", 2018, TRUE,  500000,
#   "D", 2022, TRUE,  525000   # +5%
# ) |>
  
toy_fe <- tibble::tribble(
  ~pin, ~sale_year, ~high_ff_score, ~sale_price,
  "A", 2018, FALSE, 200000,
  "A", 2022, FALSE, 280000,  
  "B", 2018, TRUE,  200000,
  "B", 2022, TRUE,  210000,  # +5%
  "C", 2018, FALSE, 500000,
  "C", 2022, FALSE, 600000,  # +20%
  "D", 2018, TRUE,  500000,
  "D", 2022, TRUE,  535000   
) |>
  mutate(
    log_price = log(sale_price),
    ff_group = if_else(
      high_ff_score,
      "High Flood Factor",
      "Low Flood Factor"
    )
  )

toy_changes <- toy_fe |>
  arrange(pin, sale_year) |>
  group_by(pin) |>
  mutate(
    first_log_price = first(log_price),
    pct_change_from_first_sale = 100 * (exp(log_price - first_log_price) - 1)
  ) |>
  ungroup()

common_year_shock <- tibble::tribble(
  ~sale_year, ~market_change,
  2018, 0,
  2022, 10
)

toy_residualized <- toy_changes |>
  left_join(common_year_shock, by = "sale_year") |>
  mutate(
    net_of_year_effect = pct_change_from_first_sale - market_change
  )

toy_residualized |>
  ggplot(aes(
    x = sale_year,
    y = net_of_year_effect,
    group = pin,
    linetype = ff_group
  )) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  scale_x_continuous(
    breaks = c(2018, 2022)
  ) +
  labs(
    x = "Sale year",
    y = "Change net of common market movement (%)",
    linetype = "Flood Factor group",
    title = "After removing property fixed effects and common year movement",
    subtitle = "Year fixed effects subtract changes shared by all sales in the same year"
  )
```


```{r}
toy_fe <- tibble::tribble(
  ~pin, ~sale_year, ~high_ff_score, ~sale_price,
  "A", 2018, FALSE, 200000,
  "A", 2022, FALSE, 244000,  # +22%
  "B", 2018, TRUE,  200000,
  "B", 2022, TRUE,  216000,  # +8%
  "C", 2018, FALSE, 500000,
  "C", 2022, FALSE, 590000,  # +18%
  "D", 2018, TRUE,  500000,
  "D", 2022, TRUE,  555000   # +11%
) |>
  mutate(
    log_price = log(sale_price),
    ff_group = if_else(
      high_ff_score,
      "High Flood Factor",
      "Low Flood Factor"
    )
  )
toy_fe |>
  ggplot(aes(
    x = sale_year,
    y = sale_price,
    group = pin,
    linetype = ff_group
  )) +
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  labs(
    x = "Sale year",
    y = "Sale price",
    linetype = "Flood Factor group",
    title = "Raw within-property price trajectories",
    subtitle = "PIN fixed effects compare each property to itself over time"
  )
```

```{r}
toy_changes <- toy_fe |>
  arrange(pin, sale_year) |>
  group_by(pin) |>
  mutate(
    first_log_price = first(log_price),
    pct_change_from_first_sale = 100 * (exp(log_price - first_log_price) - 1)
  ) |>
  ungroup()
```

```{r}
toy_changes |>
  ggplot(aes(
    x = sale_year,
    y = pct_change_from_first_sale,
    group = pin,
    linetype =ff_group
  )) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  labs(
    x = "Sale year",
    y = "Change from property’s first sale (%)",
    linetype = "Flood Factor group",
    title = "After removing property-specific price levels",
    subtitle = "The comparison is about different post-release trajectories, not raw price levels"
  )
```



```{r}
common_year_shock <- tibble::tribble(
  ~sale_year, ~market_change,
  2018, 0,
  2022, 15
)

toy_residualized <- toy_changes |>
  left_join(common_year_shock, by = "sale_year") |>
  mutate(
    net_of_year_effect = pct_change_from_first_sale - market_change
  )

toy_residualized |>
  ggplot(aes(
    x = sale_year,
    y = net_of_year_effect,
    group = pin,
    linetype = ff_group
  )) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  scale_x_continuous(
    breaks = c(2018, 2022)
  ) +
  labs(
    x = "Sale year",
    y = "Change net of common market movement (%)",
    linetype = "Flood Factor group",
    title = "After removing property fixed effects and common year movement",
    subtitle = "All properties increased in value, but high-Flood-Factor properties rose less than the market trend"
  )
```



```{r}
adjustment_diagram <- toy_residualized |>
  filter(sale_year == 2022) |>
  transmute(
    pin,
    ff_group,
    before_adjustment = pct_change_from_first_sale,
    after_adjustment = net_of_year_effect
  )

ggplot(adjustment_diagram) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = before_adjustment,
      yend = after_adjustment,
      linetype = ff_group
    ),
    arrow = arrow(length = unit(0.15, "inches")),
    linewidth = 0.7
  ) +
  
  geom_point(
    aes(
      x = 1,
      y = before_adjustment,
      shape = "Before year adjustment"
    ),
    size = 2.8
  ) +
  
  geom_point(
    aes(
      x = 2,
      y = after_adjustment,
      shape = "After year adjustment"
    ),
    size = 2.8
  ) +
  
  geom_text(
    aes(
      x = 2.08,
      y = after_adjustment,
      label = pin
    ),
    hjust = 0,
    size = 3.5
  ) +
  
  scale_x_continuous(
    breaks = c(1, 2),
    labels = c(
      "Within-property change",
      "After year FE adjustment"
    ),
    limits = c(0.8, 2.35)
  ) +
  
  labs(
    x = NULL,
    y = "Price change from first sale (%)",
    linetype = "Flood Factor group",
    shape = NULL,
    title = "How year fixed effects remove common market movement",
    subtitle = "Arrows show the same year-specific market adjustment being subtracted from each property"
  )
```


```{r}
toy_decomp <- tibble::tribble(
  ~pin, ~sale_year, ~sale_stage, ~observed_log_price, ~year_fe,
  "A", 2015, "First sale",  12.20, 0.10,
  "A", 2022, "Second sale", 12.45, 0.28
) |>
  mutate(
    adjusted_log_price = observed_log_price - year_fe,
    sale_stage = factor(sale_stage, levels = c("First sale", "Second sale"))
  )

ggplot(toy_decomp) +
  geom_segment(
    aes(
      x = sale_stage,
      xend = sale_stage,
      y = observed_log_price,
      yend = adjusted_log_price
    ),
    arrow = arrow(length = unit(0.15, "inches")),
    linewidth = 0.8
  ) +
  
  geom_point(
    aes(
      x = sale_stage,
      y = observed_log_price,
      shape = "Observed sale price"
    ),
    size = 3
  ) +
  
  geom_point(
    aes(
      x = sale_stage,
      y = adjusted_log_price,
      shape = "After subtracting year FE"
    ),
    size = 3
  ) +
  
  geom_line(
    aes(
      x = sale_stage,
      y = adjusted_log_price,
      group = pin
    ),
    linewidth = 0.8,
    linetype = "dashed"
  ) +
  
  geom_text(
    aes(
      x = sale_stage,
      y = observed_log_price,
      label = paste0("Observed\n", round(observed_log_price, 2))
    ),
    nudge_y = 0.035,
    size = 3.5
  ) +
  
  geom_text(
    aes(
      x = sale_stage,
      y = adjusted_log_price,
      label = paste0("Adjusted\n", round(adjusted_log_price, 2))
    ),
    nudge_y = -0.04,
    size = 3.5
  ) +
  
  annotate(
    "text",
    x = 1,
    y = 12.11,
    label = "Subtract 2015 year effect",
    size = 3.5
  ) +
  
  annotate(
    "text",
    x = 2,
    y = 12.25,
    label = "Subtract 2022 year effect",
    size = 3.5
  ) +
  
  labs(
    x = NULL,
    y = "Log sale price",
    shape = NULL,
    title = "How year fixed effects enter a repeated-sale comparison",
    subtitle = "Each sale is adjusted by the market conditions in its own sale year"
  ) +
  
  theme_minimal()
```


```{r}
ggplot(toy_decomp) +
  geom_line(
    aes(
      x = sale_stage,
      y = observed_log_price,
      group = pin,
      linetype = "Raw observed change"
    ),
    linewidth = 0.8
  ) +
  
  geom_line(
    aes(
      x = sale_stage,
      y = adjusted_log_price,
      group = pin,
      linetype = "After year FE adjustment"
    ),
    linewidth = 0.8
  ) +
  
  geom_segment(
    aes(
      x = sale_stage,
      xend = sale_stage,
      y = observed_log_price,
      yend = adjusted_log_price
    ),
    arrow = arrow(length = unit(0.15, "inches")),
    linewidth = 0.7
  ) +
  
  geom_point(
    aes(x = sale_stage, y = observed_log_price),
    size = 3
  ) +
  
  geom_point(
    aes(x = sale_stage, y = adjusted_log_price),
    size = 3
  ) +
  
  annotate(
    "text",
    x = 1,
    y = 12.14,
    label = "2015 year FE",
    size = 3.5
  ) +
  
  annotate(
    "text",
    x = 2,
    y = 12.32,
    label = "2022 year FE",
    size = 3.5
  ) +
  
  labs(
    x = NULL,
    y = "Log sale price",
    linetype = NULL,
    title = "Year fixed effects adjust both sales in a repeated-sale pair",
    subtitle = "The model compares adjusted price changes, not raw sale-price changes"
  ) +
  
  theme_minimal()
```

