---
title: "Q1 Model comparison"
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    warning: false
    message: false
  #  error: true
params:
  data_dir: "data/processed/targets/sales"
  

---
```{r}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
library(rlang)
library(flextable)


clusters_county <- list(
  pin10      = ~ pin10#,
 # pin        = ~ pin,
#  clean_name = ~ clean_name#, FIRM_PAN   = ~ FIRM_PAN #,
#   nbhd_code  = ~ nbhd_code
)

clusters_basic <- list(
  pin10      = ~ pin10#,#  FIRM_PAN   = ~ FIRM_PAN#,
 # clean_name = ~ clean_name#
#  pin        = ~ pin
)

run_by_cluster <- function(formula, data, clusters, prefix = "Model") {
  purrr::imap(clusters, function(cl, nm) {
    fixest::feols(formula, data = data, cluster = cl)
  }) |>
    setNames(paste0(prefix, " (cluster: ", names(clusters), ")"))
}

# Convenience: bind multiple named lists of models into one named list
bind_models <- function(...) {
  out <- c(...)
  # guard against duplicate names (modelsummary will drop/merge silently)
  if(any(duplicated(names(out)))) {
    stop("Duplicate model names detected. Fix labels so each model has a unique name.")
  }
  out
}

extract_terms <- function(models, dataset_id, block_name) {
  # models: whatever bind_models() returns. If it's a list, iterate.
  # If bind_models returns a named list of models, this works.
  out <- lapply(names(models), function(mname) {
    m <- models[[mname]]

    tt <- broom::tidy(m)
    tt$model_name  <- mname
    tt$dataset_id  <- dataset_id
    tt$block       <- block_name
    tt$n_obs       <- stats::nobs(m)
    tt
  })

  dplyr::bind_rows(out)
}


```

# Compare datasets and output

```{r}
#| label: load-8-datasets
#| message: false
#| warning: false

data_dir <- params$data_dir %||% "data/processed/targets/sales"

dataset_map <- c(
  land_baseline    = "df_prep_land_baseline_final.rds",
  land_updated     = "df_prep_land_updated_final.rds",
  bldg_baseline    = "df_prep_bldg_baseline_final.rds",
  bldg_updated     = "df_prep_bldg_updated_final.rds",
  ptaxsim_baseline = "df_prep_ptaxsim_baseline_final.rds",
  ptaxsim_updated  = "df_prep_ptaxsim_updated_final.rds",
  risk500_baseline = "df_prep_risk500_baseline_final.rds",
  risk500_updated  = "df_prep_risk500_updated_final.rds"
)

# dataset_map <- c(
#   land_baseline    = "df_prep_land_final.rds",
#   #land_updated     = "df_prep_land_updated_final.rds",
#   bldg_baseline    = "df_prep_bldg_final.rds",
#   #bldg_updated     = "df_prep_bldg_updated_final.rds",
#   ptaxsim_baseline = "df_prep_ptaxsim_final.rds",
#   #ptaxsim_updated  = "df_prep_ptaxsim_updated_final.rds",
#   risk500_baseline = "df_prep_risk500_final.rds"
#   #risk500_updated  = "df_prep_risk500_updated_final.rds"
# )

datasets <- lapply(names(dataset_map), function(id) {
  path <- file.path(data_dir, dataset_map[[id]])
  df <- readRDS(path)
  df$dataset_id <- id
  df
})

drop_parcels <- c(
  "1129312017", # Building on sherwin. Land is in Coastal SFHA for 2018 but building is not. 
  "1129315024", # coastal building not in floodplain, on Jarvis!
  "1132400037", # building miiiight be in coastal floodplain but barely.
  "1405203011", # coastal building not in floodplain
  "1405203012", # coastal building not in floodplain
  "1405211015", # coastal building not in floodplain
  "1405211016", # coastal building not in floodplain
  "1405211021", # coastal building not in floodplain
  "1405211023", # coastal building not in floodplain
  "1405215017",# coastal building, partly in 1 in 500 year floodzone
  "1405403019",# coastal building not in floodplain
  "2130123021" # coastal building, not in floodplain according to redfin
)

datasets <- lapply(datasets, function(df) {
  df |> 
    filter(!pin10 %in% drop_parcels) |>
    filter(pin10 != "0710101038") |>
  # select(any_of(-c(clean_name.x, clean_name.y)) )|>
  mutate(Triad = case_when(
    clean_name == "Chicago" ~  "City",
    as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
    as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
  ),
      in_eff_sfha    = in_eff_sfha == 1,
      in_prelim_sfha = in_prelim_sfha == 1
    )  |>
    filter(!is.na(in_eff_sfha) & !is.na(in_prelim_sfha))
})

names(datasets) <- names(dataset_map)

# quick sanity
# data.frame(
#   dataset_id = names(datasets),
#   n_rows = vapply(datasets, nrow, numeric(1))
# )

add_stars <- function(p) {
  dplyr::case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ "+",
    TRUE     ~ ""
  )
}

```

# In_SFHA vs Added and Removed, with and without Triads

```{r}
#| label: model-fns
#| message: false
#| warning: false

fit_effective_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff County - Symmetric"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff County - Add or Remove"
    ),
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff Triads - Symmetric"
    ),

    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha*Triad + removedfrom_eff_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff Triads - Add or Remove"
    )
  )
}

fit_prelim_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ in_prelim_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim County - Symmetric"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim County - Add or Remove"
    ),
    run_by_cluster(
      log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim Triads - Symmetric"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha*Triad + removedfrom_prelim_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim Triads - Add or Remove"
    )
  )
}

```





```{r}
#| label: run-models-8x
#| message: false
#| warning: false

effective_models <- lapply(datasets, fit_effective_models)
prelim_models    <- lapply(datasets, fit_prelim_models)

```



```{r}
#| label: build-complete-term-grids
#| message: false
#| warning: false

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models), function(id) {
  extract_terms(prelim_models[[id]], id, "prelim")
}))
eff_tidy <- dplyr::bind_rows(lapply(names(effective_models), function(id) {
  extract_terms(effective_models[[id]], id, "eff")
}))

# ---- 1) Canonical term universes ----
terms_eff_main <- c("in_eff_sfhaTRUE", "addedto_eff_sfhaTRUE", "removedfrom_eff_sfhaTRUE")
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")

# include any Triad interaction terms that appear anywhere (across datasets/models)
terms_eff_int <- eff_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_eff_sfha") | str_detect(term, "addedto_eff_sfha") | str_detect(term, "removedfrom_eff_sfha"))) |>
  pull(term)

terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_eff_all <- unique(c(terms_eff_main, terms_eff_int))
terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))
```



# Grid Format

```{r}
#| column: screen


# ---- 2) Enforce a complete dataset × model × term grid ----
eff_grid <- eff_tidy |>
  filter(term %in% terms_eff_all) |>
  complete(dataset_id, model_name, term = terms_eff_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))

# ---- 3) Format coefficient cells (coef + stars; SE in parentheses on next line; missing as —) 
coef_cell <- function(est, se, p) {
  if_else(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = 2, format = "f"),
      add_stars(p),
      "\n(",
      formatC(se, digits = 2, format = "f"),
      ")"
    )
  )
}

eff_tbl <- eff_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

# ---- 4) Optional: enforce a consistent dataset column order (edit to match your IDs) ----
col_order <- c(
  "land_baseline","land_updated",
  "bldg_baseline","bldg_updated",
  "ptaxsim_baseline","ptaxsim_updated",
  "risk500_baseline","risk500_updated"
)

eff_tbl <- eff_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

# ---- 5) Wide robustness tables: rows = (model_name, term), cols = dataset_id ----
eff_wide <- eff_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)

# ---- 6) Display (or comment these out and display later) ----
  flextable::flextable(eff_wide)
```


```{r}
#| column: screen


flextable::flextable(pre_wide)

```


# Not GRID Format

```{r}
#| label: robust-table-effective
#| message: false
#| warning: false
#| column: page



eff_core <- eff_tidy |>
    filter(term %in% terms_eff_all) |>
  dplyr::mutate(
    estimate = round(estimate, 4),
    std.error = round(std.error, 4),
    statistic  = round(statistic, 3),
    p.value    = round(p.value, 3)
  )

eff_core <- eff_core |>
  dplyr::mutate(
    stars = add_stars(p.value),
    estimate_star = paste0(
      formatC(estimate, format = "f", digits = 2),
      stars
    )
  )

eff_core <- eff_core |>
  dplyr::mutate(
    coef_cell = paste0(
      formatC(estimate, digits = 2, format = "f"),
      add_stars(p.value),
      "\n(",
      formatC(std.error, digits = 2, format = "f"),
      ")"
    )
  )


eff_core |> dplyr::arrange(model_name, term, dataset_id)

```

```{r}
#| column: page

pre_core <- pre_tidy |>
    filter(term %in% terms_pre_all)  |>
  # dplyr::filter(
  #   term == "in_prelim_sfha" |
  # 
  #   stringr::str_detect(
  #     term,
  #     "^addedto_prelim_sfha$|^removedfrom_prelim_sfha$"
  #   ) |
  # 
  #   stringr::str_detect(
  #     term,
  #     "in_prelim_sfha:Triad|Triad:in_prelim_sfha|
  #      addedto_prelim_sfha:Triad|removedfrom_prelim_sfha:Triad|
  #      Triad:addedto_prelim_sfha|Triad:removedfrom_prelim_sfha"
  #   )
  # ) |>
  dplyr::mutate(
    estimate = round(estimate, 4),
    std.error = round(std.error, 4),
    statistic  = round(statistic, 3),
    p.value    = round(p.value, 3)
  )

pre_core <- pre_core |>
  dplyr::mutate(
    stars = add_stars(p.value),
    estimate_star = paste0(
      formatC(estimate, format = "f", digits = 2),
      stars
    )
  )

pre_core <- pre_core |>
  dplyr::mutate(
    coef_cell = paste0(
      formatC(estimate, digits = 2, format = "f"),
      add_stars(p.value),
      "\n(",
      formatC(std.error, digits = 2, format = "f"),
      ")"
    )
  )


pre_core |> dplyr::arrange(model_name, term, dataset_id)

```

## Effective FIRM Models


```{r}
#| label: robust-flextable-effective
#| message: false
#| warning: false
#| column: page
#| eval: false

eff_ft <- eff_core |>
  dplyr::select(dataset_id, model_name, term, estimate_star, std.error, statistic, p.value, n_obs) |>
  flextable::flextable()

eff_ft


```

## Preliminary FIRM Models

```{r}
#| label: robust-flextable-preliminary
#| message: false
#| warning: false
#| column: page
#| eval: false


pre_ft <- pre_core |>
  dplyr::select(dataset_id, model_name, term, estimate_star, std.error, statistic, p.value, n_obs) |>
  flextable::flextable()

pre_ft

```

# Number of treated observations

```{r}
table(datasets$risk500_baseline$in_eff_sfha)
table(datasets$bldg_baseline$in_eff_sfha)
table(datasets$risk500_baseline$addedto_prelim_sfha)
table(datasets$bldg_baseline$addedto_prelim_sfha)

```

```{r}
# ---- Treated-observation summary (added/removed) ----

to_logical01 <- function(x) {
  # Handles logical, 0/1, and character "0"/"1"/"TRUE"/"FALSE" tolerably.
  if (is.logical(x)) return(x)
  if (is.numeric(x) || is.integer(x)) return(as.logical(x))
  if (is.character(x)) {
    x2 <- toupper(trimws(x))
    return(dplyr::case_when(
      x2 %in% c("TRUE", "T", "1")  ~ TRUE,
      x2 %in% c("FALSE", "F", "0") ~ FALSE,
      TRUE                        ~ NA
    ))
  }
  as.logical(x)
}

treated_summary <- purrr::imap_dfr(datasets, function(df, id) {
  eff_add <- to_logical01(df$addedto_eff_sfha)
  eff_rem <- to_logical01(df$removedfrom_eff_sfha)
  pre_add <- to_logical01(df$addedto_prelim_sfha)
  pre_rem <- to_logical01(df$removedfrom_prelim_sfha)

  tibble::tibble(
    dataset_id = id,
    n_obs      = nrow(df),

    eff_added_obs   = sum(eff_add, na.rm = TRUE),
    eff_removed_obs = sum(eff_rem, na.rm = TRUE),
    eff_treated_obs = sum(eff_add | eff_rem, na.rm = TRUE),
    eff_treated_pct = eff_treated_obs / n_obs,
    eff_treated_pins = dplyr::n_distinct(df$pin10[eff_add | eff_rem]),
    pre_treated_pins = dplyr::n_distinct(df$pin10[pre_add | pre_rem]),

    pre_added_obs   = sum(pre_add, na.rm = TRUE),
    pre_removed_obs = sum(pre_rem, na.rm = TRUE),
    pre_treated_obs = sum(pre_add | pre_rem, na.rm = TRUE),
    pre_treated_pct = pre_treated_obs / n_obs
  )
}) |>
  dplyr::mutate(
    eff_treated_pct = scales::percent(eff_treated_pct, accuracy = 0.1),
    pre_treated_pct = scales::percent(pre_treated_pct, accuracy = 0.1)
  )

treated_summary_ft <- treated_summary |>
  flextable::flextable() |>
  flextable::autofit()

treated_summary_ft

```

# Added moddels and removed models


```{r}
#| label: othr-model-fns
#| message: false
#| warning: false

fit_effective_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
      data = df_prep |> filter(addedto_eff_sfha == FALSE),
      clusters = clusters_county,
      prefix = "Eff County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha * Triad | pin + sale_year,
      data = df_prep |> filter(addedto_eff_sfha == FALSE),
      clusters = clusters_county,
      prefix = "Eff Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
      data = df_prep |> filter(removedfrom_eff_sfha==FALSE),
      clusters = clusters_county,
      prefix = "Eff County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha * Triad | pin + sale_year,
      data = df_prep |> filter(removedfrom_eff_sfha==FALSE),
      clusters = clusters_county,
      prefix = "Eff Triads - A"
    )
  )
}

fit_prelim_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
      data = df_prep |> filter(addedto_prelim_sfha == FALSE),
      clusters = clusters_county,
      prefix = "Prelim County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha * Triad | pin + sale_year,
      data = df_prep |> filter(addedto_prelim_sfha == FALSE),
      clusters = clusters_county,
      prefix = "Prelim Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
      data = df_prep |> filter(removedfrom_prelim_sfha==FALSE),
      clusters = clusters_county,
      prefix = "Prelim County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha * Triad | pin + sale_year,
      data = df_prep |> filter(removedfrom_prelim_sfha==FALSE),
      clusters = clusters_county,
      prefix = "Prelim Triads - A"
    )
  )
}

```





```{r}
#| label: othr-run-models-8x
#| message: false
#| warning: false

effective_models2 <- lapply(datasets, fit_effective_models)
prelim_models2    <- lapply(datasets, fit_prelim_models)

```



```{r}
#| label: othr-build-complete-term-grids
#| message: false
#| warning: false

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models2), function(id) {
  extract_terms(prelim_models2[[id]], id, "prelim")
}))
eff_tidy <- dplyr::bind_rows(lapply(names(effective_models2), function(id) {
  extract_terms(effective_models2[[id]], id, "eff")
}))

# ---- 1) Canonical term universes ----
terms_eff_main <- c("in_eff_sfhaTRUE", "addedto_eff_sfhaTRUE", "removedfrom_eff_sfhaTRUE")
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")

# include any Triad interaction terms that appear anywhere (across datasets/models)
terms_eff_int <- eff_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_eff_sfha") | str_detect(term, "addedto_eff_sfha") | str_detect(term, "removedfrom_eff_sfha"))) |>
  pull(term)

terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_eff_all <- unique(c(terms_eff_main, terms_eff_int))
terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))
```



# Grid Format

```{r}
#| column: screen


# ---- 2) Enforce a complete dataset × model × term grid ----
eff_grid <- eff_tidy |>
  filter(term %in% terms_eff_all) |>
  complete(dataset_id, model_name, term = terms_eff_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


coef_cell <- function(est, se, p) {
  if_else(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = 2, format = "f"),
      add_stars(p),
      "\n(",
      formatC(se, digits = 2, format = "f"),
      ")"
    )
  )
}

eff_tbl <- eff_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

# ---- 4) Optional: enforce a consistent dataset column order (edit to match your IDs) ----
col_order <- c(
  "land_baseline","land_updated",
  "bldg_baseline","bldg_updated",
  "ptaxsim_baseline","ptaxsim_updated",
  "risk500_baseline","risk500_updated"
)

eff_tbl <- eff_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

# ---- 5) Wide robustness tables: rows = (model_name, term), cols = dataset_id ----
eff_wide <- eff_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)

# ---- 6) Display (or comment these out and display later) ----
  flextable::flextable(eff_wide)
```


```{r}
#| column: screen


flextable::flextable(pre_wide)

```

# Other models

## Create variables

Eventually make this another output from targets maybe to not waste time trying to run this. 


```{r}

datasets <- lapply(datasets, function(df){
  df |> 
 mutate(
   eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date),
    
    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(addedto_eff_sfha== TRUE) )
                                 & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removedfrom_eff_sfha== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added or removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(addedto_prelim_sfha == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removedfrom_prelim_sfha== TRUE), year(pre_date), 10000)
    
    
  ) |>
  ungroup() |>
  mutate(
    
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
        rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000)
  ) |>
  mutate(
   # qtr  = quarter(sale_date),     # 1 to 4
    #year = year(sale_date),            
    #sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    
    # 2005-01-01 2015-02-15 2019-06-28 2021-09-22 

    group_name_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" ~ 0,
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-07-01" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,

      TRUE ~ NA),
      
      ),
    treated_group_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha|removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ NA))
    )
    })
```


> Start hr!!! 


```{r}
#| label: tbl-filteredproperties-forRQ
#| tbl-cap: "Restricts the sample to parcels whose classification changed from in → out between FIRMs with comparison group of only properties that were Always in an SFHA."
#| 


datasets2 <- lapply(datasets, function(df) { 
  df |> 
    filter(change_type_prelim != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff ==10000 & treat_year_add_prelim == 10000)
})

fit_prelim_models <- function(df2) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha * Triad | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim Triads - R"
    )
  )

}



prelim_models_sub  <- lapply(datasets2, fit_prelim_models){

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models_sub), function(id) {
  extract_terms(prelim_models_sub[[id]], id, "prelim")
}))

# ---- 1) Canonical term universes ----
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")


terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))

# ---- 3) Format coefficient cells (coef + stars; SE in parentheses on next line; missing as —) 
coef_cell <- function(est, se, p) {
  if_else(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = 2, format = "f"),
      add_stars(p),
      "\n(",
      formatC(se, digits = 2, format = "f"),
      ")"
    )
  )
}

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

# ---- 4) Optional: enforce a consistent dataset column order (edit to match your IDs) ----
col_order <- c(
  "land_baseline","land_updated",
  "bldg_baseline","bldg_updated",
  "ptaxsim_baseline","ptaxsim_updated",
  "risk500_baseline","risk500_updated"
)

pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


flextable::flextable(pre_wide)

```



```{r}
    
datasets3 <- lapply(datasets, function(df) { 
  df |> 
 filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000)
}
)

fit_prelim_models <- function(df2) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha * Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim Triads - A"
    )
  )
}



prelim_models_sub2    <- lapply(datasets3, fit_prelim_models)

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models_sub2), function(id) {
  extract_terms(prelim_models[[id]], id, "prelim")
}))

# ---- 1) Canonical term universes ----
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")


terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))

# ---- 3) Format coefficient cells (coef + stars; SE in parentheses on next line; missing as —) 
coef_cell <- function(est, se, p) {
  if_else(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = 2, format = "f"),
      add_stars(p),
      "\n(",
      formatC(se, digits = 2, format = "f"),
      ")"
    )
  )
}

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))

# ---- 4) Optional: enforce a consistent dataset column order (edit to match your IDs) ----
col_order <- c(
  "land_baseline","land_updated",
  "bldg_baseline","bldg_updated",
  "ptaxsim_baseline","ptaxsim_updated",
  "risk500_baseline","risk500_updated"
)

pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


flextable::flextable(pre_wide)

```

