---
title: "Assessing Parallel Trends Under Staggered Treatment"
format:
  html: 
    code-fold: true
execute:
  echo: true
  warning: false
  error: true
#  eval: false
---

# Purpose

This document outlines the correct diagnostics for **parallel trends assumptions in staggered treatment designs** using difference-in-differences (DiD). The presence of staggered timing requires different estimators and more careful assumptions.

> **Source**: Baker et al. (2025), esp. pp. 7–10. Staggered designs require cohort-specific diagnostics and can invalidate conventional DiD methods if assumptions are unchecked.

---

```{r setup}
library(tidyverse)
library(fixest)

library(didFF)   # for testing if functional form matters for the analysis. Tests if parallel trends assumption is sensitive to functional form (i.e. logged variable vs unlogged variable)

options(scipen = 999)
# make_sfha_lineplot <- function(
#   df,
#   y_var = c("sale_price", "log_price"),
#   facet_var = c("pre_date"),                      # e.g. "pre_date", "Triad"
#   group_vars = c("event_remapped","prelim_sfha_category", "Triad", "pre_date_chr", "pre_date"),
#   title = "Pre- and Post-Event Slopes by SFHA Status",
#   linetype = c("event_remapped"),
#   color = c("prelim_sfha_category"),
#   y_label = NULL,
#   x_breaks = seq(2010, 2026, 4),
#   x_limits = c(2009, 2027)
# ) {
# 
#   y_var <- match.arg(y_var)
# 
#   # build grouping vars programmatically
#   grp_vars <- c("sale_year", group_vars, facet_var)
# 
#   df_summarised <- df |>
#     dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
#     dplyr::summarise(
#       avg_value = mean(.data[[y_var]], na.rm = TRUE),
#       median_value = median(.data[[y_var]], na.rm=TRUE),
#       n = dplyr::n(),
#       .groups = "drop"
#     )
# 
#   if (is.null(y_label)) {
#     y_label <- ifelse(
#       y_var == "sale_price",
#       "Avg. Sale Price",
#       "Avg. Logged Sale Price"
#     )
#   }
# 
#   ggplot2::ggplot(
#     df_summarised,
#     ggplot2::aes(
#       x = sale_year,
#       y = avg_value,
#       color = .data[[group_vars[1]]]
#     )
#   ) +
#     ggplot2::geom_point() +
#     ggplot2::geom_line() +
#     ggplot2::geom_smooth(aes(lty = event_remapped),method = "lm", se = FALSE) +
#     ggplot2::facet_wrap(stats::as.formula(paste("~", facet_var))) +
#     ggplot2::labs(
#       title = title,
#       x = NULL,
#       y = y_label,
#       caption = ""
#     ) +
#     ggplot2::scale_x_continuous(
#       breaks = x_breaks,
#       limits = x_limits
#     ) +
#     ggplot2::theme_classic() +
#     ggplot2::theme(legend.position = "bottom")
# }
# 


make_sfha_lineplot <- function(
  df,
  y_var = c("sale_price", "log_price"),
  group_vars = c("event_remapped", "prelim_sfha_category"),
  facet_vars = c("pre_date_chr"),     # can be length 0, 1, or more
  color_var = "prelim_sfha_category", # set NULL for no color mapping
  linetype_var = "event_remapped",    # set NULL for no linetype mapping
  title = "Pre- and Post-Event Slopes by SFHA Status",
  y_label = NULL,
  x_breaks = seq(2010, 2026, 4),
  x_limits = c(2009, 2027),
  show_smooth = TRUE
) {
  y_var <- match.arg(y_var)

  # --- sanity checks (prevents silent nonsense) ---
  needed <- unique(c("sale_year", y_var, group_vars, facet_vars, color_var, linetype_var))
  needed <- needed[!is.null(needed) & needed != ""]
  missing <- setdiff(needed, names(df))
  if (length(missing) > 0) {
    stop("Missing columns in df: ", paste(missing, collapse = ", "))
  }

  # --- summarise ---
  grp_vars <- unique(c("sale_year", group_vars, facet_vars))

  df_sum <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
    dplyr::summarise(
      avg_value = mean(.data[[y_var]], na.rm = TRUE),
      median_value = median(.data[[y_var]], na.rm = TRUE),
      n = dplyr::n(),
      .groups = "drop"
    ) |>
    # create a stable "series id" so lines/smooths don't cross-wire
    dplyr::mutate(.series = interaction(dplyr::across(dplyr::all_of(group_vars)), drop = TRUE))

  if (is.null(y_label)) {
    y_label <- if (y_var == "sale_price") "Avg. Sale Price" else "Avg. Logged Sale Price"
  }

  # --- base aesthetics ---
  aes_base <- ggplot2::aes(
    x = sale_year,
    y = avg_value,
    group = .series
  )

  if (!is.null(color_var))    aes_base$colour   <- rlang::sym(color_var)
  if (!is.null(linetype_var)) aes_base$linetype <- rlang::sym(linetype_var)

  p <- ggplot2::ggplot(df_sum, aes_base) +
    ggplot2::geom_point() +
    ggplot2::geom_line()

  if (isTRUE(show_smooth)) {
    p <- p + ggplot2::geom_smooth(method = "lm", se = FALSE)
  }

  # --- faceting (supports 0, 1, or many) ---
  if (length(facet_vars) == 0) {
    # no facets
  } else if (length(facet_vars) == 1) {
    p <- p + ggplot2::facet_wrap(stats::as.formula(paste0("~", facet_vars)))
  } else {
    # multiple facet variables -> facet_grid
    # e.g. facet_vars = c("triad", "pre_date_chr") => rows = triad, cols = pre_date_chr
    p <- p + ggplot2::facet_grid(stats::as.formula(paste(facet_vars[1], "~", facet_vars[2])))
  }

  p +
    ggplot2::labs(
      title = title,
      x = NULL,
      y = y_label
    ) +
    ggplot2::scale_x_continuous(breaks = x_breaks, limits = x_limits) +
    ggplot2::theme_classic() +
    ggplot2::theme(legend.position = "bottom")
}

df_prep <- readRDS("data/processed/targets/sales/df_prep_land_updated_final.rds") |>
  select(-c(clean_name.x, clean_name.y))
```


```{r}
table(df_prep$change_type)
table(df_prep$change_type_prelim)

df_prep <- df_prep |> 
  mutate(log_price = log(sale_price),
         in_eff_sfha = in_eff_sfha == 1,
         in_prelim_sfha = in_prelim_sfha == 1)

df_prep <- df_prep |>
  filter(#!is.na(high_ff_score) &
           !is.na(eff_date) &
      #     !is.na(clean_name) &
           !is.na(pre_date)# &
      #     !is.na(Triad)
  )


# are there pins that sell multiple times?
# df_prep |> group_by(sale_year, pin) |> mutate(n = n()) |> filter(n > 1)
# yes 


```



```{r recode-dfpreptest}
table(df_prep$pre_date)

df_prep <- df_prep |>
  
  mutate(
    # so I can subset by FIRM date in later steps
    eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date)) |>
  group_by(pin) |>
  arrange(sale_date) |>
  mutate(

    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(addedto_eff_sfha== TRUE) )
                                 & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removedfrom_eff_sfha== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added or removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(addedto_prelim_sfha == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removedfrom_prelim_sfha== TRUE), year(pre_date), 10000)
    
  ) |>
  ungroup() |>
  mutate(
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
        rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000),
    
    # adjustment for if a sale occurs in the same year that it is treated
    # if sale is before preliminary firm, it is coded as relative year == -1, not yet treated
    rel_year_add_prelim = ifelse(rel_year_add_prelim == 0 & sale_date < pre_date, -1, rel_year_add_prelim),
    rel_year_remove_prelim = ifelse(rel_year_remove_prelim == 0 & sale_date < pre_date, -1, rel_year_remove_prelim),

    rel_year_add_eff = ifelse(rel_year_add_eff == 0 & sale_date < eff_date, -1, rel_year_add_eff),
    rel_year_remove_eff = ifelse(rel_year_remove_eff == 0 & sale_date < eff_date, -1, rel_year_remove_eff)

  ) |>
  mutate(
    qtr  = quarter(sale_date),     # 1 to 4
    year = year(sale_date),            
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # for ALL properties in the updated firms
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    
    # 2005-01-01 2015-02-15 2019-06-28 2021-09-22 

    group_name_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # for ALL properties in the updated firms
      pre_date == "2005-01-01" ~ 0,
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-07-01" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,
      TRUE ~ NA),
      ))

df_prep <- df_prep |> 
  mutate(
    treated_group_eff = (case_when(
      # for TREATED propertes in updated FIRMs!
      eff_date == "2008-08-19" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 0,
      eff_date == "2019-11-01" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 2019,
      eff_date == "2021-09-10" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 2021,
      TRUE ~ NA)),
    
    treated_group_prelim = (case_when( 
      # for TREATED propertes in updated FIRMs!
      pre_date == "2005-01-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha|removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ 0)),
        treated_group_prelim_add = (case_when( 
      # for TREATED properties in updated FIRMs!
      pre_date == "2005-01-01" & (addedto_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha) ~ 2021,

      TRUE ~ 0)),
        treated_group_prelim_remove = (case_when( 
      # for TREATED propertes in updated FIRMs!
      pre_date == "2005-01-01" & (removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ 0))
    )

```

```{r}

df_prep <- df_prep |>
  group_by(pin) |>
  mutate(
    n_sales = n(),
    ever_added_prelim   = any(addedto_prelim_sfha == TRUE),
    ever_removed_prelim = any(removedfrom_prelim_sfha == TRUE),
    event_remapped = ifelse( sale_date < pre_date, "Pre", "Post"),
    ) |>
  ungroup() |>
  mutate(
    prelim_sfha_category = 
      case_when(
        ever_added_prelim & !ever_removed_prelim ~ "Added to prelim SFHA",
        ever_removed_prelim & !ever_added_prelim ~ "Removed from prelim SFHA",
        # ever_added_prelim & ever_removed_prelim  ~ "Multiple prelim transitions",
        change_type_prelim == "Always SFHA" ~ "Always SFHA",
        change_type_prelim == "Never SFHA" ~ "Never SFHA",
        TRUE ~ "CHECK ME"  ) 
  ) |> 
  ungroup()

df_prep <- df_prep |>
  # select(any_of(-c(clean_name.x, clean_name.y)) )|>
  mutate(Triad = case_when(
    clean_name == "Chicago" ~  "City",
    as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
    as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
  ),
    Triad = factor(Triad, levels = c("South", "North", "City") )
  ) 

```

I want a non-significant result for `sale_year x in_eff_sfha` & `sale_year x high_ff_score x in_eff_sfha` coefficient in the pre-event data. 


The coefficient on sale_year is the baseline slope.

The sale_year:in_eff_sfha term tells you whether the slope differs between properties in an SFHA vs not within the SFHA (within the baseline event period).


addedto_prelim_sfha=1(treated group)×1(post)

# Slope Test

```{r}
slopetest <- lm(log_price ~ sale_year*prelim_sfha_category, 
                df_prep |> filter(sale_date < pre_date | 
                                    (sale_date < 2017 & pre_date_chr == "2005-01-01")) 
)
modelsummary::modelsummary(slopetest)
```

# Placebo Test

```{r}
#| label: tbl-appendixA-placebotest
#| 

library(dplyr)
library(lubridate)
library(fixest)

# df_prep must have: pin, pin10, sale_date, sale_year, pre_date, prelim_sfha_category, log_price

run_placebo_did <- function(df,
                            fake_shift_years = 2,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }
  df_placebo <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label,
      placebo_date = pre_date %m-% years(fake_shift_years),
      placebo_post = sale_date >= placebo_date
    ) |>
    # keep only observations strictly before the *real* event (so placebo is truly placebo)
    filter(sale_date < pre_date) |>
    # optional: keep only observations with a defined placebo_date
    filter(!is.na(placebo_date))

  fml <- as.formula(paste0(
    "log_price ~ treated * placebo_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_placebo
  )
}


m_placebo <- run_placebo_did(df_prep, treated_label = "Removed from prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)

m_placebo <- run_placebo_did(df_prep, treated_label = "Added to prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)
```

```{r}
#| label: tbl-did_test_normal
#| tbl-cap: "Same set up as placebo test, but without the placebo. Includes all years of data."


run_normal_did <- function(df,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }

  df_did <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label, #== treated_label,
      treated_date = pre_date,
      event_post = (sale_date >= treated_date  & pre_date_chr != "2005-01-01")
    ) 

  fml <- as.formula(paste0(
    "log_price ~ treated * event_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_did
  )
}

m_did_add <- run_normal_did(df_prep, treated_label = "Added to prelim SFHA")
etable(m_did_add)

m_did_remove <- run_normal_did(df_prep, treated_label = "Removed from prelim SFHA")
etable(m_did_remove)
```


```{r}
#| label: tbl-two-method-styles-comparison
#| tbl-cap: "Two ways to set up the equation that should estimate the same effect."

df_same <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(
    treated = prelim_sfha_category == "Added to prelim SFHA",
    event_post = sale_date >= pre_date
  )

m1 <- feols(
  log_price ~ addedto_prelim_sfha | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)



m2 <- feols(
  log_price ~ I(treated * event_post) | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)

m3 <- feols(
  log_price ~ treated * event_post | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)

etable(m1, m2, m3)

```

prelim_sfha_category is for group membership (treated vs control group definition).

addedto_prelim_sfha is (probably) a post-treated status indicator (treated group switches on after its pre_date, controls never switch on).

```{r}
run_normal_did_fixed <- function(df,
                                 treated_label = "Added to prelim SFHA",
                                 control_label = "Never SFHA",
                                 unit_fe = "pin",
                                 time_fe = "sale_year",
                                 cluster_var = "pin10") {

  df2 <- df |>
    filter(prelim_sfha_category %in% c(treated_label, control_label)) |>
    mutate(
      treated_group = prelim_sfha_category == treated_label, # time-invariant
      post = sale_date >= pre_date,                          # time-varying
      did = treated_group * post
    )

  # canonical DiD (will match the did-only version)
  m_did <- feols(
    as.formula(paste0("log_price ~ treated_group * post | ", unit_fe, " + ", time_fe)),
    cluster = as.formula(paste0("~", cluster_var)),
    data = df2
  )

  # did-only version (should match on the treatment effect)
  m_did_only <- feols(
    as.formula(paste0("log_price ~ did | ", unit_fe, " + ", time_fe)),
    cluster = as.formula(paste0("~", cluster_var)),
    data = df2
  )

  list(m_did = m_did, m_did_only = m_did_only, data = df2)
}

out <- run_normal_did_fixed(df_prep)
etable(out$m_did, out$m_did_only)

```

**Interpretation: adding post changes what variation is attributed to “general post-period shifts among the sample” vs “differential post shift for treated relative to control.” That can easily shrink the interaction from -0.20 to -0.14.**

treated * post ≠ I(treated * post)

With staggered timing, post is not absorbed by year FE, so including it changes the regression and the interaction coefficient.



# Parallel Trends

## Graphs 

### Pre Trends


A couple large houses sold in the treatment categories with small samples easily skews the slopes of the pre trends. So visualizations of  year interactinos for slopes are not super useful. 

```{r}

df_prep |> 
  group_by(event_remapped, sale_year, prelim_sfha_category, pre_date_chr, pre_date ) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year, y = avg_price, color = prelim_sfha_category)) +
  geom_point() +
  geom_line() +

  geom_smooth(aes(linetype = event_remapped), method = "lm", se = FALSE) +
#  geom_vline(xintercept=pre_date_chr, lty = 2) +

  facet_wrap(~pre_date_chr) +
  labs(title = "Pre- and Post-Event Slopes by Triad and SFHA Status",
       caption = "",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010, 2026, 4), limits = c(2009, 2027) ) +
  theme_classic()+
  theme(legend.position = "bottom") 

```

```{r}
#| layout-ncol: 2

df_prep <- df_prep |> filter(!pin10 %in% c("0122400028", "0516106013"))

make_sfha_lineplot(
 # df_prep,
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  facet_vars = NULL,
  linetype_var = NULL,
   group_vars = c("prelim_sfha_category"),

  title     = "Pre-Event Trends for Cook County by SFHA Status"
)



make_sfha_lineplot(
 # df_prep,
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  facet_vars = "Triad",
  linetype_var = NULL,
  
  group_vars = c("prelim_sfha_category", "Triad"),
  
  title     = "Pre-Event Trends by Triad and SFHA Status"
)

make_sfha_lineplot(
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  group_vars = c("prelim_sfha_category", "pre_date_chr"),
  linetype_var = NULL,
  facet_vars = "pre_date_chr",
  title     = "Pre-Event Trends by Update Time and SFHA Status"
)


```

### All years 

```{r}
df_prep <- df_prep |>filter(!is.na(in_eff_sfha))

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_vars = "Triad",
  linetype_var  = NULL,
  group_vars = c("prelim_sfha_category", "Triad"),
  title     = "Trends by Triad and SFHA Status"
)

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_vars = "pre_date",
  color_var = "prelim_sfha_category",
    group_vars = c("event_remapped","prelim_sfha_category"),
  title     = "Trends by FIRM Date and SFHA Status"
)

make_sfha_lineplot(
  (df_prep |> filter(sale_price < 2000000)),
  y_var     = "sale_price",
  group_vars = c("event_remapped","prelim_sfha_category", "pre_date"),
  linetype_var = "event_remapped",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)
```

```{r}
#| layout-ncol: 2


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Always SFHA", "Removed from prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Never SFHA", "Added to prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)

```

## Added Pre Trend regression


```{r}

# ---- 1. prep years (run once; safe if they already exist) ----
df_prep <- df_prep |>
  mutate(
    pre_year = if ("pre_year" %in% names(df)) pre_year else as.integer(format(pre_date, "%Y")),
    eff_year = if ("eff_year" %in% names(df)) eff_year else as.integer(format(eff_date, "%Y")),
    event_time = sale_year - pre_year,
    event_time = ifelse(event_time == 0 & sale_date < pre_date, -1, event_time)
  )

# ---- 3. bin leads/lags ----
df_prep <- df_prep |>
  mutate(
    event_time_binned = case_when(
      event_time <= -5 ~ -5L,
      event_time >=  5 ~  5L,
      TRUE ~ as.integer(event_time)
    )
  )

# ---- 4. define sample + treatment (example: Added vs Never) ----
# Added to SFHA comparison!
df_es_add <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA")

# ---- 5. event-study regression ----
# base model, no flexible fixed effects
mod_es_add_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_add
)

# ---- 6. pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_add_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ---- 7. joint test of pre-trends ----
wald(mod_es_add_none, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(mod_es_add_none, xlab = "Years relative to map year", main = "Event Study: Added")

```

Pre Trend wald test shows that pre trend coefficients are slightly statistically significant from each other. Not a steady pre event trend.  This gets better when Triad fixed effects are added below!


To relax the assumption of countywide parallel trends, event-study models are augmented with cohort-specific time trends, implemented as interactions between sale year and assessment triad or preliminary map cohort. This allows price trajectories to vary flexibly across institutional groupings while preserving identification from within-cohort deviations around the map update.

### Added pre trend events by Triad 


Properties follow the same trend within institutional cohorts
(assessment Triads or map-update cohorts)


```{r}

# ---- 5. EVENT STUDY WITH FLEXIBLE TRENDS ----

## (A) Flexible trends by TRIAD
mod_es_add_triad <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es_add
)


# (3) Pre-year cohort trends
mod_es_add_preyear <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^pre_year,
  cluster = ~ pin10,
  data = df_es_add
)

# ---- 6. pre-trend extraction (example: triad version) ----
pretrends_triad <- broom::tidy(mod_es_add_triad) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_triad

# ---- 7. joint test of pre-trends ----
wald(mod_es_add_triad, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(
  mod_es_add_triad,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends: Added"
)

```

Wald test is no longer statistically significant. Passes pre-trend test.


```{r}
# ---- 3. collect models ----
mods <- list(
  "No flexible trends"     = mod_es_add_none,
  "Triad-specific trends" = mod_es_add_triad,
  "Pre-year cohort trends"= mod_es_add_preyear
)

coef_map <- broom::tidy(mod_es_add_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(
    rel_time = as.integer(str_extract(term, "-?\\d+")),
    clean = paste0("t = ", rel_time)
  ) |>
  arrange(rel_time) |>
  pull(clean, term)

# ---- 5. comparison table ----
modelsummary::modelsummary(
  mods,
  coef_map = coef_map,
  estimate  = "{estimate}{stars}",
  statistic = "({std.error})",
  stars = c("*" = .10, "**" = .05, "***" = .01),
  gof_omit = "Adj|Pseudo|Within|RMSE"
)
```

"Table X compares event-study estimates under alternative assumptions about price trends. Allowing for assessment-triad-specific trends modestly attenuates estimated effects while preserving the overall dynamic pattern. More aggressive cohort-specific trends based on preliminary map year further reduce precision, reflecting limited identifying variation once highly flexible trends are imposed."



```{r}
# Pick shapes that are visually distinct and legible
shape_vals <- c(
  "No trends"        = 16, # filled circle
  "Triad trends"     = 17, # filled triangle
  "Pre-year trends"  = 15  # filled square
)

linetype_vals <- c(
  "No trends"        = "solid",
  "Triad trends"     = "dashed",
  "Pre-year trends"  = "dotted"
)


extract_es <- function(mod, label) {
  broom::tidy(mod) |>
    filter(str_detect(term, "^event_time_binned::")) |>
    mutate(
      rel_time = as.integer(str_extract(term, "-?\\d+")),
      spec = label
    )
}

es_df <- bind_rows(
  extract_es(mod_es_add_none,    "No trends"),
  extract_es(mod_es_add_triad,   "Triad trends"),
  extract_es(mod_es_add_preyear, "Pre-year trends")
)

ref_row <- es_df |>
  distinct(spec) |>
  mutate(
    rel_time  = -1,
    estimate  = 0,
    std.error = 0,
    ref = TRUE
  )

es_df_plot <- bind_rows(
  es_df |> mutate(ref = FALSE),
  ref_row
)

ggplot(es_df_plot, aes(x = rel_time, y = estimate, group = spec)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  geom_vline(xintercept = -1, linetype = "dotted") +

  # confidence intervals (skip ref period automatically since se = 0)
  geom_errorbar(
    aes(
      ymin = estimate - 1.96 * std.error,
      ymax = estimate + 1.96 * std.error,
      linetype = spec
    ),
    width = 0.15
  ) +

  geom_line(aes(linetype = spec), linewidth = 0.6) +

  geom_point(
    aes(shape = spec),
    size = 2.3,
    stroke = 0.6
  ) +

  # OPTIONAL: emphasize reference period
  geom_point(
    data = subset(es_df_plot, ref),
    shape = 21,       # hollow circle
    size = 3,
    stroke = 0.9
  ) +

  scale_shape_manual(values = c(
    "No trends"       = 16,
    "Triad trends"    = 17,
    "Pre-year trends" = 15
  )) +
  scale_linetype_manual(values = c(
    "No trends"       = "solid",
    "Triad trends"    = "dashed",
    "Pre-year trends" = "dotted"
  )) +

  labs(
    x = "Years relative to map year",
    y = "Estimated effect on log(price)",
    shape = "Specification",
    linetype = "Specification",
    title = "Event-study estimates under alternative trend assumptions",
    subtitle = "Year −1 is the omitted reference period (normalized to zero)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")


```



## Removed Pre Trend Regression

```{r}
# ---- 4. define sample + treatment (example: Added vs Never) ----
df_es_removed <- df_prep |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA")

# ---- 5. event-study regression ----
mod_es_removed_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_removed
)

mod_es_removed_preyear <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year^pre_year,
  cluster = ~ pin10,
  data = df_es_removed
)
# ---- 6. pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_removed_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ---- 7. joint test of pre-trends ----
wald(mod_es_removed_none, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(mod_es_removed_none, xlab = "Years relative to map year", main = "Event Study: Removed")

```

> Failed pre-trend test: Coeficients werestatistically significant from each other.  Gets better when using Triads below!

### Removed from SFHA pre trends by Triad 


Properties follow the same trend within institutional cohorts
(assessment Triads or map-update cohorts)


```{r}


##  Flexible trends by Triad
mod_es_removed_triad <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es_removed
)

# ---- 6. pre-trend extraction (example: triad version) ----
pretrends_firm <- broom::tidy(mod_es_removed_triad) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_firm

# ---- 7. joint test of pre-trends ----
wald(mod_es_removed_triad, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(
  mod_es_removed_triad,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends: Removed"
)

```



```{r}
# ---- 3. collect models ----
mods <- list(
  "No flexible trends"     = mod_es_removed_none,
  "Triad-specific trends" = mod_es_removed_triad,
  "Pre-year cohort trends"= mod_es_removed_preyear
)

coef_map <- broom::tidy(mod_es_removed_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(
    rel_time = as.integer(str_extract(term, "-?\\d+")),
    clean = paste0("t = ", rel_time)
  ) |>
  arrange(rel_time) |>
  pull(clean, term)

# ---- 5. comparison table ----
modelsummary::modelsummary(
  mods,
  coef_map = coef_map,
  estimate  = "{estimate}{stars}",
  statistic = "({std.error})",
  stars = c("*" = .10, "**" = .05, "***" = .01),
  gof_omit = "Adj|Pseudo|Within|RMSE"
)
```



```{r}
extract_es <- function(mod, label) {
  broom::tidy(mod) |>
    filter(str_detect(term, "^event_time_binned::")) |>
    mutate(
      rel_time = as.integer(str_extract(term, "-?\\d+")),
      spec = label
    )
}

es_df <- bind_rows(
  extract_es(mod_es_removed_none,    "No trends"),
  extract_es(mod_es_removed_triad,   "Triad trends"),
  extract_es(mod_es_removed_preyear, "Pre-year trends")
)

ref_row <- es_df |>
  distinct(spec) |>
  mutate(
    rel_time  = -1,
    estimate  = 0,
    std.error = 0,
    ref = TRUE
  )

es_df_plot <- bind_rows(
  es_df |> mutate(ref = FALSE),
  ref_row
)

ggplot(es_df_plot, aes(x = rel_time, y = estimate, group = spec)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  geom_vline(xintercept = -1, linetype = "dotted") +

  # confidence intervals (skip ref period automatically since se = 0)
  geom_errorbar(
    aes(
      ymin = estimate - 1.96 * std.error,
      ymax = estimate + 1.96 * std.error,
      linetype = spec
    ),
    width = 0.15
  ) +

  geom_line(aes(linetype = spec), linewidth = 0.6) +

  geom_point(
    aes(shape = spec),
    size = 2.3,
    stroke = 0.6
  ) +

  # OPTIONAL: emphasize reference period
  geom_point(
    data = subset(es_df_plot, ref),
    shape = 21,       # hollow circle
    size = 3,
    stroke = 0.9
  ) +

  scale_shape_manual(values = c(
    "No trends"       = 16,
    "Triad trends"    = 17,
    "Pre-year trends" = 15
  )) +
  scale_linetype_manual(values = c(
    "No trends"       = "solid",
    "Triad trends"    = "dashed",
    "Pre-year trends" = "dotted"
  )) +

  labs(
    x = "Years relative to map year",
    y = "Estimated effect on log(price)",
    shape = "Specification",
    linetype = "Specification",
    title = "Event-study estimates under alternative trend assumptions",
    subtitle = "Year −1 is the omitted reference period (normalized to zero)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

```




## Always and Never Treated

```{r}
# ---- 4. define sample + treatment (example: Added vs Never) ----
df_es_neither <- df_prep |>
  filter(prelim_sfha_category %in% c("Never SFHA", "Always SFHA")) |>
 mutate(treated = prelim_sfha_category == "Always SFHA",
        sale_year_factor = factor(sale_year))

# ---- 5. event-study regression ----
mod_es_neither_none <- feols(
  log(sale_price) ~ i(sale_year_factor, treated, ref = 2016) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_neither
)

# ---- 6. pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_neither_none) |>
  filter(str_detect(term, "^sale_year_factor::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 2016) |>
  arrange(rel_time)

pretrends

# ---- 7. joint test of pre-trends ----
wald(mod_es_neither_none, keep = "sale_year_factor::(2010|2011|2012|2013)")

# ---- 8. plot ----
iplot(mod_es_neither_none, xlab = "Years relative to map year", main = "Event Study: Never Treated and Always Treated")

```

# Placebo Event: 2014

 **Always SFHA and Never SFHA, aka Always Treated and Never Treated Observations**

In a pre-period only window (before any relevant map change), assign a fake “event year” and estimate whether the difference between always-in vs never-in changes over event time before the placebo event. If the lead coefficients aren’t flat, you’ve got non-parallel trends.



```{r}
test_parallel_trends_placebo <- function(df,
                                        id_var = "pin",
                                        year_var = "sale_year",
                                        y_var = "sale_price",
                                        group_var = "change_type_prelim",  # 1 = always-in, 0 = never-in
                                        placebo_year = 2014,
                                        pre_start = 2010,
                                        pre_end = 2018,   # should be BEFORE any real prelim/effective year used in this sample
                                        rel_window = c(-5, 5),
                                        cluster_var = "pin10") {

  stopifnot(all(c(id_var, year_var, y_var, group_var) %in% names(df)))

  d <- df |>
    filter(.data[[group_var]] %in% c("Never SFHA", "Always SFHA")) |>
    filter(.data[[year_var]] >= pre_start, .data[[year_var]] <= pre_end) |>
    mutate(
      log_price = log(.data[[y_var]]),
      rel_t = .data[[year_var]] - placebo_year,
      rel_t = ifelse(rel_t == 0 & sale_date < as.Date("2014-01-01"), -1, rel_t)
    ) |>
    filter(rel_t >= rel_window[1] & rel_t <= rel_window[2])

  # Event-study style: year FE are included; identification comes from within-id changes and relative-time x group interaction.
  # `i(rel_t, group, ref = -1)` gives coefficients for each event time for group==1 relative to group==0,
  # normalized to rel_t = -1.
  fml <- as.formula(paste0(
    "log_price ~ i(rel_t, ", group_var, ", ref = -1) | ",
    id_var, " + ", year_var
  ))

  m <- feols(
    fml,
    data = d,
    cluster = as.formula(paste0("~", cluster_var))
  )

  # # Extract event-time coefficients in a tidy-ish way
  # ct <- broom::tidy(m) |>
  #   filter(grepl("^rel_t::", term)) |>
  #   mutate(
  #     rel_t = as.integer(sub("rel_t::", "", term)),
  #     is_lead = rel_t < 0
  #   )

  ct <- broom::tidy(m) |>
  dplyr::filter(grepl("^rel_t::", term)) |>
  dplyr::mutate(
    rel_t   = as.integer(sub("^rel_t::(-?\\d+).*", "\\1", term)),
    group   = sub("^.*change_type_prelim::", "", term),
    is_lead = rel_t < 0
  )

  
  # Simple visual
  p <- ggplot(ct, aes(x = rel_t, y = estimate)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    geom_point() +
    scale_x_continuous(limits = c(-5, 5)) +

    labs(
      x = "Event time (years relative to placebo year)",
      y = "Difference (Always-in minus Never-in), relative to t = -1",
      title = "Placebo event-study pre-trend test"
    ) +
    theme_minimal()

  list(
    data_used = d,
    model = m,
    coef_table = ct,
    plot = p
  )
}

# You need a dataset that contains ONLY always-in and never-in observations for the relevant geography/time,
# and a window that is truly pre-treatment for that geography.
res <- test_parallel_trends_placebo(
  df = df_prep,                       
  id_var = "pin",                    
  year_var = "sale_year",
  y_var = "sale_price",
  group_var = "prelim_sfha_category",      
  placebo_year = 2014,
  pre_start = 2010,
  pre_end = 2019,                
  rel_window = c(-5, 5),
  cluster_var = "pin10"
)

res$plot
summary(res$model)
res$coef_table

```

Not super significantly different but probably not truly parallel trends during pre-trends?


```{r manual-wald-test}
# Test whether ALL lead coefficients are zero
cn <- names(coef(res$model))
lead_cn <- cn[str_detect(cn, "^rel_t::-")]

# Pull coefficients + vcov for the lead terms
b <- coef(res$model)[lead_cn]
V <- vcov(res$model)[lead_cn, lead_cn, drop = FALSE]

# Basic sanity checks
stopifnot(length(b) > 0)
if (anyNA(V) || any(!is.finite(V))) {
  stop("VCOV for lead terms contains NA/Inf. Joint test cannot be computed.")
}

# Compute Wald statistic: b' V^{-1} b
# Use solve(); if singular, fall back to generalized inverse
W <- tryCatch(
  as.numeric(t(b) %*% solve(V, b)),
  error = function(e) {
    as.numeric(t(b) %*% MASS::ginv(V) %*% b)
  }
)

df <- length(b)
p  <- 1 - pchisq(W, df = df)

list(
  statistic = W,
  df = df,
  p_value = p,
  n_leads_tested = df,
  leads = lead_cn
)

```


```{r remove-multisales-peryear}
#| eval: false
#| include: false
df_clean <- df_prep |> 
  mutate(
    sale_quarter = quarter(sale_date),
    pin_num = as.numeric(pin)
  ) |> 
  ungroup() |>
  group_by(pin_num, sale_year, pre_date, eff_date, in_eff_sfha, #addedto_eff_sfha
           ) |> 
  summarize(
    log_price = mean(log_price, na.rm=TRUE), 
    ) |> ungroup()


# are there pins that sell multiple times 
# df_clean |> group_by(sale_year, pin_num) |> mutate(n = n()) |> filter(n > 1) 
# not any more
```

> “Indicators for preliminary SFHA additions and removals are defined at the transaction-pair level. Observations with no change between consecutive sales are coded as zero; missing values therefore indicate the absence of a preliminary SFHA transition rather than missing information.”

```{r}
q1_data <- df_prep 

prop_summary_prelim <- q1_data |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    price = mean(sale_price),
    ever_added_prelim   = any(addedto_prelim_sfha == TRUE),
    ever_removed_prelim = any(removedfrom_prelim_sfha == TRUE),
    change_type_prelim = first(change_type_prelim)) |>
  mutate(
    prelim_sfha_category = 
      case_when(
        ever_added_prelim & !ever_removed_prelim ~ "Added to prelim SFHA",
        ever_removed_prelim & !ever_added_prelim ~ "Removed from prelim SFHA",
        # ever_added_prelim & ever_removed_prelim  ~ "Multiple prelim transitions",
        change_type_prelim == "Always SFHA" ~ "Always SFHA",
        change_type_prelim == "Never SFHA" ~ "Never SFHA",
        TRUE ~ "CHECK ME"  ) 
  )

prop_summary_prelim

prelim_sfha_stats <- prop_summary_prelim |>
  group_by(prelim_sfha_category) |>
  mutate(
    avg_sales_per_property = mean(n_sales)) |>
  summarize(
    n_properties = n(),
    n_sales = sum(n_sales),
    mean_price = mean(price),
    median_price = median(price),
    avg_sales_per_property = first(avg_sales_per_property),
    .groups = "drop"
  )

prelim_sfha_stats
```
```{r}
prelim_event_counts <- q1_data |>
  summarize(
    n_sales = n(),
    n_added_events = sum(addedto_prelim_sfha),
    n_removed_events = sum(removedfrom_prelim_sfha),
    pct_sales_with_event = (n_added_events + n_removed_events) / n_sales
  )
prelim_event_counts
```

“Preliminary SFHA reclassifications occur in approximately X% of observed transactions.”


```{r eval = FALSE}

data_dictionary <- df_prep |>
  summarise(across(
    everything(),
    list(
      class  = ~ paste(class(.), collapse = ", "),
      n_na   = ~ sum(is.na(.)),
      n_uniq = ~ n_distinct(.)
    ),
    .names = "{.col}__{.fn}"
  )) |>
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_sep = "__"
  ) |>
  arrange(variable)

write.csv(data_dictionary, "q1_data_dictionary.csv", row.names = FALSE)


skim_summary <- skimr::skim(df_prep)

skim_summary |>
  as.data.frame() |>
  write.csv("q1_skim_summary.csv", row.names = FALSE)


```


# Step 0: Descriptive Stats

```{r}
property_summary <- df_prep |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price),
    # FIRM exposure
    firm_date = first(pre_date),
    ever_firm_update =  ifelse(first(pre_date)=="2005-01-01",FALSE, TRUE),

    # SFHA dynamics
        change_type = first(change_type)
  )
property_summary
```

## A. Properties with no FIRM update vs ever updated

```{r}
firm_update_stats <- property_summary |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales),
    avg_price = mean(mean_price), # avg price of #avg price per property, kinda weird stat
  )

firm_update_stats
```


```{r}
firm_update_stats <- df_prep |>
     mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n_distinct(pin),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )

firm_update_stats
```

## B. Properties by FIRM panel exposure

```{r}
firm_panel_stats <- property_summary |>
  group_by(firm_date) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales)
  ) |>
  arrange(firm_date)

firm_panel_stats
```

## C. SFHA status categories

```{r}
#| layout-ncol: 2


sfha_category_stats <- df_prep |>
  group_by(pin) |> mutate(n_sales = n()) |> ungroup() |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    .groups = "drop"
  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- df_prep |>
    mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    #avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats
```

## D. Cross tab

```{r}
sfha_sales_stats <- df_prep |>
  group_by(change_type_prelim, pre_date) |>
  summarize(
    n_sales = n(),
    n_props = n_distinct(pin),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )
sfha_sales_stats
```

```{r}
price_summary <- df_prep |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    p10 = quantile(sale_price, 0.10, na.rm = TRUE),
    p90 = quantile(sale_price, 0.90, na.rm = TRUE)
  )
price_summary

price_by_sfha <- df_prep |>
  group_by(change_type_prelim) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    .groups = "drop"
  )
price_by_sfha
```

```{r}
geo_summary <- df_prep |>
  distinct(pin, Township, Triad) |>
  summarize(
    n_properties = n(),
    n_townships = n_distinct(Township),
    n_triads = n_distinct(Triad)
  )
geo_summary
```

```{r}
housing_type_summary <- df_prep |>
  distinct(pin, condo, class) |>
  summarize(
    n_properties = n(),
    condo_share = mean(condo == "Condo", na.rm = TRUE),
    n_classes = n_distinct(class)
  )
housing_type_summary
```

# Step 1: Define Treatment Cohorts


**Purpose**: Identify the first year each unit enters treatment. This cohort structure is required to estimate group-time ATT or run cohort-specific checks.

See `treat_group_prelim`


---


# Step 3: Estimate Group-Time ATT with Staggered Design Tools

group: groups based on FIRM panels that were updated at once
treated:


```{r eval=FALSE}
library(did)
df_es_removed <- df_es_removed |> 
  mutate(#treated_group_prelim_remove = as.numeric(treated_group_prelim_remove),
         pin_num = as.numeric(pin))

table(df_es_removed$change_type_prelim)
table(df_es_removed$treated_group_prelim_remove)

prelim_remove_att_gt_out <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "treated_group_prelim_remove",

                     data = df_es_removed,
                    # panel = FALSE,
                     allow_unbalanced_panel = TRUE)

summary(prelim_remove_att_gt_out)
ggdid(prelim_remove_att_gt_out)


# att_gt_eff_remove <- att_gt(yname = "log_price",
#                      tname = "sale_year",
#                      idname = "pin_num",
#                      gname = "group_name_remove",
#                      data = q3_sales,
#                      panel = TRUE,
#                      allow_unbalanced_panel = TRUE)
# summary(att_gt_eff_remove)
# ggdid(att_gt_eff_remove)

# att_gt_eff_add <- att_gt(yname = "log_price",
#                      tname = "sale_year",
#                      idname = "pin_num",
#                      gname = "group_name_add",
#                      data = q3_sales,
#                      panel = TRUE,
#                      allow_unbalanced_panel = TRUE)
# summary(att_gt_eff_add)
# ggdid(att_gt_eff_add)
```


**Purpose**: Estimate cohort-specific treatment effects that respect staggered timing using the `did` package.

**Why it matters**: This avoids “forbidden comparisons”—treating already-treated units as controls—and calculates average treatment effects relative to treatment timing, conditional on never-treated or not-yet-treated comparisons.


---

# Step 4: Visualize Event Study

Aggregated effect


```{r}
#| error: true
#| eval: false

# aggregate the group-time average treatment effects
agg_output <- aggte(prelim_add_att_gt_out, type = "dynamic")
summary(agg_output)

ggdid(agg_output)

```

**Purpose**: Plot treatment effects by event time (relative year to treatment) across cohorts.

**Why**: Validates the parallel trends assumption by visually assessing whether pre-treatment coefficients hover around zero.

> Baker et al. (2025, p. 9): "Pre-treatment effects should be statistically indistinguishable from zero."

---

# Step 5: Interpret Pre-Treatment Periods

Review the event study plot:   
- Are the estimates for periods prior to treatment flat and centered around zero?  
- Are the confidence intervals wide or tight?  
- Do any of the pre-treatment estimates appear significantly different from zero?  

**Why**: Significant pre-trends violate the key identifying assumption of DiD.

---

# Step 6: Run Placebo Tests (Optional but Recommended)

**Purpose**: Estimate treatment effects in periods before any treatment occurs.

**Why**: If “effects” show up before treatment, you’ve got either model misspecification or anticipation dynamics. Either way, your core assumptions are shaky.


---

# Step 8: Check for Spillovers or Anticipation

**Why**: Treatment effect estimates require no interference or preemptive market reactions.

---

# Step 9: Explicitly State Identification Assumptions

In your write-up, clearly state:
- Parallel trends hold for treated and not-yet-treated units
- Treatment timing is as-good-as-random conditional on covariates and fixed effects
- No spillover effects or contamination
- No anticipatory responses


> Baker et al. (2025, p. 10): "Each assumption must be directly defended."