---
title: "Assessing Parallel Trends Under Staggered Treatment"
format:
  html: default
execute:
  echo: true
  warning: false
#  eval: false
---

# Purpose

This document outlines the correct diagnostics for **parallel trends assumptions in staggered treatment designs** using difference-in-differences (DiD). The presence of staggered timing requires different estimators and more careful assumptions.

> **Source**: Baker et al. (2025), esp. pp. 7–10. Staggered designs require cohort-specific diagnostics and can invalidate conventional DiD methods if assumptions are unchecked.

---

```{r}
library(tidyverse)
library(didFF)   # for testing if functional form matters for the analysis. Tests if parallel trends assumption is sensitive to functional form (i.e. logged variable vs unlogged variable)

options(scipen = 999)

df_prep <- readRDS("data/processed/df_prep_buildings.rds") |>
  select(-c(clean_name.x, clean_name.y))

df_prep <- df_prep |> 
  filter(pin10 != "0710101038") |>
  mutate(log_price = log(sale_price))

df_prep <- df_prep |>
  filter(!is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date) &
           !is.na(Triad)
  )


# are there pins that sell multiple times 
df_prep |> group_by(sale_year, pin) |> mutate(n = n()) |> filter(n > 1)
# yes 

table(df_prep$eff_date)

df_clean <- df_prep |> 
  mutate(
    sale_quarter = quarter(sale_date),
    pin_num = as.numeric(pin)
  ) |> 
  ungroup() |>
  group_by(pin_num, sale_year, eff_date, in_eff_sfha, #addedto_eff_sfha
           ) |> 
  summarize(
    log_price = mean(log_price, na.rm=TRUE), 
    ) |> ungroup()


# are there pins that sell multiple times 
df_clean |> group_by(sale_year, pin_num) |> mutate(n = n()) |> filter(n > 1) 
# not any more
```

# Step 1: Define Treatment Cohorts

```{r}
#| label: eff-salesdata

# Define cohort based on first year treated
data <- df_clean |>
  mutate(
    c_i = ifelse(eff_date == "2008-08-19", 1, 0 ), # indicator for if never treated group
  
         group_name = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated. 
           eff_date == "2008-08-19" ~ 0,
           eff_date == "2019-11-01" ~ 2019,
           eff_date == "2021-09-10" ~ 2021,
           TRUE~ NA),
      #   period_g = sale_year-2011    #  recenter sale year to make period variable
          d_it =   ifelse(sale_year > 2020 & in_eff_sfha == 1 & group_name!=0, 1, 0),  # indicator for if treated by time t

    ) |>
  ungroup()

table(df_prep$in_eff_sfha)

q3_sales <- df_prep |>    
  mutate(    
    pin_num = as.numeric(pin),
    sale_quarter = quarter(sale_date)) |>
  filter(sale_quarter == 3) |> 
  group_by(pin_num, sale_year, eff_date, in_eff_sfha
  ) |> 
  summarize(
    log_price = mean(log_price, na.rm=TRUE), 
  ) |> 
  ungroup() |>
  mutate(
    group_name = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated. 
      eff_date == "2008-08-19"  ~ 0,
      eff_date == "2019-11-01"  ~ 2019,
      eff_date == "2021-09-10"  ~ 2021,
      #eff_date == "2019-11-01" & removedfrom_eff_sfha == "MappedOut" ~ 2019,
     # eff_date == "2021-09-10" & removedfrom_eff_sfha == "MappedOut" ~ 2021,
      TRUE ~ 0),
    #   period_g = sale_year-2011    #  recenter sale year to make period variable
  )
  
table(q3_sales$group_name)

```


```{r}
#| label: prelim-salesdata

table(df_prep$pre_date)
# 2015-02-12 2019-06-26 2021-09-22 
table(df_prep$in_prelim_sfha)

prelim_q3_sales <- df_prep |>    
  mutate(    
    pin_num = as.numeric(pin),
    sale_quarter = quarter(sale_date)) |>
  filter(sale_quarter == 3) |> 
  group_by(pin_num, sale_year, pre_date, in_prelim_sfha) |> 
  summarize(
    log_price = mean(log_price, na.rm=TRUE)) |> 
  ungroup() |>
  mutate(
    #d_it =   ifelse(sale_year >= 2020 & in_prelim_sfha == 1,1, 0),  # indicator for if treated by time t
    
    group_name = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated. 
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-06-26" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,

      # pre_date == "2015-02-12" & in_prelim_sfha== "SFHA"  ~ 2015,
      # pre_date == "2019-06-26" & in_prelim_sfha== "SFHA"~ 2019,
      # pre_date == "2021-09-22" & in_prelim_sfha == "SFHA" ~ 2021,
      TRUE~ 0),
  )

table(prelim_q3_sales$group_name)
```

**Purpose**: Identify the first year each unit enters treatment. This cohort structure is required to estimate group-time ATT or run cohort-specific checks.

---


# Step 3: Estimate Group-Time ATT with Staggered Design Tools

group: groups based on FIRM panels that were updated at once
treated:


```{r}
library(did)
att_gt_out <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "group_name",
                     xformla = ~in_eff_sfha,
                     
                     data = q3_sales,
                     panel = TRUE,
                     allow_unbalanced_panel = TRUE)

summary(att_gt_out)
ggdid(att_gt_out)

#saveRDS(out2, file = "outputs/didQ1_model_output.rds")
#saveRDS(p2, file = "outputs/didQ1_plot_output.rds")
```


```{r eval=FALSE}
prelim_att_gt_output <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "group_name",
                     data = prelim_q3_sales,
                     allow_unbalanced_panel = TRUE)

summary(prelim_att_gt_output)
ggdid(prelim_att_gt_output)
```

**Purpose**: Estimate cohort-specific treatment effects that respect staggered timing using the `did` package.

**Why it matters**: This avoids “forbidden comparisons”—treating already-treated units as controls—and calculates average treatment effects relative to treatment timing, conditional on never-treated or not-yet-treated comparisons.


---

# Step 4: Visualize Event Study

Aggregated effect


```{r}
# aggregate the group-time average treatment effects
agg_output <- aggte(att_gt_out, type = "dynamic")
summary(agg_output)

ggdid(agg_output)

```

**Purpose**: Plot treatment effects by event time (relative year to treatment) across cohorts.

**Why**: Validates the parallel trends assumption by visually assessing whether pre-treatment coefficients hover around zero.

> Baker et al. (2025, p. 9): "Pre-treatment effects should be statistically indistinguishable from zero."

---

# Step 5: Interpret Pre-Treatment Periods

```{markdown}
Review the event study plot:
- Are the estimates for periods prior to treatment flat and centered around zero?
- Are the confidence intervals wide or tight?
- Do any of the pre-treatment estimates appear significantly different from zero?
```

**Why**: Significant pre-trends violate the key identifying assumption of DiD.

---

# Step 6: Run Placebo Tests (Optional but Recommended)

```{r eval=FALSE}
placebo_data <- my_data |>
  filter(year < first_treat_year | is.na(first_treat_year))

placebo_model <- feols(outcome ~ i(relative_time, first_treat_year) + covariates | unit_id + year, 
                       data = placebo_data)
```

**Purpose**: Estimate treatment effects in periods before any treatment occurs.

**Why**: If “effects” show up before treatment, you’ve got either model misspecification or anticipation dynamics. Either way, your core assumptions are shaky.

---

# Step 7: Test Sensitivity to Cohort Definition

```{r eval=FALSE}

# Sensitivity by dropping early adopters or redefining cohorts
att_gt_trimmed <- att_gt(..., gname = first_treat_year, data = my_data |> filter(first_treat_year > 2012))
```

**Purpose**: Confirm your results are not driven by any specific cohort.

**Why**: Robust results should not depend solely on early or late adopters.

---

# Step 8: Check for Spillovers or Anticipation

```{markdown}
- Plot or tabulate trends among properties just outside the treated area
- Include leads in the `att_gt` model to test for anticipatory behavior
```

**Why**: Treatment effect estimates require no interference or preemptive market reactions.

---

# Step 9: Explicitly State Identification Assumptions

```{markdown}
In your write-up, clearly state:
- Parallel trends hold for treated and not-yet-treated units
- Treatment timing is as-good-as-random conditional on covariates and fixed effects
- No spillover effects or contamination
- No anticipatory responses
```

> Baker et al. (2025, p. 10): "Each assumption must be directly defended."