---
title: "Assessing Parallel Trends Under Staggered Treatment"
format:
  html: 
    code-fold: true
execute:
  echo: true
  warning: false
  error: true
#  eval: false
---

# Purpose

This document outlines the correct diagnostics for **parallel trends assumptions in staggered treatment designs** using difference-in-differences (DiD). The presence of staggered timing requires different estimators and more careful assumptions.

> **Source**: Baker et al. (2025), esp. pp. 7–10. Staggered designs require cohort-specific diagnostics and can invalidate conventional DiD methods if assumptions are unchecked.

---

```{r}
library(tidyverse)
library(fixest)

library(didFF)   # for testing if functional form matters for the analysis. Tests if parallel trends assumption is sensitive to functional form (i.e. logged variable vs unlogged variable)

options(scipen = 999)

df_prep <- readRDS("data/processed/targets/sales/df_prep_land_updated_final.rds") |>
  select(-c(clean_name.x, clean_name.y))

table(df_prep$change_type)
table(df_prep$change_type_prelim)

df_prep <- df_prep |> 
  mutate(log_price = log(sale_price))

df_prep <- df_prep |>
  filter(#!is.na(high_ff_score) &
           !is.na(eff_date) &
      #     !is.na(clean_name) &
           !is.na(pre_date)# &
      #     !is.na(Triad)
  )


# are there pins that sell multiple times 
df_prep |> group_by(sale_year, pin) |> mutate(n = n()) |> filter(n > 1)
# yes 
make_sfha_lineplot <- function(
  df,
  y_var = c("sale_price", "log_price"),
  facet_var,                      # e.g. "pre_date", "Triad"
  group_vars = c("prelim_sfha_category"),
  title = "Pre- and Post-Event Slopes by SFHA Status",
  y_label = NULL,
  x_breaks = seq(2010, 2026, 4),
  x_limits = c(2009, 2027)
) {

  y_var <- match.arg(y_var)

  # build grouping vars programmatically
  grp_vars <- c("sale_year", group_vars, facet_var)

  df_summarised <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
    dplyr::summarise(
      avg_value = mean(.data[[y_var]], na.rm = TRUE),
      n = dplyr::n(),
      .groups = "drop"
    )

  if (is.null(y_label)) {
    y_label <- ifelse(
      y_var == "sale_price",
      "Avg. Sale Price",
      "Avg. Logged Sale Price"
    )
  }

  ggplot2::ggplot(
    df_summarised,
    ggplot2::aes(
      x = sale_year,
      y = avg_value,
      color = .data[[group_vars[1]]]
    )
  ) +
    ggplot2::geom_point() +
    ggplot2::geom_line() +
    ggplot2::geom_smooth(method = "lm", se = FALSE) +
    ggplot2::facet_wrap(stats::as.formula(paste("~", facet_var))) +
    ggplot2::labs(
      title = title,
      x = NULL,
      y = y_label,
      caption = ""
    ) +
    ggplot2::scale_x_continuous(
      breaks = x_breaks,
      limits = x_limits
    ) +
    ggplot2::theme_classic() +
    ggplot2::theme(legend.position = "bottom")
}
```



```{r recode-dfpreptest}
table(df_prep$pre_date)

df_prep <- df_prep |>
  
  mutate(
    # so I can subset by FIRM date in later steps
    eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date)) |>
  group_by(pin) |>
  arrange(sale_date) |>
  mutate(

    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(addedto_eff_sfha== TRUE) )
                                 & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removedfrom_eff_sfha== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added or removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(addedto_prelim_sfha == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removedfrom_prelim_sfha== TRUE), year(pre_date), 10000)
    
  ) |>
  ungroup() |>
  mutate(
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
        rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000),
    
    # adjustment for if a sale occurs in the same year that it is treated
    # if sale is before preliminary firm, it is coded as relative year == -1, not yet treated
    rel_year_add_prelim = ifelse(rel_year_add_prelim == 0 & sale_date < pre_date, -1, rel_year_add_prelim),
    rel_year_remove_prelim = ifelse(rel_year_remove_prelim == 0 & sale_date < pre_date, -1, rel_year_remove_prelim),

    rel_year_add_eff = ifelse(rel_year_add_eff == 0 & sale_date < eff_date, -1, rel_year_add_eff),
    rel_year_remove_eff = ifelse(rel_year_remove_eff == 0 & sale_date < eff_date, -1, rel_year_remove_eff)

  ) |>
  mutate(
    qtr  = quarter(sale_date),     # 1 to 4
    year = year(sale_date),            
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # for ALL properties in the updated firms
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    
    # 2005-01-01 2015-02-15 2019-06-28 2021-09-22 

    group_name_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # for ALL properties in the updated firms
      pre_date == "2005-01-01" ~ 0,
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-07-01" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,
      TRUE ~ NA),
      ),
  
    treated_group_eff = factor(case_when(
      # for TREATED propertes in updated FIRMs!
      eff_date == "2008-08-19" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 0,
      eff_date == "2019-11-01" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 2019,
      eff_date == "2021-09-10" & (addedto_eff_sfha|removedfrom_eff_sfha) ~ 2021,
      TRUE ~ NA)),
    
    treated_group_prelim = factor(case_when( 
      # for TREATED propertes in updated FIRMs!
      pre_date == "2005-01-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha|removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ NA)),
        treated_group_prelim_add = factor(case_when( 
      # for TREATED properties in updated FIRMs!
      pre_date == "2005-01-01" & (addedto_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha) ~ 2021,

      TRUE ~ NA)),
        treated_group_prelim_remove = factor(case_when( 
      # for TREATED propertes in updated FIRMs!
      pre_date == "2005-01-01" & (removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ NA))
    )

```

```{r}

df_prep <- df_prep |>
  group_by(pin) |>
  mutate(
    n_sales = n(),
    ever_added_prelim   = any(addedto_prelim_sfha == TRUE),
    ever_removed_prelim = any(removedfrom_prelim_sfha == TRUE),
    ) |>
  mutate(
    prelim_sfha_category = 
      case_when(
        ever_added_prelim & !ever_removed_prelim ~ "Added to prelim SFHA",
        ever_removed_prelim & !ever_added_prelim ~ "Removed from prelim SFHA",
        # ever_added_prelim & ever_removed_prelim  ~ "Multiple prelim transitions",
        change_type_prelim == "Always SFHA" ~ "Always SFHA",
        change_type_prelim == "Never SFHA" ~ "Never SFHA",
        TRUE ~ "CHECK ME"  ) 
  ) |> 
  ungroup()

df_prep <- df_prep |>
  # select(any_of(-c(clean_name.x, clean_name.y)) )|>
  mutate(Triad = case_when(
    clean_name == "Chicago" ~  "City",
    as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
    as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
  ),
    Triad = factor(Triad, levels = c("South", "North", "City") )
  ) 

```



# Parallel Trends

```{r}
df_prep <- df_prep |>filter(!is.na(in_eff_sfha))

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_var = "Triad",
  title     = "Trends by Triad and SFHA Status"
)

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)

make_sfha_lineplot(
  (df_prep |> filter(sale_price < 2000000)),
  y_var     = "sale_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)
```

```{r}
make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Always SFHA", "Removed from prelim SFHA"))),
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Never SFHA", "Added to prelim SFHA"))),
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)

```

## Added 

```{r}

# ---- 1. prep years (run once; safe if they already exist) ----
df_prep <- df_prep |>
  mutate(
    pre_year = if ("pre_year" %in% names(df)) pre_year else as.integer(format(pre_date, "%Y")),
    eff_year = if ("eff_year" %in% names(df)) eff_year else as.integer(format(eff_date, "%Y")),
    event_time = sale_year - pre_year
  )

# ---- 3. bin leads/lags ----
df_prep <- df_prep |>
  mutate(
    event_time_binned = case_when(
      event_time <= -5 ~ -5L,
      event_time >=  5 ~  5L,
      TRUE ~ as.integer(event_time)
    )
  )

# ---- 4. define sample + treatment (example: Added vs Never) ----
df_es <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA")

# ---- 5. event-study regression ----
mod_es <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es
)

# ---- 6. pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ---- 7. joint test of pre-trends ----
wald(mod_es, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(mod_es, xlab = "Years relative to map year", main = "Event Study")

```

## Removed 

```{r}
# ---- 4. define sample + treatment (example: Added vs Never) ----
df_es_removed <- df_prep |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA")

# ---- 5. event-study regression ----
mod_es_removed <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_removed
)

# ---- 6. pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_removed) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ---- 7. joint test of pre-trends ----
wald(mod_es_removed, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(mod_es_removed, xlab = "Years relative to map year", main = "Event Study")

```

## Trends by Geography

To relax the assumption of countywide parallel trends, event-study models are augmented with cohort-specific time trends, implemented as interactions between sale year and assessment triad or preliminary map cohort. This allows price trajectories to vary flexibly across institutional groupings while preserving identification from within-cohort deviations around the map update.

```{r}

# ---- 5. EVENT STUDY WITH FLEXIBLE TRENDS ----
# CHOOSE ONE FE SPECIFICATION BELOW

## (A) Flexible trends by TRIAD
mod_es_triad <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es
)


# ---- 6. pre-trend extraction (example: triad version) ----
pretrends_triad <- broom::tidy(mod_es_triad) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_triad

# ---- 7. joint test of pre-trends ----
wald(mod_es_triad, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(
  mod_es_triad,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends"
)

```

```{r}


## (B) Flexible trends by PRE-MAP COHORT (pre_year)
mod_es_preyear <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^pre_year,
  cluster = ~ pin10,
  data = df_es
)

# ---- 6. pre-trend extraction (example: triad version) ----
pretrends_firm <- broom::tidy(mod_es_preyear) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_firm

# ---- 7. joint test of pre-trends ----
wald(mod_es_preyear, keep = "event_time_binned::-(5|4|3|2)")

# ---- 8. plot ----
iplot(
  mod_es_preyear,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends"
)

```

## simpler version

```{r}
test_parallel_trends_slope <- function(df,
                                      id_var = "pin",
                                      year_var = "sale_year",
                                      y_var = "sale_price",
                                      group_var = "change_type_prelim",
                                      pre_start = 2010,
                                      pre_end = 2014,
                                      cluster_var = "pin") {

  d <- df |>
    filter(.data[[group_var]] %in% c("Always SFHA", "Never SFHA")) |>
    filter(.data[[year_var]] >= pre_start, .data[[year_var]] <= pre_end) |>
    mutate(log_price = log(.data[[y_var]]))

  # Year FE makes it hard to estimate a single slope; instead use year as numeric without year FE,
  # but keep property FE so you’re comparing within-property changes.
  fml <- as.formula(paste0(
    "log_price ~ ", year_var, " * ", group_var, " | ", id_var
  ))

  feols(fml, data = d, cluster = as.formula(paste0("~", cluster_var)))
}

m_slope <- test_parallel_trends_slope(df_prep,
                                      id_var = "pin",
                                      year_var = "sale_year",
                                      y_var = "sale_price",
                                      group_var = "change_type_prelim",
                                      pre_start = 2010,
                                      pre_end = 2015,
                                      cluster_var = "pin10")

summary(m_slope)

m_slope <- test_parallel_trends_slope(df_prep,
                                      id_var = "pin",
                                      year_var = "sale_year",
                                      y_var = "log_price",
                                      group_var = "change_type_prelim",
                                      pre_start = 2010,
                                      pre_end = 2015,
                                      cluster_var = "pin10")

summary(m_slope)

```




> Groups appear to have different pre-trends based on the significant non-zero slope for the interaction variable.

In a pre-period only window (before any relevant map change), assign a fake “event year” and estimate whether the difference between always-in vs never-in changes over event time before the placebo event. If the lead coefficients aren’t flat, you’ve got non-parallel trends.

```{r}
test_parallel_trends_placebo <- function(df,
                                        id_var = "pin",
                                        year_var = "sale_year",
                                        y_var = "sale_price",
                                        group_var = "change_type_prelim",  # 1 = always-in, 0 = never-in
                                        placebo_year = 2012,
                                        pre_start = 2010,
                                        pre_end = 2014,   # should be BEFORE any real prelim/effective year used in this sample
                                        rel_window = c(-5, 5),
                                        cluster_var = "pin10") {

  stopifnot(all(c(id_var, year_var, y_var, group_var) %in% names(df)))

  d <- df |>
    filter(.data[[group_var]] %in% c("Always SFHA", "Never SFHA")) |>
    filter(.data[[year_var]] >= pre_start, .data[[year_var]] <= pre_end) |>
    mutate(
      log_price = log(.data[[y_var]]),
      rel_t = .data[[year_var]] - placebo_year
    ) |>
    filter(rel_t >= rel_window[1], rel_t <= rel_window[2])

  # Event-study style: year FE are included; identification comes from within-id changes and relative-time x group interaction.
  # `i(rel_t, group, ref = -1)` gives coefficients for each event time for group==1 relative to group==0,
  # normalized to rel_t = -1.
  fml <- as.formula(paste0(
    "log_price ~ i(rel_t, ", group_var, ", ref = -1) | ",
    id_var, " + ", year_var
  ))

  m <- feols(
    fml,
    data = d,
    cluster = as.formula(paste0("~", cluster_var))
  )

  # Extract event-time coefficients in a tidy-ish way
  ct <- broom::tidy(m) |>
    filter(grepl("^rel_t::", term)) |>
    mutate(
      rel_t = as.integer(sub("rel_t::", "", term)),
      is_lead = rel_t < 0
    )

  # Simple visual
  p <- ggplot(ct, aes(x = rel_t, y = estimate)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_point() +

    labs(
      x = "Event time (years relative to placebo year)",
      y = "Difference (Always-in minus Never-in), relative to t = -1",
      title = "Placebo event-study pre-trend test"
    ) +
    theme_minimal()

  list(
    data_used = d,
    model = m,
    coef_table = ct,
    plot = p
  )
}

# You need a dataset that contains ONLY always-in and never-in observations for the relevant geography/time,
# and a window that is truly pre-treatment for that geography.
res <- test_parallel_trends_placebo(
  df = df_prep,                       
  id_var = "pin",                    
  year_var = "sale_year",
  y_var = "sale_price",
  group_var = "change_type_prelim",      
  placebo_year = 2012,
  pre_start = 2010,
  pre_end = 2014,                
  rel_window = c(-5, 5),
  cluster_var = "pin10"
)

res$plot
summary(res$model)
res$coef_table

```

Not super significantly different but probably not truly parallel trends during pre-trends?

```{r}
# Test whether ALL lead coefficients are zero
# (Works if the term names match; sometimes you need to inspect names(res$model$coefficients))

lead_terms <- res$coef_table |>
  filter(is_lead) |>
  pull(term)

# Wald test: all leads = 0
fixest::wald(res$model, paste(lead_terms, "= 0", collapse = " ; "))

```

```{r}
# Test whether ALL lead coefficients are zero
# (Works if the term names match; sometimes you need to inspect names(res$model$coefficients))

lead_terms <- res$coef_table |>
  filter(is_lead) |>
  pull(term)

# Wald test: all leads = 0
fixest::wald(res$model, paste(lead_terms, "= 0", collapse = " ; "))

```

```{r remove-multisales-peryear}
df_clean <- df_prep |> 
  mutate(
    sale_quarter = quarter(sale_date),
    pin_num = as.numeric(pin)
  ) |> 
  ungroup() |>
  group_by(pin_num, sale_year, pre_date, eff_date, in_eff_sfha, #addedto_eff_sfha
           ) |> 
  summarize(
    log_price = mean(log_price, na.rm=TRUE), 
    ) |> ungroup()


# are there pins that sell multiple times 
df_clean |> group_by(sale_year, pin_num) |> mutate(n = n()) |> filter(n > 1) 
# not any more
```

> “Indicators for preliminary SFHA additions and removals are defined at the transaction-pair level. Observations with no change between consecutive sales are coded as zero; missing values therefore indicate the absence of a preliminary SFHA transition rather than missing information.”

```{r}
q1_data <- df_prep 

prop_summary_prelim <- q1_data |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    price = mean(sale_price),
    ever_added_prelim   = any(addedto_prelim_sfha == TRUE),
    ever_removed_prelim = any(removedfrom_prelim_sfha == TRUE),
    change_type_prelim = first(change_type_prelim)) |>
  mutate(
    prelim_sfha_category = 
      case_when(
        ever_added_prelim & !ever_removed_prelim ~ "Added to prelim SFHA",
        ever_removed_prelim & !ever_added_prelim ~ "Removed from prelim SFHA",
        # ever_added_prelim & ever_removed_prelim  ~ "Multiple prelim transitions",
        change_type_prelim == "Always SFHA" ~ "Always SFHA",
        change_type_prelim == "Never SFHA" ~ "Never SFHA",
        TRUE ~ "CHECK ME"  ) 
  )

prop_summary_prelim

prelim_sfha_stats <- prop_summary_prelim |>
  group_by(prelim_sfha_category) |>
  mutate(
    avg_sales_per_property = mean(n_sales)) |>
  summarize(
    n_properties = n(),
    n_sales = sum(n_sales),
    mean_price = mean(price),
    median_price = median(price),
    avg_sales_per_property = first(avg_sales_per_property),
    .groups = "drop"
  )

prelim_sfha_stats
```
```{r}
prelim_event_counts <- q1_data |>
  summarize(
    n_sales = n(),
    n_added_events = sum(addedto_prelim_sfha),
    n_removed_events = sum(removedfrom_prelim_sfha),
    pct_sales_with_event = (n_added_events + n_removed_events) / n_sales
  )
prelim_event_counts
```

“Preliminary SFHA reclassifications occur in approximately X% of observed transactions.”


```{r eval = FALSE}

data_dictionary <- df_prep |>
  summarise(across(
    everything(),
    list(
      class  = ~ paste(class(.), collapse = ", "),
      n_na   = ~ sum(is.na(.)),
      n_uniq = ~ n_distinct(.)
    ),
    .names = "{.col}__{.fn}"
  )) |>
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_sep = "__"
  ) |>
  arrange(variable)

write.csv(data_dictionary, "q1_data_dictionary.csv", row.names = FALSE)


skim_summary <- skimr::skim(df_prep)

skim_summary |>
  as.data.frame() |>
  write.csv("q1_skim_summary.csv", row.names = FALSE)


```


# Step 0: Descriptive Stats

```{r}
property_summary <- df_prep |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price),
    # FIRM exposure
    firm_date = first(pre_date),
    ever_firm_update =  ifelse(first(pre_date)=="2005-01-01",FALSE, TRUE),

    # SFHA dynamics
        change_type = first(change_type)
  )
property_summary
```

## A. Properties with no FIRM update vs ever updated

```{r}
firm_update_stats <- property_summary |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales),
    avg_price = mean(mean_price), # avg price of #avg price per property, kinda weird stat
  )

firm_update_stats
```


```{r}
firm_update_stats <- df_prep |>
     mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n_distinct(pin),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )

firm_update_stats
```

## B. Properties by FIRM panel exposure

```{r}
firm_panel_stats <- property_summary |>
  group_by(firm_date) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales)
  ) |>
  arrange(firm_date)

firm_panel_stats
```

## C. SFHA status categories

```{r}
#| layout-ncol: 2


sfha_category_stats <- df_prep |>
  group_by(pin) |> mutate(n_sales = n()) |> ungroup() |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    .groups = "drop"
  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- df_prep |>
    mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    #avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats
```

## D. Cross tab

```{r}
sfha_sales_stats <- df_prep |>
  group_by(change_type_prelim, pre_date) |>
  summarize(
    n_sales = n(),
    n_props = n_distinct(pin),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )
sfha_sales_stats
```

```{r}
price_summary <- df_prep |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    p10 = quantile(sale_price, 0.10, na.rm = TRUE),
    p90 = quantile(sale_price, 0.90, na.rm = TRUE)
  )
price_summary

price_by_sfha <- df_prep |>
  group_by(change_type_prelim) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    .groups = "drop"
  )
price_by_sfha
```

```{r}
geo_summary <- df_prep |>
  distinct(pin, Township, Triad) |>
  summarize(
    n_properties = n(),
    n_townships = n_distinct(Township),
    n_triads = n_distinct(Triad)
  )
geo_summary
```

```{r}
housing_type_summary <- df_prep |>
  distinct(pin, condo, class) |>
  summarize(
    n_properties = n(),
    condo_share = mean(condo == "Condo", na.rm = TRUE),
    n_classes = n_distinct(class)
  )
housing_type_summary
```

# Step 1: Define Treatment Cohorts


**Purpose**: Identify the first year each unit enters treatment. This cohort structure is required to estimate group-time ATT or run cohort-specific checks.

See `treat_group_prelim`


---


# Step 3: Estimate Group-Time ATT with Staggered Design Tools

group: groups based on FIRM panels that were updated at once
treated:


```{r eval=FALSE}
library(did)
att_gt_out <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "treat_group_",
                     xformla = ~in_eff_sfha,

                     data = q3_sales,
                     panel = TRUE,
                     allow_unbalanced_panel = TRUE)
# 
# summary(att_gt_output)
# ggdid(att_gt_output)
#saveRDS(out2, file = "outputs/didQ1_model_output.rds")
#saveRDS(p2, file = "outputs/didQ1_plot_output.rds")


# att_gt_eff_remove <- att_gt(yname = "log_price",
#                      tname = "sale_year",
#                      idname = "pin_num",
#                      gname = "group_name_remove",
#                      data = q3_sales,
#                      panel = TRUE,
#                      allow_unbalanced_panel = TRUE)
# summary(att_gt_eff_remove)
# ggdid(att_gt_eff_remove)

# att_gt_eff_add <- att_gt(yname = "log_price",
#                      tname = "sale_year",
#                      idname = "pin_num",
#                      gname = "group_name_add",
#                      data = q3_sales,
#                      panel = TRUE,
#                      allow_unbalanced_panel = TRUE)
# summary(att_gt_eff_add)
# ggdid(att_gt_eff_add)
```


```{r eval=FALSE}
library(did)

prelim_att_gt_output <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "group_name",
                     data = prelim_q3_sales,
                     panel = TRUE,
                     allow_unbalanced_panel = TRUE)

summary(prelim_att_gt_output)
ggdid(prelim_att_gt_output)
```

**Purpose**: Estimate cohort-specific treatment effects that respect staggered timing using the `did` package.

**Why it matters**: This avoids “forbidden comparisons”—treating already-treated units as controls—and calculates average treatment effects relative to treatment timing, conditional on never-treated or not-yet-treated comparisons.


---

# Step 4: Visualize Event Study

Aggregated effect


```{r}
#| error: true
# aggregate the group-time average treatment effects
agg_output <- aggte(att_gt_out, type = "dynamic")
summary(agg_output)

ggdid(agg_output)

```

**Purpose**: Plot treatment effects by event time (relative year to treatment) across cohorts.

**Why**: Validates the parallel trends assumption by visually assessing whether pre-treatment coefficients hover around zero.

> Baker et al. (2025, p. 9): "Pre-treatment effects should be statistically indistinguishable from zero."

---

# Step 5: Interpret Pre-Treatment Periods

```{markdown}
Review the event study plot:
- Are the estimates for periods prior to treatment flat and centered around zero?
- Are the confidence intervals wide or tight?
- Do any of the pre-treatment estimates appear significantly different from zero?
```

**Why**: Significant pre-trends violate the key identifying assumption of DiD.

---

# Step 6: Run Placebo Tests (Optional but Recommended)

```{r eval=FALSE}
placebo_data <- my_data |>
  filter(year < first_treat_year | is.na(first_treat_year))

placebo_model <- feols(outcome ~ i(relative_time, first_treat_year) + covariates | unit_id + year, 
                       data = placebo_data)
```

**Purpose**: Estimate treatment effects in periods before any treatment occurs.

**Why**: If “effects” show up before treatment, you’ve got either model misspecification or anticipation dynamics. Either way, your core assumptions are shaky.

---

# Step 7: Test Sensitivity to Cohort Definition

```{r eval=FALSE}

# Sensitivity by dropping early adopters or redefining cohorts
att_gt_trimmed <- att_gt(..., gname = first_treat_year, data = my_data |> filter(first_treat_year > 2012))
```

**Purpose**: Confirm your results are not driven by any specific cohort.

**Why**: Robust results should not depend solely on early or late adopters.

---

# Step 8: Check for Spillovers or Anticipation

```{markdown}
- Plot or tabulate trends among properties just outside the treated area
- Include leads in the `att_gt` model to test for anticipatory behavior
```

**Why**: Treatment effect estimates require no interference or preemptive market reactions.

---

# Step 9: Explicitly State Identification Assumptions

```{markdown}
In your write-up, clearly state:
- Parallel trends hold for treated and not-yet-treated units
- Treatment timing is as-good-as-random conditional on covariates and fixed effects
- No spillover effects or contamination
- No anticipatory responses
```

> Baker et al. (2025, p. 10): "Each assumption must be directly defended."