---
title: "Assessing Parallel Trends Under Staggered Treatment"
format:
  html: 
    code-fold: true
    toc: true
    toc-location: left
execute:
  echo: true
  warning: false
  error: true
---

# Purpose

This document outlines the correct diagnostics for **parallel trends assumptions in staggered treatment designs** using difference-in-differences (DiD). The presence of staggered timing requires different estimators and more careful assumptions.

> **Source**: Baker et al. (2025), esp. pp. 7–10. Staggered designs require cohort-specific diagnostics and can invalidate conventional DiD methods if assumptions are unchecked.

---

```{r setup}
library(tidyverse)
library(fixest)

library(didFF)   # for testing if functional form matters for the analysis. Tests if parallel trends assumption is sensitive to functional form (i.e. logged variable vs unlogged variable)
library(did)  # for step 3 and 4
options(scipen = 999)

# make_sfha_lineplot <- function(
#   df,
#   y_var = c("sale_price", "log_price"),
#   facet_var = c("pre_date"),                      # e.g. "pre_date", "Triad"
#   group_vars = c("event_remapped","prelim_sfha_category", "Triad", "pre_date_chr", "pre_date"),
#   title = "Pre- and Post-Event Slopes by SFHA Status",
#   linetype = c("event_remapped"),
#   color = c("prelim_sfha_category"),
#   y_label = NULL,
#   x_breaks = seq(2010, 2026, 4),
#   x_limits = c(2009, 2027)
# ) {
# 
#   y_var <- match.arg(y_var)
# 
#   # build grouping vars programmatically
#   grp_vars <- c("sale_year", group_vars, facet_var)
# 
#   df_summarised <- df |>
#     dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
#     dplyr::summarise(
#       avg_value = mean(.data[[y_var]], na.rm = TRUE),
#       median_value = median(.data[[y_var]], na.rm=TRUE),
#       n = dplyr::n(),
#       .groups = "drop"
#     )
# 
#   if (is.null(y_label)) {
#     y_label <- ifelse(
#       y_var == "sale_price",
#       "Avg. Sale Price",
#       "Avg. Logged Sale Price"
#     )
#   }
# 
#   ggplot2::ggplot(
#     df_summarised,
#     ggplot2::aes(
#       x = sale_year,
#       y = avg_value,
#       color = .data[[group_vars[1]]]
#     )
#   ) +
#     ggplot2::geom_point() +
#     ggplot2::geom_line() +
#     ggplot2::geom_smooth(aes(lty = event_remapped),method = "lm", se = FALSE) +
#     ggplot2::facet_wrap(stats::as.formula(paste("~", facet_var))) +
#     ggplot2::labs(
#       title = title,
#       x = NULL,
#       y = y_label,
#       caption = ""
#     ) +
#     ggplot2::scale_x_continuous(
#       breaks = x_breaks,
#       limits = x_limits
#     ) +
#     ggplot2::theme_classic() +
#     ggplot2::theme(legend.position = "bottom")
# }
# 


make_sfha_lineplot <- function(
  df,
  y_var = c("sale_price", "log_price"),
  group_vars = c("event_remapped", "prelim_sfha_category"),
  facet_vars = c("pre_date_chr"),     # can be length 0, 1, or more
  color_var = "prelim_sfha_category", # set NULL for no color mapping
  linetype_var = "event_remapped",    # set NULL for no linetype mapping
  title = "Pre- and Post-Event Slopes by SFHA Status",
  y_label = NULL,
  x_breaks = seq(2010, 2026, 4),
  x_limits = c(2009, 2027),
  show_smooth = TRUE
) {
  y_var <- match.arg(y_var)

  # --- sanity checks (prevents silent nonsense) ---
  needed <- unique(c("sale_year", y_var, group_vars, facet_vars, color_var, linetype_var))
  needed <- needed[!is.null(needed) & needed != ""]
  missing <- setdiff(needed, names(df))
  if (length(missing) > 0) {
    stop("Missing columns in df: ", paste(missing, collapse = ", "))
  }

  # --- summarise ---
  grp_vars <- unique(c("sale_year", group_vars, facet_vars))

  df_sum <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
    dplyr::summarise(
      avg_value = mean(.data[[y_var]], na.rm = TRUE),
      median_value = median(.data[[y_var]], na.rm = TRUE),
      n = dplyr::n(),
      .groups = "drop"
    ) |>
    # create a stable "series id" so lines/smooths don't cross-wire
    dplyr::mutate(.series = interaction(dplyr::across(dplyr::all_of(group_vars)), drop = TRUE))

  if (is.null(y_label)) {
    y_label <- if (y_var == "sale_price") "Avg. Sale Price" else "Avg. Logged Sale Price"
  }

  # --- base aesthetics ---
  aes_base <- ggplot2::aes(
    x = sale_year,
    y = avg_value,
    group = .series
  )

  if (!is.null(color_var))    aes_base$colour   <- rlang::sym(color_var)
  if (!is.null(linetype_var)) aes_base$linetype <- rlang::sym(linetype_var)

  p <- ggplot2::ggplot(df_sum, aes_base) +
    ggplot2::geom_point() +
    ggplot2::geom_line()

  if (isTRUE(show_smooth)) {
    p <- p + ggplot2::geom_smooth(method = "lm", se = FALSE)
  }

  # --- faceting (supports 0, 1, or many) ---
  if (length(facet_vars) == 0) {
    # no facets
  } else if (length(facet_vars) == 1) {
    p <- p + ggplot2::facet_wrap(stats::as.formula(paste0("~", facet_vars)))
  } else {
    # multiple facet variables -> facet_grid
    # e.g. facet_vars = c("triad", "pre_date_chr") => rows = triad, cols = pre_date_chr
    p <- p + ggplot2::facet_grid(stats::as.formula(paste(facet_vars[1], "~", facet_vars[2])))
  }

  p +
    ggplot2::labs(
      title = title,
      x = NULL,
      y = y_label
    ) +
    ggplot2::scale_x_continuous(breaks = x_breaks, limits = x_limits) +
    ggplot2::theme_classic() +
    ggplot2::theme(legend.position = "bottom")
}

```


# Step 1: Define Treatment Cohorts


**Purpose**: Identify the first year each unit enters treatment. This cohort structure is required to estimate group-time ATT or run cohort-specific checks.

See `treat_group_prelim`


---


```{r}
# created in Q1_final_variables.R script
# df_prep <- readRDS("data/processed/df_prep_forQ1_assumptiontests.RDS")

# created in sfha_indicator_processing.R that uses arcgis and 2025 parcels 
df_prep <- readRDS("data/processed/df_prep_bldg_sfha_updated_arcgis_forQ1_assumptiontests.RDS")

source("R/helper_pins_to_drop.R")

df_prep <- df_prep |> filter(!pin10 %in% drop_parcels  |          
               (pin10 == "0113301013" & sale_year > 2014)
             )


table(df_prep$change_type)
table(df_prep$change_type_prelim)

table(df_prep$pre_date)
table(df_prep$prelim_sfha_category)
```


```{r}
#| layout-ncol: 2

#df_prep |> filter(removedfrom_prelim_sfha == TRUE & times_sold >2) |> arrange(pin)
#df_prep |> filter(addedto_prelim_sfha == TRUE & times_sold >2) |> arrange(pin)

table(df_prep$sale_year, df_prep$addedto_prelim_sfha)
table(df_prep$sale_year, df_prep$removedfrom_prelim_sfha)


```

```{r}
#| include: false
table(df_prep$sale_year, df_prep$pre_date, df_prep$addedto_prelim_sfha)
table(df_prep$sale_year, df_prep$pre_date, df_prep$removedfrom_prelim_sfha)

```

## Step 2: Is TWFE messed up?

Goodman-Bacon decomposition

If your subset models are:

full sample

cohort 2015

cohort 2019

cohort 2021

Those separate regressions are not what TWFE is averaging in a clean way. TWFE is mixing:

2015 vs never

2019 vs never

2021 vs never

2015 vs 2019

2015 vs 2021

2019 vs 2021


```{r}
#| eval: false
library(bacondecomp)   # bacon-decomp doesn't work with unbalanced panels!
# bd <- bacon(
#   log_price ~ removedfrom_prelim_sfha,
#   data = df_prep,
#   id_var = "pin",
#   time_var = "sale_year"
# )
# 
# bd |> 
#   dplyr::group_by(type) |> 
#   dplyr::summarise(
#     total_weight = sum(weight),
#     avg_estimate = weighted.mean(estimate, weight)
#   )
```

```{r}
library(etwfe)


mod1 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = Triad, 
  cgroup = "never",
  gvar = treat_year_add_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            filter(treat_year_remove_prelim==10000
                   
                   & change_type_prelim != "Always SFHA")
          )
  
  )
mod1


emfx(mod1)


emfx(mod1, type = "group")
emfx(mod1, type = "event")
plot(emfx(mod1))
plot(emfx(mod1, type = "event"))

```

if not treated, then treat_year_remove_prelim == 0

```{r}
mod2 = etwfe(
  fml = log_price ~ 1, 
  tvar = sale_year, 
  ivar = pin, 
  xvar = Triad, 
    cgroup = "never",

  gvar = treat_year_remove_prelim, 
  vcov = ~pin10, 
  data = (df_prep|> 
            # do not want treated properties that move in opposite direction. 
            filter(treat_year_add_prelim==10000 |
                     # and only want to compare to properties that were Always in the SFHA (also keeps properties that changed SFHA status), 
                     change_type_prelim != "Never SFHA") 
          )
  )
mod2
emfx(mod2)
emfx(mod2, type = "group")
emfx(mod2, type = "event")
plot(emfx(mod2))
plot(emfx(mod2, type = "event"))


```

# Step 3: Estimate Group-Time ATT with Staggered Design Tools



**Purpose**: Estimate cohort-specific treatment effects that respect staggered timing using the `did` package.

**Why it matters**: This avoids “forbidden comparisons”—treating already-treated units as controls—and calculates average treatment effects relative to treatment timing, conditional on never-treated or not-yet-treated comparisons.


## Removed PINs

“What happens to prices after buyers can observe that a parcel is removed, conditional on when that information first enters the market?”

**Treated:** Group indicator for PINs that were ever removed from the SFHA due to a preliminary map release. 

**g_remove** first sale after the treated group has been treated (first sale_year when treated). Cohorts of properties were treated only in 2015, 2019, and 2021, but the first treated sale can happen much later. 

```{r}
df_es_removed <- df_prep |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(pin_num = as.numeric(pin)) |>
  dplyr::arrange(pin_num, sale_year, sale_date) |>
  dplyr::group_by(pin_num, sale_year, pre_date_chr) |>
  dplyr::slice_tail(n = 1) |>
  dplyr::ungroup() |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA") |> 
  
   group_by(pin_num) |>
  mutate(
    g_remove = if (any(removedfrom_prelim_sfha == TRUE, na.rm = TRUE)) {
      min(sale_year[removedfrom_prelim_sfha == TRUE], na.rm = TRUE)
    } else {
      0L
    }
  ) |>
  ungroup()


table(df_es_removed$g_remove, df_es_removed$pre_date)
```

With g_remove:

_base_period == "universal" uses "long-differences" for pre-treatment coefficients as well as post-treatment coefficients._

```{r message=FALSE}
prelim_remove_att_gt_out <- att_gt(yname = "log_price",
                                 #  xformla = ~"pre_date_chr",
                     tname = "sale_year",
                     idname = "pin_num",
                     #gname = "treated_group_prelim_remove",
                     gname = "g_remove",
                     clustervars = "pin10",
                     base_period = "universal",
                     data = df_es_removed,
                     allow_unbalanced_panel = TRUE#,
                   # print_details = TRUE
                    )

summary(prelim_remove_att_gt_out)

# looks like nothing, too bunched together, doesn't show cohorts.
# ggdid(prelim_remove_att_gt_out)


agg_group <- aggte(prelim_remove_att_gt_out, type = "group", na.rm = TRUE)
summary(agg_group)  
ggdid(agg_group)


```


2015 removals massively outperform always-SFHA parcels

2021 removals massively underperform always-SFHA parcels. Much smaller sample size


```{r}
#| label: tbl-treatedpins-removed
#| tbl-cap: "Number of treated PINs per cohort"

df_es_removed |>
  filter(g_remove %in% c(2015, 2021)) |>
  group_by(g_remove) |>
  summarise(
    n_pins = n_distinct(pin_num),
    n_obs  = n()
  )

```

These estimates compare parcels removed from the preliminary SFHA to parcels that remain continuously within the SFHA, isolating the effect of removal relative to persistently high-risk properties rather than floodplain-free controls.



## Added 

```{r }
#| label: create-added-rds-output


df_es_added <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(pin_num = as.numeric(pin)) |>
  dplyr::arrange(pin_num, sale_year, sale_date) |>
  dplyr::group_by(pin_num, sale_year, pre_date_chr) |>
  dplyr::slice_tail(n = 1) |>
  dplyr::ungroup() |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA") |> 
  
   group_by(pin_num) |>
  mutate(
    g_add = if (any(addedto_prelim_sfha == 1, na.rm = TRUE)) {
      min(sale_year[addedto_prelim_sfha == 1], na.rm = TRUE)
    } else {
      0L
    }
  ) |>
  ungroup()


table(df_es_added$g_add)
```


```{r }
#| eval: false
#| include: false

#takes a lot longer than the removed & always in SFHA model above. 
prelim_add_att_gt_out <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "g_add",
                     clustervars = "pin10",
                     data = df_es_added,
                     allow_unbalanced_panel = TRUE,
                    print_details = TRUE)

#save output and read it in in next chunk to deal with rendering time.
saveRDS(prelim_add_att_gt_out, file = "outputs/Q1_prelim_add_gt_out.rds")
```

**skipping ggdid versions of event studies. Go to next section instead.**

```{r}
#| eval: false
#| include: false
#| 
prelim_add_att_gt_out <- read_rds("outputs/Q1_prelim_add_gt_out.rds")
summary(prelim_add_att_gt_out)
ggdid(prelim_add_att_gt_out)

agg_group <- aggte(prelim_add_att_gt_out, type = "group", na.rm = TRUE)
summary(agg_group)  
ggdid(agg_group)


```


# Step 4: Visualize Event Study

**Purpose:** Plot treatment effects by event time (relative year to treatment) across cohorts.

**Why:** Validates the parallel trends assumption by visually assessing whether pre-treatment coefficients hover around zero.

## Using Callaway & Santana did package

Added to Preliminary SFHA graph is wrong though. It is grabbing 2022 as a treatment year even though that is false. 

```{r}
#| label: fig-eventstudy-graphs-using-aggtedynamic
#| fig-cap: "Event study version of cohort effects. Uses releative time to treatment."
#| eval: false
#| include: false

prelim_add_att_gt_out <- read_rds("outputs/Q1_prelim_add_gt_out.rds")

agg_es <- aggte(prelim_remove_att_gt_out, type = "dynamic", na.rm=TRUE)
summary(agg_es)
ggdid(agg_es)

agg_es <- aggte(prelim_add_att_gt_out, type = "dynamic", na.rm=TRUE)
summary(agg_es)
ggdid(agg_es)
```


## Added to SFHA -  Event Study

**Added to SFHA properties compared to Never in SFHA properties**

addedto_prelim_sfha=1(treated group)×1(post)

```{r}
#| label: appendix-added-es-jointtest

df_prep <- df_prep |>
  mutate(
    pre_year = if ("pre_year" %in% names(df)) pre_year else as.integer(format(pre_date, "%Y")),
    eff_year = if ("eff_year" %in% names(df)) eff_year else as.integer(format(eff_date, "%Y")),
    event_time = sale_year - pre_year,
    event_time = ifelse(event_time == 0 & sale_date < pre_date, -1, event_time)
  )

# ----  bin leads/lags ----
df_prep <- df_prep |>
  mutate(
    event_time_binned = case_when(
      event_time <= -5 ~ -5L,
      event_time >=  5 ~  5L,
      TRUE ~ as.integer(event_time)
    )
  )

# ---- define sample + treatment (Added vs Never) ----
# Added to SFHA comparison!
df_es_add <- df_prep |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(treated = prelim_sfha_category == "Added to prelim SFHA")

# ---- (A) event-study regression ----
# base model, no flexible fixed effects
mod_es_add_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_add
)


# ----  plot ----
iplot(mod_es_add_none, xlab = "Years relative to map year", main = "Event Study: Added")

```


```{r}
# ---- pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_add_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ----  joint test of pre-trends ----
wald(mod_es_add_none, keep = "event_time_binned::-(5|4|3|2)")
```

There is no evidence of differential pre-trends between treated and control units in the periods before treatment.


This gets better when Triad fixed effects are added below!



### Geographic Heterogeneity: Added to SFHA ES by Triad 

To relax the assumption of countywide parallel trends, event-study models are augmented with cohort-specific time trends, implemented as interactions between sale year and assessment triad or preliminary map cohort. This allows price trajectories to vary flexibly across institutional groupings while preserving identification from within-cohort deviations around the map update.


```{r}

# ----  EVENT STUDY WITH FLEXIBLE TRENDS ----

## (B) Flexible trends by TRIAD
mod_es_add_triad <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es_add
)


# (C) Pre-year cohort trends
mod_es_add_preyear <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^pre_year,
  cluster = ~ pin10,
  data = df_es_add
)

# ----  pre-trend extraction (triad version) ----
pretrends_triad <- broom::tidy(mod_es_add_triad) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_triad

# ---- joint test of pre-trendsfor year-triad flexible fixed effects ----
wald(mod_es_add_triad, keep = "event_time_binned::-(5|4|3|2)")

# ----  plot ----
iplot(
  mod_es_add_triad,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends: Added"
)

```

Still passes pre-trend test!


```{r}
#| label: tbl-added-comparisonofFE
#| tbl-cap: "Table compares event-study estimates under alternative assumptions about price trends. Allowing for assessment-triad-specific trends modestly attenuates estimated effects while preserving the overall dynamic pattern. More aggressive cohort-specific trends based on preliminary map year further reduce precision, reflecting limited identifying variation once highly flexible trends are imposed."

# ---- collect and label models ----
mods <- list(
  "No flexible trends"     = mod_es_add_none,
  "Triad-specific trends" = mod_es_add_triad,
  "Pre-year cohort trends"= mod_es_add_preyear
)

coef_map <- broom::tidy(mod_es_add_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(
    rel_time = as.integer(str_extract(term, "-?\\d+")),
    clean = paste0("t = ", rel_time)
  ) |>
  arrange(rel_time) |>
  pull(clean, term)

# ---- 5. comparison table ----
modelsummary::modelsummary(
  mods,
  coef_map = coef_map,
  estimate  = "{estimate}{stars}",
  statistic = "({std.error})",
  stars = c("*" = .10, "**" = .05, "***" = .01),
  gof_omit = "Adj|Pseudo|Within|RMSE|AIC|BIC"
)
```


#### Graphed Coefficients  - Added to SFHA
 
```{r}
# Pick shapes that are visually distinct and legible
shape_vals <- c(
  "No trends"        = 16, # filled circle
  "Triad trends"     = 17, # filled triangle
  "Pre-year trends"  = 15  # filled square
)

linetype_vals <- c(
  "No trends"        = "solid",
  "Triad trends"     = "dashed",
  "Pre-year trends"  = "dotted"
)


extract_es <- function(mod, label) {
  broom::tidy(mod) |>
    filter(str_detect(term, "^event_time_binned::")) |>
    mutate(
      rel_time = as.integer(str_extract(term, "-?\\d+")),
      spec = label
    )
}

es_df <- bind_rows(
  extract_es(mod_es_add_none,    "No trends"),
  extract_es(mod_es_add_triad,   "Triad trends"),
  extract_es(mod_es_add_preyear, "Pre-year trends")
)

ref_row <- es_df |>
  distinct(spec) |>
  mutate(
    rel_time  = -1,
    estimate  = 0,
    std.error = 0,
    ref = TRUE
  )

es_df_plot <- bind_rows(
  es_df |> mutate(ref = FALSE),
  ref_row
)

ggplot(es_df_plot, aes(x = rel_time, y = estimate, group = spec)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  geom_vline(xintercept = -1, linetype = "dotted") +

  # confidence intervals (skip ref period automatically since se = 0)
  geom_errorbar(
    aes(
      ymin = estimate - 1.96 * std.error,
      ymax = estimate + 1.96 * std.error,
      linetype = spec
    ),
    width = 0.15
  ) +

  geom_line(aes(linetype = spec), linewidth = 0.6) +

  geom_point(
    aes(shape = spec),
    size = 2.3,
    stroke = 0.6
  ) +

  # OPTIONAL: emphasize reference period
  geom_point(
    data = subset(es_df_plot, ref),
    shape = 21,       # hollow circle
    size = 3,
    stroke = 0.9
  ) +

  scale_shape_manual(values = c(
    "No trends"       = 16,
    "Triad trends"    = 17,
    "Pre-year trends" = 15
  )) +
  scale_linetype_manual(values = c(
    "No trends"       = "solid",
    "Triad trends"    = "dashed",
    "Pre-year trends" = "dotted"
  )) +

  labs(
    x = "Years relative to map year",
    y = "Estimated effect on log(price)",
    shape = "Specification",
    linetype = "Specification",
    title = "Event-study estimates under alternative trend assumptions",
    subtitle = "Year −1 is the omitted reference period (normalized to zero)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")


```



## Removed from SFHA - Event Study

```{r}
# --- define sample + treatment (Removed vs Always) ----
df_es_removed <- df_prep |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(treated = prelim_sfha_category == "Removed from prelim SFHA")

range(df_es_removed$sale_year, na.rm = TRUE)

# ---- event-study regression ----
mod_es_removed_none <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year,
  cluster = ~ pin10,
  data = df_es_removed
)

mod_es_removed_preyear <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) | pin + sale_year^pre_year,
  cluster = ~ pin10,
  data = df_es_removed
)


# ----  plot ----
iplot(mod_es_removed_none, xlab = "Years relative to map year", main = "Event Study: Removed")

```

This spec is implicitly assuming North Cook, South Cook, and Chicago share a single price trend. That assumption is false. Regional growth differences get misattributed to the flood-risk information shock.

```{r}
# ---- pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_removed_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends

# ----  joint test of pre-trends ----
wald(mod_es_removed_none, keep = "event_time_binned::-(5|4|3|2)")

```

> Failed pre-trend test: Coefficients were statistically significant from each other.  Gets better when using Triads below!

### Geographic Heterogeneity - Removed from SFHA ES by Triad 

Do properties follow the same trend within institutional cohorts (assessment Triads or map-update cohorts)


```{r}
##  Flexible trends by Triad
mod_es_removed_triad <- feols(
  log(sale_price) ~ i(event_time_binned, treated, ref = -1) |
    pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es_removed
)

# ----  plot ----
iplot(
  mod_es_removed_triad,
  xlab = "Years relative to map year",
  main = "Event Study with Triad-Specific Trends: Removed"
)
```


```{r}
# ----  pre-trend extraction (example: triad version) ----
pretrends_firm <- broom::tidy(mod_es_removed_triad) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_firm

# ----  joint test of pre-trends ----
wald(mod_es_removed_triad, keep = "event_time_binned::-(5|4|3|2)")



pretrends_firm <- broom::tidy(mod_es_removed_preyear) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 0) |>
  arrange(rel_time)

pretrends_firm

# ----  joint test of pre-trends ----
wald(mod_es_removed_preyear, keep = "event_time_binned::-(5|4|3|2)")

```

These pre-period coefficients are not jointly zero.

- Smaller Sample size


```{r}
# ---- collect and label models ----
mods <- list(
  "No flexible trends"     = mod_es_removed_none,
  "Triad-specific trends" = mod_es_removed_triad,
  "Pre-year cohort trends"= mod_es_removed_preyear
)

coef_map <- broom::tidy(mod_es_removed_none) |>
  filter(str_detect(term, "^event_time_binned::")) |>
  mutate(
    rel_time = as.integer(str_extract(term, "-?\\d+")),
    clean = paste0("t = ", rel_time)
  ) |>
  arrange(rel_time) |>
  pull(clean, term)

# ----  comparison table ----
modelsummary::modelsummary(
  mods,
  coef_map = coef_map,
  estimate  = "{estimate}{stars}",
  statistic = "({std.error})",
  stars = c("*" = .10, "**" = .05, "***" = .01),
  gof_omit = "Adj|Pseudo|Within|RMSE"
)
```


#### Graphed coefficients: Removed from SFHA ES

```{r}
extract_es <- function(mod, label) {
  broom::tidy(mod) |>
    filter(str_detect(term, "^event_time_binned::")) |>
    mutate(
      rel_time = as.integer(str_extract(term, "-?\\d+")),
      spec = label
    )
}

es_df <- bind_rows(
  extract_es(mod_es_removed_none,    "No trends"),
  extract_es(mod_es_removed_triad,   "Triad trends"),
  extract_es(mod_es_removed_preyear, "Pre-year trends")
)

ref_row <- es_df |>
  distinct(spec) |>
  mutate(
    rel_time  = -1,
    estimate  = 0,
    std.error = 0,
    ref = TRUE
  )

es_df_plot <- bind_rows(
  es_df |> mutate(ref = FALSE),
  ref_row
)

ggplot(es_df_plot, aes(x = rel_time, y = estimate, group = spec)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  geom_vline(xintercept = -1, linetype = "dotted") +

  # confidence intervals (skip ref period automatically since se = 0)
  geom_errorbar(
    aes(
      ymin = estimate - 1.96 * std.error,
      ymax = estimate + 1.96 * std.error,
      linetype = spec
    ),
    width = 0.15
  ) +

  geom_line(aes(linetype = spec), linewidth = 0.6) +

  geom_point(
    aes(shape = spec),
    size = 2.3,
    stroke = 0.6
  ) +

  #  emphasize reference period
  geom_point(
    data = subset(es_df_plot, ref),
    shape = 21,       # hollow circle
    size = 3,
    stroke = 0.9
  ) +

  scale_shape_manual(values = c(
    "No trends"       = 16,
    "Triad trends"    = 17,
    "Pre-year trends" = 15
  )) +
  scale_linetype_manual(values = c(
    "No trends"       = "solid",
    "Triad trends"    = "dashed",
    "Pre-year trends" = "dotted"
  )) +

  labs(
    x = "Years relative to map year",
    y = "Estimated effect on log(price)",
    shape = "Specification",
    linetype = "Specification",
    title = "Event-study estimates under alternative trend assumptions",
    subtitle = "Year −1 is the omitted reference period (normalized to zero)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

```

The No trends line is a raw TWFE Event study. The other two lines allow for differential trends across geographic regions.

- Pre-period coefficients drifting in one direction

- Post-event coefficients moving in the opposite direction

- The magnitude and shape of both change depending on which trend structure you allow


Some of the apparent pre-trend was actually driven by geographic-dynamics, not flood-risk information.

Differences in timing of preliminary map releases generate cohort-specific price dynamics that, if not controlled for, contaminate both pre- and post-period estimates.

> Figure X compares event-study estimates under alternative assumptions about underlying price trends. In the baseline specification with PIN and year fixed effects, pre-treatment coefficients exhibit a trend in the opposite direction of the post-treatment response, raising concern that differential trends may be confounded with the estimated treatment effect. When year-by-Triad fixed effects are included, allowing housing prices to evolve differently in North Cook, South Cook, and the City of Chicago, pre-period divergence is substantially reduced and post-event estimates attenuate.

> When cohort-specific trends based on the timing of preliminary map releases are included, pre-period coefficients are largely flattened, while a positive post-event response remains. This pattern suggests that simpler specifications partially conflate underlying cohort-specific price dynamics with the effect of flood-risk information, and that models allowing for richer trend heterogeneity provide more credible estimates of the treatment effect. 

## Always and Never Treated

**not sure if this one matters**

```{r}
# ---- define sample + treatment (Added vs Never) ----
df_es_neither <- df_prep |>
  filter(prelim_sfha_category %in% c("Never SFHA", "Always SFHA")) |>
 mutate(treated = prelim_sfha_category == "Always SFHA",
        sale_year_factor = factor(sale_year),
        post = sale_date > as.Date("2020-04-20"))

# ---- event-study regression ----
mod_es_neither_none <- feols(
  log(sale_price) ~ i(sale_year_factor, treated, ref = 2019) | pin + sale_year^Triad,
  cluster = ~ pin10,
  data = df_es_neither
)
# ----  plot ----
iplot(mod_es_neither_none, xlab = "Years relative to map year", main = "Event Study: Never Treated and Always Treated")
```


```{r}
# ---- pre-trend check (leads only) ----
pretrends <- broom::tidy(mod_es_neither_none) |>
  filter(str_detect(term, "^sale_year_factor::")) |>
  mutate(rel_time = as.integer(str_extract(term, "-?\\d+"))) |>
  filter(rel_time < 2019) |>
  arrange(rel_time)

pretrends

# ---- joint test of pre-trends ----
wald(mod_es_neither_none, keep = "sale_year_factor::(2014|2015|2016|2017|2018)")


```

Always treated and never treated do not have significantly different pre trends. 

# Aggregated effect


```{r}
#| error: true
#| eval: false


library(did)

att_gt_out <- att_gt(yname = "log_price",
                     tname = "sale_year",
                     idname = "pin_num",
                     gname = "first_treat_year",
                     xformla = ~ covariates,
                     data = my_data)


# aggregate the group-time average treatment effects
agg_output <- aggte(prelim_add_att_gt_out, type = "dynamic")
summary(agg_output)

ggdid(agg_output)

```

**Purpose**: Plot treatment effects by event time (relative year to treatment) across cohorts.

**Why**: Validates the parallel trends assumption by visually assessing whether pre-treatment coefficients hover around zero.

> Baker et al. (2025, p. 9): "Pre-treatment effects should be statistically indistinguishable from zero."

---


# Step 5:  Run Placebo Tests 

**Purpose**: Estimate treatment effects in periods before any treatment occurs.

**Why**: If “effects” show up before treatment, you’ve got either model misspecification or anticipation dynamics. Either way, your core assumptions are shaky.


```{r}
#| label: tbl-appendixA-placebotest
#| 

library(dplyr)
library(lubridate)
library(fixest)

# df_prep must have: pin, pin10, sale_date, sale_year, pre_date, prelim_sfha_category, log_price

run_placebo_did <- function(df,
                            fake_shift_years = 2,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }
  df_placebo <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label,
      placebo_date = pre_date %m-% years(fake_shift_years),
      placebo_post = sale_date >= placebo_date
    ) |>
    # keep only observations strictly before the *real* event (so placebo is truly placebo)
    filter(sale_date < pre_date) |>
    # optional: keep only observations with a defined placebo_date
    filter(!is.na(placebo_date))

  fml <- as.formula(paste0(
    "log_price ~ treated * placebo_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_placebo
  )
}


m_placebo <- run_placebo_did(df_prep, treated_label = "Removed from prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)

m_placebo <- run_placebo_did(df_prep, treated_label = "Added to prelim SFHA",
                             fake_shift_years = 2)
etable(m_placebo)
```

```{r}
#| label: tbl-did_test_normal
#| tbl-cap: "Same set up as placebo test, but without the placebo. Includes all years of data."


run_normal_did <- function(df,
                            treated_label = "Added to prelim SFHA",
                            unit_fe = "pin",
                            time_fe = "sale_year",
                            cluster_var = "pin10") {
  if(treated_label == "Added to prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA"))
  }
  if(treated_label == "Removed from prelim SFHA"){
    df <- df |> filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA"))
  }

  df_did <- df |>
    mutate(
      treated = prelim_sfha_category == treated_label, #== treated_label,
      treated_date = pre_date,
      event_post = (sale_date >= treated_date  & pre_date_chr != "2005-01-01")
    ) 

  fml <- as.formula(paste0(
    "log_price ~ treated * event_post | ",
    unit_fe, " + ", time_fe
  ))

  feols(
    fml,
    cluster = as.formula(paste0("~", cluster_var)),
    data = df_did
  )
}

df_prep |> filter(treated== TRUE)

m_did_add <- run_normal_did(df_prep, treated_label = "Added to prelim SFHA")
etable(m_did_add)

m_did_remove <- run_normal_did(df_prep, treated_label = "Removed from prelim SFHA")
etable(m_did_remove)
```

Using addedto_prelim_sfha estimates the correct DiD treatment effect because the variable equals the interaction between treated group membership and the post-treatment period. However, this formulation obscures the underlying DiD structure and complicates assumption checks and interpretation.

```{r}
#| label: tbl-two-method-styles-comparison-added
#| tbl-cap: "Two ways to set up the equation that should estimate the same effect."
#| warning: true
#| message: true
#| eval: false
#| include: false

# df_prep |> filter(prelim_sfha_category ==  "Added to prelim SFHA") |> group_by(pin) |> mutate(n = n())  |> filter( n < 2)

# table(df_prep$change_type_prelim)
# df_prep |> filter(pin %in% singletons$pin) |> View()

df_same <- df_es_add |>
  filter(prelim_sfha_category %in% c("Added to prelim SFHA", "Never SFHA")) |>
  mutate(
    treated = ifelse(prelim_sfha_category == "Added to prelim SFHA", TRUE, FALSE),
    event_post = ifelse(sale_date >= pre_date & pre_date!= as.Date("2005-01-01"), TRUE, FALSE
  )
  )


# df_same |>
#   group_by(pin) |>
#   summarise(n_vals = n_distinct(treated), .groups = "drop") |>
#   count(n_vals)



m1 <- feols(
  log_price ~ addedto_prelim_sfha | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)



m2 <- feols(
  log_price ~ i(treated * event_post) | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)

m3 <- feols(
      log_price ~ treated*event_post  | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)
m4 <- feols(
  log_price ~ event_post + treated:event_post | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)
# summary(m3)
# etable(m1, m2, m3)
# summary(m3, collinearity = TRUE)

modelsummary::modelsummary(list(m1, m2, m3, m4), stars = TRUE)


```

prelim_sfha_category is for group membership (treated vs control group definition).

addedto_prelim_sfha is (probably) a post-treated status indicator (treated group switches on after its pre_date, controls never switch on).

```{r}
run_normal_did_fixed <- function(df,
                                 treated_label = "Added to prelim SFHA",
                                 control_label = "Never SFHA",
                                 unit_fe = "pin",
                                 time_fe = "sale_year",
                                 cluster_var = "pin10") {

  df2 <- df |>
    filter(prelim_sfha_category %in% c(treated_label, control_label)) |>
    mutate(
      treated_group = prelim_sfha_category == treated_label, # time-invariant
      post = sale_date >= pre_date,                          # time-varying
      did = treated_group * post
    )

  # canonical DiD (will match the did-only version)
  m_did <- feols(
    as.formula(paste0("log_price ~ treated_group * post | ", unit_fe, " + ", time_fe)),
    cluster = as.formula(paste0("~", cluster_var)),
    data = df2
  )

  # did-only version (should match on the treatment effect)
  m_did_only <- feols(
    as.formula(paste0("log_price ~ did | ", unit_fe, " + ", time_fe)),
    cluster = as.formula(paste0("~", cluster_var)),
    data = df2
  )

  list(m_did = m_did, m_did_only = m_did_only, data = df2)
}

out <- run_normal_did_fixed(df_prep)
etable(out$m_did, out$m_did_only)

```

**Interpretation: adding post changes what variation is attributed to “general post-period shifts among the sample” vs “differential post shift for treated relative to control.” That can easily shrink the interaction from -0.20 to -0.14.**

treated * post ≠ I(treated * post)

With staggered timing, post is not absorbed by year FE, so including it changes the regression and the interaction coefficient.

```{r}
#| label: tbl-two-method-styles-comparison-removed
#| tbl-cap: "Two ways to set up the equation that should estimate the same effect."
#| eval: false
#| include: false

df_same <- df_es_removed |>
  filter(prelim_sfha_category %in% c("Removed from prelim SFHA", "Always SFHA")) |>
  mutate(
    treated = prelim_sfha_category == "Removed from prelim SFHA",
    event_post = sale_date >= pre_date
  )

m1 <- feols(
  log_price ~ removedfrom_prelim_sfha | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)



m2 <- feols(
  log_price ~ i(treated * event_post) | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)

m3 <- feols(
  log_price ~ treated * event_post | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)
m4 <- feols(
  log_price ~ treated:event_post | pin + sale_year,
  cluster = ~ pin10,
  data = df_same
)

#etable(m1, m2, m3,4)
modelsummary::modelsummary(list(m1, m2, m3, m4), stars = TRUE)
# cor.test(df_same$treated, df_same$event_post)
table(df_same$treated, df_same$event_post)
```





# Step 6: Interpret Pre-Treatment Periods

Review the event study plot:   
- Are the estimates for periods prior to treatment flat and centered around zero?  
- Are the confidence intervals wide or tight?  
- Do any of the pre-treatment estimates appear significantly different from zero?  

**Why**: Significant pre-trends violate the key identifying assumption of DiD.

## Pre Trend Slope Test - Linear Model (not good enough)

```{r}
slopetest <- lm(log_price ~ sale_year*prelim_sfha_category, 
                df_prep |> filter(sale_date < pre_date | 
                                    (sale_date < 2017 & pre_date_chr == "2005-01-01")) 
)
modelsummary::modelsummary(slopetest)
```

---


## Parallel Trends - Graphs 

### Pre Trends


A couple large houses sold in the treatment categories with small samples easily skews the slopes of the pre trends. So visualizations of  year interactinos for slopes are not super useful. 

```{r}
df_prep |> 
  group_by(event_remapped, sale_year, prelim_sfha_category ) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year, y = avg_price, color = prelim_sfha_category)) +
  geom_point() +
  geom_line() +

  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Average Market Trends in Cook County",
       caption = "",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010, 2026, 4), limits = c(2009, 2027) ) +
  theme_classic()+
  theme(legend.position = "bottom") 


df_prep |> 
  group_by(event_remapped, sale_year, prelim_sfha_category, pre_date_chr, pre_date ) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year, y = avg_price, color = prelim_sfha_category)) +
  geom_point() +
  geom_line() +

  geom_smooth(aes(linetype = event_remapped), method = "lm", se = FALSE) +
#  geom_vline(xintercept=pre_date_chr, lty = 2) +

  facet_wrap(~pre_date_chr) +
  labs(title = "Pre- and Post-Event Slopes by Triad and SFHA Status",
       caption = "",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010, 2026, 4), limits = c(2009, 2027) ) +
  theme_classic()+
  theme(legend.position = "bottom") 

```

```{r}
#| layout-ncol: 2

df_prep <- df_prep |> filter(!pin10 %in% c("0122400028", "0516106013"))

make_sfha_lineplot(
 # df_prep,
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  facet_vars = NULL,
  linetype_var = NULL,
   group_vars = c("prelim_sfha_category"),

  title     = "Pre-Event Trends for Cook County by SFHA Status"
)



make_sfha_lineplot(
 # df_prep,
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  facet_vars = "Triad",
  linetype_var = NULL,
  
  group_vars = c("prelim_sfha_category", "Triad"),
  
  title     = "Pre-Event Trends by Triad and SFHA Status"
)

make_sfha_lineplot(
  (df_prep |> filter(sale_date < pre_date)) ,
  y_var     = "log_price",
  group_vars = c("prelim_sfha_category", "pre_date_chr"),
  linetype_var = NULL,
  facet_vars = "pre_date_chr",
  title     = "Pre-Event Trends by Update Time and SFHA Status"
)


```

### All years 

```{r}
df_prep <- df_prep |>filter(!is.na(in_eff_sfha))

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_vars = "Triad",
  linetype_var  = NULL,
  group_vars = c("prelim_sfha_category", "Triad"),
  title     = "Trends by Triad and SFHA Status"
)

make_sfha_lineplot(
  df_prep,
  y_var     = "log_price",
  facet_vars = "pre_date",
  color_var = "prelim_sfha_category",
    group_vars = c("event_remapped","prelim_sfha_category"),
  title     = "Trends by FIRM Date and SFHA Status"
)

make_sfha_lineplot(
  (df_prep |> filter(sale_price < 2000000)),
  y_var     = "sale_price",
  group_vars = c("event_remapped","prelim_sfha_category", "pre_date"),
  linetype_var = "event_remapped",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)
```

```{r}
#| layout-ncol: 2


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Always SFHA", "Removed from prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Never SFHA", "Added to prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status"
)

```

```{r}
#| layout-ncol: 2


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Always SFHA", "Removed from prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = NULL,
  title     = "County Trends by SFHA Group: Removed v Always"
)


make_sfha_lineplot(
  (df_prep |> filter(prelim_sfha_category %in% c("Never SFHA", "Added to prelim SFHA"))),
  y_var     = "log_price",
  facet_vars = NULL,
  title     = "County Trends by SFHA Group: Added v Never"
)

```

# Placebo Event: 2014

 **Always SFHA and Never SFHA, aka Always Treated and Never Treated Observations**

In a pre-period only window (before any relevant map change), assign a fake “event year” and estimate whether the difference between always-in vs never-in changes over event time before the placebo event. If the lead coefficients aren’t flat, you’ve got non-parallel trends.



```{r}
test_parallel_trends_placebo <- function(df,
                                        id_var = "pin",
                                        year_var = "sale_year",
                                        y_var = "sale_price",
                                        group_var = "change_type_prelim",  # 1 = always-in, 0 = never-in
                                        placebo_year = 2014,
                                        pre_start = 2010,
                                        pre_end = 2018,   # should be BEFORE any real prelim/effective year used in this sample
                                        rel_window = c(-5, 5),
                                        cluster_var = "pin10") {

  stopifnot(all(c(id_var, year_var, y_var, group_var) %in% names(df)))

  d <- df |>
    filter(.data[[group_var]] %in% c("Never SFHA", "Always SFHA")) |>
    filter(.data[[year_var]] >= pre_start, .data[[year_var]] <= pre_end) |>
    mutate(
      log_price = log(.data[[y_var]]),
      rel_t = .data[[year_var]] - placebo_year,
      rel_t = ifelse(rel_t == 0 & sale_date < as.Date("2014-01-01"), -1, rel_t)
    ) |>
    filter(rel_t >= rel_window[1] & rel_t <= rel_window[2])

  # Event-study style: year FE are included; identification comes from within-id changes and relative-time x group interaction.
  # `i(rel_t, group, ref = -1)` gives coefficients for each event time for group==1 relative to group==0,
  # normalized to rel_t = -1.
  fml <- as.formula(paste0(
    "log_price ~ i(rel_t, ", group_var, ", ref = -1) | ",
    id_var, " + ", year_var
  ))

  m <- feols(
    fml,
    data = d,
    cluster = as.formula(paste0("~", cluster_var))
  )

  ct <- broom::tidy(m) |>
  dplyr::filter(grepl("^rel_t::", term)) |>
  dplyr::mutate(
    rel_t   = as.integer(sub("^rel_t::(-?\\d+).*", "\\1", term)),
    group   = sub("^.*change_type_prelim::", "", term),
    is_lead = rel_t < 0
  )

  
  # Simple visual
  p <- ggplot(ct, aes(x = rel_t, y = estimate)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    geom_point() +
    scale_x_continuous(limits = c(-5, 5)) +

    labs(
      x = "Event time (years relative to placebo year)",
      y = "Difference (Always-in minus Never-in), relative to t = -1",
      title = "Placebo event-study pre-trend test"
    ) +
    theme_minimal()

  list(
    data_used = d,
    model = m,
    coef_table = ct,
    plot = p
  )
}

# You need a dataset that contains ONLY always-in and never-in observations for the relevant geography/time,
# and a window that is truly pre-treatment for that geography.
res <- test_parallel_trends_placebo(
  df = df_prep,                       
  id_var = "pin",                    
  year_var = "sale_year",
  y_var = "sale_price",
  group_var = "prelim_sfha_category",      
  placebo_year = 2014,
  pre_start = 2010,
  pre_end = 2019,                
  rel_window = c(-5, 5),
  cluster_var = "pin10"
)

res$plot
summary(res$model)
res$coef_table

```

Not super significantly different but probably not truly parallel trends during pre-trends?


```{r manual-wald-test}
# Test whether ALL lead coefficients are zero
cn <- names(coef(res$model))
lead_cn <- cn[str_detect(cn, "^rel_t::-")]

# Pull coefficients + vcov for the lead terms
b <- coef(res$model)[lead_cn]
V <- vcov(res$model)[lead_cn, lead_cn, drop = FALSE]

# Basic sanity checks
stopifnot(length(b) > 0)
if (anyNA(V) || any(!is.finite(V))) {
  stop("VCOV for lead terms contains NA/Inf. Joint test cannot be computed.")
}

# Compute Wald statistic: b' V^{-1} b
# Use solve(); if singular, fall back to generalized inverse
W <- tryCatch(
  as.numeric(t(b) %*% solve(V, b)),
  error = function(e) {
    as.numeric(t(b) %*% MASS::ginv(V) %*% b)
  }
)

df <- length(b)
p  <- 1 - pchisq(W, df = df)

list(
  statistic = W,
  df = df,
  p_value = p,
  n_leads_tested = df,
  leads = lead_cn
)

```




```{r}
q1_data <- df_prep 

prop_summary_prelim <- q1_data |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    price = mean(sale_price),
    ever_added_prelim   = any(addedto_prelim_sfha == TRUE),
    ever_removed_prelim = any(removedfrom_prelim_sfha == TRUE),
    change_type_prelim = first(change_type_prelim)) |>
  mutate(
    prelim_sfha_category = 
      case_when(
        ever_added_prelim & !ever_removed_prelim ~ "Added to prelim SFHA",
        ever_removed_prelim & !ever_added_prelim ~ "Removed from prelim SFHA",
        # ever_added_prelim & ever_removed_prelim  ~ "Multiple prelim transitions",
        change_type_prelim == "Always SFHA" ~ "Always SFHA",
        change_type_prelim == "Never SFHA" ~ "Never SFHA",
        TRUE ~ "CHECK ME"  ) 
  )

prop_summary_prelim

prelim_sfha_stats <- prop_summary_prelim |>
  group_by(prelim_sfha_category) |>
  mutate(
    avg_sales_per_property = mean(n_sales)) |>
  summarize(
    n_properties = n(),
    n_sales = sum(n_sales),
    mean_price = mean(price),
    median_price = median(price),
    avg_sales_per_property = first(avg_sales_per_property),
    .groups = "drop"
  )

prelim_sfha_stats
```

```{r}
prelim_event_counts <- q1_data |>
  summarize(
    n_sales = n(),
    n_added_events = sum(addedto_prelim_sfha),
    n_removed_events = sum(removedfrom_prelim_sfha),
    pct_sales_with_event = (n_added_events + n_removed_events) / n_sales
  )
prelim_event_counts
```

“Preliminary SFHA reclassifications occur in approximately X% of observed transactions.”


```{r eval = FALSE}

data_dictionary <- df_prep |>
  summarise(across(
    everything(),
    list(
      class  = ~ paste(class(.), collapse = ", "),
      n_na   = ~ sum(is.na(.)),
      n_uniq = ~ n_distinct(.)
    ),
    .names = "{.col}__{.fn}"
  )) |>
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_sep = "__"
  ) |>
  arrange(variable)

write.csv(data_dictionary, "q1_data_dictionary.csv", row.names = FALSE)


skim_summary <- skimr::skim(df_prep)

skim_summary |>
  as.data.frame() |>
  write.csv("q1_skim_summary.csv", row.names = FALSE)


```


# Step 0: Descriptive Stats

```{r}
property_summary <- df_prep |>
  group_by(pin) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price),
    # FIRM exposure
    firm_date = first(pre_date),
    ever_firm_update =  ifelse(first(pre_date)=="2005-01-01",FALSE, TRUE),

    # SFHA dynamics
        change_type = first(change_type)
  )
property_summary
```

## A. Properties with no FIRM update vs ever updated

```{r}
firm_update_stats <- property_summary |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales),
    avg_price = mean(mean_price), # avg price of #avg price per property, kinda weird stat
  )

firm_update_stats
```


```{r}
firm_update_stats <- df_prep |>
     mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(ever_firm_update) |>
  summarize(
    n_properties = n_distinct(pin),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )

firm_update_stats
```

## B. Properties by FIRM panel exposure

```{r}
firm_panel_stats <- property_summary |>
  group_by(firm_date) |>
  summarize(
    n_properties = n(),
    n_sales      = sum(n_sales)
  ) |>
  arrange(firm_date)

firm_panel_stats
```

## C. SFHA status categories

```{r}
#| layout-ncol: 2


sfha_category_stats <- df_prep |>
  group_by(pin) |> mutate(n_sales = n()) |> ungroup() |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    .groups = "drop"
  ) |>
  arrange(desc(n_properties))

sfha_category_stats

sfha_category_stats <- df_prep |>
    mutate(ever_firm_update =  ifelse(pre_date =="2005-01-01", FALSE, TRUE) ) |>
  group_by(change_type_prelim) |>
  summarize(
    n_properties = n_distinct(pin),
    #avg_sales_per_property = mean(n_sales),
    n_sales      = n(),
    avg_price = mean(sale_price),
    median_price = median(sale_price)  ) |>
  arrange(desc(n_properties))

sfha_category_stats
```

## D. Cross tab

```{r}
sfha_sales_stats <- df_prep |>
  group_by(change_type_prelim, pre_date) |>
  summarize(
    n_sales = n(),
    n_props = n_distinct(pin),
    avg_price = mean(sale_price),
    median_price = median(sale_price)
  )
sfha_sales_stats
```

```{r}
price_summary <- df_prep |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    p10 = quantile(sale_price, 0.10, na.rm = TRUE),
    p90 = quantile(sale_price, 0.90, na.rm = TRUE)
  )
price_summary

price_by_sfha <- df_prep |>
  group_by(change_type_prelim) |>
  summarize(
    n_sales = n(),
    mean_price = mean(sale_price, na.rm = TRUE),
    median_price = median(sale_price, na.rm = TRUE),
    .groups = "drop"
  )
price_by_sfha
```

```{r}
geo_summary <- df_prep |>
  distinct(pin, Township, Triad) |>
  summarize(
    n_properties = n(),
    n_townships = n_distinct(Township),
    n_triads = n_distinct(Triad)
  )
geo_summary
```

```{r}
housing_type_summary <- df_prep |>
  distinct(pin, condo, class) |>
  summarize(
    n_properties = n(),
    condo_share = mean(condo == "Condo", na.rm = TRUE),
    n_classes = n_distinct(class)
  )
housing_type_summary
```





---

# Step 9: Explicitly State Identification Assumptions

In your write-up, clearly state:
- Parallel trends hold for treated and not-yet-treated units
- Treatment timing is as-good-as-random conditional on covariates and fixed effects
- No spillover effects or contamination
- No anticipatory responses


> Baker et al. (2025, p. 10): "Each assumption must be directly defended."