---
title: "Cook County Parcel Sales"
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    warning: false
    message: false
    error: true
---

# Data Sources and Background Information

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(plm)    # panel linear models. interchangable with fixest but have different syntax for models
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
```

#### Effective FIRMs

**Added to SFHA compared to properties that were never in the SFHA**. Comparison group excludes properties that were always in the SFHA and those that were removed from the SFHA at some point.

> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. LOMRs are only considered in the bottom section on effective FIRMs and insurance requirements.

```{r}


clusters_county <- list(
  pin10      = ~ pin10,
  pin        = ~ pin,
  clean_name = ~ clean_name,
  FIRM_PAN   = ~ FIRM_PAN,
  nbhd_code  = ~ nbhd_code
)


run_by_cluster <- function(formula, data, clusters, label_prefix = "Model") {
  imap(clusters, \(cl, nm) {
    feols(formula, data = data, cluster = cl)
  }) |>
    setNames(paste0(label_prefix, " (cluster: ", names(clusters), ")"))
}
```


clean_name == "Chicago", then triad is "City", Townships 01-12 are North Townships 13 and higher and not chicago mean south triad

# Research Question 1

## Model Info

To investigate whether the value of real estate parcels increases when they are removed from a Special Flood Hazard Area (SFHA), I used a Fixed Effects on PINs with sales from 2010 to 2025.

**For Fixed Effect Models:** The dataset was first prepared by filtering out irrelevant parcels and ensuring that each property had at least two recorded sales. There is an indicator variable for if a PIN was in an SFHA at the time of sale or not.

These models tested whether being removed from the SFHA is associated with a statistically significant increase in log sale price.

I also explored interaction terms with LOMR status. Owners can appeal their flood zone designation and have the map altered. This results in them no longer having mandatory flood insurance if their appeal is accepted.

I also included alternative specifications, such as including binary indicators specifically for whether a parcel was added or removed from an SFHA.

All models clustered standard errors at the parcel level to account for repeated observations of the same land polygon.

-   Robustness checks: cluster at eff_date or muni level, vcov = "hetero", etc.

Notes:

1.  Removal from the SFHA is due to the FEMA flood insurance rate maps being updated. Properties are either in or out of the "1-in-100" year flood plain. They can be located in the SFHA and also have a LOMR that "removes" them from the floodplain. This information is represented in multiple variables (`in_eff_sfha` and `in_lomr`). If an observation is coded as `Removed` from an SFHA, it indicates that the floodplain shapefile itself changed that was created by FEMA.

-   If a property was in an SFHA in a FIRM and had an approved LOMR and then the FIRM is updated years later and the LOMR was still viewed as accurate and valid, then the PIN will appear as "removed from the SFHA" because the updated FIRM will incorporate the old LOMR into the updated floodplain. Depending on the time of sale, being flagged as removed from the SFHA would miss the potential price change from the change in insurance requirement (which again, was not the original research question).

2.  Treatment window timing: In theory, EFF_DATE would be associated with a change in price due to the capitalization of mandatory flood insurance requirement for homes that have mortgages in floodplains.

-   PRE_DATE is also used due to a buyers anticipation of a policy's impact. The knowledge of the risk and the potential loss due to future floods may decrease the amount that buyers are willing to pay for a property that they see as more risky even if the financial ties to required flood insurance are not effective yet.

-   Areas that have received new flood maps are mostly wealthier parts of Cook County. The pins added to flood plains in the preliminary FIRM are all in Northern Cook County. The FIRMs updated in 2019 and 2021 are along the lake front and include Glencoe/Wilmette areas. Could really influence price trends.

Contributions to the literature: Many models model if SFHA status changes, but have it as one variable. this assumes that the effect of being added in or removed from an SFHA is the same in both directions. I model in_eff_sfha as one variable and separate it into added and removed to see if there are different effects.

```{r}
skim(df_prep)
```

## Comparison of Prelim and Eff FIRM Counts


```{r}
feols(log(sale_price) ~ in_eff_sfha*Triad | pin + sale_year,
     data = df_prep,
      cluster = ~pin10,
) |> modelsummary(stars = TRUE)
```


```{r}
df_prep |> filter((change_type == "Changes SFHA" &  change_type != "Always SFHA") |
                           # and properties that are never treated for being removed from the SFHA
                           (treat_year_remove_eff == 10000 ) ) |>
feols(log(sale_price) ~ sw(addedto_eff_sfha*in_lomr) | pin + sale_year,
     # data = df_prep,
     subset = ~eff_date_chr != "2008-08-19",
      cluster = ~pin10,
      fsplit= ~eff_date_chr
) |> modelsummary(stars = TRUE)
```

```{r}
#| label: tbl-mappedin-eff-fsplit
#| tbl-cap: "Subsets models so that comparison group is only PINs in same FIRMs that were updated."

df_prep |> filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000)  |>
feols(log(sale_price) ~ sw(addedto_eff_sfha*in_lomr) | pin + sale_year,
     # data = df_prep,
     subset = ~eff_date_chr != "2008-08-19",
      cluster = ~pin10,
      fsplit= ~eff_date_chr
) |> modelsummary(stars = TRUE)
```

# Models

> Skim this: https://www.bookdown.org/rwnahhas/RMPH/mlr-interaction.html

"Stratification is equivalent to interacting the effect modifier with every other predictor in the model whereas including an interaction only interacts the effect modifier with the predictor of interest" \## Effect of Insurance Requirement

### Effective FIRM Descriptive Stats

```{r}
#| tbl-cap: "Observations per year. Includes the pre and post treatment sales for those that were added or removed from an EFFECTIVE SFHA"
#| layout-ncol: 2
#| include: false
#| 

table(df_prep$sale_year, df_prep$treat_year_add_eff)

table(df_prep$sale_year, df_prep$treat_year_remove_eff)
```

```{r}
#| tbl-cap: "Observations per year. Added to (removed from) Effective SFHA"
#| layout-ncol: 2

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$addedto_eff_sfha[df_prep$sale_year>=2016])

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$removedfrom_eff_sfha[df_prep$sale_year>=2016])
```

```{r}
# eff_date_chr and group_names should have same number of observations. 
table(df_prep$eff_date_chr)
table(df_prep$group_name_eff)

table(df_prep$addedto_eff_sfha)
table(df_prep$removedfrom_eff_sfha)
```

```{r}
#| tbl-cap: "Properties in South Triad that were removed from SFHA in 2019 and properties in South Triad that were always in the SFHA that were in FIRMs updated in 2019."


df_prep |> filter(Triad == "South" & treat_year_remove_eff == "2019") # all 2019 treatment pins are in South Triad

df_prep |> filter(Triad == "South" & change_type == "Always SFHA" & eff_date_chr == "2019-11-01") 
# change type only exists for effective 
```

-   Reminder: Cohort should be fixed for each unit and represent the period when the treatment was received.\

-   to get the canonical two-way fixed effects (TWFE) estimates, use interaction command `i(factor_variable, number variable, reference_period)`

-   `iplot` reports coefficients of variables created with `i()` and only those variables. `coefplot()` would display all coefficients.

If a PIN is in an SFHA and a LOMR, then the insurance requirement is removed. If measuring capitalization of the flood insurance cost, then whether or not flood insurance would be required for a federally backed mortgage is the key variable. This is what capitalization literature does.

```{r}
df_prep  |> 
  group_by(sale_year, in_eff_sfha, in_lomr) |> summarize(n = n())

df_prep  |> 
  group_by(sale_year, removedfrom_eff_sfha, in_lomr) |> summarize(n = n())


df_prep  |> group_by(sale_year, ins_req) |> summarize(n=n())
table(df_prep$sale_year, df_prep$ins_req)
```

```{r}

lomr_pins <- readRDS("./data/processed/df_allsales.rds")  |> 
  filter(lomr_date != 0 ) |> 
  select(pin, lomr_date) |> distinct()


table(lomr_pins$lomr_date)
table(df_prep$removedfrom_eff_sfha)
table(df_prep$in_eff_sfha)
```

```{r}

table(df_prep$sale_year)

df_prep <- df_prep |>
  left_join(lomr_pins) |>
  group_by(pin) |>
  arrange(sale_year) |>
  
  mutate(
    removed = if_else(dplyr::lag(ins_req == TRUE) & ins_req == FALSE, TRUE, FALSE),
    removed_ever = any(removed, na.rm=TRUE) )|>
  ungroup() |>
  mutate(
    removed_date = if_else(removed_ever==TRUE & lomr_date < EFF_DATE, lomr_date, NA_Date_),
    removed_date = if_else(removed_ever==TRUE & is.na(removed_date), EFF_DATE, removed_date
  )) |>
  ungroup() |>
  mutate(
  removed_year = if_else(!is.na(removed_date), year(removed_date), NA),
  rel_year_removed = if_else(!is.na(removed_year), as.integer(sale_year - removed_year), -1000))


table(df_prep$lomr_date)

df_prep <- df_prep |> distinct(pin, sale_date, sale_price, .keep_all = TRUE)
```

```{r}
df_prep$removed_year[is.na(df_prep$removed_year)] <- 10000
#df_prep$rel_year_removed[is.na(df_prep$rel_year_removed)] <- -1000
#df_prep$rel_year_removed[is.infinite(df_prep$rel_year_removed)] <- -1000

table(df_prep$removed_date)
table(df_prep$removed_ever)

table(df_prep$removed_year)
table(df_prep$rel_year_removed)

#df_prep$removed_year = as.factor(df_prep$removed_year)

```

```{r}
#| label: tbl-removedbasic
#| tbl-cap: "Removal of insurance requirement's effect on sale price."

twfe_removed2 = feols(log(sale_price) ~ removed  | 
                      pin + sale_year,   
                    cluster = ~pin10,
                    data = df_prep#,
                  #  subset = ~ rel_year_removed!= -12
)
twfe_removed2|> etable()

```

### Insurance requirement removed due to LOMRs or Mapped Out of SFHA

```{r}
#| label: sa-v-twfe

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed,
                                      ref.c = 10000, 
                                      ref.p = c(-1, -1000)
                                      ) | pin + sale_year,
              cluster = ~pin10,
              data = df_prep              )
#etable(mod2)
summary(mod2, agg= "att")

twfe_removed= feols(log(sale_price) ~ i(rel_year_removed,  ref =c(-1, -1000 ))  | 
                      pin + sale_year,   
                    cluster = ~pin10,
                    data = df_prep#,
                             #     subset = ~ rel_year_removed != -12
)

#summary(twfe_removed)
#iplot(twfe_removed)


iplot(list(twfe_removed, mod2), xlim = c(-8, 6), ylim= c(-1,1), 
      main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

# switches order color/icon order
# iplot(list(mod2, twfe_removed), 
#       main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
# legend("topleft", col = c(1, 2), pch = c(20, 15), 
#        legend = c("S&A (2020)", "TWFE"))
```

### Excludes PINs that were in LOMRs

```{r}
#| label: excludeslomrs

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed, 
                                      ref.p = c(-1, -1000))  | pin + sale_year,
              cluster= ~pin10,
              data = (df_prep |> filter(in_lomr == FALSE))
              )
#modelsummary::modelsummary(mod2, stars = TRUE)
summary(mod2, agg= "att")
# iplot(mod2)

#table(df_prep$in_lomr)
twfe_removed <-  feols(log(sale_price) ~ i(rel_year_removed,
                                           ref =c(-1, -1000 ))  | 
                         pin + sale_year,   
                       cluster = ~pin10,
              data = (df_prep |> filter(in_lomr == FALSE))
                     #  subset = ~in_lomr == "Not in LOMR"
)

etable(twfe_removed)
#iplot(twfe_removed)

iplot(list(mod2, twfe_removed), 
      main = "Effect of Removal from SFHA (in_lomr == FALSE)",xlim = c(-8,8))
legend("topleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("S&A (2020)", "TWFE"))


```
