---
title: "Q1 Model comparison"
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    warning: false
    message: false
---

```{r}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
library(rlang)
library(flextable)


data_version <- "targets_hybrid_polychange"  # targets, targets_hybrid, or arcgis, arcgis_notfiltered

clusters_county <- list(
  pin10      = ~ pin10#,
 # pin        = ~ pin,
#  clean_name = ~ clean_name#, FIRM_PAN   = ~ FIRM_PAN #,
#   nbhd_code  = ~ nbhd_code
)

clusters_basic <- list(
  pin10      = ~ pin10#,#  FIRM_PAN   = ~ FIRM_PAN#,
 # clean_name = ~ clean_name#
#  pin        = ~ pin
)

run_by_cluster <- function(formula, data, clusters, prefix = "Model") {
  purrr::imap(clusters, function(cl, nm) {
    fixest::feols(formula, data = data, cluster = cl)
  }) |>
    setNames(paste0(prefix, " (cluster: ", names(clusters), ")"))
}

# Convenience: bind multiple named lists of models into one named list
bind_models <- function(...) {
  out <- c(...)
  # guard against duplicate names (modelsummary will drop/merge silently)
  if(any(duplicated(names(out)))) {
    stop("Duplicate model names detected. Fix labels so each model has a unique name.")
  }
  out
}

extract_terms <- function(models, dataset_id, block_name) {
  # models: whatever bind_models() returns. If it's a list, iterate.
  # If bind_models returns a named list of models, this works.
  out <- lapply(names(models), function(mname) {
    m <- models[[mname]]

    tt <- broom::tidy(m)
    tt$model_name  <- mname
    tt$dataset_id  <- dataset_id
    tt$block       <- block_name
    tt$n_obs       <- stats::nobs(m)
    tt
  })

  dplyr::bind_rows(out)
}

to_logical01 <- function(x) {
  # Handles logical, 0/1, and character "0"/"1"/"TRUE"/"FALSE" tolerably.
  if (is.logical(x)) return(x)
  if (is.numeric(x) || is.integer(x)) return(as.logical(x))
  if (is.character(x)) {
    x2 <- toupper(trimws(x))
    return(dplyr::case_when(
      x2 %in% c("TRUE", "T", "1")  ~ TRUE,
      x2 %in% c("FALSE", "F", "0") ~ FALSE,
      TRUE                        ~ NA
    ))
  }
  as.logical(x)
}


add_stars <- function(p) {
  dplyr::case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ "+",
    TRUE     ~ ""
  )
}

coef_cell <- function(est, se, p, n_obs= NULL){
  if_else(
    is.na(est),
    "—",
    paste0(
      formatC(est, digits = 2, format = "f"),
      add_stars(p),
      "\n(",
      formatC(se, digits = 2, format = "f"),
      ")"#,
    #  if (!is.null(nobs)) paste0("\n[N = ", formatC(n_obs, format = "d", big.mark = ","), "]") else ""
          )
  )
  }

```

# Compare datasets and output

```{r}
#| label: load-4-new-datasets

source("R/helper_pins_to_drop.R")
# source("R/helper_pins_to_drop_forsure.R")


if(data_version %in% c("arcgis")){
  
  data_dir <- "data/processed/variants"
  
  if(data_version == "arcgis"){
    dataset_map <- c(
      bldg_sfha  = "df_prep__bldg_sfhaarcgis_redo_2026sales.rds",
      parcel_sfha  = "df_prep__parcel_sfhaarcgis_redo_2026sales.rds",
      bldg_1in500     = "df_prep__bldg_1in500arcgis_redo_2026sales.rds",
      parcel_1in500     = "df_prep__parcel_1in500arcgis_redo_2026sales.rds"
    )
  }
  
  datasets <- lapply(names(dataset_map), function(id) {
    path <- file.path(data_dir, dataset_map[[id]])
    df <- readRDS(path)
    df$dataset_id <- id
    df
  })
  
  datasets_og <- lapply(datasets, function(df) {
    df |> 
      filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014)
      ) |>
      mutate(
        Triad = case_when(
          clean_name == "Chicago" ~  "City",
          as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
          as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
        ),
        Triad = factor(Triad, levels = c("South", "North", "City") ),
        in_eff_sfha    = in_eff_sfha == 1,
        in_prelim_sfha = in_prelim_sfha == 1
      )  |>
      filter(!is.na(in_eff_sfha) & !is.na(in_prelim_sfha)) |>
      group_by(pin) |>
      mutate(d_price_pct = round((sale_price-dplyr::lag(sale_price))/(dplyr::lag(sale_price)), digits = 2), .after = pin) |> ungroup() |> 
      filter(is.na(d_price_pct) | d_price_pct < 20) 
  }) 
  
  names(datasets_og) <- names(dataset_map)
  
  col_order <- c(
    "bldg_sfha",
    "parcel_sfha",
    "bldg_1in500",
    "parcel_1in500"
  )
  
  pretty_cols <- c(
    model_name = "Model",
    term       = "Term",
    bldg_sfha  = "Bldg - SFHA",
    parcel_sfha  = "Parcel - SFHA",
    bldg_1in500     = "Bldg - 1 in 500",
    parcel_1in500     = "Parcel - 1 in 500"
  )
  
  
  }else if(data_version == "targets" | 
           data_version == "targets_hybrid" | 
           data_version == "targets_hybrid_2026sales" |
           data_version == "targets_hybrid_polychange"
           ){
  
    data_dir <-  "data/processed/targets/sales"

    if(data_version == "targets"){
      dataset_map <- c(
        #  land_baseline    = "df_prep_land_baseline_final.rds",
        land_updated     = "df_prep_land_updated_final.rds",
        # bldg_baseline    = "df_prep_bldg_baseline_final.rds",
        bldg_updated     = "df_prep_bldg_updated_final.rds",
        #  ptaxsim_baseline = "df_prep_ptaxsim_baseline_final.rds",
        ptaxsim_updated  = "df_prep_ptaxsim_updated_final.rds",
        #  risk500_baseline = "df_prep_risk500_baseline_final.rds",
        risk500_updated  = "df_prep_risk500_updated_final.rds",
        #  risk500_land_baseline = "df_prep_risk500_land_baseline_final.rds",
        risk500_land_updated = "df_prep_risk500_land_updated_final.rds"
      )
      
      col_order <- c(
        "bldg_updated",
        "land_updated",
        "risk500_updated",
        "risk500_land_updated",
        "ptaxsim_updated"
      )
      
  pretty_cols <- c(
    model_name = "Model",
    term       = "Term",
    bldg_updated  = "Bldg - SFHA",
    land_updated  = "10-dig Land - SFHA",
    risk500_updated  = " Bldg - 1-in-500",
    risk500_land_updated  = "Land - 1-in-500", 
    ptaxsim_updated = "PTAX Bldg SFHA"

  )
    }else if(data_version == "targets_hybrid_2026sales" | data_version == "targets_hybrid_polychange"
             ){
        # note, "updated" names use the December 2025 download of sales because it was updated from the "baseline" sales data from July 2025
        # newest file is named with _2026_ in the title
      
      if(data_version == "targets_hybrid_2026sales"){
        dataset_map <- c(
          bldg_updated     = "df_prep_bldg_2026_arcgis_forQ1_assumptiontests.rds",
          land_updated     = "df_prep_land_2026_arcgis_forQ1_assumptiontests.rds",
          risk500_updated  = "df_prep_risk500_2026_arcgis_forQ1_assumptiontests.rds",  # bldg polygon intersections
          risk500_land_updated = "df_prep_risk500_land_2026_arcgis_forQ1_assumptiontests.rds"
          
          # commenting out because it does not have the for_Q1_assumptiontest variables created.
          # ptaxsim_updated  = "df_prep_ptaxsim_updated_final.rds"
        )
      }else if(data_version == "targets_hybrid_polychange"){
        # dataset_map <- c(
        #   bldg_updated     = "df_prep_bldg_v2025_12.rds",
        #   land_updated     = "df_prep_land_v2025_12.rds",
        #   risk500_updated  = "df_prep_risk500_v2025_12.rds",  # bldg polygon intersections
        #   risk500_land_updated = "df_prep_risk500_land_v2025_12.rds"
        # ),
        
         dataset_map <- c(
          bldg_updated     = "df_prep_bldg_v2026_03.rds",
          land_updated     = "df_prep_land_v2026_03.rds",
          risk500_updated  = "df_prep_risk500_v2026_03.rds",  # bldg polygon intersections
          risk500_land_updated = "df_prep_risk500_land_v2026_03.rds"
        )
      }
      
    col_order <- c(
    "bldg_updated",
    "land_updated",
    "risk500_updated",
    "risk500_land_updated"#,
   # "ptaxsim_updated"
  )
  
  pretty_cols <- c(
    model_name = "Model",
    term       = "Term",
    bldg_updated  = "Bldg - SFHA",
    land_updated  = "10-dig Land - SFHA",
    risk500_updated  = " Bldg - 1-in-500",
    risk500_land_updated  = "Land - 1-in-500"#,
   # ptaxsim_updated = "Ptaxsim w/ bldg, SFHA"

  )
    }else if(data_version == "targets_hybrid"){

      dataset_map <- c(
        # note, "updated" names use the December 2025 download of sales.
        # newest file is named with _2026_ in the title
        bldg_updated     = "df_prep_bldg_updated_arcgis_forQ1_assumptiontests.rds",
        land_updated     = "df_prep_land_updated_arcgis_forQ1_assumptiontests.rds",
        risk500_updated  = "df_prep_risk500_updated_arcgis_forQ1_assumptiontests.rds",  # bldg polygon intersections
        risk500_land_updated = "df_prep_risk500_land_updated_arcgis_forQ1_assumptiontests.rds"
      
        # doesn't have newest variables yet that let it skip the slow variable creation chunk
        #  ptaxsim_updated  = "df_prep_ptaxsim_updated_final.rds"
      )
      
    col_order <- c(
    "bldg_updated",
    "land_updated",
    "risk500_updated",
    "risk500_land_updated"  )
  
  pretty_cols <- c(
    model_name = "Model",
    term       = "Term",
    bldg_updated  = "Bldg - SFHA",
    land_updated  = "10-dig Land - SFHA",
    risk500_updated  = " Bldg - 1-in-500",
    risk500_land_updated  = "Land - 1-in-500"  )
    }
   
    datasets <- lapply(names(dataset_map), function(id) {
    path <- file.path(data_dir, dataset_map[[id]])
    df <- readRDS(path)
    df$dataset_id <- id
    df
  })
  
 # no matter what targets version gets read in, then do these steps
  datasets_og <- lapply(datasets, function(df) {
    df |> 
      filter(!pin10 %in% drop_parcels  |          
               (pin10 == "0113301013" & sale_year > 2014)
             ) |>
      mutate(
        Triad = case_when(
          clean_name == "Chicago" ~  "City",
          as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
          as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
        ),
        Triad = factor(Triad, levels = c("South", "North", "City") ),
        in_eff_sfha    = in_eff_sfha == 1,
        in_prelim_sfha = in_prelim_sfha == 1
      )  |>
      filter(!is.na(in_eff_sfha) & !is.na(in_prelim_sfha))
  }) 
  
  names(datasets_og) <- names(dataset_map)
  

}

```


```{r}
# ---- Treated-observation summary (added/removed) ----

treated_summary <- purrr::imap_dfr(datasets_og, function(df, id) {
 
  pre_add <- to_logical01(df$addedto_prelim_sfha)
  pre_rem <- to_logical01(df$removedfrom_prelim_sfha)

  tibble::tibble(
    dataset_id = id,
    n_obs      = nrow(df),
    pre_add_obs   = sum(pre_add, na.rm = TRUE),
    pre_treat_add_pin10 = dplyr::n_distinct(df$pin10[pre_add]),
    pre_remove_obs = sum(pre_rem, na.rm = TRUE),
    pre_treat_rem_pin10 = dplyr::n_distinct(df$pin10[pre_rem])
  )
}) 

treated_summary_ft <- treated_summary |>
  flextable::flextable() |>
  flextable::autofit()

treated_summary_ft

treated_summary <- purrr::imap_dfr(datasets_og, function(df, id) {
  eff_add <- to_logical01(df$addedto_eff_sfha)
  eff_rem <- to_logical01(df$removedfrom_eff_sfha)
  tibble::tibble(
    dataset_id = id,
    n_obs      = nrow(df),

    eff_add_obs   = sum(eff_add, na.rm = TRUE),
    eff_treat_add_pin10 = dplyr::n_distinct(df$pin10[eff_add]),
    eff_remove_obs = sum(eff_rem, na.rm = TRUE),
    eff_treat_rem_pin10 = dplyr::n_distinct(df$pin10[eff_rem])
  )
}) 

treated_summary_ft <- treated_summary |>
  flextable::flextable() |>
  flextable::autofit()

treated_summary_ft

```

```{r}
#| label: build-treatment-variables
#| eval: false

# how datasets_og was created! it is read in from an RDS object now to speed things up.
datasets_og <- lapply(datasets_og, function(df){
  df |> 
      filter(!pin10 %in% drop_parcels  |          
               (pin10 == "0113301013" & sale_year > 2014)
             ) |>

    group_by(pin) |>
 mutate(
   eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date),
    
    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(addedto_eff_sfha== TRUE) )
                                 & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removedfrom_eff_sfha== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added or removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(addedto_prelim_sfha == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removedfrom_prelim_sfha== TRUE), year(pre_date), 10000)
    
    
  ) |>
  ungroup() |>
  mutate(
    
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
        rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000)
  ) |>
  mutate(
   # qtr  = quarter(sale_date),     # 1 to 4
    #year = year(sale_date),            
    #sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    
    # 2005-01-01 2015-02-15 2019-06-28 2021-09-22 

    group_name_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" ~ 0,
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-07-01" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,

      TRUE ~ NA),
      
      ),
    treated_group_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha|removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ NA))
    )

    })

if(data_version == "targets_hybrid"){

  write_rds(datasets2, "data/processed/combined_datasets_targets_2025parcels.rds")
  
  } else if(data_version == "targets_hybrid_2026sales"){
    write_rds(datasets2, "data/processed/combined_datasets_targets_hybrid_2026sales.rds")
    
  } else if(data_version == "targets"){
    write_rds(datasets2, "data/processed/combined_datasets.rds")
    
}
```



# In_SFHA vs Added vs Removed, with and without Triads

```{r}
#| label: model-fns


fit_effective_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff County - Symmetric"
    ),
    
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha * Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff Triads - Symmetric"
    ),
    
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff County - R"
    ),
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_eff ==10000)),
      clusters = clusters_county,
      prefix = "Eff Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff Triads - A"
    )
  )
}

fit_prelim_models <- function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ in_prelim_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim County - Symmetric"
    ),
    
    run_by_cluster( 
      log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim Triads - Symmetric"
    ),
     
    run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim Triads - A"
    )
  )
}

effective_models <- lapply(datasets_og, fit_effective_models)
prelim_models    <- lapply(datasets_og, fit_prelim_models)

```




```{r}

eff_and_prelim <-  function(df_prep) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff County - Symmetric"
    ),
    
    run_by_cluster(
      log(sale_price) ~ in_eff_sfha * Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Eff Triads - Symmetric"
    ),
    
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff County - R"
    ),
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_eff ==10000)),
      clusters = clusters_county,
      prefix = "Eff Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_eff == 10000)),
      clusters = clusters_county,
      prefix = "Eff Triads - A"
    ),
    
      run_by_cluster(
      log(sale_price) ~ in_prelim_sfha | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim County - Symmetric"
    ),
    
    run_by_cluster( 
      log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
      data = df_prep,
      clusters = clusters_county,
      prefix = "Prelim Triads - Symmetric"
    ),
     
    run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_add_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim Triads - R"
    ),
    
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha * Triad | pin + sale_year,
      data = (df_prep |> filter(treat_year_remove_prelim == 10000)),
      clusters = clusters_county,
      prefix = "Prelim Triads - A"
    )
  )
}

standardize_term <- function(term) {
  term |>
    str_replace("_(eff|prelim)_", "_") |>
    str_replace("^in_(eff|prelim)_", "in_") |>
    str_replace("^addedto_(eff|prelim)_", "addedto_") |>
    str_replace("^removedfrom_(eff|prelim)_", "removedfrom_")
}

coef_label_map <- function() {
  c(
    "addedto_sfhaTRUE"      = "Mapped In",
    "removedfrom_sfhaTRUE"  = "Mapped Out",
    "in_sfhaTRUE"           = "In SFHA",

    "addedto_sfhaTRUE:TriadCity"     = "Mapped In × City",
    "addedto_sfhaTRUE:TriadNorth"    = "Mapped In × North",
    "removedfrom_sfhaTRUE:TriadCity" = "Mapped Out × City",
    "removedfrom_sfhaTRUE:TriadNorth"= "Mapped Out × North",
    "in_sfhaTRUE:TriadCity"          = "In SFHA × City",
    "in_sfhaTRUE:TriadNorth"         = "In SFHA × North"
  )
}

# flatten list(list(models)) into a tibble with dataset_id + model_name + model
flatten_models <- function(eff_and_pre_models) {
  imap_dfr(eff_and_pre_models, function(model_list, dataset_id) {
    imap_dfr(model_list, function(mod, model_name) {
      tibble(dataset_id = dataset_id, model_name = model_name, model = list(mod))
    })
  })
}
standardize_model_base <- function(model_label) {
  model_label |>
    # drop leading stage tag
    str_remove("^(Eff|Prelim)\\s+") |>
    # normalize Triad/Triads variations
    str_replace("^Triad\\s+-\\s+", "Triads - ") |>
    str_replace("^Triads\\s+-\\s+", "Triads - ") |>
    # normalize spacing around hyphens
    str_replace_all("\\s+-\\s+", " - ") |>
    str_trim()
}

parse_model_name <- function(model_name) {
  cluster <- str_match(model_name, "\\(cluster:\\s*([^\\)]+)\\)")[,2]
  model_label <- str_trim(str_remove(model_name, "\\s*\\(cluster:.*\\)$"))

  stage <- case_when(
    str_detect(model_label, "^Eff\\b") ~ "eff",
    str_detect(model_label, "^Prelim\\b") ~ "prelim",
    TRUE ~ NA_character_
  )

  tibble(model_label = model_label, cluster = cluster, stage = stage)
}



  model_levels <- c(
  "County - Symmetric",
  "County - R",
  "County - Add",
  "Triads - Symmetric",
  "Triads - R",
  "Triads - A"
)


  term_levels <- c(
  "In SFHA",
  "In SFHA × City",
  "In SFHA × North",
  "Mapped Out",
  "Mapped Out × City",
  "Mapped Out × North",
  "Mapped In",
  "Mapped In × City",
  "Mapped In × North"
)
  
  library(gt)

  
# -------- main function: returns a gt table in "grid form" --------
make_eff_pre_grid <- function(
  eff_and_pre_models,
  dataset_labels,
  digits = 2
) {

  coef_map <- coef_label_map()

  tidy_df <-
    flatten_models(eff_and_pre_models) |>
    mutate(parsed = map(model_name, parse_model_name)) |>
    unnest(parsed) |>
    mutate(tidy = map(model, broom::tidy)) |>
    unnest(tidy) |>
    mutate(
      # if stage not parsed from label, infer from term
      stage = coalesce(
        stage,
        case_when(
          str_detect(term, "_eff_") | str_detect(term, "^in_eff_") |
            str_detect(term, "^addedto_eff_") | str_detect(term, "^removedfrom_eff_") ~ "eff",
          str_detect(term, "_prelim_") | str_detect(term, "^in_prelim_") |
            str_detect(term, "^addedto_prelim_") | str_detect(term, "^removedfrom_prelim_") ~ "prelim",
          TRUE ~ NA_character_
        )
      ),
      dataset = recode(dataset_id, !!!dataset_labels, .default = dataset_id),
      stage_lab = if_else(stage == "eff", "Effective", "Preliminary"),
      term_std = standardize_term(term),
      term_lab = recode(term_std, !!!coef_map, .default = term_std),
      cell = paste0(
        formatC(estimate, digits = digits, format = "f"),
        add_stars(p.value),
        "<br>(",
        formatC(std.error, digits = digits, format = "f"),
        ")"
      )
    )
tidy_df <- tidy_df |>
  mutate(
    model_base = standardize_model_base(model_label)
  )

tidy_df <- tidy_df |>
  mutate(
    model_base = factor(model_base, levels = model_levels),
    term_lab   = factor(term_lab, levels = term_levels)
  )

tidy_df <- tidy_df |>
  arrange(model_base, term_lab)
  
  # Create paired columns per dataset: dataset__eff and dataset__prelim
  wide_df <-
    tidy_df |>
    select(model_base, term_lab, dataset, stage, stage_lab, cell) |>
    distinct() |>
    mutate(col = paste0(dataset, "__", stage)) |>
    select(model_base, term_lab, col, cell) |>
    pivot_wider(names_from = col, values_from = cell)

  # Ensure column order: for each dataset, eff then prelim
  ds <- unname(dataset_labels)
  col_order <- c("model_base", "term_lab", as.vector(rbind(paste0(ds, "__eff"), paste0(ds, "__prelim"))))
  col_order <- col_order[col_order %in% names(wide_df)]
  wide_df <- wide_df |> select(all_of(col_order))

  # Build gt table
  gt_tbl <- wide_df |>
    gt(rowname_col = NULL) |>
    cols_label(
      model_base = "Model",
      term_lab = "Term"
    )

  # Label subcolumns and add spanners
  for (d in ds) {
    pre_col <- paste0(d, "__prelim")

    eff_col <- paste0(d, "__eff")

    present <- c( pre_col, eff_col) %in% names(wide_df)
    if (!any(present)) next

    # subcolumn labels
    gt_tbl <- gt_tbl |>
            cols_label(!!!setNames(list("Preliminary"), pre_col)) |>
      cols_label(!!!setNames(list("Effective"), eff_col))

    # spanner across the pair (only if both exist)
    if (all(c(pre_col, eff_col) %in% names(wide_df))) {
      gt_tbl <- gt_tbl |>
        tab_spanner(
          label = d,
          columns = c( all_of(pre_col), all_of(eff_col))
        )
    }
  }
  


  # small formatting niceties
  gt_tbl |>
    cols_align(align = "left", columns = c(model_base, term_lab)) |>
    cols_align(align = "center", columns = -c(model_base, term_lab)) |>
    tab_options(
      table.font.size = px(12),
      data_row.padding = px(3)
    )
}
```

```{r}
dataset_family <- if (data_version %in% c("arcgis", "arcgis_notfiltered", "arcgis_2026sales_notfiltered")) {
  "arcgis"
} else if (data_version %in% c("targets")) {
  "targets"
} else if(data_version %in% c("targets_hybrid", "targets_hybrid_2026sales", "targets_hybrid_polychange")){
  "targets_4"
} else{
  stop("Unrecognized data_version: ", data_version)
}

datasets_for_grid <- switch(
  dataset_family,
  arcgis  = datasets_og,
  targets = datasets_og,
  targets_4 = datasets_og
)

all_labels <- switch(
  dataset_family,
  arcgis = c(
    bldg_sfha     = "Bldg - SFHA",
    parcel_sfha   = "Parcel - SFHA",
    bldg_1in500   = "Bldg - 1 in 500",
    parcel_1in500 = "Parcel - 1 in 500"
  ),
  targets = c(
    bldg_updated         = "Bldg - SFHA",
    land_updated         = "Parcel - SFHA (2022 & 2018)",
    risk500_updated      = "Bldg - 1-in-500",
    risk500_land_updated = "Parcel - 1-in-500",
    ptaxsim_updated      = "PTAXSIM Parcels"
  ),
    targets_4 = c(
    bldg_updated         = "Bldg - SFHA",
    land_updated         = "Parcel - SFHA",
    risk500_updated      = "Bldg - 1-in-500",
    risk500_land_updated = "Parcel - 1-in-500"  )
)

dataset_labels <- all_labels[names(datasets_for_grid)]

# Build models for the mega grid
eff_and_pre_models <- lapply(datasets_for_grid, eff_and_prelim)

```

```{r}

grid_tbl <- make_eff_pre_grid(
  eff_and_pre_models = eff_and_pre_models,
  dataset_labels = dataset_labels
)

#grid_tbl <- grid_tbl |>
 # gt::fmt_markdown(gt::everything())

gt_tbl <- grid_tbl |>
    fmt_markdown(columns = everything()) |>
    cols_align(align = "left", columns = c(model_base, term_lab)) |>
    cols_align(align = "center", columns = -c(model_base, term_lab)) |>
    tab_options(
      table.font.size = px(12),
      data_row.padding = px(3),
      column_labels.font.weight = "bold"
    ) |>
    tab_source_note(
      source_note = md("\\* p < 0.1, ** p < 0.05, *** p < 0.01")
    )
saveRDS(gt_tbl, "outputs/tables/grid_tbl_twfe.rds")

gt_tbl


```


```{r}
#| label: build-complete-term-grids
#| message: false
#| warning: false



pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models), function(id) {
  extract_terms(prelim_models[[id]], id, "prelim")
}))
eff_tidy <- dplyr::bind_rows(lapply(names(effective_models), function(id) {
  extract_terms(effective_models[[id]], id, "eff")
}))

# ---- 1) Canonical term universes ----
terms_eff_main <- c("in_eff_sfhaTRUE", "addedto_eff_sfhaTRUE", "removedfrom_eff_sfhaTRUE")
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")

# include any Triad interaction terms that appear anywhere (across datasets/models)
terms_eff_int <- eff_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_eff_sfha") | str_detect(term, "addedto_eff_sfha") | str_detect(term, "removedfrom_eff_sfha"))) |>
  pull(term)

terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_eff_all <- unique(c(terms_eff_main, terms_eff_int))
terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))
```



```{r}
#| column: screen-inset


# ---- 2) Enforce a complete dataset × model × term grid ----
eff_grid <- eff_tidy |>
  filter(term %in% terms_eff_all) |>
  complete(dataset_id, model_name, term = terms_eff_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


eff_tbl <- eff_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value#, n_obs
                          ))

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value#, n_obs
                          ))

# eff_tbl <- eff_grid |>
#   mutate(cell = coef_cell(estimate, std.error, p.value)) |>
#   select(dataset_id, model_name, term, cell)
# 
# pre_tbl <- pre_grid |>
#   mutate(cell = coef_cell(estimate, std.error, p.value)) |>
#   select(dataset_id, model_name, term, cell)
#
# add GOF rows (these already have 'cell')
# eff_tbl <- bind_rows(eff_tbl, eff_gof)
# pre_tbl <- bind_rows(pre_tbl, pre_gof)


eff_tbl <- eff_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

# ---- ) Wide robustness tables: rows = (model_name, term), cols = dataset_id ----
eff_wide <- eff_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


pretty_term <- function(term) {
  term <- as.character(term)
  term <- str_replace_all(term, "::", ":")

  map_one <- function(x) {
    x <- str_trim(x)
    dplyr::case_when(
      x %in% c("Observations")          ~ "N",
x %in% c("Treated observations")  ~ "Treated N",
      x %in% c("in_eff_sfhaTRUE")              ~ "In SFHA",
      x %in% c("addedto_eff_sfhaTRUE")         ~ "Mapped In",
      x %in% c("removedfrom_eff_sfhaTRUE",
               "removed_from_eff_sfhaTRUE")   ~ "Mapped Out",

      x %in% c("in_prelim_sfhaTRUE")           ~ "In SFHA (Prelim)",
      x %in% c("addedto_prelim_sfhaTRUE")      ~ "Mapped In (Prelim)",
      x %in% c("removedfrom_prelim_sfhaTRUE",
               "removed_from_prelim_sfhaTRUE") ~ "Mapped Out (Prelim)",

      TRUE ~ x
    )
  }

  vapply(term, function(t) {
    if (str_detect(t, ":")) {
      parts <- str_split(t, ":", simplify = TRUE)
      parts <- as.character(parts)

      parts <- vapply(parts, map_one, character(1))
      parts <- parts |>
        str_replace_all("_", " ") |>
        str_squish() |>
        str_to_title() |>
        str_replace_all("\\bSfha\\b", "SFHA")

      paste(parts, collapse = " × ")
    } else {
      out <- map_one(t)
      out <- out |>
        str_replace_all("_", " ") |>
        str_squish() |>
        str_replace_all("\\bSfha\\b", "SFHA")
      out
    }
  }, character(1))
}

id_cols <- c("model_name", "term")
data_cols <- setdiff(names(eff_wide), id_cols)

col_order_final <- c(intersect(col_order, data_cols),
                     setdiff(data_cols, col_order))

eff_wide_labeled <- eff_wide |>
  mutate(term = pretty_term(term))

pre_wide_labeled <- pre_wide |>
  mutate(term = pretty_term(term))



ft_eff <- eff_wide_labeled |>
    dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>
  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)


ft_eff


```


```{r}
#| label: tbl-preliminary-mainmodels
#| column: screen


ft_pre <- pre_wide_labeled |>
   dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>
  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)


ft_pre      # with labels

# flextable::flextable(pre_wide)  # without labels

```



```{r}
#| label: robust-table-effective
#| message: false
#| warning: false
#| column: page



eff_core <- eff_tidy |>
    filter(term %in% terms_eff_all) |>
  dplyr::mutate(
    estimate = round(estimate, 4),
    std.error = round(std.error, 4),
    statistic  = round(statistic, 3),
    p.value    = round(p.value, 3)
  )

eff_core <- eff_core |>
  dplyr::mutate(
    stars = add_stars(p.value),
    estimate_star = paste0(
      formatC(estimate, format = "f", digits = 2),
      stars
    )
  )

eff_core <- eff_core |>
  dplyr::mutate(
    coef_cell = paste0(
      formatC(estimate, digits = 2, format = "f"),
      add_stars(p.value),
      "\n(",
      formatC(std.error, digits = 2, format = "f"),
      ")"
    )
  )


eff_core |> dplyr::arrange(model_name, term, dataset_id)

```

```{r}
#| column: page

pre_core <- pre_tidy |>
    filter(term %in% terms_pre_all)  |>
  dplyr::mutate(
    estimate = round(estimate, 4),
    std.error = round(std.error, 4),
    statistic  = round(statistic, 3),
    p.value    = round(p.value, 3)
  )

pre_core <- pre_core |>
  dplyr::mutate(
    stars = add_stars(p.value),
    estimate_star = paste0(
      formatC(estimate, format = "f", digits = 2),
      stars
    )
  )

pre_core <- pre_core |>
  dplyr::mutate(
    coef_cell = paste0(
      formatC(estimate, digits = 2, format = "f"),
      add_stars(p.value),
      "\n(",
      formatC(std.error, digits = 2, format = "f"),
      ")"
    )
  )


pre_core |> dplyr::arrange(model_name, term, dataset_id)

```

## Effective FIRM Models


```{r}
#| label: robust-flextable-effective
#| message: false
#| warning: false
#| column: page
#| eval: false

eff_ft <- eff_core |>
  dplyr::select(dataset_id, model_name, term, estimate_star, std.error, statistic, p.value, n_obs) |>
  flextable::flextable()

eff_ft


```

## Preliminary FIRM Models

```{r}
#| label: robust-flextable-preliminary
#| message: false
#| warning: false
#| column: page
#| eval: false


pre_ft <- pre_core |>
  dplyr::select(dataset_id, model_name, term, estimate_star, std.error, statistic, p.value, n_obs) |>
  flextable::flextable()

pre_ft

```






# Subset models

Restricts the control groups to the group it should be compared to (i.e. Removed compared to Always SFHA & Added compared to Never SFHA)

```{r}
#| eval: false
#| include: false


if(data_version %in% c("arcgis", "arcgis_notfiltered", "arcgis_2026sales_notfiltered")) {
  
  datasets2 <- datasets_og 
  
}else if(data_version == "targets" | data_version == "targets_hybrid"){
  
  # has the treatment variables used in the later section. 
  if(data_version == "targets"){
    
    datasets2 <- read_rds( "data/processed/combined_datasets.rds")
    
  }else if(data_version == "targets_hybrid"){
    
    datasets2 <- read_rds("data/processed/combined_datasets_targets_2025parcels.rds") 
    
  }else if(data_version == "targets_hybrid_2026sales") {
    
    datasets2 <- read_rds("data/processed/combined_datasets_targets_hybrid_2026sales.rds")
  }
   
  datasets2 <-  lapply(datasets2, function(df){
    df |> 
      mutate(
        Triad = case_when(
          clean_name == "Chicago" ~  "City",
          as.numeric(str_sub(pin, 1, 2) ) < 13 ~ "North",
          as.numeric(str_sub(pin, 1, 2) ) >= 13 ~ "South"
        ),
        Triad = factor(Triad, levels = c("South", "North", "City") ),
        in_eff_sfha    = in_eff_sfha == 1,
        in_prelim_sfha = in_prelim_sfha == 1
      )  |>
      filter(!is.na(in_eff_sfha) & !is.na(in_prelim_sfha)) |>
    filter(!pin10 %in% drop_parcels)
    }
    ) 
}
 
```


## Mapped Out

### Effective

```{r}


datasets_h1a <- map(datasets_og, ~ .x |> 
                      filter(change_type != "Never SFHA" &   # properties always in or changed status
                           #  treat_year_add_eff == 10000 & 
                             treat_year_add_eff == 10000)
                           # and properties that are never treated for being added to the SFHA
                  )
```




```{r}
#| label: tbl-filteredproperties-forRQ-effective
#| tbl-cap: "Restricts the sample to parcels whose classification changed from in → out between FIRMs with comparison group of only properties that were Always in an SFHA."
#| column: screen-inset


fit_h1a_models <- function(df) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_eff_sfha * Triad | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Triads - R"
    )
  )

}



eff_models_h1a  <- lapply(datasets_h1a, fit_h1a_models)

eff_tidy <- dplyr::bind_rows(lapply(names(eff_models_h1a), function(id) {
  extract_terms(eff_models_h1a[[id]], id, "eff")
}))

# ---- 1) Canonical term universes ----
terms_eff_main <- c("in_eff_sfhaTRUE", "addedto_eff_sfhaTRUE", "removedfrom_eff_sfhaTRUE")


terms_eff_int <- eff_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_eff_sfha") | str_detect(term, "addedto_eff_sfha") | str_detect(term, "removedfrom_eff_sfha"))) |>
  pull(term)

terms_eff_all <- unique(c(terms_eff_main, terms_eff_int))


eff_grid <- eff_tidy |>
  filter(term %in% terms_eff_all) |>
  complete(dataset_id, model_name, term = terms_eff_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


eff_tbl <- eff_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))


eff_tbl <- eff_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

eff_wide <- eff_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


# flextable::flextable(eff_wide)      # without labels!

data_cols <- setdiff(names(eff_wide), id_cols)

col_order_final <- c(intersect(col_order, data_cols),
                     setdiff(data_cols, col_order))

eff_wide_labeled <- eff_wide |>
  mutate(term = pretty_term(term))

ft_eff <- eff_wide_labeled |>
      dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>

  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)

ft_eff

```


### Preliminary

```{r}

datasets_h1a <- map(datasets_og, ~ .x |> 
                      filter(change_type_prelim != "Never SFHA" &   # properties always in or changed status
                           #  treat_year_add_eff == 10000 & 
                             treat_year_add_prelim == 10000)
                           # and properties that are never treated for being added to the SFHA
                  )
```




```{r}
#| label: tbl-filteredproperties-forRQ
#| tbl-cap: "Restricts the sample to parcels whose classification changed from in → out between FIRMs with comparison group of only properties that were Always in an SFHA."
#| column: screen-inset


fit_h1a_models <- function(df) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim County - R"
    ),
       run_by_cluster(
      log(sale_price) ~ removedfrom_prelim_sfha * Triad | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim Triads - R"
    )
  )

}



prelim_models_h1a  <- lapply(datasets_h1a, fit_h1a_models)

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models_h1a), function(id) {
  extract_terms(prelim_models_h1a[[id]], id, "prelim")
}))

# ---- 1) Canonical term universes ----
terms_pre_main <- c("in_prelim_sfhaTRUE", "addedto_prelim_sfhaTRUE", "removedfrom_prelim_sfhaTRUE")


terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))


pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))


pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


# flextable::flextable(pre_wide)      # without labels!

data_cols <- setdiff(names(eff_wide), id_cols)

col_order_final <- c(intersect(col_order, data_cols),
                     setdiff(data_cols, col_order))

pre_wide_labeled <- pre_wide |>
  mutate(term = pretty_term(term))

ft_pre <- pre_wide_labeled |>
      dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>

  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)

ft_pre

```

### Summary Table

```{r}
#| column: screen-inset


treated_summary <- purrr::imap_dfr(datasets_h1a, function(df, id) {
   eff_removed_obs <- sum(df$removedfrom_eff_sfha == TRUE, na.rm = TRUE)
  pre_removed_obs <- sum(df$removedfrom_prelim_sfha == TRUE, na.rm = TRUE)
  
  tibble::tibble(
    dataset_id = id,
    n_obs = nrow(df),
    eff_treat_pin10_N = dplyr::n_distinct(df$pin10[df$removedfrom_eff_sfha == TRUE & df$Triad == "North"]),
    pre_treat_pin10_N = dplyr::n_distinct(df$pin10[df$removedfrom_prelim_sfha == TRUE& df$Triad == "North"]),
    eff_treat_pin10_S = dplyr::n_distinct(df$pin10[df$removedfrom_eff_sfha == TRUE & df$Triad == "South"]),
    pre_treat_pin10_S = dplyr::n_distinct(df$pin10[df$removedfrom_prelim_sfha == TRUE& df$Triad == "South"]),
        eff_treat_pins_chi = dplyr::n_distinct(df$pin10[df$removedfrom_eff_sfha == TRUE & df$Triad == "City"]),
    pre_treat_pins_chi = dplyr::n_distinct(df$pin10[df$removedfrom_prelim_sfha == TRUE & df$Triad == "City"]),
    eff_rem_obs = eff_removed_obs,
    pre_rem_obs = pre_removed_obs,
    eff_treat_pins = dplyr::n_distinct(df$pin10[df$removedfrom_eff_sfha == TRUE]),
    pre_treat_pins = dplyr::n_distinct(df$pin10[df$removedfrom_prelim_sfha == TRUE]),

   # pre_removed_obs = pre_removed_obs,
   # eff_treated_pct = eff_removed_obs / n_obs,
  #  pre_treated_pct = pre_removed_obs / n_obs
  )
}) # |>
  # dplyr::mutate(
  #   eff_treated_pct = scales::percent(eff_treated_pct, accuracy = 0.1),
  #   pre_treated_pct = scales::percent(pre_treated_pct, accuracy = 0.1)
  # )
```


```{r}

if(data_version == "arcgis" | data_version == "arcgis_notfiltered"){

table(datasets_h1a$parcel_sfha$addedto_eff_sfha)

table(datasets_h1a$parcel_sfha$removedfrom_eff_sfha)

} else{
table(datasets_h1a$land_updated$addedto_eff_sfha)

table(datasets_h1a$land_updated$removedfrom_eff_sfha)
}
treated_summary_ft <- treated_summary |>
  flextable::flextable() |>
  flextable::autofit()

treated_summary_ft

```

## Mapped In


### Effective


```{r}
#| error: true

datasets_h1b <- map(datasets_og, ~.x |> filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                          # treat_year_remove_eff == 10000 & 
                             treat_year_remove_eff == 10000)
)

fit_h1b_models <- function(df) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "eff County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_eff_sfha * Triad | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "eff Triads - A"
    )
  )
}

eff_models_h1b    <- lapply(datasets_h1b, fit_h1b_models)

eff_tidy <- dplyr::bind_rows(lapply(names(eff_models_h1b), function(id) {
  extract_terms(eff_models_h1b[[id]], id, "eff")
}))


terms_eff_int <- eff_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_eff_sfha") | str_detect(term, "addedto_eff_sfha") | str_detect(term, "removedfrom_eff_sfha"))) |>
  pull(term)

terms_eff_all <- unique(c(terms_eff_main, terms_eff_int))


eff_grid <- eff_tidy |>
  filter(term %in% terms_eff_all) |>
  complete(dataset_id, model_name, term = terms_eff_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))

eff_tbl <- eff_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))


eff_tbl <- eff_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

eff_wide <- eff_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


# flextable::flextable(eff_wide)        # Without labels!

data_cols <- setdiff(names(eff_wide), id_cols)

col_order_final <- c(intersect(col_order, data_cols),
                     setdiff(data_cols, col_order))

eff_wide_labeled <- eff_wide |>
  mutate(term = pretty_term(term))

ft_eff <- eff_wide_labeled |>
      dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>
  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)
```

```{r}
#| error: true
#| column: screen-inset
ft_eff

```



### Preliminary

```{r}
#| error: true

datasets_h1b <- map(datasets_og, ~.x |> filter(change_type_prelim != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                          # treat_year_remove_eff == 10000 & 
                             treat_year_remove_prelim == 10000)
)

fit_h1b_models <- function(df) {
  bind_models(
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim County - Add"
    ),
    run_by_cluster(
      log(sale_price) ~ addedto_prelim_sfha * Triad | pin + sale_year,
      data = df,
      clusters = clusters_county,
      prefix = "Prelim Triads - A"
    )
  )
}

prelim_models_h1b    <- lapply(datasets_h1b, fit_h1b_models)

pre_tidy <- dplyr::bind_rows(lapply(names(prelim_models_h1b), function(id) {
  extract_terms(prelim_models_h1b[[id]], id, "prelim")
}))


terms_pre_int <- pre_tidy |>
  distinct(term) |>
  filter(str_detect(term, "Triad") & (str_detect(term, "in_prelim_sfha") | str_detect(term, "addedto_prelim_sfha") | str_detect(term, "removedfrom_prelim_sfha"))) |>
  pull(term)

terms_pre_all <- unique(c(terms_pre_main, terms_pre_int))


pre_grid <- pre_tidy |>
  filter(term %in% terms_pre_all) |>
  complete(dataset_id, model_name, term = terms_pre_all) |>
  filter(!(is.na(estimate) & is.na(std.error) & is.na(statistic) & is.na(p.value)))

pre_tbl <- pre_grid |>
  mutate(cell = coef_cell(estimate, std.error, p.value))


pre_tbl <- pre_tbl |>
  mutate(dataset_id = factor(dataset_id, levels = col_order))

pre_wide <- pre_tbl |>
  select(model_name, term, dataset_id, cell) |>
  pivot_wider(names_from = dataset_id, values_from = cell) |>
  arrange(model_name, term)


# flextable::flextable(pre_wide)        # Without labels!

data_cols <- setdiff(names(pre_wide), id_cols)

col_order_final <- c(intersect(col_order, data_cols),
                     setdiff(data_cols, col_order))

pre_wide_labeled <- pre_wide |>
  mutate(term = pretty_term(term))

ft_pre <- pre_wide_labeled |>
      dplyr::select(dplyr::all_of(id_cols), dplyr::all_of(col_order_final)) |>
  flextable::flextable() |>
  flextable::set_header_labels(values = pretty_cols)
```

```{r}
#| error: true
#| column: screen-inset
ft_pre

```


```{r}
#| column: screen-inset


treated_summary <- purrr::imap_dfr(datasets_h1b, function(df, id) {
   eff_added_obs <- sum(df$addedto_eff_sfha == TRUE, na.rm = TRUE)
  pre_added_obs <- sum(df$addedto_prelim_sfha == TRUE, na.rm = TRUE)
  
  tibble::tibble(
    dataset_id = id,
    n_obs = nrow(df),
    eff_treat_pins_N = dplyr::n_distinct(df$pin10[df$addedto_eff_sfha == TRUE & df$Triad == "North"]),
    pre_treat_pins_N = dplyr::n_distinct(df$pin10[df$addedto_prelim_sfha == TRUE& df$Triad == "North"]),
        eff_treat_pins_S = dplyr::n_distinct(df$pin10[df$addedto_eff_sfha == TRUE & df$Triad == "South"]),
    pre_treat_pins_S = dplyr::n_distinct(df$pin10[df$addedto_prelim_sfha == TRUE& df$Triad == "South"]),
     eff_treat_pins_chi = dplyr::n_distinct(df$pin10[df$addedto_eff_sfha == TRUE & df$Triad == "City"]),
    pre_treat_pins_chi = dplyr::n_distinct(df$pin10[df$addedto_prelim_sfha == TRUE& df$Triad == "City"]),
    pre_added_obs = pre_added_obs,
    eff_added_obs = eff_added_obs,
    eff_treated_pins = dplyr::n_distinct(df$pin10[df$addedto_eff_sfha == TRUE]),
    pre_treated_pins = dplyr::n_distinct(df$pin10[df$addedto_prelim_sfha == TRUE]),
    # eff_treated_pct = eff_added_obs / n_obs,
    # pre_treated_pct = pre_added_obs / n_obs
  )
})# |>
  # dplyr::mutate(
  #   eff_treated_pct = scales::percent(eff_treated_ pct, accuracy = 0.1),
  #   pre_treated_pct = scales::percent(pre_treated_pct, accuracy = 0.1)
  # )

treated_summary_ft <- treated_summary |>
  flextable::flextable() |>
  flextable::autofit()

treated_summary_ft

```


# FIRMs Updated Subsets

```{r}
if(data_version %in% c( "targets", "targets_hybrid", "targets_hybrid_2026sales", "targets_hybrid_polychange")){
  datasets_og$bldg_sfha = datasets_og$bldg_updated
  datasets_og$land_sfha = datasets_og$land_updated
}
```


### Building Polygon Datset

```{r}
#| error: true

## Without LOMRs
df_sub <- datasets_og$bldg_sfha |> filter(change_type_prelim != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000)  

valid_cohorts <- df_sub |>
  group_by(pre_date_chr) |>
  summarise(
    n = n(),
    n_treated = sum(removedfrom_prelim_sfha == TRUE, na.rm = TRUE),
    n_untreated = sum(removedfrom_prelim_sfha == FALSE, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(n_treated > 0, n_untreated > 0) |>
  pull(pre_date_chr)

df2 <- df_sub |>filter(pre_date_chr %in% valid_cohorts)

df2 |> feols(log(sale_price) ~ sw(removedfrom_prelim_sfha) | pin + sale_year,
    # subset = ~ pre_date_chr != "2005-01-01" & pre_date_chr != "2019-07-01",
      cluster = ~pin10,
      fsplit= ~pre_date_chr
) |> modelsummary(stars = TRUE)

# 
# ## Adds LOMR interaction
# df2 |> 
#   feols(log(sale_price) ~ sw(removedfrom_prelim_sfha*in_lomr) | pin + sale_year,
#      #subset = ~ pre_date_chr != "2005-01-01" & pre_date_chr != "2019-07-01",
#       cluster = ~pin10,
#       fsplit= ~pre_date_chr
# ) |> modelsummary(stars = TRUE)
# 

```
```{r}
bldg_1in500 <- readRDS("data/processed/targets/sales/df_prep_risk500_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014)) |>
  select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr,
         addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code,
         zip_code, event, change_type, change_type_prelim, Triad, clean_name,
         pin10, log_price, eff_date_chr, pre_date_chr, treat_year_add_eff,
         treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff,
         qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim,
         treated_group_eff:prelim_sfha_category)
```

# Individual Models

## Parts of Table 13: Buildings in 1-in-500 Flood Zones

```{r}
#| label: tbl-Table13-bldg-in-1in500-fz
#| tbl-cap: "Table 13: Effect on Price of Buildings Mapped Into or Out of a 1-in-500 year Flood Plain"


models_1in500_bldg <- list(

  
 "I" =  feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500
  ),

    "I Subset" = feols(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500 |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000),

  ),

  "II" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  ),


  "II Subset" =  feols(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500 |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000),

  ),
 
  # Symmetric effect of location in risk zone
    "III" = feols(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  ),
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  ),
 
 
 
   
 "I-Eff" =  feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500
  ),

    "I-Eff Subset" = feols(
    log(sale_price) ~ addedto_eff_sfha  | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500 |> filter(change_type != "Always SFHA" & treat_year_remove_eff == 10000),

  ),

  "II-Eff" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  ),


  "II-Eff Subset" =  feols(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500 |> filter(change_type != "Never SFHA" & treat_year_add_prelim == 10000),

  ),
 
  # Symmetric effect of location in risk zone
    "III-Eff" = feols(
    log(sale_price) ~ in_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  ),
  # Asymmetric: added vs removed in one equation
  "0" = feols(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,
    cluster = ~ pin10,
        data = bldg_1in500,

  )
 
)

models_1in500_bldg <- modelsummary::modelsummary(models_1in500_bldg,
               output = "flextable",
               fmt = function(x) round(x, 3),

             stars = TRUE)

models_1in500_bldg
```

### TWFE Regional Heterogeneity with Triad Slopes

```{r}
#| label: tbl-regionalheterogeneity
#| tbl-cap: "Regional Hetergeneity for SFHA Changes due to Preliminary FIRM Updates"
#| 
bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS") |>
  filter(!pin10 %in% drop_parcels |
           (pin10 == "0113301013" & sale_year > 2014)) |>
  select(pin, sale_date, sale_price, ins_req, in_eff_sfha, in_prelim_sfha, in_lomr,
         addedto_eff_sfha:removedfrom_prelim_sfha, condo, FIRM_PAN, nbhd_code,
         zip_code, event, change_type, change_type_prelim, Triad, clean_name,
         pin10, log_price, eff_date_chr, pre_date_chr, treat_year_add_eff,
         treat_year_add_prelim, treat_year_remove_prelim, treat_year_remove_eff,
         qtr, year, sale_year, sale_qtr_dec, group_name_eff, group_name_prelim,
         treated_group_eff:prelim_sfha_category)
models <- list(

  # Heterogeneity by Triad: added/removed interacted with Triad
  "I" = feols(
    log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
    data = bldg_sfha,
    cluster = ~pin10,
  ),

      # Heterogeneity by Triad: added interacted with Triad
 "I Subset" =  feols(
    log(sale_price) ~ addedto_prelim_sfha*Triad  | pin + sale_year,
    data = bldg_sfha |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000),
    cluster = ~pin10,
  ),
  # Heterogeneity by Triad: added/removed interacted with Triad
  "II" = feols(
    log(sale_price) ~ removedfrom_prelim_sfha*Triad | pin + sale_year,
    data = bldg_sfha,
    cluster = ~pin10,
  ),

    # Heterogeneity by Triad: added interacted with Triad
 "II Subset" =  feols(
    log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
    data = bldg_sfha |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000),
cluster = ~ pin10
  ),
    # Heterogeneity by Triad: added/removed interacted with Triad
  "III" = feols(
    log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
    data = bldg_sfha,
    cluster = ~pin10,
  )
  
)

all_models_formatted <- modelsummary::modelsummary(models,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted

```
