---
title: "Parallel Trends Graphs for Q2"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
---


| Variable          | Description                                     |
| ----------------- | ----------------------------------------------- |
| `log_price`       |  log price  (your main DV)                      |
| `high_ff_score x event` |  Main treatment interaction     |
|`event` | Pre or Post data release. It is NOT the treatment. Just the additional extra value in homes after 2020 above and beyond the sale year fixed effects. | 
|`high_ff_sore` | True or False. Represents persisting actual risk, even if it is not known. |
| `sale_year`       | Year of sale                    |
| `sale_quarter`    |  Quarter of sale                       |
| `change_type`     | SFHA transition category (e.g., Added, Removed, Always, Never) |
| `eff_date`        | Flood map effective date. Us to create in_eff_sfha or in_prelim_sfha    |
| `in_eff_sfha`     | Indicator for if property is in a FEMA SFHA at time of sale |
| `clean_name`      | Municipality                                    |
| `Triad`           | Subregional identifier (potential FE subgroup)  |



```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(tidyverse)
library(glue)
library(fixest)
library(skimr)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


df_prep <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS") |>
  select(-c(clean_name.x, clean_name.y))
source("R/helper_pins_to_drop.R")

df_prep <- df_prep |> filter(!pin10 %in% drop_parcels  |          
               (pin10 == "0113301013" & sale_year > 2014)
             )


df_prep <- df_prep |> 
  mutate(log_price = log(sale_price)) |> 
  filter(!is.na(Triad) & Triad != "NA") |>
filter(!is.na(high_ff_score))
    # mutate(in_eff_sfha = in_eff_sfha==1,
  #        in_prelim_sfha = in_prelim_sfha == 1)

table(df_prep$in_prelim_sfha)  # buildings in SFHA
```


```{r}

df_prep <- df_prep |>
  filter(change_type %in% c("Always SFHA", "Never SFHA") )
```


### A couple graphs for RQ1

::: panel-tabset

```{r accessible-plot}
make_sfha_lineplot <- function(
  df,
  y_var = c("sale_price", "log_price"),
  facet_var,                      
  group_var = "prelim_sfha_category",
  title = "Market Trends by SFHA Status",
  y_label = NULL,
  x_breaks = seq(2010, 2026, 4),
  x_limits = c(2009, 2027)
) {

  y_var <- match.arg(y_var)

  grp_vars <- c("sale_year", group_var, facet_var)

  df_summarised <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(grp_vars))) |>
    dplyr::summarise(
      avg_value = mean(.data[[y_var]], na.rm = TRUE),
      n = dplyr::n(),
      .groups = "drop"
    )

  if (is.null(y_label)) {
    y_label <- ifelse(
      y_var == "sale_price",
      "Average sale price",
      "Average logged sale price"
    )
  }

  ggplot2::ggplot(
    df_summarised,
    ggplot2::aes(
      x = sale_year,
      y = avg_value,
      group = .data[[group_var]],
      linetype = .data[[group_var]],
      shape = .data[[group_var]]
    )
  ) + 
    ggplot2::geom_smooth(alpha = .5, color = "darkgray", size = 1,
      method = "lm",
      se = FALSE    ) +
    ggplot2::geom_line(lwd = 1) +
    ggplot2::geom_point(size = 2,color = "black") +

    ggplot2::facet_wrap(stats::as.formula(paste("~", facet_var))) +
    ggplot2::labs(
      title = title,
      x = "Sale year",
      y = y_label,
      linetype = "Group",
      shape = "Group",
      caption = NULL
    ) +
    ggplot2::scale_x_continuous(
      breaks = x_breaks,
      limits = x_limits
    ) +
    ggplot2::scale_shape_manual(values = c(16, 17, 15, 1, 2, 0)) +
    #ggplot2::scale_linetype_manual(values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")) +
    ggplot2::theme_classic() +
    ggplot2::theme(
      legend.title = element_blank(),
      legend.position = "bottom"#,
    #  legend.title = ggplot2::element_text(face = "bold")
    )
}
```

### Dissertation figures

**Figure 6 and 7 in Q1**

```{r fig-figure6}
#| fig-height: 8
#| fig-width: 8

make_sfha_lineplot(
  df_prep |> filter(change_type_prelim %in% c("Always SFHA", "Never SFHA")),
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status - Include Chicago"
)
```


```{r fig-figure7}
#| fig-height: 8
#| fig-width: 8

make_sfha_lineplot(
  df_prep |>  filter(change_type_prelim %in% c("Always SFHA", "Never SFHA") & Triad != "City"),
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Trends by FIRM Date and SFHA Status - Exclude Chicago"
)


```


**Similar to Figure 6 and Figure 7 in Q1. Graphs in dissertation are by Cohort instead of Triad**

```{r}
#| fig-height: 6
#| fig-width: 8

make_sfha_lineplot(
  df_prep |> filter(change_type_prelim %in% c("Always SFHA", "Never SFHA")),
  y_var     = "log_price",
  facet_var = "Triad",
  title     = "Trends by Triad and SFHA Status"
)

```

**Appendix A Figure 13**

```{r fig-rq1-appendix-fig13}
#| fig-height: 8
#| fig-width: 8

make_sfha_lineplot(
  df_prep |># filter(#!(pre_date == "2019-07-01" &  sale_price < 1500000),
    filter(!pin10 %in% c("0122400028", "0516106013")),
  y_var     = "sale_price",
  facet_var = "pre_date",
  title     = "Price Trends by Cohort and SFHA Status"
)
```

**Appendix A Figure 14**

```{r fig-rq1-figure14}
#| fig-height: 8
#| fig-width: 8

make_sfha_lineplot(
  df_prep |># filter(#!(pre_date == "2019-07-01" &  sale_price < 1500000),
    filter(!pin10 %in% c("0122400028", "0516106013")),
  y_var     = "log_price",
  facet_var = "pre_date",
  title     = "Price Trends by Cohort and SFHA Status"
)
```
### Prelim Graphs 

```{r}

df_prep |> 
  group_by(sale_year, in_prelim_sfha, Triad) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = avg_price, lty = in_prelim_sfha, shape = in_prelim_sfha)) +
    geom_smooth(method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) +
  geom_point() +
  geom_line(color = "black") +
    ggplot2::scale_shape_manual(values = c(16, 17, 15, 1, 2, 0)) +
    ggplot2::scale_linetype_manual(values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")) +
  facet_wrap(~Triad) +
  labs(title = "Pre- and Post-Event Slopes by Triad and SFHA Status",
       caption = "",
       lty= "In SFHA",
       shape = "In SFHA",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010, 2026, 4), limits = c(2009, 2027) ) +
  theme_classic()+
  theme(legend.position = "bottom" )


df_prep |> 
  group_by(sale_year, in_prelim_sfha, pre_date) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = avg_price, lty = in_prelim_sfha, shape = in_prelim_sfha)) +
  
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) +
  ggplot2::scale_shape_manual(values = c(16, 17, 15, 1, 2, 0)) +
  ggplot2::scale_linetype_manual(values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=2020, lty = 2) +

  facet_wrap(~pre_date) +
  labs(title = "Pre- and Post-Event Slopes by Triad and SFHA Status",
       caption = "",
       lty = "In SFHA",
       shape = "In SFHA",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010, 2026, 4), limits = c(2009, 2027) ) +
  theme_classic()+
  theme(legend.position = "bottom") 

```

### Coastal Property Sensitivity 


```{r}
#| fig-height: 10

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  mutate(period = if_else(sale_date < new_info_released, "1.Pre", "2.Post")) |> 
  group_by(period, sale_year, in_eff_sfha, high_ff_score, Triad ) |> 
  summarise(median_price = median(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = median_price, shape = high_ff_score) ) +

    geom_vline(xintercept=2020) +
  facet_wrap(vars(Triad, in_eff_sfha), ncol = 2) +

  geom_smooth(aes(linetype = period), method = "lm", se = FALSE, color = "darkgray", alpha = .5) +
     geom_line() +

     geom_point(size = 2) +

  labs(title = "Pre vs Post Slopes by Triad and FEMA SFHA Status",
       shape = "FF Score > 4",
       lty = "Info Released",
       x = NULL, y = "Median Logged Price"       ) +
    #  scale_y_continuous(limits = c(11, 14)) +

  scale_x_continuous(breaks = c(2010,2020, 2024), limits = c(2015, 2025))+
    theme_classic()+

  theme(legend.position = "bottom") 

```


```{r}
#| fig-height: 10

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  mutate(period = if_else(sale_date < new_info_released, "1.Pre", "2.Post")) |> 
  group_by(period, sale_year, in_eff_sfha, high_ff_score, Triad ) |> 
  summarise(median_price = median(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = median_price, shape = high_ff_score) ) +

    geom_vline(xintercept=2020) +
  facet_wrap(vars(Triad, in_eff_sfha), ncol = 2) +

  geom_smooth(aes(linetype = period), method = "lm", se = FALSE, color = "darkgray", alpha = .5) +
     geom_line() +

     geom_point(size = 2) +

  labs(title = "Pre vs Post Slopes by Triad and FEMA SFHA Status",
       subtitle =  "Excludes Coastal properties",
       shape = "FF Score > 4",
       lty = "Info Released",
       x = NULL, y = "Median Logged Price"       ) +
    #  scale_y_continuous(limits = c(11, 14)) +

  scale_x_continuous(breaks = c(2010,2020, 2024), limits = c(2015, 2025))+
    theme_classic()+

  theme(legend.position = "bottom") 

```

```{r}
#| include: false 

df_prep |> filter(high_ff_score == TRUE & in_eff_sfha == "Not SFHA" & Triad == "North" & sale_year == 2022) |> mutate(pin10 = str_sub(pin,1,10)) |> group_by(pin10) |> mutate(n = n()) |> arrange(desc(n), pin) |>
  select(pin10, pin, clean_name, n, sale_price, flood_factor_score, times_sold, in_eff_sfha)
```

:::


## Parallel Trends Assumptions


::: panel-tabset

### Not Logged Sales Price by FF

```{r}
#| column: page
#| message: false
#| layout-ncol: 2

df_prep |> 
  group_by(sale_year, high_ff_score, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = high_ff_score, lty = event)) +
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  scale_y_continuous(labels = scales::dollar) +
    scale_x_continuous(limits = c(2009,2026)) + 

  geom_vline(xintercept=2020, lty = 2) +
  theme_classic() + 
      theme(legend.position =  "bottom")+

  #    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  labs(title = "Pre- and Post- Event Treatment Trends",
       y = "Avg. Sale Price",
         shape = "FF > 4",
       lty = "Event",
       x = NULL)

df_prep |> 
  group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = high_ff_score, lty = event)) +
 geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  scale_y_continuous(labels = scales::dollar) + 
      scale_x_continuous(limits = c(2009,2026)) + 

  geom_vline(xintercept=2020, lty = 2) +
  theme_classic()+
    theme(legend.position =  "bottom")+

  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Sale Price",
         shape = "FF > 4",
       lty = "Event",
       x = NULL) +
  facet_wrap(~Triad)

```

### Transformations of Sale Price by FF Score

**Appendix B Figure 18**

```{r}
#| column: page
#| message: false
#| layout-ncol: 2


df_prep |> 
    group_by(sale_year, high_ff_score, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, shape = high_ff_score)) +
  geom_line() +
  theme_classic() + 
geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  theme_classic()+ 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Logged Sale Price",
         shape = "FF > 4",
       lty = "Event",
       x = NULL)

df_prep |> 
  group_by(sale_year, high_ff_score, event, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, shape = high_ff_score)) +
geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  theme_classic()+ 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Logged Sale Price",
         shape = "FF > 4",
       lty = "Event",
       x = NULL) +
  facet_wrap(~Triad)
```


**Appendix B Figure 19**

```{r}
#| column: page
#| layout-ncol: 2

df_prep |> 
  group_by(sale_year, high_ff_score, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, shape = high_ff_score)) +
  theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", alpha= 0.5, lwd = 1) + 
  geom_line() +
  geom_point(size = 2) + 
  geom_vline(xintercept=2020, lty = 2) +
    scale_y_continuous(labels = scales::dollar) + 

  scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 
  
  labs(title = "Pre- and Post-Event Trends",
       y = "1/Sale Price",
       shape = "FF > 4",
       lty = "Event",
       x = NULL) 

df_prep |> 
  group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, shape = high_ff_score)) +
  theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", alpha= 0.5, lwd = 1) + 
  geom_line() +
  geom_point(size = 2) + 
  
  scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 
    scale_y_continuous(labels = scales::dollar) + 

  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
              shape = "FF > 4",
       lty = "Event",
       caption = "Inverse Price = 1 / sale_price") +
  facet_wrap(~Triad)

```


### Not Logged Sales Price by SFHA

**Appendix B Figure 17**

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  group_by(sale_year, in_eff_sfha, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = in_eff_sfha, lty = event)) +
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point() + 
  
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  theme_classic() + 
  #    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  labs(title = "Pre- and Post- Event Treatment Trends",
       y = "Avg. Sale Price",
       shape = "In SFHA",
       lty = "Event",
       x = NULL)


df_prep |> 
  group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = in_eff_sfha, lty = event)) +
  theme_classic() + 
  geom_smooth(method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) +  geom_line() +
  
  geom_point(size = 2) + 
  
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Sale Price",
         shape = "In SFHA",
       lty = "Event",
       x = NULL) +
  facet_wrap(~Triad)

```

With fewer years pre-trend:

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  filter(sale_year > 2013) |>
  group_by(sale_year, in_eff_sfha, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = in_eff_sfha, lty = event)) +
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  theme_classic() + 
  #    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  labs(title = "Pre- and Post- Event Treatment Trends",
       y = "Avg. Sale Price",
         shape = "In SFHA",
       lty = "Event",
       x = NULL)


df_prep |> 
    filter(sale_year > 2013) |>
  group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, shape = in_eff_sfha, lty = event)) +
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_line() +
  geom_point(size = 2) + 
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  theme_classic() + 
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Sale Price",
         shape = "In SFHA",
       lty = "Event",
       x = NULL) +
  facet_wrap(~Triad)

```


### Transformations of Sale Price by SFHA Status

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, shape = in_eff_sfha)) +
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
    geom_line() +

  geom_point(size = 2) + 
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by SFHA Status",
       y = "Avg. Logged Sale Price",
                shape = "In SFHA",
       lty = "Event",
       x = NULL) 



df_prep |> 
    group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, shape = in_eff_sfha)) +
  geom_line() +
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
  geom_point(size = 2) +
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by Triad & SFHA Status",
       y = "Avg. Logged Sale Price",
              shape = "In SFHA",
       lty = "Event",
       x = NULL) + 
       facet_wrap(~Triad)



df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, shape = in_eff_sfha)) +
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
    geom_line() +
  scale_y_continuous(labels = scales::dollar) + 

  geom_point(size = 2) +
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by SFHA Status",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
             shape = "In SFHA",
       lty = "Event",
       caption = "Inverse Price = 1 / sale_price")


df_prep |> 
    group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, shape = in_eff_sfha)) +
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", lwd = 1, alpha = .5) + 
    geom_line() +

  geom_point(size = 2) +
  scale_y_continuous(labels = scales::dollar) + 

  scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad and SFHA Status",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
             shape = "In SFHA",
       lty = "Event",
       caption = "Inverse Price = 1 / sale_price") + 
  facet_wrap(~Triad)


```

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(asinh_price = mean(asinh(sale_price)),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, shape = in_eff_sfha)) +
    geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", alpha = .5, size = 1) + 
  geom_line() +
   theme_classic() + 
  geom_point(size = 2) +
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. asinh(Sale Price)",
                  shape = "In SFHA",
       lty = "Event",
       x = NULL)




df_prep |> 
  group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(asinh_price = mean(asinh(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, shape = in_eff_sfha)) +
    geom_smooth(aes(lty = event), method = "lm", se = FALSE, color = "darkgray", alpha = .5, size = 1) + 
  geom_line() +
   theme_classic() + 
  geom_point(size = 2) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. asinh(Sale Price)",
             shape = "In SFHA",
       lty = "Event",
       x = NULL) + 
  facet_wrap(~Triad)



```


:::


### Q2 Testing slopes with Flood Factor Score

**Models vary by transformation of the DV**

```{r}
#| layout-ncol: 1
#| label: tbl-notloggedDV

slopes1 <- lm(sale_price ~ high_ff_score*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes1,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


slopes2 <- lm(log(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)
# 
# modelsummary::modelsummary(
#   slopes2,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)

slopes3 <- lm(asinh(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes3,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


modelsummary::modelsummary(
  list(slopes1, slopes2, slopes3),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)



```

**sale_year:in_eff_sfha**\
If not statistically significant, then I fail to reject the null hypothesis --> there is no evidence of different pre-treatment trends between properties that were in and out of SFHAs.

**sale_year:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.


```{r}
#| layout-ncol: 1
#| label: tbl-transformedDV-forsfha
#| tbl-cap: "Sales Price, Logged Sales Price, and asymptotic sine of sale price as the DV."

slopes1 <- lm(sale_price ~ in_eff_sfha*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes1,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


slopes2 <- lm(log(sale_price) ~ in_eff_sfha*event*sale_year, data = df_prep)
# 
# modelsummary::modelsummary(
#   slopes2,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)

slopes3 <- lm(asinh(sale_price) ~ in_eff_sfha*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes3,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


modelsummary::modelsummary(
  list(slopes1, slopes2, slopes3),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)



```


:::

## Other random stuff


```{r}
missing_ff_score <- df_prep |> filter(is.na(high_ff_score) | is.na(in_eff_sfha))

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)


df_prep <- df_prep |> 
  filter(!is.na(high_ff_score))
```


```{r}

df_prep |> 
    filter(sale_year > 2015) |>     # just to have roughly the same number of years on both sides of the event
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )

df_prep |> 
  filter(sale_year > 2015) |>
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )


```



<!---Properties with high flood score but no SFHA
- "02014000171053" = "1354 whispering springs Palatine IL" Parcel is a "condo" but a bunch of detached homes around a pond. Flood score is 7. Has a parcel inside of it (1733 EMERALD BAY 5, PALATINE, IL 60074) with a FF=6 that IS in a FEMA flood zone. Not sure if there was a specific pin division for this reason) ---> 


```{r}
#| eval: false


df_prep |> 
  filter(high_ff_score == FALSE & in_eff_sfha == "SFHA") |> 
  mutate(parcel = str_sub(pin, 1, 10)) |> 
  distinct(parcel, in_eff_sfha, high_ff_score)


```



SOLVED "01014050100000" = "804 division st, barrington IL"  
SOLVED "01021000330000"  = "7 Marmon LN Barringonton IL"  
"0102300012" = "221 Oakdene Drive Barrington" # only land barely touches SFHA  

"02013020771280" = "2 Dundee Quarter 302 Palatine IL" # considered condo but its all detached homes or townhomes. AND IN A LOMR

"0216410003" = "25 North Clyde Avenue, Palatine, IL, 60067, USA" # actually has a flood factor of 5

"1505117011" = "100 S Roberta AVe Northlake" # parcel boundary touches SFHA but not house

"1504117057" = "1642 N 39th Ave Stone Park" # score of 6, is in SFHA

"1505205013" = "1652 43RD AVE, STONE PARK, IL 60165" # has a flood score of 7! and is in SFHA

