---
title: "Parallel Trends Graphs for Q2"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
    error: true
---

| Variable | Description |
| --- | --- |
| `log_price` | log price, your main DV |
| `high_ff_score x event` | Main treatment interaction |
| `event` | Pre or Post data release. It is NOT the treatment. Just the additional extra value in homes after 2020 above and beyond the sale year fixed effects. |
| `high_ff_score` | TRUE or FALSE. Represents persistent actual risk, even if it is not known. |
| `sale_year` | Year of sale |
| `sale_quarter` | Quarter of sale |
| `change_type` | SFHA transition category, such as Added, Removed, Always, or Never |
| `eff_date` | Flood map effective date. Used to create `in_eff_sfha` or `in_prelim_sfha`. |
| `in_eff_sfha` | Indicator for whether property is in a FEMA SFHA at time of sale |
| `clean_name` | Municipality |
| `Triad` | Subregional identifier / potential FE subgroup |

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(fixest)
library(skimr)
library(modelsummary)
library(flextable)
library(DT)
library(scales)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

data_path <- "outputs/q2_models/bldg_sfha_q2_prepped.RDS"
df_prep <- readRDS(data_path)


object_dir <- "outputs/q2_assumption_tests"
required_objects <- file.path(
  object_dir,
  c(
    "q2_assumption_plots.rds",
    "q2_assumption_models.rds",
    "q2_assumption_tables.rds"
  )
)

if (!all(file.exists(required_objects))) {
  missing_objects <- required_objects[!file.exists(required_objects)]
  stop(
    "Missing precomputed Q2 assumption-test objects. Run this from the project root first:\n",
    "source('scripts/q2_assumption_tests/run_all_q2_assumption_tests.R')\n\n",
    "Missing file(s):\n",
    paste(missing_objects, collapse = "\n")
  )
}

q2_plots <- readRDS(file.path(object_dir, "q2_assumption_plots.rds"))
q2_models <- readRDS(file.path(object_dir, "q2_assumption_models.rds"))
q2_tables <- readRDS(file.path(object_dir, "q2_assumption_tables.rds"))
```

```{r quick-checks}
table(df_prep$in_prelim_sfha)
```

### A couple graphs for RQ1

::: panel-tabset

### Dissertation figures

**Figure 6 and 7 in Q1**

```{r fig-figure6}
#| fig-height: 8
#| fig-width: 8
q2_plots$figure6_prelim_cohort_include_chicago
```

```{r fig-figure7}
#| fig-height: 8
#| fig-width: 8
q2_plots$figure7_prelim_cohort_exclude_chicago
```

**Similar to Figure 6 and Figure 7 in Q1. Graphs in dissertation are by Cohort instead of Triad**

```{r fig-rq1-triad-sfha-status}
#| fig-height: 6
#| fig-width: 8
q2_plots$sfha_trends_by_triad
```

**Appendix A Figure 13**

```{r fig-rq1-appendix-fig13}
#| fig-height: 8
#| fig-width: 8
q2_plots$appendix_fig13_price_by_cohort
```

**Appendix A Figure 14**

```{r fig-rq1-figure14}
#| fig-height: 8
#| fig-width: 8
q2_plots$appendix_fig14_log_by_cohort
```

### Prelim Graphs

```{r fig-prelim-by-triad}
q2_plots$prelim_by_triad
```

```{r fig-prelim-by-pre-date}
q2_plots$prelim_by_pre_date
```

### Coastal Property Sensitivity

```{r fig-coastal-sensitivity}
#| fig-height: 10
q2_plots$coastal_sensitivity
```

```{r fig-coastal-sensitivity-excludes-coastal}
#| fig-height: 10
q2_plots$coastal_sensitivity_excludes_coastal_label_only
```

```{r coastal-sensitive-record-check, include=FALSE}
df_prep |>
  filter(high_ff_score == TRUE, in_eff_sfha == "Not SFHA", Triad == "North", sale_year == 2022) |>
  mutate(pin10 = str_sub(pin, 1, 10)) |>
  group_by(pin10) |>
  mutate(n = n()) |>
  arrange(desc(n), pin) |>
  select(pin10, pin, clean_name, n, sale_price, flood_factor_score, times_sold, in_eff_sfha)
```

:::

## Parallel Trends Assumptions

::: panel-tabset

### Not Logged Sales Price by FF

```{r fig-ff-sale-price}
#| column: page
#| message: false
#| layout-ncol: 2
q2_plots$ff_sale_price_overall
q2_plots$ff_sale_price_triad
```

### Transformations of Sale Price by FF Score

**Appendix B Figure 18**

```{r fig-ff-log-price}
#| column: page
#| message: false
#| layout-ncol: 2
q2_plots$ff_log_overall
q2_plots$ff_log_triad
```

**Appendix B Figure 19**

```{r fig-ff-inverse-price}
#| column: page
#| layout-ncol: 2
q2_plots$ff_inverse_overall
q2_plots$ff_inverse_triad
```

### Not Logged Sales Price by SFHA

**Appendix B Figure 17**

```{r fig-sfha-sale-price}
#| column: page
#| layout-ncol: 2
#| message: false
q2_plots$sfha_sale_price_overall
q2_plots$sfha_sale_price_triad
```

With fewer years pre-trend:

```{r fig-sfha-sale-price-since-2014}
#| column: page
#| layout-ncol: 2
#| message: false
q2_plots$sfha_sale_price_since_2014_overall
q2_plots$sfha_sale_price_since_2014_triad
```

### Transformations of Sale Price by SFHA Status

```{r fig-sfha-log-and-inverse}
#| column: page
#| layout-ncol: 2
#| message: false
q2_plots$sfha_log_overall
q2_plots$sfha_log_triad
q2_plots$sfha_inverse_overall
q2_plots$sfha_inverse_triad
```

```{r fig-sfha-asinh}
#| column: page
#| layout-ncol: 2
#| message: false
q2_plots$sfha_asinh_overall
q2_plots$sfha_asinh_triad
```

:::

### Q2 Testing slopes with Flood Factor Score

**Models vary by transformation of the DV**

```{r tbl-notloggedDV}
#| layout-ncol: 1
modelsummary(
  q2_models$ff_transformations,
  output = "flextable",
  fmt = function(x) round(x, 2),
  stars = TRUE
)
```

**`sale_year:in_eff_sfha`**  
If not statistically significant, then I fail to reject the null hypothesis: there is no evidence of different pre-treatment trends between properties that were in and out of SFHAs.

**`sale_year:event:in_eff_sfha`**  
If significant, it means the difference in slope between groups changed after the event. That does not support parallel trends assumptions for difference-in-differences models.

```{r tbl-transformedDV-forsfha}
#| layout-ncol: 1
#| tbl-cap: "Sales Price, Logged Sales Price, and asymptotic sine of sale price as the DV."
modelsummary(
  q2_models$sfha_transformations,
  output = "flextable",
  fmt = function(x) round(x, 2),
  stars = TRUE
)
```

## Other random stuff

```{r summary-tables-by-year}
DT::datatable(q2_tables$ff_sfha_log_by_year, rownames = FALSE)
DT::datatable(q2_tables$ff_sfha_price_by_year, rownames = FALSE)
```

```{r summary-tables-since-2016}
q2_tables$ff_sfha_log_since_2016
q2_tables$ff_sfha_price_since_2016
```

<!---
Properties with high flood score but no SFHA
- "02014000171053" = "1354 whispering springs Palatine IL" Parcel is a "condo" but a bunch of detached homes around a pond. Flood score is 7. Has a parcel inside of it (1733 EMERALD BAY 5, PALATINE, IL 60074) with a FF=6 that IS in a FEMA flood zone. Not sure if there was a specific pin division for this reason)
--->

```{r high-ff-no-sfha-check, eval=FALSE}
df_prep |>
  filter(high_ff_score == FALSE, in_eff_sfha == "SFHA") |>
  mutate(parcel = str_sub(pin, 1, 10)) |>
  distinct(parcel, in_eff_sfha, high_ff_score)
```

SOLVED "01014050100000" = "804 division st, barrington IL"  
SOLVED "01021000330000" = "7 Marmon LN Barringonton IL"  
"0102300012" = "221 Oakdene Drive Barrington" # only land barely touches SFHA  

"02013020771280" = "2 Dundee Quarter 302 Palatine IL" # considered condo but its all detached homes or townhomes. AND IN A LOMR

"0216410003" = "25 North Clyde Avenue, Palatine, IL, 60067, USA" # actually has a flood factor of 5

"1505117011" = "100 S Roberta AVe Northlake" # parcel boundary touches SFHA but not house

"1504117057" = "1642 N 39th Ave Stone Park" # score of 6, is in SFHA

"1505205013" = "1652 43RD AVE, STONE PARK, IL 60165" # has a flood score of 7! and is in SFHA
