---
title: "Main marginal comparisons models"
format: 
  html:
    df-print: paged
---


```{r setup}
library(tidyverse)
library(fixest)
library(did)  
library(etwfe)
library(tidyverse)
library(modelsummary)
library(gt)
library(marginaleffects)

options(scipen = 999)

# bldg_sfha <- readRDS("data/processed/variants/df_prep__bldg_sfha.RDS")
# 
# parcels <- readRDS("data/processed/variants/df_prep__parcel_sfha.RDS")
# 
# bldg_1in500 <- readRDS("data/processed/variants/df_prep__bldg_1in500.RDS")

source("R/helper_pins_to_drop.R")
```


```{r}

lake100ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within100ft_ExportTable_TableToExcel.xlsx")
lake500ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within500ft_ExportTable_TableToExcel.xlsx")

bldg_sfha <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS")

bldg_sfha <- bldg_sfha |> filter(!pin10 %in% drop_parcels  |
               (pin10 == "0113301013" & sale_year > 2014)
             )

bldg_sfha <- bldg_sfha |> filter(change_type != "Changes SFHA")
```

`Event == TRUE` for all sales that occurred after First Street released its flood risk data.

`high_ff_score == TRUE` for properties that had a flood factor score of 5 or higher

```{r}

bldg_sfha <- bldg_sfha |> 
  mutate(event = sale_date > new_info_released)

bldg_sfha <- bldg_sfha |> 
  mutate(
    highff_post = (high_ff_score == TRUE &  sale_date > new_info_released ),
    Triad = as.character(Triad),
    triad_coast = ifelse(pin10 %in% lake100ft$PIN10, "Coastal", Triad)
                                 )

bldg_sfha <- bldg_sfha |> 
  group_by(pin) |>
  mutate(pin_num = as.numeric(pin),
    # ff_group = ifelse(high_ff_score==TRUE & sale_date > new_info_released, as.character(min(sale_year[sale_date > new_info_released])), "0")) |>
      ff_group = ifelse(high_ff_score==TRUE & sale_date > new_info_released, "2020", "0")) |>

  ungroup()

#table(bldg_sfha$triad_coast)
#table(bldg_sfha$Triad)
```

# Separated timing and underlying risk

```{r}
base_mod = feols(log_price ~ high_ff_score * event  | pin + sale_year, vcov = ~pin10, data = bldg_sfha)

modelsummary(base_mod, stars = TRUE)

```

# With highff_post (4-way interaction) 


```{r}
## change type is for effective maps
# triad_mod_notriads_4way = feols(log(sale_price) ~ change_type * high_ff_score * event  | pin + sale_year, vcov = ~pin10, data= bldg_sfha)

## change type is for effective maps

simp4way_notriad = feols(log(sale_price) ~ high_ff_score * event | pin + sale_year, vcov = ~pin10, data = bldg_sfha)


simp4way = feols(log(sale_price) ~ high_ff_score * event * Triad | pin + sale_year, vcov = ~pin10, data = bldg_sfha)


## change type is for effective maps
triad_mod_4way = feols(log(sale_price) ~ change_type * high_ff_score * event * Triad | pin + sale_year, vcov = ~ pin10, data = bldg_sfha)

triad_mod_4way_notria = feols(log(sale_price) ~ change_type * high_ff_score * event | pin + sale_year, vcov = ~pin10, data = bldg_sfha)

coef_map <- c(
  "eventTRUE" = "Post-release",
  "high_ff_scoreTRUE:eventTRUE" = "High Flood Factor × Post-release",
  "change_typeAlways SFHA:eventTRUE" = "Always SFHA × Post-release",
  "change_typeChanges SFHA:eventTRUE" = "Changed SFHA × Post-release",
  "change_typeAlways SFHA:high_ff_scoreTRUE:eventTRUE" = "Always SFHA × High Flood Factor × Post-release",
  "change_typeChanges SFHA:high_ff_scoreTRUE:eventTRUE" = "Changed SFHA × High Flood Factor × Post-release"
)

# modelsummary(
#   triad_mod_3way,
#   coef_map = coef_map,
#   coef_omit = "Triad|change_typeChanges SFHA$|high_ff_scoreTRUE|high_ff_scoreTRUE × TriadSouth|AIC|BIC|RMSE",
#   statistic = "({std.error})",
#   stars = TRUE,
#   gof_omit = "IC|Log|Adj|Within",
#   output = "gt"
# )

modelsummary(list(simp4way_notriad, simp4way, triad_mod_4way, triad_mod_4way_notria), stars = TRUE)

```

```{r}
ex1 <- avg_comparisons(triad_mod_4way_notria, 
               variables = "event", 
                by = c("change_type", "high_ff_score" ))
ex1
```

Effect of just `event`. On average, properties sold for around 4% more after 2020.

```{r}
ex2 <- avg_comparisons(triad_mod_4way, 
                variables = list(event = "pairwise"), 
            comparison = "difference")
ex2
```

The effect of the treatment might be stronger or weaker at different levels of the other treatment variable. 

On average, properties with low flood factor scores sold for 5.5% more than before the event, while properties with high flood factor score sold for 4.6% less than they did before the event. 

A difference of 10%. 

```{r}
#| tbl-cap: "The estimated effect of a change from a having a **visible** flood factor score score in the subset of observations with a FF score < 5 and for the subset of properties with a FF score of 5+."

avg_comparisons(triad_mod_4way, 
                variables = "event", 
                by = c("high_ff_score"))

```

```{r}
#| tbl-cap: "`Hypothesis` argument lets us check if estimates are different enough to matter (i.e. statistically significantly different). If p < 0.05(or whatever cut off you want to use), then I can reject the null hypothesis that the effect of visible flood risk information is the same for high and low risk properties."

avg_comparisons(triad_mod_4way, 
                variables = "event", 
                by = c("high_ff_score"),
                hypothesis = "b2 - b1 = 0")

```

> High-risk and low-risk properties are statistically significantly different from each other (p < 0.01). Therefore the effect of visible flood risk information was not the same for these subgroups. 

```{r}
#Now, we ask if M2 changes the way in which M1 moderates the effect of X on Y. The difference is subtle but important: we are asking if the moderation effect of M1 is itself moderated by M2.

results <- avg_comparisons(triad_mod_4way, 
                variables = "event", 
                by = c("change_type", "high_ff_score" ))
results
```

```{r}
preds <- predictions(triad_mod_4way, variables = "event",
            newdata = datagrid(
              high_ff_score = c(TRUE, FALSE), 
              change_type =c("Always SFHA", "Never SFHA"), 
              Triad = c("North", "South", "City")), vcov = FALSE)
preds
```

```{r}
avg_comparisons(triad_mod_4way, 
                variables = "event", 
                by = c("change_type", "high_ff_score" ), hypothesis = "b2- b1 = 0")

avg_comparisons(triad_mod_4way, 
                variables = "event", 
                by = c("change_type", "high_ff_score" ), hypothesis = "b4 - b3 = 0")
```

To answer the question of whether M2 moderates the moderation effect of M1, we can specify the hypothesis as a difference in differences:

```{r}
avg_comparisons(triad_mod_4way, 
    hypothesis = "(b2 - b1) - (b4 - b3) = 0",
    variables = "event", 
    by = c("change_type", "high_ff_score"))
```

 > SFHA status moderates the moderation effect of a having a high flood score on the information's effect on sale prices (p <0.05).
 
```{r}
#| label: fig-avgpredictions-moderator-simpler
#| fig-cap: "Average predicted outcomes for different combinations of X, M1, and  Not broken down by Triad or SFHA status."


plot_predictions(triad_mod_4way, by = c("event", "high_ff_score"), vcov = FALSE) +
  geom_line(aes(x=event, y = estimate, group = high_ff_score)) + labs( x = "Info Released", y = "Estimated log(price)") + theme_bw() + theme(legend.position = "bottom")
```


```{r}
#| label: fig-avgpredictions-moderator
#| fig-cap: "Average predicted outcomes for different combinations of X, M1, and  Not broken down by Triad."


plot_predictions(triad_mod_4way, by = c( "event", "high_ff_score", "change_type"  ), vcov = FALSE) + labs( x = "Info Released", y = "Estimated log(price)") + geom_line(aes(x=event, y = estimate, group = high_ff_score)) + labs( x = "Info Released", y = "Estimated log(price)") + theme_bw() + theme(legend.position = "bottom")

```

```{r}
#| label: fig-avgpredictions-moderator-effectivedates-4way
#| fig-cap: "eff_pred_graph <- plot_predictions(triad_mod_4way, by = event, high_ff_score, change_type, Triad"


eff_pred_graph <- plot_predictions(triad_mod_4way, by = c( "event", "high_ff_score", "change_type", "Triad"  ), vcov = FALSE) + geom_line(aes(x=event, y = estimate, group = high_ff_score)) + labs( x = "Info Released", y = "Estimated log(price)")

eff_pred_graph + theme_bw() + theme(legend.position = "bottom")
```

```{r}
comps <- comparisons(triad_mod_4way, variables = "event",
            newdata = datagrid(
              high_ff_score = c(TRUE, FALSE), 
              change_type =c("Always SFHA", "Never SFHA"), 
              Triad = c("North", "South", "City")), vcov = FALSE)
comps
```

```{r}

df <- as.data.frame(results)

ff_diff_by_sfha <- df |>
  group_by(change_type) |>
  summarize(
    diff = estimate[high_ff_score == TRUE] -
           estimate[high_ff_score == FALSE]
  )

ff_diff_by_sfha

ff_diff_by_sfha |>
  summarize(
    moderation = diff[change_type == "Always SFHA"] -
                 diff[change_type == "Never SFHA"]
  )
```


> Price divergence between high- and low-risk properties is larger within SFHA areas


```{r}
table_df <- as.data.frame(results) |>
  select(change_type, high_ff_score, estimate) |>
  mutate(
    ff_group = ifelse(high_ff_score, "High FF", "Low FF")
  ) |>
  select(-high_ff_score) |>
  pivot_wider(
    names_from = ff_group,
    values_from = estimate
  ) |>
  mutate(
    `Difference (High - Low)` = `High FF` - `Low FF`
  )

table_df |>
  mutate(
    across(c(`Low FF`, `High FF`, `Difference (High - Low)`),
           ~ round(.x, 3))
  )
```

"Entries report average changes in log sale prices from the pre- to post-information period, estimated separately by Flood Factor risk group and FEMA flood zone status. The final column reports the difference between high- and low-risk properties within each SFHA category."


# prelim model check



```{r}
#| label: fig-avgpredictions-moderator-preliminarydates
#| fig-cap: "**Preliminary Dates** Average predicted outcomes for different combinations of X, M1 and M2 (and Triad)."

prelim_mod_4way = feols(log_price ~ change_type_prelim * high_ff_score * event * Triad | pin + sale_year, vcov = ~pin10, data= bldg_sfha)


prelim_pred_graph <- plot_predictions(prelim_mod_4way, by = c( "event", "high_ff_score", "change_type_prelim", "Triad"  ), vcov = FALSE)  + geom_line(aes(x=event, y = estimate, group = high_ff_score)) + labs( x = "Info Released", y = "Estimated log(price)")

prelim_pred_graph + theme_bw()
```

# (Wrong but simpler way) With highff_post (3-way interaction) 


`highff_post == TRUE` if property had a high flood factor score and if the sale occurred after the data was available (i.e. if event==T and high_ff_score == T, then highff_post == T)



**Is the effect of having a high flood score moderated by SFHA status?**

`avg_comparisons(triad_mod, variables = "highff_post", by = "change_type")`

The expected change in Y (logged sale price) associated with a change in X (one SFHA status to another) differs based on the value of `change_type`

Never SFHA(-0.574) vs (-0.0450)

Are these statistically significantly different from each other?

**Table in Dissertation:**

```{r}
simp_mod <- feols(log_price ~ highff_post | pin + sale_year, data = bldg_sfha, vcov = ~ pin10)

mod_3way <- feols(log_price ~ change_type * highff_post | pin + sale_year, data = bldg_sfha, vcov = ~ pin10)

modelsummary(list(simp_mod, mod_3way), stars = TRUE)
```

```{r}
#| error: true

triad_mod <- feols(log_price ~ change_type * highff_post * Triad | pin + sale_year, data = bldg_sfha, vcov = ~ pin10)

modelsummary(triad_mod, stars = TRUE)

post_by_changetype <- avg_comparisons(triad_mod, variables = "highff_post", by = "change_type")
post_by_changetype
```

Are the coefficients for Always SFHA and Never SFHA statistically different from each other? 

```{r}
#| error: true

avg_comparisons(triad_mod, variables = "highff_post", by = "change_type", hypothesis = "b1=b2")

```

Always SFHA not statistically significant from Never SFHA

