---
title: "Q2 Simplermodel Assumptions and Diagnostics"
format:
  html:
    theme: darkly
toc: true
toc-depth: 3
number-sections: true
code-fold: show
code-tools: true
smooth-scroll: true
df-print: paged
fig-cap-location: top
anchor-sections: true
link-external-icon: true
link-external-newwindow: true
execute:
  warning: false
  message: false
 # cache: true
#freeze: auto
---

```{r}
#| label: setup
knitr::opts_chunk$set(fig.align = "center", fig.width = 8, fig.height = 5, dpi = 150)

suppressPackageStartupMessages({
  library(tidyverse)
  library(fixest)
  library(modelsummary)
  library(gt)
  library(broom)
  library(scales)
  library(lubridate)
})

theme_set(theme_minimal(base_size = 12))
update_geom_defaults("line",  list(lineend = "round", linewidth = 0.8))
update_geom_defaults("point", list(alpha = 0.65, size = 1.7))
```

# Data and canonical variables

```{r}
# Read in processed data (user’s edit retained)
#df_prep <- readr::read_rds("data/processed/df_prep.rds")

source("R/helper_pins_to_drop.R")


#df_prep <- readRDS("data/processed/df_prep_forQ1_assumptiontests.RDS")
df_prep <- readRDS("data/processed/targets/sales/df_prep_bldg_v2026_03.RDS") |> filter(!pin10 %in% drop_parcels)


fsf_release_year <- 2020.493

# Keep variable names; add only what's needed for the simple model
df <- df_prep |>
  mutate(
    log_price = log(sale_price),
   # in_eff_sfha = factor(in_eff_sfha, levels = c("Not SFHA","SFHA")),
    Triad = factor(Triad, levels = c("North","South","City")),
    event = if_else(sale_year + 0.0 > fsf_release_year, "Post", "Pre") |> factor(c("Pre","Post")),
    rel_year = (sale_year - fsf_release_year) |> floor(),
    sale_quarter = quarter(sale_date),
    sale_quarter = factor(sale_quarter),
    # Treatment: High FF switches on only after release
    highff_post = as.integer((high_ff_score %in% c(1, TRUE, "1", "TRUE")) & event == "Post")
  ) |>
  filter(pin10 != "0710101038")  # had 100ish sales in one year, suspicious parcel


df <- df |>
  filter(
    !is.na(high_ff_score) &
      !is.na(in_eff_sfha) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date) &
           !is.na(Triad)
         )


```

# Transformation of the Dependent Variable

paste in model results and figure output from script file. 

# Pre-trends checks faceted by Triad

::: {.panel-tabset}
### Narrative

We test whether **within each Triad**, groups run parallel trends pre-event. Faceting often reveals flatter, less significant differences because the Triad captures systematic geography-specific drifts.


### Models

Slopes before Event:
```{r}
# Option A: Linear pre-trend slope test (restrict to Pre)
pre <- df |> filter(sale_date < new_info_released)

# Compare slopes over time by SFHA, by High FF, and by their interaction
m_sfha   <- feols(log_price ~ sale_year * in_eff_sfha, data = pre, cluster = ~pin10)
m_highff <- feols(log_price ~ sale_year * high_ff_score, data = pre, cluster = ~pin10)

# technically high_ff_Score is not known yet, but it could could convey true risk and if properties that were high risk were already on a different trend than less risky properties.
m_both   <- feols(log_price ~ sale_year * in_eff_sfha * high_ff_score, data = pre, cluster = ~pin)

modelsummary(
  list("SFHA × time" = m_sfha, "HighFF × time" = m_highff, "SFHA×HighFF × time" = m_both),
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests"
) |>
  tab_options(data_row.padding = px(2)) |>
  tab_source_note(md("We want NOT statistically significant interaction slope terms for variablesinteracted with sale_year."))
```

With Fixed Effects:

```{r}
# Option B: Linear pre-trend slope test (restrict to Pre)
pre <- df |> filter(sale_date < new_info_released)

# Compare slopes over time by SFHA, by High FF, and by their interaction
m_sfha   <- feols(log_price ~ sale_year * in_eff_sfha | pin + sale_year, data = pre, cluster = ~pin10)
m_highff <- feols(log_price ~ sale_year * high_ff_score| pin + sale_year, data = pre, cluster = ~pin10)

# technically high_ff_Score is not known yet, but it could could convey true risk and if properties that were high risk were already on a different trend than less risky properties.
m_both   <- feols(log_price ~ sale_year * in_eff_sfha * high_ff_score | pin + sale_year, data = pre, cluster = ~pin10)

modelsummary(
  list("SFHA × time" = m_sfha, "HighFF × time" = m_highff, "SFHA×HighFF × time" = m_both),
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests"
) |>
  tab_options(data_row.padding = px(2)) |>
  tab_source_note(md("We want NOT statistically significant interaction slope terms for variablesinteracted with sale_year."))
```


### Models (by Triad)

```{r}
pre <- df |> dplyr::filter(event == "Pre", !is.na(Triad))
triads <- levels(droplevels(df$Triad))

mods <- purrr::map(triads, function(tr){
  d <- dplyr::filter(pre, Triad == tr)
  feols(log_price ~ sale_year * in_eff_sfha * high_ff_score, data = d, cluster = ~pin)
}) |> rlang::set_names(triads)

modelsummary(
  mods,
  output     = "gt",
  stars      = TRUE,
  estimate   = "{estimate}{stars}",
  statistic  = "({std.error})",
  gof_omit   = "IC|Log|Adj|AIC|BIC",
#  add_rows   = data.frame(Term = "SE clustered", Value = "pin"),
  title      = "Pre-event slope tests by Triad"
)
```

```{r}
#| results: asis
sig_terms <- c(
  "sale_year:in_eff_sfhaSFHA",
  "sale_year:high_ff_scoreHigh FF",
  "sale_year:in_eff_sfhaSFHA:high_ff_scoreHigh FF"
)

summ <- purrr::imap_dfr(mods, ~ broom::tidy(.x) |> dplyr::mutate(Triad = .y)) |>
  dplyr::filter(term %in% sig_terms) |>
  dplyr::mutate(sig = p.value < 0.05)

pass <- summ |>
  dplyr::group_by(Triad) |>
  dplyr::summarise(pass = !any(sig), .groups = "drop")

pass_triads <- paste(pass$Triad[pass$pass], collapse = ", ")
fail_triads <- paste(pass$Triad[!pass$pass], collapse = ", ")

cat("::: callout-tip\n")
cat("#### Parallel trends check (Triad-specific)\n")
if (nzchar(pass_triads)) cat("**Pass (no significant pre-event slope differences at 5%)**: ", pass_triads, "\n\n", sep = "")
if (nzchar(fail_triads)) cat("**Flagged (>=1 significant pre-event slope)**: ", fail_triads, ". For these Triads, consider narrowing the pre window or adding group-specific trends.\n", sep = "")
cat(":::\n")
```

### Figures (facet by Triad)

```{r}
pre_summ <- pre |>
  dplyr::group_by(sale_year, Triad, in_eff_sfha, high_ff_score) |>
  dplyr::summarise(
    n = dplyr::n(),
    mean_lp = mean(log_price, na.rm = TRUE),
    sd_lp   = sd(log_price,   na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(se = sd_lp / sqrt(pmax(n, 1)), grp = interaction(in_eff_sfha, high_ff_score, sep = " · "))

pre_summ |>
  ggplot(aes(x = sale_year, y = mean_lp, color = grp)) +
  geom_line() +
  geom_ribbon(aes(ymin = mean_lp - 1.96*se, ymax = mean_lp + 1.96*se, fill = grp), alpha = 0.12, linewidth = 0) +
  facet_wrap(~ Triad, nrow = 1) +
  geom_vline(xintercept = fsf_release_year, linetype = 2) +
  annotate("label", x = fsf_release_year + 0.1, y = max(pre_summ$mean_lp, na.rm = TRUE),
           label = "FSF public release (2020.5)", hjust = 0, vjust = 1) +
  scale_x_continuous(expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Mean log(price)", color = NULL, fill = NULL,
       title = "Pre-event trends by Triad (colored by SFHA · FF)") +
  theme(legend.position = "bottom")
```



### Figures

```{r}

```

:::

# Placebo (false event)

```{r}
placebo_cut <- 2017
pre_placebo <- df |> filter(sale_year <= 2019) |> 
  mutate(event_pb = if_else(sale_year > placebo_cut, "PostPB", "PrePB") |> factor(c("PrePB","PostPB")))

mpb <- feols(log_price ~ high_ff_score * in_eff_sfha * event_pb | pin + sale_year + Triad,
             cluster = ~pin, data = pre_placebo)

modelsummary(mpb, output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             title = "Placebo test (cut at 2017)") |>
  tab_source_note(md("Finding: PostPB terms insignificant → placebo passes, no fake effect at 2017."))
```


# Main specification & robustness

::: {.panel-tabset}
### Main spec

```{r}
lake100ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within100ft_ExportTable_TableToExcel.xlsx")
lake500ft <- readxl::read_xlsx("data/processed/parcels_2025_lakeMI_within500ft_ExportTable_TableToExcel.xlsx")

df <- df |>
  mutate(coastal_100 = pin10 %in% lake100ft$PIN10,
         coastal_500 = pin10 %in% lake500ft$PIN10)

# df <- df |>
#   mutate(coastal = substr(pin, 1, 2) %in% c("05", "11", "14", "17", "20", "21") & condo == "Condo")

# df |> filter(coastal ==TRUE) |> group_by(pin10) |>distinct()

table(df$coastal_100)

df$Triad <- relevel(df$Triad, ref = "South")

## Use in_eff_sfha!!
main_mod <- feols(
  log_price ~ highff_post * in_eff_sfha | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df
)
main_mod_2fe <- feols(
  log_price ~ highff_post * in_eff_sfha | pin + sale_year,
  cluster = ~ pin10,
  data = df
)
main_mod_no100coast <- feols(
  log_price ~ highff_post * in_eff_sfha | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df|>filter(coastal_100 == FALSE)
)

main_mod_no500coast <- feols(
  log_price ~ highff_post * in_eff_sfha | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df|>filter(coastal_500 == FALSE)
)



# Uses change_type!!
main_modv2 <- feols(
  log_price ~ highff_post * change_type | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df
)
main_modv3 <- feols(
  log_price ~ highff_post * change_type * Triad| pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df
)
main_modv3_2fe <- feols(
  log_price ~ highff_post * change_type * Triad| pin + sale_year,
  cluster = ~ pin10,
  data = df
)
main_mod_changetype_no100coast <- feols(
  log_price ~ highff_post * change_type * Triad| pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = (df |> filter(coastal_100 == FALSE))
)
main_mod_changetype_no500coast <- feols(
  log_price ~ high_ff_score* change_type * event *Triad | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = (df |> filter(coastal_500 == FALSE))
)

main_mod_mvh <- feols(
  log_price ~ high_ff_score + change_type + event + Triad + high_ff_score*change_type * event *Triad 
  | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df
)

main_mod_mvh2 <- feols(
  log_price ~ high_ff_score + change_type + event  + high_ff_score*change_type * event 
  | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df
)

modelsummary::modelsummary(list(main_mod_mvh, main_mod_mvh2), stars = TRUE)
# modelsummary(main_mod, output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
#              statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
#              coef_map = c(
#                "highff_post" = "High FF (Post only)",
#                "in_eff_sfhaSFHA" = "In SFHA",
#                "highff_post:in_eff_sfhaSFHA" = "High FF(Post) × In SFHA"
#              ),
#              title = "Main spec: log(price) ~ HighFF(Post) × SFHA + FE") |>
#   tab_source_note(md("FE: pin, sale_year. SE clustered at pin. Treatment switches on only after the information release for High-FF parcels."))

coef_map <- c(
  "in_eff_sfhaTRUE" = "In SFHA",
  "eventPost" = "Post",
  # Two-way interactions
  "high_ff_scoreTRUE:eventPost" = "High Flood Factor × Post",
  "change_typeAlways SFHA:eventPost" = "Always in SFHA × Post",
  "change_typeChanges SFHA:eventPost" = "Changed SFHA Status × Post",
 # "high_ff_scoreTRUE:TriadNorth" = "High Flood Factor × North",
 # "high_ff_scoreTRUE:TriadSouth" = "High Flood Factor × South",
#  "high_ff_scoreTRUE:TriadCity" = "High Flood Factor × City",
  "eventPost:TriadSouth" = "Post × South",
  "eventPost:TriadCity" = "Post × City",
  "eventPost:TriadNorth" = "Post × North",

  # Three-way interactions
  "high_ff_scoreTRUE:change_typeAlways SFHA:eventPost" = "High Flood Factor × Always in SFHA × Post",
  "high_ff_scoreTRUE:change_typeChanges SFHA:eventPost" = "High Flood Factor × Changed SFHA Status × Post",
    "high_ff_scoreTRUE:eventPost:TriadNorth" = "High Flood Factor × Post × North",

  "high_ff_scoreTRUE:eventPost:TriadSouth" = "High Flood Factor × Post × South",
  "high_ff_scoreTRUE:eventPost:TriadCity" = "High Flood Factor × Post × City",
  "change_typeAlways SFHA:eventPost:TriadSouth" = "Always in SFHA × Post × South",
  "change_typeAlways SFHA:eventPost:TriadCity" = "Always in SFHA × Post × City",

  # Four-way interactions
  "high_ff_scoreTRUE:change_typeAlways SFHA:eventPost:TriadSouth" = "High Flood Factor × Always in SFHA × Post × South",
    "high_ff_scoreTRUE:change_typeAlways SFHA:eventPost:TriadNorth" = "High Flood Factor × Always in SFHA × Post × North",

  "high_ff_scoreTRUE:change_typeAlways SFHA:eventPost:TriadCity" = "High Flood Factor × Always in SFHA × Post × City",


    # Main effects
  "highff_post" = "High Flood Factor (Post)",
  # Two-way interactions
  "highff_post:change_typeAlways SFHA" = "High Flood Factor (Post) × Always in SFHA",
  "highff_post:change_typeChanges SFHA" = "High Flood Factor (Post) × Changed SFHA Status",
    "highff_post:TriadNorth" = "High Flood Factor (Post) × North",

  "highff_post:TriadSouth" = "High Flood Factor (Post) × South",
  "highff_post:TriadCity" = "High Flood Factor (Post) × City",

  # Three-way interactions
    "highff_post:change_typeAlways SFHA:TriadNorth" = "High Flood Factor (Post) × Always in SFHA × North",
  "highff_post:change_typeAlways SFHA:TriadSouth" = "High Flood Factor (Post) × Always in SFHA × South",
  "highff_post:change_typeAlways SFHA:TriadCity" = "High Flood Factor (Post) × Always in SFHA × City"
)

coef_map2_short <- c(
  # Main effects
  "highff_post" = "High FF (Post)",
  "in_eff_sfhaTRUE" = "In SFHA",
  
  # Two-way interactions
  "highff_post:change_typeAlways SFHA" = "High FF × Always SFHA",
  "highff_post:change_typeChanges SFHA" = "High FF × Changed SFHA",
  "highff_post:TriadCity" = "High FF × City",
  "highff_post:TriadNorth" = "High FF × North",
  "highff_post:in_eff_sfhaTRUE" = "High FF & in SFHA",

  # Three-way interactions
  "highff_post:change_typeAlways SFHA:TriadCity" = "High FF × Always SFHA × City",
  "highff_post:change_typeAlways SFHA:TriadNorth" = "High FF × Always SFHA × North"
)

coef_map2 <- c(
  "highff_post" = "High Flood Factor (Post)",
  "highff_post:change_typeAlways SFHA" = "High Flood Factor (Post) × Always in SFHA",
  "highff_post:change_typeChanges SFHA" = "High Flood Factor (Post) × Changed SFHA Status",
  "highff_post:TriadCity" = "High Flood Factor (Post) × City",
  "highff_post:TriadNorth" = "High Flood Factor (Post) × North",

  "highff_post:change_typeAlways SFHA:TriadCity" = "High Flood Factor (Post) × Always in SFHA × City",
  "highff_post:change_typeAlways SFHA:TriadNorth" = "High Flood Factor (Post) × Always in SFHA × North",
    "in_eff_sfhaTRUE" = "In SFHA"
  
)
```


```{r}
modelsummary(list(main_modv2, main_modv3, main_modv3_2fe, main_mod_changetype_no100coast, main_mod_changetype_no500coast), output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
            # coef_map = coef_map2_short,
             title = "Main spec: log(price) ~ HighFF(Post) × SFHA + FE") |>
  tab_source_note(md("FE: pin, sale_year. SE clustered at pin. Treatment switches on only after the information release for High-FF parcels."))
```



```{r}
modelsummary(list(main_mod, main_mod_2fe, main_mod_no100coast, main_mod_no500coast), output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             coef_map = coef_map2_short,
             title = "Main spec: log(price) ~ HighFF(Post) × In Eff. SFHA + FE") |>
  tab_source_note(md("FE: pin, sale_year, sale_quarter. SE clustered at pin. Treatment switches on only after the information release for High-FF parcels."))
```




```{r}
#| eval: false
#table(df$sale_year, df$high_ff_score)

main_mod_prelim_check <- feols(
  log_price ~ high_ff_score* change_type_prelim * event * Triad | pin + sale_year + sale_quarter,
  cluster = ~ pin10,
  data = df |> filter(coastal_100==FALSE)
)
  
modelsummary(list(main_mod_prelim_check), output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             title = "Check to see if Prelim Map has different results") |>
  tab_source_note(md("FE: pin, sale_year. SE clustered at parcel level. Post event means the FF risk information is visible to the public."))
```
```{r}
# Percent interpretation (+95% CI)
tt <- broom::tidy(main_mod, conf.int = TRUE)
terms <- c("highff_post","in_eff_sfhaTRUE","highff_post:in_eff_sfhaTRUE")
pct <- tt[tt$term %in% terms, ] |>
  mutate(
    label = dplyr::recode(term,
      "highff_post"="High FF (Post only)",
      "in_eff_sfhaTRUE"="In SFHA",
      "highff_post:in_eff_sfhaTRUE"="High FF(Post) × In SFHA"),
    effect_pct = 100*(exp(estimate)-1),
    lo = 100*(exp(conf.low)-1),
    hi = 100*(exp(conf.high)-1)
  ) |>
  transmute(Term = label,
            `Effect (%)` = sprintf("%.1f", effect_pct),
            `95% CI` = sprintf("[%.1f, %.1f]", lo, hi))

gt::gt(pct) |> gt::tab_caption("Percent interpretation of key coefficients")
```

::: callout-tip
**Interpretation of coefficients**
- **High FF (Post only):** change for High-FF parcels *outside SFHA* after info release vs. pre.
- **In SFHA:** time-invariant difference for SFHA vs. non-SFHA (net of FE).
- **High FF(Post) × In SFHA:** extra post-release change for High-FF parcels *in SFHA* vs. the reference.
:::

### Event-study view

Doesn't work.


```{r eval = FALSE}
ev_mod <- feols(
  log_price ~ i(rel_year, high_ff_score, ref = -1) | pin + sale_year + Triad,
  cluster = ~pin,
  data = df
)


iplot <- iplot(ev_mod, main = "Event-study: dynamics by Triad, SFHA × FF")
iplot


# Joint pre-period test
pre_wald <- wald(ev_mod, keep = "rel_year::(-[2-9]|1[0-9])::")
cat(sprintf("**Joint pre-period test:** p = %.3f (H0: all pre coefficients = 0)", pre_wald$p.value))
```



### Robustness


```{r}
robust_mod_qtr <- tryCatch(
  feols(
    log_price ~ highff_post * in_eff_sfha | pin + sale_year + sale_quarter + Triad,
    cluster = ~pin,
    data = df |> filter(!is.na(sale_quarter))
  ), error = function(e) NULL)

mods_triad <- setNames(
  lapply(levels(df$Triad), function(tr){
    feols(log_price ~ highff_post * in_eff_sfha | pin + sale_year,
          cluster = ~pin,
          data = df |> filter(Triad == tr))
  }),
  paste("Triad:", levels(df$Triad))
)

ms_models <- c(list("Main (Year+Triad FE)" = main_mod), if (!is.null(robust_mod_qtr)) list("Quarter FE + Triad" = robust_mod_qtr) else list(), mods_triad)

modelsummary(ms_models,
             output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             coef_map = c(
               "highff_post" = "High FF (Post only)",
               "in_eff_sfhaTRUE" = "In SFHA",
               "highff_post:in_eff_sfhaTRUE" = "High FF(Post) × In SFHA"
             ),
             title = "Robustness: alternative time FE and Triad splits (simple model)") |>
  tab_source_note(md("Triad splits estimate the simple model within North/South/City separately."))
```

::: callout-note
**Bottom line (models):** If pre-trends pass within a Triad, rely on that Triad’s estimate. If flagged, either narrow the pre window or show results *with and without* that Triad.
:::

```{r}
df$pre_date2 <- as.factor(df$pre_date)
table(df$pre_date2)

robust_mod_qtr <- tryCatch(
  feols(
    log_price ~ highff_post * in_prelim_sfha | pin + sale_year + sale_quarter + pre_date2,
    cluster = ~pin,
    data = df |> filter(!is.na(sale_quarter))
  ), error = function(e) NULL)

mods_predate <- setNames(
  lapply(levels(df$pre_date2), function(tr){
    feols(log_price ~ highff_post * in_prelim_sfha | pin + sale_year,
          cluster = ~pin,
          data = df |> filter(pre_date2 == tr))
  }),
  paste("FIRM Pre-date:", levels(df$pre_date2))
)

ms_models <- c(list("Main (Year-Q FE)" = main_mod), if (!is.null(robust_mod_qtr)) list("Year-Q + FIRM date" = robust_mod_qtr) else list(), mods_predate)

modelsummary(ms_models,
             output = "gt", stars = TRUE, estimate = "{estimate}{stars}",
             statistic = "({std.error})", gof_omit = "IC|Log|Adj|AIC|BIC",
             coef_map = c(
               "highff_post" = "High FF (Post only)",
               "in_prelim_sfhaTRUE" = "In SFHA",
               "highff_post:in_prelim_sfhaTRUE" = "High FF(Post) × In SFHA"
             ),
             title = "Robustness: alternative time FE and Triad splits (simple model)") |>
  tab_source_note(md("Preliminary FIRM date splits estimate the simple model within North/South/City separately."))
```


:::




# Appendix & Notes

- Schaumburg condo exclusion and other data notes here.

## Sample size with trends

```{r}
# Keep a few polished figures only; send the rest to Appendix
# Example: group means across time with count labels
by_grp <- df |>
  group_by(sale_year, in_eff_sfha, high_ff_score) |>
  summarise(n = n(), mean_lp = mean(log_price, na.rm = TRUE), .groups = "drop")

by_grp |>
  ggplot(aes(sale_year, mean_lp, color = interaction(in_eff_sfha, high_ff_score, sep = " · "))) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = paste0("n=", n)), vjust = -0.9, size = 3, show.legend = FALSE) +
  geom_vline(xintercept = fsf_release_year, linetype = 2) +
  labs(x = NULL, y = "Mean log(price)", color = NULL, title = "Trends with sample sizes") +
  theme(legend.position = "bottom")
```

