---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---
# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.


# Data Sources and Background Information

> TO DO: Fill in missing municipality names. Probably can do by shared assessor neighborhood? or even a spatial join if needed for only the parcels that don't have muni names associated with them. Wouldn't be as big of a computational list for a select list of parcels.

> TO DO: Manually collect the \~2000 flood scores for pins that didn't have them. They are also almost all missing nbhd_code, zip_code, and some are missing clean_name.

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)

```

> Sales are not winsorized

```{r warning = FALSE, message = FALSE}
res_sales  <- readRDS("./data/processed/res_sales.rds") |> 
  filter(sale_date > date("2010-01-01"))  


pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

nicknames <- readxl::read_xlsx("../Merriman RA/ptax/Necessary_Files/muni_shortnames.xlsx")

pin_muni_key <- pin_muni_key |> left_join(nicknames)

```

```{r dropped_pins, message = FALSE}
# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N Lakeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000",     # another CoOp
               "21301140150000",  # vacant lot by the lake, 
               "21301140160000"   # vacant lot by the lake
               
)

res_sales <- res_sales |> filter(pin %nin% drop_pins )

repeat_sales <- res_sales |> 
  
  group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup() |> 

  # a couple outliers were in there
  filter( sale_price < 5000000)


# price corrections randomly spotted
repeat_sales <- repeat_sales |> 
  mutate(sale_price = 
         case_when(
           pin == "15154220240000" & sale_date == as_date("2006-11-01") ~ 180000,   # not 180 million
           pin == "08153010051151" ~ 81000, # not 81 million
         TRUE ~ sale_price
         ))
```

```{r warning = FALSE, message = FALSE}
puni_pins <- read_csv("data/processed/floodfactor_scores.csv")

pin_muni_key <- left_join(pin_muni_key, puni_pins)

```

```{r make-df_prep, message = FALSE}

# 1) Make sure sale_date is a Date (if not already)
df_prep <- repeat_sales %>%
  mutate(
    sale_year  = year(sale_date),
    eff_date = ymd(EFF_DATE),
    pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date, sale_year, sale_price, in_eff_sfha, in_prelim_sfha, 
         eff_date, pre_date, in_lomr) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



df_prep <- left_join(df_prep, pin_muni_key)

df_prep <- df_prep |> 
  mutate(
    event = ifelse(sale_date < as_date("2020-06-29"), "1. Pre", "2. Post"),
    high_ff_score = ifelse(env_flood_fs_factor > 4, TRUE, FALSE),
    new_info_released = ymd("2020-06-29")
  ) |>
  select(-c(agency_name, agency_num, short_name, shpfile_name) )

```

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.

```{r}

df_prep |> filter(is.na(in_eff_sfha)) |> ## 22 missing indicators - Take care of 7/1/2023. Dropped in dropped_pins section.
  distinct(pin) |>
  arrange(pin)
# 21301140150000 is vacant lot right on the lake. Was coded as 241 in 2010 but is just a parking lot. will be filtered out. 
# 21301140160000 ditto. 



# muni_zip_lookup <- df_prep |> 
#   distinct(zip_code, clean_name, Triad, Township) |> 
#   filter(!is.na(clean_name) & !is.na(zip_code)& !is.na(Triad) & !is.na(Township))

missing_muniname <- df_prep |> 
  filter(is.na(clean_name)) |>
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 distinct(pin10, 
          nbhd_code, zip_code, 
         clean_name
          ) |>
  arrange(pin10)

muni_nbhd_lookup <- df_prep |> 
  distinct(nbhd_code, 
           zip_code,
           clean_name, Triad, Township) |> 
  filter(!is.na(clean_name) & !is.na(nbhd_code) & !is.na(zip_code) & !is.na(Triad) & !is.na(Township) ) 
  

df_prep <- df_prep |> 
  # WARNING: Uses first match. Some zipcodes and assessor neighborhoods 
  # are in multiple municipalities, triads, and townships which is IGNORED FOR NOW 
  left_join(muni_nbhd_lookup, by = c("zip_code", "nbhd_code"), multiple = "first") |>
    mutate(
      clean_name = ifelse(is.na(clean_name.x), clean_name.y, clean_name.x),
            Triad = ifelse(is.na(Triad.x), Triad.y, Triad.x),
            Township = ifelse(is.na(Township.x), Township.y, Township.x)


           ) |>
  select(-c(clean_name.x, clean_name.y, Triad.x, Triad.y, Township.x, Township.y))



missing_muniname2 <- df_prep |>   
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 filter(is.na(clean_name)) |> 
  distinct(pin10, zip_code, nbhd_code, clean_name)



missing_ff <- df_prep |> 
  filter(is.na(env_flood_fs_factor)) |>
  mutate(pin10 = str_sub(pin, 1, 10)) |>
 distinct(pin10, 
         # pin, 
          nbhd_code, zip_code, clean_name
          ) |>
  arrange(pin10)

# missing_ff  # 4768 distinct pins, over 12K observations
# 2723 parcels missing flood factor scores

#write_csv(missing_ff, "data/processed/missing_floodfactor_scores.csv")

```

```{r make-df_pairs, message = FALSE}
# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),
  #  in_sfha_t1      = ifelse(is.na(in_sfha_t1), "Not SFHA", in_sfha_t1),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha,
  ) %>%

  ungroup() |> 
  mutate(new_info_released = ymd("2020-06-29")) |>
  # get rid of redundant variables that would be confusing
  select(-c(sale_price, sale_date, sale_year, in_eff_sfha)) 



df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)        
        # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")),  # between sales
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),    # between sales
        years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
        ann_d_log_price = d_log_price / years_btwn,

    
    # SFHA change as a factor variable
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
  ) |>
  
  # add additional location variables (Triad, township, municipality, etc)
  left_join(pin_muni_key)



df_pairs <- df_pairs |> 
  mutate(
    
    # relative time variables 
    t_months_eff = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
    
    t_years_eff = round(time_length(sale_date_t1 - eff_date, "years") ),    # first sale to FIRM update, in years

    t_months_prelim = round(time_length(sale_date_t1 - pre_date, "months") ), # first sale to FIRM update, in months

    t_years_prelim = round(time_length(sale_date_t1 - pre_date, "years") ),    # first sale to FIRM update, in years

  )|>
  # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1))



df_pairs <- df_pairs |> 
  select(pin, 
         ann_d_log_price, d_log_price,
         sale_year_t1, sale_price_t1, in_sfha_t1, 
         sale_year_t2, sale_price_t2, in_sfha_t2, 
         years_btwn, change_type, everything()
  )

df_pairs <- df_pairs |> 
  mutate(change_type = factor(change_type, levels = c("Both Out of SFHA", "Both In SFHA", "Added", "Removed")))


df_pairs <- df_pairs |> 
  mutate(ff_factor = factor(env_flood_fs_factor))


```

```{r read-indata}
df_pairs <- readRDS("data/processed/df_pairs.RDS")
ff_pairs <- readRDS("data/processed/ff_pairs.rds")
df_prep <- readRDS("data/processed/df_prep.rds")

```

There are `r n_distinct(df_pairs$pin)` pins remaining in `df_pairs`.

```{r}
## Create event indicators

## if the first sale was before the release and the next sale was after the release, then coded as TRUE, otherwise, FALSE
ff_pairs <- df_pairs |>  
  mutate(
    treated = ifelse(sale_date_t1 < as_date("2020-06-29") & sale_date_t2 >= as_date("2020-06-29"), TRUE, FALSE),
    high_ff_score = ifelse(env_flood_fs_factor > 4, TRUE, FALSE)
  )
```

There are `r print(ff_pairs |> filter(treated ==TRUE & high_ff_score == TRUE) |> count())` observations that are treated and have a high flood factor score (greater than 4).

```{r}
table(ff_pairs$sale_year_t2, ff_pairs$change_type)
```

## Descriptive Stats

::: panel-tabset
### df_prep Descriptive Stats

```{r descriptive-stats-df_prep}
skim(df_prep)
```

### ff_pairs Descriptive Stats
```{r descriptive-stats-df_pairs}
skim(ff_pairs)
```
:::


## Parallel Trends Assumptions


::: panel-tabset
### Parallel Trends assumption for all sales

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)


df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score) |> 
  summarise(mean_growth = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)")
```

```{r}

slopes1 <- lm(log(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)


slopes2 <- lm(log(sale_price) ~ in_eff_sfha*event*sale_year, data = df_prep)


modelsummary::modelsummary(
  list(slopes1, slopes2),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

**sale_date:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.

```{r}
#| layout-ncol: 2
#| column: page
#| message: false

ggplot(df_prep |> filter(!is.na(high_ff_score)), aes(x = sale_year, y = log(sale_price), color = high_ff_score)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by High Flood Factor",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "High FF Score",
        caption = "Dataset: All Sales (df_prep)"

  ) +
  theme_minimal()

ggplot(df_prep |> 
         filter(!is.na(in_eff_sfha)), aes(x = sale_year, y = log(sale_price), color = in_eff_sfha)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event
             ) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by SFHA Status",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "In SFHA",
    caption = "Dataset: All Sales (df_prep)"
  ) +
  theme_minimal()
```


### Parallel trends test for repeat sales

DV is change in logged price.

```{r}
#| layout-ncol: 2
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released &
              !is.na(ff_factor)) |> 
    group_by(sale_year_t1, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n() ) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type", 
       caption = "Dataset: Repeat Sales") 


ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
           !is.na(ff_factor)) |>
  group_by(sale_year_t2, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type", caption = "Dataset: Repeat Sales")
```

```{r}
#| column: page
#| layout-ncol: 3
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year_t1, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 < new_info_released & sale_year_t2 > 2015 &
            !is.na(high_ff_score)) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
             n = n() ) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends for 2nd sale by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")
```


Is testing the assumption on repeat sales actually right to do or should I just use all sales?? I feel like it should be all sales.

```{r}

slopes1<- lm(d_log_price ~ sale_year_t2*treated*high_ff_score, data = ff_pairs)

slopes2 <- lm(d_log_price ~ sale_year_t2*treated*change_type, data = ff_pairs)

modelsummary::modelsummary(
  list(slopes1, slopes2),
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

Parallel trends not super supported in either model for repeat sales?
:::

# Models

```{r}
#| column: page
#| label: tbl-proposal-models-ffscores
#| tbl-cap: "Model in proposal"


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ change_type,       
                   data = ff_pairs,
                   cluster = ~pin
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated*change_type,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "IV" = feols(d_log_price ~ high_ff_score*treated*change_type | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "V" = feols(d_log_price ~ high_ff_score*treated*change_type | sale_year_t2 + pin,
                    data = ff_pairs,
                    cluster = ~pin
                    
      )
    )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

```{r}
#| column: page
#| label: tbl-fixedeffects-models-ffscores
#| tbl-cap: "Categorical or Ordinal Risk Scores and then adding some Controls"


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(d_log_price ~ change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated | clean_name,
                    data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ), 
       "IV" = feols(d_log_price ~ high_ff_score*treated | pin + sale_year_t2 + clean_name,
                    data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    ))
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

# Using All Sales Data - Not just Repeat Sales

**using df_prep**

```{r}
#| label: tbl-models-with-dfprep
#| tbl-cap: "A 'high' flood factor score is a score of 5 or higher. Sales after the 'event' are coded as 'Post' event, which is coded as June 2020 when the scores were released. The interaction of a high flood factor score and being post event is a key variable to look at. Year Fixed Effects are probably necessary due to the growth in sales prices during and after COVID. The last column has PIN, municipality, and sales year fixed effects."

  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(log(sale_price) ~ high_ff_score | clean_name,       
                  data = df_prep,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep,
                  cluster = ~pin + clean_name
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "pin fes" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "2 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin+ clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ high_ff_score*event | pin + clean_name + sale_year,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin + clean_name + sale_year,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      )
    
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

# Robustness Checks

## Risk Score as Categorical Variable

```{r}
all_models = list(

"Risk Score as Factor" = list(
    
      
      "III" = feols(d_log_price ~ ff_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
         "IV" = feols(d_log_price ~ ff_factor*change_type*treated | pin + clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      "V" = feols(d_log_price ~ ff_factor*change_type*treated | pin,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
      ,
      "V" = feols(d_log_price ~ ff_factor*change_type*treated | pin + sale_year_t2,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    
    )
)

all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```

## Risk Score as Ordinal Variable

```{r}
model_list <- list(
        "No FEs" = list(
      
      "I" = feols(d_log_price ~ change_type+ env_flood_fs_factor*treated,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ env_flood_fs_factor*change_type*treated,       
                   data = ff_pairs,
                   cluster = ~pin
                    
      )),
        "FEs" = list(
      
      "Muni FE" = feols(d_log_price ~ change_type*treated + env_flood_fs_factor*treated | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "Muni Fe" = feols(d_log_price ~ env_flood_fs_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      
      "PIN FE" = feols(d_log_price ~ env_flood_fs_factor*change_type | pin,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name           
      )
    )
        )

all_models_formatted <- modelsummary::modelsummary(model_list,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```
