---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---

# Data Sources and Background Information

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

Parcel shapefile used in ArcGIS Pro is downloaded from CCAO's Archived 2022 parcel dataset [here.](https://datacatalog.cookcountyil.gov/Property-Taxation/ccgisdata-Parcel-2021/77tz-riq7/about_data)

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(plm)

```





> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. 



```{r}
df_prep <- readRDS("data/processed/df_prep.rds")
```



# Research Question 1 

The final data set represents the difference in price appreciation for properties that were mapped into an SFHA compared to the hypothetical price they would havesold at if they had not been mapped into an SFHA. 

between sales growth rate for ___ observations and _____ properties.


**Does the value of real estate parcels increase when they are removed from an SFHA?** 

H1: A property removed from a SFHA will increase in value more than if it had not beenremoved from an SFHA.

## Model Info 

To investigate whether the value of real estate parcels increases when they are removed from a Special Flood Hazard Area (SFHA), I used a Fixed Effects on PINs with sales from2010 to 2024. 


**For Fixed Effect Models:** The dataset was first prepared by filtering out irrelevant parcels and ensuring that each property had at least two recorded sales. There is an indicator variable for if a PIN was in an SFHA at the time of sale or not. 

_For 3 way interaction: In order to include PINs that did not change SFHA status, an additional indicator for post-FIRM update sales was created to interact with SFHA status._



Additional variables were constructed to measure the timing of sales relative to the date a new Flood Insurance Rate Map (FIRM) took effect, allowing me to distinguish between sales occurring before and after floodplain reclassification. The time between sales was measured in both months and years.

These models tested whether being removed from the SFHA is associated with a statistically significant increase in log sale price.

I also explored interaction terms with LOMR status. Owners can appeal their flood zone designation and have the map altered. This results in them no longer having mandatory flood insurance if their appeal is accepted. I also included alternative specifications, such as including binary indicators specifically for whether a parcel was added or removed from an SFHA. 

All models clustered standard errors at the parcel (PIN) level to account for repeated observations of the same property.


Notes:

1. Removal from the SFHA is due to the FEMA flood insurance rate maps being updated. Properties are either in or out of the "1-in-100" year flood plain. They can be located in the SFHA and also have a LOMR that "removes" them from the floodplain. This information is represented in multiple variables (`in_eff_sfha` and `in_lomr`). If an observation is coded as `Removed` from an SFHA, it indicates that the floodplain shapefile itself changed that was created by FEMA. If a FIRM is updated and the property previously had a LOMR and FEMA finds that the LOMR still is good. 

- If a property was in an SFHA in a FIRM and had an approved LOMR and then the FIRM is updated years later and the LOMR was still viewed as accurate and valid, then the PIN will appear as "removed from the SFHA" because the updated FIRM will incorporate the old LOMR into the updated floodplain.   

2. Treatment window timing: In theory, EFF_DATE would be associated with a change in price due to the capitalization of mandatory flood insurance requirement for homes that have mortgages in floodplains. The knowledge of the risk and the potential loss due to future floods may decrease the amount that buyers are willing to pay for a property that they know see as more risky even if the financial ties to required flood insurance are not effective yet. PRE_DATE is used due to a buyers anticipation of a policy's impact. 

Concerns: 

- Who's included or excluded? Are the properties that are in floodplains different in ways that impact the sales? Are people less willing to buy risky properties in general, resulting in fewer sales? 

 - Inflation? Market trends? Year or regional fixed effects?   
 
 - If parcels were removed from the FEMA flood zone but still at risk, does that say more about information asymmetry or regulatory trust than flood safety?
 
 
 - Areas that have received new flood maps are mostly wealthier parts of Cook County. The 800+ pins added to flood plains in the preliminary FIRM are all in Northern Cook County. The FIRMs updated in 2018 and 2021 are along the lake front and include Glencoe/Wilmette areas. Could really influence price trends.



```{r}
library(skimr)

skim(df_prep)
```





```{r}
df_prep <- df_prep |> 
  mutate(year = as.factor(sale_year))

df_prep |> group_by(pin, sale_year) |> 
  mutate(n = n()) |>
  filter(n() > 1) |>
  select(pin, n, sale_year, flood_factor_score, sale_price) |> arrange(desc(n))

df_prep <- df_prep |> group_by(pin, sale_year) |> 
  mutate(sale_price = mean(sale_price)) |>
  distinct(pin, sale_year,high_ff_score, in_eff_sfha, in_prelim_sfha, Triad, event, in_lomr, addedto_eff_sfha, removedfrom_eff_sfha, sale_price, eff_date, pre_date)

df_prep |> group_by(pin, sale_year) |> filter(n() > 1) |> distinct(pin)

```


```{r}
df_prep <- df_prep |> 
  group_by(pin, sale_year, eff_date, pre_date ) |>
  summarize(sale_price = mean(sale_price),
            log_price = mean(log(sale_price)),
            in_prelim_sfha = last(in_prelim_sfha),
            in_eff_sfha = last(in_eff_sfha),
            in_lomr = last(in_lomr),
            addedto_eff_sfha = last(addedto_eff_sfha), 
            removedfrom_eff_sfha = last(removedfrom_eff_sfha))


df_prep$eff_date_chr <- as.character(df_prep$eff_date)
df_prep$pre_date_chr <- as.character(df_prep$pre_date)

table(df_prep$eff_date_chr)
table(df_prep$pre_date_chr)

```

# Models

## Twoway FE

```{r}
#| label: tbl-plmmodels-fixedeffects


library(jtools)
all_models <- list(
  
  "Eff SFHA" = plm(log(sale_price) ~ in_eff_sfha,   
                   index = c("pin", "sale_year"),
                   model = "within",
                   effect = "twoway",
                   data = df_prep
  ),
  
  "Prelim SFHA" = plm(log(sale_price) ~ in_prelim_sfha,
                      index = c("pin", "sale_year"),
                      model = "within",
                      effect = "twoway",
                      data = df_prep
  ),
  
  "With LOMRs" = plm(log(sale_price) ~ in_eff_sfha + in_lomr,
                     index  =c ("pin", "sale_year"),
                     model = "within",
                     
                     effect = "twoway",
                     data = df_prep 
  ),
  
  
  "Prelim With LOMRs" = plm(log(sale_price) ~ in_prelim_sfha + in_lomr,
                     index  =c ("pin", "sale_year"),
                     model = "within",
                     
                     effect = "twoway",
                     data = df_prep 
  )
) 


all_models_formatted <- modelsummary::modelsummary(all_models,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)


# export_summs(all_models)

all_models_formatted


```


```{r}
#| label: tbl-addedremoved-fixedeffects


table(df_prep$addedto_eff_sfha)
table(df_prep$removedfrom_eff_sfha)

all_models <- list(
  
  "Added or Removed SFHA" = plm(log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha,   
                   index = c("pin", "sale_year"),
                   model = "within",
                   effect = "twoway",
                   data = df_prep

  )
  )


export_summs(all_models )


```
 
```{r}
#| label: tbl-feolsmodels-fixedeffects

df_prep <- df_prep |> mutate(sale_year = as.factor(sale_year))

all_models <- list(
  
  "Eff SFHA" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,   
                   data = df_prep
  ),
  
  "Prelim SFHA" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                      data = df_prep
                      
  ),
  
  "With LOMRs" = feols(log(sale_price) ~ in_eff_sfha + in_lomr | pin + sale_year,
       
                     data = df_prep
  ),
  
  "Prelim SFHA w LOMRs" = feols(log(sale_price) ~ in_prelim_sfha + in_lomr | pin + sale_year,
                      data = df_prep
                      
  )
  ) 


all_models_formatted <- modelsummary::modelsummary(all_models,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted

```


## Subsets for policy rollouts


Models with Policy Rollout Subsets

> FIRMs are updated in different years!! Fixed Effects is not great with this! 

### Effective FIRMs


```{r}
#| label: tbl-plmmodels-fixedeffects-subsets

table(df_prep$eff_date)


table(df_prep$addedto_eff_sfha)
table(df_prep$removedfrom_eff_sfha)

df_prep$in_eff_sfha <- factor(df_prep$in_eff_sfha)
df_prep$in_lomr <- factor(df_prep$in_lomr)


all_models <- list(

  
  "2019 FIRM Update" = plm(log(sale_price) ~ in_eff_sfha,
                   index = c("pin", "sale_year"),
                   subset = eff_date_chr=="2019-11-01",
                   model = "within",
                   effect = "twoway",
                   data = df_prep
  ),
  
  "2021 FIRM Update" = plm(log(sale_price) ~ in_eff_sfha,
                      index = c("pin", "sale_year"),
                      model = "within",
                      effect = "twoway",
                      data = df_prep,
                      subset = eff_date_chr == "2021-09-10"
  )
) 


export_summs(all_models)


```


### Preliminary FIRMs



```{r}
table(df_prep$pre_date)
all_models <- list(

  "2015 PreFIRM Update" = plm(log(sale_price) ~ in_prelim_sfha,
                   index = c("pin", "sale_year"),
                   subset = pre_date_chr=="2015-02-12",
                   model = "within",
                   effect = "twoway",
                   data = df_prep
  ),

  "2019 PreFIRM Update" = plm(log(sale_price) ~ in_prelim_sfha,
                      index = c("pin", "sale_year"),
                      model = "within",
                      effect = "twoway",
                      data = df_prep,
                      subset = pre_date_chr == "2019-06-26"

  ),
    "2021 PreFIRM Update" = plm(log(sale_price) ~ in_prelim_sfha,
                      index = c("pin", "sale_year"),
                      model = "within",
                      effect = "twoway",
                      data = df_prep,
                      subset = pre_date_chr == "2021-09-22"

  )
) 


export_summs(all_models )

```

