---
title: "Cook County Parcel Sales"
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    warning: false
    message: false
  #  error: true
---

# Data Sources and Background Information


```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(plm)    # panel linear models. interchangable with fixest but have different syntax for models
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
```

> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. LOMRs are only considered in the bottom section on effective FIRMs and insurance requirements. 

```{r}
df_prep <- readRDS("data/processed/df_prep_parcels_20260109.rds") |>
  filter(pin10 != "1129315024")  # Building on sherwin. Land is in Coastal SFHA for 2018 but building is not. 

res_sales <- readRDS("./data/processed/df_allsales.rds")
```

```{r remove-missingvalues}
df_prep <- df_prep |>
    filter(pin10 != "0710101038") |>

  filter(
   # !is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) #&
           #!is.na(Triad)
         ) |>
  mutate()


res_sales <- res_sales |>
    filter(pin10 != "0710101038") |>

  filter(
    !is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date) &
           !is.na(Triad)
         )

#res_sales <- res_sales |> distinct(pin, sale_date, sale_price, .keep_all = TRUE)

# remove duplicates

df_prep <- df_prep |> distinct(pin, sale_date, sale_price, .keep_all = TRUE)
```

# Research Question 1

The final data set represents the difference in price appreciation for properties that were mapped into an SFHA compared to the hypothetical price they would have sold at if they had not been mapped into an SFHA.

between sales growth rate for \_\_\_ observations and \_\_\_\_\_ properties.

**Does the value of real estate parcels increase when they are removed from an SFHA?**

H1: A property removed from a SFHA will increase in value more than if it had not been removed from an SFHA.

## Model Info

To investigate whether the value of real estate parcels increases when they are removed from a Special Flood Hazard Area (SFHA), I used a Fixed Effects on PINs with sales from2010 to 2024.

**For Fixed Effect Models:** The dataset was first prepared by filtering out irrelevant parcels and ensuring that each property had at least two recorded sales. There is an indicator variable for if a PIN was in an SFHA at the time of sale or not.

*For 3 way interaction: In order to include PINs that did not change SFHA status, an additional indicator for post-FIRM update sales was created to interact with SFHA status.*

Additional variables were constructed to measure the timing of sales relative to the date a new Flood Insurance Rate Map (FIRM) took effect, allowing me to distinguish between sales occurring before and after floodplain reclassification. The time between sales was measured in both months and years.

These models tested whether being removed from the SFHA is associated with a statistically significant increase in log sale price.

I also explored interaction terms with LOMR status. Owners can appeal their flood zone designation and have the map altered. This results in them no longer having mandatory flood insurance if their appeal is accepted. I also included alternative specifications, such as including binary indicators specifically for whether a parcel was added or removed from an SFHA.

All models clustered standard errors at the parcel (PIN) level to account for repeated observations of the same property.

-   Robustness checks: cluster at eff_date or muni level, vcov = "hetero", etc.

Notes:

1.  Removal from the SFHA is due to the FEMA flood insurance rate maps being updated. Properties are either in or out of the "1-in-100" year flood plain. They can be located in the SFHA and also have a LOMR that "removes" them from the floodplain. This information is represented in multiple variables (`in_eff_sfha` and `in_lomr`). If an observation is coded as `Removed` from an SFHA, it indicates that the floodplain shapefile itself changed that was created by FEMA.

-   If a property was in an SFHA in a FIRM and had an approved LOMR and then the FIRM is updated years later and the LOMR was still viewed as accurate and valid, then the PIN will appear as "removed from the SFHA" because the updated FIRM will incorporate the old LOMR into the updated floodplain. Depending on the time of sale, being flaggeda as removed from the SFHA would miss the potential price change from the change in insurance requirement (which again, was not the original research question).

2.  Treatment window timing: In theory, EFF_DATE would be associated with a change in price due to the capitalization of mandatory flood insurance requirement for homes that have mortgages in floodplains. 

- PRE_DATE is also used due to a buyers anticipation of a policy's impact. The knowledge of the risk and the potential loss due to future floods may decrease the amount that buyers are willing to pay for a property that they see as more risky even if the financial ties to required flood insurance are not effective yet.   


Concerns:

-   Who's included or excluded? Are the properties that are in floodplains different in ways that impact the sales? Are people less willing to buy risky properties in general, resulting in fewer sales?

-   If parcels were removed from the FEMA flood zone but still at risk, does that say more about information asymmetry or regulatory trust than flood safety?

-   Areas that have received new flood maps are mostly wealthier parts of Cook County. The pins added to flood plains in the preliminary FIRM are all in Northern Cook County. The FIRMs updated in 2019 and 2021 are along the lake front and include Glencoe/Wilmette areas. Could really influence price trends.

Contributions to the literature: Many models model if SFHA status changes, but have it as one variable. this assumes that the effect of being added in or removed from an SFHA is the same in both directions. I model in_eff_sfha as one variable and separate it into added and removed to see if there are different effects.

```{r}
skim(df_prep)
```

## Variable Coding


```{r recode-dfpreptest}
table(df_prep$pre_date)
# df_prep <- df_prep |>
#   mutate(
#     in_eff_sfha = ifelse(is.na(in_eff_sfha), FALSE, in_eff_sfha),
#     in_prelim_sfha = ifelse(is.na(in_prelim_sfha), FALSE, in_prelim_sfha),
#     
#     addedto_eff_sfha = ifelse(is.na(addedto_eff_sfha), FALSE, addedto_eff_sfha),
#     removedfrom_eff_sfha = ifelse(is.na(removedfrom_eff_sfha), FALSE, removedfrom_eff_sfha),
#     
#     addedto_prelim_sfha = ifelse(is.na(addedto_prelim_sfha), FALSE, addedto_prelim_sfha),
#     removedfrom_prelim_sfha = ifelse(is.na(removedfrom_prelim_sfha), FALSE, removedfrom_prelim_sfha)
# 
#          )

df_prep <- df_prep |>
  
  mutate(
    # so I can subset by FIRM date in later steps
    eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date),
    
   # removed_out = removedfrom_eff_sfha == TRUE,# & in_lomr != TRUE,
   # added_in_prelim    = addedto_prelim_sfha == TRUE,
   # removed_out_prelim = removedfrom_prelim_sfha == TRUE,# & in_lomr != TRUE
  ) |>
  group_by(pin) |>
  arrange(sale_date) |>
  mutate(

    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(addedto_eff_sfha== TRUE) )
                                 & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removedfrom_eff_sfha== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added or removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(addedto_prelim_sfha == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removedfrom_prelim_sfha== TRUE), year(pre_date), 10000)
    
    
  ) |>
  ungroup() |>
  mutate(
    
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
        rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000),
    
    # adjustment for if a sale occurs in the same year that it is treated
    # if sale is before preliminary firm, it is coded as relative year == -1, not yet treated
    # rel_year_add_prelim = ifelse(rel_year_add_prelim == 0 & sale_date < pre_date, -1, rel_year_add_prelim),
    # rel_year_remove_prelim = ifelse(rel_year_remove_prelim == 0 & sale_date < pre_date, -1, rel_year_remove_prelim),
    # 
    #     rel_year_add_eff = ifelse(rel_year_add_eff == 0 & sale_date < eff_date, -1, rel_year_add_eff),
    # rel_year_remove_eff = ifelse(rel_year_remove_eff == 0 & sale_date < eff_date, -1, rel_year_remove_eff)
    #     
  ) |>
  mutate(
    qtr  = quarter(sale_date),     # 1 to 4
    year = year(sale_date),            
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    
    # 2005-01-01 2015-02-15 2019-06-28 2021-09-22 

    group_name_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" ~ 0,
      pre_date == "2015-02-12" ~ 2015,
      pre_date == "2019-07-01" ~ 2019,
      pre_date == "2021-09-22" ~ 2021,

      TRUE ~ NA),
      
      ),
    treated_group_prelim = factor(case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      pre_date == "2005-01-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 0,
      pre_date == "2015-02-12" &  (addedto_prelim_sfha|removedfrom_prelim_sfha)~ 2015,
      pre_date == "2019-07-01" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2019,
      pre_date == "2021-09-22" & (addedto_prelim_sfha|removedfrom_prelim_sfha) ~ 2021,

      TRUE ~ NA))
    )

# same concept as grouping by dfirm 
table(df_prep$group_name_prelim)  # number of sales from each area that was updated in cook county
table(df_prep$addedto_prelim_sfha, df_prep$group_name_prelim)
table(df_prep$removedfrom_prelim_sfha, df_prep$group_name_prelim)


table(df_prep$treated_group_prelim)
```


```{r}
table(df_prep$treat_year_remove_prelim, df_prep$Triad)
table(df_prep$treat_year_add_prelim, df_prep$Triad)

```


## Preliminary FIRM descriptive Stats


```{r}
#| tbl-cap: "Observations per year. Added to (removed from) Effective SFHA"
#| layout-ncol: 2

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$addedto_prelim_sfha[df_prep$sale_year>=2016])

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$removedfrom_prelim_sfha[df_prep$sale_year>=2016])
```


```{r} 
table(df_prep$group_name_prelim)    # treated and nontreated  properties in each group of panels updated

table(df_prep$addedto_prelim_sfha)
table(df_prep$removedfrom_prelim_sfha)
```


```{r}
#| tbl-cap: "Properties in South Triad that were removed from PRELIMINARY SFHA in 2015 and properties in South Triad that were always in the SFHA that were in FIRMs updated in 2015."


df_prep |> filter(Triad == "South" & treat_year_remove_prelim == "2015") # all 2019 treatment pins are in South Triad

df_prep |> filter(Triad == "South" & change_type == "Always SFHA" & pre_date_chr == "2015-02-12") 
# change type only exists for effective 
```


```{r}
#| tbl-cap: "Properties in Chicago that were removed from PRELIMINARY SFHA in 2019 and properties in Chicago that were always in the SFHA that were in FIRMs updated in 2019."
#| layout-ncol: 2


df_prep |> filter(Triad == "City" & treat_year_remove_prelim == "2019") # all 2019 treatment pins are in Chicago Triad

df_prep |> filter(Triad == "City" & change_type == "Always SFHA" & pre_date_chr == "2019-07-01") 
# change type only exists for effective
```

## Comparison of Prelim and Eff FIRM Counts

```{r}
#| layout-ncol: 2

table(df_prep$treat_year_remove_eff)
table(df_prep$treat_year_remove_prelim)


table(df_prep$treat_year_add_eff)
table(df_prep$treat_year_add_prelim)


table(df_prep$in_eff_sfha)
table(df_prep$in_prelim_sfha)

table(df_prep$rel_year_remove_eff)
table(df_prep$rel_year_remove_prelim)

```



# Models


> Skim this: https://www.bookdown.org/rwnahhas/RMPH/mlr-interaction.html

"Stratification is equivalent to interacting the effect modifier with every other predictor in the model whereas including an interaction only interacts the effect modifier with the predictor of interest"

## New attempt without subsets

need treatment cohort dummies

```{r}
#| label: tbl-asymeffect-sfha-regional-add
#| tbl-cap: "Heterogeneity of SFHA location assuming an Asymmetric effect"

models <- list(

  # "Heterogeneity of SFHA location assuming an Asymmetric effect"
  added <- feols(
  log(sale_price) ~ group_name_prelim*addedto_prelim_sfha | pin + sale_year,
  data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
  cluster = ~ pin10
),

symmetric <- feols(
  log(sale_price) ~ group_name_prelim*in_prelim_sfha | pin + sale_year,
  data = df_prep,
  cluster = ~ pin10
),

# "Heterogeneity in Effect of being Mapped out of SFHA"
removed<- feols(
  log(sale_price) ~ group_name_prelim*removedfrom_prelim_sfha | pin + sale_year,
  data = df_prep |> filter(treat_year_add_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
  cluster = ~ pin10
)
)

modelsummary(models, stars = TRUE)
  
```





```{r}
#| label: tbl-etwfe
#| tbl-cap: "Extended TWFE? Ideally this is what Wooldridge (2025) would want?. For added to Prelim SFHA."

#extended twoway fe?
twfemodels <- list(
  "TWFE" = feols(
    log(sale_price) ~ Triad*addedto_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  ),
  
  "TWFE 3 FEs" = feols(
    log(sale_price) ~ addedto_prelim_sfha | pin + Triad + sale_year,
    data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  ),
  
  
  "TWFE removed" = feols(
    log(sale_price) ~ Triad*removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_add_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  )
)

modelsummary(twfemodels, stars = TRUE)

```



```{r}
# ============================================================
# Staggered adoption event-studies for:
#  (1) Added to preliminary SFHA  (cohort = treat_year_add_pre)
#  (2) Removed from preliminary SFHA (cohort = treat_year_remove_pre)
# Assumption per you: no unit is both added and removed.
# ============================================================

table(df_prep$treat_year_remove_prelim)
table(df_prep$treat_year_remove_prelim)
table(df_prep$Triad,df_prep$treat_year_remove_prelim)


# --- 0) Prep: cohorts (NA = never-treated), and log outcome
df_es <- df_prep %>%
  mutate(
    # Cohorts (your names)
    g_add_pre = if_else(treat_year_add_prelim == 10000, NA, treat_year_add_prelim),
    g_rem_pre = if_else(treat_year_remove_prelim == 10000, NA, treat_year_remove_prelim)
  )
table(df_es$g_add_pre)
table(df_es$g_rem_pre)

# --- 1) Risk sets (clean because no unit is both added and removed)
# Added model: exclude any "removed" units (if they exist at all)
df_add <- df_es %>% filter(is.na(g_rem_pre))

# Removed model: exclude any "added" units (if they exist at all)
df_rem <- df_es %>% filter(is.na(g_add_pre))

# --- 2) Staggered event studies (Sun & Abraham) with unit FE + year FE
m_add_pre <- feols(
  log(sale_price) ~ sunab(g_add_pre, sale_year, ref.p = -1) | pin + sale_year,
  data = df_add,
  cluster = ~ pin10
)

m_rem_pre <- feols(
  log(sale_price) ~ sunab(g_rem_pre, sale_year,  ref.p = -1) | pin + sale_year,
  data = df_rem,
  cluster = ~ pin10
)

# --- 3) Plots (leads/lags around ref period -1)
iplot(m_add_pre,
      main = "Event study: Added to preliminary SFHA",
      xlab = "Event time (years relative to addition)",
      ylab = "Effect on log price")

iplot(m_rem_pre,
      main = "Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")

# --- 4) Table-ready coefficient output
# (a) Quick regression table
etable(m_add_pre, m_rem_pre,
       headers = c("Added (prelim SFHA)", "Removed (prelim SFHA)"),
       se.below = TRUE)

# (b) Data frame of event-time coefficients (nice for custom tables/ggplot)
add_coefs <- as.data.frame(coeftable(m_add_pre), stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("term")

rem_coefs <- as.data.frame(coeftable(m_rem_pre), stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("term")

# --- 5) Joint pre-trends tests (all leads = 0)
# This tests whether the *pre-treatment* event-time coefficients are jointly zero.
# Pattern below is conservative: it grabs any sunab term with a negative event time.
lead_terms_add <- grep("sunab\\(.*\\)::[-][0-9]+", add_coefs$term, value = TRUE)
lead_terms_rem <- grep("sunab\\(.*\\)::[-][0-9]+", rem_coefs$term, value = TRUE)

if(length(lead_terms_add) > 0) {
  cat("\nJoint pre-trends test (Added):\n")
  print(wald(m_add_pre, lead_terms_add))
}

if(length(lead_terms_rem) > 0) {
  cat("\nJoint pre-trends test (Removed):\n")
  print(wald(m_rem_pre, lead_terms_rem))
}
```


```{r}
m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_remove_prelim, ref = "2021") | pin+ sale_year,
  #data = (df_prep |> mutate(addedto_prelim_sfha = ifelse(addedto_prelim_sfha=="-1000", NA, addedto_prelim_sfha))),
  data = df_prep |> filter(Triad== "North"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "North Cook Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")

 m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_remove_prelim, ref = "2015") | pin + sale_year,
  data = df_prep |> filter(Triad== "South"),
  cluster = ~ pin10
)
iplot(m_rem_pre,
      main = "South Cook Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")



```



```{r}
m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2021") | pin + sale_year,
  data = df_prep |> filter(Triad== "North"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "North Cook Event study: Added to preliminary SFHA",
      ylab = "Effect on log price")

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2015") | pin + sale_year,
  data = df_prep |> filter(Triad== "South"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "South Cook Event study: Added from preliminary SFHA",
      ylab = "Effect on log price")

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2019") | pin + sale_year,
  data = df_prep |> filter(Triad== "City"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "Chicago Event study: Added from preliminary SFHA",
      ylab = "Effect on log price")
```

```{r}
# --- 6) Optional: add geography-by-year trends instead of subsetting (edit Triad var name)

m_add_pre_geo <- feols(log(sale_price) ~ sunab(g_add_pre, sale_year, ref.p = -1) | pin + sale_year + Triad^sale_year,
                         data = df_add, cluster = ~ pin10)
  
  ## Triad FE don't work with removed because the year and triad are collinear
  m_rem_pre_geo <- feols(log(sale_price) ~ sunab(g_rem_pre, sale_year, ref.p = -1) | pin + sale_year,
                         data = df_rem, cluster = ~ pin10)


etable(m_add_pre_geo, m_rem_pre_geo)

summary(m_add_pre_geo, agg = "att" )
summary(m_rem_pre_geo, agg = "att")

```


```{r}
iplot(m_add_pre_geo,
      main = "Event study: Added to preliminary SFHA",
      xlab = "Event time (years relative to addition)",
      ylab = "Effect on log price")

iplot(m_rem_pre_geo,
      main = "Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")
```


## FIRM updates as Information Events


### County Wide Models

Potentially wrong estimates due to staggered treatment of FIRM updates. Also combines multiple comparison groups that shouldn't be combined for the research question.

**Average Within-Parcel Effect of SFHA Status (PIN × Year FE)**

The “countywide” models average within-parcel response to SFHA status, aggregated across all parcels that ever change status. `in_eff_sfha` ignores asymmetric effects of being added or removed to the SFHA. `addedto_eff_sfha` and `removedfrom_eff_sfha` allow for estimation of the effect of being added or removed from an SFHA without assuming that the effect is symmetric. 

```{r}
#| label: tbl-feolsmodels-fixedeffects
#| tbl-cap: "**Average Effect of EFFECTIVE SFHA Status** Within-parcel effect of SFHA exposure over time. Only identifies the effect if SFHA status changes for a parcel. For always-in or always-out parcels, FE wipe out the variation. Interacting with Triad allows for regioinal heterogeneity in the effect."

effective_twfe <- list(

  "Eff SFHA -  County ATE" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
                     cluster = ~ pin + nbhd_code,

                     data = df_prep
  ),
    "Eff SFHA -  County ATE" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
                     cluster = ~ pin,

                     data = df_prep
  ),
      "Eff SFHA -  County ATE" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
                     cluster = ~ clean_name,

                     data = df_prep
  ),
        "Eff SFHA -  County ATE" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
                     cluster = ~ FIRM_PAN,

                     data = df_prep
  ),
        "Eff SFHA -  County ATE" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
                     cluster = ~ pin10,

                     data = df_prep
  ),
  "Eff Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha  | pin + sale_year,
                            cluster = ~ pin + clean_name,

                            data = df_prep
  ) ,
  "Eff Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha  | pin + sale_year,
                            cluster =  ~ clean_name,

                            data = df_prep
  ),
  "Eff Triads - Add or Remove" = feols(log(sale_price) ~ addedto_eff_sfha*Triad + removedfrom_eff_sfha*Triad  | pin + sale_year,
                            cluster =  ~ pin + nbhd_code,

                            data = df_prep
  ),  "Eff Triads - Add or Remove" = feols(log(sale_price) ~ addedto_eff_sfha*Triad + removedfrom_eff_sfha*Triad  | pin + sale_year,
                            cluster =  ~ pin10,

                            data = df_prep
  ),  "Eff Triads - Add or Remove" = feols(log(sale_price) ~ addedto_eff_sfha*Triad + removedfrom_eff_sfha*Triad  | pin + sale_year,
                            cluster =  ~ FIRM_PAN,

                            data = df_prep
  )
)


all_models_formatted <- modelsummary::modelsummary(effective_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


```{r}
#| label: tbl-prelim-ate-fullsample
#| tbl-cap: "**Average Effect of Preliminary SFHA Status** Within-parcel effect of SFHA exposure over time. Only identifies the effect if SFHA status changes for a parcel. For always-in or always-out parcels, FE wipe out the variation and group them together as the comparison group. Interacting with Triad allows for regional heterogeneity in the effect."



prelim_twfe <- list(  
      "Prelim SFHA - Countywide " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin,
                        data = df_prep
  ),
  
  "Prelim SFHA - Countywide" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin10,
                        data = df_prep
  ),
  
    "Prelim SFHA - Countywide " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ clean_name,
                        data = df_prep
  ),
  
      "Prelim SFHA - Countywide " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ FIRM_PAN,
                        data = df_prep
  ),
  
  
  "Prelim Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
                                cluster=  ~ pin,
                                data = df_prep
                                
  ),
    "Prelim Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
                                cluster=  ~ clean_name,
                                data = df_prep
                                
  ),
      "Prelim Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
                                cluster=  ~ FIRM_PAN,
                                data = df_prep
                                
  ),
        "Prelim Countywide - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
                                cluster=  ~ pin10,
                                data = df_prep
                                
  ),
      "Prelim SFHA - Triads" = feols(log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
                        cluster =  ~ pin,
                        data = df_prep
  ),
  
        "Prelim SFHA - Triads" = feols(log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
                        cluster =  ~ clean_name,
                        data = df_prep
  ),
  
  
  "Prelim Triads - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad + removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster=  ~ pin,
                                data = df_prep
                                
  ),
  
  
  "Prelim Triads - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad + removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df_prep
                                
  ),
    "Prelim Triads - Add or Remove" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad + removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin10,
                                data = df_prep
                                
  )
) 



all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}
#| label: tbl-prelim-ate-restrictedsamples-triad
#| tbl-cap: "**Average Effect of Preliminary SFHA Status** Within-parcel effect of SFHA exposure over time. Only identifies the effect if SFHA status changes for a parcel. For always-in or always-out parcels, FE wipe out the variation and group them together as the comparison group. Interacting with Triad allows for regional heterogeneity in the effect."



prelim_twfe <- list(  

  "5" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad  | pin + sale_year,
                                cluster=  ~ pin10,
                                data = df_prep
  ),
  
  "5" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df_prep
  ),
  
  "6" = feols(log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin10,
                                data = df_prep
                                
  ),
      "6" = feols(log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df_prep
  ),
      "6-Restricted" = feols(log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin10,
                                data = df_prep |> filter(change_type != "Never SFHA" & addedto_prelim_sfha == FALSE)
                                
  ),
      "6-Restricted" = feols(log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df_prep  |> filter(change_type != "Never SFHA" & addedto_prelim_sfha == FALSE)
  ),
      "5-Restricted" = feols(log(sale_price) ~  addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin10,
                                data = df_prep |> filter(change_type != "Always SFHA" & removedfrom_prelim_sfha == FALSE)
                                
  ),
      "5-Restricted" = feols(log(sale_price) ~  addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df_prep  |> filter(change_type != "Always SFHA" & removedfrom_prelim_sfha == FALSE)
  )
  
) 



all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


### Subset to just properties Always in SFHA or Changed SFHA (specifically removed from)

Exclude properties that were never in SFHA.   

```{r}
#| label: tbl-filteredproperties-forRQ
#| tbl-cap: "Restricts the sample to parcels whose classification changed from in → out between FIRMs with comparison group of only properties that were Always in an SFHA."


df2 <- df_prep |> filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff ==10000 & treat_year_add_prelim == 10000)

table(df2$change_type)

# effective_twfe <- list(
#   
#   "Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
#                      cluster = ~ pin + nbhd_code,
#                      
#                      data = df2
#   ),
#     "Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
#                      cluster = ~ pin,
#                      
#                      data = df2
#   ),
#       "Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
#                      cluster = ~ FIRM_PAN,
#                      
#                      data = df2
#   ),
#   "Eff Countywide - Remove" = feols(log(sale_price) ~ removedfrom_eff_sfha  | pin + sale_year,  
#                             cluster = ~ pin + clean_name,
#                             
#                             data = df2
#   ) ,
#   "Eff Countywide - Remove" = feols(log(sale_price) ~  removedfrom_eff_sfha  | pin + sale_year,  
#                             cluster =  ~ pin,
#                             
#                             data = df2
#   ),
#   "Eff Triads - Remove" = feols(log(sale_price) ~ removedfrom_eff_sfha*Triad  | pin + sale_year,  
#                             cluster =  ~ pin + nbhd_code,
#                             
#                             data = df2
#   )
# )

prelim_twfe <- list(  
  
  "Prelim SFHA" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ nbhd_code,
                        data = df2
  ),
    "Prelim SFHA " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin,
                        data = df2
  ),
      "Prelim SFHA " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ FIRM_PAN,
                        data = df2
  ),
  
  "Prelim SFHA" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin + clean_name,
                        data = df2
  ),
  
  "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
                                cluster =  ~ pin + clean_name,
                                data = df2
  ),
  
    "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
                                cluster =  ~ pin,
                                data = df2
  ),

  "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
                                cluster =  ~ FIRM_PAN,
                                data = df2
  ),

 
  "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df2
  ), 
  "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster=  ~ pin,
                                data = df2
                                
  ),
    
  "Prelim - Remove" = feols(log(sale_price) ~ removedfrom_prelim_sfha*Triad | pin + sale_year,
                                cluster=  ~ nbhd_code,
                                data = df2
                                
  )
) 


# all_models_formatted <- modelsummary::modelsummary(effective_twfe,
#                output = "flextable",
#                fmt = function(x) round(x, 2),
# 
#              stars = TRUE)
# 
# all_models_formatted



all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


### Subset to just properties Never in SFHA or Changed SFHA (specifically added to SFHA)

Exclude properties that were Always in SFHA.   

Coefficient is hopefully the local average treatment effect (LATE).  

```{r}
df2 <- df_prep |> 
  # only want PINs Never in SFHA and added to SFHA for comparison
  filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000)
table(df2$change_type)
```


```{r}
#| label: tbl-filteredproperties-forRQ-added
#| tbl-cap: "Restricts the sample to parcels whose classification changed from out → in between FIRMs and those that Never in an SFHA."
#| eval: false



effective_twfe <- list(
  
  "In Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                     cluster = ~ nbhd_code,
                     data = df2
  ),
    "In Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                     cluster = ~ pin,
                     data = df2
  ),
  "In Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                     cluster = ~ clean_name,
                     data = df2
  ),
    "In Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                     cluster = ~ FIRM_PAN,
                     data = df2
  ),
    "In Eff SFHA - Countywide" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                     vcov = "hetero",
                     data = df2
  )
  
)

all_models_formatted_eff <- modelsummary::modelsummary(effective_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted_eff
```


```{r}
#| label: tbl-conditional-ate-effective
#| tbl-cap: "**Conditional ATE / Subgroup ATE.** Allows the average capitalization of SFHA status to vary across Triads, capturing regional heterogeneity."
#| eval: false



eff_mapped_out <- list(
  "Eff Countywide - Mapped In" = feols(log(sale_price) ~ addedto_eff_sfha   | pin + sale_year,  
                            cluster = ~ pin + clean_name,
                            data = df2
  ) ,
  "Eff Countywide - Mapped In" = feols(log(sale_price) ~ addedto_eff_sfha   | pin + sale_year,  
                            cluster =  ~ pin,
                            
                            data = df2
  ),
  "Eff Triads - Mapped In" = feols(log(sale_price) ~ addedto_eff_sfha*Triad   | pin + sale_year,  
                            cluster =  ~ pin,
                            
                            data = df2
  ),
  "Eff Triads - Mapped In" = feols(log(sale_price) ~ addedto_eff_sfha*Triad | pin + sale_year,  
                            cluster =  ~ pin + clean_name,
                            
                            data = df2
  )
)

all_models_formatted_eff <- modelsummary::modelsummary(eff_mapped_out,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted_eff
```


```{r}
#| label: tbl-att-and-conditional-ate-prelim
#| tbl-cap: "**ATT for County and Conditional ATE for Triads** Allows the average capitalization of SFHA status to vary across Triads, capturing regional heterogeneity in flood risk perception or housing market elasticity. Still descriptive, not causal."

prelim_twfe <- list(  
  
  "In Prelim SFHA - Countywide" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin,
                        data = df2
  ),
    "In Prelim SFHA - Countywide " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ pin10,
                        data = df2
  ),
      "In Prelim SFHA - Countywide " = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        cluster =  ~ FIRM_PAN,
                        data = df2
  ),
    "Prelim SFHA - Triads" = feols(log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
                        cluster =  ~ pin,
                        data = df2
  ),
      "Prelim SFHA - Triads" = feols(log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
                        cluster =  ~ pin10,
                        data = df2
  ))

all_models_formatted_prelim <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted_prelim
```


```{r}
#| label: tbl-att-and-conditional-ate-prelim-mappedin
#| tbl-cap: "**ATT for County and Conditional ATE for Triads for Properties Mapped into SFHA** Allows the average capitalization of SFHA status to vary across Triads, capturing regional heterogeneity. Sample restricted to properties never in the SFHA and those that were added to the SFHA."


prelim_addedto <- list(

    "Prelim Countywide - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
                                cluster=  ~ pin,
                                data = df2
  ),
      "Prelim Countywide - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
                                cluster=  ~ pin10,
                                data = df2
  ),
  "Prelim Countywide - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
                                cluster=  ~ clean_name,
                                data = df2
  ),
    "Prelim Countywide - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
                                cluster=  ~ FIRM_PAN,
                                data = df2
  ),
  "Prelim Triads - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin,
                                data = df2
  ),
    "Prelim Triads - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ pin10,
                                data = df2
  ),
    "Prelim Triads - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ clean_name,
                                data = df2
  ),
      "Prelim Triads - Mapped In" = feols(log(sale_price) ~ addedto_prelim_sfha*Triad | pin + sale_year,
                                cluster =  ~ FIRM_PAN,
                                data = df2
  )
  
) 

all_models_formatted_prelim <- modelsummary::modelsummary(prelim_addedto,
               output = "flextable",
               fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted_prelim
```


### Subsets for policy rollouts - Local Average Treatment Effects (LATE) ??


#### Effective FIRMs


**Added to SFHA compared to properties that were never in the SFHA**. Comparison group excludes properties that were always in the SFHA and those that were removed from the SFHA at some point. 


```{r}
#| eval: false

df_prep |> filter((change_type == "Changes SFHA" &  change_type != "Always SFHA") |
                           # and properties that are never treated for being removed from the SFHA
                           (treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000) ) |>
feols(log(sale_price) ~ sw(addedto_eff_sfha*in_lomr) | pin + sale_year,
     # data = df_prep,
     subset = ~eff_date_chr != "2008-08-19",
      cluster = ~pin + nbhd_code,
      fsplit= ~eff_date_chr
) |> modelsummary(stars = TRUE)
```


```{r}
#| label: tbl-mappedin-eff-fsplit
#| tbl-cap: "Subsets models so that comparison group is only PINs in same FIRMs that were updated."
#| eval: false

df_prep |> filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000)  |>
feols(log(sale_price) ~ sw(addedto_eff_sfha*in_lomr) | pin + sale_year,
     # data = df_prep,
     subset = ~eff_date_chr != "2008-08-19",
      cluster = ~pin,
      fsplit= ~eff_date_chr
) |> modelsummary(stars = TRUE)
```



#### Preliminary FIRMs

**Added to SFHA compared to properties that were never in the SFHA**. Comparison group excludes properties that were always in the SFHA and those that were removed from the SFHA at some point. 

```{r}
#| label: tbl-mappedin-prelim-fsplit
#| tbl-cap: "**Part of Table 6.** Comparison group is only PINs in same FIRMs that were updated that were never in an SFHA."

df_prep |> filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000 )  |>
  
  feols(log(sale_price) ~ sw(addedto_prelim_sfha*in_lomr) | pin + sale_year,
        fsplit= ~pre_date_chr,
       # subset = ~pre_date > "2010-01-01" ,
        cluster = ~pin
        
  ) |> modelsummary(stars = TRUE)



basemodel_added_fullsample <- df_prep |> filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                           treat_year_remove_eff == 10000 & treat_year_remove_prelim == 10000 )  |>
feols(log(sale_price) ~ addedto_prelim_sfha | pin + sale_year) 

#colnames(modelsummary::get_gof(basemodel_removed_fullsample))

modelsummary(
  list(
    "Clustered by PIN" = basemodel_added_fullsample,
    "Clustered by Parcel" = basemodel_added_fullsample,
    "Clustered by Muni" = basemodel_added_fullsample
  ),
  vcov = list(
    ~pin,
    ~pin10,
    ~clean_name
  ),
  gof_map = c("nobs", "r.squared", "adj.r.squared", "rmse"), # Customize which GOF statistics to show
  stars = TRUE
)


```


**Removed from SFHA compared to properties that were still in the SFHA**. Comparison group excludes properties that were never in the SFHA and those that were added to the SFHA at some point. 

```{r}
#| label: tbl-mappedout-prelim-fsplit
#| tbl-cap: "Comparison group is only PINs in same FIRMs that were updated."
#| eval: false


df_prep |> filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000)  |>
feols(log(sale_price) ~ sw(removedfrom_prelim_sfha*change_type) | pin + sale_year,
     # data = df_prep,
   #  subset = ~eff_date_chr != "2008-08-19",
      cluster = ~pin + clean_name,
      fsplit= ~pre_date_chr
) |> modelsummary(stars = TRUE)
```






```{r}
#| label: tbl-mappedout-prelim-fsplit2
#| tbl-cap: "**Part of Table 5. Full sample, removed from SFHA.**Comparison group is only PINs in same FIRMs that were updated. that were always in SFHA"

basemodel_removed_fullsample <- df_prep |> filter(change_type_prelim != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000)  |>
feols(log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year) 


modelsummary(
  list(
    "Clustered by PIN" = basemodel_removed_fullsample,
    "Clustered by Parcel" =  basemodel_removed_fullsample,
    "Clustered by Muni" = basemodel_removed_fullsample
  ),
  vcov = list(
    ~pin,
    ~pin10,
    ~clean_name
  ),
  gof_map = c("nobs", "r.squared", "adj.r.squared", "rmse"), # Customize which GOF statistics to show
  stars = TRUE
)

```


> Only 1 FIRM update resulted in PINs being removed fromthe SFHA (the one in the South-West part of Cook County)


```{r}
#| label: tbl-mappedout-prelim-restricteddfirm
#| tbl-cap: "**Part of Table 5. Restricted sample to DFIRM updated in 2015** Comparison group is only PINs in same FIRMs that were updated. that were always in SFHA"
#| error: true
#| warning: true
#| message: true

df3 <- df_prep |> filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000) 

prelim_twfe <- list( 

  mod1 <- feols(log(sale_price) ~ removedfrom_prelim_sfha*in_lomr| pin + sale_year,
      data = df3,
    subset = ~pre_date_chr == "2015-02-15",
      cluster = ~pin10
)

) 

all_models_formatted_prelim <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted_prelim

```

## Effect of Insurance Requirement

### Effective FIRM Descriptive Stats

```{r recode-df_prep}
#| eval: false

table(df_prep$addedto_eff_sfha)

df_prep <- df_prep |> 
  # pin didn't exist in 2018 but did in 2024, so got considered as mapped out?
  mutate(
    removedfrom_eff_sfha = ifelse(pin10 == "1729309054", "0", removedfrom_eff_sfha),
         )




df_prep$removedfrom_eff_sfha
  
df_prep <- df_prep |>
  
  mutate(
    # so I can subset by FIRM date in later steps
    eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date),
    
    added_in    = addedto_eff_sfha == "MappedIn",
    removed_out = removedfrom_eff_sfha == "MappedOut" & in_lomr != "Received LOMR",
    added_in_prelim    = addedto_prelim_sfha == "MappedIn",
    removed_out_prelim = removedfrom_prelim_sfha == "MappedOut" & in_lomr != "Received LOMR"
  ) |>
  group_by(pin) |>
  mutate(
    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(added_in == TRUE) ), 
                                # & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removed_out== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added ore removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(added_in_prelim == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removed_out_prelim== TRUE), year(pre_date), 10000)
    
    
  ) |>
  ungroup() |>
  mutate(
    
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
    rel_year_add_prelim = ifelse(rel_year_add_prelim == 0 & sale_date < pre_date, -1, rel_year_add_prelim),
    rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000),
    rel_year_remove_prelim = ifelse(rel_year_remove_prelim ==0 & sale_date < pre_date, -1, rel_year_remove_prelim)
    
  ) |>
  mutate(
    qtr  = quarter(sale_date),     # 1..4
    year = year(sale_date),            
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    

    
    # delete once checked that code still works if commented out
   # rel_time = round(lubridate::as.difftime(sale_date - eff_date) / 365), # get it to approximate years from event
  #  time_to_treat = round((sale_date - eff_date)/365)
    )
```

```{r}
#| tbl-cap: "Observations per year. Includes the pre and post treatment sales for those that were added or removed from an EFFECTIVE SFHA"
#| layout-ncol: 2
#| include: false

table(df_prep$sale_year, df_prep$treat_year_add_eff)

table(df_prep$sale_year, df_prep$treat_year_remove_eff)
```


```{r}
#| tbl-cap: "Observations per year. Added to (removed from) Effective SFHA"
#| layout-ncol: 2

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$addedto_eff_sfha[df_prep$sale_year>=2016])

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$removedfrom_eff_sfha[df_prep$sale_year>=2016])
```




```{r}
# eff_date_chr and group_names should have same number of observations. 
table(df_prep$eff_date_chr)
table(df_prep$pre_date_chr)
table(df_prep$group_name_eff)

table(df_prep$addedto_eff_sfha)
table(df_prep$removedfrom_eff_sfha)
```


```{r}
#| tbl-cap: "Properties in South Triad that were removed from SFHA in 2019 and properties in South Triad that were always in the SFHA that were in FIRMs updated in 2019."


df_prep |> filter(Triad == "South" & treat_year_remove_eff == "2019") # all 2019 treatment pins are in South Triad

df_prep |> filter(Triad == "South" & change_type == "Always SFHA" & eff_date_chr == "2019-11-01") 
# change type only exists for effective 
```



- Reminder: Cohort should be fixed for each unit and represent the period when the treatment was received.   
- to get the canonical two-way fixed effects (TWFE) estimates, use interaction command  `i(factor_variable, number variable, reference_period)`    

- `iplot` reports coefficients of variables created with `i()` and only those variables. `coefplot()` would display all coefficients.   

If a PIN is in an SFHA and a LOMR, then the insurance requirement is removed. If measuring capitalization of the flood insurance cost, then whether or not flood insurance would be required for a federally backed mortgage is the key variable. This is what capitalization literature does. 

```{r}
df_prep  |> 
  group_by(sale_year, in_eff_sfha, in_lomr) |> summarize(n = n())

df_prep  |> 
  group_by(sale_year, removedfrom_eff_sfha, in_lomr) |> summarize(n = n())


df_prep  |> group_by(sale_year, ins_req) |> summarize(n=n())
table(df_prep$sale_year, df_prep$ins_req)
```


```{r}
lomr_pins <- res_sales |> filter(lomr_date != 0 ) |> select(pin, lomr_date, sfha2024, sfha2018) |> distinct()


table(lomr_pins$lomr_date)
table(df_prep$removedfrom_eff_sfha)
table(df_prep$in_eff_sfha)
```

```{r}

table(df_prep$sale_year)

df_prep <- df_prep |>
  left_join(lomr_pins) |>
  group_by(pin) |>
  arrange(sale_year) |>
  mutate(
    removed = if_else(dplyr::lag(ins_req == TRUE) & ins_req == FALSE, TRUE, FALSE),
    removed_ever = any(removed, na.rm=TRUE) )|>
  ungroup() |>
  mutate(
    removed_date = if_else(removed_ever==TRUE & lomr_date > eff_date, lomr_date, NA_Date_),
    removed_date = if_else(removed_ever==TRUE & is.na(removed_date), eff_date, removed_date,
        
      #  removed_year = year(remove_date)
 #mutate(
       #  removed_FIRM = ifelse(removed==TRUE  & in_lomr != "Received LOMR", TRUE, FALSE),

       #  removed_LOMR = ifelse(removed==TRUE & in_lomr == "Received LOMR", TRUE, FALSE),

  #) |>
#  removed_year = ifelse(any(removed==TRUE & (lomr_date > eff_date)), lomr_date, eff_date),
          #  max(eff_date[removed==TRUE], lomr_date[removed==TRUE]),
          # removed_FIRM_date = last(eff_date[removed_FIRM == TRUE]),
          # removed_LOMR_year = min(year(lomr_date[removed_LOMR == TRUE]))
  )) |>
  ungroup() |>
  mutate(
  removed_year = if_else(!is.na(removed_date), year(removed_date), NA),
  rel_year_removed = if_else(!is.na(removed_year), as.integer(sale_year - removed_year), -1000))

     #    rel_year_FIRM_removed = round(lubridate::as.difftime(sale_date - removed_FIRM_date) / 365),
     #     rel_year_FIRM_removed = round(lubridate::as.difftime(sale_date - removed_FIRM_date) / 365)
    # ) #|>
 # mutate(across(rel_year_removed, is.infinite, -1000))


# df_prep[duplicated(df_prep),] # 5440 duplicates? from years 2010 to 2014 only.
table(df_prep$lomr_date)

df_prep <- df_prep |> distinct(pin, sale_date, sale_price, .keep_all = TRUE)
```


```{r}
df_prep$removed_year[is.na(df_prep$removed_year)] <- 10000
#df_prep$rel_year_removed[is.na(df_prep$rel_year_removed)] <- -1000
#df_prep$rel_year_removed[is.infinite(df_prep$rel_year_removed)] <- -1000

table(df_prep$removed_date)
table(df_prep$removed_ever)

table(df_prep$removed_year)
table(df_prep$rel_year_removed)

#df_prep$removed_year = as.factor(df_prep$removed_year)

```

```{r}
#| tbl-cap: "Removal of insurance requirement's effect on sale price."
twfe_removed2 = feols(log(sale_price) ~ removed  | 
                      pin + sale_year,   
                    cluster = ~clean_name,
                    data = df_prep#,
                  #  subset = ~ rel_year_removed!= -12
)
twfe_removed2|> etable()

```


### Insurance requirement removed due to LOMRs or Mapped Out of SFHA


```{r}

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed#,
                                      #ref.c = "10000", ref.p = c(-1, -1000)
                                      ) | pin + sale_year,
              cluster = ~clean_name,
              data = df_prep              )
#etable(mod2)
summary(mod2, agg= "att")

twfe_removed= feols(log(sale_price) ~ i(rel_year_removed,  ref =c(-1, -1000 ))  | 
                      pin + sale_year,   
                    cluster = ~clean_name,
                    data = df_prep#,
                             #     subset = ~ rel_year_removed != -12
)

#summary(twfe_removed)
#iplot(twfe_removed)


iplot(list(twfe_removed, mod2), #xlim = c(-8, 8), 
      main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

# switches order color/icon order
# iplot(list(mod2, twfe_removed), 
#       main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
# legend("topleft", col = c(1, 2), pch = c(20, 15), 
#        legend = c("S&A (2020)", "TWFE"))
```

### Excludes PINs that were in LOMRs

```{r}
#| label: excludeslomrs

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed, 
                                      ref.p = c(-1, -1000))  | pin + sale_year,
              cluster= ~pin,
              data = (df_prep |> filter(in_lomr == FALSE))
              )
#modelsummary::modelsummary(mod2, stars = TRUE)
summary(mod2, agg= "att")
# iplot(mod2)

#table(df_prep$in_lomr)
twfe_removed <-  feols(log(sale_price) ~ i(rel_year_removed,
                                           ref =c(-1, -1000 ))  | 
                         pin + sale_year,   
                       cluster = ~pin,
              data = (df_prep |> filter(in_lomr == FALSE))
                     #  subset = ~in_lomr == "Not in LOMR"
)

etable(twfe_removed)
#iplot(twfe_removed)

iplot(list(mod2, twfe_removed), 
      main = "Effect of Removal from SFHA (in_lomr == FALSE)")
legend("topleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("S&A (2020)", "TWFE"))


```



