---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
---
# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.


# Data Sources and Background Information

> TO DO: Fill in missing municipality names. Probably can do by shared assessor neighborhood? or even a spatial join if needed for only the parcels that don't have muni names associated with them. Wouldn't be as big of a computational list for a select list of parcels.

> TO DO: Manually collect the \~2000 flood scores for pins that didn't have them. They are also almost all missing nbhd_code, zip_code, and some are missing clean_name.

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(plm)
library(jtools)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, results = "hold"  )


ff_pairs <- readRDS("data/processed/ff_pairs.rds") |>
  rename(around_event = treated)

df_prep <- readRDS("data/processed/df_prep.rds")

```

> Sales are not winsorized

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.



There are `r n_distinct(ff_pairs$pin)` pins remaining in `ff_pairs`.


There are `r print(ff_pairs |> filter(around_event ==TRUE & high_ff_score == TRUE) |> count())` observations that are around_event and have a high flood factor score (greater than 4).

```{r}
table(ff_pairs$sale_year_t2, ff_pairs$change_type)
```

## Descriptive Stats

::: panel-tabset
### df_prep Descriptive Stats

```{r descriptive-stats-df_prep}
#| column: page
skim(df_prep)
```


### ff_pairs Descriptive Stats

```{r descriptive-stats-ff_pairs}
#| column: page
skim(ff_pairs)
```


:::


## Parallel Trends Assumptions


::: panel-tabset
### Not Logged Sales Price

```{r}
#| column: page
#| layout-ncol: 2
#| message: false
df_prep <- df_prep |> filter(!is.na(Triad))


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   #   geom_text(aes(label = n), vjust = -1, size = 3) + 
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep). \n Sales is NOT winsorized or logged.")

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 
#    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)")


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep). \n Sales is NOT winsorized or logged.") +
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```

```{r include = FALSE, eval=FALSE}
# code from MVH
# not tested

library(fixest)

# df columns assumed: y (your chosen transform), x (running var), year, id
didrd_pretest <- function(df, y, x, year, id, cutoff, T0, h, poly = 1, cl = NULL
                          ){
  d <- df[abs(df[[x]] - cutoff) <= h, ]
  d$right <- as.integer(d[[x]] >= cutoff)

  fml <- as.formula(paste0(
    y, " ~ right + ",
    "poly(", x, ",", poly, ")+poly(", x, ",", poly, "):right + ",
    "i(", year, ") + ",
    "i(", year, ", right, ref=", T0 - 1, ") | ",
    id
  ))
  m <- feols(fml, data = d, cluster = cl)

  pre_years <- sort(unique(d[[year]][d[[year]] < T0]))
  # joint test: all pre-year deviations from the base pre-year = 0
  w <- wald(m, paste0("i(", year, ", right)::", pre_years[pre_years != (T0 - 1)]))
  list(model = m, pretrend_p = w$p.value, wald = w)
}

# Run on levels / log1p / asinh using the SAME h
didrd_pretest(df_prep, "sale_price",  "dist", "sale_year", "pin", 2020, 2019, h = 5)
# didrd_pretest(df, "log1p_sales", "dist", "yr", "pin", 0, 2019, h = 5)
# didrd_pretest(df, "asinh_sales","dist","yr","pin",0, 2019, h = 5)





# Local RD × DiD pretrend check, narrated.
didrd_pretest <- function(
  df, y, x, year, id,
  cutoff, T0, h,
  poly = 1,
  cluster = NULL,
  verbose = TRUE
){
  # 1) Enforce that column names are strings
  #    because we’re doing non-standard evaluation below.
  stopifnot(is.character(c(y, x, year, id)))

  # 2) Keep only observations within bandwidth h around the cutoff
  #    because RD logic only makes sense locally near the threshold.
  d <- subset(df,
              is.finite(df[[y]]) & is.finite(df[[x]]) &
              abs(df[[x]] - cutoff) <= h)

  # 3) Indicator for being on the right side of the cutoff
  #    because treatment/exposure flips at the boundary.
  d$right <- as.integer(d[[x]] >= cutoff)

  # 4) Build the regression in parts so the “why” is clear.
  #    (a) poly(x, poly) + poly(x, poly):right
  #        because we allow different smooth trends in the running variable
  #        on each side of the cutoff (local polynomial RD control).
  run_side <- sprintf("poly(%s,%d) + poly(%s,%d):right", x, poly, x, poly)

  #    (b) i(year)
  #        because we need time fixed effects to net out common shocks.
  time_fe  <- sprintf("i(%s)", year)

  #    (c) i(year, right, ref = T0-1)
  #        because we want an event-study of right vs. left
  #        with the last pre-treatment year as the base.
  evt      <- sprintf("i(%s, right, ref=%s)", year, T0 - 1)

  #    (d) | id
  #        because unit fixed effects soak up time-invariant differences.
  fe_part  <- id

  # Full formula:
  #    y ~ right + {RD polynomials by side} + {time FE} + {event study} | {unit FE}
  # The “right” main effect is the post-baseline difference-in-levels at the base year.
  fml_str  <- sprintf("%s ~ right + %s + %s + %s | %s", 
                      y, run_side, time_fe, evt, fe_part)
  fml      <- as.formula(fml_str)

  # 5) Cluster by unit by default
  #    because serial correlation within units is expected.
  cl <- if (is.null(cluster)) as.formula(paste0("~", id)) else cluster

  if (verbose) {
    cat("\n================ Model Specification (human-readable) ================\n")
    cat("Outcome:\n  ", y, "\n\n", sep = "")
    cat("Local window:\n  |", x, " - ", cutoff, "| <= ", h, "\n\n", sep = "")
    cat("Key terms & WHY:\n")
    cat("  right                                 # because treatment flips at the cutoff; captures side difference at base year\n")
    cat("  poly(", x, ",", poly, ")              # because we control for smooth trend in running variable (left side)\n", sep = "")
    cat("  poly(", x, ",", poly, "):right        # because we allow a different trend on the right side (RD by side)\n", sep = "")
    cat("  i(", year, ")                         # because time FE remove common shocks across both sides\n", sep = "")
    cat("  i(", year, ", right, ref=", T0 - 1, ")  # because event-study: right vs. left by year (base = last pre year)\n", sep = "")
    cat("  | ", id, "                            # because unit FE remove time-invariant unit heterogeneity\n\n", sep = "")
    cat("Null we test (parallel pretrends, locally):\n")
    cat("  All pre-treatment coefficients from i(", year, ", right, ...) equal 0 (except the base year).\n\n", sep = "")
    cat("Full fixest formula:\n  ", fml_str, "\n", sep = "")
    cat("======================================================================\n\n")
  }

  # 6) Estimate
  m <- feols(fml, data = d, cluster = cl)

  # 7) Collect all pre-treatment years
  pre_years <- sort(unique(d[[year]][d[[year]] < T0]))

  # 8) Joint Wald: all pre-treatment right-side deviations = 0 (ex base year)
  test_terms <- paste0("i(", year, ", right)::", pre_years[pre_years != (T0 - 1)])
  w <- if (length(test_terms)) wald(m, test_terms) else NULL

  # 9) Return
  list(
    model      = m,
    window_n   = nrow(d),
    pre_years  = pre_years,
    wald_terms = test_terms,
    pretrend_p = if (is.null(w)) NA_real_ else w$p.value,
    wald       = w
  )
}
```

### Parallel Trends assumption for all sales

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") 

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
     #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)")



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
    #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
     #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      #geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
     #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, in_eff_sfha) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
    #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") 

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
    group_by(sale_year, in_eff_sfha) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
    #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") 



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, in_eff_sfha, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
     # geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, in_eff_sfha, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
      #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, in_eff_sfha, Triad) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, in_eff_sfha, Triad) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
     #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, in_eff_sfha) |> 
  summarise(asinh_price = mean(asinh(sale_price)),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
    #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by SFHA Status") 

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
    group_by(sale_year, in_eff_sfha) |> 
  summarise(asinh_price = mean(asinh(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
    #  geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by SFHA Status") 



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(asinh_price = mean(asinh(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   #   geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
    scale_x_continuous(breaks = c(2010,  2015, 2020), limits = c(2009,2021 ) ) + 

  labs(title = "Pre-Treatment Trends by SFHA Status") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(asinh_price = mean(asinh(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
    #    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
      scale_x_continuous(breaks = c(2020, 2024), limits = c(2019,2025 ) ) + 

  labs(title = "Post-Treatment Trends by SFHA Status",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)




```

### Testing slopes 

```{r}
#| layout-ncol: 1
#| label: tbl-notloggedDV

slopes1 <- lm(sale_price ~ high_ff_score*event*sale_year, data = df_prep)

modelsummary::modelsummary(
  slopes1,
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)


```


```{r}
#| label: tbl-loggedDV


slopes1 <- lm(log(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)

modelsummary::modelsummary(
  slopes1,
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

slopes3 <- lm(asinh(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)

modelsummary::modelsummary(
  slopes3,
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)


```

**sale_year:in_eff_sfha**\
If not statistically significant, then I fail to reject the null hypothesis --> there is no evidence of different pre-treatment trends between properties that were in and out of SFHAs.

**sale_year:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.



```{r}
#| layout-ncol: 2
#| column: page
#| message: false

ggplot(df_prep |> filter(!is.na(high_ff_score)), aes(x = sale_year, y = log(sale_price), color = high_ff_score)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by High Flood Factor",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "High FF Score",
        caption = "Dataset: All Sales (df_prep)"

  ) +
  theme_minimal()

ggplot(df_prep |> 
         filter(!is.na(in_eff_sfha)), aes(x = sale_year, y = log(sale_price), color = in_eff_sfha)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event
             ) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by SFHA Status",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "In SFHA",
    caption = "Dataset: All Sales (df_prep)"
  ) +
  theme_minimal()
```


:::


```{r}
missing_ff_score <- df_prep |> filter(is.na(high_ff_score) | is.na(in_eff_sfha))

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)


df_prep <- df_prep |> 
  filter(!is.na(high_ff_score))
```


```{r}

df_prep |> 
    filter(sale_year > 2015) |>     # just to have roughly the same number of years on both sides of the event
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )

df_prep |> 
  filter(sale_year > 2015) |>
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )


```



Properties with high flood score but no SFHA
- "02014000171053" = "1354 whispering springs Palatine IL" Parcel is a "condo" but a bunch of detached homes around a pond. Flood score is 7. Has a parcel inside of it (1733 EMERALD BAY 5, PALATINE, IL 60074) with a FF=6 that IS in a FEMA flood zone. Not sure if there was a specific pin divisin for this reason 
)

```{r}

df_prep |> filter(high_ff_score == FALSE & in_eff_sfha == "SFHA") |> 
  mutate(parcel = str_sub(pin, 1, 10)) |> distinct(parcel, in_eff_sfha, high_ff_score)

# Not in SFHA
"01014050100000" = "804 division st, barrington IL"
"01021000330000"  = "7 Marmon LN Barringonton IL"
"02013020771280" = "2 Dundee Quarter 302 Palatine IL" # considered condo but its all detached homes or townhomes. AND IN A LOMR
"0102300012" = "221 Oakdene Drive Barrington" # only land barely touches SFHA

"0216410003" = "25 North Clyde Avenue, Palatine, IL, 60067, USA" # actually has a flood factor of 5

"1505117011" = "100 S Roberta AVe Northlake" # parcel boundary touches SFHA but not house

"1504117057" = "1642 N 39th Ave Stone Park" # score of 6, is in SFHA
"1505205013" = "1652 43RD AVE, STONE PARK, IL 60165" # has a flood score of 7! and is in SFHA
```


# Models

```{r}
#| label: trial-removelomrs
#| eval: false

# would filter out pins that had LOMRs
df_prep <- df_prep |> 
  filter(in_lomr == "Not in LOMR") |> group_by(pin) |> 
  mutate(times_sold = n()) |> filter(times_sold > 1) |> ungroup()

```


```{r}
#| include: false

df_prep <- df_prep |> 
  mutate(in_sfha = ifelse(in_eff_sfha == "SFHA", 1, 0))

df_prep |>
  group_by(in_sfha) |>
  summarize(mean = mean(env_flood_fs_factor, na.rm = T),
            sd = sd(env_flood_fs_factor, na.rm = T))
```

::: panel-tabset
## DV = Logged Sale Price


```{r}
#| label: tbl-models-forDFM2
#| tbl-cap: "feols() command. Exported with export_summs() DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  # high_ff_score shouldn't change at PIN level. Variable drops out. 
  #   "I" = feols(log(sale_price) ~ high_ff_score | pin + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
              panel.id = "pin",
              
              data = df_prep,
              cluster = ~ clean_name
              
  ),
  "II.5" = feols(log(sale_price) ~ high_ff_score*event*in_lomr*in_prelim_sfha | pin+sale_year,
               data = df_prep,
               cluster = ~ clean_name

  ),
  "III" = feols(log(sale_price) ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
                              vcov = "hetero" 

  ),
  
  "IV" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event  | pin + sale_year,
               panel.id = "pin",
               data = df_prep,
                             vcov = "hetero"
  ) ,
  
  "IV" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event*in_lomr  | pin + sale_year,
               panel.id = "pin",
               data = df_prep,
                                            vcov = "hetero"

  )
)

# 
# cm2 <- c(
#   
#   'Post Event' = 'event2.Post',
#   'High FF Score x Post Event' = 'high_ff_scoreTRUE:event2.Post',
#   'In Preliminary SFHA' = 'in_prelim_sfhaSFHA',
#   'High FF Score x In Prelim SFHA' = 'high_ff_scoreTRUE:in_prelim_sfhaSFHA',
#   'In Effective SFHA' = 'in_eff_sfhaSFHA',
#   'In Eff. SFHA x Post Event' = 'in_eff_sfhaSFHA:event2.Post',
#   'In SFHA, High FF Score & Post Event' = 'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2.Post',
#   'In Prelim SFHA & Post Event' = 'event2.Post:in_prelim_sfhaSFHA',
#   'In Prelim SFHA, High FF Score & Post Event' = 'high_ff_scoreTRUE:event2.Post:in_prelim_sfhaSFHA'
# )
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", "Data Release and Year Dummies", "Preliminary SFHA", "Effective SFHA"),
#              robust = "HC3"#,               coefs = cm
# 
#              #statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              )





cm = c(
  'event2. Post' = 'Post Event',
  'in_lomrLOMR' = 'Has LOMR',
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',

  'in_prelim_sfhaSFHA' = 'In Preliminary SFHA',  
  'event2.Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'in_prelim_sfhaSFHA:event2.Post' = 'In Prelim SFHA & Post Event',

  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',

  'in_eff_sfhaSFHA'= 'In Effective SFHA',
  'in_eff_sfhaSFHA:event2. Post' = 'In Eff. SFHA x Post Event',
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',

  'high_ff_ScoreTRUE:in_eff_sfhaSFHA' = 'In Eff. SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_ScoreTRUE' = 'In Eff. SFHA x High FF Score',

  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event'
  
)


all_models_formatted <- modelsummary::msummary(
  merriman_models,
  fmt = function(x) round(x, 2),
  stars = TRUE,
  coef_map = cm
  )

all_models_formatted

```

```{r}
#| label: tbl-models-forDFM2-
#| tbl-cap: "feols() command. Exported with msummary() DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025. Without pretty labels." 
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  # high_ff_score shouldn't change at PIN level. Variable drops out. 
  #   "I" = feols(log(sale_price) ~ high_ff_score | pin + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
              panel.id = "pin",
              
              data = df_prep,
              cluster = ~ clean_name
              
  ),
  # "II.5" = feols(log(sale_price) ~ high_ff_score*event + factor(sale_year) | pin,
  #              data = df_prep,
  #              cluster = ~ clean_name
  #              
  # ),
  "III" = feols(log(sale_price) ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
               # cluster = ~ clean_name
                              vcov = "hetero" 

  ),
  
  "IV" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event  | pin + sale_year,
               panel.id = "pin",
               
               data = df_prep,
                             vcov = "hetero"
  ) 
)





all_models_formatted <- modelsummary::msummary(
  merriman_models,
  fmt = function(x) round(x, 2),
  stars = TRUE
  )

all_models_formatted

```


## DV = Sales Price (not logged!)


```{r}
#| label: tbl-models-forDFM2-nonlogged
#| tbl-cap: "feols() command. Exported with export_summs() DV is sale_price NOT LOGGED. Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  
  #   "I" = feols(sale_price ~ high_ff_score | pin  + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(sale_price ~ event*high_ff_score | pin + sale_year,

              data = df_prep,
              cluster = ~ clean_name
              
  ),
  # "II.5" = feols(sale_price ~ event + factor(sale_year) | pin,
  #              data = df_prep,
  #              cluster = ~ clean_name
  #              
  # ),
  "III" = feols(sale_price ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
                              vcov = "hetero" 

  ),
  
  "IV" = feols(sale_price ~ high_ff_score*event*in_eff_sfha  | pin + sale_year,

               data = df_prep,
                             vcov = "hetero"
  ) 
)

# cm2 <- c(
#   "Post Event" = "event2. Post",
#   "High FF Score x Post Event" = "event2. Post:high_ff_scoreTRUE",
#   
#   "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
#   "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
#   
#   "In Effective SFHA" = "in_eff_sfhaSFHA",
#  # "In Eff. SFHA x Post Event" = "in_eff_sfhaSFHA:event2. Post",
#   "In SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",
#   "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
#   "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
# )
# 
# 
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", 
#                            #  "Data Release and Year Dummies", 
#                              "Preliminary SFHA", 
#                            "Effective SFHA"),
#           #   robust = "HC3", #, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              coefs = cm2
#              )



cm3 = c(
  'event2. Post' = 'Post Event',
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',
  
  'in_prelim_sfhaSFHA' = 'In Preliminary SFHA',
  'event2.Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',

  
  'in_eff_sfhaSFHA'= 'In Effective SFHA',
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',
  'high_ff_scoreTRUE:in_eff_sfhaSFHA' = 'In Effective SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event',
  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event'
)

all_models_formatted <- modelsummary::msummary(merriman_models,

           #    output = "flextable",
          #  fmt = function(x) round(x, 2),
            fmt = function(x) scales::comma(x, big.mark = ",", accuracy = 1),


             stars = TRUE,
          coef_map = cm3
          )

all_models_formatted
```


_A panelmodel object contains: coefficients, residuals, fitted.values, vcov, df.residual and call and functions that extract these elements are provided._ 


```{r}
#| label: tbl-models-forDFM2-PLM
#| tbl-cap: "PLM package! DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left

merriman_models <- list(

  "II" = plm(log(sale_price) ~ in_eff_sfha,
              index = c("pin", "sale_year"),
                 effect = "twoway",

              data = df_prep
              
  ),
  "II" = plm(log(sale_price) ~ event,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
               
  ),
    "III" = plm(log(sale_price) ~ high_ff_score*event*in_eff_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              ),

  "IV" = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
              )

  )

cm <- c(
  "Post Event" = "event2. Post",
#  "High FF Score x Post Event" = "event2. Post:high_ff_scoreTRUE",
    "High FF Score x Post Event" = "high_ff_scoreTRUE:event2. Post",

  "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
  "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
  
  "In Effective SFHA" = "in_eff_sfhaSFHA",
 # "In Eff. SFHA x Post Event" = "in_eff_sfhaSFHA:event2. Post",
  "In SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",
  "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
  "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
)


export_summs(merriman_models,
             model.names = c("Just SFHA", "Post FF Data Release", "Add Effective SFHA", "Add Prelim SFHA Identifier"),
             coefs = cm
            # robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))
)
# all_models_formatted <- modelsummary::modelsummary(merriman_models,
# 
#            #    output = "flextable",
#              fmt = function(x) round(x, 2), coef_map = cm,
#              stars = TRUE)
# 
# all_models_formatted

```


### Distribution of Sale Prices

```{r}
ggplot(df_prep, aes(x = sale_price)) +
      geom_histogram(#binwidth = 0.1, 
                     fill = "skyblue", color = "black") +
      labs(title = "Sale Price  Distribution",
           x = "$",
           y = "Frequency") +
      theme_minimal() 

ggplot(df_prep, aes(x = log(sale_price))) +
      geom_histogram(#binwidth = 0.1, 
                     fill = "skyblue", color = "black") +
      labs(title = "Logged Sale Price  Distribution",
           x = "$",
           y = "Frequency") +
      theme_minimal()
```


```{r residuals, include = FALSE, eval = FALSE}
mod1_fe = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data1 <- broom::augment(mod1_fe, data = df_prep)
    

ggplot(fitted_data1, aes(x = .resid)) +
      geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  



mod2_fe = plm(sale_price ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data2 <- broom::augment(mod2_fe, data = df_prep)
    

ggplot(fitted_data2, aes(x = .resid)) +
      geom_histogram(binwidth = 100000, 
                     fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  

```


## Annualized Price Change

```{r}
#| label: tbl-models-forDFM1V2
#| tbl-cap: "Models for Merriman: Repeat Sales Data Structure. DV = Annualized Change in Sale Price. 1 observation in data represents two sales."
#| tbl-cap-location: top
#| layout-ncol: 2


merriman_models <- list(
  
  
  "I" = feols(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn | sale_year_t2,
              data = ff_pairs,
              vcov = "hetero"
  ),
  "II" = feols(ann_d_log_price ~ high_ff_score*around_event + in_sfha_t1 + in_sfha_t2 + years_btwn | sale_year_t2,
               data = ff_pairs,
               cluster = ~clean_name
               
  ))

export_summs(merriman_models,
             model.names = c("3-way interaction", "FF Score * Data Release"))

models <- list(
  
  "III" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + years_btwn,
                data = ff_pairs,
                cluster = ~clean_name
                
  ),
     
  "III" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + years_btwn + Triad | sale_year_t2,
                data = ff_pairs,
                cluster = ~clean_name
  
))

export_summs(models,
             model.names = c( "Other SFHAvariables", "Adds triad"),
             robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
             )
# 
# all_models_formatted <- modelsummary::modelsummary(merriman_models,
#                                                    
#                                                    output = "flextable",
#                                                    fmt = function(x) round(x, 2),
#                                                    stars = TRUE)
# 
# all_models_formatted

```



## Muni Fixed Effects, DV = ln(p)

**using df_prep**

> Put it into some year's dollars. Convert to common dollar for sales.

```{r}
#| label: tbl-models-with-dfprep
#| tbl-cap: "A 'high' flood factor score is a score of 5 or higher. Sales after the 'event' are coded as 'Post' event, which is coded as June 2020 when the scores were released. The interaction of a high flood factor score and being post event is a key variable to look at. Year Fixed Effects are probably necessary due to the growth in sales prices during and after COVID. The last column has PIN, municipality, and sales year fixed effects."
#| column: page-left


  all_models <- list(
    
    "High or Low" = list(

      "I" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep
                    
      ),
     "muni & year fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name + sale_year,
                    data = df_prep
                    
      )
      

    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-dfprep-ffscorerelease
#| tbl-cap: "Uses sales data `df_prep`."


  all_models <- list(
    
    "High or Low" = list(

      
      "PIN & Sale Year FE" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
                    data = df_prep,

      ),
      
      
      "Triad Interaction" = feols(log(sale_price) ~ high_ff_score*event*Triad | pin + sale_year,
                    data = df_prep,

      ), 

         "4way Interaction" = feols(log(sale_price) ~ high_ff_score*event*in_eff_sfha*Triad | pin + clean_name + sale_year,
                    data = df_prep,

      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```




 ## Repeat Sales

```{r}
#| column: page
#| label: tbl-simplified-repeatsales-ffscores-plm
#| tbl-cap: "PLM output: Uses repeat_sales `ff_pairs`."
#| eval: false
#| include: false



  all_models <- list(
    
    "d_log_price" = list(
      
      "III" = plm(d_log_price ~ high_ff_score*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs

      
      )),
        "Annualized Change P" = list(

      "I" = plm(ann_d_log_price ~ high_ff_score*around_event + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs

      ),

            "Ann Change P" = plm(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs
                  ),

      # keeps only sales that bracket the event. No longer would need around_event in the equation
      "Around Event Only" = plm(ann_d_log_price ~ high_ff_score*change_type  + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs, 
                    subset = around_event == TRUE,
      ),

      
      "Hetero SE" = plm(ann_d_log_price ~ high_ff_score*around_event  + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs,
                    ),

      "Repeat Repeat Sales (pin FE)" = plm(ann_d_log_price ~ high_ff_score*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                  model = "within",
                    data = ff_pairs,
      )
      )
    
    )
  
  
  export_summs(merriman_models,
            # model.names = c("FF Score Indicator", "FF Score * Data Release", "Data Release and Year Dummies", "3-way nteraction", "3-way interaction with muni FE"),
            # robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
             )
  
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted


```

```{r}
#| column: page
#| label: tbl-simplified-repeatsales-ffscores
#| tbl-cap: "Feols Package: Uses repeat_sales `ff_pairs`. "


  all_models <- list(
    
    "d_log_price" = list(
      
      "III" = feols(d_log_price ~ high_ff_score*around_event + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      
      )),
        "Annualized Change P" = list(

      "I" = feols(ann_d_log_price ~ high_ff_score*around_event | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~sale_year_t2
                    
      ),

      "Ann Change P" = feols(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    vcov = "hetero"      ),

      # keeps only sales that bracket the event. No longer would need around_event in the equation
      "Around Event Only" = feols(ann_d_log_price ~ high_ff_score*change_type  + years_btwn | sale_year_t2,
                    data = (ff_pairs |> group_by(pin) |> filter(n() > 1)) ,
                    vcov = "hetero"
      ),

      
      "Hetero SE" = feols(ann_d_log_price ~ high_ff_score*around_event  + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    vcov = "hetero"
                    ),

      "Repeat Repeat Sales (pin FE)" = feols(ann_d_log_price ~ high_ff_score*around_event + years_btwn | pin + sale_year_t2,
                    data = (ff_pairs |> group_by(pin) |> filter(n() > 1)) ,
                    cluster = ~clean_name
      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted


```


```{r}
#| column: page
#| label: tbl-proposal-models-ffscores
#| tbl-cap: "Model in proposal. Uses repeat_sales `ff_pairs`."


  all_models <- list(
    

      # "I" = feols(d_log_price ~ high_ff_score,       
      #             data = ff_pairs,
      #             cluster = ~pin
      # ),
      # 
      # "II" = feols(d_log_price ~ change_type,       
      #              data = ff_pairs,
      #              cluster = ~pin
      #              
     # ),
      "Controls for Risk" = feols(d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      ),
      
            "Controls for Risk - Annualized" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      ),
            "Annualized w SFHA indicators" = feols(ann_d_log_price ~ high_ff_score*around_event + in_sfha_t1 + in_sfha_t2 + factor(sale_year_t2) + years_btwn,
                    data = ff_pairs,
                    cluster = ~clean_name
                  
      ),
      
                  "Annualized sfha interactions" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + factor(sale_year_t2) + years_btwn,
                    data = ff_pairs,
                    cluster = ~clean_name
                  
      )
  )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
            # shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```



```{r}
#| column: page
#| label: tbl-fixedeffects-models-ffscores
#| tbl-cap: "Categorical or Ordinal Risk Scores and then adding some Controls"


  all_models <- list(
    
    "High or Low" = list(

      "Categorical FF" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + sale_year_t2,
                    data = ff_pairs,
                  cluster = ~clean_name
      )
      , 
       "Risk Controlled" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor + sale_year_t2,
                    data = ff_pairs,
                  cluster = ~ clean_name)
                  , 
      
       "Risk Controlled & Muni FE" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor + sale_year_t2 | clean_name,
                    data = ff_pairs
      ),
      
       "Ordinal FF" = feols(ann_d_log_price ~ env_flood_fs_factor*around_event*change_type  + sale_year_t2 | clean_name,
                    data = ff_pairs
                    
      )
    ))
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

:::
