---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
---
# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.


# Data Sources and Background Information

> TO DO: Fill in missing municipality names. Probably can do by shared assessor neighborhood? or even a spatial join if needed for only the parcels that don't have muni names associated with them. Wouldn't be as big of a computational list for a select list of parcels.

> TO DO: Manually collect the \~2000 flood scores for pins that didn't have them. They are also almost all missing nbhd_code, zip_code, and some are missing clean_name.

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(plm)
library(jtools)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, results = "hold"  )

```

> Sales are not winsorized

```{r warning = FALSE, message = FALSE}
#df_pairs <- readRDS("data/processed/df_pairs.RDS") 

ff_pairs <- readRDS("data/processed/ff_pairs.rds") |>
  rename(around_event = treated)

df_prep <- readRDS("data/processed/df_prep.rds")

```

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.



There are `r n_distinct(ff_pairs$pin)` pins remaining in `ff_pairs`.


There are `r print(ff_pairs |> filter(around_event ==TRUE & high_ff_score == TRUE) |> count())` observations that are around_event and have a high flood factor score (greater than 4).

```{r}
table(ff_pairs$sale_year_t2, ff_pairs$change_type)
```

## Descriptive Stats

::: panel-tabset
### df_prep Descriptive Stats

```{r descriptive-stats-df_prep}
#| column: page
skim(df_prep)
```


### ff_pairs Descriptive Stats

```{r descriptive-stats-ff_pairs}
#| column: page
skim(ff_pairs)
```
```{r}
ggplot() + 
  geom_histogram(data = ff_pairs, aes( x = ann_d_log_price), bins = 100) + theme_classic()

ggplot() + 
  geom_histogram(data = ff_pairs, aes( x = d_log_price), bins = 100) + theme_classic()
```


:::


## Parallel Trends Assumptions


::: panel-tabset
### Not Logged Sales Price

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep). \n Sales is NOT winsorized or logged.")

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)")


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep). \n Sales is NOT winsorized or logged.") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```


### Parallel Trends assumption for all sales

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") 

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score) |> 
  summarise(mean_growth = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)")



df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(mean_growth = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```

```{r}

slopes1 <- lm(log(sale_price) ~ high_ff_score*event*factor(sale_year), data = df_prep)


slopes2 <- lm(log(sale_price) ~ in_eff_sfha*event*factor(sale_year), data = df_prep)


modelsummary::modelsummary(
  list(slopes1, slopes2),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

**sale_date:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.

```{r}
#| layout-ncol: 2
#| column: page
#| message: false

ggplot(df_prep |> filter(!is.na(high_ff_score)), aes(x = sale_year, y = log(sale_price), color = high_ff_score)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by High Flood Factor",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "High FF Score",
        caption = "Dataset: All Sales (df_prep)"

  ) +
  theme_minimal()

ggplot(df_prep |> 
         filter(!is.na(in_eff_sfha)), aes(x = sale_year, y = log(sale_price), color = in_eff_sfha)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event
             ) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by SFHA Status",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "In SFHA",
    caption = "Dataset: All Sales (df_prep)"
  ) +
  theme_minimal()
```


### Parallel trends test for repeat sales

DV is change in logged price.

```{r}
#| layout-ncol: 2
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released &
              !is.na(ff_factor)) |> 
    group_by(sale_year_t1, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n() ) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type", 
       caption = "Dataset: Repeat Sales") 


ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
           !is.na(ff_factor)) |>
  group_by(sale_year_t2, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type", caption = "Dataset: Repeat Sales")
```

```{r}
#| column: page
#| layout-ncol: 3
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year_t1, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 < new_info_released & sale_year_t2 > 2015 &
            !is.na(high_ff_score)) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
             n = n() ) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends for 2nd sale by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")
```


Is testing the assumption on repeat sales actually right to do or should I just use all sales?? I feel like it should be all sales.

```{r}

slopes1<- lm(d_log_price ~ sale_year_t2*around_event*high_ff_score, data = ff_pairs)

slopes2 <- lm(d_log_price ~ sale_year_t2*around_event*change_type, data = ff_pairs)

modelsummary::modelsummary(
  list(slopes1, slopes2),
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

Parallel trends not super supported in either model for repeat sales?
:::


```{r}
missing_ff_score <- df_prep |> filter(is.na(high_ff_score) | is.na(in_eff_sfha))

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(n = n(), 
            distinct_pins = n_distinct(pin),
            avg_log_price = mean(log(sale_price), na.rm=TRUE))

df_prep |> 
    filter(!is.na(high_ff_score)) |>
    filter(!is.na(in_eff_sfha)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(n = n(), 
                        distinct_pins = n_distinct(pin),

            avg_price = mean(sale_price, na.rm=TRUE))

df_prep <- df_prep |> 
  filter(!is.na(high_ff_score))
```


# Models



```{r}
#| include: false

df_prep <- df_prep |> 
  mutate(in_sfha = ifelse(in_eff_sfha == "SFHA", 1, 0))

df_prep |>
  group_by(in_sfha) |>
  summarize(mean = mean(env_flood_fs_factor, na.rm = T),
            sd = sd(env_flood_fs_factor, na.rm = T))
```

::: panel-tabset
## Models for Merriman


```{r}
#| label: tbl-models-forDFM2
#| tbl-cap: "feols() command. Exported with export_summs() DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  # high_ff_score shouldn't change at PIN level. Variable drops out. 
  #   "I" = feols(log(sale_price) ~ high_ff_score | pin + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
              panel.id = "pin",
              
              data = df_prep,
              cluster = ~ clean_name
              
  ),
  # "II.5" = feols(log(sale_price) ~ high_ff_score*event + factor(sale_year) | pin,
  #              data = df_prep,
  #              cluster = ~ clean_name
  #              
  # ),
  "III" = feols(log(sale_price) ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
               # cluster = ~ clean_name
                              vcov = "hetero" 

  ),
  
  "IV" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event  | pin + sale_year,
               panel.id = "pin",
               
               data = df_prep,
                             vcov = "hetero"
  ) 
)

# 
# cm2 <- c(
#   
#   'Post Event' = 'event2.Post',
#   'High FF Score x Post Event' = 'high_ff_scoreTRUE:event2.Post',
#   'In Preliminary SFHA' = 'in_prelim_sfhaSFHA',
#   'High FF Score x In Prelim SFHA' = 'high_ff_scoreTRUE:in_prelim_sfhaSFHA',
#   'In Effective SFHA' = 'in_eff_sfhaSFHA',
#   'In Eff. SFHA x Post Event' = 'in_eff_sfhaSFHA:event2.Post',
#   'In SFHA, High FF Score & Post Event' = 'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2.Post',
#   'In Prelim SFHA & Post Event' = 'event2.Post:in_prelim_sfhaSFHA',
#   'In Prelim SFHA, High FF Score & Post Event' = 'high_ff_scoreTRUE:event2.Post:in_prelim_sfhaSFHA'
# )
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", "Data Release and Year Dummies", "Preliminary SFHA", "Effective SFHA"),
#              robust = "HC3"#,               coefs = cm
# 
#              #statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              )





cm = c(
  'event2. Post' = 'Post Event',
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',

  'in_prelim_sfhaSFHA' = 'In Preliminary SFHA',  
  'event2.Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'in_prelim_sfhaSFHA:event2.Post' = 'In Prelim SFHA & Post Event',

  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',

  'in_eff_sfhaSFHA'= 'In Effective SFHA',
  'in_eff_sfhaSFHA:event2. Post' = 'In Eff. SFHA x Post Event',
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',

  'high_ff_ScoreTRUE:in_eff_sfhaSFHA' = 'In Eff. SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_ScoreTRUE' = 'In Eff. SFHA x High FF Score',

  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event'
  
)


all_models_formatted <- modelsummary::msummary(
  merriman_models,
  fmt = function(x) round(x, 2),
  stars = TRUE,coef_map = cm
  )

all_models_formatted

```


## Not Logged Sales Price


```{r}
#| label: tbl-models-forDFM2-nonlogged
#| tbl-cap: "feols() command. Exported with export_summs() DV is sale_price NOT LOGGED. Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  
  #   "I" = feols(sale_price ~ high_ff_score | pin  + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(sale_price ~ event*high_ff_score | pin + sale_year,

              data = df_prep,
              cluster = ~ clean_name
              
  ),
  # "II.5" = feols(sale_price ~ event + factor(sale_year) | pin,
  #              data = df_prep,
  #              cluster = ~ clean_name
  #              
  # ),
  "III" = feols(sale_price ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
                              vcov = "hetero" 

  ),
  
  "IV" = feols(sale_price ~ high_ff_score*event*in_eff_sfha  | pin + sale_year,

               data = df_prep,
                             vcov = "hetero"
  ) 
)

# cm2 <- c(
#   "Post Event" = "event2. Post",
#   "High FF Score x Post Event" = "event2. Post:high_ff_scoreTRUE",
#   
#   "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
#   "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
#   
#   "In Effective SFHA" = "in_eff_sfhaSFHA",
#  # "In Eff. SFHA x Post Event" = "in_eff_sfhaSFHA:event2. Post",
#   "In SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",
#   "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
#   "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
# )
# 
# 
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", 
#                            #  "Data Release and Year Dummies", 
#                              "Preliminary SFHA", 
#                            "Effective SFHA"),
#           #   robust = "HC3", #, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              coefs = cm2
#              )



cm3 = c(
  'event2. Post' = 'Post Event',
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',
  
  'in_prelim_sfhaSFHA' = 'In Preliminary SFHA',
  'event2.Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',

  
  'in_eff_sfhaSFHA'= 'In Effective SFHA',
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',
  'high_ff_scoreTRUE:in_eff_sfhaSFHA' = 'In Effective SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event',
  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event'
)

all_models_formatted <- modelsummary::msummary(merriman_models,

           #    output = "flextable",
          #  fmt = function(x) round(x, 2),
            fmt = function(x) scales::comma(x, big.mark = ",", accuracy = 1),


             stars = TRUE,
          coef_map = cm3
          )

all_models_formatted
```


_A panelmodel object contains: coefficients, residuals, fitted.values, vcov, df.residual and call and functions that extract these elements are provided._ 


```{r}
#| label: tbl-models-forDFM2-PLM
#| tbl-cap: "PLM package! DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left

merriman_models <- list(

  "II" = plm(log(sale_price) ~ in_eff_sfha,
              index = c("pin", "sale_year"),
                 effect = "twoway",

              data = df_prep
              
  ),
  "II" = plm(log(sale_price) ~ event,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
               
  ),
    "III" = plm(log(sale_price) ~ high_ff_score*event*in_eff_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              ),

  "IV" = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
              )

  )

cm <- c(
  "Post Event" = "event2. Post",
#  "High FF Score x Post Event" = "event2. Post:high_ff_scoreTRUE",
    "High FF Score x Post Event" = "high_ff_scoreTRUE:event2. Post",

  "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
  "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
  
  "In Effective SFHA" = "in_eff_sfhaSFHA",
 # "In Eff. SFHA x Post Event" = "in_eff_sfhaSFHA:event2. Post",
  "In SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",
  "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
  "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
)


export_summs(merriman_models,
             model.names = c("Just SFHA", "Post FF Data Release", "Add Effective SFHA", "Add Prelim SFHA Identifier"),
             coefs = cm
            # robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))
)
# all_models_formatted <- modelsummary::modelsummary(merriman_models,
# 
#            #    output = "flextable",
#              fmt = function(x) round(x, 2), coef_map = cm,
#              stars = TRUE)
# 
# all_models_formatted

```

### Residuals

```{r}

mod1_fe = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data <- broom::augment(mod1_fe, data = df_prep)
    

ggplot(fitted_data, aes(x = .resid)) +
      geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  



mod2_fe = plm(sale_price ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data <- broom::augment(mod2_fe, data = df_prep)
    

ggplot(fitted_data, aes(x = .resid)) +
      geom_histogram(binwidth = 100000, 
                     fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  

```


## Annualized Price Change

```{r}
#| label: tbl-models-forDFM1V2
#| tbl-cap: "Models for Merriman: Repeat Sales Data Structure. DV = Annualized Change in Sale Price. 1 observation in data represents two sales."
#| tbl-cap-location: top
#| layout-ncol: 2


merriman_models <- list(
  
  
  "I" = feols(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn | sale_year_t2,
              data = ff_pairs,
              vcov = "hetero"
  ),
  "II" = feols(ann_d_log_price ~ high_ff_score*around_event + in_sfha_t1 + in_sfha_t2 + years_btwn | sale_year_t2,
               data = ff_pairs,
               cluster = ~clean_name
               
  ))

export_summs(merriman_models,
             model.names = c("3-way interaction", "FF Score * Data Release"))

models <- list(
  
  "III" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + years_btwn,
                data = ff_pairs,
                cluster = ~clean_name
                
  ),
     
  "III" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + years_btwn + Triad | sale_year_t2,
                data = ff_pairs,
                cluster = ~clean_name
  
))

export_summs(models,
             model.names = c( "Other SFHAvariables", "Adds triad"),
             robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
             )
# 
# all_models_formatted <- modelsummary::modelsummary(merriman_models,
#                                                    
#                                                    output = "flextable",
#                                                    fmt = function(x) round(x, 2),
#                                                    stars = TRUE)
# 
# all_models_formatted

```



## Using All Sales Data - Not just Repeat Sales

**using df_prep**

> Put it into some year's dollars. Convert to common dollar for sales.

```{r}
#| label: tbl-models-with-dfprep
#| tbl-cap: "A 'high' flood factor score is a score of 5 or higher. Sales after the 'event' are coded as 'Post' event, which is coded as June 2020 when the scores were released. The interaction of a high flood factor score and being post event is a key variable to look at. Year Fixed Effects are probably necessary due to the growth in sales prices during and after COVID. The last column has PIN, municipality, and sales year fixed effects."
#| column: page-left


df_prep2 <- df_prep |> filter(times_sold > 1)

  all_models <- list(
    
    "High or Low" = list(

      "I" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep,
                  cluster = ~pin + clean_name
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "pin fes" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "2 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin+ clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ high_ff_score*event | pin + clean_name + sale_year,
                                         panel.id = "pin",

                       data = df_prep2,
                  cluster = ~ clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin + clean_name + sale_year,
                      panel.id = "pin",
                    data = df_prep2,
                  cluster = ~ clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin + clean_name + sale_year,
                                            panel.id = "pin",

                    data = df_prep2,
                  cluster = ~pin + clean_name
                    
      )
    
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-dfprep-ffscorerelease
#| tbl-cap: "Uses sales data `df_prep`."


  all_models <- list(
    
    "High or Low" = list(
      
      "PIN FE" = feols(log(sale_price) ~ high_ff_score*event | pin ,       
                  data = df_prep,
      ),
                   
      "No FE" = feols(log(sale_price) ~ high_ff_score*event,
                    data = df_prep,
                    cluster = ~pin + clean_name
                    
      ),
      
      "PIN & Sale Year FE" = feols(log(sale_price) ~ high_ff_score*event | sale_year + pin,
                    data = df_prep2,

      ),
      
      
      "Control for Triad" = feols(log(sale_price) ~ high_ff_score*event*Triad | sale_year + pin,
                    data = df_prep2,

      ), 
            "3 FEs" = feols(log(sale_price) ~ high_ff_score*event*Triad | pin + clean_name+ sale_year,
                    data = df_prep2,

      ),
         "With SFHA" = feols(log(sale_price) ~ high_ff_score*event*in_eff_sfha | pin + clean_name + sale_year,
                    data = df_prep2,

      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```




## Repeat Sales

```{r}
#| column: page
#| label: tbl-simplified-repeatsales-ffscores-plm
#| tbl-cap: "PLM output: Uses repeat_sales `ff_pairs`."
#| eval: false
#| include: false



  all_models <- list(
    
    "d_log_price" = list(
      
      "III" = plm(d_log_price ~ high_ff_score*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs

      
      )),
        "Annualized Change P" = list(

      "I" = plm(ann_d_log_price ~ high_ff_score*around_event + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs

      ),

            "Ann Change P" = plm(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs
                  ),

      # keeps only sales that bracket the event. No longer would need around_event in the equation
      "Around Event Only" = plm(ann_d_log_price ~ high_ff_score*change_type  + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs, 
                    subset = around_event == TRUE,
      ),

      
      "Hetero SE" = plm(ann_d_log_price ~ high_ff_score*around_event  + years_btwn + factor(sale_year_t2),
                  index = "pin",
                    data = ff_pairs,
                    ),

      "Repeat Repeat Sales (pin FE)" = plm(ann_d_log_price ~ high_ff_score*around_event + years_btwn + factor(sale_year_t2),
                  index = "pin",
                  model = "within",
                    data = ff_pairs,
      )
      )
    
    )
  
  
  export_summs(merriman_models,
            # model.names = c("FF Score Indicator", "FF Score * Data Release", "Data Release and Year Dummies", "3-way nteraction", "3-way interaction with muni FE"),
            # robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
             )
  
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted


```

```{r}
#| column: page
#| label: tbl-simplified-repeatsales-ffscores
#| tbl-cap: "Feols Package: Uses repeat_sales `ff_pairs`. "


  all_models <- list(
    
    "d_log_price" = list(
      
      "III" = feols(d_log_price ~ high_ff_score*around_event + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      
      )),
        "Annualized Change P" = list(

      "I" = feols(ann_d_log_price ~ high_ff_score*around_event | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~sale_year_t2
                    
      ),

      "Ann Change P" = feols(ann_d_log_price ~ high_ff_score*change_type*around_event + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    vcov = "hetero"      ),

      # keeps only sales that bracket the event. No longer would need around_event in the equation
      "Around Event Only" = feols(ann_d_log_price ~ high_ff_score*change_type  + years_btwn | sale_year_t2,
                    data = (ff_pairs |> group_by(pin) |> filter(n() > 1)) ,
                    vcov = "hetero"
      ),

      
      "Hetero SE" = feols(ann_d_log_price ~ high_ff_score*around_event  + years_btwn | sale_year_t2,
                    data = ff_pairs,
                    vcov = "hetero"
                    ),

      "Repeat Repeat Sales (pin FE)" = feols(ann_d_log_price ~ high_ff_score*around_event + years_btwn | pin + sale_year_t2,
                    data = (ff_pairs |> group_by(pin) |> filter(n() > 1)) ,
                    cluster = ~clean_name
      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted


```


```{r}
#| column: page
#| label: tbl-proposal-models-ffscores
#| tbl-cap: "Model in proposal. Uses repeat_sales `ff_pairs`."


  all_models <- list(
    

      # "I" = feols(d_log_price ~ high_ff_score,       
      #             data = ff_pairs,
      #             cluster = ~pin
      # ),
      # 
      # "II" = feols(d_log_price ~ change_type,       
      #              data = ff_pairs,
      #              cluster = ~pin
      #              
     # ),
      "Controls for Risk" = feols(d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      ),
      
            "Controls for Risk - Annualized" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor,
                    data = ff_pairs,
                    cluster = ~clean_name
                    
      ),
            "Annualized w SFHA indicators" = feols(ann_d_log_price ~ high_ff_score*around_event + in_sfha_t1 + in_sfha_t2 + factor(sale_year_t2) + years_btwn,
                    data = ff_pairs,
                    cluster = ~clean_name
                  
      ),
      
                  "Annualized sfha interactions" = feols(ann_d_log_price ~ high_ff_score*around_event*in_sfha_t1*in_sfha_t2 + factor(sale_year_t2) + years_btwn,
                    data = ff_pairs,
                    cluster = ~clean_name
                  
      )
  )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
            # shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```



```{r}
#| column: page
#| label: tbl-fixedeffects-models-ffscores
#| tbl-cap: "Categorical or Ordinal Risk Scores and then adding some Controls"


  all_models <- list(
    
    "High or Low" = list(

      "Categorical FF" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + sale_year_t2,
                    data = ff_pairs,
                  cluster = ~clean_name
      )
      , 
       "Risk Controlled" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor + sale_year_t2,
                    data = ff_pairs,
                  cluster = ~ clean_name)
                  , 
      
       "Risk Controlled & Muni FE" = feols(ann_d_log_price ~ high_ff_score*around_event*change_type + env_flood_fs_factor + sale_year_t2 | clean_name,
                    data = ff_pairs
      ),
      
       "Ordinal FF" = feols(ann_d_log_price ~ env_flood_fs_factor*around_event*change_type  + sale_year_t2 | clean_name,
                    data = ff_pairs
                    
      )
    ))
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

:::

# Robustness Checks

## Risk Score as Categorical Variable

```{r}
#| label: tbl-categoricalrisk
#| tbl-cap: "Repeat Sales data structure. DV is change in logged price."
#| eval: false


# eval set to false
all_models = list(

"Risk Score as Factor" = list(
    
      
      "Muni FE" = feols(d_log_price ~ ff_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
         "Muni FE" = feols(d_log_price ~ ff_factor*change_type*around_event | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      "No FE" = feols(d_log_price ~ ff_factor*change_type*around_event,       
                   data = ff_pairs,
                  cluster = ~clean_name
                    
      )
      ,
      "Sale Year FE" = feols(d_log_price ~ ff_factor*change_type*around_event | sale_year_t2,       
                   data = ff_pairs,
                  cluster = ~clean_name
                    
      )
    
    )
)

all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```

## Risk Score as Ordinal Variable - Repeat sales

```{r}
#| label: tbl-ordinalrisk
#| tbl-cap: "Repeat Sales data structure. DV is change in logged price."
#| eval: false

# eval set to false
model_list <- list(
        "No FEs" = list(
      
      "I" = feols(d_log_price ~ change_type+ env_flood_fs_factor*around_event,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ env_flood_fs_factor*in_sfha_t2*in_sfha_t2*around_event,       
                   data = ff_pairs,
                   cluster = ~pin
                    
      )),
        "FEs" = list(
      
      "Muni FE" = feols(d_log_price ~ change_type*around_event + env_flood_fs_factor*around_event | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "Muni Fe" = feols(d_log_price ~ env_flood_fs_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      
      "Sold >3 Times, PIN FE" = feols(d_log_price ~ env_flood_fs_factor*change_type | pin,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name           
      )
    )
        )

all_models_formatted <- modelsummary::modelsummary(model_list,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```
