---
title: "Question1_continued_staggered"
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
  #  warning: false
   # message: false
    error: true
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(plm)    # panel linear models. interchangable with fixest but have different syntax for models
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
```

```{r}
# made in Q1_final_variables 
# uses land parcel intersections with SFHA polygons
df_prep <- readRDS("data/processed/df_prep_forQ1_assumptiontests.RDS") 

res_sales <- readRDS("./data/processed/df_allsales.rds")
```


```{r}
table(df_prep$pre_date)

table(df_prep$treat_year_add_prelim)
table(df_prep$addedto_prelim_sfha[df_prep$pre_date_chr == "2021-09-22"])

```


```{r remove-missingvalues}


res_sales <- res_sales |>
    filter(!pin10 %in% drop_parcels) |>

  filter(
    !is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date) &
           !is.na(Triad)
         )

```


## Staggered Policy Rollout Methods

### Preliminary FIRMS

#### Added to Preliminary


```{r}
#| label: fig-feolscomparison-prelimfirms-restricted
#| fig-cap: "**Appendix Item:Restricted Sample - Added to Preliminary SFHA** Information shock = preliminary FIRM."
#| results: hold


est_twfe = feols(log(sale_price) ~ i(rel_year_add_prelim,  ref =c(-1, -1000 )) | 
                  pin + sale_year, 
                cluster = ~pin10, 
                data = df_prep |> filter(change_type != "Always SFHA" & treat_year_remove_prelim == 10000))
#summary(est_did)
 
est_sa = feols(log(sale_price) ~ sunab(cohort = treat_year_add_prelim, period = rel_year_add_prelim, ref.p = c(-1,-1000)) | 
               pin + sale_year,
             cluster= ~pin10,
             data = df_prep |> filter(change_type != "Always SFHA" & treat_year_remove_prelim == 10000))

# modelsummary::modelsummary(mod1,
#                output = "flextable",
#                fmt = function(x) round(x, 2),
#              stars = TRUE)

iplot(list(est_twfe, est_sa), main = "Mapped into Prelim FIRMs")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)")) 
```

```{r}
#| layout-ncol: 2
summary(est_sa, agg = "ATT")
summary(est_sa, agg = "cohort")
```


#### Removed from preliminary

```{r}
#| label: fig-removeprelims
#| fig-cap: "Removed from Preliminary SFHA and added LOMR Fixed Effects"
#| results: hold

est_sa = feols(log(sale_price) ~ sunab(cohort = treat_year_remove_prelim, period = rel_year_remove_prelim, ref.p = c(-1,-1000) ) | pin + sale_year^pre_date_chr + in_lomr,
               cluster= ~pin10,
               data = df_prep)

# modelsummary::modelsummary(est_sa,
#                            output = "flextable",
#                            fmt = function(x) round(x, 2),
#                            stars = TRUE)
# coefplot(est_sa)


est_twfe = feols(log(sale_price) ~ i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
                   pin + sale_year^pre_date_chr + in_lomr, cluster = ~pin10, 
                 data = df_prep )

# 
# prelim_noLOMRPINs = feols(log(sale_price) ~ i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
#                             pin + sale_year,   
#                           cluster = ~clean_name,
#                           subset = ~in_lomr == "Not in LOMR" & !is.na(clean_name),
#                           data = df_prep)


iplot(list(est_twfe, est_sa), main = "Removed from Prelim, Controls for LOMRs")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)")) 
```

```{r}
#| layout-ncol: 2
summary(est_sa, agg = "ATT")
summary(est_sa, agg = "cohort")
```

```{r}
#| label: fig-removeprelims-restricted
#| fig-cap: "**Appendix Item: Restricted sample, Removed from Preliminary SFHA**. Does not control for LOMR status"
#| results: hold


est_sa = feols(log(sale_price) ~  sunab(cohort = treat_year_remove_prelim, period = rel_year_remove_prelim) | pin + sale_year^pre_date_chr,
               cluster= ~pin10,
               data = df_prep |> filter(treat_year_add_prelim==10000 & change_type != "Never SFHA"))

# modelsummary::modelsummary(est_sa,
#                            output = "flextable",
#                            fmt = function(x) round(x, 2),
#                            stars = TRUE)
# coefplot(est_sa)


est_twfe = feols(log(sale_price) ~  i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
                   pin + sale_year^pre_date_chr, cluster = ~pin10, 
                 data = df_prep |> filter(treat_year_add_prelim==10000 & change_type != "Never SFHA") )

# 
# prelim_noLOMRPINs = feols(log(sale_price) ~ i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
#                             pin + sale_year,   
#                           cluster = ~clean_name,
#                           subset = ~in_lomr == "Not in LOMR" & !is.na(clean_name),
#                           data = df_prep)


iplot(list(est_twfe, est_sa), main = "Removed from Prelim, FE have cohort-time FE")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))
```

```{r}
#| layout-ncol: 2
summary(est_sa, agg = "ATT")
summary(est_sa, agg = "cohort")
```




```{r}
#| label: fig-removeprelims-restricted-controlforLOMRs
#| fig-cap: "**Appendix Item: Restricted sample, Removed from Preliminary SFHA**. Controls for LOMR status"
#| results: hold

est_sa = feols(log(sale_price) ~  in_lomr + sunab(cohort = treat_year_remove_prelim, period = rel_year_remove_prelim) | pin + sale_year,
               cluster= ~pin10,
               data = df_prep |> filter(treat_year_add_prelim==10000 & change_type != "Never SFHA"))

# modelsummary::modelsummary(est_sa,
#                            output = "flextable",
#                            fmt = function(x) round(x, 2),
#                            stars = TRUE)
# coefplot(est_sa)


est_twfe = feols(log(sale_price) ~ in_lomr +  i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
                   pin + sale_year, cluster = ~pin10, 
                 data = df_prep |> filter(treat_year_add_prelim==10000 & change_type != "Never SFHA") )

# 
# prelim_noLOMRPINs = feols(log(sale_price) ~ i(rel_year_remove_prelim,  ref =c(-1, -1000 )) | 
#                             pin + sale_year,   
#                           cluster = ~clean_name,
#                           subset = ~in_lomr == "Not in LOMR" & !is.na(clean_name),
#                           data = df_prep)


iplot(list(est_twfe, est_sa ), main = "Removed from Prelim, controls for LOMRs")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))
```

```{r}
#| layout-ncol: 2
summary(est_sa, agg = "ATT")
summary(est_sa, agg = "cohort")
```



### Callaway and Sant'Anna

```{r}
#| eval: false


library(did)

df_prep_cs <- df_prep |> 
  mutate(log_price = log(sale_price),
         pin_num = as.numeric(pin),
         treat_year_remove = ifelse(is.na(treat_year_remove), 0 , treat_year_remove)) |>
  filter(change_type != "Always SFHA")

attgt <- att_gt(yname = "log_price",
                        tname = "sale_year",
                        idname = "pin_num",
                        gname = "treat_year_remove",
                        data = df_prep_cs,
                allow_unbalanced_panel = TRUE
                        )
  
summary(attgt) 
saveRDS(attgt, file = "outputs/attgt_Q1_didoutput.rds")

did_graph <- ggdid(attgt)
did_graph

aggte_output_simp <- aggte(attgt, type = "simple", na.rm=TRUE)
summary(aggte_output_simp)

aggte_output_dynamic <- aggte(attgt, type = "dynamic", na.rm = TRUE)
summary(aggte_output_dynamic)
ggdid(aggte_output_dynamic)

agg_group <- aggte(attgt, type = "group", na.rm=TRUE)
ggdid(agg_group)
```



### Effective FIRMs

#### Removedfrom Effective FIRM

```{r}
#| layout-ncol: 2
#| results: hold

eff_hasLOMRPINs = feols(log(sale_price) ~ sunab(cohort = treat_year_remove_eff, period = sale_year)  | 
                         pin + sale_year,   
                       cluster = ~pin10,
                       subset = ~ rel_year_remove_eff > -7 | rel_year_remove_eff == -1000,
                       data = df_prep)

summary(eff_hasLOMRPINs)
coefplot(eff_hasLOMRPINs)
summary(eff_hasLOMRPINs, agg = "ATT")
summary(eff_hasLOMRPINs, agg = "cohort")
iplot(eff_hasLOMRPINs, main = "Removed from Eff SFHAs. TWFE & S&A20.")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("S&A (2020)"))

```

```{r}
#| label: fig-removedfromeffective-models 
#| fig-cap: "TWFE to compare with sunab() output. Uses Effective FIRM dates and year relative to treatment year. Does not control for LOMR status. Excludes sales that happened 7 or more years before removal from SFHA."
#| results: hold

eff_hasLOMRPINs = feols(log(sale_price) ~ i(rel_year_remove_eff,  ref =c(-1, -1000 ))  | 
                         pin + sale_year^pre_date_chr,   
                       cluster = ~pin10,
                       subset = ~ rel_year_remove_eff > -7 | rel_year_remove_eff == -1000,
                       data = df_prep)
#summary(eff_hasLOMRPINs)
  
est_sa_haslomrs = feols(log(sale_price) ~ sunab(treat_year_remove_eff, rel_year_remove_eff) | 
                         pin + sale_year, 
                       cluster = ~pin10,
                       subset = ~ rel_year_remove_eff > -7 | rel_year_remove_eff == -1000,
                       data = df_prep)
#summary(est_sa_haslomrs)

iplot(list(eff_hasLOMRPINs, est_sa_haslomrs), main = "Removed from Eff SFHAs. TWFE & S&A20.")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

# coefplot(eff_hasLOMRPINs)
# coefplot(est_sa_haslomrs)

# feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
#                      cluster = ~ pin + clean_name,
#                      data = df_prep) |> modelsummary()
```


```{r}
#| label: fig-feolscomparison-removedfromfirms 
#| fig-cap: "TWFE to compare with sunab() output. Uses Effective FIRM dates and year relative to treatment year. Controls for LOMR status with `in_lomr` variable in model"
#| results: hold

eff_hasLOMRPINs = feols(log(sale_price) ~ in_lomr  + i(rel_year_remove_eff,  ref =c(-1, -1000 ))  | 
                         pin + sale_year,   
                       cluster = ~pin10,
                       data = df_prep)
#summary(eff_hasLOMRPINs)

est_sa_haslomrs = feols(log(sale_price) ~ in_lomr  + sunab(treat_year_remove_eff, rel_year_remove_eff) | 
                         pin + sale_year, 
                       cluster = ~pin10,
                       data = df_prep)
#summary(est_sa_haslomrs)

iplot(list(eff_hasLOMRPINs, est_sa_haslomrs), main = "Removed from Eff SFHAs. TWFE & S&A20. ")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

# coefplot(eff_hasLOMRPINs)
# coefplot(est_sa_haslomrs)

# feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
#                      cluster = ~ pin + clean_name,
#                      data = df_prep) |> modelsummary()
```


```{r}
#| tbl-cap: "Models control for LOMR status."
#| layout-ncol: 2

summary(est_sa_haslomrs, agg = "ATT")
summary(est_sa_haslomrs, agg = "cohort")
```

**Removed from Effective - Excludes LOMR PINs by using `in_lomr` == FALSE**

```{r}
#| label: fig-feolscomparison-removedfromfirms-nolomrs
#| fig-cap: "TWFE to compare with sunab() output. Uses Effective FIRM dates and year relative to treatment year. Excludes PINs that had LOMRs!"
#| message: false
#| warning: false
#| results: hold

eff_noLOMRPINs = feols(log(sale_price) ~ i(rel_year_remove_eff,  ref =c(-1, -1000 ))  | 
                         pin + sale_year,   
                       cluster = ~pin10,
                       subset = ~in_lomr == FALSE & !is.na(clean_name),
                       data = df_prep)
summary(eff_noLOMRPINs)
#iplot(eff_noLOMRPINs)

est_sa_nolomrs = feols(log(sale_price) ~ sunab(treat_year_remove_eff, rel_year_remove_eff) | 
                         pin + sale_year, 
                       cluster = ~pin10,
                       subset = ~in_lomr == FALSE & !is.na(clean_name),
                       data = df_prep)
summary(est_sa_nolomrs, agg = "cohort")

iplot(list(eff_noLOMRPINs, est_sa_nolomrs), main = "Removed from Eff SFHAs. Excludes LOMR PINs from model.")
# 
# feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,
#                      cluster = ~ pin + clean_name,
#                        subset = ~in_lomr == FALSE & !is.na(clean_name),
#                      data = df_prep) |> modelsummary()
```


```{r}
#| tbl-cap: "Uses in_lomr==FALSE PINs only."
#| layout-ncol: 2

summary(est_sa_nolomrs, agg = "ATT")
summary(est_sa_nolomrs, agg = "cohort")
```



```{r}
#| label: fig-changereferenceyear2
#| fig-cap: "SA20. Changes reference year from -1 to -2 for Added to Effective SFHA."
#| eval: false
#| include: false

mod1 = feols(log(sale_price) ~ sunab(treat_year_add_eff, rel_year_add_eff) | pin + sale_year, 
                          cluster = ~pin10,

  data = df_prep)

#summary(mod1)
mod2 = feols(log(sale_price) ~ sunab(cohort = treat_year_add_eff, period = rel_year_add_eff, ref.p = c(-2,-1000)) | pin + sale_year, 
             cluster = ~pin10,
  data = df_prep)

#summary(mod2)
#iplot(mod1)

iplot(list(mod1, mod2), main = "Reference year as -1 and -2, Added to Eff.")

summary(mod2, agg = "ATT")
summary(mod2, agg = "cohort")
```


#### Added to Effective SFHA 

```{r}
#| label: tbl-feolscomparison-addedtofirms-effective
#| fig-cap: "Mapped into Effective SFHA. In_lomr variable in equation"
#| results: hold

est_twfe = feols(log(sale_price) ~ in_lomr + i(rel_year_add_eff,  ref =c(-1, -1000 )) | 
                  pin + sale_year,   
                cluster = ~pin10,
                data = df_prep)
#coefplot(est_twfe)

est_sa = feols(log(sale_price) ~ in_lomr +  sunab(treat_year_add_eff, rel_year_add_eff) | pin + sale_year, 
                           cluster = ~ pin10,
               data = df_prep)
#coefplot(est_sa)


iplot(list(est_twfe, est_sa), main = "Mapped into Effective SFHA")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

```

```{r}
#| layout-ncol: 2
#etable(est_sa)
#summary(est_sa)
summary(est_sa, agg = "ATT")
summary(est_sa, agg = "cohort")
```



# Transaction trends

## Volume

```{r}
res_sales |>
  group_by(sale_year, change_type, eff_date) |>  
  summarize(n_txn = n(), .groups = "drop") |>  # number of transactions
  ggplot(aes(x = sale_year, y = n_txn, color = change_type)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    x = "Year of Sale",
    y = "Number of Transactions",
    color = "Property Type",
    title = "Number of Transactions by SFHA & Flood Factor Status"
  ) +
  theme_minimal() +
  theme(legend.position = "top") + 
  facet_wrap(~eff_date)



res_sales |>
  group_by(sale_year, change_type, eff_date) |> 
  summarize(n_txn = n(), .groups = "drop") |>
  mutate(indexed = n_txn / n_txn[sale_year==2012], .by = c(change_type, eff_date)) |>
  ggplot(aes(x = sale_year, y = indexed, color = change_type)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    x = "Year of Sale",
    y = "Transactions indexed to 2012 volume",
    color = "Property Type",
    title = "Number of Transactions by SFHA & Flood Factor Status"
  ) +
  theme_minimal() +
  theme(legend.position = "top") + 
  facet_wrap(~eff_date) +
  scale_y_continuous(labels=scales::percent)


```

```{r}
res_sales |>
  mutate(
    ff_label = ifelse(high_ff_score, "High FF", "Low FF"),
    sfha_label = ifelse(in_eff_sfha == "SFHA", "In SFHA", "Not in SFHA"),
    group = paste(ff_label, sfha_label, sep = " & ")
  ) |>
  group_by(sale_year, group) |>   # replace sale_year with your actual year variable
  summarize(n_txn = n(), .groups = "drop") |>
  ggplot(aes(x = sale_year, y = n_txn, color = group)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    x = "Year of Sale",
    y = "Number of Transactions",
    color = "Property Type",
    title = "Number of Transactions by SFHA & Flood Factor Status"
  ) +
  theme_minimal() +
  theme(legend.position = "top")

```

## Indexed Volume of Sales

```{r}
res_sales |>
  mutate(
    ff_label = ifelse(high_ff_score, "High FF", "Low FF"),
    sfha_label = ifelse(in_eff_sfha == "SFHA", "In SFHA", "Not in SFHA"),
    group = paste(ff_label, sfha_label, sep = " & ")
  ) |>
  group_by(sale_year, group) |>
  summarize(n_txn = n(), .groups = "drop") |>
  group_by(group) |>
  mutate(
    base2012 = n_txn[sale_year == 2012],
    index2012 = n_txn / base2012
  ) |>
  ggplot(aes(x = sale_year, y = index2012, color = group)) +
  geom_line(size = 1) +
  geom_point() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Year of Sale",
    y = "Indexed Transactions (2012 = 100%)",
    color = "Property Type",
    title = "Relative Change in Transactions by SFHA & Flood Factor Status"
  ) +
  theme_minimal() +
  theme(legend.position = "top")

```

```{r}

# 1) Build a quarterly decimal from sale_date
res_q <- res_sales |>
  mutate(
    # ensure Date
    sale_date = as.Date(sale_date),
    year  = year(sale_date),
    qtr   = quarter(sale_date),                 # 1..4
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    ff_label  = ifelse(high_ff_score, "High FF", "Low FF"),
    sfha_label = ifelse(in_eff_sfha == "SFHA", "In SFHA", "Not in SFHA"),
    group = paste(ff_label, sfha_label, sep = " & "),
    time_year = sale_year - 2010
  ) |>
  group_by(sale_qtr_dec, group) |>
  summarise(n_txn = n(), .groups = "drop")

# (Optional) Fill missing quarters with 0 so lines don’t break
res_q <- res_q |>
  group_by(group) |>
  complete(sale_qtr_dec = seq(floor(min(sale_qtr_dec, na.rm = TRUE)),
                              ceiling(max(sale_qtr_dec, na.rm = TRUE)) - 0.75,
                              by = 0.25),
           fill = list(n_txn = 0)) |>
  ungroup()

# 2A) Plot raw quarterly counts
p_counts <- res_q |>
  ggplot(aes(x = sale_qtr_dec, y = n_txn, color = group)) +
  geom_line(size = 0.9) +
  geom_point(size = 1.6) +
  scale_x_continuous(
    breaks = seq(floor(min(res_q$sale_qtr_dec, na.rm = TRUE)),
                 ceiling(max(res_q$sale_qtr_dec, na.rm = TRUE)),
                 by = 1),
    labels = function(x) sprintf("%d", x)  # show clean years on ticks
  ) +
  labs(
    x = "Sale Quarter (decimal years)",
    y = "Number of Transactions",
    color = "Property Type",
    title = "Quarterly Transactions by SFHA & Flood Factor Status"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")

p_counts

# Choose base quarter explicitly: 2012 Q1 (i.e., 2012.00)
res_q_idx <- res_q |>
  group_by(group) |>
  mutate(
    base_val = n_txn[sale_qtr_dec == 2012.00],
    index_2012q1 = ifelse(is.na(base_val) | base_val == 0, NA_real_, n_txn / base_val)
  ) |>
  ungroup()

p_index <- res_q_idx |>
  ggplot(aes(x = sale_qtr_dec, y = index_2012q1, color = group)) +
  geom_line(size = 0.9) +
  geom_point(size = 1.6) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_x_continuous(
    breaks = seq(floor(min(res_q_idx$sale_qtr_dec, na.rm = TRUE)),
                 ceiling(max(res_q_idx$sale_qtr_dec, na.rm = TRUE)),
                 by = 1),
    labels = function(x) sprintf("%d", x)
  ) +
  labs(
    x = "Sale Quarter (decimal years)",
    y = "Indexed Transactions (2012 Q1 = 100%)",
    color = "Property Type",
    title = "Relative Quarterly Change by SFHA & Flood Factor (2012 Q1 = 100%)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")

p_index

```

```{r}
res_q_idx_season <- res_q |>
  mutate(
    year = floor(sale_qtr_dec),                          # extract year
    qtr  = 1 + (sale_qtr_dec - year) * 4                 # recover quarter (1–4)
  ) |>
  group_by(group, qtr) |>
  mutate(
    base_val = n_txn[year == 2012],                      # use 2012's value for that quarter
    rel_index = ifelse(is.na(base_val) | base_val == 0,
                       NA_real_,
                       n_txn / base_val)
  ) |>
  ungroup()

ggplot(res_q_idx_season, aes(x = sale_qtr_dec, y = rel_index, color = group)) +
  geom_line(size = 0.9) +
  geom_point(size = 1.6) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Sale Quarter (decimal years)",
    y = "Indexed Transactions (2012 Quarter = 100%)",
    color = "Property Type",
    title = "Relative Quarterly Change (Seasonally Indexed to 2012)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")
```

## Transaction volume for properties outside of SFHAs

```{r}
#| label: fig-floodfactorcomparison
#| fig-cap: "Figure for Question 2. Will move it to correct file eventually."

ggplot(res_q_idx_season |> filter(group %in% c("High FF & Not in SFHA","Low FF & Not in SFHA")), aes(x = sale_qtr_dec, y = rel_index, color = group)) +
  geom_line(size = 0.9) +
  geom_point(size = 1.6) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Sale Quarter (decimal years)",
    y = "Indexed Transactions (2012 Quarter = 100%)",
    color = "Property Type",
    title = "Relative Quarterly Change (Seasonally Indexed to 2012)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")

```

```{r}
#| label: fig-FIRMupdates
#| fig-cap: "Indexed transaction volume for properties outside of SFHA. Shown by geographic areas (based on FIRM effective dates). Uses df_prep which has PINs that sold 2+ times instead of all residentialsales."

res_sales |>
  mutate(
    ff_label = ifelse(high_ff_score, "High FF", "Low FF"),
    sfha_label = ifelse(in_eff_sfha == "SFHA", "In SFHA", "Not in SFHA"),
    group = paste(ff_label, sfha_label, sep = " & ")
  ) |>
    filter(group %in% c("High FF & Not in SFHA","Low FF & Not in SFHA")) |>

  group_by(group, eff_date, sale_year) |>
  summarize(n_txn = n()) |>
  ungroup() |>
  group_by(group, eff_date) |>
  mutate(
    base2012 = n_txn[sale_year == 2012],
    index2012 = n_txn / base2012) |>
  ungroup() |>
  ggplot(aes(x = sale_year, y = index2012, color = group), group = eff_date) +
  geom_line(size = 0.9) +
  geom_point(size = 1.6) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Sale Year",
    y = "Indexed Transactions (2012  = 100%)",
    color = "Property Type",
    title = "Relative Yearly Change (Seasonally Indexed to 2012)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top") +
  facet_wrap(~eff_date)

```


