---
title: "Parallel Trends Graphs for Q2"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
---



```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(plm)
library(jtools)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


df_prep <- readRDS("data/processed/df_prep_buildings.rds") |>
  select(-c(clean_name.x, clean_name.y))

df_prep <- df_prep |> 
  # 282 PINs in 2022 were sold as part of a new Condo in Schaumburg 
  # (parcel = 0710101038). Condo building has high flood factor score. 
  # Looks like it is now apartments? 21 Kristin Drive.  DROPPED

  filter(pin10 != "0710101038") |>
  mutate(log_price = log(sale_price)) |> 
  filter(!is.na(Triad) & Triad != "NA")

```


```{r remove-missingvalues}
df_prep <- df_prep |>
  filter(
    !is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date) &
           !is.na(Triad)
         )
``` 


```{r}
df_prep |> 
  mutate(period = if_else(sale_date < new_info_released, "1.Pre", "2.Post")) |> 
  group_by(period, sale_year, in_eff_sfha, Triad) |> 
  summarise(avg_price = mean(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = avg_price, color = in_eff_sfha)) +
  geom_point() +
  geom_line() +
    geom_vline(xintercept=2020, lty = 2) +

  geom_smooth(aes(linetype = period), method = "lm", se = FALSE) +
  facet_wrap(~Triad) +
  labs(title = "Pre- and Post-Event Slopes by Triad and SFHA Status",
       caption = "",
       x = NULL, y = "Avg. Logged Sale Price") +
  scale_x_continuous(breaks = seq(2010,2025,5))+
  theme_classic()+
  theme(legend.position = "bottom") 

```

```{r}


df_prep |> 
  mutate(period = if_else(sale_date < new_info_released, "1.Pre", "2.Post")) |> 
  group_by(period, sale_year, in_eff_sfha, high_ff_score, Triad ) |> 
  summarise(median_price = median(log_price, na.rm = TRUE),
            n = n(), .groups = "drop") |> 
  ggplot(aes(x = sale_year, y = median_price, color = high_ff_score) ) +
  geom_point() +
  geom_line(alpha = .5) +
    geom_vline(xintercept=2020) +
  facet_wrap(vars(Triad, in_eff_sfha), ncol = 2) +

  geom_smooth(aes(linetype = period), method = "lm", se = FALSE) +
  labs(title = "Pre vs Post Slopes by Triad and FEMA SFHA Status",
       x = NULL, y = "Median Logged Price"       ) +
      scale_y_continuous(limits = c(11, 14)) +

  scale_x_continuous(breaks = c(2010,2020, 2024), limits = c(2015, 2025))+
    theme_classic()+

  theme(legend.position = "bottom") 

```

```{r}
#| include: false 

df_prep |> filter(high_ff_score == TRUE & in_eff_sfha == "Not SFHA" & Triad == "North" & sale_year == 2022) |> mutate(pin10 = str_sub(pin,1,10)) |> group_by(pin10) |> mutate(n = n()) |> arrange(desc(n), pin) |>
  select(pin10, pin, clean_name, n, sale_price, flood_factor_score, times_sold, in_eff_sfha)
```




## Parallel Trends Assumptions


::: panel-tabset

### Not Logged Sales Price

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  group_by(sale_year, high_ff_score, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score, lty = event)) +
  geom_line() +
  geom_point() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  theme_classic() + 
  #    geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  labs(title = "Pre- and Post- Event Treatment Trends",
       y = "Avg. Sale Price",
       x = NULL)


df_prep |> 
  group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(avg_price = mean(sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_price, color = high_ff_score, lty = event)) +
  geom_line() +
  geom_point() + 
  theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Sale Price",
       x = NULL) +
  facet_wrap(~Triad)

```

### Transformations of Sale Price

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
    group_by(sale_year, high_ff_score, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
  theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Logged Sale Price",
       x = NULL)

df_prep |> 
  group_by(sale_year, high_ff_score, event, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Logged Sale Price",
       x = NULL) +
  facet_wrap(~Triad)
```


```{r}
#| layout-ncol: 2

df_prep |> 
    group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "1/Sale Price",
       x = NULL) +
  facet_wrap(~Triad)

df_prep |> 
  group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
       caption = "Inverse Price = 1 / sale_price") +
  facet_wrap(~Triad)

```

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by SFHA Status",
       y = "Avg. Logged Sale Price",
       x = NULL) 



df_prep |> 
    group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. Logged Sale Price",
       x = NULL) + 
       facet_wrap(~Triad)



df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  geom_vline(xintercept=2020, lty = 2) +
    scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 

  labs(title = "Pre- and Post-Event Trends by SFHA Status",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
       caption = "Inverse Price = 1 / sale_price")


df_prep |> 
    group_by(sale_year, in_eff_sfha, Triad, event) |> 
  summarise(inverse_price = mean(1/sale_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = inverse_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 

  scale_x_continuous(breaks = c(2010, 2015, 2020, 2024)) + 
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad and SFHA Status",
       y = "Avg. Inverse of Sale Price",
       x = NULL,
       caption = "Inverse Price = 1 / sale_price") + 
  facet_wrap(~Triad)


```

```{r}
#| column: page
#| layout-ncol: 2
#| message: false


df_prep |> 
    group_by(sale_year, in_eff_sfha, event) |> 
  summarise(asinh_price = mean(asinh(sale_price)),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = in_eff_sfha)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. asinh(Sale Price)",
       x = NULL)




df_prep |> 
  group_by(sale_year, high_ff_score, Triad, event) |> 
  summarise(asinh_price = mean(asinh(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = asinh_price, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
   theme_classic() + 
  geom_smooth(aes(lty = event), method = "lm", se = FALSE) + 
  #     geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes
  scale_y_continuous(labels = scales::dollar) + 
  geom_vline(xintercept=2020, lty = 2) +
  
  labs(title = "Pre- and Post-Event Trends by Triad",
       y = "Avg. asinh(Sale Price)",
       x = NULL) + 
  facet_wrap(~Triad)



```

### Testing slopes 

```{r}
#| layout-ncol: 1
#| label: tbl-notloggedDV

slopes1 <- lm(sale_price ~ high_ff_score*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes1,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


slopes2 <- lm(log(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)
# 
# modelsummary::modelsummary(
#   slopes2,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)

slopes3 <- lm(asinh(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)

# modelsummary::modelsummary(
#   slopes3,
#               output = "flextable",
#              fmt = function(x) round(x, 2),
#              stars = TRUE)


modelsummary::modelsummary(
  list(slopes1, slopes2, slopes3),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)



```

**sale_year:in_eff_sfha**\
If not statistically significant, then I fail to reject the null hypothesis --> there is no evidence of different pre-treatment trends between properties that were in and out of SFHAs.

**sale_year:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.


:::

## Other random stuff


```{r}
missing_ff_score <- df_prep |> filter(is.na(high_ff_score) | is.na(in_eff_sfha))

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)

df_prep |> 
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(sale_year, high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  ) |> DT::datatable(rownames = FALSE)


df_prep <- df_prep |> 
  filter(!is.na(high_ff_score))
```


```{r}

df_prep |> 
    filter(sale_year > 2015) |>     # just to have roughly the same number of years on both sides of the event
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  mutate(log_price = log(sale_price)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(            
    avg_log_price = mean(log_price, na.rm=TRUE),
    median = median(log_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )

df_prep |> 
  filter(sale_year > 2015) |>
  filter(!is.na(high_ff_score)) |>
  filter(!is.na(in_eff_sfha)) |>
  group_by(high_ff_score, in_eff_sfha, event) |>
  summarize(
    avg_price = mean(sale_price, na.rm=TRUE),
    median = median(sale_price),
    n = n(), 
    distinct_pins = n_distinct(pin),
  )


```



<!---Properties with high flood score but no SFHA
- "02014000171053" = "1354 whispering springs Palatine IL" Parcel is a "condo" but a bunch of detached homes around a pond. Flood score is 7. Has a parcel inside of it (1733 EMERALD BAY 5, PALATINE, IL 60074) with a FF=6 that IS in a FEMA flood zone. Not sure if there was a specific pin division for this reason) ---> 


```{r}
#| eval: false


df_prep |> 
  filter(high_ff_score == FALSE & in_eff_sfha == "SFHA") |> 
  mutate(parcel = str_sub(pin, 1, 10)) |> 
  distinct(parcel, in_eff_sfha, high_ff_score)


```



SOLVED "01014050100000" = "804 division st, barrington IL"  
SOLVED "01021000330000"  = "7 Marmon LN Barringonton IL"  
"0102300012" = "221 Oakdene Drive Barrington" # only land barely touches SFHA  

"02013020771280" = "2 Dundee Quarter 302 Palatine IL" # considered condo but its all detached homes or townhomes. AND IN A LOMR

"0216410003" = "25 North Clyde Avenue, Palatine, IL, 60067, USA" # actually has a flood factor of 5

"1505117011" = "100 S Roberta AVe Northlake" # parcel boundary touches SFHA but not house

"1504117057" = "1642 N 39th Ave Stone Park" # score of 6, is in SFHA

"1505205013" = "1652 43RD AVE, STONE PARK, IL 60165" # has a flood score of 7! and is in SFHA

