---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---
# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.


# Data Sources and Background Information

> TO DO: Fill in missing municipality names. Probably can do by shared assessor neighborhood? or even a spatial join if needed for only the parcels that don't have muni names associated with them. Wouldn't be as big of a computational list for a select list of parcels.

> TO DO: Manually collect the \~2000 flood scores for pins that didn't have them. They are also almost all missing nbhd_code, zip_code, and some are missing clean_name.

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)

```

> Sales are not winsorized

```{r warning = FALSE, message = FALSE}
df_pairs <- readRDS("data/processed/df_pairs.RDS")
ff_pairs <- readRDS("data/processed/ff_pairs.rds")
df_prep <- readRDS("data/processed/df_prep.rds")

```

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.



There are `r n_distinct(df_pairs$pin)` pins remaining in `df_pairs`.


There are `r print(ff_pairs |> filter(treated ==TRUE & high_ff_score == TRUE) |> count())` observations that are treated and have a high flood factor score (greater than 4).

```{r}
table(ff_pairs$sale_year_t2, ff_pairs$change_type)
```

## Descriptive Stats

::: panel-tabset
### df_prep Descriptive Stats

```{r descriptive-stats-df_prep}
skim(df_prep)
```

### ff_pairs Descriptive Stats
```{r descriptive-stats-df_pairs}
skim(ff_pairs)
```
:::


## Parallel Trends Assumptions


::: panel-tabset
### Parallel Trends assumption for all sales

```{r}
#| column: page
#| layout-ncol: 2
#| message: false

df_prep |> 
  filter(sale_date < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year, high_ff_score, Triad) |> 
  summarise(avg_logprice = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = avg_logprice, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
  facet_wrap(~Triad)

df_prep |> 
  filter(sale_date > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year, high_ff_score, Triad) |> 
  summarise(mean_growth = mean(log(sale_price), na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: All Sales (df_prep)") +
    facet_wrap(~Triad)

```

```{r}

slopes1 <- lm(log(sale_price) ~ high_ff_score*event*sale_year, data = df_prep)


slopes2 <- lm(log(sale_price) ~ in_eff_sfha*event*sale_year, data = df_prep)


modelsummary::modelsummary(
  list(slopes1, slopes2),
              output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

**sale_date:event:in_eff_sfha**\
→ If significant, it means the difference in slope between groups changed after the event. That does NOT SUPPORT parallel trends assumptions for difference in differences models.

```{r}
#| layout-ncol: 2
#| column: page
#| message: false

ggplot(df_prep |> filter(!is.na(high_ff_score)), aes(x = sale_year, y = log(sale_price), color = high_ff_score)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by High Flood Factor",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "High FF Score",
        caption = "Dataset: All Sales (df_prep)"

  ) +
  theme_minimal()

ggplot(df_prep |> 
         filter(!is.na(in_eff_sfha)), aes(x = sale_year, y = log(sale_price), color = in_eff_sfha)) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ event
             ) +
  labs(
    title = "Slope Comparison Pre vs. Post Event by SFHA Status",
    x = "Sale Year",
    y = "Log Price Growth Between Sales",
    color = "In SFHA",
    caption = "Dataset: All Sales (df_prep)"
  ) +
  theme_minimal()
```


### Parallel trends test for repeat sales

DV is change in logged price.

```{r}
#| layout-ncol: 2
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released &
              !is.na(ff_factor)) |> 
    group_by(sale_year_t1, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n() ) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type", 
       caption = "Dataset: Repeat Sales") 


ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
           !is.na(ff_factor)) |>
  group_by(sale_year_t2, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type", caption = "Dataset: Repeat Sales")
```

```{r}
#| column: page
#| layout-ncol: 3
#| message: false

ff_pairs |> 
  filter(sale_date_t1 < new_info_released  &
            !is.na(high_ff_score)
         ) |> 
    group_by(sale_year_t1, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
      geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 < new_info_released & sale_year_t2 > 2015 &
            !is.na(high_ff_score)) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
             n = n() ) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Pre-Treatment Trends for 2nd sale by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")

ff_pairs |> 
  filter(sale_date_t2 > new_info_released &
            !is.na(high_ff_score)
         ) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE),
            n = n()) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
        geom_text(aes(label = n), vjust = -1, size = 3) +  # or geom_label() for boxes

  labs(title = "Post-Treatment Trends by FF Score 5 or higher",
        caption = "Dataset: Repeat Sales (ff_pairs)")
```


Is testing the assumption on repeat sales actually right to do or should I just use all sales?? I feel like it should be all sales.

```{r}

slopes1<- lm(d_log_price ~ sale_year_t2*treated*high_ff_score, data = ff_pairs)

slopes2 <- lm(d_log_price ~ sale_year_t2*treated*change_type, data = ff_pairs)

modelsummary::modelsummary(
  list(slopes1, slopes2),
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)
```

Parallel trends not super supported in either model for repeat sales?
:::

# Models

## Repeat Sales

```{r}
#| column: page
#| label: tbl-simplified-repeatsales-ffscores
#| tbl-cap: "Uses repeat_sales `ff_pairs`."


  all_models <- list(
    
    "d_log_price" = list(
      
      "I" = feols(d_log_price ~ high_ff_score,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
              
      "II" = feols(d_log_price ~ high_ff_score*treated | pin,
                    data = ff_pairs,
                    cluster = ~pin + clean_name
                    
      ),
      
      "III" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "IV" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs,
                    cluster = ~pin
        
      ),
      
      "V" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs |> group_by(pin) |> filter(n() > 1),
                    cluster = ~pin
        
      )),
        "Annualized Change P" = list(

      "I" = feols(ann_d_log_price ~ high_ff_score,       
                   data = ff_pairs,
                   cluster = ~pin
                   
      ),
      "II" = feols(ann_d_log_price ~ high_ff_score*treated | pin,
                    data = ff_pairs,
                    cluster = ~pin + clean_name
                    
      ),
      
      "III" = feols(ann_d_log_price ~ high_ff_score*treated | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "IV" = feols(ann_d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs,
                    cluster = ~pin
        
      ),
      
      "IV" = feols(ann_d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs |> group_by(pin) |> filter(n() > 1),
                    cluster = ~pin
        
      ))
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted


```


```{r}
#| column: page
#| label: tbl-proposal-models-ffscores
#| tbl-cap: "Model in proposal. Uses repeat_sales `ff_pairs`."


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ change_type,       
                   data = ff_pairs,
                   cluster = ~pin
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated*change_type,
                    data = ff_pairs,
                    cluster = ~pin + clean_name
                    
      ),
      
      "IV" = feols(d_log_price ~ high_ff_score*treated*change_type | sale_year_t2,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "V" = feols(d_log_price ~ high_ff_score*treated*change_type | sale_year_t2 + pin,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "VI" = feols(d_log_price ~ high_ff_score*treated*change_type | sale_year_t2 + pin + clean_name,
                    data = ff_pairs,
                    cluster = ~pin + clean_name
                    
      ))
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-dissertation-ffscorerelease
#| tbl-cap: "Uses repeat sales `ff_pairs`."


  all_models <- list(
    
    "High or Low" = list(
      
      "PIN FE" = feols(d_log_price ~ high_ff_score ,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "No FE" = feols(d_log_price ~ treated | pin,       
                   data = ff_pairs,
                   cluster = ~pin
                   
      ),
      "No FE" = feols(d_log_price ~ high_ff_score*treated,
                    data = ff_pairs,
                    cluster = ~pin + clean_name
                    
      ),
      
      "IV" = feols(d_log_price ~ high_ff_score*treated | pin,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ),
      
      "V" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs,
                    cluster = ~pin
                    
      ))
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-fixedeffects-models-ffscores
#| tbl-cap: "Categorical or Ordinal Risk Scores and then adding some Controls"


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
        "I" = feols(d_log_price ~ high_ff_score | sale_year_t2,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(d_log_price ~ change_type | sale_year_t2,       
                   data = ff_pairs,
                  cluster = ~pin
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2,
                    data = ff_pairs,
                  cluster = ~pin
                    
      ), 
      "III" = feols(d_log_price ~ high_ff_score*treated | sale_year_t2 + pin,
                    data = ff_pairs,
                  cluster = ~pin
                    
      ), 
       "IV" = feols(d_log_price ~ high_ff_score*treated | pin + sale_year_t2 + clean_name,
                    data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    ))
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

## Using All Sales Data - Not just Repeat Sales

**using df_prep**

```{r}
#| label: tbl-models-with-dfprep
#| tbl-cap: "A 'high' flood factor score is a score of 5 or higher. Sales after the 'event' are coded as 'Post' event, which is coded as June 2020 when the scores were released. The interaction of a high flood factor score and being post event is a key variable to look at. Year Fixed Effects are probably necessary due to the growth in sales prices during and after COVID. The last column has PIN, municipality, and sales year fixed effects."

  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(log(sale_price) ~ high_ff_score | clean_name,       
                  data = df_prep,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep,
                  cluster = ~pin + clean_name
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "pin fes" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "2 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin+ clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ high_ff_score*event | pin + clean_name + sale_year,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin + clean_name + sale_year,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      )
    
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-dfprep-ffscorerelease
#| tbl-cap: "Uses sales data `df_prep`."


  all_models <- list(
    
    "High or Low" = list(
      
      "PIN FE" = feols(log(sale_price) ~ high_ff_score ,       
                  data = df_prep,
                  cluster = ~pin
      ),
      
      "No FE" = feols(log(sale_price) ~ event | pin,       
                   data = df_prep,
                   cluster = ~pin
                   
      ),
      "No FE" = feols(log(sale_price) ~ high_ff_score*event,
                    data = df_prep,
                    cluster = ~pin + clean_name
                    
      ),
      
      "IV" = feols(log(sale_price) ~ high_ff_score*event | pin,
                    data = df_prep,
                    cluster = ~pin
                    
      ),
      
      "V" = feols(log(sale_price) ~ high_ff_score*event | sale_year + pin,
                    data = df_prep,
                    cluster = ~pin
                    
      ),
      
      
      "Triad" = feols(log(sale_price) ~ high_ff_score*event*Triad | sale_year + pin,
                    data = df_prep,
                    cluster = ~pin
                    
      ), 
            "3 FEs" = feols(log(sale_price) ~ high_ff_score*event*Triad | pin + clean_name+ sale_year,
                    data = df_prep,
                    cluster = ~pin
                    
      ),
         "With SFHA" = feols(log(sale_price) ~ high_ff_score*event*in_eff_sfha | pin + clean_name + sale_year,
                    data = df_prep,
                    cluster = ~pin
                    
      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


# Robustness Checks

## Risk Score as Categorical Variable

```{r}
all_models = list(

"Risk Score as Factor" = list(
    
      
      "III" = feols(d_log_price ~ ff_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
         "IV" = feols(d_log_price ~ ff_factor*change_type*treated | pin + clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      "V" = feols(d_log_price ~ ff_factor*change_type*treated | pin,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
      ,
      "V" = feols(d_log_price ~ ff_factor*change_type*treated | pin + sale_year_t2,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    
    )
)

all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```

## Risk Score as Ordinal Variable

```{r}
model_list <- list(
        "No FEs" = list(
      
      "I" = feols(d_log_price ~ change_type+ env_flood_fs_factor*treated,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ env_flood_fs_factor*change_type*treated,       
                   data = ff_pairs,
                   cluster = ~pin
                    
      )),
        "FEs" = list(
      
      "Muni FE" = feols(d_log_price ~ change_type*treated + env_flood_fs_factor*treated | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "Muni Fe" = feols(d_log_price ~ env_flood_fs_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      
      "PIN FE" = feols(d_log_price ~ env_flood_fs_factor*change_type | pin,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name           
      )
    )
        )

all_models_formatted <- modelsummary::modelsummary(model_list,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted
```
