---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: margin
    error: true
---
# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.


# Data Sources and Background Information

> TO DO: Fill in missing municipality names. Probably can do by shared assessor neighborhood? or even a spatial join if needed for only the parcels that don't have muni names associated with them. Wouldn't be as big of a computational list for a select list of parcels.

> TO DO: Manually collect the \~2000 flood scores for pins that didn't have them. They are also almost all missing nbhd_code, zip_code, and some are missing clean_name.

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)
library(plm)
library(jtools)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, results = "hold"  )


# ff_pairs <- readRDS("data/processed/ff_pairs_buildings.rds") |>
#   rename(around_event = treated) |>
#     select(-c(clean_name.x, clean_name.y))

df_prep <- readRDS("data/processed/variants/df_prep__bldg_sfha.rds")

#df_prep <- readRDS("data/processed/df_prep_buildings.rds") |>
  #select(-c(clean_name.x, clean_name.y))

```

> Sales are not winsorized

> Most of these parcels with missing municipality names have been given addresses using the Assessor's parcel address dataset. Parcels that still haven't matched tend to be parcels that were consolidated for larger homes/buildings and no longer exist. In general, pin splits and consolidations are NOT considered in this analysis.

```{r}
table(df_prep$sale_year, df_prep$change_type)
table(df_prep$sale_year, df_prep$high_ff_score)

```


There are `r n_distinct(df_prep$pin)` pins remaining in `df_prep`.


```{r}
#| layout-ncol: 2

table(df_prep$sale_year, df_prep$addedto_eff_sfha)
table(df_prep$sale_year, df_prep$removedfrom_eff_sfha)

```

**Removes missing values until final data cleaning is completed. Dropping them here to see smallest sample sizes in models and graphs.**

```{r remove-missingvalues}
df_prep <- df_prep |>
  filter(!is.na(high_ff_score) &
           !is.na(eff_date) &
           !is.na(clean_name) &
           !is.na(pre_date)
         )
``` 

## Descriptive Stats

### df_prep Descriptive Stats

```{r descriptive-stats-df_prep}
#| column: page
skim(df_prep)
```

```{r}
ggplot() + 
  geom_histogram(data = df_prep, aes( x = sale_price), bins = 100) + theme_classic()

ggplot() + 
  geom_histogram(data = df_prep, aes( x = log(sale_price)), bins = 100) + theme_classic()

ggplot() + 
  geom_histogram(data = df_prep, aes( x = asinh(sale_price)), bins = 100) + theme_classic()
```



# Models

```{r}
#| label: trial-removelomrs

df_prep |> filter(high_ff_score == FALSE & in_eff_sfha == "SFHA") |>   mutate(parcel = str_sub(pin, 1, 10)) |> 
  distinct(parcel, in_eff_sfha, in_lomr, high_ff_score)

df_prep |> filter(high_ff_score == FALSE & in_eff_sfha == "SFHA" & in_lomr == "Not in LOMR") |>   mutate(parcel = str_sub(pin, 1, 10)) |> 
  distinct(parcel, in_eff_sfha, in_lomr, high_ff_score)

#df_prep <- df_prep |> filter(in_lomr == "Not in LOMR") |> group_by(pin) |> mutate(times_sold = n()) |> filter(times_sold > 1) |> ungroup()




```


```{r}
#| include: false

df_prep <- df_prep |> 
  mutate(in_sfha = ifelse(in_eff_sfha == "SFHA", 1, 0))

df_prep |>
  group_by(in_sfha) |>
  summarize(mean = mean(env_flood_fs_factor, na.rm = T),
            sd = sd(env_flood_fs_factor, na.rm = T))
```

## DV = Logged Sale Price


```{r}
#| label: tbl-models-forDFM2
#| tbl-cap: "feols() command. Exported with export_summs() DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  

  "High FF Score after Info Release" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
              panel.id = "pin",
              
              data = df_prep,
              cluster = ~ clean_name
              
  ),

  "3-way Interaction (Preliminary SFHA)" = feols(log(sale_price) ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
               # cluster = ~ clean_name
                              vcov = "hetero" 
               
  ),
  
  "3-way Interaction (Effective SFHA)" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event  | pin + sale_year,
               panel.id = "pin",
               data = df_prep,
               vcov = "hetero"
  ) ,
  
  "Adds in_lomr" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event*in_lomr  | pin + sale_year,
               panel.id = "pin",
               vcov = "hetero",
               data = df_prep
  )
)

# 
# cm2 <- c(
#   
#   'Post Event' = 'event2.Post',
#   'High FF Score x Post Event' = 'high_ff_scoreTRUE:event2.Post',
#   'In Preliminary SFHA' = 'in_prelim_sfhaSFHA',
#   'High FF Score x In Prelim SFHA' = 'high_ff_scoreTRUE:in_prelim_sfhaSFHA',
#   'In Effective SFHA' = 'in_eff_sfhaSFHA',
#   'In Eff. SFHA x Post Event' = 'in_eff_sfhaSFHA:event2.Post',
#   'In SFHA, High FF Score & Post Event' = 'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2.Post',
#   'In Prelim SFHA & Post Event' = 'event2.Post:in_prelim_sfhaSFHA',
#   'In Prelim SFHA, High FF Score & Post Event' = 'high_ff_scoreTRUE:event2.Post:in_prelim_sfhaSFHA'
# )
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", "Data Release and Year Dummies", "Preliminary SFHA", "Effective SFHA"),
#              robust = "HC3"#,               coefs = cm
# 
#              #statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              )





cm = c(
  'event2. Post' = 'Post Event',
  
  'in_prelim_sfhaSFHA' = 'Enters Prelim. SFHA',  
  
  'event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'in_prelim_sfhaSFHA:event2. Post' = 'In Prelim SFHA & Post Event',
  
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',
  
  
  'in_prelim_sfhaSFHA:high_ff_scoreTRUE' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',
  'in_prelim_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event',
  
  
  'in_eff_sfhaSFHA'= 'Enters Effective SFHA',
  
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',
  'in_eff_sfhaSFHA:event2. Post' = 'In Eff. SFHA x Post Event',
  
  'high_ff_ScoreTRUE:event2. Post' = 'High FF Score & Post Event',
  'event2. Post:high_ff_ScoreTRUE' = 'High FF Score & Post Event',
  
  'high_ff_ScoreTRUE:in_eff_sfhaSFHA' = 'In Eff. SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_ScoreTRUE' = 'In Eff. SFHA x High FF Score',

  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event'
  
)


all_models_formatted <- modelsummary::msummary(
  merriman_models,
  fmt = function(x) round(x, 2),
  stars = TRUE,
  coef_map = cm
  )

all_models_formatted

```

```{r}
#| label: tbl-models-forDFM2-
#| tbl-cap: "feols() command. Exported with msummary() DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025. Without pretty labels." 
#| column: page-left


options(scipen = 99)

merriman_models2 <- list(

    "No 'Event' Variable" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*in_lomr  | pin + sale_year,
              panel.id = "pin",
              data = df_prep,
                vcov = "hetero" 
              
  ),
  
  "II" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
              panel.id = "pin",
              data = df_prep,
              cluster = ~ clean_name
              
  ),

  "III" = feols(log(sale_price) ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
                vcov = "hetero" 

  ),
  
  "IV" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event  | pin + sale_year,
               panel.id = "pin",
               data = df_prep,
               vcov = "hetero"
  )  ,
  
  "V" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event*in_lomr  | pin + sale_year,
               panel.id = "pin",
               vcov = "hetero",
               data = df_prep
  )
)





all_models_formatted <- modelsummary::msummary(
  merriman_models2,
  fmt = function(x) round(x, 2),
  stars = TRUE
  )

all_models_formatted

```

```{r}
feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event*in_lomr  | pin + sale_year,
               panel.id = "pin",
               vcov = "hetero",
               data = df_prep) |> modelsummary::msummary()

feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event*in_lomr  | pin + sale_year,
               panel.id = "pin",
               vcov = "hetero",
               data = df_prep) |> export_summs()
```

## DV = Sales Price (not logged!)


```{r}
#| label: tbl-models-forDFM2-nonlogged
#| tbl-cap: "feols() command. Exported with export_summs() DV is sale_price NOT LOGGED. Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left


options(scipen = 99)

merriman_models <- list(
  
  
  #   "I" = feols(sale_price ~ high_ff_score | pin  + sale_year,
  #             panel.id = c("pin", "sale_year"),
  #             vcov = "hetero",
  #             data = df_prep,
  # 
  # ),
  # 
  "II" = feols(sale_price ~ event*high_ff_score | pin + sale_year,

              data = df_prep,
              cluster = ~ clean_name
              
  ),
  # "II.5" = feols(sale_price ~ event + factor(sale_year) | pin,
  #              data = df_prep,
  #              cluster = ~ clean_name
  #              
  # ),
  "III" = feols(sale_price ~ high_ff_score*event*in_prelim_sfha | pin + sale_year,
                data = df_prep,
                              vcov = "hetero" 

  ),
  
  "IV" = feols(sale_price ~ high_ff_score*event*in_eff_sfha  | pin + sale_year,

               data = df_prep,
                             vcov = "hetero"
  ) 
)

# cm2 <- c(
#   "Post Event" = "event2. Post",
#   "High FF Score x Post Event" = "event2. Post:high_ff_scoreTRUE",
#   
#   "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
#   "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
#   
#   "In Effective SFHA" = "in_eff_sfhaSFHA",
#  # "In Eff. SFHA x Post Event" = "in_eff_sfhaSFHA:event2. Post",
#   "In SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",
#   "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
#   "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
# )
# 
# 
# 
# export_summs(merriman_models,
#              model.names = c(#"FF Score Indicator", 
#                              "FF Score * Data Release", 
#                            #  "Data Release and Year Dummies", 
#                              "Preliminary SFHA", 
#                            "Effective SFHA"),
#           #   robust = "HC3", #, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared")
#              coefs = cm2
#              )



cm3 = c(
  'event2. Post' = 'Post Event',
  'high_ff_scoreTRUE:event2. Post' = 'High FF Score x Post Event',
  'event2. Post:high_ff_scoreTRUE' = 'High FF Score x Post Event',
  
  'in_prelim_sfhaSFHA' = 'In Preliminary SFHA',
  'event2.Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA & Post Event',
  'high_ff_scoreTRUE:in_prelim_sfhaSFHA' = 'In Prelim SFHA x High FF Score',
  'high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA' = 'In Prelim SFHA, High FF Score & Post Event',

  
  'in_eff_sfhaSFHA'= 'In Effective SFHA',
  'event2. Post:in_eff_sfhaSFHA' = 'In Eff. SFHA x Post Event',
  'high_ff_scoreTRUE:in_eff_sfhaSFHA' = 'In Effective SFHA x High FF Score',
  'in_eff_sfhaSFHA:high_ff_scoreTRUE:event2. Post' = 'In Effective SFHA, High FF Score & Post Event',
  'high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA' = 'In Effective SFHA, High FF Score & Post Event'
)

all_models_formatted <- modelsummary::msummary(merriman_models,

           #    output = "flextable",
          #  fmt = function(x) round(x, 2),
            fmt = function(x) scales::comma(x, big.mark = ",", accuracy = 1),


             stars = TRUE,
          coef_map = cm3
          )

all_models_formatted
```


_A panelmodel object contains: coefficients, residuals, fitted.values, vcov, df.residual and call and functions that extract these elements are provided._ 


```{r}
#| label: tbl-models-forDFM2-PLM
#| tbl-cap: "PLM package! DV is log(sale_price). Observations include pins that sold 2+ times between 2010 and 2025."
#| column: page-left

merriman_models <- list(

  "II" = plm(log(sale_price) ~ in_eff_sfha,
              index = c("pin", "sale_year"),
                 effect = "twoway",

              data = df_prep
              
  ),
  "II" = plm(log(sale_price) ~ event,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
               
  ),
    "III" = plm(log(sale_price) ~ high_ff_score*event*in_eff_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              ),

  "IV" = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
                           effect = "twoway",

              data = df_prep
              )

  )

cm <- c(
  "Post Event" = "event2. Post",
 "High FF Score x Post Event" = "high_ff_scoreTRUE:event2. Post",
    "High FF Score x Post Event" = "high_ff_scoreTRUE:event2. Post",

  "In Effective SFHA" = "in_eff_sfhaSFHA",
  "In Eff. SFHA x Post Event" = "event2. Post:in_eff_sfhaSFHA",
  "In SFHA, High FF Score & Post Event"   = "high_ff_scoreTRUE:event2. Post:in_eff_sfhaSFHA",



  "In Preliminary SFHA" = "in_prelim_sfhaSFHA",
  "High FF Score x In Prelim SFHA" = "high_ff_scoreTRUE:in_prelim_sfhaSFHA",
  
  
  "In Prelim SFHA & Post Event" = "event2. Post:in_prelim_sfhaSFHA",
  "In Prelim SFHA, High FF Score & Post Event" = "high_ff_scoreTRUE:event2. Post:in_prelim_sfhaSFHA"
)


export_summs(merriman_models,
             model.names = c("Just SFHA", "Post FF Data Release", "Add Effective SFHA", "Add Prelim SFHA Identifier"),
             coefs = cm
            # robust = "HC3"#, statistics = c(N = "nobs", adj.R2 = "adj.r.squared", R2 = "r.squared"))
)
# all_models_formatted <- modelsummary::modelsummary(merriman_models,
# 
#            #    output = "flextable",
#              fmt = function(x) round(x, 2), coef_map = cm,
#              stars = TRUE)
# 
# all_models_formatted

```


### Distribution of Sale Prices

```{r}
ggplot(df_prep, aes(x = sale_price)) +
      geom_histogram(#binwidth = 0.1, 
                     fill = "skyblue", color = "black") +
      labs(title = "Sale Price  Distribution",
           x = "$",
           y = "Frequency") +
      theme_minimal() 

ggplot(df_prep, aes(x = log(sale_price))) +
      geom_histogram(#binwidth = 0.1, 
                     fill = "skyblue", color = "black") +
      labs(title = "Logged Sale Price  Distribution",
           x = "$",
           y = "Frequency") +
      theme_minimal()
```


```{r residuals, include = FALSE, eval = FALSE}
mod1_fe = plm(log(sale_price) ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data1 <- broom::augment(mod1_fe, data = df_prep)
    

ggplot(fitted_data1, aes(x = .resid)) +
      geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  



mod2_fe = plm(sale_price ~ high_ff_score*event*in_prelim_sfha,       
              index = c("pin", "sale_year"),
              effect = "twoway",
              data = df_prep
              )

fitted_data2 <- broom::augment(mod2_fe, data = df_prep)
    

ggplot(fitted_data2, aes(x = .resid)) +
      geom_histogram(binwidth = 100000, 
                     fill = "skyblue", color = "black") +
      labs(title = "Histogram of Residuals",
           x = "Residuals",
           y = "Frequency") +
      theme_minimal()  

```


## Muni Fixed Effects, DV = ln(p)

**using df_prep**

> Put it into some year's dollars. Convert to common dollar for sales.

```{r}
#| label: tbl-models-with-dfprep
#| tbl-cap: "A 'high' flood factor score is a score of 5 or higher. Sales after the 'event' are coded as 'Post' event, which is coded as June 2020 when the scores were released. The interaction of a high flood factor score and being post event is a key variable to look at. Year Fixed Effects are probably necessary due to the growth in sales prices during and after COVID. The last column has PIN, municipality, and sales year fixed effects."
#| column: page-left


  all_models <- list(
    
    "High or Low" = list(

      "I" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep
                    
      ),
     "muni & year fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name + sale_year,
                    data = df_prep
                    
      )
      

    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


```{r}
#| column: page
#| label: tbl-dfprep-ffscorerelease
#| tbl-cap: "Uses sales data `df_prep`."


  all_models <- list(
    
    "High or Low" = list(

      
      "PIN & Sale Year FE" = feols(log(sale_price) ~ high_ff_score*event | pin + sale_year,
                    data = df_prep,

      ),
      
      
      "Triad Interaction" = feols(log(sale_price) ~ high_ff_score*event*Triad | pin + sale_year,
                    data = df_prep,

      ), 

         "4way Interaction" = feols(log(sale_price) ~ high_ff_score*event*in_eff_sfha*Triad | pin + clean_name + sale_year,
                    data = df_prep,

      )
      )
    
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```


