---
title: "Cook County Parcel Sales"
subtitle: "Variant: `r params$variant_key`"
params:
 variant_key: "bldg_1in500" # "bldg_sfha"   # options: parcel_sfha, bldg_sfha, parcel_1in500, bldg_1in500
 # bldg_updated, land_updated, ptaxsim_updated, risk500_land_updated, risk500_updated, df_prep_bldg_updated_arcgis,

 
format: 
  html:
  #  theme: darkly
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
    warning: false
    message: false
    error: true

---


# Data Sources and Background Information

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(fixest)
library(jtools) # for model table formatting
library(skimr)  # for skim() command for descriptive statistics
library(scales)
library(modelsummary)
```


```{r}
source("R/helper_pins_to_drop.R")

# source("R/helper_pins_to_drop_forsure.R")

variant_key  <- params$variant_key
variants_dir <- params$variants_dir

if(variant_key %in% c("parcel_sfha", "bldg_sfha", "parcel_1in500", "bldg_1in500")){
  
  variants_dir <-  "data/processed/variants"
  
  variant_path <- file.path(variants_dir,
                            paste0("df_prep__", variant_key, ".rds")
                            
  )
}else if (variant_key %in% c("bldg_updated", "land_updated", "ptaxsim_updated","risk500_land_updated", "risk500_updated", "df_prep_bldg_updated_arcgis")) {
  
  variants_dir <- "data/processed/targets/sales"
  
  variant_path <- file.path(
    variants_dir,
    paste0("df_prep_", variant_key, ".rds"))
  
}

if (!file.exists(variant_path)) {
  stop("Variant file not found: ", variant_path)
}
```


```{r}

df_prep <- readRDS(variant_path) |> filter(!pin10 %in% drop_parcels)


# helpful stamp
variant_label <- case_when(
  variant_key == "parcel_sfha"   ~ "Parcel × SFHA (1%)",
  variant_key == "bldg_sfha"     ~ "Building × SFHA (1%)",
  variant_key == "parcel_1in500" ~ "Parcel × 0.2%",
  variant_key == "bldg_1in500"   ~ "Building × 0.2%",
  
  TRUE ~ variant_key
)

cat("Loaded variant:", variant_label, "\n")


variant_label <- dplyr::case_when(
  variant_key == "parcel_sfha"   ~ "Parcel × SFHA (1-in-100)",
  variant_key == "bldg_sfha"     ~ "Building × SFHA (1-in-100)",
  variant_key == "parcel_1in500" ~ "Parcel × 0.2% (1-in-500)",
  variant_key == "bldg_1in500"   ~ "Building × 0.2% (1-in-500)",
  TRUE ~ variant_key
)

# Handy text you can drop anywhere
variant_stamp <- paste0("[", variant_label, "]")


```

::: {.callout-note}
**Variant:** `r variant_label`
**File loaded:** `r paste0("df_prep__", params$variant_key, ".rds")`
:::


<!--- Can run from command line with: quarto::quarto_render("Question1.qmd", execute_params = list(variant_key = "bldg_sfha"))
) --->




```{r}
#| include: false
#| eval: false

df_prep <- readRDS("data/processed/targets/sales/df_prep_land_updated_arcgis.rds") |> 
  filter(!pin10 %in%drop_parcels)



df_prep |> filter(Triad == "City" & removedfrom_eff_sfha == TRUE) 
df_prep |> filter(Triad == "City" & addedto_eff_sfha == TRUE)


df_prep |> filter(Triad == "City" & removedfrom_eff_sfha == TRUE)  |> distinct(pin10)
df_prep |> filter(Triad == "City" & addedto_eff_sfha == TRUE) |> distinct(pin10)
```


```{r}

#source("R/helper_pins_to_drop.R")

# df_prep <- readRDS("data/processed/variants/df_prep__bldg_sfha.RDS") |> filter(!pin10 %in% drop_parcels)

#df_prep <- readRDS("data/processed/df_prep_bldg_sfha_updated_arcgis_forQ1_assumptiontests.RDS") |> filter(!pin10 %in% drop_parcels)

#df_prep <- readRDS("data/processed/df_prep_forQ1_assumptiontests.rds") |> filter(!pin10 %in%drop_parcels)

df_prep <- df_prep |>
  group_by(pin) |>
   mutate(d_price_pct = round((sale_price-dplyr::lag(sale_price))/(dplyr::lag(sale_price)), digits = 2), .after = pin) |> ungroup()


df_prep <-  df_prep |> filter((is.na(d_price_pct) & sale_price > 20000) | ( d_price_pct < 20 & sale_price > 20000) )

df_prep <- df_prep |> group_by(pin) |> 
  mutate(times_sold = n()) |> filter(times_sold > 1)
```



```{r}

clusters_county <- list(
  pin10      = ~ pin10#,
#  pin        = ~ pin,
#  clean_name = ~ clean_name#,
 # FIRM_PAN   = ~ FIRM_PAN
 # nbhd_code  = ~ nbhd_code
)

run_by_cluster <- function(formula, data, clusters, prefix = "Model") {
  imap(clusters, \(cl, nm) {
    feols(formula, data = data, cluster = cl)
  }) |>
    setNames(paste0(prefix, " (cluster: ", names(clusters), ")"))
}


# Convenience: bind multiple named lists of models into one named list
bind_models <- function(...) {
  out <- c(...)
  # guard against duplicate names (modelsummary will drop/merge silently)
  if(any(duplicated(names(out)))) {
    stop("Duplicate model names detected. Fix labels so each model has a unique name.")
  }
  out
}


```



# Research Question 1

The final data set represents the difference in price appreciation for properties that were mapped into an SFHA compared to the hypothetical price they would have sold at if they had not been mapped into an SFHA.

**Does the value of real estate parcels increase when they are removed from an SFHA?**

H1: A property removed from a SFHA will increase in value more than if it had not been removed from an SFHA.

## Model Info

To investigate whether the value of real estate parcels increases when they are removed from a Special Flood Hazard Area (SFHA), I used a Fixed Effects on PINs with sales from2010 to 2024.

**For Fixed Effect Models:** The dataset was first prepared by filtering out irrelevant parcels and ensuring that each property had at least two recorded sales. There is an indicator variable for if a PIN was in an SFHA at the time of sale or not.

*For 3 way interaction: In order to include PINs that did not change SFHA status, an additional indicator for post-FIRM update sales was created to interact with SFHA status.*

Additional variables were constructed to measure the timing of sales relative to the date a new Flood Insurance Rate Map (FIRM) took effect, allowing me to distinguish between sales occurring before and after floodplain reclassification. The time between sales was measured in both months and years.

These models tested whether being removed from the SFHA is associated with a statistically significant increase in log sale price.

I also explored interaction terms with LOMR status. Owners can appeal their flood zone designation and have the map altered. This results in them no longer having mandatory flood insurance if their appeal is accepted. I also included alternative specifications, such as including binary indicators specifically for whether a parcel was added or removed from an SFHA.

All models clustered standard errors at the parcel (PIN) level to account for repeated observations of the same property.

-   Robustness checks: cluster at land_parcel, FIRM_PAN, or muni level, vcov = "hetero", etc.

Notes:

1.  Removal from the SFHA is due to the FEMA flood insurance rate maps being updated. Properties are either in or out of the "1-in-100" year flood plain. They can be located in the SFHA and also have a LOMR that "removes" them from the floodplain. This information is represented in multiple variables (`in_eff_sfha` and `in_lomr`). If an observation is coded as `Removed` from an SFHA, it indicates that the floodplain shapefile itself changed that was created by FEMA.

-   If a property was in an SFHA in a FIRM and had an approved LOMR and then the FIRM is updated years later and the LOMR was still viewed as accurate and valid, then the PIN will appear as "removed from the SFHA" because the updated FIRM will incorporate the old LOMR into the updated floodplain. Depending on the time of sale, being flagged as removed from the SFHA would miss the potential price change from the change in insurance requirement (which again, was not the original research question).

2.  Treatment window timing: In theory, EFF_DATE would be associated with a change in price due to the capitalization of mandatory flood insurance requirement for homes that have mortgages in floodplains.

-   PRE_DATE is also used due to a buyers anticipation of a policy's impact and to measure the effect of risk information conveyed in preliminary FIRMs. The knowledge of the risk and the potential loss due to future floods may decrease the amount that buyers are willing to pay for a property that they see as more risky even if the financial ties to required flood insurance are not effective yet.

Concerns:

-   Who's included or excluded? Are the properties that are in floodplains different in ways that impact the sales? Are people less willing to buy risky properties in general, resulting in fewer sales?

-   Areas that have received new flood maps are mostly wealthier parts of Cook County. The pins added to flood plains in the preliminary FIRM are all in Northern Cook County. The FIRMs updated in 2019 and 2021 are along the lake front and include Glencoe/Wilmette areas. Could really influence price trends. 

Contributions to the literature: Many models model if SFHA status changes, but have it as one variable. this assumes that the effect of being added in or removed from an SFHA is the same in both directions. I model in_eff_sfha as one variable and separate it into added and removed to see if there are different effects.

```{r}
# skim(df_prep)
```


```{r}
table(df_prep$pre_date)

```

## PIN Inspection

```{r }



# same concept as grouping by dfirm 
table(df_prep$group_name_prelim)  # number of sales from each area that was updated in cook county
table(df_prep$addedto_prelim_sfha, df_prep$group_name_prelim)
table(df_prep$removedfrom_prelim_sfha, df_prep$group_name_prelim)

table(df_prep$treated_group_eff)
table(df_prep$treated_group_prelim)
```

```{r}
table(df_prep$treat_year_remove_prelim, df_prep$Triad)
table(df_prep$treat_year_add_prelim, df_prep$Triad)

```


```{r}
#| tbl-cap: "Observations per year. Added to (removed from) Effective SFHA"
#| layout-ncol: 2

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$addedto_prelim_sfha[df_prep$sale_year>=2016])

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$removedfrom_prelim_sfha[df_prep$sale_year>=2016])
```

```{r}
table(df_prep$addedto_prelim_sfha)
table(df_prep$removedfrom_prelim_sfha)
```

### Southern Cook County PINs of Interest

Crestwood, Oak Forest, Alsip, etc. 


```{r}
#| include: false

n_parcels_interest <- df_prep |>
  dplyr::filter(treat_year_remove_prelim == "2015") |>
  dplyr::distinct(pin10) |>
  nrow()
```

```{r}
#| label: tbl-southerncook-obs
#| tbl-cap: !expr 'glue::glue("Properties in South Triad that were removed from SFHAs by a PRELIMINARY map release in 2015. Distinct parcels: {n_parcels_interest}.")'

df_prep |> filter(
  treat_year_remove_prelim == "2015") |> DT::datatable(rownames = FALSE) # all 2015 treatment pins are in South Triad
```

```{r}
#| include: false

n_parcels_interest <- df_prep |>
  dplyr::filter(treat_year_add_prelim == "2015") |>
  dplyr::distinct(pin10) |>
  nrow()
```

```{r}
#| label: tbl-southerncook-obs-added
#| tbl-cap: !expr 'glue::glue("Properties in South Triad that were added to SFHAs by a PRELIMINARY map release in 2015. Distinct parcels: {n_parcels_interest}.")'

df_prep |> filter(
  treat_year_add_prelim == "2015") |> DT::datatable(rownames = FALSE)
```

```{r}
#| label: tbl-southerncook-obs-alwayssfha
#| tbl-cap: "Properties in South Triad that were always in the SFHA and in FIRMs updated in 2015."

df_prep |> filter(Triad == "South" & change_type_prelim == "Always SFHA" & pre_date_chr == "2015-02-12") 
```

### Chicago PINs of Interest

Mostly ignoring Chicago PINs though because they are nearly all Coastal condos that are false positives since they are up to the waterfront. 

```{r}
#| label: tbl-chicago-obs
#| tbl-cap: "Properties in Chicago that were added or removed from PRELIMINARY SFHA in 2019 and properties in Chicago that were always in the SFHA that were in FIRMs updated in 2019. Should be close to zero or zero number of PINs identified. "


df_prep |> filter(Triad == "City" & treat_year_add_prelim == "2019") # |> group_by(pin10) |> summarize(n = n())  |> View()

df_prep |> filter(Triad == "City" & treat_year_remove_prelim == "2019") # |> group_by(pin10) |> summarize(n = n())  |> View()
```

```{r}
#| label: tbl-chicago-obs-parcels
#| tbl-cap: "Distinct buildings that changed status. These are most likely on the coast of Lake Michigan."

df_prep |> filter(Triad == "City" & treat_year_add_prelim == "2019")  |> group_by(pin10) |> summarize(n = n())  

df_prep |> filter(Triad == "City" & treat_year_remove_prelim == "2019")  |> group_by(pin10) |> summarize(n = n())  
```


```{r}
#| label: tbl-chicago-obs-alwaysin
#| tbl-cap: "Properties in Chicago that were always in an SFHA. Mostly Coastal condos."

df_prep |> filter(Triad == "City" & change_type_prelim == "Always SFHA" & pre_date_chr == "2019-07-01")
```

### Northern Cook County PINs of Interest

Note: Some parts of northern Cook were part of the coastal FIRMs updated (Wilmette, Winnetka, etc.). This area had a preliminary map released in 2019 which became effective in 2021.

The other section of the county updated is in the north-west corner (Barrington Hills, etc.).  This area had a preliminary map released in 2021 which became effective in 2026. Only PINs identified with the preliminary map update are used in the analysis since the FIRMs became effective at the end of the dissertation and there were essentially no sales to use for a third effective treatment cohort. 

```{r}
#| include: false

n_parcels_interest <- df_prep |>
 filter(Triad == "North" & (treat_year_add_prelim == "2021" | treat_year_add_prelim == "2019")) |>
  dplyr::distinct(pin10) |>
  nrow()
```


```{r}
#| label: tbl-northerncook-obs-added
#| tbl-cap: !expr 'glue::glue("Properties in Northern half of Cook County that were added to flood risk zone. From 2019 OR 2021 preliminary map releases!  Distinct parcels: {n_parcels_interest}.")'


df_prep |> filter(Triad == "North" & (treat_year_add_prelim == "2021" | treat_year_add_prelim == "2019")) |> DT::datatable(rownames = FALSE) 
```

```{r}
#| include: false

n_parcels_interest <- df_prep |>
 filter(Triad == "North" & (treat_year_remove_prelim == "2021" | treat_year_remove_prelim == "2019")) |>
  dplyr::distinct(pin10) |>
  nrow()
```

```{r}
#| label: tbl-northerncook-obs-removed
#| tbl-cap: !expr 'glue::glue("Properties in Northern half of Cook County that were removed from flood risk zone. From 2019 OR 2021 preliminary map releases!  Distinct parcels: {n_parcels_interest}.")'


df_prep |> filter(Triad == "North" & (treat_year_remove_prelim == "2021" | treat_year_remove_prelim == "2019"))|> DT::datatable(rownames = FALSE)
```


```{r}
#| label: tbl-northerncook-obs-alwayssfha
#| tbl-cap: "Properties in Northern half of Cook County that were always in flood risk zone."
#| 
df_prep |> 
  filter(Triad == "North" & change_type_prelim == "Always SFHA")  |>
  DT::datatable(rownames = FALSE)
```

## Comparison of Prelim and Eff FIRM Counts

```{r}
#| layout-ncol: 2

table(df_prep$treat_year_remove_eff)
table(df_prep$treat_year_remove_prelim)


table(df_prep$treat_year_add_eff)
table(df_prep$treat_year_add_prelim)


table(df_prep$in_eff_sfha)
table(df_prep$in_prelim_sfha)

table(df_prep$rel_year_remove_eff)
table(df_prep$rel_year_remove_prelim)

```

 # Models

```{r fe-avgs}
df_changes <- df_prep |>
  dplyr::arrange(pin, sale_year) |>
  dplyr::group_by(pin) |>
  dplyr::mutate(
    d_price = sale_price - dplyr::lag(sale_price),
    d_log_price = log(sale_price) - dplyr::lag(log(sale_price))
  ) |>
  dplyr::ungroup() |>
  mutate(post = sale_date >= pre_date & pre_date_chr != "2005-01-01"  )

# cohort average change
df_changes |>
  dplyr::filter(!is.na(d_log_price)) |>
  dplyr::group_by(treat_year_remove_prelim) |>
  dplyr::summarise(mean_change = mean(d_log_price, na.rm = TRUE))

mean(df_prep$sale_price[df_prep$sale_year==2013])

mean(df_prep$sale_price[df_prep$sale_year==2018])


mean(df_prep$sale_price[df_prep$sale_year==2013 & df_prep$in_prelim_sfha==TRUE])

mean(df_prep$sale_price[df_prep$sale_year==2013 & df_prep$in_prelim_sfha==FALSE])

```

```{r}
# deman by PIN
df_fe <- df_prep |>
  dplyr::mutate(
    y = log(sale_price),
    x = as.numeric(removedfrom_prelim_sfha)
  ) |>
  dplyr::group_by(pin) |>
  dplyr::mutate(
    y_w1 = y - mean(y, na.rm = TRUE),
    x_w1 = x - mean(x, na.rm = TRUE)
  ) |>
  dplyr::ungroup()

# demean by year
df_fe <- df_fe |>
  dplyr::group_by(sale_year) |>
  dplyr::mutate(
    y_dd = y_w1 - mean(y_w1, na.rm = TRUE),
    x_dd = x_w1 - mean(x_w1, na.rm = TRUE)
  ) |>
  dplyr::ungroup()

beta_hat <- with(df_fe,
  sum(x_dd * y_dd, na.rm = TRUE) /
  sum(x_dd^2, na.rm = TRUE)
)

beta_hat
```


Exact way of demeaning:

```{r}
df_fe <- df_prep |>
  dplyr::mutate(
    y = log(sale_price),
    x = as.numeric(in_prelim_sfha)
  )  

grand_mean_y <- mean(df_fe$y, na.rm = TRUE)
grand_mean_x <- mean(df_fe$x, na.rm = TRUE)

pin_means <- df_fe |>
  dplyr::group_by(pin) |>
  dplyr::summarise(
    y_i = mean(y, na.rm = TRUE),
    x_i = mean(x, na.rm = TRUE)
  )

year_means <- df_fe |>
  dplyr::group_by(sale_year) |>
  dplyr::summarise(
    y_t = mean(y, na.rm = TRUE),
    x_t = mean(x, na.rm = TRUE)
  )

df_fe <- df_fe |>
  dplyr::left_join(pin_means, by = "pin") |>
  dplyr::left_join(year_means, by = "sale_year") |>
  dplyr::mutate(
    y_dd = y - y_i - y_t + grand_mean_y,
    x_dd = x - x_i - x_t + grand_mean_x
  )

df_fe |> 
  select(pin, sale_year, sale_price , y_dd, x_dd,  addedto_prelim_sfha, removedfrom_prelim_sfha, everything())|> filter(Triad == "North" & treat_year_remove_prelim  != 10000) |>
  group_by(pin) |>
  arrange(pin) |>
  mutate(d_price = sale_price- dplyr::lag(sale_price), .after = sale_price) |> ungroup()
                                                                                        

beta_hat <- with(df_fe,
  sum(x_dd * y_dd, na.rm = TRUE) /
  sum(x_dd^2, na.rm = TRUE)
)

beta_hat


```

```{r}
df_fe <- df_prep |>
  dplyr::group_by(pin) |>
  dplyr::mutate(y_w = log(sale_price) - mean(log(sale_price))) |>
  dplyr::ungroup() |>
  dplyr::group_by(sale_year, event_remapped) |>
  dplyr::mutate(y_w = y_w - mean(y_w)) |>
  dplyr::ungroup() |> 
  select(y_w,  addedto_prelim_sfha, removedfrom_prelim_sfha, everything())

df_treatment <- df_prep |>
  dplyr::group_by(pin) |>
  dplyr::mutate(y_w = log(sale_price) - mean(log(sale_price))) |>
  dplyr::ungroup() |>
  dplyr::group_by(sale_year) |>
  dplyr::mutate(y_w = y_w - mean(y_w)) |>
  dplyr::ungroup()

```


> Skim this: https://www.bookdown.org/rwnahhas/RMPH/mlr-interaction.html

"Stratification is equivalent to interacting the effect modifier with every other predictor in the model whereas including an interaction only interacts the effect modifier with the predictor of interest"

## FIRM updates as Information Events

**Average Within-Parcel Effect of SFHA Status (PIN × Year FE)**

The “countywide” models average within-parcel response to SFHA status, aggregated across all parcels that ever change status. `in_eff_sfha` ignores asymmetric effects of being added or removed to the SFHA. `addedto_eff_sfha` and `removedfrom_eff_sfha` allow for estimation of the effect of being added or removed from an SFHA without assuming that the effect is symmetric.

$\log(p_{it}) = \beta_1 \text{in_eff_sfha}_{it} + \gamma_i + \eta_t + \varepsilon_{it}$

$\log(p_{it}) = \beta_1 \text{in_eff_sfha}_{it} + \beta_2 \text{Triad} + \beta_{3} (\text{in_eff_sfha}_{it} \times \text{Triad}) + \gamma_i + \eta_t + \varepsilon_{it}$

$\log(p_{it}) = \beta_1 \text{SFHA Added}_{it} + \beta_2 \text{SFHA Removed}_{it} + \gamma_i + \eta_t + \varepsilon_{it}$

$\log(p_{it}) = \beta_1 \text{SFHA Added}_{it} + \beta_2 \text{Triad} + \beta_{3} (\text{SFHA Added}_{it} \times \text{Triad}) + \beta_1 \text{SFHA Removed}_{it}  + \beta_{3} (\text{SFHA Removed}_{it} \times \text{Triad})+ \gamma_i + \eta_t + \varepsilon_{it}$

where Triad drops out of the equation because it is time invariant.

```{r}
#| label: tbl-effective-fixedeffects-allmodels
#| tbl-cap: "**Average Effect of EFFECTIVE SFHA Status** Within-parcel effect of SFHA exposure over time. Only identifies the effect if SFHA status changes for a parcel. For always-in or always-out parcels, FE wipe out the variation. Interacting with Triad allows for regioinal heterogeneity in the effect."
#| error: true
#| warning: true
#| message: true




effective_twfe <- bind_models(
  # Average effect (ATE): in_eff_sfha
  run_by_cluster(
    log(sale_price) ~ in_eff_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Eff SFHA - County ATE"
  ),

  # Asymmetric: added vs removed
  run_by_cluster(
    log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
   prefix = "Eff County - Both Togeth"
  ),
  # # Asymmetric: added
  # run_by_cluster(
  #   log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
  #   data = df_prep,
  #   clusters = clusters_county,
  #  prefix = "Eff County - Added"
  # ),
  
  #   run_by_cluster(
  #   log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
  #   data = df_prep |> filter(treat_year_remove_eff == 10000),
  #   clusters = clusters_county,
  #  prefix = "Eff County - Added - No Rem"
  # ),
  # 
  #     run_by_cluster(
  #   log(sale_price) ~ addedto_eff_sfha | pin + sale_year,
  #   data = df_prep |> filter(change_type !=  "Always SFHA" & treat_year_remove_eff == 10000),
  #   clusters = clusters_county,
  #  prefix = "Eff County - Added - Subset"
  # ),
  
  run_by_cluster(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
   prefix = "Eff County - Remove"
  ),
  
  run_by_cluster(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_add_eff== 10000),
    clusters = clusters_county,
   prefix = "Eff County - Remove - No Add"
  ),
    run_by_cluster(
    log(sale_price) ~ removedfrom_eff_sfha | pin + sale_year,
    data = df_prep |> filter(change_type != "Never SFHA" & treat_year_add_eff== 10000),
    clusters = clusters_county,
   prefix = "Eff County - Remove - Subset"
  ),


  # Heterogeneity by Triad (interaction spec)
  run_by_cluster(
    log(sale_price) ~ addedto_eff_sfha*Triad + removedfrom_eff_sfha*Triad | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
   prefix = "Eff Triads - Add or Remove"
  ),

  # 
  # # Heterogeneity by Triad (interaction spec)
  # run_by_cluster(
  #   log(sale_price) ~ addedto_eff_sfha*Triad | pin + sale_year,
  #   data = df_prep |> filter(change_type !=  "Always SFHA" & treat_year_remove_eff == 10000),
  #   clusters = clusters_county,
  #  prefix = "Eff Triads - Add - Subset"
  # ),


  # Heterogeneity by Triad (interaction spec)
  run_by_cluster(
    log(sale_price) ~  removedfrom_eff_sfha | pin + sale_year^Triad,
    data = df_prep |> filter(change_type != "Never SFHA" & treat_year_add_eff== 10000),
    clusters = clusters_county,
   prefix = "Eff Remove - Year^Triad FE"
  )
)

all_models_formatted <- modelsummary::modelsummary(effective_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```

```{r}
#| label: tbl-prelim-ate-allmodels
#| tbl-cap: "**Average Effect of Preliminary SFHA Status** Within-parcel effect of SFHA exposure over time. Only identifies the effect if SFHA status changes for a parcel. For always-in or always-out parcels, FE wipe out the variation and group them together as the comparison group. Interacting with Triad allows for regional heterogeneity in the effect."



prelim_twfe <- bind_models(
  # Average effect (ATE): in_prelim_sfha
  run_by_cluster(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Prelim SFHA - County"
  ),

  # Asymmetric: added vs removed
  run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha + removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Prelim County - Both Togeth"
  ),
  
  run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Prelim County- Add"
  ),

    run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    data = df_prep |> filter(treat_year_remove_prelim == 10000),
    clusters = clusters_county,
    prefix = "Prelim County- Add - No Remove"
  ),
  # 
  # run_by_cluster(
  #   log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year + qtr,
  #   data = df_prep |> filter(treat_year_remove_prelim == 10000),
  #   clusters = clusters_county,
  #   prefix = "Prelim County- Add - No Remove - Qtr FE"
  # ),
  
  
    run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha  | pin + sale_year,
    data = df_prep |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000),
    clusters = clusters_county,
    prefix = "Prelim County- Add - Subset"
  ),

    run_by_cluster(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
   prefix = "Pre County - Remove"
  ),
  
  run_by_cluster(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_add_prelim == 10000),
    clusters = clusters_county,
   prefix = "Pre County - Remove - No Add"
  ),
  # 
  # run_by_cluster(
  #   log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year + qtr,
  #   data = df_prep |> filter(treat_year_add_prelim == 10000),
  #   clusters = clusters_county,
  #  prefix = "Pre County - Remove - No Add - Qtr FE"
  # ),
  # 
  
    run_by_cluster(
    log(sale_price) ~ removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000),
    clusters = clusters_county,
   prefix = "Pre County - Remove - Subset"
  ),
  # Heterogeneity by Triad: in_prelim_sfha * Triad
  run_by_cluster(
    log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Prelim SFHA - Triads"
  ),

  # Heterogeneity by Triad: added/removed interacted with Triad
  run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha*Triad + removedfrom_prelim_sfha*Triad | pin + sale_year,
    data = df_prep,
    clusters = clusters_county,
    prefix = "Prelim Triads - Both Togeth"
  ),
    # Heterogeneity by Triad: added interacted with Triad
  run_by_cluster(
    log(sale_price) ~ addedto_prelim_sfha*Triad  | pin + sale_year,
    data = df_prep |> filter(change_type_prelim != "Always SFHA" & treat_year_remove_prelim == 10000),
    clusters = clusters_county,
    prefix = "Prelim Triads - Add - Subset"
  ),
    # Heterogeneity by Triad: added interacted with Triad
  run_by_cluster(
    log(sale_price) ~  removedfrom_prelim_sfha*Triad | pin + sale_year,
    data = df_prep |> filter(change_type_prelim != "Never SFHA" & treat_year_add_prelim == 10000),
    clusters = clusters_county,
    prefix = "Prelim Triads - Remove - Subset"
  )
)

all_models_formatted <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted
```


$\log(p_{it}) = \beta_1 \text{SFHA Added}_{it} + \beta_2 \text{Triad}_{it} + \beta_{3} (\text{SFHA Added}_{it} \times \text{Triad}) + \gamma_i + \eta_t + \varepsilon_{it}$

where the sample excludes properties that were removed from the SFHA.


$\log(p_{it}) = \beta_1 \text{SFHA Removed}_{it} + \beta_2 \text{Triad}_{it} + \beta_{3} (\text{SFHA Removed}_{it} \times \text{Triad}) + \gamma_i + \eta_t + \varepsilon_{it}$

where the sample excludes properties that were added to the SFHA.


### Subset to just properties Always in SFHA or Changed SFHA (specifically removed from)

Exclude properties that were never in SFHA.  

$\log(p_{it}) = \beta_1 \text{SFHA Removed}_{it} + \beta_2 \text{Triad}_{it} + \beta_{3} (\text{SFHA Removed}_{it} \times \text{Triad}) + \gamma_i + \eta_t + \varepsilon_{it}$   

where the sample excludes properties that were added to the SFHA.

```{r}
#| label: tbl-filteredproperties-forRQ
#| tbl-cap: "Restricts the sample to parcels whose classification changed from in → out between FIRMs with comparison group of only properties that were Always in an SFHA."


df_sub <- df_prep |> filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff ==10000 & treat_year_add_prelim == 10000)

valid_cohorts <- df_sub |>
  group_by(pre_date_chr) |>
  summarise(
    n = n(),
    n_treated = sum(removedfrom_prelim_sfha == TRUE, na.rm = TRUE),
    n_untreated = sum(removedfrom_prelim_sfha == FALSE, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(n_treated > 0, n_untreated > 0) |>
  pull(pre_date_chr)

df2 <- df_sub |>filter(pre_date_chr %in% valid_cohorts)

prelim_twfe <- bind_models(
  run_by_cluster(
    log(sale_price) ~ in_prelim_sfha | pin + sale_year,
    data = df2,
    clusters = clusters_county,
    prefix = "Prelim SFHA (filtered sample)"
  ),

  run_by_cluster(
    log(sale_price) ~ in_prelim_sfha*Triad | pin + sale_year,
    data = df2,
    clusters = clusters_county,
    prefix = "Prelim SFHA × Triad (filtered sample)"
  )
)

all_models_formatted_prelim <- modelsummary::modelsummary(prelim_twfe,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted_prelim
```

Exclude properties that were Always in SFHA.

Coefficient is hopefully the local average treatment effect (LATE).

$\log(p_{it}) = \beta_1 \text{SFHA Added}_{it} + \beta_2 \text{Triad}_{it} + \beta_{3} (\text{SFHA Added}_{it} \times \text{Triad}) + \gamma_i + \eta_t + \varepsilon_{it}$

where the sample excludes properties that were added to the SFHA.

**Added to SFHA compared to properties that were never in the SFHA**. Comparison group excludes properties that were always in the SFHA and those that were removed from the SFHA at some point.

```{r}
#| label: tbl-mappedin-prelim-fsplit
#| tbl-cap: "**Part of Table 6.** Comparison group is only PINs in same FIRMs that were updated that were never in an SFHA."

df_sub <- df_prep |> 
  filter(change_type != "Always SFHA" & 
                           # and properties that are never treated for being removed to the SFHA
                    treat_year_remove_prelim == 10000  )
                  

valid_cohorts <- df_sub |>
  group_by(pre_date_chr) |>
  summarise(
    n = n(),
    n_treated = sum(addedto_prelim_sfha == TRUE, na.rm = TRUE),
    n_untreated = sum(addedto_prelim_sfha == FALSE, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(n_treated > 0, n_untreated > 0) |>
  pull(pre_date_chr)
  
df_sub |> filter(pre_date_chr %in% valid_cohorts) |> feols(log(sale_price) ~ addedto_prelim_sfha | pin + sale_year,
        fsplit= ~pre_date_chr,
        cluster = ~pin10
        
  ) |> modelsummary(stars = TRUE)
```

**Removed from SFHA compared to properties that were still in the SFHA**. Comparison group excludes properties that were never in the SFHA and those that were added to the SFHA at some point.


```{r}
#| label: tbl-mappedout-prelim-restricteddfirm
#| tbl-cap: "**Part of Table 5. Restricted sample to DFIRM updated in 2015** Comparison group is only PINs in same FIRMs that were updated. that were always in SFHA"
#| error: true
#| warning: true
#| message: true

df_sub <- df_prep |> filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000 ) 

valid_cohorts <- df_sub |>
  group_by(pre_date_chr) |>
  summarise(
    n = n(),
    n_treated = sum(removedfrom_prelim_sfha == TRUE, na.rm = TRUE),
    n_untreated = sum(removedfrom_prelim_sfha == FALSE, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(n_treated > 0, n_untreated > 0) |>
  pull(pre_date_chr)
  
df3 <- df_sub |> filter(pre_date_chr %in% valid_cohorts)
  
removed_models <- list( 
  mod1 <- feols(log(sale_price) ~ i(sale_year, removedfrom_prelim_sfha) | pin + Triad,
      data = df3,
          fsplit= ~ pre_date_chr,
      cluster = ~ pin10
)
) 

all_models_formatted_prelim_removed_dfirm <- modelsummary::modelsummary(removed_models,
               output = "flextable",
               fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted_prelim_removed_dfirm


```

```{r}
#| label: tbl-mappedout-prelim-withlomrs
#| tbl-cap: "**Part of Table 5. Has LOMRs for removal."
#| error: true
#| warning: true
#| message: true

df_sub <- df_prep |> 
 # mutate(removedfrom_prelim_sfha = ifelse( in_prelim_sfha == TRUE & in_lomr ==TRUE, removedfrom_prelim_sfha == TRUE, removedfrom_prelim_sfha ) ) |>

filter(change_type != "Never SFHA" & 
                           # and properties that are never treated for being added to the SFHA
                           treat_year_add_eff == 10000 & treat_year_add_prelim == 10000) 

valid_cohorts <- df_sub |>
  group_by(pre_date_chr) |>
  summarise(
    n = n(),
    n_treated = sum(removedfrom_prelim_sfha == TRUE, na.rm = TRUE),
    n_untreated = sum(removedfrom_prelim_sfha == FALSE, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(n_treated > 0, n_untreated > 0) |>
  pull(pre_date_chr)
  
df3 <- df_sub |> filter(pre_date_chr %in% valid_cohorts)

removed_models <- list( 

  mod1 <- feols(log(sale_price) ~ sw(removedfrom_prelim_sfha*in_lomr) | pin + sale_year,
      data = df3,
          fsplit= ~ pre_date_chr,
      cluster = ~pin10
)

) 

all_models_formatted_prelim_removed_dfirm <- modelsummary::modelsummary(removed_models,
               output = "flextable",
               fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted_prelim_removed_dfirm


```
