---
title: "Cook County Parcel Sales"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---

# Data Sources and Background Information

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
library(skimr)

```



> Sales are not winsorized

```{r}
res_sales  <- readRDS("./data/processed/res_sales.rds") |> filter(sale_date > date("2010-01-01"))  


pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

nicknames <- readxl::read_xlsx("../Merriman RA/ptax/Necessary_Files/muni_shortnames.xlsx")

pin_muni_key <- pin_muni_key |> left_join(nicknames)


# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N Lakeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000"     # another CoOp
               
)

res_sales <- res_sales |> filter(pin %nin% drop_pins )


repeat_sales <- res_sales |> 
  
  group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup() |> 

  # a couple outliers were in there
  filter( sale_price < 5000000)

```

```{r dropped_pins}

# price corrections randomly spotted
repeat_sales <- repeat_sales |> 
  mutate(sale_price = 
         case_when(
           pin == "15154220240000" & sale_date == as_date("2006-11-01") ~ 180000,   # not 180 million
           pin == "08153010051151" ~ 81000, # not 81 million
         TRUE ~ sale_price
         ))


```


```{r}
# 1) Make sure sale_date is a Date (if not already)
df_prep <- repeat_sales %>%
  filter(pin %nin% drop_pins) |> 
  
  mutate(
    sale_year  = year(sale_date),
    eff_date = ymd(EFF_DATE),
    pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date, sale_year, sale_price, in_eff_sfha, in_prelim_sfha, 
         eff_date, pre_date, in_lomr) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),
    in_sfha_t1      = ifelse(is.na(in_sfha_t1), "Not SFHA", in_sfha_t1),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha
  ) %>%

  ungroup() |> 
  # get rid of redundant variables that would be confusing
  select(-c(sale_price, sale_date, sale_year, in_eff_sfha))



df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)        
        # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")),  # between sales
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),    # between sales
        years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
        ann_d_log_price = d_log_price / years_btwn,

    
    # SFHA change as a factor variable
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
  ) |>
  
  # add additional location variables (Triad, township, municipality, etc)
  left_join(pin_muni_key)

df_pairs <- df_pairs |> filter(change_type != "OTHER")



df_pairs <- df_pairs |> 
  mutate(
    
    # relative time variables 
    t_months_eff = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
    
    t_years_eff = round(time_length(sale_date_t1 - eff_date, "years") ),    # first sale to FIRM update, in years

    t_months_prelim = round(time_length(sale_date_t1 - pre_date, "months") ), # first sale to FIRM update, in months

    t_years_prelim = round(time_length(sale_date_t1 - pre_date, "years") ),    # first sale to FIRM update, in years

  )|>
  # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1))

df_pairs <- df_pairs |> 
  select(pin, 
         ann_d_log_price, d_log_price,
         sale_year_t1, sale_price_t1, in_sfha_t1, 
         sale_year_t2, sale_price_t2, in_sfha_t2, 
         years_btwn, change_type, everything()
  )

df_pairs <- df_pairs |> 
  mutate(change_type = factor(change_type, levels = c("Both Out of SFHA", "Both In SFHA", "Added", "Removed")))
```


```{r}
table(df_pairs$years_btwn, df_pairs$change_type)

table(df_pairs$sale_year_t2, df_pairs$change_type)
```

```{r descriptive-stats-df_prep}
skim(df_prep)
```


```{r descriptive-stats-df_pairs}
skim(df_pairs)
```

# Research Question 2

On June 29th, 2020, First Street Foundation released their flood risk data and the Flood Factor. Provided flood risk data for inland areas that were typically overlooked in FEMA flood maps.

**Does information on flood risk available to the buyer get capitalized into the property value? If so, to what extent? Is this effect moderated by pre-existing information unavailable to the buyer?**

H3: A High risk rating score available to the buyer from First Street will be associated with a larger decrease in the value of the properties outside of an SFHA than properties in an SFHA.




```{r}
#ff_scores <- read_csv("data/raw/floodfactor_scores.csv")

puni_pins <- read_csv("./data/raw/parcel_universe_currentyear.csv") |> 
  mutate(pin7 = str_sub(pin, 1, 7))

pin_muni_key <- left_join(pin_muni_key, puni_pins)

```


```{r}
df_pairs <- left_join(df_pairs, pin_muni_key)

df_prep <- left_join(df_prep, pin_muni_key)

df_prep <- df_prep |> 
  mutate(
    event = ifelse(sale_date < as_date("2020-06-29"), "1. Pre", "2. Post"),
    high_ff_score = ifelse(env_flood_fs_factor > 4, TRUE, FALSE),
  )

n_distinct(df_pairs$pin)

df_pairs <- df_pairs |> 
  mutate(ff_factor = factor(env_flood_fs_factor))


## Create event indicators

## if the first sale was before the release and the next sale was after the release, then coded as TRUE, otherwise, FALSE
ff_pairs <- df_pairs |>  
  mutate(
    treated = ifelse(sale_date_t1 < as_date("2020-06-29") & sale_date_t2 >= as_date("2020-06-29"), TRUE, FALSE),
    high_ff_score = ifelse(env_flood_fs_factor > 4, TRUE, FALSE),
    new_info_released = ymd("2020-06-29")
  )




ff_pairs |> filter(treated ==TRUE
                   & env_flood_fema_sfha == TRUE)

ff_pairs |> filter(treated ==TRUE &
                  high_ff_score == TRUE)

ff_pairs |> filter(treated ==TRUE
                   & change_type %in% c("Added", "Removed"))


table(ff_pairs$high_ff_score, ff_pairs$treated)
table(ff_pairs$high_ff_score, ff_pairs$change_type)

```

## Graphs


```{r}
ff_pairs |> 
  filter(sale_date_t1 < new_info_released) |> 
    group_by(sale_year_t1, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by SFHA Change Type")


ff_pairs |> 
  filter(sale_date_t2 > new_info_released) |>
  group_by(sale_year_t2, ff_factor) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = ff_factor)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by SFHA Change Type")
```

```{r}

ff_pairs |> 
  filter(sale_date_t1 < new_info_released) |> 
    group_by(sale_year_t1, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t1 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends by FF Score 5 or higher")

ff_pairs |> 
  filter(sale_date_t2 < new_info_released & sale_year_t2 > 2015) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
  labs(title = "Pre-Treatment Trends for 2nd sale by FF Score 5 or higher")

ff_pairs |> 
  filter(sale_date_t2 > new_info_released ) |>
  group_by(sale_year_t2, high_ff_score) |> 
  summarise(mean_growth = mean(ann_d_log_price, na.rm = TRUE)) |> 
  ggplot(aes(x = sale_year_t2 , y = mean_growth, color = high_ff_score)) +
  geom_line() +
  geom_point() + 
  labs(title = "Post-Treatment Trends by FF Score 5 or higher")
```


## Models

```{r}
#| column: page
#| label: tbl-proposal-models-ffscores
#| tbl-cap: "Model in proposal"


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ change_type,       
                   data = ff_pairs,
                   cluster = ~pin
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated,
                    data = ff_pairs,
                    cluster = ~pin
                    
      )
    ),
        "Ordinal" = list(
      
      "I" = feols(d_log_price ~ change_type+ env_flood_fs_factor*treated,       
                  data = ff_pairs,
                  cluster = ~pin
      ),
      
      "II" = feols(d_log_price ~ env_flood_fs_factor*change_type,       
                   data = ff_pairs,
                   cluster = ~pin
                    
      )
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

```{r}
#| column: page
#| label: tbl-fixedeffects-models-ffscores
#| tbl-cap: "Control for Municipality"


  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(d_log_price ~ high_ff_score | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(d_log_price ~ change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                   
      ),
      "III" = feols(d_log_price ~ high_ff_score*treated | clean_name,
                    data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    ),
        "Ordinal" = list(
      
      "I" = feols(d_log_price ~ change_type+ env_flood_fs_factor*treated | clean_name,       
                  data = ff_pairs,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(d_log_price ~ env_flood_fs_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      ),
      
      "II" = feols(d_log_price ~ ff_factor*change_type | clean_name,       
                   data = ff_pairs,
                  cluster = ~pin + clean_name
                    
      )
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

                                                                                 

## using df_prep

```{r}

  all_models <- list(
    
    "High or Low" = list(
      
      "I" = feols(log(sale_price) ~ high_ff_score | clean_name,       
                  data = df_prep,
                  cluster = ~pin + clean_name
      ),
      
      "II" = feols(log(sale_price) ~ high_ff_score*in_eff_sfha | clean_name,       
                   data = df_prep,
                  cluster = ~pin + clean_name
                   
      ),
      "muni fe" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "pin fes" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "2 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin+ clean_name,
                    data = df_prep,
                  cluster = ~pin + clean_name
                    
      ),
      
      "3 FEs" = feols(log(sale_price) ~ in_eff_sfha*high_ff_score*event | pin + clean_name + sale_year,
                    data = df_prep,
                    ref = 2020,
                  cluster = ~pin + clean_name
                    
      )
    
    )
    )
  
all_models_formatted <- modelsummary::modelsummary(all_models,
             shape = "cbind",    
               output = "flextable",
             fmt = function(x) round(x, 2),
             stars = TRUE)

all_models_formatted



```

