---
title: "File Overview"
format: # html
  html:
    page-layout: full
    code-fold: true
    #toc: true
    #toc-location: left
---

## Project: Flood Risk and Property Values

```{r}
library(tidyverse)
library(glue)
library(kableExtra)
library(stringr)

files <- readxl::read_xlsx("readme_file_information.xlsx")
```

```{r eval = FALSE, include = FALSE}
files <- files %>% 
  mutate(
    # turn any literal newline into a comma
    Inputs_clean  = str_replace_all(Inputs,  "\\s*\\n\\s*",  ", "),
    Outputs_clean = str_replace_all(Outputs, "\\u00A0",   ""),           # drop NBSP
    Outputs_clean = str_replace_all(Outputs_clean,  "\\s*\\n\\s*", ", ")
  )

```
```{r eval=FALSE, results='asis', include = FALSE}
files %>% 
  mutate(
    # split your comma-separated text into character vectors
    Inputs_list  = str_split(Inputs,  ",\\s*"),
    Outputs_list = str_split(Outputs, ",\\s*"),
    
    # build the markdown string for each row
    markdown = pmap_chr(
      list(
        idx    = row_number(),
        file   = File,
        purpose= Purpose,
        in_lst = Inputs_list,
        out_lst= Outputs_list,
        status = `Analysis Step`
        ),
      function(idx, file, purpose, in_lst, out_lst, status) {
        glue("
### {idx}. `{file}`  
**Purpose:**  
{purpose}

**Inputs:**  

- {paste(in_lst, collapse = '\n- ')}

**Outputs:**  

- {paste(out_lst, collapse = '\n- ')}

**Analysis Step:** {status}
")
      }
    )
  ) %>% 
  pull(markdown) %>% 
  cat(sep = "\n\n")

```

```{r results='asis'}
files |> 
  select(File, Purpose, Inputs, Outputs, `Analysis Step`) |>
  mutate(markdown = glue::glue("
### {row_number()}. `{File}`  
**Purpose:**  
{Purpose}  

**Inputs:**   

- {str_replace_all(Inputs, ', ', '\n- ')}  

**Outputs:**  

- {str_replace_all(Outputs, ', ', '\n- ')}  
")) |> 
  pull(markdown) |> 
  cat(sep = "\n\n")
```

```{r}
#| label: tbl-kabletable
#| tbl-colwidths: [15, 40, 10, 10, 10]


#DT::datatable(files)


files |> kable(booktabs = TRUE) |> #kable_paper(full_width = F) |>
  column_spec(1, width = "1in") |>
  column_spec(2, width = "3in") |>
  column_spec(3, width = "1in") |>
  column_spec(4, width = "1in") |>
  column_spec(5, width = "1in")
  
```

### Output Files


| Output                                                             | Created By                                |
|--------------------------------------------------------------------|-------------------------------------------|
| `data/raw/parcels_2018.gpkg`                                       | `pull_parcel_sfs.R`                       |
| `data/raw/parcels_2023.gpkg`                                       | `pull_parcel_sfs.R`                       | `data/processed/parcels_wFIRMs.csv`                                | `pull_parcel_sfs.R`                       | outputs/pins_in_Blocks_2006_2023_20241126.csv" | ?? |
|
| `data/raw/nfippolicies_CookCounty_all.csv`                         | `pull_NFIP_redactedclaims.R`              |
| `data/raw/nfipclaims_CookCounty.csv`                               | `pull_NFIP_redactedclaims.R`              |
| `data/raw/indiv_assistance_CookCounty.csv`                         | `pull_individual_assistance_applicants.R` |
| `data/raw/residential_pins_ever.csv`                               | `pull_distinct_resPINs.R`                 |
| `data/raw/pin_muni_key.csv`                                        | `pull_distinct_resPINs.R`                 |
| `data/raw/muniname_taxcode_key.csv`                                | `pull_distinct_resPINs.R`                 |
| `data/raw/pins_floodfactor_2019.csv`                               | `pull_floodfactor_pin_list.R`             |
| processed/ treated.csv                                                        | `make_panel_data.qmd`                     |
| raw/floodfactor_scores.csv | pull_floodfactor_pin_list.R |
| outputs/nbh_pins_parceluniversepull2022.csv | ?? |
| outputs/pins_in_Blocks_2006_2023_20241126.csv| ?? |

```{r, include=FALSE, eval=FALSE}

## Keeping just in case

### Data Preparation Scripts



| File | Purpose | Inputs | Outputs |
|-------|-----------------|-----------------|---------------------|
| `pull_distinct_resPINs.R` | Extract all parcels that were residential from 2006–2023 and pull assessed values | PTAXSIM database | `data/raw/residential_pins_ever.csv`, `pin_muni_key.csv`, `muniname_taxcode_key.csv` |
| `pull_parcel_sfs.R` | Download and convert Cook County parcel shapefiles for 2018 and 2023 | ptaxsim parcel centroids | `S_FIRM_PAN.csv`, `parcels_wFIRMS.csv` |
| `pull_floodfactor` `_pin_list.R` | Join Flood Factor risk scores (2019 snapshot) to Cook County parcel universe | Parcel universe with PINs, Flood Factor data | `data/raw/floodfactor_scores.csv` |
| `shapefile_sfha_changes.R` | Compares CCAO flood variables to NFHL. Makes shapefiles and also CSV versions of PINs that are in each SFHA or LOMR | NFHL 2018 and NFHL 2024 (NFHL_17_20180129.gdb and Statewide_NFHL_17_20240628.gdb) | sfha_indicator_pins.csv, S_FIRM_PAN.csv, parcels_sfha_2018.csv(shp), parcels_lomrs_2018.csv(shp), sfha_pins_2024.csv, lomr_pins_2024.csv, |
| `detect_flood_variable` `_change_in_CCAO` | Tries to identify if CCAO removed PINs that were in LOMRs from SFHA indicator or what year they stopped updating the LOMR data if removed | Open FEMA API | None |
| `clean_damangedCity` `_names` | Takes damagedCity variable from Open FEMA individual assistance, exports city names which had tons of typos. This was put in chatGPT to match with clean names | Open FEMA API | `data/raw/ia.city_names.csv` which becomes `data/processed/City_Mapping_Names.csv` |

------------------------------------------------------------------------

### Other External Data Exploration

| File | Purpose | Inputs | Outputs |
|-----------------|---------------------|-----------------|-----------------|
| `pull_NFIP_redactedclaims.R` | Pull NFIP policy and claims data for Cook County from FEMA API | NFIP Policies API, NFIP Claims API | `data/raw/nfippolicies_CookCounty_all.csv`, `data/raw/nfipclaims_CookCounty.csv` |
| `pull_individual_assis` `tance_applicants.R` | Pull FEMA Individual Assistance (IA) application data for Cook County (accepted and denied) | FEMA IA API | `data/raw/indiv_assistance_CookCounty.csv`, `data/processed/treated_zipcodes.csv`|
| `buyouts.R` | Identifies PINs that were bought out due to high flood risk | Illinois Buyout Database `BuyoutPoints_Statewide.xlsx` | none |

------------------------------------------------------------------------

### Exploratory & Descriptive Analysis

| File | Purpose | Inputs | Outputs |
|-----------------|----------------------|-----------------|-----------------|
| `CC_Individual_FEMA` `_Assistance.qmd` | Analyzes FEMA IA aid at ZIP level during recent flood events; descriptive stats on applicants and aid granted | `data/raw/indiv_assistance_CookCounty.csv`, `data/processed/treated_zipcodes.csv` | census block, tract, zip code, and muni level post-disaster aid data |
| `Cook_flood_policies` `_and_claims.qmd` | Summarizes NFIP claims and policies across geographies (ZIP, block, tract, muni) | `data/raw/nfipclaims_CookCounty.csv`, `data/raw/nfippolicies_CookCounty_all.csv` | Aggregated claim/policy stats. Not used except to show that there are not many claims or insurance policies in cook county. But there are a lot of post-disaster FEMA aid. |
| `Cook_Sales_data.qmd` | Links sales data with flood risk indicators (SFHA, LOMR, Flood Factor); identifies multi-sale parcels and treatment status | `data/raw/assessor_parcel_sales.csv`, `parcels_sfha_2018.gpkg`, `parcels_sfha_2024.gpkg`, `parcels_lomrs.gpkg`, `data/raw/pins_floodfactor_2019.csv` | Counts of PINs by treatment status, sales trends |
| `make_panel_data.qmd` | | | |
| AssessedValues_ andFIRMS.qmd | | | | 
| descriptive_stats _singlefam.qmd | | | | 
| mcmillen_sales comparison.qmd | | | | 
| `Flood_factor_pins.qmd` ARCHIVED | Filter for PINs with Flood Factor ≥ 5; analyze post-2023 PTAX-245 flood appeals; calculates AV changes in affected land blocks | Parcel universe API, PTAX-245 appeal forms | Summary tables and figures |
| `Flood_Appeal_PINs.qmd` ARCHIVED | Identifies and summarizes AV appeal activity for PINs affected by 2023 flood; compares AV changes for appeal vs. neighbor parcels | PTAX-245 appeal forms, assessed values | Graphs of average AV changes, summary stats |
| `AssessedValue_Explor` `atoryGraphs.rmd` ARCHIVED | Early exploration of AV trends in SFHA and flood-prone parcels using CCAO data | Parcel universe, AV data | Exploratory graphs and maps |
| `CookCounty_ParcelMaps.qmd` ARCHIVED | Early mapping of parcels marked SFHA in CCAO data; not currently used | CCAO parcel universe | Static SFHA parcel maps |


```

------------------------------------------------------------------------

### Data Cleaning Notes

Do filtering steps last. Keep all property classes until creating the panel dataset for analysis.

```{r eval=FALSE, include=FALSE}

## File Overview




------------------------------------------------------------------------

### X. `Models.qmd.R`

**Purpose:**\
Based off of cook_sales_Data.qmd but removes a lot of the preliminary coding chunks

**Output:**\


**Status:** Active - update and use more

------------------------------------------------------------------------

### X. `descriptive_stats_singlefam.qmd`

**Purpose:**\
has checklist of variables/code that needs to be done

**Output:**\


**Status:** Active ? Use more!

------------------------------------------------------------------------

### 1. `pull_distinct_resPINs.R`

**Purpose:**\
Extracts PINs that were residential at any time (2006–2023) using PTAXSIM and pulls corresponding assessed values. Also generates PIN–municipality key.

**Output:**\
- `data/raw/residential_pins_ever.csv`\
- `data/raw/pin_muni_key.csv`\
- `data/raw/muniname_taxcode_key.csv`

**Status:** Active

------------------------------------------------------------------------

### 2. `pull_parcel_sfs.R`

**Purpose:**\
Downloads parcel shapefiles for Cook County for two time points: 2018 and 2023. Converts shapefiles into spatial databases.

**Output:**\
- ~~`data/raw/parcels_2018.gpkg`~~\
- ~~`data/raw/parcels_2023.gpkg`~~\
- S_FIRM_PAN.csv\
- parcels_wFIRMS.csv

**Status:** Active

------------------------------------------------------------------------

### 5. `pull_floodfactor_pin_list.R`

**Purpose:**\
Pulls 2019 Flood Factor scores and SFHA indicator used by Assessor from parcel universe.

**Output:**\
- `data/raw/floodfactor_scores.csv` with variables `env_flood_factor_score`, `env_flood_factor_risk_direction`, `env_flood_fema_sfha`, and `nbhd_code` for the neighborhoods used by the Assessor during property valutation.

**Status:** Active

------------------------------------------------------------------------

### 6. `Flood_factor_pins.qmd`

**Purpose:**\
Filters for PINs with Flood Factor ≥ 5; integrates PTAX-245 appeal data after the 2023 flood; calculates differences in AV before and after appeals in affected land blocks.

**Output:**\
- Summary tables and figures on AV changes from appeals

**Status:** Archived

------------------------------------------------------------------------

### 7. `Flood_Appeal_PINs.qmd`

**Purpose:**\
Identifies PINs that submitted PTAX-245 forms after the 2023 flood and compares changes in AV due to appeals across affected and nearby properties.

**Output:**\
- Graphs and summary tables of AV differences

**Status:** Archived

------------------------------------------------------------------------

### 8. `CC_Individual_FEMA_Assistance.qmd`

**Purpose:**\
Summarizes FEMA IA data by ZIP code. Focuses on descriptive statistics and trends for recent flood events and aid received.
Identifies treated areas of Cook County that experienced flood damage using post-disaster aid data.

**Input:**\
- `data/raw/indiv_assistance_CookCounty.csv`

**Output:**\
- ZIP-level descriptive statistics\
- Summary tables and visualizations by event  
- `data/processed/treated_zipcodes.csv`  


**Status:** Active

------------------------------------------------------------------------

### 9. `Cook_flood_policies_and_claims.qmd`

**Purpose:**\
Uses NFIP policy and claim data to summarize flood damage at various geographies (ZIP code, census block, census tract, municipality).

**Input:**\
- `data/raw/nfipclaims_CookCounty.csv`\
- `data/raw/nfippolicies_CookCounty_all.csv`

**Output:**\
- Aggregated stats by spatial unit

**Status:** Active

------------------------------------------------------------------------

### 10. `Cook_Sales_data.qmd`

**Purpose:**\
Integrates sales data with SFHA, LOMR, and Flood Factor overlays. Identifies PINs sold multiple times and tracks treatment exposure.
Models.qmd is based off of this file.

**Input:**\
- `parcels_wFIRMs.csv`
- `data/raw/assessor_parcel_sales.csv`\
- `pin_muni_key.csv`\ 
- `parcels_sfha_2018.shp`\
- `parcels_sfha_2024.shp`\
- `parcels_lomrs_2024.shp` becomes `lomr_pins_2024.csv`\
- `data/raw/pins_floodfactor_2019.csv`\
- nbh_pins_parceluniversepull2022.csv\
- Parcels_in_PrelimFIRMSFHA_NWCook.xlsx\

**Output:**\
- Summary of sales by treatment group\
- Stats on repeat sales and exposure

**Status:** Active? Archived? 

------------------------------------------------------------------------

### 11. `AssessedValue_andFIRMs.qmd`

**Purpose:**\
Early exploration of AV trends for parcels inside and outside SFHAs using CCAO data. Includes preliminary figures and mapping.
Codes PINs by if they have a building on the parcel or not. 

**Input:**\
- Parcel universe\
- AV data

**Output:**\
- `outputs/pins_in_Blocks_2006_2023_20241126.csv`


**Status:** New but not used?

------------------------------------------------------------------------

### 11. `AssessedValue_ExploratoryGraphs.rmd`

**Purpose:**\
Early exploration of AV trends for parcels inside and outside SFHAs using CCAO data. Includes preliminary figures and mapping.
Codes PINs by if they have a building on the parcel or not. 

**Input:**\
- Parcel universe\
- AV data

**Output:**\
- Exploratory maps and graphs of AV trends by risk status  
- `outputs/pins_in_Blocks_2006_2023_20241126.csv`  

**Status:** Archived

------------------------------------------------------------------------

### 12. `CookCounty_ParcelMaps.qmd`

**Purpose:**\
Initial mapping of parcels marked SFHA using CCAO parcel universe. Made for exploratory purposes and currently unused.

**Input:**\
- CCAO parcel universe

**Output:**\
- Parcel maps with SFHA indicators

**Status:** Archived

------------------------------------------------------------------------

### 2. `pull_NFIP_redactedclaims.R`

**Purpose:**\
Pulls National Flood Insurance Program (NFIP) claims and policy data from FEMA’s open API, filtered to Cook County, IL.

**Output:**\
- `data/raw/nfippolicies_CookCounty_all.csv`\
- `data/raw/nfipclaims_CookCounty.csv`

**Status:** Active

------------------------------------------------------------------------

### 3. `pull_individual_assistance_applicants.R`

**Purpose:**\
Downloads FEMA Individual Assistance (IA) data from the OpenFEMA API for Cook County. Includes both approved and denied applications.

**Output:**\
- `data/raw/indiv_assistance_CookCounty.csv`

**Status:** Active

------------------------------------------------------------------------

### X. `DAG_chart.qmd`

**Purpose:**\
had variable dag charts 

**Output:**\

**Status:** Not Used

```

------------------------------------------------------------------------


Create a long-format dataset with:

PIN \| year \| in_sfha \| flood_factor_score \| in_lomr \| av \| sale_price \| sold \| treatment \| post

Key Variables:

-   year: Matching the time of assessment or sale

-   in_sfha: 0/1 for floodplain presence that year

-   flood_factor_score: Ordinal flood risk score (e.g., 1–10)

-   in_lomr: 0/1 if parcel is in a LOMR revision area that year

-   av: Assessed value that year

-   sale_price: Sale price (if sold that year)

-   sold: 0/1 if there was a sale

-   treatment: 1 if the PIN was ever added to (or removed from) the SFHA (i.e., eligible for treatment)

-   post: 1 if observation is after the map change

-   added_to_sfha = (in_sfha_2024 == 1 & in_sfha_2018 == 0) removed_from_sfha = (in_sfha_2024 == 0 & in_sfha_2018 == 1)

-   treatment = 1 if added_to_sfha \| removed_from_sfha

If you're using multiple years of sales and assessed values, define:

-   post = 1 for all years after the map change

-   pre = 1 for years before

Optionally use event_time = year - treatment_year to do event study style DiD
