---
title: "Create df_pairs from Sales data"
format: 
  html:
    code-fold: true
    code-tools: true
    df-print: paged
    toc: true
    toc-location: left
    tbl-cap-location: margin
    fig-cap-location: top
---


# Data Prep

Code from [CCAO](https://ccao-data.github.io/assessr/articles/example-ratio-study.html).

Description of functions and [measurements](https://ccao-data.github.io/assessr/reference/index.html).

Parcel shapefile used in ArcGIS Pro is downloaded from CCAO's Archived 2022 parcel dataset [here.](https://datacatalog.cookcountyil.gov/Property-Taxation/ccgisdata-Parcel-2021/77tz-riq7/about_data)

```{r setup, warning=FALSE, message=FALSE}
library(DescTools)
library(sf)
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
library(fixest)
```



> Coding note: sale_price can be winsorized by grouping the year & major class (technically the 1st digit of the class code). Check that this is how you want it to be winsorized. It is currenty commented out and NOT WINSORIZED.

> If property is in SFHA and LOMR, both variables will be coded as 1. I no longer "remove" the SFHA indicator if it is in a LOMR. 


# Sales Data

1,762,627 sales for all property classes (1,869,796 after new download in January)

1,070,348 sales for Class 2 Residential properties (1,655,745 after new download and identifying any pin that was residential at any point in time and including it)


> TO DO: Use grepl() to identify properties bought by municipalities? list of Muni names and if they are similar to the buyer name? Useful for flagging buyouts?


# Frequency of Sales

`res_sales` includes any pin that was residential at some point in time. 

 
```{r}
#sales      <- readRDS("./data/processed/sales_prepped.rds")
res_sales  <- readRDS("./data/processed/res_sales.rds") 


pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")
nicknames <- readxl::read_xlsx("../Merriman RA/ptax/Necessary_Files/muni_shortnames.xlsx")

pin_muni_key <- pin_muni_key |> left_join(nicknames)


# sampled_data <- res_sales |> 
#   sample_frac(0.05)
# write_csv(sampled_data, 
#           "data_sample.csv")

```





## Sales

### Condo Sales

```{r}
#| label: tbl-condorepeatsalesPINs
#| tbl-cap: "**How many condos in floodplains are repeat sales?** Around 9000 Condo PINs with repeat sales. Class 297s are special residential improvements and usually apply to condos and included in these filters." 

res_sales |> 
  filter(in_eff_sfha == "SFHA") |>
  filter(class %in% c(297, 298, 299)) |>
  reframe(n=n(), .by = "pin") |> 
            filter(n >= 2)
```


```{r}
#| label: tbl-condorepeatsales-parcels
#| tlb-cap: "**How many distinct parcels with condos with repeat sales and in floodplains?**  Around 400 parcels with repeat sales." 

res_sales |> 
  filter(in_eff_sfha == "SFHA") |>
  filter(class %in% c(297, 298, 299)) |>
  reframe(n=n(), .by = "pin10") |> 
            filter(n >= 2)
```

**Are there CoOps and other weird properties in floodplains?** -- NO, filter these property classes out and don't worry about them.

#### Manual PIN or parcel exclusion from SFHA

Code above helped identify parcels that coded as condos but are separate homes. The parcel itself owns a pond in an SFHA, which coded all PINs as in the SFHA. Manually recoding below.

```{r}
res_sales <- res_sales |> 
  mutate(
    in_eff_sfha = 
      case_when(
        pin10 =="0210406033" ~ "Not SFHA", # parcel owns a pond which is in the SFHA. Lots of "condos" on this parcel that are separate townhomes but no building outlines are in floodplain
        pin10 == "0212410056" ~ "Not SFHA", 
        pin10 == "0214100090" ~ "Not SFHA",  # Actual vertical condo, but building outline is not in SFHA
        pin10 == "0426103043" ~ "Not SFHA", # is in 1-500 year floodplain though
      TRUE ~ in_eff_sfha
        ),
    in_prelim_sfha = case_when(
              pin10 =="0210406033" ~ "Not SFHA", # parcel owns a pond which is in the SFHA. Lots of "condos" on this parcel that are separate townhomes but no building outlines are in floodplain
        pin10 == "0212410056" ~ "Not SFHA", 
        pin10 == "0214100090" ~ "Not SFHA",  # Actual vertical condo, but building outline is not in SFHA
        pin10 == "0426103043" ~ "Not SFHA", # is in 1-500 year floodplain though
        TRUE ~ in_prelim_sfha 
      )
    )
```


```{r}
table(res_sales$in_eff_sfha)

```

### Non-Condo Repeat Sales 

```{r}

repeat_sales <- res_sales |> 
  group_by(pin) |> 
  mutate(times_sold = n()) |> 
  filter(times_sold > 1) |> 
  ungroup() # |>
#  filter(class %nin% c("297", "298", "299"))
  

#res_sales |> group_by(pin, sale_date) |> n_distinct()
```

```{r dropped_pins}
# price corrections randomly spotted
repeat_sales <- repeat_sales |> 
  mutate(sale_price = 
         case_when(
           pin == "15154220240000" & sale_date == as_date("2006-11-01") ~ 180000,   # not 180 million
         TRUE ~ sale_price
         ))


# problem pins for various reasons
drop_pins <- c("05272000470000",  # co op
               "17103180800000",  # became 325 W Wacker Drive, the building that looks like water waves, condo in loop
               "14281050350000",  # is a condo building, whole building bought in 2006, Currently classed as land? probably due to remodeling permit? 
               "10191030030000",     # land trust sale and then maybe split into other pins?
               "17032220150000",   #  becomes 880 N LakeShore Drive and is a CoOp
               "17032220180000",   # also part of 880 N Lakeshore Dr  and is  a CoOp
               "17032220200000",    # ditto
               "05272000010000"     # another CoOp
               
)
```


```{r inspect-highmultisales}
repeat_sales |> filter(times_sold > 5) |> arrange(desc(sale_price))

repeat_sales |> filter(times_sold > 5) |>  filter(pin %nin% drop_pins) |> arrange(desc(sale_price))

repeat_sales |> 
  filter(num_parcels_sale > 10) |> 
  arrange(pin, desc(num_parcels_sale)) |>
  select(pin, year, num_parcels_sale, sale_price, in_eff_sfha, class, everything())

repeat_sales |> filter(times_sold > 5) |> 
  ggplot() + 
  geom_line(aes(x=sale_date, y = sale_price, group = pin))
```

```{r}
table(repeat_sales$times_sold)

table(repeat_sales$PRE_DATE)

table(repeat_sales$year, repeat_sales$in_eff_sfha)
table(repeat_sales$year, repeat_sales$in_lomr)

```


```{r}
#| label: fig-pinsales
#| fig-cap: "PIN Sale Price Over time."
#| fig-subcap: 
#| - pin == 09163040191019. Flood Factor 6/10 & in SFHA. 1675 E Mills St. Des Plaines IL. Condo building.
#| - pin == 05201210150000. Flood Factor 6/10 & in SFHA. 1103 Willow Rd Winnetka. (Side note, this is in New Trier Township, if worried about Assessor's timing of using the flood zone variables in assessment models). Class 207 for first sale and then class 205 for later sales.
#| - pin == 09281140060000. Flood Factor 5/10 and in SFHA.  1918 Kennicott Ct Des Plaines. Class 205.
#| layout-ncol: 3


repeat_sales %>% 
  filter(pin == "09163040191019") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price))



repeat_sales %>% 
  filter(pin == "05201210150000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price))



repeat_sales %>% 
  filter(pin == "09281140060000") %>% 
  ggplot() +
  geom_line(aes(x=year, y = sale_price), lty = 1)+
  geom_point(aes(x=year, y = sale_price)) 


```


## Sales in and Out of FEMA SFHAs

```{r}
#| layout-ncol: 2

repeat_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Sales") |>
  mutate(
    Year = as.character(year),
    TotalSales = `In FP` + `Outside FP`,
    `FP Share (%)` = `In FP` / TotalSales,
   `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)) |>
  select(-c(TotalSales, year)) |> 
  mutate(Year = as.character(Year), .before = `In FP`) |> 
  select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |>
  flextable::flextable()


repeat_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  group_by(year, Location) |>
  summarize(Sales = n()) |>
  # ungroup() |>
   pivot_wider(names_from = "Location", values_from = "Sales") |>
   mutate(
     TotalSales = `In FP` + `Outside FP`,
     `FP Share (%)` = `In FP` / TotalSales,
     # `FP Share (%)` =  scales::percent(`FP Share (%)`, accuracy = 0.01)
   ) |>
  # select(-c(TotalSales, year)) |> 
  # mutate(Year = as.character(Year), .before = `In FP`) |> 
  # select(Year, `In FP`, `Outside FP`, `FP Share (%)`) |> 
  ggplot() +
  geom_line(aes(x=year, y= `FP Share (%)`)) + 
  scale_y_continuous(limits = c(0, 0.06), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Flood Plain Properties make up less than 1.5% of Sales",
       x = element_blank(),
       y = "Share of Sales")
```

```{r}
#| layout-ncol: 2

repeat_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
   Ratio =  scales::percent(Ratio, accuracy = 0.01),
   Year = as.character(year)) |> 
  select(Year, Sales, `In FP`, `Outside FP`, Ratio) |>
  flextable::flextable()

repeat_sales |> 
  filter(class >= 200 & class <= 299) |>
  mutate(Location = ifelse(in_eff_sfha == "Not SFHA", "Outside FP", "In FP" )) |> 
  mutate(Sales = n(), .by = year) |>
  group_by(year, Sales, Location) |>
  summarize(Price = round(median(sale_price))) |>
  ungroup() |>
  pivot_wider(names_from = "Location", values_from = "Price") |>
  mutate(Ratio = `In FP`/`Outside FP`,
  # Ratio =  scales::percent(Ratio, accuracy = 0.01)
   ) |>
  ggplot() +
  geom_line(aes(x=year, y = Ratio)) +
  scale_y_continuous(limits = c(0, 1), 
                     labels = scales::percent, expand = c(0, 0)) +
  scale_x_continuous(limits = c(2006, 2024), breaks = c(2006, 2010, 2015, 2020, 2024)) +
  
  theme_classic() +
  labs(title = "Ratio of Median Value for Properties In and Out of Floodplain",
       x = element_blank(),
       y = "Ratio",
       caption = "Ratio = Median Sale Price in FP / Median Price outside FP") 
```

## LOMRs

```{r}
#| label: tbl-pins-inlomrs
#| layout-ncol: 2
#| tbl-cap: "LOMR PINs"
#| tbl-subcap: 
#| - Grouped by LOMR date and municipality
#| - Grouped by municipality


repeat_sales |> 
  left_join(pin_muni_key) |> 
  filter(!is.na(lomr_date)) |>
  group_by(lomr_date, agency_name)|> 
  distinct(pin, lomr_date, in_lomr) |>
  summarize(pins_in_LOMR = sum(in_lomr == "Received LOMR", na.rm=TRUE)) |>
#  arrange(desc(pins_in_LOMR))
  arrange(desc(lomr_date))


repeat_sales |> 
  left_join(pin_muni_key) |> 
  filter(!is.na(lomr_date)) |>
  group_by(agency_name)|> 
  distinct(pin, in_lomr) |>
  summarize(pins_in_LOMR = sum(in_lomr == "Received LOMR", na.rm=TRUE)) |>
  arrange(desc(pins_in_LOMR))
```



```{r}
repeat_sales |> 
  filter(lomr2018 != lomr2024) |> 
  distinct(pin, sale_date, sale_price, lomr_date, lomr2018, lomr2024) |>
  arrange(lomr_date, pin) |>
  group_by(lomr2018, lomr2024) |> summarize(n = n())

```



```{r}

# 1) Make sure sale_date is a Date (if not already)
df_prep <- repeat_sales %>%
  filter(pin %nin% drop_pins) |> 
  
  mutate(
  #  sale_date2 = mdy(sale_date),         # parse "September 01 2018" → Date
    sale_year  = year(sale_date),       # or just use your existing `year` column
  eff_date = ymd(EFF_DATE),
  pre_date = ymd(PRE_DATE)
  ) %>%
  # 2) Keep only the columns we need for repeat‐sales. You can drop geometry, etc.
  select(pin, sale_date, sale_year, sale_price, in_eff_sfha, in_prelim_sfha, eff_date, pre_date, in_lomr) %>%
  # 3) Sort by pin and date
  arrange(pin, sale_date) %>%
  # 4) Tag how many times each PIN sold
  group_by(pin) %>%
  mutate(times_sold = n()) %>%
  ungroup() %>%
  # 5) Keep only those with at least two sales
  filter(times_sold >= 2)



# 6) Now create the “paired” records: for each pin, pull next‐row info as “t2”
df_pairs <- df_prep %>%
  group_by(pin) %>%
  arrange(sale_date) %>%
  # Lead‐lag step: each row’s “lag_” is the previous sale
  mutate(
    sale_price_t1   = lag(sale_price),
    sale_date_t1    = lag(sale_date),
    sale_year_t1    = year(sale_date_t1),
    in_sfha_t1      = lag(in_eff_sfha),
    in_sfha_t1      = ifelse(is.na(in_sfha_t1), "Not SFHA", in_sfha_t1),

    sale_price_t2   = sale_price,
    sale_date_t2    = sale_date,
    sale_year_t2    = sale_year,
    in_sfha_t2      = in_eff_sfha
  ) %>%

  ungroup() |> 
  select(-c(sale_price, sale_date, sale_year, in_eff_sfha))
```

```{r}
write_csv(df_prep, "./data/processed/df_prep.csv")
```

```{r }
df_pairs <- df_pairs %>%
  mutate(
        d_log_price = log(sale_price_t2) - log(sale_price_t1),  # same as log (sale2 / sale1)        
        # time between sales
         months_btwn = round(time_length(sale_date_t2 - sale_date_t1, "months")),  # between sales
         years_btwn = round(time_length(sale_date_t2 - sale_date_t1, "years")),    # between sales
        years_btwn = ifelse(years_btwn < 1, 1, years_btwn),
        ann_d_log_price = d_log_price / years_btwn,
        
        # binary variable options
    removed_between = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA"),
    added_between = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA"),
    stayed_sfha = (in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA"),
    neither_sfha = (in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA"),
    
    # SFHA change as a factor variable
    change_type = case_when(
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "Not SFHA" ~ "Removed",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "SFHA" ~ "Added",
      in_sfha_t1 == "SFHA" & in_sfha_t2 == "SFHA" ~ "Both In SFHA",
      in_sfha_t1 == "Not SFHA" & in_sfha_t2 == "Not SFHA" ~ "Both Out of SFHA",
      TRUE ~ "OTHER"
      
    )
  ) |>
  
  # add additional location variables (Triad, township, municipality, etc)
  left_join(pin_muni_key)

df_pairs <- df_pairs |> filter(change_type != "OTHER")

```


### Effective Dates

Models only use preliminary dates as of June 8th.

Models only use effective dates as of June 9th.

```{r code-for-effectiveFIRM}
df_pairs <- df_pairs |> 
  mutate(
    # years_btwn = sale_year_t2 - sale_year_t1,
    time_btw_sales = lubridate::as.difftime(sale_date_t2 - sale_date_t1),
    
    
    t1_months = round(time_length(sale_date_t1 - eff_date, "months") ), # first sale to FIRM update, in months
    t2_months = round(time_length(sale_date_t2 - eff_date, "months")),
    
    t1_years = round(time_length(sale_date_t1 - eff_date, "years") ),    # first sale to FIRM update, in years
    t2_years = round(time_length(sale_date_t2 - eff_date, "years")),     # time since FIRM update, in years
        
    t1_months_prelim = round(time_length(sale_date_t1 - pre_date, "months") ), # first sale to FIRM update, in months
    t2_months_prelim = round(time_length(sale_date_t2 - pre_date, "months")),
    
    t1_years_prelim = round(time_length(sale_date_t1 - pre_date, "years") ),    # first sale to FIRM update, in years
    t2_years_prelim = round(time_length(sale_date_t2 - pre_date, "years")),     # time since FIRM update, in years
    
  )|>
  # Only keep rows where lag exists (i.e. drop the very first sale for each PIN)
  filter(!is.na(sale_price_t1)) 


table(df_pairs$years_btwn, df_pairs$change_type)

table(df_pairs$sale_year_t2, df_pairs$change_type)
```


```{r}
df_pairs <- df_pairs |> 
  select(pin, 
         ann_d_log_price, d_log_price,
         sale_year_t1, sale_price_t1, in_sfha_t1, t1_months, t1_years,
         sale_year_t2, sale_price_t2, in_sfha_t2, t2_months, t2_years,
         years_btwn, removed_between, added_between, change_type, everything()
  )

df_pairs <- df_pairs |> 
  mutate(change_type = factor(change_type, levels = c("Both Out of SFHA", "Both In SFHA", "Added", "Removed")))  

# df_pairs <- df_pairs |>
#   filter(t1_years < -6 & t2_years > 6)


```


```{r exportdata}
# sampled_data <- df_pairs |>
#   sample_frac(0.1)
# write_csv(sampled_data,
#           "repeatsales_sample.csv")


saveRDS(df_pairs, file = "./data/processed/df_pairs.RDS")

table(df_pairs$years_btwn, df_pairs$change_type)

```




### PIN pair Descriptive Stats

```{r eval=FALSE, include = FALSE}
df_pin_summary <- df_pairs %>%
  group_by(pin) %>%
  summarize(
    n_pairs    = n(),
    avg_dlog   = mean(d_log_price),
    ever_removed = as.integer(any(removed_between == 1))
  )
```

## Add Location Variables to all PINs

```{r}
#| eval: false



pin_muni_key <- read_csv("./data/raw/pin_muni_key.csv")

nicknames <- readxl::read_xlsx("../Merriman RA/ptax/Necessary_Files/muni_shortnames.xlsx")

pin_muni_key <- pin_muni_key |> left_join(nicknames)


puni_pins <- read_csv("./data/raw/parcel_universe_currentyear.csv") |> 
  mutate(pin7 = str_sub(pin, 1, 7))

pin_muni_key <- left_join(pin_muni_key, puni_pins)
skim(pin_muni_key)


# List of columns to fill
fill_cols <- c("clean_name", "Triad", "Township",
               "nbhd_code", "zip_code")



parcels_first <- pin_muni_key  |> 
  mutate(pin10 = str_sub(pin, 1,10)) |>
  group_by(pin10) |>
  summarize(clean_name = first(clean_name, na_rm=TRUE),
            Triad = first(Triad, na_rm=TRUE),
            Township = first(Township, na_rm=TRUE),
            nbhd_code = first(nbhd_code, na_rm=TRUE),
            zip_code = first(zip_code, na_rm=TRUE))

parcels_first <- parcels_first |> 
  fill(clean_name, .direction = "down") |>
  fill(Township, .direction = "down") |>
  fill(Triad, .direction = "down") |>
  fill(nbhd_code, .direction = "down") |>
  fill(zip_code, .direction = "down")


# landblocks_first <- pin_muni_key  |> 
#   mutate(pin7 = str_sub(pin, 1,7)) |>
#   group_by(pin7) |>
#   summarize(clean_name = first(clean_name),
#             Triad = first(Triad),
#             Township = first(Township),
#             nbhd_code = first(nbhd_code),
#             zip_code = first(zip_code))

parcels_first <- pin_muni_key  |> 
  mutate(pin10 = str_sub(pin, 1,10)) |>
  group_by(pin10) |>
  summarize(clean_name = first(clean_name, na_rm=TRUE),
            Triad = first(Triad, na_rm=TRUE),
            Township = first(Township, na_rm=TRUE),
            nbhd_code = first(nbhd_code, na_rm=TRUE),
            zip_code = first(zip_code, na_rm=TRUE))

landblocks_first <- parcels_first  |> 
  mutate(pin7 = str_sub(pin10, 1,7)) |>
  group_by(pin7) |>
  summarize(clean_name = first(clean_name, na_rm = TRUE),
            Triad = first(Triad, na_rm = TRUE),
            Township = first(Township, na_rm = TRUE),
            nbhd_code = first(nbhd_code, na_rm = TRUE),
            zip_code = first(zip_code, na_rm = TRUE)) |>
    ungroup() |> 
  group_by(nbhd_code, zip_code) |>
  fill(clean_name, .direction = "downup") |>
  fill(Triad, .direction =  "downup") |>
  fill(Township, .direction = "downup") |> ungroup()

landblocks_last <- parcels_first  |> 
  mutate(pin7 = str_sub(pin10, 1,7)) |>
  group_by(pin7) |>
  summarize(clean_name = last(clean_name, na_rm = TRUE),
            Triad = last(Triad, na_rm = TRUE),
            Township = last(Township, na_rm = TRUE),
            nbhd_code = last(nbhd_code, na_rm = TRUE),
            zip_code = last(zip_code, na_rm = TRUE)) |>
  ungroup() |> 
  group_by(nbhd_code, zip_code) |>
  fill(clean_name, .direction = "downup") |>
  fill(Triad, .direction =  "downup") |>
  fill(Township, .direction = "downup") |> ungroup()

anti_join(landblocks_first, landblocks_last) |> arrange(pin7)

inner_join(landblocks_first, landblocks_last) |> arrange(pin7)

pin_muni_key <- left_join(pin_muni_key, landblocks_first) 
skim(pin_muni_key)

```


