---
title: "Model Graveyard"
format: html
---


## Effect of Insurance Requirement

### Effective FIRM Descriptive Stats

```{r recode-df_prep}
#| eval: false

table(df_prep$addedto_eff_sfha)

df_prep <- df_prep |> 
  # pin didn't exist in 2018 but did in 2024, so got considered as mapped out?
  mutate(
    removedfrom_eff_sfha = ifelse(pin10 == "1729309054", "0", removedfrom_eff_sfha),
         )




df_prep$removedfrom_eff_sfha
  
df_prep <- df_prep |>
  
  mutate(
    # so I can subset by FIRM date in later steps
    eff_date_chr = as.factor(eff_date),
    pre_date_chr = as.factor(pre_date),
    
    added_in    = addedto_eff_sfha == "MappedIn",
    removed_out = removedfrom_eff_sfha == "MappedOut" & in_lomr != "Received LOMR",
    added_in_prelim    = addedto_prelim_sfha == "MappedIn",
    removed_out_prelim = removedfrom_prelim_sfha == "MappedOut" & in_lomr != "Received LOMR"
  ) |>
  group_by(pin) |>
  mutate(
    # first year it was mapped IN (per PIN)
    treat_year_add_eff = ifelse((any(added_in == TRUE) ), 
                                # & eff_date_chr != "2008-08-19", 
                                year(eff_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_eff = ifelse(any(removed_out== TRUE)
                                   & eff_date_chr != "2008-08-19", 
                                   year(eff_date), 10000),
    
    
    # Added ore removed from Preliminary FIRMs
    treat_year_add_prelim = ifelse((any(added_in_prelim == TRUE) ), year(pre_date), 10000),  # never treated set to 10,000
    
    # first year it was mapped OUT (per PIN)
    treat_year_remove_prelim = ifelse(any(removed_out_prelim== TRUE), year(pre_date), 10000)
    
    
  ) |>
  ungroup() |>
  mutate(
    
    # Event time (relative year) for each outcome
    # coded to match S&A's method of relative time
    
    rel_year_add_eff    = ifelse(treat_year_add_eff != 10000,    sale_year - treat_year_add_eff,    -1000),
    rel_year_remove_eff = ifelse(treat_year_remove_eff != 10000, sale_year - treat_year_remove_eff, -1000),
    
    
    rel_year_add_prelim    = ifelse(treat_year_add_prelim != 10000,    sale_year - treat_year_add_prelim,    -1000),
    rel_year_add_prelim = ifelse(rel_year_add_prelim == 0 & sale_date < pre_date, -1, rel_year_add_prelim),
    rel_year_remove_prelim = ifelse(treat_year_remove_prelim != 10000, sale_year - treat_year_remove_prelim, -1000),
    rel_year_remove_prelim = ifelse(rel_year_remove_prelim ==0 & sale_date < pre_date, -1, rel_year_remove_prelim)
    
  ) |>
  mutate(
    qtr  = quarter(sale_date),     # 1..4
    year = year(sale_date),            
    sale_qtr_dec = year + (qtr - 1) / 4,        # 2012.00, .25, .50, .75
    
    group_name_eff = case_when(  # group variable, based on the time period that FIRMs were updated. which is when they were first treated.
      # used for callaway way I think? Delete soon or move. not needed for S&A method
      eff_date == "2008-08-19" ~ 0,
      eff_date == "2019-11-01" ~ 2019,
      eff_date == "2021-09-10" ~ 2021,
      TRUE ~ NA),
    

    
    # delete once checked that code still works if commented out
   # rel_time = round(lubridate::as.difftime(sale_date - eff_date) / 365), # get it to approximate years from event
  #  time_to_treat = round((sale_date - eff_date)/365)
    )
```

```{r}
#| tbl-cap: "Observations per year. Includes the pre and post treatment sales for those that were added or removed from an EFFECTIVE SFHA"
#| layout-ncol: 2
#| include: false
#| 

table(df_prep$sale_year, df_prep$treat_year_add_eff)

table(df_prep$sale_year, df_prep$treat_year_remove_eff)
```


```{r}
#| tbl-cap: "Observations per year. Added to (removed from) Effective SFHA"
#| layout-ncol: 2

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$addedto_eff_sfha[df_prep$sale_year>=2016])

table(df_prep$sale_year[df_prep$sale_year>=2016], df_prep$removedfrom_eff_sfha[df_prep$sale_year>=2016])
```




```{r}
# eff_date_chr and group_names should have same number of observations. 
table(df_prep$eff_date_chr)
table(df_prep$pre_date_chr)
table(df_prep$group_name_eff)

table(df_prep$addedto_eff_sfha)
table(df_prep$removedfrom_eff_sfha)
```


```{r}
#| tbl-cap: "Properties in South Triad that were removed from SFHA in 2019 and properties in South Triad that were always in the SFHA that were in FIRMs updated in 2019."


df_prep |> filter(Triad == "South" & treat_year_remove_eff == "2019") # all 2019 treatment pins are in South Triad

df_prep |> filter(Triad == "South" & change_type == "Always SFHA" & eff_date_chr == "2019-11-01") 
# change type only exists for effective 
```



- Reminder: Cohort should be fixed for each unit and represent the period when the treatment was received.   
- to get the canonical two-way fixed effects (TWFE) estimates, use interaction command  `i(factor_variable, number variable, reference_period)`    

- `iplot` reports coefficients of variables created with `i()` and only those variables. `coefplot()` would display all coefficients.   

If a PIN is in an SFHA and a LOMR, then the insurance requirement is removed. If measuring capitalization of the flood insurance cost, then whether or not flood insurance would be required for a federally backed mortgage is the key variable. This is what capitalization literature does. 

```{r}
df_prep  |> 
  group_by(sale_year, in_eff_sfha, in_lomr) |> summarize(n = n())

df_prep  |> 
  group_by(sale_year, removedfrom_eff_sfha, in_lomr) |> summarize(n = n())


df_prep  |> group_by(sale_year, ins_req) |> summarize(n=n())
table(df_prep$sale_year, df_prep$ins_req)
```


```{r}

lomr_pins <- readRDS("./data/processed/df_allsales.rds")  |> 
  filter(lomr_date != 0 ) |> 
  select(pin, lomr_date, sfha2024, sfha2018) |> distinct()


table(lomr_pins$lomr_date)
table(df_prep$removedfrom_eff_sfha)
table(df_prep$in_eff_sfha)
```

```{r}

table(df_prep$sale_year)

df_prep <- df_prep |>
  left_join(lomr_pins) |>
  group_by(pin) |>
  arrange(sale_year) |>
  mutate(
    removed = if_else(dplyr::lag(ins_req == TRUE) & ins_req == FALSE, TRUE, FALSE),
    removed_ever = any(removed, na.rm=TRUE) )|>
  ungroup() |>
  mutate(
    removed_date = if_else(removed_ever==TRUE & lomr_date > eff_date, lomr_date, NA_Date_),
    removed_date = if_else(removed_ever==TRUE & is.na(removed_date), eff_date, removed_date,
        
      #  removed_year = year(remove_date)
 #mutate(
       #  removed_FIRM = ifelse(removed==TRUE  & in_lomr != "Received LOMR", TRUE, FALSE),

       #  removed_LOMR = ifelse(removed==TRUE & in_lomr == "Received LOMR", TRUE, FALSE),

  #) |>
#  removed_year = ifelse(any(removed==TRUE & (lomr_date > eff_date)), lomr_date, eff_date),
          #  max(eff_date[removed==TRUE], lomr_date[removed==TRUE]),
          # removed_FIRM_date = last(eff_date[removed_FIRM == TRUE]),
          # removed_LOMR_year = min(year(lomr_date[removed_LOMR == TRUE]))
  )) |>
  ungroup() |>
  mutate(
  removed_year = if_else(!is.na(removed_date), year(removed_date), NA),
  rel_year_removed = if_else(!is.na(removed_year), as.integer(sale_year - removed_year), -1000))

     #    rel_year_FIRM_removed = round(lubridate::as.difftime(sale_date - removed_FIRM_date) / 365),
     #     rel_year_FIRM_removed = round(lubridate::as.difftime(sale_date - removed_FIRM_date) / 365)
    # ) #|>
 # mutate(across(rel_year_removed, is.infinite, -1000))


# df_prep[duplicated(df_prep),] # 5440 duplicates? from years 2010 to 2014 only.
table(df_prep$lomr_date)

df_prep <- df_prep |> distinct(pin, sale_date, sale_price, .keep_all = TRUE)
```


```{r}
df_prep$removed_year[is.na(df_prep$removed_year)] <- 10000
#df_prep$rel_year_removed[is.na(df_prep$rel_year_removed)] <- -1000
#df_prep$rel_year_removed[is.infinite(df_prep$rel_year_removed)] <- -1000

table(df_prep$removed_date)
table(df_prep$removed_ever)

table(df_prep$removed_year)
table(df_prep$rel_year_removed)

#df_prep$removed_year = as.factor(df_prep$removed_year)

```

```{r}
#| tbl-cap: "Removal of insurance requirement's effect on sale price."

twfe_removed2 = feols(log(sale_price) ~ removed  | 
                      pin + sale_year,   
                    cluster = ~clean_name,
                    data = df_prep#,
                  #  subset = ~ rel_year_removed!= -12
)
twfe_removed2|> etable()

```


### Insurance requirement removed due to LOMRs or Mapped Out of SFHA


```{r}

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed#,
                                      #ref.c = "10000", ref.p = c(-1, -1000)
                                      ) | pin + sale_year,
              cluster = ~clean_name,
              data = df_prep              )
#etable(mod2)
summary(mod2, agg= "att")

twfe_removed= feols(log(sale_price) ~ i(rel_year_removed,  ref =c(-1, -1000 ))  | 
                      pin + sale_year,   
                    cluster = ~clean_name,
                    data = df_prep#,
                             #     subset = ~ rel_year_removed != -12
)

#summary(twfe_removed)
#iplot(twfe_removed)


iplot(list(twfe_removed, mod2), #xlim = c(-8, 8), 
      main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
legend("topleft", col = c(1, 2), pch = c(20, 15), 
       legend = c("TWFE", "S&A (2020)"))

# switches order color/icon order
# iplot(list(mod2, twfe_removed), 
#       main = "Effect of Removal from SFHA (LOMR or FIRM Update)")
# legend("topleft", col = c(1, 2), pch = c(20, 15), 
#        legend = c("S&A (2020)", "TWFE"))
```

### Excludes PINs that were in LOMRs

```{r}
#| label: excludeslomrs

mod2 <- feols(log(sale_price) ~ sunab(cohort = removed_year, period = rel_year_removed, 
                                      ref.p = c(-1, -1000))  | pin + sale_year,
              cluster= ~pin,
              data = (df_prep |> filter(in_lomr == FALSE))
              )
#modelsummary::modelsummary(mod2, stars = TRUE)
summary(mod2, agg= "att")
# iplot(mod2)

#table(df_prep$in_lomr)
twfe_removed <-  feols(log(sale_price) ~ i(rel_year_removed,
                                           ref =c(-1, -1000 ))  | 
                         pin + sale_year,   
                       cluster = ~pin,
              data = (df_prep |> filter(in_lomr == FALSE))
                     #  subset = ~in_lomr == "Not in LOMR"
)

etable(twfe_removed)
#iplot(twfe_removed)

iplot(list(mod2, twfe_removed), 
      main = "Effect of Removal from SFHA (in_lomr == FALSE)")
legend("topleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("S&A (2020)", "TWFE"))


```





## From Q1 quarto: New attempt without subsets

need treatment cohort dummies

```{r}
#| label: tbl-asymeffect-sfha-regional-add
#| tbl-cap: "Heterogeneity of SFHA location assuming an Asymmetric effect"
#| eval: false


models <- list(

  # "Heterogeneity of SFHA location assuming an Asymmetric effect"
  added <- feols(
  log(sale_price) ~ group_name_prelim*addedto_prelim_sfha | pin + sale_year,
  data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
  cluster = ~ pin10
),

symmetric <- feols(
  log(sale_price) ~ group_name_prelim*in_prelim_sfha | pin + sale_year,
  data = df_prep,
  cluster = ~ pin10
),

# "Heterogeneity in Effect of being Mapped out of SFHA"
removed<- feols(
  log(sale_price) ~ group_name_prelim*removedfrom_prelim_sfha | pin + sale_year,
  data = df_prep |> filter(treat_year_add_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
  cluster = ~ pin10
)
)

modelsummary(models, stars = TRUE)
  
```





```{r}
#| label: tbl-etwfe
#| tbl-cap: "Extended TWFE? Ideally this is what Wooldridge (2025) would want?. For added to Prelim SFHA."
#| eval: false


#extended twoway fe?
twfemodels <- list(
  "TWFE" = feols(
    log(sale_price) ~ Triad*addedto_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  ),
  
  "TWFE 3 FEs" = feols(
    log(sale_price) ~ addedto_prelim_sfha | pin + Triad + sale_year,
    data = df_prep |> filter(treat_year_remove_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  ),
  
  
  "TWFE removed" = feols(
    log(sale_price) ~ Triad*removedfrom_prelim_sfha | pin + sale_year,
    data = df_prep |> filter(treat_year_add_prelim==10000),  # remove PINs that are removed from SFHA due to FIRM update
    cluster = ~ pin10
  )
)

modelsummary(twfemodels, stars = TRUE)

```



```{r}
# ============================================================
# Staggered adoption event-studies for:
#  (1) Added to preliminary SFHA  (cohort = treat_year_add_pre)
#  (2) Removed from preliminary SFHA (cohort = treat_year_remove_pre)
# Assumption per you: no unit is both added and removed.
# ============================================================

table(df_prep$treat_year_remove_prelim)
table(df_prep$treat_year_remove_prelim)
table(df_prep$Triad,df_prep$treat_year_remove_prelim)


# --- 0) Prep: cohorts (NA = never-treated), and log outcome
df_es <- df_prep %>%
  mutate(
    # Cohorts (your names)
    g_add_pre = if_else(treat_year_add_prelim == 10000, NA, treat_year_add_prelim),
    g_rem_pre = if_else(treat_year_remove_prelim == 10000, NA, treat_year_remove_prelim)
  )
table(df_es$g_add_pre)
table(df_es$g_rem_pre)

# --- 1) Risk sets (clean because no unit is both added and removed)
# Added model: exclude any "removed" units (if they exist at all)
df_add <- df_es %>% filter(is.na(g_rem_pre))

# Removed model: exclude any "added" units (if they exist at all)
df_rem <- df_es %>% filter(is.na(g_add_pre))

# --- 2) Staggered event studies (Sun & Abraham) with unit FE + year FE
m_add_pre <- feols(
  log(sale_price) ~ sunab(g_add_pre, sale_year, ref.p = -1) | pin + sale_year,
  data = df_add,
  cluster = ~ pin10
)

m_rem_pre <- feols(
  log(sale_price) ~ sunab(g_rem_pre, sale_year,  ref.p = -1) | pin + sale_year,
  data = df_rem,
  cluster = ~ pin10
)

# --- 3) Plots (leads/lags around ref period -1)
iplot(m_add_pre,
      main = "Event study: Added to preliminary SFHA",
      xlab = "Event time (years relative to addition)",
      ylab = "Effect on log price")

iplot(m_rem_pre,
      main = "Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")

# --- 4) Table-ready coefficient output
# (a) Quick regression table
etable(m_add_pre, m_rem_pre,
       headers = c("Added (prelim SFHA)", "Removed (prelim SFHA)"),
       se.below = TRUE)

# (b) Data frame of event-time coefficients (nice for custom tables/ggplot)
add_coefs <- as.data.frame(coeftable(m_add_pre), stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("term")

rem_coefs <- as.data.frame(coeftable(m_rem_pre), stringsAsFactors = FALSE) %>%
  tibble::rownames_to_column("term")

# --- 5) Joint pre-trends tests (all leads = 0)
# This tests whether the *pre-treatment* event-time coefficients are jointly zero.
# Pattern below is conservative: it grabs any sunab term with a negative event time.
lead_terms_add <- grep("sunab\\(.*\\)::[-][0-9]+", add_coefs$term, value = TRUE)
lead_terms_rem <- grep("sunab\\(.*\\)::[-][0-9]+", rem_coefs$term, value = TRUE)

if(length(lead_terms_add) > 0) {
  cat("\nJoint pre-trends test (Added):\n")
  print(wald(m_add_pre, lead_terms_add))
}

if(length(lead_terms_rem) > 0) {
  cat("\nJoint pre-trends test (Removed):\n")
  print(wald(m_rem_pre, lead_terms_rem))
}
```


```{r}
#| eval: false

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_remove_prelim, ref = "2021") | pin+ sale_year,
  #data = (df_prep |> mutate(addedto_prelim_sfha = ifelse(addedto_prelim_sfha=="-1000", NA, addedto_prelim_sfha))),
  data = df_prep |> filter(Triad== "North"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "North Cook Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")

 m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_remove_prelim, ref = "2015") | pin + sale_year,
  data = df_prep |> filter(Triad== "South"),
  cluster = ~ pin10
)
iplot(m_rem_pre,
      main = "South Cook Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")



```



```{r}
#| eval: false

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2021") | pin + sale_year,
  data = df_prep |> filter(Triad== "North"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "North Cook Event study: Added to preliminary SFHA",
      ylab = "Effect on log price")

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2015") | pin + sale_year,
  data = df_prep |> filter(Triad== "South"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "South Cook Event study: Added from preliminary SFHA",
      ylab = "Effect on log price")

m_rem_pre <- feols(
  log(sale_price) ~  + i(sale_year, treat_year_add_prelim, ref = "2019") | pin + sale_year,
  data = df_prep |> filter(Triad== "City"),
  cluster = ~ pin10
)

iplot(m_rem_pre,
      main = "Chicago Event study: Added from preliminary SFHA",
      ylab = "Effect on log price")
```

```{r}
# --- 6) Optional: add geography-by-year trends instead of subsetting (edit Triad var name)

m_add_pre_geo <- feols(log(sale_price) ~ sunab(g_add_pre, sale_year, ref.p = -1) | pin + sale_year + Triad^sale_year,
                         data = df_add, cluster = ~ pin10)
  
  ## Triad FE don't work with removed because the year and triad are collinear
  m_rem_pre_geo <- feols(log(sale_price) ~ sunab(g_rem_pre, sale_year, ref.p = -1) | pin + sale_year,
                         data = df_rem, cluster = ~ pin10)


etable(m_add_pre_geo, m_rem_pre_geo)

summary(m_add_pre_geo, agg = "att" )
summary(m_rem_pre_geo, agg = "att")

```


```{r}
iplot(m_add_pre_geo,
      main = "Event study: Added to preliminary SFHA",
      xlab = "Event time (years relative to addition)",
      ylab = "Effect on log price")

iplot(m_rem_pre_geo,
      main = "Event study: Removed from preliminary SFHA",
      xlab = "Event time (years relative to removal)",
      ylab = "Effect on log price")
```




```{r}
#| label: tbl-feolsmodels-fixedeffects-with_df_prep_2
#| tbl-cap:  "Uses df_prep_2 which makes sure there is only one transaction per PIN-sale_year combo. Did not significantly change results."
#| eval: false

# groups by PIN and year and calculates the average sale price (PLM does not like duplicate observations per id-time unit in its panel regressions).

df_prep_2 <- df_prep |>
  arrange(pin, sale_date) |>
  summarise(
    sale_price = mean(sale_price),
    log_sale_price  = mean(log(sale_price)),
    across(c(in_prelim_sfha, in_eff_sfha, in_lomr, change_type,
             #addedto_eff_sfha, removedfrom_eff_sfha,
    treat_year_add, rel_year_add, treat_year_remove, rel_year_remove,
             Triad),
           ~ dplyr::last(.x)),
    .by = c(pin, sale_year, eff_date, pre_date)
  )

df_prep <- df_prep |> mutate(sale_year = as.factor(sale_year))

all_models <- list(
  
  "Eff SFHA" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,   
                   data = df_prep_2
  ),
  
  "Prelim SFHA" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                      data = df_prep_2
                      
  ),
    "Eff SFHA" = feols(log(sale_price) ~ in_eff_sfha  | pin + sale_year,  
                       vcov= "hetero",
                   data = df_prep_2
  ),
  
  "Prelim SFHA" = feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year,
                        vcov="hetero",
                      data = df_prep_2
                      
  ),
  
  "With LOMRs" = feols(log(sale_price) ~ in_eff_sfha + in_lomr | pin + sale_year,
       
                     data = df_prep_2
  ),
  
  "Prelim SFHA w LOMRs" = feols(log(sale_price) ~ in_prelim_sfha + in_lomr | pin + sale_year,
                      data = df_prep_2
                      
  ),
  
  "Eff. With LOMRs" = feols(log(sale_price) ~ in_eff_sfha + in_lomr | pin + sale_year,
                               vcov="hetero",

                     data = df_prep
  ),
  
  "Prelim SFHA w LOMRs" = feols(log(sale_price) ~ in_prelim_sfha + in_lomr | pin + sale_year,                        vcov="hetero",

                      data = df_prep
                      
  )
  ) 


all_models_formatted <- modelsummary::modelsummary(all_models,
               output = "flextable",
               fmt = function(x) round(x, 2),

             stars = TRUE)

all_models_formatted

```


# In FIRM or not In SFHA

```{r}
#| label: tbl-clustervariations
#| tbl-cap: "Robustness checks: Model variations with different clustering."
#| eval: false


# --- Your models (estimate ONCE each) ---
m1 <- feols(log(sale_price) ~ in_eff_sfha | pin + sale_year, data = df_prep)
m2 <- feols(log(sale_price) ~ in_eff_sfha * Triad | pin + sale_year, data = df_prep)
m3 <- feols(log(sale_price) ~ in_prelim_sfha | pin + sale_year, data = df_prep)
m4 <- feols(log(sale_price) ~ in_prelim_sfha * Triad | pin + sale_year, data = df_prep)

models <- list("Eff" = m1, "EFF*Triad" = m2, "Prelim" = m3, "Prelim*Triad" = m4)

# --- Define clustering schemes (edit to your geography variables) ---
clusters <- list(
  "PIN"         = ~ pin,
  "PIN × Year"  = ~ pin + sale_year,
  "Muni"        = ~ clean_name,
  "Muni × Year" = ~ clean_name + sale_year  # or municipality if that's your column
)

# --- Build summaries for all model × cluster combos ---
sums <- list()
for (mname in names(models)) {
  for (cname in names(clusters)) {
    lbl <- paste(mname, "·", cname)  # e.g., "M1 · PIN"
    sums[[lbl]] <- summary(models[[mname]], cluster = clusters[[cname]])
  }
}

# --- Optional: clean coefficient labels (add/modify as needed) ---
cm <- c(
  "in_eff_sfhaSFHA"          = "In Effective SFHA",
  "in_prelim_sfhaSFHA"       = "In Preliminary SFHA",
 # "TriadNorth"               = "Triad: North",
 # "TriadSouth"               = "Triad: South",
  "in_eff_sfhaSFHA:TriadNorth"   = "In Eff SFHA × North",
  "in_eff_sfhaSFHA:TriadSouth"   = "In Eff SFHA × South",
  "in_prelim_sfhaSFHA:TriadNorth"= "In Prelim SFHA × North",
  "in_prelim_sfhaSFHA:TriadSouth"= "In Prelim SFHA × South"
)

# --- Make nested-column table (panels group by model) ---
ms_tbl <- modelsummary(
  sums,
  output = "flextable",              # "html", "latex", "docx" also work
  coef_map = cm,                    # optional for labeled coefficents instead of variable names
  stars = TRUE,
  gof_omit = "IC|Log|Adj|Pseudo",  # keep the table tight
  escape = FALSE                   # keep the × symbol
)

ms_tbl

```

# Added or Removed from SFHA
```{r}
#| label: tbl-addedremoved-fixedeffects


m1 = feols(log(sale_price) ~ addedto_eff_sfha + removedfrom_eff_sfha | pin + sale_year,   
                   data = df_prep
)

models <- list ("Add or Removed" = m1)
# --- Define clustering schemes (edit to your geography variables) ---
clusters <- list(
  "PIN"         = ~ pin,
  "PIN × Year"  = ~ pin + sale_year,
  "Muni"        = ~ clean_name,
  "Muni × Year" = ~ clean_name + sale_year  # or municipality if that's your column
)

# --- Build summaries for all model × cluster combos ---
sums <- list()
for (mname in names(models)) {
  for (cname in names(clusters)) {
    lbl <- paste(mname, "·", cname)  # e.g., "M1 · PIN"
    sums[[lbl]] <- summary(models[[mname]], cluster = clusters[[cname]])
  }
}


ms_tbl <- modelsummary(
  sums,
  output = "flextable",              # "html", "latex", "docx" also work
  stars = TRUE,
  gof_omit = "IC|Log|Adj|Pseudo",  # keep the table tight
  escape = FALSE                   # keep the × symbol
)

ms_tbl

```

